### 2019-03-30 stableLimit.tex
add stableLimit.tex

%---The preamble----------------------
\documentclass[12pt, a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{stackrel}
\usepackage{autonum}
\usepackage[utf8]{inputenc}
\usepackage{comment}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{innerasp}{Assumption}
\newenvironment{asp}[1]{\renewcommand\theinnerasp{#1}\innerasp}{\endinnerasp}
\numberwithin{equation}{section}

%---Top matter------------------------------
\begin{document}
\title
	[Manuscript]
	{\large Limit theorems for a class of critical superprocesses with stable branching}
\author{Yan-Xia Ren, Renming Song and Zhenyao Sun}
%---Yan-Xia Ren
\address
	{Yan-Xia Ren\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
%---Renming Song
\address
	{Renming Song\\
	Dept of Mathematics\\
	University of Illinois at Urbana-Champaign\\
	Urbana, IL 61801}
\email{rsong@illinois.edu}
\thanks{The research of Renming Song is supported in part by the Simons Foundation (\#429343, Renming Song).}
%---Zhenyao Sun
\address
	{Zhenyao Sun\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\curraddr
	{Department of Mathematics\\
	University of Illinois at Urbana-Champaign\\
	Urbana, IL 61801}
\email{zhenyao.sun@pku.edu.cn}
%\thanks{Zhenyao Sun is supported by the China Scholarship Council.}
\begin{abstract}
\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%\tableofcontents
%---Contents-----------------------
\section{Introduction}

\subsection{Motivation and literature review}

	The study of the asymptotic behavior of the critical branching particle system has a long history.
	It is well known that for a critical Galton-Watson process $(Z_n)$, we have
	\[\label{eq: Kolmogorov's result with finite variance}
		n P(Z_n > 0) 
		\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2},
	\]
	and
	\[\label{eq: Yaglom's result with finite variance}
		\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
		\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e, 
	\]
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}. 
	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.  
	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2rd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.

	Note that result \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2rd moment is infinite, i.e. $\sigma^2 = \infty$. 
	In this case, the scaling limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so more proper scaling is required.
	This was firstly obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
	which is then extended by Slack \cite{Slack1968A-branching} for discrit time critical Galton-Watson processes allowing infinite variance:  Consider the critical Galton-Watson process $(Z_n)$ with infinite variance. 
	Assuming that the offspring generating function $f(s)$ takes the form
\[\label{eq: offspring generating function with alpha moment}
	f(s) 
	= s + (1-s)^{1+ \alpha} l(1-s), 
	\quad s\geq 0,
\]
	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$, then
\[ \label{eq: extinction probability of critical GW process without 2rd moment}
	P(Z_n > 0) = n^{-1/\alpha} L(n),
\]
	where $L$ is a slowly varying function at $\infty$, and
\[\label{eq: conditional distribution of critical GW process without 2rd moment}
	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
\]
	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
\[
	E[e^{- u \mathbf z^{(\alpha)}}]  
	= 1 - (1+ u^{-\alpha})^{-1/\alpha}, 
	\quad u \geq 0.
\]
	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ the \emph{Zolotarev's distribution with index $\alpha$}.
	Slack \cite{Slack1972Further} considered the converse of this problem: 
	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must take the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
	For shorter and more unified approaches to these results, we refer our reader to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson process without 2rd moment condition:
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ denote a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denoted by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function. 
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ its left and right principle eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ the vector $(1,\dots, 1)$.
	Suppose that
\[\label{eq: regularly varying condition for multitype branching process}
	\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u 
	= x^\alpha l(x),
	\quad x > 0,
\]
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and  the matrix $E(\mathbf s)$ is defined by
\[
	\mathbf 1 - \mathbf F(\mathbf s) 
	= (M - E(\mathbf s))(\mathbf 1 - \mathbf s), 
	\quad \mathbf s \in \mathbb R_+^d.
\]
	Then \cite{GoldsteinHoppe1978Critical} shows that, if we let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ the vector $(0,\dots, 0)$, then for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{Pr}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha 
	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha, 
\]
	and for each $\mathbf j \in \mathbb N_0^d$
\[\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)}.
\]
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.  
	Vatutin \cite{Vatutin1977Limit} also considered analogue results for the continuous time mutitype critical Galton-Watson processes.

	Asmussen and Hering \cite{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M) see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$ (see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
	In the case without the finite second moment, under a condition  paralleling  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), they proved results (see \cite[Theorem 4.2]{AsmussenHering1983Branching}) paralleling to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} for the critical branching Markov processes.

	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
\[ \label{eq: branching mechanism}
	\psi(x,z):= 
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy), 
	\quad x\in E, z\geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\alpha \in bp\mathscr B_E$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ s.t. $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
	We refer our reader to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.

	Results paralleling to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}. 
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses when  the branching mechanism is $(x,z)\mapsto z^2$ and the spatial motion satisfies some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} refined their results for a class of critical superprocesses with general branching mechanism and general spatial motions: 
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$. 
	Suppose that its spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and its branching mechanism $\psi$ satisfies the following second moment condition:
\[\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\]
	Under some other mild assumptions, it was proved by Ren, Song and Zhang \cite{RenSongZhang2015Limit} that
\[\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(X_t \not \equiv 0) 
	\xrightarrow[t\to \infty]{} c^{-1} \langle \phi, \mu \rangle_m,
\]
	and for a large class of testing functions $f$ on $E$,
\[\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot | X_t \not\equiv 0)\} 
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\]
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$; 
	$\mathbf e$ is an exponential random variable with mean $1$; 
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$. 
	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to result \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	As a continuation of those works, it is natural to ask weather results paralleling to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} can be obtained for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	Perhaps a simpler version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements. 
	Kyprianou \cite{Kyprianou2008Continuous} considered a CSBP $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$, 
\[ \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\} 
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} generalized this result, by considering a CSBP with branching mechanism 
\[\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z) 
	= c z^\gamma l(z), 
	\quad z\geq 0.
\] 
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$. 
	They showed that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\[\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Later, \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ which verifying Grey's condition. 
	In order the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

	In this paper, we establish a result paralleling to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form 
\[
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\gamma \in bp\mathscr B_E$, $\kappa \in bp\mathscr B_E$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$. 
	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ convergence to $0$ while $t\to \infty$, and is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that 
\[
	\mathbf P_{\delta_x}( X_t \not \equiv 0) 
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t
\] 
	and for a large class of non-negative testing function $f$,
\[
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}} 
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\] 
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
	A regrously statements of the assumptions and the results are presented in the next subsection.
	Perhaps it is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ is primarily depended only by the lowest index $\gamma_0$.

\subsection{Model and results}

	We first set some notations.
	For any measurable space $(E,\mathscr E)$, denote by $r\mathscr E$ the colloction of all the measurable real function on $E$. 
	Define $b\mathscr E :=\{f \in r\mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $p\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $s\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\neq 0\}$. 
	Define $bp\mathscr E := b\mathscr E \cap p\mathscr E$, $bs\mathscr E:= b\mathscr E \cap s\mathscr E$, $sp\mathscr E:= s\mathscr E \cap p\mathscr E$ and $spb\mathscr E : = s\mathscr E \cap p\mathscr E \cap b\mathscr E$.	
	Denote by $\mathcal M_E$ the collection of all the measures on $(E,\mathscr E)$.
	Denote by $\mathcal M^\sigma_E$ the collection of all the $\sigma$-finite measures on $(E,\mathscr E)$. 
	In this paper, to simplify the notation, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$. 
	We also write $\langle f,g\rangle_m$ meaning $ \int_E fg dm$ if we want to emphasize the inner product structure of Hilbert space $L^2(dm)$.
	For any $\phi \in p\mathscr E$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
	In particular, $\mathcal M^1_E$ is the collection of all the finite measures on $E$.
	If $E$ is a topology space, denote by $\mathscr B_E$ the collection of all the Borel measurable subset of $E$.

	We now give the definition of a $(\xi, \psi)$-superprocess: 
	Let the \emph{state space} $E$ be a locally compact separable metric space,
	the \emph{underlying motion} $\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be a $E$-valued Hunt process with its life time denoted by $\zeta$, and the \emph{branching mechanism} $\psi$ being a function on $ E\times [0,\infty)$ with form of \eqref{eq: branching mechanism}.
	We say a $\mathcal M^1_E$-valued Hunt process $\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  testing function $f\in bp\mathscr B_E$, we have
\[
	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
\] 
	where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is defined as the unique locally bounded positive solution to the equation
\[\label{eq:FKPP_in_definition}
	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
	=\Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
	t\geq 0, x \in E.
\]
	(In this paper, to simplify the notation, for any real function $F$ on $E\times [0,\infty)$ and real function $f$ on $E$, we simply write $F(x,f):= F(x,f(x)).$)

	Define the \emph{Feyman-Kac semigroup} 
\[
	P^\beta_tf(x) 
	= \Pi_x \big[e^{\int_0^{t\wedge \zeta} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
	\quad t\geq 0, x\in E, f\in b\mathscr B_E.
\]
	(Notice that if $\beta \equiv 0$, then $P_t:= P^\beta_t$ is the \emph{transition semigroup} of process $\{\xi; \Pi\}$.) 
	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
	\[ \label{eq: Ygalom type result without 2rd moment}
	\mathbf P_\mu [X_t(f)]
	= \mu(P^\beta_t f),
	\quad \mu \in \mathcal M_f, t \geq 0,f \in b\mathscr B_E.
	\]
	This mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
	As it already be discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} or \eqref{eq: Ygalom type result without 2rd moment}, we have to first establish the asymptotic behavior of the mean semigroup. 
	This can be done under the following assumptions on the underlying motion $\{\xi; \Pi\}$:
\begin{asp}{1}
\label{asp: 1}
	There exists an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$, and a family of strictly positive, bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that,
\[\begin{split}
	\Pi_x[ f(\xi_t)\mathbf 1_{t < \zeta} ]
	= \int_E p_t(x,y) f(y) m(dy),
	&\quad t>0, x \in E,f \in b\mathscr B_E;
	\\\int_E p_t(y,x)m(dy)
	\leq 1,	
	&\quad t>0,x\in E;
	\\\int_E \int_E p_t(x,y)^2 m(dx) m(dy)
	<\infty,
	&\quad t> 0;
\end{split}\]
	and, $x \mapsto \int_E p_t(x,y)^2 m(dy)$, $x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous on $E$.
\end{asp}

	Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
\[
	e^{-\|\beta\|_\infty t} p_t(x,y)
	\leq p^{\beta}_t(x,y)
	\leq e^{\|\beta\|_\infty t} p_t(x,y),
	\quad t>0, x, y\in E,
\]
	and that for any $t>0, x\in E$ and $f \in b\mathscr B_E$,
\[
	P^\beta_t f(x)
	= \int_E p_t^\beta (x,y) f(y) m(dy).
\]
	We will call $(p^\beta_t)$ the \emph{transition density of semigroup $(P^\beta_t)$}.
	Define a family of transition kernels $(P^{\beta *}_t)_{t \geq 0}$ on $E$ by
\[
	P^{\beta *}_0 = I;
	\quad P^{\beta *}_t f(x)
	:= \int_E p^\beta_t (y,x) f(y) m(dy),
	\quad t>0, x\in E, f\in b\mathscr B_E.
\]
	It is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and its dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
	Let $L$ and $L^*$ be the generators of the semigroups $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$, respectively.
	Denote by $\sigma(L)$ and $\sigma(L^*)$ the spectra of $L$ and $L^*$, respectively.
	According to \cite[Theorem V.6.6.]{Schaefer1974Banach}, $\lambda := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common eigenvalue of multiplicity $1$ for both $L$ and $L^*$.
	Using the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\phi$ of $L$ and $\phi^*$ of $L^*$ associated with the eigenvalue $\lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
	We further normalize $\phi$ and $\phi^*$ by $\langle\phi, \phi\rangle_m = \langle\phi,\phi^*\rangle_m = 1$ so that they are unique.
	Moreover, for each $t\geq 0,x\in E$, we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$. 
	We refer to $\phi$ (repct. $\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of the simegroup $(P^\beta_t)_{t\geq 0}$ (respct. $(P^{\beta *}_t)_{t\geq 0}$).

	Now, from
\[
	\mathbf P_\mu[X_t(\phi)] 
	= e^{\lambda t} \mu(\phi).
\]  
	we see that, if $\lambda > 0$, the mean of $X_t(\phi)$ will increase exponentially; if $\lambda < 0$, the mean of $X_t(\phi)$ will decrease exponentially; and if $\lambda = 0$, the mean of $X_t(\phi)$ will be a constant. 
	Therefore, we say $X$ is \emph{supercritical, critical or subcritical}, according to $\lambda > 0$, $\lambda = 0$ or $\lambda < 0$, respectively.
	Since we are only interested in the critical case, we assume the following:
\begin{asp}{2} \label{asp: 2}
	The superprocess $(X_t)$ is critical, i.e. $\lambda = 0$.
\end{asp}

	Let $\varphi$ (respect. $\varphi^*$) be the principal eigenfunction of (respct. the dual of) the transition semigroup $(P_t)$ of the underlying process $\{\xi;\Pi\}$. Our second assumption on the underlying process $\{\xi; \Pi\}$ is the following:

\begin{asp}{3} \label{asp: 3}
	$\varphi$ is bounded, and $(P_t)$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
\end{asp}

	Under Assumption \ref{asp: 3},	It is proved in \cite{RenSongZhang2017Central,RenSongZhang2015Limit} that the principal eigenfunction $\phi$ of Feyman-Kac semigroup $(P^\beta_t)$ is also bounded.
	Moreover, $(P^\beta_t)$ is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ s.t. for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
	In fact, it is proved by \cite{KimSong2008Intrinsic} that for each $t>0$, $(p^\beta_t(x,y))_{x,y\in E}$ is comparable to $(\phi(x)\phi^*(y))_{x,y\in E}$ in the sense that there is a constant $c_t > 1$ s.t. 
\[\label{eq: p-t-beta is comparable to phi phi-star}
	c_t^{-1}
	\leq \frac {p^\beta_t(x,y)} {\phi(x)\phi^*(y)}  
	\leq c_t,
	\quad x,y \in E.
\]
	It is also shown in \cite{KimSong2008Intrinsic} that $(e^{-\lambda t}p^\beta_t(x,y))_{x,y\in E}$ is asymptotic equivalent to $\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ uniformly in $x$ and $y$, and exponentially fast while $t\to \infty$, in the sense that, there are constants $c_0,c_1 > 0$ s.t. 
\[\label{eq:q(t,x,y)}
	\sup_{x,y\in E} \big|\frac{e^{-\lambda t}p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \big| \leq c_0 e^{-c_1 t},
	\quad t > 1.
\]
	We refer our reader to \cite{RenSongZhang2015Limit} for a list of examples of underlying processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.

	In this paper, we will only consider the superprocesses with the following spatially dependent stable branching:
\begin{asp}{4} \label{asp: 4}
	The branching mechanism $\psi$ takes the following form:
\[\begin{split}
	\psi(x,z) 
	&= - \beta(x) z + \kappa(x) \int_0^\infty (e^{-z y} - 1+ z y) \frac{dy}{\Gamma(- \gamma(x)) y^{1+ \gamma(x)}}
	\\&= -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\end{split}\]
	where $\beta \in b\mathscr B_E, \gamma \in bp\mathscr B_E$ and $\kappa \in spb\mathscr B_E$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
\end{asp}
	Note that here, we used the definition of the Gamma function on the negative real line:
\[\label{eq: definition of Gamma function}
	\Gamma(x) 
	:= \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt, 
	\quad -n< x< -n+1, n\in \mathbb N.
\]

	We now present the main results of this paper:

\begin{thm}
\label{thm: main theorem}
	Suppose that $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M_E^1}\}$ is a $(\xi, \psi)$-superprocess satisfying Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}. Then,
\begin{itemize}
	\item[(1)] $\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$. 
	\item[(2)] For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$ convergences to $0$ while $t\to \infty$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$. 
	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then 
\[
	\mathbf P_{\delta_x}(X_t \not \equiv 0)
	\stackrel[t\to \infty]{}{\sim} \phi(x)\eta_t.
\]
	\item[(3)] Suppose $m( x:\gamma(x)=\gamma_0 )>0$. 
	Let $f \in p\mathscr B$ be a testing function such that $\langle f, \phi^* \rangle_m > 0$  and $\| \phi^{-1}f \|_\infty < \infty$, then
\[
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}} 
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}.
\]  
\end{itemize}
	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
\end{thm}

\subsection{Methods and overview}

	In this paper, to establish the Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition method of superprocess $\{X; \mathbf P\}$.
	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the summation of an original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
	The family of functions used for the size-biased transform is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$, which is a martingale. 
	Therefore, this size-biased transformation can be viewed as a martingale change of measure. 
	Under the Assumption \ref{asp: 1} and \ref{asp: 3}, the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process. 
	To study the asymptotic behavior of superprocesses, one can take advantage of this ergodicity.

	This idea has already been used by Powell \cite{Powell2015An-invariance} while establishing results paralleling to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes. 
	Let $(Y_t)$ be a branching diffusion processes in a bounded domain with finite second moment.
	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation which is known to be satisfied by $(t,x) \mapsto P(Y_t \not\equiv 0)$, the survival probability for branching diffusion process, is tricky.
	Instead, using a spine decomposition approach, \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principle eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capture the uniform speed. 
	Then, the problem is reduced to the study of a single ODE satisfied by the speed function $a(t)$.
	Later, inspired by \cite{Powell2015An-invariance}, in \cite{RenSongSun2017Spine}, we gave a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of critical superprocesses with finite second moment.
	In this paper, we are able to generalize those arguments for a class of critical superprocesses without the finite second moment, and establish Theorem \ref{thm: main theorem}(2).

	For the conditional weak convergence result, i.e. Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform of Zolotarev's distribution can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
	Using the spine method, we show that the Laplace transform of the one-dimensional conditioned distributions for the superprocess, after a proper rescaling, can also be characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
	Then, the desired convergence of the distributions can be established by a comparison between equations.	
	Again, the ergodicity of the spine process plays a central role in the comparison.

	A similar idea of establishing conditional weak convergence to the exponential distribution, though a comparison of distributional equations method, have already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}. 
	To be precise, we characterized the exponential distribution using an $x^2$-transform distributional equation; and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
	However, the $x^2$-transform of a random variable requires the existence of its finite variance. 
	In this paper, since we don't have the finite variance, we can not use the method of $x^2$-transform. 
	Instead, a non-linear delay equation is used.

	In \cite{Powell2015An-invariance}, for the critical branching diffusion in a bounded domain with finite variance, and in \cite{RenSongZhang2015Limit} and \cite{RenSongSun2017Spine}, for the critical superprocess with finite variance, when the authors were establishing the conditional weak convergence, they did not proved the results for all general testing functions $f$ at the same time.
	Instead, the authors first established the results for a specific testing function $\phi$, the principle eigenfunction of the mean matrix of the corresponding processes, and then passed the result to a general testing function $f$. 
	While passing to the general result, \cite{Powell2015An-invariance}, \cite{RenSongZhang2015Limit} and \cite{RenSongSun2017Spine} all used a second moment argument to control the differences.

	However, in this paper, since we simply don't have the second moment, this type of argument fails to hold.
	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for all general testing function $f$ at the same time.
	This generalized spine decomposition theorem considered the $X_T(g)$-transform of the superprocess $(X_t)_{0\leq t\leq T}$ for a large class of general function $g$.
	The transformed process behaves similarly as in the classical case, despite that, the spine process $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$ is not the same.

	The rest of this paper is organized as follows:  
	In Section \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly varying functions and superprocesses, respectively. 
	In Section \ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem. 
	In Section \ref{sec: Ergodicity}, we discuss the ergodicity of the spine process.
	In Section \ref{sec: proof of result 1} and \ref{sec: proof of result 2} we give the poof of Theorem \ref{thm: main theorem}(1) and \ref{thm: main theorem}(2), respectively. 
	In Section \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
	In Section \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize Zolotarev's distribution.
	Finally, in Section \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
\section{Preliminaries}
\label{sec: Preliminaries}

\subsection{Asymptotic equivalence}
\label{sec: Asymptotic equivalence}
	In this subsection, we give a lemma about the asymptotic equivalence.	
	Let $t_0 \in [-\infty,\infty]$.
	For any $f_0, f_1\in s\mathscr B_{\mathbb R}$, we say $f_0$ and $f_1$ are \emph{asymptotic equivalent at $t_0$}, if $\big|\frac{f_0(t)}{f_1(t)} - 1\big| \xrightarrow[t\to t_0]{} 0$;
	and in this case, we write $f_0(t) \stackrel[t\to t_0]{}{\sim} f_1(t)$.
	Let $E$ be a measurable space.
	For any $g_0, g_1\in s\mathscr B_{\mathbb R\times E}$, we say $g_0$ and $g_1$ are \emph{uniformly asymptotic equivalent at $t_0$}, if $\sup_{x\in E}\big|\frac{g_0(t,x)}{g_1(t,x)} - 1\big| \xrightarrow[t\to t_0]{} 0$; and in this case, we write $g_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}g_1(t,x)$.

\begin{lem}
\label{lem: asymptotic equivalent of integration}
	Suppose that $f_0,f_1\in spb\mathscr B_{\mathbb R \times E}$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
	Let $m \in \mathcal M^1_E$. Then we have 
\[
	\int_E f_0(t,x)m(dx) 
	\stackrel[t\to t_0]{}{\sim}
	\int_E f_1(t,x)m(dx) 
\]
\end{lem}
\begin{proof}
	We see that
\[\begin{split}
	&\Big| \frac{	\int_E f_0(t,x)m(dx) }{ 	\int_E f_1(t,x)m(dx)  } - 1 \Big|
	= \Big| \int_E \frac{f_0(t,x)}{f_1(t,x)} \frac{f_1(t,x)m(dx)}{	\int_E f_1(t,y)m(dy)  } - 1\Big|
	\\&\quad \leq \int_E \Big|  \frac{f_0(t,x)}{f_1(t,x)} - 1 \Big| \frac{f_1(t,x)m(dx)}{	\int_E f_1(t,y)m(dy)  } 
	\leq \sup_{x\in E} \Big|  \frac{f_0(t,x)}{f_1(t,x)} - 1 \Big| 
	\xrightarrow[t\to t_0]{} 0,
\end{split}\]
	as required.
\end{proof}

\subsection{Regularly variation}
\label{sec: Regularly variation}
	In this subsection, we give some preliminary results on the regularly variation.
	We refer the reader to \cite{BinghamGoldieTeugels1989Regular} as a classical reference for regularly varying functions.
	For $f\in sp\mathscr B_{(0,\infty)}$, we say $f$ is regularly varying at $\infty$ (respt. at $0$) with index $\gamma \in (-\infty,\infty)$ and denote that $f\in \mathcal R^\infty_\gamma$ (respt. $f\in \mathcal R^0_\gamma$) if for any $\lambda \in (0,\infty)$, 
\[
	\lim_{t\to\infty}\frac{f(\lambda t)}{f(t)} 
	= \lambda^\gamma
	\quad (\text{respt. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
	= \lambda^\gamma).
\]
	Further, if $\gamma_0 = 0$, then we say $f$ is slowly varying.
	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, if $L$ is a function which is slowly varying at $\infty$, then it can be written in the form
\[
	L(t) 
	= c(t) e^{\int_{t_0}^t \epsilon(u) \frac{du}{u}},\quad t\geq t_0,
\]
	for some $t_0>0$, where $(c(t))_{t\geq t_0}$ and $(\epsilon(t))_{t\geq t_0}$ are measurable functions with $c(t) \xrightarrow[t\to \infty]{} c \in (0,\infty)$ and $\epsilon(t) \xrightarrow[t\to \infty]{} 0$. 
	In particular, we know that, there is $t_0 > 0$ large enough such that $L$ is locally bounded on $[t_0,\infty)$.

\begin{lem}[{\cite[Proposition 1.5.8. and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
\label{lem: exchange slowly varying function and integration}
	Let $L\in \mathcal R^\infty_0$. 
\begin{itemize}
\item 
	Let $t_0\in (0,\infty)$ be large enough such that $L$ is locally bounded on $[t_0,\infty)$. If $\alpha>0 $, then
\[
	\int_{t_0}^t L(u)du^\alpha 
	\stackrel[t\to \infty]{}{\sim} t^\alpha L(t).
\]  
\item 
	If $\alpha< 0$ then $\int_t^\infty L(u) du^\alpha < \infty$ for $t$ large enough, and
\[
	-\int_t^\infty L(u)du^\alpha 
	\stackrel[t\to \infty]{}{\sim} t^\alpha L(t).
\]
\end{itemize}
\end{lem}

\begin{cro}
\label{cro: power law and ingetration}
	Let $l\in \mathcal R^0_0$. 
\begin{itemize}
\item 
	Let $s_0\in (0,\infty)$ be small enough such that $l$ is locally bounded on $(0,s_0]$. 
	If $\alpha < 0$, then 
	\[
	-\int_s^{s_0} l(u)du^\alpha 
	\stackrel[s\to 0]{}{\sim} s^{\alpha} l(s).
	\]
\item
	If $\alpha > 0$, then $\int_0^s l(u)du^\alpha<\infty$ for $s$ small enough, and
\[
	\int_0^s l(u)du^\alpha 
	\stackrel[s\to 0]{}{\sim} s^{\alpha} l(s).
\]  
\end{itemize}
\end{cro}

\begin{proof}
	Since $l \in \mathcal R^0_0$, we know that, if one define $L(t):=l(t^{-1})$ for each $t\in (0,\infty)$, then $ L \in \mathcal R^\infty_0$.  
	Therefore, there exists $t_0\in (0,\infty)$ such that $L$ is locally bounded on $[t_0,\infty)$.
	Taking $s_0:= t_0^{-1}$, we then immediately know that $l$ is locally bounded on $(0,s_0]$.
	If $\alpha<0 $, then according to Lemma \ref{lem: exchange slowly varying function and integration}, we have
\[
	\int_{t_0}^t L(u)du^{-\alpha} 
	\stackrel[t\to \infty]{}{\sim} t^{-\alpha}  L(t).
\]  
	Replacing $t$ with $s^{-1}$, we have
\[
	-\int_{s}^{s_0} l(u)du^{\alpha} 
	=\int_{s_0^{-1}}^{s^{-1}} L(u)du^{-\alpha}
	\stackrel[s\to 0]{}{\sim}  (s^{-1})^{-\alpha}L(s^{-1})
	=s^\alpha l(s),
\]
	as desired.
	The second assertion can be proved similarly.
\end{proof}

	The following lemma considered the inverse of an invertible regularly varying function. 
	In this paper, if a function $f$ is invertible, we write $f^{(-1)}$ for its inverse; if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.

\begin{lem}
\label{lem: regularly variation and inverse}
	Suppose that $f$ is an invertible map from $(0,\infty)$ to $(0,\infty)$. Then, for each $\alpha > 0$, we have
\[ \label{eq: inverse of a regularly varying function at infinity with alpha > 0}
	f
	\in \mathcal R^\infty_{\alpha}
	\iff f^{(-1)}
	\in \mathcal R^\infty_{1/\alpha},
\] 
	and
\[ \label{eq: inverse of a regularly varying function at 0 with alpha > 0}
	f
	\in \mathcal R^0_{\alpha}
	\iff f^{(-1)}
	\in \mathcal R^0_{1/\alpha};
\] 
	for each $\alpha < 0$, we have
\[ \label{eq: inverse of a regularly varying function with alpha < 0}
	f
	\in \mathcal R^\infty_{\alpha}
	\iff f^{(-1)}
	\in \mathcal R^0_{1/\alpha}.
\] 
	Further, if $f$ is invertible and monotone, then for each $\alpha > 0$ and $c > 0$, we have
\[\label{eq: inverse and power equivalent at infinity with alpha > 0}
	f(t)
	\stackrel[t\to \infty]{}{\sim} c t^\alpha 
	\iff f^{(-1)}(t)
	\stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha},
\]
	and
\[\label{eq: inverse and power equivalent at 0 with alpha > 0}
	f(t)
	\stackrel[t\to 0]{}{\sim} c t^\alpha 
	\iff f^{(-1)}(t)
	\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha};
\]
	for each $\alpha < 0$ and $c > 0$, we have
\[\label{eq: inverse and power equivalent with alpha < 0}
	f(t)
	\stackrel[t\to \infty]{}{\sim} c t^\alpha 
	\iff f^{(-1)}(t)
	\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha}. 
\]
\end{lem}
\begin{proof}
	Let $f$ be invertible.
	If $\alpha>0$, then according to \cite[Theorem 1.5.12.]{BinghamGoldieTeugels1989Regular}, we have \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} is true. 
	To see 	\eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} is true, we write $h(t) : = f(t^{-1})^{-1}$. 
	It's easy to verify that $h$ is also invertible with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1} $. 
	Therefore,
\[ 
	f
	\in \mathcal R^0_{\alpha}
	\iff h 
	\in \mathcal R^\infty_{\alpha}
	\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} }   }{\iff} h^{(-1)} 
	\in \mathcal R^\infty_{1/\alpha}
	\iff f^{(-1)} 
	\in \mathcal R^0_{1/\alpha}.
\]

	If $\alpha < 0$, to see	\eqref{eq: inverse of a regularly varying function with alpha < 0} is true, we write $g(t) : = f(t^{-1})$. 
	It's easy to verify that $g$ is also invertible with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$. 
	Therefore,
\[ 
	f
	\in \mathcal R^\infty_{\alpha}
	\iff g
	\in \mathcal R^0_{-\alpha}
	\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} }   }{\iff} g^{(-1)} 
	\in \mathcal R^0_{-1/\alpha}
	\iff f^{(-1)} 
	\in \mathcal R^0_{1/\alpha}.
\]

	Now, further assume that $f$ is invertible and monotone, and $f(t) \stackrel[t\to \infty]{}{\sim} c t^\alpha$ for some $\alpha > 0$ and $c > 0$, we want to show that $f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}$.
	Note that, since $\alpha >0$, we must have $f$ is non-decreasing.
	From the definition of the asymptotic equivalence, we have, for each $\epsilon> 0$, 
\[
	\big|\frac{f(t)}{c t^\alpha} - 1\big|
	< \epsilon,
	\quad t \text{ large enough.}
\]
	This is equivalent to 
\[
	(1-\epsilon) c t^{\alpha} 
	< f(t) 
	< (1+ \epsilon)c t^{\alpha}, 
	\quad t \text{ large enough,}
\]
	which, by the non-decreasing nature of $f^{(-1)}$, gives that
\[\label{eq: inverse and inequality}
	f^{(-1)}[(1-\epsilon) c t^{\alpha}] \leq t \leq f^{(-1)}[(1+ \epsilon)c t^{\alpha}], \quad t \text{ large enough.}
\]
	If we replace $(1-\epsilon) c t^{\alpha}$ with $y$ on the left side of \eqref{eq: inverse and inequality}, and respectively, replace $(1+\epsilon) c t^{\alpha}$ with $y$ on the right side of \eqref{eq: inverse and inequality}, then we get
\[
	\Big(\frac{y}{c(1-\epsilon)}\Big)^{1/\alpha} 
	\leq f^{(-1)}(y) \leq \Big(\frac{y}{c(1+\epsilon)}\Big)^{1/\alpha}, 
	\quad y \text{ large enough.}
\]
	This, in fact, implies that $ f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}. $ 
	This proved one side of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}. 
	The other side of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}, and \eqref{eq: inverse and power equivalent at 0 with alpha > 0}, as well as \eqref{eq: inverse and power equivalent with alpha < 0}, can be proved similarly.
\end{proof}

\begin{lem}\label{lem:regularly_variation_and_integration}
	Let $E$ be a measurable space with a non-degenerate measure $m \in \mathcal M^1_E$.
	Let $ \gamma \in b\mathscr B_E$ with 
\[
	\gamma_0 
	:= \operatorname*{ess\,inf}_{m(dx)} \gamma(x) 
	:= \sup\{r:m(x:\gamma(x) < r) = 0\}.
\]
	Then $\big(\int_E t^{\gamma(x)} m(dx)\big)_{t\in (0,\infty)} \in \mathcal R^0_{\gamma_0}$.
	Further, if $m\{x:\gamma(x) = \gamma_0\}>0$ then
\[
	\int_E t^{\gamma(x)} m(dx)
	\stackrel[t\to 0]{}{\sim}  m\{x:\gamma(x) = \gamma_0\} t^{\gamma_0}.
\]

\end{lem}

\begin{proof}
	If $\lambda \in (0,1]$, then we have
\[
	\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)} 
	\leq \frac{\int_E \lambda^{\gamma_0} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
	= \lambda^{\gamma_0}, 
	\quad t\in (0,\infty).
\]
	This implies that
\[
	\limsup_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)} 
	\leq \lambda ^{\gamma_0}.
\]
	Also, for any $\epsilon \in (0,\infty)$, we have
\[\begin{split}
	&\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)} 
	\geq \frac{ \int_{ \gamma(x) \leq  \gamma_0 + \epsilon } \lambda^{ \gamma(x) } t^{ \gamma(x)} m(dx) } { \int_E t^{ \gamma(x) } m(dx) }
	\\&\quad \geq \lambda^{ \gamma_0 + \epsilon} \frac{ \int_{ \gamma(x) \leq \gamma_0 + \epsilon } t^{ \gamma(x)} m(dx) } { \int_{ \gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)}m(dx)+ \int_{\gamma(x) > \gamma_0 + \epsilon} t^{\gamma(x)}m(dx)} 
	\\&\quad = \lambda^{\gamma_0 + \epsilon} \frac{1}{1+ \frac{\int_{\gamma(x) > \gamma_0 + \epsilon}t^{\gamma(x) - (\gamma_0 + \epsilon)}m(dx)}{\int_{\gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)- (\gamma_0 + \epsilon)}m(dx)}} 
	\xrightarrow[t\to 0]{} \lambda ^{\gamma_0 + \epsilon},
	\quad \epsilon\in (0, \infty),
\end{split}\]
	where the last convergence is due to monotone convergence theorem.
	Therefore 
\[
	\liminf_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)} 
	\geq \lambda ^{\gamma_0}.
\]
	To sum up we have
\[
	\lim_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)} 
	= \lambda ^{\gamma_0},	
	\quad \lambda \in (0,1].
\]
	If $\lambda \in (1,\infty)$, taking $f(x, t):= t^{\gamma(x)}$, from what we have proved, we also have that
\[
	\lim_{t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)} 
	= \lim_{t\to 0}\frac{\int_E f(x,t)m(dx)}{\int_E f(x, \lambda^{-1} t)m(dx)} 
	= \big((\lambda^{-1})^{\gamma_0} \big)^{-1}
	= \lambda ^{\gamma_0}.
\]
	This proved the first part of the Lemma.

	If further we have $m\{x:\gamma(x) = \gamma_0\}>0$, then by monotone convergence theorem  it is easy to see that
\[
	\frac{\int_E t^{\gamma(x)} m(dx)}{t^{\gamma_0}}
	\xrightarrow[t\to 0]{} m\{x:\gamma(x) = \gamma_0\}\in (0,\infty) .
\]
	The proof is complete.

\end{proof}

\subsection{Superprocesses}
\label{sec: Superprocesses}
	In this subsection, we will recall some known results about the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$. 
\subsubsection{FKPP equations}
	It is known, see \cite[Theorem 2.23]{Li2011Measure-valued} for example, that \eqref{eq:FKPP_in_definition} can be written as
\[\label{eq:mean-fkpp}
	V_t f(x) + \int_0^t P^\beta_{t-r} \psi_0(x,V_r f) dr
	= P^\beta_t f(x),
	\quad f \in bp\mathscr B_E, t \geq 0,x \in E,
\]
	where
\[
	\psi_0(x,z)
	:= \alpha(x) z^2 + \int_{(0,\infty)} (e^{-z y} - 1 + z y) \pi(x,dy),
	\quad x \in E,z \geq 0.
\]
	Suppose that Assumption \ref{asp: 1} and \ref{asp: 2} is true. Integrating with measure $\phi^*dm$, we can derive from \eqref{eq:mean-fkpp} that
	\[\label{eq:langleVtfphiranglem_equation}
	 \langle V_tf,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,V_r f) , \phi^*\rangle_mdr 
	= \langle V_sf,\phi^*\rangle_m,
	\quad s,t\geq 0, f\in bp\mathscr B_E.
	\]

\subsubsection{Non-presistency} 
	Let $\mathbb W$ be the collection of all the $\mathcal M^1_E$-valued cadlag paths on $[0,\infty)$. 
	We refer to $\mathbb W$ the \emph{canonical space of $X$}.
	In fact, $X$ can be viewed as a $\mathbb W$-valued random element. 
	Denoted by $(W_t)_{t\geq 0}$ the \emph{coordinate process of $\mathbb W$}.

	We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$ for all $x\in E$ and $t> 0$.
	Suppose that $X$ is non-persistent, then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ s.t. 
\begin{itemize}
	\item 
	$\mathbb N_x [ \forall t \geq 0, W_t \equiv 0] =0$, $\mathbb N_x[W_0 \not\equiv 0] = 0$;
	\item
	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Possion random measure in some probability space with mean measure $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, 
	then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\tilde X_0 := \mu$ and $\tilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
\end{itemize}
	We refer to $(\mathbb N_x)_{x\in E}$ the \emph{Kuznestov measures} of $X$.
	For the existence and further properties of such measures, we refer our readers to \cite{Li2011Measure-valued}.
	It's worth mention that in the classical literature, the Kuznestov measures are defined in the following space of excursion paths:
	\[\begin{split}
	\mathbb W^{cad}_{0,ex}:=\{ &w: t \mapsto w_t \text{ is a right-continuous path from $(0,\infty)$ to $\mathcal M_E^1$}
		\\&\quad \text {having the null measure as a trap}\}.
	\end{split} \]
	However, since the underlying process $\xi$ is a Hunt process, the Kuznestov measures can actually be carried on the space $\mathbb W$.

	From the Campbell's formula, see  the proof of \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
\[ \label{eq: equation for N measure}
	- \log \mathbf P_\mu [e^{-X_t(f)}] 
	= \mathbb N_\mu[ 1-e^{- W_t(f)}], 
	\quad \mu \in \mathcal M_E^1, t>0, f\in bp\mathscr B_E.
\]
	Taking $\mu = \delta_x$ for some $x\in E$ and $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and then taking $\lambda \to \infty$, we can write
\[ \label{eq: definition of v_t(x)}
	v_t(x)
	:= \lim_{t\to \infty} V_t(\mathbf 1_E)(x)
	= -\log \mathbf P_{\delta_x} [X_t \equiv 0] 
	= \mathbb N_x[X_t\not \equiv 0],
	\quad t\geq 0, x\in E.
\]
	For each $\mu \in \mathcal M_E^1$ and $t > 0$, by \eqref{eq: equation for N measure}, \eqref{eq: definition of v_t(x)} and monotone convergence theorem, we have
\[ \label{eq: equation for mu v-t}\begin{split}
	\mathbb N_\mu[X_t\not \equiv 0]
	&= -\log \mathbf P_{\mu} [X_t \equiv 0] 
	= \lim_{\lambda \to \infty} (- \log \mathbf P_\mu [e^{-\lambda X_t(\mathbf 1_E)}])
	\\&= \lim_{\lambda \to \infty} \langle \mu, V_t(\lambda \mathbf 1_E)\rangle
	= \mu(v_t).
\end{split}\]

\subsection{Spine decompositions}
\label{sec: Spine decompositions}
	Let $(\Omega, \mathscr F)$ be a measurable space with $\sigma$-finite measure $\mu$, which is not necessarily a probability measure or a finite measure.
	For any $F\in r\mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and $\mu [f] \in (0,\infty)$. 
	And if this happens, define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ s.t. $d\mu^F= \frac{F}{\mu[F]}d \mu$.

	Let $\{X;\mathbf P\}$ be a non-persistent superprocess.
	Let $\mu \in \mathcal M^1_E$ and $T>0$. 
	Suppose that $g\in p\mathscr B_E$ satisfies that $\mu(P^\beta_Tg) \in (0,\infty)$.
	Denote by $\mathbb N^{W_T(g)}_\mu$ and $\mathbf P_\mu^{X_T(g)}$, the $W_T(g)$-transform of $\mathbb N_\mu$ and the $X_T(g)$-transform of $\mathbf P_\mu$, respectively.
	The so-called spine decomposition theorem characterize the law of $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ in two steps.
	The first step of the theorem says that $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the summation of two independent measure valued processes:

\begin{thm}[Size-biased decomposition, \cite{RenSongSun2017Spine}]\label{thm: size-biased decomposition}
\[
	\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}
	\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{W_T(g)}_\mu\}.
\]
\end{thm}
	The second step of the theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has the so-called spine representation:
	We say $\{(Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is \emph{the spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
\begin{itemize}
\item
	\emph{The spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) e^{-\int_0^T \beta(\xi_s)ds}$-transform of measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
\item
	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with \emph{its conditioned mean measure} defined by
\[
	\mathbf m^\xi_T(ds,dw)
	:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
\]
\item
	$\{(Y_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is an $\mathcal M^1_E$-valued process defined by
\[
	Y_t
	:= \int_{(0,t] \times \mathbb W} w_{t-s} \mathbf n_T(ds,dw),
	\quad 0 \leq t\leq T.
\]
\end{itemize}

\begin{thm}[Spine representation,\cite{RenSongSun2017Spine}]\label{thm: spine representation}
	Let $\{(Y_t)_{0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ be the spine representation of $\mathbb N^{W_T(g)}_\mu$ defined above.
	Then we have
\[
	\{(Y_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}
	\overset{f.d.d.}{=} \{(W_t)_{0\leq t\leq T}; \mathbb N_\mu^{W_T(g)}\}.
\]
\end{thm}

	Note that if we have an a.s. event $\{B;P\}$, i.e. $P(B) = 1$, then under any possible size-biased transform of probability $P$, $B$ is still an a.s. event. 
	From this, we have that $\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
	Note that $\mathbb N_\mu$ is not typically a probability measure. 
	But after the transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
	Since $\mathbb N_x(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.

\begin{rem}
\label{rem: initial configuration of transformed process}
	Note that $\Pi_{\mu}$ is not typically a probability measure. 
	But after the transformation, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
	We can verify that 
\[
	\Pi_{\mu}^{(T,g)} (\xi_0 \in dx) 
	= \mu(P^\beta_T g)^{-1} S_T g(x)\mu(dx),
	\quad x\in E.
\] 
	In fact, 
\[
	\Pi_{\mu}^{(T,g)} [ f(\xi_0) ] 
	= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } f(\xi_0) ] 
	= \mu(S_T g)^{-1} \int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx).
\]
\end{rem}

	Now, suppose that $\{\xi; \Pi\}$ satisfies the Assumption \ref{asp: 1}.
	Denote by $\phi$ the principal eigenfunction of the mean semigroup of $X$.
	The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, considered the case when $g = \phi$ only.
	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov extension theorem.
	In another word, process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$, on the finite interval $[0,T]$.
	In fact, one can also verify that this consistence property is satisfied by all those families of probabilities: $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)$.
	Therefore, the actual statement of the classical spine decomposition theorem is a little different from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}, and doesn't restrict the corresponding processes on the finite interval $[0,T]$.
	Because of its theoretical importance, we state the classical spine decomposition theorem explicitly:

\begin{cro}
	For each $\mu \in \mathcal M_E^\phi \cap \mathcal M_E^1$, we have
\[
	\{(X_t)_{t\geq 0}; \mathbf P_\mu^{(\phi)}\}
	\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{(\phi)}_\mu\}.
\]
	Here, probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of process $(X_t)_{t\geq 0}$ is defined by
\[
	d ( \mathbf P_\mu^{(\phi)}|_{\mathscr F_t^X}) = \frac{X_t(\phi)}{ \mu(\phi)} d(\mathbf P_\mu|_{\mathscr F_t^X}),
	\quad t\geq 0;
\]
	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of process $(W_t)_{t\geq 0}$ is defined by
\[
	d(\mathbb N_\mu^{(\phi)} |_{\mathscr F^W_t}  )
	= \frac{W_t(\phi)}{\mu(\phi)} d(\mathbb N_\mu |_{\mathscr F^W_t}  ),
	\quad t\geq 0.
\] 
\end{cro}

	Let $\mu \in \mathcal M^{(\phi)}_\mu$, we say $\{(Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$ is \emph{the spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
\begin{itemize}
\item
	\emph{The spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of process $(\xi_t)_{t\geq 0}$ is defined by
\[
	d(\Pi_{\mu}^{(\phi)} |_{\mathscr F_t^\xi}) 
	= \frac{\phi(\xi_t)e^{-\int_0^t \beta(\xi_s)ds}}{\mu(\phi)} d(\Pi_{\mu} |_{\mathscr F_t^\xi}),
	\quad t\geq 0;
\]
\item
	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with \emph{its conditioned mean measure} defined by
\[\label{eq:meanMeasImmigr}
	\mathbf m^\xi(ds,dw)
	:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
\]
\item
	$\{(Y_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is an $\mathcal M^1_E$-valued process defined by
\[\label{eq:defSpinImmigr}
	Y_t
	:= \int_{(0,t] \times \mathbb W} w_{t-s} \mathbf n(ds,dw),
	\quad t\geq 0.
\]
\end{itemize}

\begin{cro}
	Let $\{(Y_t)_{t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$ be the spine representation of $\mathbb N^{(\phi)}_\mu$ defined above.
	Then we have
\[
	\{(Y_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}
	\overset{f.d.d.}{=} \{(W_t)_{t\geq 0}; \mathbb N_\mu^{(\phi)}\}.
\]
\end{cro}

	For the sake of generality, the spine decomposition theorems above are all stated with respect to a general initial configuration $\mu$.
	If $\mu = \delta_x$ for some $x\in E$, then from Remark \ref{rem: initial configuration of transformed process}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$. 
	Similarly, we write $\Pi_x^{(\phi)}$ for $\Pi_{\delta_x}^{(\phi)}$.

\subsection{Ergodicity of the spine process $\{\xi; \Pi^{(\phi)}_x\}$}
\label{sec: Ergodicity}
	In this subsection, we discuss the ergodicity property of the spine processes $\{\xi; \Pi^{(\phi)}_x\}$ under Assumptions \ref{asp: 1}, \ref{asp: 2} and \ref{asp: 3}.
	One can verify that $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
\[
	q_t(x,y) := \frac{\phi(y)}{\phi(x)} p^\beta_t(x,y),
	\quad x,y\in E, t>0.
\]
	If we take constants $c_0>0$ and $c_1>0$ as in \eqref{eq:q(t,x,y)}, then we have
\[\label{eq: asymptotic for q_t(x,y)}
	\sup_{x\in E} \Big| \frac{q_t(x,y)}{\phi(y)\phi^*(y)} - 1\Big| 
	\leq c_0 e^{-c_1 t},
	\quad t > 1.
\]
	This characterize the ergodicity of process $\{\xi; \Pi^{(\phi)}_x\}$.
	One can easily verify from \eqref{eq: asymptotic for q_t(x,y)} that $(\phi\phi^*)(x)m(dx)$ is the unique invariant probability measure of $\{\xi; \Pi^{(\phi)}_x\}$.
	The following two lemmas are also simple consequences of \eqref{eq: asymptotic for q_t(x,y)}. 
	They will be needed in the proof of  Theorem \ref{thm: main theorem}(3).
\begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
	If $F$ is bounded and Borel measurable on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$. 
	Then we have
\[
	\int_0^1 F(\xi_{(1-u)t},u,t) du 
	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)} ; L^2} \int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle_m du,
	\quad x\in E.
\]
\end{lem}
\begin{lem}\label{lem: Fatou-ergodic lemma for the uderlying process}
	Let $F$ be a non-negative bounded Borel measurable on $E\times [0,1]\times [0,\infty)$. 
	Define $F(y,u):= \limsup_{t\to \infty} F(y,u,t)$ for each $y\in E$ and $u \in [0,1]$. 
	Then, for each $x\in E$ and $p \geq 1$, we have
\[
	\limsup_{ t \to \infty}  \Big\| \int_0^1 F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
	\leq \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle du, 
	\quad x\in E.
\]
\end{lem}

\begin{proof}
	For each $(y,u,t)\in E\times [0,1]\times [0,\infty)$, define $\bar F(y,u,t) := \sup_{s:s\geq t} F(y,u,s)$.
	Then $\bar F$ is a bounded Borel measurable function on $E\times [0,1]\times [0,\infty)$ with 
\[
	F(x,u)
	= \lim_{t\to \infty} \bar F(x,u,t),
	\quad x\in E, u\in [0,1].
\]
	Therefore, according to Lemma \ref{lem: ergodicity of the underlying process}, we have that
\[
	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du 
	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2} \int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
	\quad x\in E.
\]
	The bounded convergence theorem then gives that, for each $p \geq 1$, 
\[
	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du 
	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^p} \int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
	\quad x\in E.
\]
	Finally, note that that $0\leq F \leq \bar F$, we have
\[\begin{split}
	& \limsup_{ t \to \infty}  \Big\| \int_0^1 F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
	\leq 	\limsup_{ t \to \infty}  \Big\| \int_0^1 \bar F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
	\\& \quad = \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle du, 
	\quad x\in E,
\end{split}\]
	as desired.
\end{proof}

\section{Proofs}
\subsection{Proof of Theorem \ref{thm: main theorem}(1)}
\label{sec: proof of result 1}
	Let $\{X; \mathbf P\}$ be a superprocess satisfies Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
	In this section, we will proof the following stronger result:

\begin{prop}
\label{prop: non-presistent}
	For each $t > 0$, $\inf_{x\in E} \mathbf P_{\delta_x}(X_t \equiv 0) > 0$.
\end{prop}

\begin{proof}
	For each $x\in E$, let $\tilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\tilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$. 
	Then, we know that $\tilde \kappa = \kappa$ and $\tilde \gamma = \gamma$ almost everywhere with respect to measure $m$.
	Define $\tilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\tilde \psi(\cdot, z) = \psi(\cdot , z) $ almost everywhere with respect to measure $m$.
	Therefore, if we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
\[
	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \tilde \psi (\xi_s,V_{t-s} f) ds \Big]
	=\Pi_x \big[ f(\xi_t)\mathbf 1_{t<\zeta} \big].
\] 
	So, we can view $\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
	Define another branching mechanism for a continuous state branching process:
\[
	\hat\psi(z) 
	:= - (\|\beta\|_\infty +\kappa_0 )z + \kappa_0 z^{\gamma_0}, 
	\quad z\geq 0.
\]
	Using the fact that $\gamma_0 > 1$ and $\kappa_0 > 0$, it is easy to verify that 
\[
	\inf_{x\in E}\tilde \psi(x,z) 
	\geq \hat\psi(z),
	\quad z\geq 0; 
	\quad \int_1^\infty \frac{1}{\hat\psi(z)} dz 
	< \infty;
	\quad \hat \psi(+\infty) = +\infty.
\]
	Therefore $\tilde \psi$ satisfies the condition of \cite[Lemma 2.3]{RenSongZhang2015Limit}.
	As a consequence, by \cite[Lemma 2.3]{RenSongZhang2015Limit}, we have the desired result.
\end{proof}

\subsection{Proof of Theorem \ref{thm: main theorem}(2)}
\label{sec: proof of result 2}
	Let $\{X; \mathbf P\}$ be a superprocess satisfies Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent.
	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have $\mathbf P_{\delta_x}(X_t \equiv 0)<1$, for each $x\in E$ and $t>0$.
	Therefore, from \eqref{eq: definition of v_t(x)}, we have that $v_t \in spb\mathscr B_E$. 
	According to \eqref{eq:mean-fkpp}, by monotonicity, we see that $(v_t)$ satisfies the equation
\[
	v_{s+t}(x) + \int_0^t P^\beta_{t-r} \psi_0(x,v_{s+r}) dr
	= P^\beta_t v_s(x)
	\in [0,\infty),
	\quad s>0, t \geq 0,x \in E.
\]

	Note that, under the Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
	Therefore, we have $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
	Then, according to \eqref{eq:langleVtfphiranglem_equation}, by monotonicity, we have another equation
\[ \label{eq: equation of <vt,phi>}
	 \langle v_t,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,v_t) , \phi^*\rangle_m dr 
	= \langle v_s,\phi^*\rangle_m
	\in [0,\infty),
	\quad s, t > 0.
\]
	One of the consequence of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example, $\phi^{-1}v_t$ converges to $0$ uniformly when $t\to\infty$.
	Therefore, it is natural to ask the speed of this convergence. 
	This is answered in two steps, the first step says that $(\phi^{-1}v_t)(x)$ will convergence to $0$ in a same speed of $\langle v_t,\phi^*\rangle_m $, uniformly in $x\in E$:

\begin{prop}
\label{prop: convergence in a same speed}
	$(\phi^{-1}v_t)(x) \stackrel[t\to\infty]{x\in E}{\sim} \langle v_t,\phi^*\rangle_m$. 
\end{prop}
\label{prop: asymptotic equivalence of vtphi}
	The second step characterize this speed:
\begin{prop}
\label{prop: regularly varying of vt-phi-star}
	$\langle v_t,\phi^*\rangle_m $ is regularly varying with index $-\frac{1}{\gamma_0-1}$ while $t\to \infty$. 
	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then 
\[
	\langle v_t,\phi^*\rangle_m
	\stackrel[t\to \infty]{}{\sim} \big(C_X(\gamma_0-1) t \big)^{-\frac{1}{\gamma_0 - 1}},
\]
	where $C_X:= \langle \mathbf 1_{\gamma= \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m $.
\end{prop}

	Note that Theorem \ref{thm: main theorem}(2) is simply a corollary of Proposition \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.

\begin{proof}[Proof of Proposition \ref{prop: convergence in a same speed}]
	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2rd moment.
	For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t)_{t\geq 0}, (\xi_t)_{t\geq 0},\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$.
	According to \eqref{eq: definition of v_t(x)} and Theorem \ref{thm: size-biased decomposition}, we have that for each $t>0$,
\[\begin{split}\label{eq:vt-and-Y}
	&\langle \mu,\phi \rangle \dot {\mathbf P}^{(\phi)}_\mu [Y_t(\phi)^{-1}]
	= \mathbb N_\mu[W_t(\phi)] \mathbb N^{W_t(\phi)}_\mu [W_t(\phi)^{-1}]
	= \mathbb N_\mu[W_t(\phi) > 0]
	= \langle \mu,v_t \rangle.
\end{split}\]
	Taking $\mu = \delta_x$ in \eqref{eq:vt-and-Y}, we get $(\phi^{-1}v_t)(x) =\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]$.
	Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
	Therefore, to complete the proof, we only have to show that
\[
	\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
	\stackrel[t\to \infty]{x\in E}{\sim}  \dot {\mathbf P}_\nu^{(\phi)} [Y_t(\phi)^{-1}].
\]

	For any $t>0$ and any $G\in \mathscr B_{(0,t]}$, define
$
	Y^G_t
	:= \int_{G\times \mathbb W} w_{t-s} \mathbf n(ds,dw).
$
	Then for any $0 < t_0 < t$, we can decompose $Y_t$ by
$
	Y_t
	= Y^{(0,t_0]}_t + Y^{(t_0,t]}_t.
$
	Using this decomposition, for each $0<t_0<t<\infty$ and $x\in E$, we can write
\[\label{eq: starting point of phi-1v_t(x)}
	 \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
	= \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] + \epsilon_x^1(t_0,t) +\epsilon_x^2(t_0,t)
\]
	where 
\[\begin{split}
	\epsilon_x^1(t_0,t) 
	&:= \dot {\mathbf P}_{\delta_x}^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] - \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}];
	\\\epsilon_x^2(t_0,t)
	&:= \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1} - Y^{(t_0,t]}_t(\phi)^{-1}].
\end{split}\]

	From the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, the following identity can be verified:
\[\label{eq: some equations for PY-1}\begin{split}
	\dot{\mathbf P}^{(\phi)} [Y_t^{(t_0,t]}(\phi)^{-1}|\mathscr F^\xi_{t_0}]
	&= \dot{\mathbf P}_{\delta_{\xi_{t_0}}}^{(\phi)}  [Y_{t-t_0}(\phi)^{-1}]
	= (\phi^{-1}v_{t-t_0})(\xi_{t_0});
	\\ \dot{\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]
	&= \Pi_{\nu}^{(\phi)}[(\phi^{-1}v_{t-t_0})(\xi_{t_0}) ]
	= \langle v_{t-t_0},\phi^* \rangle_m;
	\\ \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]
	&= \Pi_x^{(\phi)}[(\phi^{-1}v_{t-t_0})(\xi_{t_0}) ]
	=  \int_E  q_{t_0}(x,y)(\phi^{-1}v_{t-t_0})(y) m(dy).
\end{split}\]

	Taking constants $c_0, c_1>0$ as in \eqref{eq:q(t,x,y)}, if $t_0 > 1$, then it has been argued in the proof of
	\cite[Lemma 5.3]{RenSongSun2017Spine} that
$
	|\epsilon_x^1(t_0,t)|
	\leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m .
$
	In fact, 
\[\label{eq:epsilon-1}\begin{split}
	|\epsilon_x^1(t_0,t)|
	& = \big| \dot {\mathbf P}_{\delta_x}^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] - \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] \big| \\
	& = \big|  \int_E  q_{t_0}(x,y)(\phi^{-1}v_{t-t_0})(y) m(dy) - \langle v_{t-t_0},\phi^* \rangle_m \big|\\
	& \leq \int_{y\in E} \big| q_{t_0}(x,y) - (\phi\phi^*)(y) \big| (\phi^{-1}v_{t-t_0})(y) m(dy)\\
	& \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m .
\end{split}\]

	We now claim that, if $t_0 > 1$ and $t-t_0$ is large enough, then
\[\label{eq:upperbound_of_epsilon-2}
	|\epsilon_x^2(t_0,t)|
	\leq t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
\]

	In fact, we have
\[\label{eq:epsilon-2}\begin{split}
	|\epsilon_x^2(t_0,t)|
	&= \big| \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1} - Y^{(t_0,t]}_t(\phi)^{-1}] \big| 
	= \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t^{(0,t_0]}(\phi)\cdot Y_t(\phi)^{-1}\cdot Y^{(t_0,t]}_t(\phi)^{-1}]
	\\&\leq \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}(\phi)\neq 0}\cdot Y^{(t_0,t]}_t(\phi)^{-1}]
	\\&= \dot{\mathbf P}_{\delta_x}^{(\phi)} \big[\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}(\phi)\neq 0}|\mathscr F^\xi_{t_0}] \cdot \dot{\mathbf P}_{\delta_x}^{(\phi)} [ Y^{(t_0,t]}_t(\phi)^{-1}|\mathscr F^\xi_{t_0}] \big].
\end{split}\]
	On one hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1}, we know that
\[\label{eq:epsilon-2-final}\begin{split}
	\dot{\mathbf P}_{\delta_x}^{(\phi)}[ Y^{(t_0,t]}_t(\phi)^{-1}]
	\leq (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
\end{split}\]
	On the other hand, since $\phi^{-1}v_s$ convergence to $0$ uniformly while $s\to \infty$, we can chose an $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
	Then, if $t-s > t-t_0 \geq s_0$, note that $v_t$ is non-increasing in $t$, we have
\[\begin{split}
	\kappa(x)\gamma(x) v_{t-s}(x)^{\gamma(x)-1}
	\leq \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1} v_{t-s}\|^{\gamma_0-1}_\infty
	\leq \|\kappa\gamma\phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
\end{split}\]
	Therefore, by Campbell's formula, while $t-t_0 \geq s_0$,
\[\label{eq:firstpart-of-Y}\begin{split}
	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]
	\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]\big)
	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
	= -\log \lim_{\lambda \to \infty}e^{- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ]}
	\\&\quad = \mathbf m^\xi [\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0}]
	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{X_{t-s} \not\equiv 0}]\pi(\xi_s,dy)
	\\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
	= \int_0^{t_0} \big( \kappa \gamma (v_{t-s})^{\gamma - 1} \big) (\xi_s)ds
	\\&\quad \leq  t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
\end{split}\]
	Then \eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-final} and \eqref{eq:firstpart-of-Y} implies \eqref{eq:upperbound_of_epsilon-2}.

	Now, for each $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)} and \eqref{eq: some equations for PY-1}, we have
\[\label{vts-inequality}\begin{split}
	&\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0},\phi^* \rangle_m}-1 \Big|
	\leq \frac{|\epsilon_x^1(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m} + \frac{|\epsilon_x^2(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m}\\
	&\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-s}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
\end{split}\]
	Since $\phi^{-1}v_s$ convergence to $0$ uniformly while $s\to \infty$, there exists a map $t\mapsto t_0(t)$ such that,
\[
	t_0(t)
	\xrightarrow[t\to\infty]{} \infty;
	\quad t_0(t)\| \phi^{-1}v_{t-t_0(t)}\|^{\gamma_0 - 1}_\infty
	\xrightarrow[t\to\infty]{} 0.
\]
	Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
\[\label{eq:k1}
	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
	\xrightarrow[t\to\infty]{} 0.
\]
	Now notice that
\[\label{eq:k2}\begin{split}
	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
	&\leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle} - 1 \Big| \phi \phi^*(x) m(dx)\\
	&\leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
	\xrightarrow[t\to\infty]{} 0.
\end{split}\]
	Finally, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we have
\[
	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
	\xrightarrow[t\to\infty]{} 0,
\]
	as desired.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop: regularly varying of vt-phi-star}]

	From \eqref{eq: equation of <vt,phi>} we know that $\langle v_t,\phi^* \rangle_m$ is continuous and strictly decreasing in $t \in (0,\infty)$. 
	Since $X$ is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$, $\mathbf P_\mu (X_t \not \equiv 0) \xrightarrow[t\to 0]{} 1$. 
	Taking $\mu = \nu$, according to \eqref{eq: equation for mu v-t}, we have that $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to 0]{} +\infty$.
	On the other hand, since $\phi^{-1}v_t$ converges to $0$ uniformly in $E$, we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
	Therefore, mapping $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$ which we denote by $R : (0,\infty) \to (0,\infty)$.

	Now, if we denote by
\[
	\epsilon_{t}(x) 
	: = \frac{v_t(x)}{\langle v_t, \phi^*\rangle \phi(x)} - 1,
	\quad t>0, x\in E.
\]
	Then, we have
\[
	v_t(x) 
	= \big(1+ \epsilon_{R(\langle v_t,\phi^* \rangle)}(x) \big )\langle v_t,\phi^* \rangle \phi(x),
	\quad t>0, x\in E.
\]
	Further, by Proposition \ref{prop: convergence in a same speed} and $R(u)\xrightarrow[u\to 0]{} \infty$, we have
$
	\sup_{x\in E}|\epsilon_{R(u)}(x)| 
	\xrightarrow[u\to 0]{} 0.
$

	Now, by \eqref{eq: equation of <vt,phi>}, we have
\[
	\frac{d \langle v_r, \phi^* \rangle_m}{dr} 
	= - \langle \psi_0(\cdot ,v_r) ,\phi^*\rangle_m 
	> 0
\]
	almost everywhere for $r\in (0,\infty)$ with respect to Lebesgue measure. 
	Therefore, we have
\[\begin{split}
	s-t
	& = \int_t^s dr
	= \int_s^t \langle \psi_0(\cdot ,v_r), \phi^*\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
	\\&= \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle \phi \big), \phi^* \big\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
	\\&= \int_{\langle v_s,\phi^*\rangle}^{\langle v_t, \phi^* \rangle} \big\langle \psi_0 \big( \cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du.
\end{split}\] 
	While $t\to 0$, we have that
\[
	s 
	= \int_{\langle v_s,\phi^*\rangle}^\infty \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du,
	\quad s\in (0,\infty).
\]
	This implies that
\[
	R(r)
	= \int_r^\infty \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)}(x) ) u \phi \big), \phi^* \big\rangle_m^{-1} du, 
	\quad r\in (0,\infty).
\]

	We are interested in the regularly varying property of $R(r)$ while $r\to 0$. 
	This can be down by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ while $u \to 0$.
	In fact, since $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$ and $\gamma(\cdot)$ is bounded, we have $\big(1+ \epsilon_{R(u)}(x)\big)^{\gamma(x)}\stackrel[u\to 0]{x\in E}{\sim} 1$. 
	Therefore, from Lemma \ref{lem: asymptotic equivalent of integration}, we have that
\[\label{eq: }\begin{split}
	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
	= \big\langle \kappa (x)\big( 1 + \epsilon_{R(u)}(x)\big )^{\gamma(x)} u^{\gamma(x)} \phi(x)^{\gamma(x)} , \phi^*(x) \big\rangle_{m(dx)}
	\\ &\quad \stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_{m(dx)}.
\end{split}\]
	According to Lemma \ref{lem:regularly_variation_and_integration}, this implies that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$. 
	According to Corollary \ref{cro: power law and ingetration}, this implies that $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
	Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and \eqref{eq: inverse of a regularly varying function with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.

	Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration}, we know that 
\[\begin{split}
	&\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
	\stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_m.
	\\ & \stackrel[u\to 0]{}{\sim}  \langle \mathbf 1_{\gamma(x)= \gamma_0}, \kappa (x)\phi(x)^{\gamma_0} \phi^*(x) \rangle_m u^{\gamma_0}
	=: C_X u^{\gamma_0}.
\end{split}\]
	Therefore, we can write $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ convergence to constant $C_X^{-1}$ while $u \to 0$.
	Now according to Corollary \ref{cro: power law and ingetration} we have that
\[\begin{split}
	R(r)
	&= \int_r^\infty \big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
	= \int_r^\infty u^{-\gamma_0} l(u) du 
	\\&= -\frac{1}{\gamma_0-1}\int_r^\infty l(u) du^{-(\gamma_0 - 1)} 
	\\&\stackrel[r\to 0]{}{\sim} C_X^{-1} (\gamma_0-1)^{-1} r^{-(\gamma_0 - 1)}.
\end{split}\]
	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from \eqref{eq: inverse and power equivalent with alpha < 0}, we have
\[
	\langle v_r,\phi^*\rangle_m
	\stackrel[r\to \infty]{}{\sim} \big(C_X (\gamma_0-1) r \big)^{-\frac{1}{\gamma_0 - 1}}.
\]
\end{proof}

\subsection{Characterizing the conditional distribution}
\label{sec: conditional distribution}
	Let $\{X; \mathbf P\}$ be a superprocess satisfies Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
	Suppose that $m(x: \gamma(x) = \gamma_0)>0$. 
	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | X_t \not \equiv 0\big)\big\}$ convergence weakly to a non-degenerate distribution for a large class of testing function $f$ and initial configuration $\mu$.
	Our guess of $(\eta_t)$ is 
\[
	\eta_t
	:= (C_X(\gamma_0 - 1) t)^{-\frac{1}{\gamma_0 - 1}},
	\quad t\geq 0,
\] 
	because in this case $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ have the mean convergence:
 \[
 	\mathbf P_{\delta_x}[\eta_t X_t(f)|X_t \not \equiv 0]
	= \frac{\mathbf P_{\delta_x}[\eta_t X_t(f) \mathbf 1_{X_t \not \equiv 0}]} {\mathbf P_{\delta_x}(X_t \not \equiv 0) }
	= \frac{\eta_t}{\mathbf P_{\delta_x}(X_t \not \equiv 0)} P^\beta_t f(x)
	\stackrel[t\to \infty]{}{\sim}  \langle f,\phi^* \rangle_m.
 \]
 	Here we have used Theorem \ref{thm: main theorem}(2) and the fact that (see \eqref{eq:q(t,x,y)})
 \[
 	P^\beta_t f(x)
 	= \int_E p_t^\beta(x,y)f(y)dy 
 	\xrightarrow[t\to \infty]{}  \phi(x) \langle f,\phi^*\rangle_m.
 \]

 	From the Laplace transform point of view, the desired result that $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ weakly convergence to some probability distribution $F_{f,x}$, is equivalent to the following convergence:
\[\begin{split}
 	&\frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\eta_t} 
	= \frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\mathbf P_{\delta_x}(X_t \not \equiv 0)} \frac{ \mathbf P_{\delta_x}(X_t \not \equiv 0) } { \eta_t }
	= \mathbf P_{\delta_x}[1-e^{-\theta \eta_t X_t(f)}| X_t \not \equiv 0]  \frac{ \mathbf P_{\delta_x}(X_t \not \equiv 0) } { \eta_t }
	\\&\quad \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
\end{split}\] 
	Further, note that $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
\[\label{eq: equivalent result}
	\frac{V_t(\theta \eta_t f)(x)}{\eta_t}  
	\quad \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
\]
	Therefore, to actually establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$, one only have to verify \eqref{eq: equivalent result}.

	In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, we need to characterizes the dynamic of $V_t(\theta f)$ while $\theta$ is varying. 
	(Note that \eqref{eq:mean-fkpp} only characterize the dynamic of $V_t(\theta f)$ while $t$ is varying.)
	This is done by the following proposition:

\begin{prop}
	For any $f\in pb\mathscr B_E,\theta \geq 0,x\in E$ and $T>0$, we have
\[\label{eq: equation for Vt(theta f) for theta}
	V_T ( \theta f) ( x)
	= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr.
\]
\end{prop}

\begin{proof}
	It follows by Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
\[
	\frac{ \mathbf P_{\delta_x}[X_T(f)e^{-\theta X_T(f)}] } {  \mathbf P_{\delta_x} [X_T(f)] }
	= \mathbf P_{\delta_x}^{X_T(f)} [e^{-\theta X_T(f)}] 
	= \mathbf P_{\delta_x} [e^{-\theta X_T(f)}] \dot {\mathbf P}_x^{(T,f)}[e^{-\theta Y_T(f)}],
\]
	where $\{Y; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with spine process $\xi$, immigrate measure $\mathbf n_T$ and its conditioned mean measure $\mathbf m^\xi_T$.
	From this, we have
\[ \label{eq: dynamic of theta on v_t theta reason 1}
	\partial_\theta (-\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}])
	= \frac{\mathbf P_{\delta_x}[X_T(f)e^{-\theta X_T(f)}]}{\mathbf P_{\delta_x}[e^{-\theta X_T(f)}]}
	= P^\beta_T f(x) \dot {\mathbf P}_x^{(T,f)}[e^{-\theta Y_T(f)}].
\]
	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Campbell's formula and \eqref{eq: definition of Gamma function}, we have
\[\label{eq: dynamic of theta on v_t theta reason 2}\begin{split}
	&-\log \dot {\mathbf P}^{(T,f)}_{x}[e^{-\theta \mathbf n_T(F)}|\mathbf m_T^\xi] 
	= \mathbf m_T^\xi(1-e^{-\theta F})
	\\&\quad = \int_0^T ds \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}[1- e^{-\theta X_{T-s}(f)}] \pi(\xi_s,y)
	\\&\quad = \int_0^T ds \cdot \kappa(\xi_s) \int_{(0,\infty)} \mathbf (1- e^{- y V_{T-s}(\theta f)(\xi_s)}) \frac{dy}{\Gamma(-\gamma(\xi_s)) y^{\gamma(\xi_s)}}
	\\&\quad = \int_0^T \big(\kappa\gamma V_{T-s}(\theta f)^{\gamma-1}\big)(\xi_s) ds.
\end{split}\]
	Note that, since $\mathbf n_T(F)= Y_T(f)$, we can derive from \eqref{eq: dynamic of theta on v_t theta reason 1} and \eqref{eq: dynamic of theta on v_t theta reason 2} that
\[\begin{split}
	V_T(\theta f)(x)
	&= -\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}]
	= \int_0^\theta S_Tf(x) \dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
	\\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \big[e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds}\big] dr
	\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr,
\end{split}\]
as required.
\end{proof}

	Replacing $\theta$ with $\theta \eta_T$ in \eqref{eq: equation for Vt(theta f) for theta}, we have

\[\label{eq: equation for normalized V_T}\begin{split}
	&\frac{V_T(\theta \eta_T f)(x)}{\eta_T}
	= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
	\\&\quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
	\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} e^{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du}\Big] dr.
\end{split}\]

\subsection{Characterizing the Zolotarev's distribution}
\label{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}

	Recall that a non negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have the Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
\[
	E[1-e^{-\theta\mathbf z^{(\gamma_0 - 1)}}] 
	=\Big( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} \Big)^{\frac{1}{\gamma_0 - 1}}.
\]
	It turns out that we can characterize this distribution by the following Lemma:

\begin{lem}
\label{lem: characterize the general Mittag-Leffler distribution}
	The non-linear delay equation
\[\label{eq: equation for the distribution}
	G( \theta) 
	= \int_0^\theta e^{ - \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1} })^{\gamma_0 - 1}\frac{du}{u} } dr,
	\quad \theta \geq 0,
\]
	has a unique solution:
\[\label{eq: solution for the equation}
	G(\theta) 
	= \big(\frac{1}{1+\theta^{-(\gamma_0 - 1)}}\big)^{\frac{1}{\gamma_0 - 1}}, 
	\quad \theta \geq 0.
\]
\end{lem}

	We first give a convention of notation:
	If $f$ is a measurable function which is $L^p$ integrable on a measurable space $(S,\mathscr S,\mu)$ with $p > 0$, then we write 
\[
	\|f\|_{\mu;p} := \Big(\int_{S} |f|^p d\mu \Big)^{\frac{1}{p}}.
\]
	Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to measure $\mu$.	
	In order to proof the above Lemma, we will need the following Lemma:

\begin{lem}\label{lem: F is zero}
	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying that there exists a constant $C>0$ s.t. for all $\theta \geq 0$ we have $F(\theta) \leq C\theta$ and 
\[
	F(\theta)
	\leq C \int_0^\theta \|  F(ru^{ \frac{1}{\gamma_0- 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0.
\]
	Then, $F \equiv 0$.
\end{lem}

\begin{proof}
	We proof this Lemma by a contradiction.
	Assume that $\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty$. 
	Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
	We first claim that
\[
	F_\alpha (\theta) 
	\leq C(\rho C + 1) \theta, 
	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
\]
	In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
\[\begin{split}
	F_\alpha (\theta) 
	&\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; (\gamma_0 - 1)} dr
	\leq C\int_\alpha^{\alpha + \theta} \|Cru^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
	\\&\leq C^2 (\alpha + \theta) \theta \|u^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
	\leq C(\rho C + 1) \theta.
\end{split}\]
	We then claim that, if 
\[\label{eq: FATLC}
	F_\alpha (\theta) 
	\leq C^k(\rho C + 1) \theta^k, 
	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
\]
	for some $k \in \mathbb N$, then
\[
	F_\alpha (\theta) 
	\leq C^{k+1}(\rho C + 1) \theta^{k+1}, 
	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
	\]
	In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
\[\begin{split}
	F_\alpha (\theta) 
	&\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
	=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) \big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
	\\& =  C\int_0^\theta \|F_{\alpha u^{\frac{1}{\gamma_0 - 1}}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
	\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
	\\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
	\leq C^{k+1} (\rho C+1) \theta^{k+1} .
\end{split}\]
	Therefore, by induction, we have
\[
	F_\alpha (\theta) 
	\leq C^k(\rho C + 1) \theta^k, 
	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
\]
	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
	This, however, is a contradiction to the definition of $\rho$. 
	The proof is complete.
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem: characterize the general Mittag-Leffler distribution}]

	We first verify that \eqref{eq: solution for the equation}  is a solution of \eqref{eq: equation for the distribution}.
	In fact, if $G(\theta) = (\frac{1}{1+ \theta^{-(\gamma_0 - 1)}})^{\frac{1}{\gamma_0 - 1}}$, then
\[\begin{split}
	& \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}} dr
	\\&\quad = \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 \frac{du}{u+r^{-(\gamma_0 - 1)}} } dr
	= \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \log\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} } } dr
	\\&\quad = \int_0^\theta \big(\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} }\big)^{- \frac{\gamma_0} {\gamma_0 - 1}} dr
	= \int_0^\theta \big( 1 + r^{ - ( \gamma_0 - 1 ) } \big)^{- \frac{\gamma_0} {\gamma_0 - 1}} r^{-\gamma_0} dr
	= G(\theta).
\end{split}\]
	The last equality are due to $G(0) = 0$ and 
\[\begin{split}
	&\frac{d}{d\theta}G(\theta) 
	= - \frac{1}{\gamma_0 - 1} \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{1}{\gamma_0 - 1} - 1} \frac{d}{d\theta} \theta^{-(\gamma_0 - 1)}
	\\&\quad =  \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{\gamma_0}{\gamma_0 - 1} } \theta^{-\gamma_0}.
\end{split}\]

	Now assume that $G_0$ is another solution to the equation \eqref{eq: equation for the distribution}, we then only have to show that $G_0 = G$.
	This can be done by showing that $F(\theta) = 0$ where
\[
		F(\theta) := |G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|^{\frac{1}{\gamma_0 - 1}},
		\quad \theta \geq 0.
\]
	We claim that the non-negative function $F$ satisfies the following equation:
\[\label{eq: inequality of F(theta)}
	F(\theta)
	\leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\gamma_0 - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0,
\]
	for some constant $C_0 > 0$.
	In fact, according to the Minkowski inequality of the $L^p$ norm with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
\[\begin{split}
	&|G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|
	\\&\quad = \Big| \|e^{-\gamma_0\int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}} - \|e^{-\gamma_0\int_0^1 G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}} \Big| 
	\\ & \quad \leq \| e^{-\gamma_0\int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} - e^{-\gamma_0\int_0^1 G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}}
	\\ & \quad \leq \Big\| \gamma_0\int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} - \gamma_0\int_0^1 G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}}
	\\ & \quad \leq \gamma_0 \Big( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} - G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}| \frac{du}{u} \Big)^{\frac{1}{\gamma_0 - 1}} dr \Big)^{\gamma_0 - 1}.
\end{split}\]
	In another word, there is a constant $C_0:= \gamma_0^{\frac{1}{\gamma_0 - 1}}>0$ s.t. \eqref{eq: inequality of F(theta)} is true.
	On the other hand, according to \eqref{eq: equation for the distribution}, we have that $G(\theta) \leq c\theta$ and $G_0(\theta) \leq c \theta$.
	Therefore, we also have that there is a constant $C_1 > 0$ s.t. $F(\theta) \leq C_1 \theta$.
	Finally, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
\end{proof}

\subsection{Proof of Theorem \ref{thm: main theorem}(3)}
\label{sec: proof of result 3}
	Consider the $(\xi, \psi)$-superprocess $\{X;\mathbf P\}$ which satisfies Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
	Suppose that $m\{ x:\gamma(x)=\gamma_0 \}>0$. 
	Let $f \in p\mathscr B$ be a testing function such that $ \langle f, \phi^* \rangle_m > 0$  and $c_f:=\| \phi^{-1}f \|_\infty < \infty$.

	Without loss any of generality, we assume that $\langle f, \phi^* \rangle_m = 1$.
	As have been discussed in Section \ref{sec: conditional distribution}, in order to proof Theorem \ref{thm: main theorem}(3), we only have to show that
\[
	g(t,\theta,x)
	:=\frac{V_t (\theta \eta_t f) (x)}{\eta_t \phi(x)} 
	\xrightarrow[t\to \infty]{} G(\theta)
	:= ( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} )^{ \frac{1}{\gamma_0 - 1} },
	\quad x\in E, \theta \geq 0.
\]
	The underlying idea is to make comparison between \eqref{eq: equation for normalized V_T} and \eqref{eq: equation for the distribution}.

	In fact, from Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we can rewrite the equation for $G$:
\[\label{eq: equation for G}
	G(\theta)
	= \int_0^\theta e^{ - \frac{1} {\gamma_0 - 1} J_G(r)} dr,
	\quad \theta \geq 0,
\]
	where
\[\label{eq: definition for J_G}
	J_G(r):=
	\gamma_0 \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}}) ^{\gamma_0 - 1}\frac{du}{u},
	\quad r\geq 0 .
\]
	According to \eqref{eq: equation for normalized V_T}, we can rewrite the equation for $g$:
\[\label{eq: equation for g}
	g(t,\theta, x)= \int_0^{\theta} \Pi_x^{(\phi)} [ (\phi^{-1}f)(\xi_t) e^{-\frac{1}{\gamma_0 - 1} J_g(t,r,\xi) } ] dr,
	\quad t\geq 0, \theta \geq 0, x\in E,
\]
	where, for each $t\geq 0, r\geq 0$,
\[\label{eq: definition for J_g}
	J_g(t,r,\xi):=
	(\gamma_0 - 1)t\int_0^1 \Big(  \kappa\gamma \big(   \phi \eta_{ut}   \big)^{\gamma - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot \big)^{\gamma-1}  \Big) \big(  \xi_{(1-u)t}  \big) du.
\]
	For each $t\geq 0$ and $r\geq 0$, define
\[\label{eq: definition of J'_G}
	J'_G(t,r,\xi):=
	\gamma_0 (\gamma_0 - 1) t \int_0^1 \Big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \Big) (\xi_{(1-u)t}) du.
\]
	and
\[\label{eq: definition of J'_g}
	J'_g(t,r,\xi):= 
	\gamma_0 (\gamma_0 - 1) t \int_0^1 \Big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \Big) (\xi_{(1-u)t})  du.
\]
	The underlying idea of the proof is to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense while $t\to \infty$.

	Step 1: We will give upper bounds for $G,g,J_G,J'_G,J_g$ and $J'_g$, respectively.
	From \eqref{eq: equation for G} we have 
\[\label{eq: upper bound for G}
	G(r) 
	\leq r,
	\quad r \geq 0.
\]	
	From \eqref{eq: definition for J_G} and \eqref{eq: upper bound for G}, we have
\[\label{eq: upper bound for J_G}
	J_G(r) 
	\leq \gamma_0 r^{\gamma_0 - 1}, 
	\quad r \geq 0.
\]
	From \eqref{eq: equation for g}, we have
\[\label{eq: upper bound for g}
	g(t,r, x) \leq c_f r, 
	\quad t\geq 0, r \geq 0, x\in E.
\]
	From \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
\[\begin{split}
	J_g(t,r, \xi) 
	&\leq \|\kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \int_0^1 \big(  t\eta_{ut}^{\gamma - 1} (ru^{\frac{1}{\gamma_0 - 1}} )^{\gamma-1}  \big) \big(  \xi_{(1-u)t} \big) du
	\\&= \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \int_0^1 \big(  r^{\gamma - 1}t^{1-\frac{\gamma - 1}{\gamma_0 - 1}}  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}  \big) \big( \xi_{(1-u)t} \big) du
	\\& \leq \max\{1,r\} \cdot \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \Big\|  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}\Big\|_\infty
	\\& := c_2 \cdot \max  \{1,r\}, 
	\quad t\geq 1, r\geq 0.
\end{split}\]
	From \eqref{eq: definition of J'_g}, \eqref{eq: upper bound for g} and definition of $\eta_t$, we have
\[\begin{split}
	J'_g(t,r,\xi) 
	&\leq \gamma_0(\gamma_0 - 1) c_f^{\gamma_0 - 1}r^{\gamma_0 - 1} \|  \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \|_\infty \int_0^1 t \big( C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
	\\&=: c_3 \cdot r^{\gamma_0 - 1},
	\quad t\geq 0, r\geq 0.
\end{split}\]
	From \eqref{eq: definition of J'_G}, \eqref{eq: upper bound for G} and definition of $\eta_t$, we have
\[\label{eq: upper bound for J'_G} \begin{split}
	J'_G(t,r,\xi) 
	&\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
	\\&=: c_4 \cdot r^{\gamma_0 - 1},
	\quad t\geq 0, r\geq 0.
\end{split}\]

	Step 2: We will show that 
\[\begin{split}
	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} | 
	\\&\quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) +c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x),
	\quad t\geq 0, \theta \geq 0, x\in E,
\end{split}\]
	where
\[\begin{split}
	I_1(t,\theta,x)
	&:= \big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}} ,
	\\I_2(t,\theta,x)
	&:= \big\|  \|  J_G(r) - J'_G(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
	\\I_3(t,\theta,x)
	&:= \big\| \|  J'_G(t,r,\xi) - J'_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
\end{split}\]
	and
\[
	I_4(t,\theta,x)
	:= \big\| \| J'_g(t,r,\xi) - J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
\]
	In fact, we can rewrite \eqref{eq: equation for G} and \eqref{eq: equation for g} as:
\[
	G(\theta)^{\gamma_0 - 1} = 
	\| e^{ - J_G(r)} \|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
	\quad \theta \geq 0,
\]	
	and
\[
	g(t,\theta,x)^{\gamma_0 - 1} 
	=\big\| \| (\phi^{-1}f)(\xi_t) ^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}, 
	\quad t\geq 0, \theta \geq 0, x\in E.
\]
	Therefore, by the Minkoviski inequality we have that
\[\begin{split}
	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
	\\&\quad \leq \big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
	\\&\quad \leq I_1(t,\theta,x) + \big\| \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
	\\&\quad \leq I_1(t,\theta,x) + \big\| \|  (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} ( e^{-J_G(r)} - e^{-J_g(t,r,\xi)} )  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1}\big\| \|  J_G(r) -J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1} I_2(t,\theta,x) +c_f^{\gamma_0 - 1} I_3(t,\theta,x)+c_f^{\gamma_0 - 1} I_4(t,\theta,x),
	\quad t\geq 0, \theta \geq 0, x\in E.
\end{split}\]

	Step 3: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta,x) \xrightarrow[t\to \infty]{} 0$. 
	We first note that, by \eqref{eq: asymptotic for q_t(x,y)},
\[
	\Pi_x^{(\phi)} [(\phi^{-1}f)(\xi_t)] 
	= \phi(x)^{-1}\Pi_x[f(\xi_t) e^{- \int_0^t \beta(\xi_s) ds}]
	= \phi(x)^{-1} P^\beta_t f(x)
	\xrightarrow[t\to \infty]{} 1,
	\quad x\in E.
\]
	Therefore,
\[\begin{split}
	&e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} 
	\\&\quad =e^{ - J_G(r)} \big( 1   -  \Pi_x^{(\phi)}[ (\phi^{-1}f)(\xi_t) ]^{\gamma_0 - 1}   \big)
	\xrightarrow[t\to \infty]{} 0,
	\quad x\in E, r\geq 0.
\end{split}\]
	We also have the following bound:
\[
	\big| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big|
	\leq 1+ c_f^{\gamma_0 - 1}.
\]
	Therefore, by the bounded convergence theorem, we have that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta, x) \xrightarrow[t\to \infty]{} 0$.

	Step 4: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_2(t,\theta,x) \xrightarrow[t\to \infty]{} 0$. 
	We first note that, for each $t\geq 0$ and $r\geq 0$,
\[\begin{split}
	&J_G(r) - J'_G(t,r,\xi)
	\\&\quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- (\gamma_0 - 1) \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} tu\eta_{ut}^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}
	\\&\quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}.
\end{split}\]
	We then note that, according to \eqref{eq: upper bound for G}, for each $r \geq 0$, $u\in [0,1]$ and $x\in E$,
\[\begin{split}
	&\big| \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \frac{1}{u} \big|
	\\&\quad \leq \frac{\gamma_0}{u} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big|\big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \big| 
	\\&\quad \leq \gamma_0r^{\gamma_0 - 1} \big( 1+ \big\|C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big\|_\infty \big).
\end{split} \]
	Therefore, according to Lemma \ref{lem: ergodicity of the underlying process} and the definition of $C_X$, we have that, for each $r\geq 0$ and $x\in E$,
\[
	J_G(r) - J'_G(t,r,\xi)
	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2} \int_0^1 \frac{\gamma_0}{u} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big\langle 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1}, \phi\phi^*\big\rangle_m du
	=0.
\]
	According to \eqref{eq: upper bound for J_G} and \eqref{eq: upper bound for J'_G}, we have that, for each $r\geq 0$ and $t\geq 0$,
\[ \label{eq: upper bound for J_G - J'_G}
	\big| J_G(r) - J'_G(t,r,\xi)\big|
	\leq (\gamma_0 + c_4) r^{\gamma_0 - 1}.
\]
	Therefore, according to the bounded convergence theorem, we have that, for each $r\geq 0$ and $x\in E$,
\[
	 \big\|  J_G(r) - J'_G(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} 
	 \xrightarrow[t\to \infty]{} 0.
\]
	According to \eqref{eq: upper bound for J_G - J'_G}, we have that, for each $\theta \geq 0$, $r\in [0,\theta]$ and $x\in E$,
\[
	\big\|  J_G(r) - J'_G(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} 
	\leq (\gamma_0 + c_4) \theta^{\gamma_0 - 1}.
\]
	Finally, according to the bounded convergence theorem, we have that, for each $\theta\geq 0$ and $x\in E$, $I_2(t,\theta,x)\xrightarrow[t\to \infty]{} 0$.

	Step 5: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_4(t,\theta,x) \xrightarrow[t\to \infty]{} 0$. 
	We first note that, for each $t\geq 0$ and $r\geq 0$, we have 
\[\label{eq: expression for J_g - J'_g}
	J_g(t,r,\xi) - J'_g(t,r,\xi) 
	= (\gamma_0 - 1)t\int_0^1 \big( \mathbf 1_{\gamma(\cdot )> \gamma_0}  \kappa\gamma (   \phi \eta_{ut}   )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) \big(  \xi_{(1-u)t}  \big) du.
\]
	We then note that, according \eqref{eq: upper bound for g} and the definition of $\eta_t$, for each $r\geq 0$, $u\in (0,1)$ and $x\in E$, we have
\[\label{eq: integer in the expression of J_g - J'_g convergences to 0}\begin{split}
	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}  
	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \eta_{ut}^{\gamma(x) - 1} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
	\\&\quad = (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \big( C_X(\gamma_0 - 1) ut\big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
	\\&\quad \leq (\gamma_0 - 1) \mathbf 1_{\gamma(x) > \gamma_0} t^{1-\frac{\gamma(x) - 1}{\gamma_0 - 1}}\big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}
	\\&\quad \xrightarrow[t\to \infty]{} 0.
\end{split}\]
	This also gives an upper bound: For each $r\geq 0$, $u \in (0,1)$, $x\in E$ and $t\geq 1$, we have
\[\label{eq: upper bound for the integrator of J_g - J'_g} \begin{split}
	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}  
	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
\end{split}\]
	Now, with \eqref{eq: expression for J_g - J'_g}, \eqref{eq: integer in the expression of J_g - J'_g convergences to 0} and \eqref{eq: upper bound for J_g - J'_g}, we can apply Lemma \ref{lem: ergodicity of the underlying process} to function
\[
	(y,u,t)\mapsto (\gamma_0 - 1)t  \mathbf 1_{\gamma(y)> \gamma_0}  \kappa(y)\gamma(y) \big(   \phi(y) \eta_{ut}   \big)^{\gamma(y) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},y \big)^{\gamma(y)-1},
\]
	which says that, for each $r\geq 0$,
\[
	J_g(t,r,\xi) - J'_g(t,r,\xi) 
	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)}; L^2} 0.
\]
	According to \eqref{eq: expression for J_g - J'_g} and \eqref{eq: upper bound for the integrator of J_g - J'_g}, for each $r\geq 0$ and $t\geq 1$, we have that
\[\label{eq: upper bound for J_g - J'_g}
	\big |	J_g(t,r,\xi) - J'_g(t,r,\xi)  \big |
	\leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
\]
	Therefore, according to the bounded convergence theorem, for each $r\geq 0$ and $x\in E$, we have that
\[
		\big\| J'_g(t,r,\xi) - J_g(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} 
		\xrightarrow[t\to \infty]{} 0.
\]
	According to \eqref{eq: upper bound for J_g - J'_g}, for each $\theta \geq 0$, $r\in [0,\theta]$ , $t\geq 1$ and $x\in E$, we have that
\[
	\big\| J'_g(t,r,\xi) - J_g(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} 
	\leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f \theta \phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
\]
	Therefore, according to the bounded convergence theorem, for each $\theta \geq 0$ and $x\in E$, we have that $I_4(t,\theta, x) \xrightarrow[t\to \infty]{} 0$.

	Step 6: We will show that
\[
	\limsup_{t\to \infty} I_3(t,\theta,x) 
	\leq \gamma_0 \Big(  \int_0^\theta  \| M(r u^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1}, 
	\quad \theta \geq 0, x\in E,
\]
	where
\[
	M(t,r,x)
	:= |G(r)^{\gamma_0 - 1} - g(t,r,x)^{\gamma_0 - 1}|^{\frac{1}{\gamma_0 - 1}},
	\quad t\geq 0, r\geq 0, x\in E,
\]
	and
\[
	M(r,x)
	:= \limsup_{t\to \infty} M(t,r,x);
	\quad M(r):= \sup_{x\in E} M(r,x),
	\quad r\geq 0, x\in E.
\]
	We first note that, according to \eqref{eq: upper bound for G} and \eqref{eq: upper bound for g}, we have the following bound:
\[\label{eq: upper bound for M(t,r,x)}
	M(t,r,x) 
	\leq |r^{\gamma_0 - 1} + c_f^{\gamma_0 - 1} r^{\gamma_0 - 1} | ^{\frac{1}{\gamma_0 - 1}}
	=: c_6 r,
\]
	where the constant $c_6$ is not related to $t$ and $x$. 
	Therefore, we have
\[
	M(r,x)
	\leq M(r)
	\leq c_6 r,
	\quad r\geq 0, x\in E.
\]	
	We then note that, from the definition of $J'_G, J'_g$ and $\eta_t$, we have
\[\label{eq: differences between J'_G and J'_g}\begin{split}
	&|J'_G(t,r,\xi) - J'_g(t,r,\xi)|
	\\&\quad \leq \gamma_0(\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du
	\\&\quad = \gamma_0 C_X^{-1}\int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa  \phi^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du,
	\quad t\geq 0, r\geq 0.
\end{split}\]
	According to \eqref{eq: upper bound for M(t,r,x)}, we have the following upper bound:
\[\begin{split}
		u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}}, x) 
		\leq c_6 ru^{\frac{2-\gamma_0}{\gamma_0 - 1}}
		\leq c_6 r,
		\quad u\in (0,1), r\geq 0, t\geq 0, x\in E.
\end{split}\]
	Therefore, fixing an $r\geq 0$, we can apply Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process} to function 
\[
	(y,u,t) 
	\mapsto \gamma_0 C_X^{-1}\mathbf 1_{\gamma(y) = \gamma_0} \kappa(y)  \phi(y)^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},y)^{\gamma_0 - 1}
\]
	since it is bounded and Borel measurable on $E\times (0,1) \times [0,\infty)$.
	Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process},  \eqref{eq: differences between J'_G and J'_g} and definition of $M(r,x), M(r)$ and $C_X$, we have
\[\label{eq: limsup of J_G - J'_g}\begin{split}
	&\limsup_{t\to \infty} \| J_G'(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{\phi};\frac{1}{\gamma_0 - 1}}
	\\&\quad\leq  \gamma_0 C_X^{-1} \int_0^1 \big\langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} M(ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}, \phi\phi^* \big\rangle_m \frac{du}{u}
	\\&\quad\leq  \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}.
\end{split}\]
	We now recall the reverse Fatou's lemma in the sense of $L^p$ norm with $p\geq 1$: Let $(f_n)_{n\in \mathbb N}$ be a sequence of non-negative measurable functions defined on a measure space $S$ with $\sigma$-finite measure $\mu$. If there exists a non-negative $L^p(\mu)$-integrable function $g$ on $S$ such that $f_n \leq g$ for all $n$, then according to the classical reverse Fatou's lemma, we have
\[
	\limsup_{n\to \infty}\big\| f_n \big\|_{\mu;p} 
	= \big (   \limsup_{n\to \infty}  \int f^p_n d\mu        \big)^{\frac{1}{p}} 
	\leq  \big (   \int \limsup_{n\to \infty} f^p_n d\mu        \big)^{\frac{1}{p}} 
	= \big\| \limsup_{n\to \infty} f_n \big\|_{\mu;p}.
\]
	Now, use this version of Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
\[\begin{split}
	&\limsup_{t\to \infty} I_3(t,\theta, x)
	\leq \big\| \limsup_{t\to \infty} \|    J'_G(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
	\\&\quad\leq \Big\| \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
	= \gamma_0 \bigg( \int_0^\theta \Big (   \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}   \Big )^{\frac{1}{\gamma_0 - 1}} dr \bigg)^{\gamma_0 - 1}
	\\&\quad = \gamma_0 \Big(  \int_0^\theta  \| M(r u^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1}, 
	\quad \theta \geq 0, x\in E.
\end{split}\]

	Step 7. We will show that $M(\theta) = 0$ for each $\theta \geq 0$.
	We first claim that
\[
	M(\theta) 
	\leq c_M\int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr ,
	\quad \theta \geq 0,
\]
	for some constant $c_M > 0$.
	In fact, a direct application of step 2-6 gives that, for each $t\geq 0$ and $x\in E$:
\[\begin{split}
	&M(r,x)^{\gamma_0 - 1}
	=\limsup_{t\to \infty} M(t,r,x)^{\gamma_0 - 1} 
	= \limsup_{t\to \infty}|G(r)^{\gamma_0 - 1} - g(t,r,x)^{\gamma_0 - 1}|
	\\&\quad \leq \limsup_{t\to \infty} \big( I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) +c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x) \big)
	\\& \quad = c_f^{\gamma_0 - 1} \limsup_{t\to \infty} I_3(t,\theta ,x)
	\leq c_f^{\gamma_0 - 1} \gamma_0 \Big(  \int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1}.
\end{split}\]
	Therefore, for each $\theta \geq 0$,
\[
	M(\theta) 
	= \sup_{x\in E}  M(r,x)
	\leq c_f \gamma_0^{\frac{1}{\gamma_0 - 1}} \int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr.
\]
	Finally, according to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality which gives us the desired result.

	Finally, recalling the definition of $M$, by showing that $M\equiv 0$, the proof is complete.

\begin{thebibliography}{10}

	\bibitem{AsmussenHering1983Branching}
	S.~Asmussen and H.~Hering, \emph{Branching processes}, Progress in Probability
	and Statistics, vol.~3, Birkh{\"a}user Boston, Inc., Boston, MA, 1983.
	\MR{701538}

	\bibitem{AthreyaNey1974Functionals}
	K.~Athreya and P.~Ney, \emph{Functionals of critical multitype branching
		processes}, Ann. Probability \textbf{2} (1974), 339--343. \MR{0356264}

	\bibitem{AthreyaNey1972Branching}
	K.~B. Athreya and P.~E. Ney, \emph{Branching processes}, Springer-Verlag, New
	York-Heidelberg, 1972, Die Grundlehren der mathematischen Wissenschaften,
	Band 196. \MR{0373040}

	\bibitem{BinghamGoldieTeugels1989Regular}
	N.~H. Bingham, C.~M. Goldie, and J.~L. Teugels, \emph{Regular variation},
	Encyclopedia of Mathematics and its Applications, vol.~27, Cambridge
	University Press, Cambridge, 1989. \MR{1015093}

	\bibitem{Borovkov1989Method}
	K.~A. Borovkov, \emph{A method of proving limit theorems for branching
		processes}, Theory of Probability \& Its Applications \textbf{33} (1989),
	no.~1, 105--113.

	\bibitem{EckhoffKyprianouWinkel2015Spines}
	M.~Eckhoff, A.~E. Kyprianou, and M.~Winkel, \emph{Spines, skeletons and the
		strong law of large numbers for superdiffusions}, Ann. Probab. \textbf{43}
	(2015), no.~5, 2545--2610. \MR{3395469}

	\bibitem{EnglanderKyprianou2004Local}
	J.~Engl{\"a}nder and A.~E. Kyprianou, \emph{Local extinction versus local
		exponential growth for spatial branching processes}, Ann. Probab. \textbf{32}
	(2004), no.~1A, 78--99. \MR{2040776}

	\bibitem{EvansPerkins1990Measure-valued}
	S.~N. Evans and E.~Perkins, \emph{Measure-valued {M}arkov branching processes
		conditioned on nonextinction}, Israel J. Math. \textbf{71} (1990), no.~3,
	329--337. \MR{1088825}

	\bibitem{GoldsteinHoppe1978Critical}
	M.~I. Goldstein and F.~M. Hoppe, \emph{Critical multitype branching processes
		with infinite variance}, Journal of Mathematical Analysis and Applications
	\textbf{65} (1978), no.~3, 675--686.

	\bibitem{Harris2002The-theory}
	T.~E. Harris, \emph{The theory of branching processes}, Dover Phoenix Editions,
	Dover Publications, Inc., Mineola, NY, 2002, Corrected reprint of the 1963
	original [Springer, Berlin; MR0163361 (29 \#664)]. \MR{1991122}

	\bibitem{IyerLegerPego2015Limit}
	G.~Iyer, N.~Leger, and R.~L. Pego, \emph{Limit theorems for {S}moluchowski
		dynamics associated with critical continuous-state branching processes}, Ann.
	Appl. Probab. \textbf{25} (2015), no.~2, 675--713. \MR{3313753}

	\bibitem{JoffeSpitzer1967On-multitype}
	A.~Joffe and F.~Spitzer, \emph{On multitype branching processes with {$\rho
			\leq 1$}}, J. Math. Anal. Appl. \textbf{19} (1967), 409--430. \MR{0212895}

	\bibitem{KestenNeySpitzer1966The-Galton-Watson}
	H.~Kesten, P.~Ney, and F.~Spitzer, \emph{The {G}alton-{W}atson process with
		mean one and finite variance}, Teor. Verojatnost. i Primenen. \textbf{11}
	(1966), 579--611. \MR{0207052}

	\bibitem{KimSong2008Intrinsic}
	P.~Kim and R.~Song, \emph{Intrinsic ultracontractivity of non-symmetric
		diffusion semigroups in bounded domains}, Tohoku Math. J. (2) \textbf{60}
	(2008), no.~4, 527--547. \MR{2487824}

	\bibitem{Kolmogorov1938Zur-losung}
	A.~N. Kolmogorov, \emph{Zur l{\"o}sung einer biologischen aufgabe}, Comm. Math.
	Mech. Chebyshev Univ. Tomsk \textbf{2} (1938), no.~1, 1--12.

	\bibitem{Kyprianou2014Fluctuations}
	A.~E. Kyprianou, \emph{Fluctuations of {L}{\'e}vy processes with applications},
	second ed., Universitext, Springer, Heidelberg, 2014, Introductory lectures.
	\MR{3155252}

	\bibitem{Kyprianou2008Continuous}
	A.~E. Kyprianou and J.~C. Pardo, \emph{Continuous-state branching processes and
		self-similarity}, Journal of Applied Probability \textbf{45} (2008), no.~4,
	1140--1160.

	\bibitem{Li2011Measure-valued}
	Z.~Li, \emph{Measure-valued branching {M}arkov processes}, Probability and its
	Applications (New York), Springer, Heidelberg, 2011. \MR{2760602}

	\bibitem{LiuRenSong2009Llog}
	R.~Liu, Y.-X. Ren, and R.~Song, \emph{{$L\log L$} criterion for a class of
		superdiffusions}, J. Appl. Probab. \textbf{46} (2009), no.~2, 479--496.
	\MR{2535827}

	\bibitem{Pakes2010Critical}
	A.~G. Pakes, \emph{Critical {M}arkov branching process limit theorems allowing
		infinite variance}, Adv. in Appl. Probab. \textbf{42} (2010), no.~2,
	460--488. \MR{2675112}

	\bibitem{Powell2015An-invariance}
	E.~Powell, \emph{An invariance principle for branching diffusions in bounded
		domains}, arXiv preprint arXiv:1512.00031 (2015).

	\bibitem{RenSongSun2017A-2-spine}
	Y.-X. Ren, R.~Song, and Z.~Sun, \emph{A 2-spine decomposition of the critical
		galton-watson tree and a probabilistic proof of yaglom's theorem}, arXiv
	preprint arXiv:1706.07125 (2017).

	\bibitem{RenSongSun2017Spine}
	\bysame, \emph{Spine decompositions and limit theorems for a class of critical
		superprocesses}, arXiv preprint arXiv:1711.09188 (2017).

	\bibitem{RenSongZhang2015Limit}
	Y.-X. Ren, R.~Song, and R.~Zhang, \emph{Limit theorems for some critical
		superprocesses}, Illinois J. Math. \textbf{59} (2015), no.~1, 235--276.
	\MR{3459635}

	\bibitem{RenSongZhang2017Central}
	\bysame, \emph{Central limit theorems for supercritical branching nonsymmetric
		{M}arkov processes}, Ann. Probab. \textbf{45} (2017), no.~1, 564--623.
	\MR{3601657}

	\bibitem{RenYangZhao2014Conditional}
	Y.-X. Ren, T.~Yang, and G.~Zhao, \emph{Conditional limit theorems for critical
		continuous-state branching processes}, Science China Mathematics \textbf{57}
	(2014), no.~12, 2577--2588.

	\bibitem{Schaefer1974Banach}
	H.~H. Schaefer, \emph{Banach lattices and positive operators}, Springer-Verlag,
	New York-Heidelberg, 1974, Die Grundlehren der mathematischen Wissenschaften,
	Band 215. \MR{0423039}

	\bibitem{Slack1968A-branching}
	R.~S. Slack, \emph{A branching process with mean one and possibly infinite
		variance}, Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{9} (1968),
	139--145. \MR{0228077}

	\bibitem{Slack1972Further}
	\bysame, \emph{Further notes on branching processes with mean 1}, Zeitschrift
	f{\"u}r Wahrscheinlichkeitstheorie und Verwandte Gebiete \textbf{25} (1972),
	no.~1, 31--38.

	\bibitem{Vatutin1977Limit}
	V.~A. Vatutin, \emph{Limit theorems for critical markov branching processes
		with several types of particles and infinite second moments}, Sbornik:
	Mathematics \textbf{32} (1977), no.~2, 215--225.

	\bibitem{Yaglom1947Certain}
	A.~M. Yaglom, \emph{Certain limit theorems of the theory of branching random
		processes}, Doklady Akad. Nauk SSSR (N.S.) \textbf{56} (1947), 795--798.
	\MR{0022045}

	\bibitem{Zolotarev1957More}
	V.~M. Zolotarev, \emph{More exact statements of several theorems in the theory
		of branching processes}, Theory of Probability \& Its Applications \textbf{2}
	(1957), no.~2, 245--253.

\end{thebibliography}

\end{document}

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
 \usepackage{autonum}
-\usepackage[utf8]{inputenc}
-\usepackage{comment}
 \newtheorem{thm}{Theorem}[section]
@@
 	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ denote a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
-	Denoted by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function. 
+	Denoted by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
+	%new added 
+	and  $\mathbf F_n(\mathbf s), \quad n>1$, its iterates. 
+	%end new
 	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ its left and right principle eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ the vector $(1,\dots, 1)$.
@@
 \]
-	Then \cite{GoldsteinHoppe1978Critical} shows that, if we let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ the vector $(0,\dots, 0)$, then for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
+%	Then \cite{GoldsteinHoppe1978Critical} shows that, 
+Then \cite{GoldsteinHoppe1978Critical} showed that,
+	if we let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ the vector $(0,\dots, 0)$, then for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
 \[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
-	n L(a_n) \operatorname{Pr}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha 
+	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
 	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha,
@@
 	where $\beta \in b\mathscr B_E$, $\alpha \in bp\mathscr B_E$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ s.t. $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
-	We refer our reader to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
+	We refer our readers to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
 	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.
@@
 	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
-	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to result \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
+	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to results \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
 
 	As a continuation of those works, it is natural to ask weather results paralleling to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} can be obtained for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
-	Perhaps a simpler version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements. 
+	%Perhaps a 	simpler
+	A simpler
+	version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements.
 	Kyprianou \cite{Kyprianou2008Continuous} considered a CSBP $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$.
@@
 \]
-	Later, \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ which verifying Grey's condition. 
+	Later, \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ 
+	%which verifying Grey's condition.
+	which satisfies Grey's condition.
 	In order the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
@@
 	A regrously statements of the assumptions and the results are presented in the next subsection.
-	Perhaps it is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ is primarily depended only by the lowest index $\gamma_0$.
+	%Perhaps it
+	It
+	is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ is primarily depended only by the lowest index $\gamma_0$.
 
@@
 	We first set some notations.
-	For any measurable space $(E,\mathscr E)$, denote by $r\mathscr E$ the colloction of all the measurable real function on $E$. 
+	For any measurable space $(E,\mathscr E)$, denote by $r\mathscr E$ the colloction of all measurable real functions on $E$.
 	Define $b\mathscr E :=\{f \in r\mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $p\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $s\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\neq 0\}$.
 	Define $bp\mathscr E := b\mathscr E \cap p\mathscr E$, $bs\mathscr E:= b\mathscr E \cap s\mathscr E$, $sp\mathscr E:= s\mathscr E \cap p\mathscr E$ and $spb\mathscr E : = s\mathscr E \cap p\mathscr E \cap b\mathscr E$.
-	Denote by $\mathcal M_E$ the collection of all the measures on $(E,\mathscr E)$.
-	Denote by $\mathcal M^\sigma_E$ the collection of all the $\sigma$-finite measures on $(E,\mathscr E)$. 
+	Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
+	Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
 	In this paper, to simplify the notation, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$.
-	We also write $\langle f,g\rangle_m$ meaning $ \int_E fg dm$ if we want to emphasize the inner product structure of Hilbert space $L^2(dm)$.
+%	We also write $\langle f,g\rangle_m$ meaning $ \int_E fg dm$  	if we want  to emphasize the inner product structure of Hilbert space $L^2(dm)$.
+    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$  
+    to emphasize that it is the inner product in the Hilbert space $L^2(dm)$.
 	For any $\phi \in p\mathscr E$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
-	In particular, $\mathcal M^1_E$ is the collection of all the finite measures on $E$.
-	If $E$ is a topology space, denote by $\mathscr B_E$ the collection of all the Borel measurable subset of $E$.
+	In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
+	If $E$ is a topology space, denote by $\mathscr B_E$ the collection of all  Borel measurable subsets of $E$.
 
@@
 	Let the \emph{state space} $E$ be a locally compact separable metric space,
-	the \emph{underlying motion} $\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be a $E$-valued Hunt process with its life time denoted by $\zeta$, and the \emph{branching mechanism} $\psi$ being a function on $ E\times [0,\infty)$ with form of \eqref{eq: branching mechanism}.
+	the \emph{underlying motion} $\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be a $E$-valued Hunt process with its life time denoted by $\zeta$, and the \emph{branching mechanism} $\psi$ 
+%	being a function on $ E\times [0,\infty)$ with form of
+be a function on $E\times[0,\infty)$ given by
+	\eqref{eq: branching mechanism}.
 	We say a $\mathcal M^1_E$-valued Hunt process $\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  testing function $f\in bp\mathscr B_E$, we have
@@
 	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
-	=\Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
+	=\Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],\quad
 	t\geq 0, x \in E.
@@
 	P^\beta_tf(x)
-	= \Pi_x \big[e^{\int_0^{t\wedge \zeta} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
+	= \Pi_x \big[e^{\int_0^{t} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
 	\quad t\geq 0, x\in E, f\in b\mathscr B_E.
 \]
-	(Notice that if $\beta \equiv 0$, then $P_t:= P^\beta_t$ is the \emph{transition semigroup} of process $\{\xi; \Pi\}$.) 
+	(Notice that if $\beta \equiv 0$,
+	%then $P_t:= P^\beta_t$ is the \emph{transition semigroup} of process $\{\xi; \Pi\}$.)
+	 $P_t:= P^0_t$ is the \emph{transition semigroup} of process $\xi:=\{(\xi)_{t\ge 0}; (\Pi)_{x\in E}\}$.)
 	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
@@
 \end{split}\]
-	and, $x \mapsto \int_E p_t(x,y)^2 m(dy)$, $x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous on $E$.
+	and, $x \mapsto \int_E p_t(x,y)^2 m(dy)$
+%	, 
+and 
+	$x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous on $E$.
 \end{asp}
@@
 \]
-	We will call $(p^\beta_t)$ the \emph{transition density of semigroup $(P^\beta_t)$}.
+	%We will call $(p^\beta_t)$ the 
+	 $(p^\beta_t)$ is called the
+	\emph{transition density of semigroup $(P^\beta_t)$}.
 	Define a family of transition kernels $(P^{\beta *}_t)_{t \geq 0}$ on $E$ by
@@
 	Therefore, this size-biased transformation can be viewed as a martingale change of measure.
-	Under the Assumption \ref{asp: 1} and \ref{asp: 3}, the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process. 
+	Under the Assumption \ref{asp: 1} and \ref{asp: 3}, 
+	Under the Assumptions \ref{asp: 1} and \ref{asp: 3}, 
+	the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process.
 	To study the asymptotic behavior of superprocesses, one can take advantage of this ergodicity.
@@
 	Let $(Y_t)$ be a branching diffusion processes in a bounded domain with finite second moment.
-	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation which is known to be satisfied by $(t,x) \mapsto P(Y_t \not\equiv 0)$, the survival probability for branching diffusion process, is tricky.
+	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation
+%which is known to be 
+	satisfied by $(t,x) \mapsto P(Y_t \not\equiv 0)$, the survival probability for branching diffusion process, is tricky.
 	Instead, using a spine decomposition approach, \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principle eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capture the uniform speed.
@@
 
-	In \cite{Powell2015An-invariance}, for the critical branching diffusion in a bounded domain with finite variance, and in \cite{RenSongZhang2015Limit} and \cite{RenSongSun2017Spine}, for the critical superprocess with finite variance, when the authors were establishing the conditional weak convergence, they did not proved the results for all general testing functions $f$ at the same time.
+	In \cite{Powell2015An-invariance}, for the critical branching diffusion in a bounded domain with finite variance, and in \cite{RenSongSun2017Spine} and
+	\cite{RenSongZhang2015Limit}, for the critical superprocess with finite variance, when the authors were establishing the conditional weak convergence, they did not prove the results for all general testing functions $f$ at the same time.
 	Instead, the authors first established the results for a specific testing function $\phi$, the principle eigenfunction of the mean matrix of the corresponding processes, and then passed the result to a general testing function $f$.
@@
 	This generalized spine decomposition theorem considered the $X_T(g)$-transform of the superprocess $(X_t)_{0\leq t\leq T}$ for a large class of general function $g$.
-	The transformed process behaves similarly as in the classical case, despite that, the spine process $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$ is not the same.
+	The transformed process behaves similarly as in the classical case, despite that, the spine processes $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$ 
+	%is not the same. 
+	are not consistent for all $T>0$.
 
@@
 \]
-	Further, if $\gamma_0 = 0$, then we say $f$ is slowly varying.
+	%Further, if $\gamma_0 = 0$, 
+	Further, if $\gamma = 0$,
+	then we say $f$ is slowly varying.
 	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, if $L$ is a function which is slowly varying at $\infty$, then it can be written in the form
@@
 
-\begin{lem}[{\cite[Proposition 1.5.8. and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
+\begin{lem}[{\cite[Propositions 1.5.8. and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
 \label{lem: exchange slowly varying function and integration}
@@
 
-	The following lemma considered the inverse of an invertible regularly varying function. 
-	In this paper, if a function $f$ is invertible, we write $f^{(-1)}$ for its inverse; if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
+	The following lemma considered the inverse of an 
+%	invertible  
+   %R: same change below without mark
+	reversible
+	regularly varying function.
+	In this paper, if a function $f$ is reversible, we write $f^{(-1)}$ for its inverse; if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
 
@@
 \label{lem: regularly variation and inverse}
-	Suppose that $f$ is an invertible map from $(0,\infty)$ to $(0,\infty)$. Then, for each $\alpha > 0$, we have
+	Suppose that $f$ is a reversible map from $(0,\infty)$ to $(0,\infty)$. Then, for each $\alpha > 0$, we have
 \[ \label{eq: inverse of a regularly varying function at infinity with alpha > 0}
@@
 \]
-	Suppose that Assumption \ref{asp: 1} and \ref{asp: 2} is true. Integrating with measure $\phi^*dm$, we can derive from \eqref{eq:mean-fkpp} that
+%	Suppose that Assumption \ref{asp: 1} and \ref{asp: 2} is true. 
+    Suppose that Assumptions \ref{asp: 1} and \ref{asp: 2} hold. 
+%	Integrating with measure $\phi^*dm$, we can derive from \eqref{eq:mean-fkpp} that
+Integrating both sides of\eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we arrive that
 	\[\label{eq:langleVtfphiranglem_equation}
@@
 	= \langle V_sf,\phi^*\rangle_m,
-	\quad s,t\geq 0, f\in bp\mathscr B_E.
+%	\quad s,t\geq 0, f\in bp\mathscr B_E.
+	\quad t\geq s\geq 0, f\in bp\mathscr B_E.
 	\]
@@
 \subsubsection{Non-presistency}
-	Let $\mathbb W$ be the collection of all the $\mathcal M^1_E$-valued cadlag paths on $[0,\infty)$. 
+	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued cadlag paths on $[0,\infty)$.
 	We refer to $\mathbb W$ the \emph{canonical space of $X$}.
@@
 
-	We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$ for all $x\in E$ and $t> 0$.
+	We say that $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$ for all $x\in E$ and $t> 0$.
 	Suppose that $X$ is non-persistent, then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ s.t.
@@
 	\item
-	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Possion random measure in some probability space with mean measure $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, 
+	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Possion random %measure in some
+	measure defined on some
+	probability space with mean measure $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
 	then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\tilde X_0 := \mu$ and $\tilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
@@
 	v_t(x)
-	:= \lim_{t\to \infty} V_t(\mathbf 1_E)(x)
+%	:= \lim_{t\to \infty} V_t(\mathbf 1_E)(x)
+	:= \lim_{\lambda\to \infty} V_t(\lambda\mathbf 1_E)(x)
 	= -\log \mathbf P_{\delta_x} [X_t \equiv 0]
-	= \mathbb N_x[X_t\not \equiv 0],
+%	= \mathbb N_x[X_t\not \equiv 0],
+	= \mathbb N_x[W_t\not \equiv 0],
 	\quad t\geq 0, x\in E.
@@
 \[ \label{eq: equation for mu v-t}\begin{split}
-	\mathbb N_\mu[X_t\not \equiv 0]
+%	\mathbb N_\mu[X_t\not \equiv 0]
+\mathbb N_\mu[W_t\not \equiv 0]
 	&= -\log \mathbf P_{\mu} [X_t \equiv 0]
@@
 
+%new added
+It is know that for any $f\in bp{\cal B}_E$,
+\[\label{mean-N}
+\mathbb N_{\mu}[W_t(f)]=\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
+\]
+see \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
+The we see that $\{(X_t(\phi))_{t\geq 0};\mathbf P_{\mu}\}$ is nonnegative martingale,  and $\{(W_t(\phi))_{t\geq 0};\mathbb N_{\mu}\}$ is also a nonnegative martingale.
+%end new
+
 \subsection{Spine decompositions}
@@
 	Let $(\Omega, \mathscr F)$ be a measurable space with $\sigma$-finite measure $\mu$, which is not necessarily a probability measure or a finite measure.
-	For any $F\in r\mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and $\mu [f] \in (0,\infty)$. 
-	And if this happens, define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ s.t. $d\mu^F= \frac{F}{\mu[F]}d \mu$.
+	For any $F\in r\mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and 
+	%$\mu [f] \in (0,\infty)$.
+	$\mu [F] \in (0,\infty)$.
+	And if this happens, define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ s.t. 
+%  $d\mu^F= \frac{F}{\mu[F]}d \mu.$
+	$$d\mu^F= \frac{F}{\mu[F]}d \mu.$$
 
@@
 
-	Note that if we have an a.s. event $\{B;P\}$, i.e. $P(B) = 1$, then under any possible size-biased transform of probability $P$, $B$ is still an a.s. event. 
-	From this, we have that $\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
-	Note that $\mathbb N_\mu$ is not typically a probability measure. 
+%	Note that if we have an a.s. event $\{B;P\}$, i.e. $P(B) = 1$, then under any possible size-biased transform of probability $P$, $B$ is still an a.s. event.
+%	From this, we have that 
+Note that
+		$\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
+%	Note that $\mathbb N_\mu$ is not typically a probability measure.
+Also note that  $\mathbb N_\mu$ is not a probability measure.
 	But after the transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
-	Since $\mathbb N_x(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.
+%	Since $\mathbb N_x(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.
+	Since $\mathbb N_{\mu}(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.
 
@@
 \label{rem: initial configuration of transformed process}
-	Note that $\Pi_{\mu}$ is not typically a probability measure. 
+	Note that $\Pi_{\mu}$ is not typically a probability measure. ({\bf Remark: why  $\Pi_{\mu}$ is not probability measure？})
 	But after the transformation, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
 	We can verify that
-\[
-	\Pi_{\mu}^{(T,g)} (\xi_0 \in dx) 
-	= \mu(P^\beta_T g)^{-1} S_T g(x)\mu(dx),
-	\quad x\in E.
-\] 
-	In fact, 
+%moved from below with modification
+Note that
 \[
@@
 	= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } f(\xi_0) ]
-	= \mu(S_T g)^{-1} \int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx).
-\]
+%	= \mu(S_T g)^{-1} 
+	= \mu(P^\beta_T g)^{-1} 
+	\int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx),
+\]
+which says that
+%end move
+\[
+	\Pi_{\mu}^{(T,g)} (\xi_0 \in dx)
+	= \mu(P^\beta_T g)^{-1}
+%S_T g(x)\mu(dx),
+    P^\beta_T g(x)\mu(dx),
+	\quad x\in E.
+\]
+%The following is moved forward	
+%	In fact,
+%\[
+%	\Pi_{\mu}^{(T,g)} [ f(\xi_0) ]
+%	= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } %f(\xi_0) ]
+%	= \mu(S_T g)^{-1} 
+%	\int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx).
+%\]
 \end{rem}
@@
 	\int_0^1 F(\xi_{(1-u)t},u,t) du
-	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)} ; L^2} \int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle_m du,
+%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)} ; L^2} 
+\xrightarrow[t\to \infty]{ L^2(\Pi_x^{(\phi)})} 
+\int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle_m du,
 	\quad x\in E.
@@
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
-	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2} \int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
-	\quad x\in E.
-\]
+%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2} 
+	\xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})}
+	\int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
+	\quad x\in E,
+\]
+%new added
+wwhich implies convergence in probability.
+%end new
 	The bounded convergence theorem then gives that, for each $p \geq 1$,
@@
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
-	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^p} \int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
+%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^p}
+	\xrightarrow[t\to \infty]{L^p(\Pi_x^{(\phi)})}
+	\int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
 	\quad x\in E.
@@
 \label{sec: proof of result 1}
-	Let $\{X; \mathbf P\}$ be a superprocess satisfies Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
-	In this section, we will proof the following stronger result:
+	Let $\{X; \mathbf P\}$ be a superprocess satisfies 
+	%Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	Assumptions \ref{asp: 1}-\ref{asp: 4}.
+%	In this section, we will proof the following stronger result:
+    In this section, we will prove the following stronger result:
 
@@
 	Then, we know that $\tilde \kappa = \kappa$ and $\tilde \gamma = \gamma$ almost everywhere with respect to measure $m$.
-	Define $\tilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\tilde \psi(\cdot, z) = \psi(\cdot , z) $ almost everywhere with respect to measure $m$.
+	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z) $ almost everywhere with respect to measure $m$.
 	Therefore, if we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
 \[
-	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \tilde \psi (\xi_s,V_{t-s} f) ds \Big]
+	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \widetilde \psi (\xi_s,V_{t-s} f) ds \Big]
 	=\Pi_x \big[ f(\xi_t)\mathbf 1_{t<\zeta} \big].
@@
 \[
-	\hat\psi(z) 
+	\widehat\psi(z)
 	:= - (\|\beta\|_\infty +\kappa_0 )z + \kappa_0 z^{\gamma_0},
@@
 \[
-	\inf_{x\in E}\tilde \psi(x,z) 
+	\inf_{x\in E}\widetilde \psi(x,z)
 	\geq \hat\psi(z),
 	\quad z\geq 0;
-	\quad \int_1^\infty \frac{1}{\hat\psi(z)} dz 
+	\quad \int_1^\infty \frac{1}{\widehat\psi(z)} dz
 	< \infty;
@@
 \]
-	Therefore $\tilde \psi$ satisfies the condition of \cite[Lemma 2.3]{RenSongZhang2015Limit}.
-	As a consequence, by \cite[Lemma 2.3]{RenSongZhang2015Limit}, we have the desired result.
+	Therefore $\widetilde \psi$ satisfies the condition of \cite[Lemma 2.3]{RenSongZhang2015Limit}.
+	As a consequence,
+	%by \cite[Lemma 2.3]{RenSongZhang2015Limit}, 
+	we have the desired result.
 \end{proof}
@@
 \label{sec: proof of result 2}
-	Let $\{X; \mathbf P\}$ be a superprocess satisfies Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	Let $\{X; \mathbf P\}$ be a superprocess satisfies 
+	%Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	Assumptions \ref{asp: 1}-\ref{asp: 4}.
 	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent.
@@
 	Therefore, we have $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
-	Then, according to \eqref{eq:langleVtfphiranglem_equation}, by monotonicity, we have another equation
+	Then, according to \eqref{eq:langleVtfphiranglem_equation}
+%	, by monotonicity,  
+and monotone convergence theorem,
+	we have another equation
 \[ \label{eq: equation of <vt,phi>}
@@
 	For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t)_{t\geq 0}, (\xi_t)_{t\geq 0},\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$.
-	According to \eqref{eq: definition of v_t(x)} and Theorem \ref{thm: size-biased decomposition}, we have that for each $t>0$,
+%	According to \eqref{eq: definition of v_t(x)} and Theorem \ref{thm: size-biased decomposition}, 
+	According to \eqref	{eq: equation for mu v-t} and Theorem \ref{thm: spine representation}, 
+	we have that for each $t>0$,
 \[\begin{split}\label{eq:vt-and-Y}
@@
 	Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
-	Therefore, to complete the proof, we only have to show that
+	Therefore, to complete the proof, 
+	%we only have to show that
+	we only need to show that
 \[
@@
 
-	From the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, the following identity can be verified:
+	From the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, 
+	%the following identity can be verified:
+	 we have the following identities:
 \[\label{eq: some equations for PY-1}\begin{split}
@@
 
-	Taking constants $c_0, c_1>0$ as in \eqref{eq:q(t,x,y)}, if $t_0 > 1$, then it has been argued in the proof of
-	\cite[Lemma 5.3]{RenSongSun2017Spine} that
+	Taking constants $c_0, c_1>0$ as in \eqref{eq:q(t,x,y)}, 
+	%if $t_0 > 1$, then it has been argued in the proof of 	\cite[Lemma 5.3]{RenSongSun2017Spine} that
+	it has been argued in the proof of
+	\cite[Lemma 5.3]{RenSongSun2017Spine} that, if $t_0>1$,
 $
@@
 \end{split}\]
-	On the other hand, since $\phi^{-1}v_s$ convergence to $0$ uniformly while $s\to \infty$, we can chose an $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
+	On the other hand, since $\phi^{-1}v_s$ convergence to $0$ uniformly while $s\to \infty$, we can chose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
 	Then, if $t-s > t-t_0 \geq s_0$, note that $v_t$ is non-increasing in $t$, we have
@@
 	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
-	= -\log \lim_{\lambda \to \infty}e^{- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ]}
+	= -\log \lim_{\lambda \to \infty}
+	%e^{- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ]}
+	\exp(- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ])
 	\\&\quad = \mathbf m^\xi [\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0}]
@@
 	This can be down by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ while $u \to 0$.
-	In fact, since $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$ and $\gamma(\cdot)$ is bounded, we have $\big(1+ \epsilon_{R(u)}(x)\big)^{\gamma(x)}\stackrel[u\to 0]{x\in E}{\sim} 1$. 
+%	In fact, since $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$ and
+In fact, according to Proposition \ref{prop: convergence in a same speed},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$. Since
+$\gamma(\cdot)$ is bounded, we have $\big(1+ \epsilon_{R(u)}(x)\big)^{\gamma(x)}\stackrel[u\to 0]{x\in E}{\sim} 1$.
 	Therefore, from Lemma \ref{lem: asymptotic equivalent of integration}, we have that
@@
 \label{sec: conditional distribution}
-	Let $\{X; \mathbf P\}$ be a superprocess satisfies Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	Let $\{X; \mathbf P\}$ be a superprocess satisfies
+	$Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	Assumptions \ref{asp: 1}-\ref{asp: 4}.
 	Suppose that $m(x: \gamma(x) = \gamma_0)>0$.
-	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | X_t \not \equiv 0\big)\big\}$ convergence weakly to a non-degenerate distribution for a large class of testing function $f$ and initial configuration $\mu$.
+	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | X_t \not \equiv 0\big)\big\}$
+	%convergence weakly 
+	converges weakly
+	to a non-degenerate distribution for a large class of testing function $f$ and initial configuration $\mu$.
 	Our guess of $(\eta_t)$ is
@@
 
- 	From the Laplace transform point of view, the desired result that $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ weakly convergence to some probability distribution $F_{f,x}$, is equivalent to the following convergence:
+ 	From the Laplace transform point of view, the desired result that $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$
+ %	weakly convergence
+ converge weakly 
+ 	to some probability distribution $F_{f,x}$, is equivalent to the following convergence:
 \[\begin{split}
@@
 \]
-	Therefore, to actually establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$, one only have to verify \eqref{eq: equivalent result}.
+	Therefore, to 
+%	actually 
+	establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$, one only have to verify \eqref{eq: equivalent result}.
 
@@
 \]
-	where $\{Y; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with spine process $\xi$, immigrate measure $\mathbf n_T$ and its conditioned mean measure $\mathbf m^\xi_T$.
+	where $\{Y; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with spine process $\xi$, 
+%	immigrate measure 
+immigration measure
+	$\mathbf n_T$ and 
+%	its conditioned mean measure
+conditional mean measure
+	$\mathbf m^\xi_T$.
 	From this, we have
 \[ \label{eq: dynamic of theta on v_t theta reason 1}
-	\partial_\theta (-\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}])
+%	\partial_\theta
+	\frac{\partial}{\partial_\theta}
+	(-\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}])
 	= \frac{\mathbf P_{\delta_x}[X_T(f)e^{-\theta X_T(f)}]}{\mathbf P_{\delta_x}[e^{-\theta X_T(f)}]}
@@
 	&= -\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}]
-	= \int_0^\theta S_Tf(x) \dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
+	= \int_0^\theta
+%	S_Tf(x) 
+P^\beta_Tf(x)
+	\dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
 	\\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \big[e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds}\big] dr
@@
 
-\subsection{Characterizing the Zolotarev's distribution}
+%\\subsection{Characterizing the Zolotarev's distribution}
+\subsection{Zolotarev's distribution}
 \label{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}
@@
 \begin{proof}
-	We proof this Lemma by a contradiction.
+%	We proof this Lemma by a contradiction.
+We prove this lemma using contradiction method.
 	Assume that $\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty$.
@@
 \label{sec: proof of result 3}
-	Consider the $(\xi, \psi)$-superprocess $\{X;\mathbf P\}$ which satisfies Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	Consider the $(\xi, \psi)$-superprocess $\{X;\mathbf P\}$ which satisfies %Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	Assumptions \ref{asp: 1}-\ref{asp: 4}.
 	Suppose that $m\{ x:\gamma(x)=\gamma_0 \}>0$.
@@
 	Without loss any of generality, we assume that $\langle f, \phi^* \rangle_m = 1$.
-	As have been discussed in Section \ref{sec: conditional distribution}, in order to proof Theorem \ref{thm: main theorem}(3), we only have to show that
+	As have been discussed in Section \ref{sec: conditional distribution}, 
+	% in order to proof Theorem \ref{thm: main theorem}(3), we only have to show that
+	in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
 \[
@@
 	J_G(r) - J'_G(t,r,\xi)
-	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2} \int_0^1 \frac{\gamma_0}{u} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big\langle 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1}, \phi\phi^*\big\rangle_m du
+%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2} 
+	\xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})}
+	\int_0^1 \frac{\gamma_0}{u} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big\langle 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1}, \phi\phi^*\big\rangle_m du
 	=0.
@@
 	J_g(t,r,\xi) - J'_g(t,r,\xi)
-	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)}; L^2} 0.
+%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)}; L^2} 0.
+\xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})} 0.
 \]

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
 %new added
-It is know that for any $f\in bp{\cal B}_E$,
+It is know that for any $f\in bp\mathcal{B}_E$,
 \[\label{mean-N}
@@
 	Let $\{X; \mathbf P\}$ be a superprocess satisfies
-	$Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
+	%Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
 	Assumptions \ref{asp: 1}-\ref{asp: 4}.

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
 
-\subsection{Motivation and literature review}
-
-	The study of the asymptotic behavior of the critical branching particle system has a long history.
+%\subsection{Motivation and literature review}
+\subsection{Background}
+
+The study of the asymptotic behavior of 
+%the critical branching particle system has a long history.
+critical branching particle systems has a long history
 	It is well known that for a critical Galton-Watson process $(Z_n)$, we have
@@
 		n P(Z_n > 0)
-		\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2},
+		\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
 	\]
@@
 	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
-	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2rd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.
-
-	Note that result \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2rd moment is infinite, i.e.
+	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.
+
+%Note that result \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2rd moment is infinite, i.e.
 $\sigma^2 = \infty$.
-	In this case, the scaling limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so more proper scaling is required.
-	This was firstly obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
-	which is then extended by Slack \cite{Slack1968A-branching} for discrit time critical Galton-Watson processes allowing infinite variance:  Consider the critical Galton-Watson process $(Z_n)$ with infinite variance.
-	Assuming that the offspring generating function $f(s)$ takes the form
+Note that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
+%In this case, the scaling limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so more proper scaling is required.
+In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so a more appropriate scaling is needed.
+	This was first obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
+	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson process $(Z_n)$ with infinite variance.
+	Assuming that the offspring generating function $f(s)$ is of the form
 \[\label{eq: offspring generating function with alpha moment}
@@
 \]
-	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ the \emph{Zolotarev's distribution with index $\alpha$}.
+	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
 	Slack \cite{Slack1972Further} considered the converse of this problem:
-	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must take the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
-	For shorter and more unified approaches to these results, we refer our reader to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.
-
-	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson process without 2rd moment condition:
-	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ denote a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
-	Denoted by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
-	%new added
-	and  $\mathbf F_n(\mathbf s), \quad n>1$, its iterates.
-	%end new
-	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ its left and right principle eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ the vector $(1,\dots, 1)$.
+	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must be of  the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
+	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.
+
+	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment condition:
+	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
+	Denote by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
+	and  by $\mathbf F_n(\mathbf s), \quad n>1$ its iterates. 
+	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right principal  eigenvectors respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
 	Suppose that
@@
 \]
-%	Then \cite{GoldsteinHoppe1978Critical} shows that,
-Then \cite{GoldsteinHoppe1978Critical} showed that,
-	if we let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ the vector $(0,\dots, 0)$, then for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
+Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
+It was shown in \cite{GoldsteinHoppe1978Critical} that,
+ for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
 \[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
@@
 \]
-	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
-	Vatutin \cite{Vatutin1977Limit} also considered analogue results for the continuous time mutitype critical Galton-Watson processes.
-
-	Asmussen and Hering \cite{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M) see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$ (see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
-	In the case without the finite second moment, under a condition  paralleling  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), they proved results (see \cite[Theorem 4.2]{AsmussenHering1983Branching}) paralleling to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} for the critical branching Markov processes.
-
-	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
-	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
+	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
+	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time mutitype critical Galton-Watson processes.
+
+	Asmussen and Hering \cite{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$ (see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
+	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite{AsmussenHering1983Branching} for critical branching Markov processes,
+see \cite[Theorem 4.2]{AsmussenHering1983Branching}.
+
+%	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
+%	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
+In this paper, we are interested in a class of measure-valued branching Markov process 
+known as $(\xi, \psi)$-superprocesses.
+$\xi$, the spatial motion of the superprocess, is a a Hunt process on a locally 
+compact, separable, metric space $E$, $\psi$, the branching mechanism of the superprocess,
+is function $\psi$ on $E \times [0,\infty)$ of the form
 \[ \label{eq: branching mechanism}
@@
 \]
-	where $\beta \in b\mathscr B_E$, $\alpha \in bp\mathscr B_E$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ s.t. $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
-	We refer our readers to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
-	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.
-
-	Results paralleling to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
-	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses when  the branching mechanism is $(x,z)\mapsto z^2$ and the spatial motion satisfies some ergodicity conditions.
-	Ren, Song and Zhang \cite{RenSongZhang2015Limit} refined their results for a class of critical superprocesses with general branching mechanism and general spatial motions:
+	where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+	For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
+	In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.
+%	We refer our readers to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
+%	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.
+
+	Results parallel to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
+	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses with branching mechanism of the form $(x,z)\mapsto z^2$ and with the spatial motion satisfying some ergodicity conditions.
+	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to  
+	a class of critical superprocesses with general branching mechanism and general spatial motions:
 	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$.
-	Suppose that its spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and its branching mechanism $\psi$ satisfies the following second moment condition:
+	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$ and the branching mechanism $\psi$ satisfies the following second moment condition:
 \[\label{eq: second moment condition}
@@
 \]
-	Under some other mild assumptions, it was proved by Ren, Song and Zhang \cite{RenSongZhang2015Limit} that
+	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
 \[\label{eq: Kolmogorov type result with 2rd moment}
@@
 	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
-	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to results \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
-
-	As a continuation of those works, it is natural to ask weather results paralleling to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} can be obtained for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
-	%Perhaps a 	simpler
+	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to\eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
+
+	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
 	A simpler
 	version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements.
-	Kyprianou \cite{Kyprianou2008Continuous} considered a CSBP $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$.
+	Kyprianou \cite{Kyprianou2008Continuous} considered CSBP's $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$.
 He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
@@
 \]
-	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} generalized this result, by considering a CSBP with branching mechanism
+	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBP's with branching mechanism
 \[\label{eq: regular varing of branching mechanism of a CSBP}
@@
 	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
-	They showed that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
+It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
 \[\label{eq: conditional limit of CSBP}
@@
 \]
-	Later, \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$
-	%which verifying Grey's condition.
-	which satisfies Grey's condition.
-	In order the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
-
-	In this paper, we establish a result paralleling to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
+	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ 
+	satisfying Grey's condition.
+	In order for the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
+
+%	In this paper, we establish a result paralleling 
+In this paper, we will establish a result parallel
+	to \eqref{eq: conditional limit of CSBP with stable branching} for some 
+   critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ 
+	with spatially dependent stable branching mechanism.
 	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
@@
 \]
-	where $\beta \in b\mathscr B_E$, $\gamma \in bp\mathscr B_E$, $\kappa \in bp\mathscr B_E$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
-	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ convergence to $0$ while $t\to \infty$, and is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
+	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
+	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and is regularly varying with index $\frac{1}{\gamma_0 - 1}$ at $\infty$..
 	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
@@
 \]
-	and for a large class of non-negative testing function $f$,
+	and for a large class of non-negative testing functions $f$,
 \[
@@
 	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
-	A regrously statements of the assumptions and the results are presented in the next subsection.
-	%Perhaps it
-	It
-	is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ is primarily depended only by the lowest index $\gamma_0$.
+	Precise statements of the assumptions and the results are presented in the next subsection.
+It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ depend primarily on the lowest index $\gamma_0$.
 
@@
 
-	We first set some notations.
-	For any measurable space $(E,\mathscr E)$, denote by $r\mathscr E$ the colloction of all measurable real functions on $E$.
-	Define $b\mathscr E :=\{f \in r\mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $p\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $s\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\neq 0\}$.
-	Define $bp\mathscr E := b\mathscr E \cap p\mathscr E$, $bs\mathscr E:= b\mathscr E \cap s\mathscr E$, $sp\mathscr E:= s\mathscr E \cap p\mathscr E$ and $spb\mathscr E : = s\mathscr E \cap p\mathscr E \cap b\mathscr E$.
+	We first fix our notation.
+	For any measurable space $(E,\mathscr E)$, we denote by $\mathscr E$ the collection of all real-valued measurable functions on $E$.
+	Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
+	Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$, $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.	
 	Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
 	Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
-	In this paper, to simplify the notation, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$.
-%	We also write $\langle f,g\rangle_m$ meaning $ \int_E fg dm$  	if we want  to emphasize the inner product structure of Hilbert space $L^2(dm)$.
+	For simplicity, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$.
     We also write $\langle f, g\rangle_m$ for $\int_E fg dm$  
     to emphasize that it is the inner product in the Hilbert space $L^2(dm)$.
-	For any $\phi \in p\mathscr E$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
+	For any $\phi \in \mathscr E^+$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
 	In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
-	If $E$ is a topology space, denote by $\mathscr B_E$ the collection of all  Borel measurable subsets of $E$.
+	If $E$ is a topological space, denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
 
 	We now give the definition of a $(\xi, \psi)$-superprocess:
-	Let the \emph{state space} $E$ be a locally compact separable metric space,
-	the \emph{underlying motion} $\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be a $E$-valued Hunt process with its life time denoted by $\zeta$, and the \emph{branching mechanism} $\psi$
-%	being a function on $ E\times [0,\infty)$ with form of
+	Let t$E$ be a locally compact separable metric space,
+	the spatial motion
+%	$\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ 
+   $\xi:=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ 
+	be a $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ 
 be a function on $E\times[0,\infty)$ given by
 	\eqref{eq: branching mechanism}.
-	We say a $\mathcal M^1_E$-valued Hunt process $\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  testing function $f\in bp\mathscr B_E$, we have
+	We say a $\mathcal M^1_E$-valued Hunt process $\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
 \[
@@
 \]
-	(In this paper, to simplify the notation, for any real function $F$ on $E\times [0,\infty)$ and real function $f$ on $E$, we simply write $F(x,f):= F(x,f(x)).$)
+	(In this paper, for any real-valued function $F$ on $E\times [0,\infty)$ and real-valued function $f$ on $E$, we write $F(x,f):= F(x,f(x))$ for simplicity.)
 
@@
 	= \Pi_x \big[e^{\int_0^{t} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
-	\quad t\geq 0, x\in E, f\in b\mathscr B_E.
+	\quad t\geq 0, x\in E, f\in \mathscr B_b(E).
 \]
 	(Notice that if $\beta \equiv 0$,
-	%then $P_t:= P^\beta_t$ is the \emph{transition semigroup} of process $\{\xi; \Pi\}$.)
-	 $P_t:= P^0_t$ is the \emph{transition semigroup} of process $\xi:=\{(\xi)_{t\ge 0}; (\Pi)_{x\in E}\}$.)
+%	 $P_t:= P^0_t$ is the \emph{transition semigroup} of process $\xi:=\{(\xi)_{t\ge 0}; (\Pi)_{x\in E}\}$.)
+then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
 	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
@@
 	= \mu(P^\beta_t f),
-	\quad \mu \in \mathcal M_f, t \geq 0,f \in b\mathscr B_E.
+	\quad \mu \in \mathcal M_f, t \geq 0,f \in \mathscr B_b(E).
 	\]
 	This mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
-	As it already be discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} or \eqref{eq: Ygalom type result without 2rd moment}, we have to first establish the asymptotic behavior of the mean semigroup.
+	As discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} or \eqref{eq: Ygalom type result without 2rd moment}, we have to establish the asymptotic behavior of the mean semigroup first.
 	This can be done under the following assumptions on the underlying motion $\{\xi; \Pi\}$:
@@
 	= \int_E p_t(x,y) f(y) m(dy),
-	&\quad t>0, x \in E,f \in b\mathscr B_E;
+	&\quad t>0, x \in E,f \in \mathscr B_b(E);
 	\\\int_E p_t(y,x)m(dy)
@@
 \end{split}\]
-	and, $x \mapsto \int_E p_t(x,y)^2 m(dy)$
-%	,
+	and the functions $x \mapsto \int_E p_t(x,y)^2 m(dy)$
 and 
-	$x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous on $E$.
+	$x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous.
 \end{asp}
@@
 \]
-	and that for any $t>0, x\in E$ and $f \in b\mathscr B_E$,
+	and that for any $t>0, x\in E$ and $f \in \mathscr B_b(E)$,
 \[
@@
 \]
-	%We will call $(p^\beta_t)$ the
 	 $(p^\beta_t)$ is called the
-	\emph{transition density of semigroup $(P^\beta_t)$}.
-	Define a family of transition kernels $(P^{\beta *}_t)_{t \geq 0}$ on $E$ by
+	\emph{density of semigroup $(P^\beta_t)$}.
+	Define a family of kernels $(P^{\beta *}_t)_{t \geq 0}$ on $E$ by
 \[
@@
 	:= \int_E p^\beta_t (y,x) f(y) m(dy),
-	\quad t>0, x\in E, f\in b\mathscr B_E.
+	\quad t>0, x\in E, f\in \mathscr B_b(E).
 \]
@@
 	Moreover, for each $t\geq 0,x\in E$, we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
-	We refer to $\phi$ (repct.
-$\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of the simegroup $(P^\beta_t)_{t\geq 0}$ (respct.
-$(P^{\beta *}_t)_{t\geq 0}$).
+	We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of 
+%the simegroup $(P^\beta_t)_{t\geq 0}$ (respct. $(P^{\beta *}_t)_{t\geq 0}$).
+$L$ (resp. $L^*$).
 
@@
 \begin{asp}{2} \label{asp: 2}
-	The superprocess $(X_t)$ is critical, i.e. $\lambda = 0$.
+	The superprocess $(X_t)$ is critical, i.e., $\lambda = 0$.
 \end{asp}
 
-	Let $\varphi$ (respect.
-$\varphi^*$) be the principal eigenfunction of (respct.
+	Let $\varphi$ (resp.
+$\varphi^*$) be the principal eigenfunction of (resp.
 the dual of) the transition semigroup $(P_t)$ of the underlying process $\{\xi;\Pi\}$.
@@
 
-	Under Assumption \ref{asp: 3},	It is proved in \cite{RenSongZhang2017Central,RenSongZhang2015Limit} that the principal eigenfunction $\phi$ of Feyman-Kac semigroup $(P^\beta_t)$ is also bounded.
-	Moreover, $(P^\beta_t)$ is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ s.t.
-for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
-	In fact, it is proved by \cite{KimSong2008Intrinsic} that for each $t>0$, $(p^\beta_t(x,y))_{x,y\in E}$ is comparable to $(\phi(x)\phi^*(y))_{x,y\in E}$ in the sense that there is a constant $c_t > 1$ s.t.
+	Under Assumption \ref{asp: 3},	it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of Feyman-Kac semigroup $(P^\beta_t)$ is also bounded.
+	Moreover, $(P^\beta_t)$ is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
+	In fact, it is proved in \cite{KimSong2008Intrinsic} that for each $t>0$, $(p^\beta_t(x,y))_{x,y\in E}$ is comparable to $(\phi(x)\phi^*(y))_{x,y\in E}$ in the sense that there is a constant $c_t > 1$ such that
 \[\label{eq: p-t-beta is comparable to phi phi-star}
@@
 \]
-	It is also shown in \cite{KimSong2008Intrinsic} that $(e^{-\lambda t}p^\beta_t(x,y))_{x,y\in E}$ is asymptotic equivalent to $\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ uniformly in $x$ and $y$, and exponentially fast while $t\to \infty$, in the sense that, there are constants $c_0,c_1 > 0$ s.t.
+It is also shown in \cite{KimSong2008Intrinsic} that $(e^{-\lambda t}p^\beta_t(x,y))_{x,y\in E}$ 
+%	is asymptotic equivalent to 
+	is,  uniformly in $x$ and $y$, asymptotically equivalent to 
+%	$\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ uniformly in $x$ and $y$, and exponentially fast while $t\to \infty$, 
+$\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ as $t\to \infty$
+in the sense that, there are constants $c_0, c_1 > 0$ such that
 \[\label{eq:q(t,x,y)}
@@
 \]
-	We refer our reader to \cite{RenSongZhang2015Limit} for a list of examples of underlying processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
-
-	In this paper, we will only consider the superprocesses with the following spatially dependent stable branching:
+	We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of underlying processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
+
+	In this paper, we will only consider superprocesses with the following spatially dependent stable branching mechanism:
 \begin{asp}{4} \label{asp: 4}
-	The branching mechanism $\psi$ takes the following form:
+	The branching mechanism $\psi$ is of  the following form:
 \[\begin{split}
@@
 \end{split}\]
-	where $\beta \in b\mathscr B_E, \gamma \in bp\mathscr B_E$ and $\kappa \in spb\mathscr B_E$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
+	where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
 \end{asp}
-	Note that here, we used the definition of the Gamma function on the negative real line:
+	Here we used the definition of the Gamma function on the negative half line:
 \[\label{eq: definition of Gamma function}
@@
 \label{thm: main theorem}
-	Suppose that $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M_E^1}\}$ is a $(\xi, \psi)$-superprocess satisfying Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}. Then,
+	Suppose that $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M_E^1}\}$ is a $(\xi, \psi)$-superprocess satisfying 
+%Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}. Then,
+Assumptions \ref{asp: 1}--\ref{asp: 4}. Then,
 \begin{itemize}
 	\item[(1)] $\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$.
-	\item[(2)] For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$ convergences to $0$ while $t\to \infty$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$.
+	\item[(2)] For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$ converges to $0$ as $t\to \infty$, and is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
@@
 	\item[(3)] Suppose $m( x:\gamma(x)=\gamma_0 )>0$.
-	Let $f \in p\mathscr B$ be a testing function such that $\langle f, \phi^* \rangle_m > 0$  and $\| \phi^{-1}f \|_\infty < \infty$, then
+	Let $f \in \mathscr B^+(E)$ be  such that $\langle f, \phi^* \rangle_m > 0$  and $\| \phi^{-1}f \|_\infty < \infty$, then
 \[
@@
 
-	In this paper, to establish the Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition method of superprocess $\{X; \mathbf P\}$.
-	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the summation of an original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
+	In this paper, to establish the Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition of  $\{X; \mathbf P\}$.
+	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
 	The family of functions used for the size-biased transform is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$, which is a martingale.
-	Therefore, this size-biased transformation can be viewed as a martingale change of measure.
+	Therefore, this size-biased transform can be viewed as a martingale change of measure.
 	Under the Assumption \ref{asp: 1} and \ref{asp: 3}, 
@@
 	the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process.
-	To study the asymptotic behavior of superprocesses, one can take advantage of this ergodicity.
-
-	This idea has already been used by Powell \cite{Powell2015An-invariance} while establishing results paralleling to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
+	We take advantage of this ergodicity to study the asymptotic behavior of the superprocess.
+
+	This idea has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
 	Let $(Y_t)$ be a branching diffusion processes in a bounded domain with finite second moment.
 	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation
-%which is known to be
-	satisfied by $(t,x) \mapsto P(Y_t \not\equiv 0)$, the survival probability for branching diffusion process, is tricky.
-	Instead, using a spine decomposition approach, \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principle eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capture the uniform speed.
+	satisfied by the survival probability $(t,x) \mapsto P(Y_t \not\equiv 0)$ is tricky.
+	Instead, by using a spine decomposition approach, Powell \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principal eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capturing the uniform speed.
 	Then, the problem is reduced to the study of a single ODE satisfied by the speed function $a(t)$.
-	Later, inspired by \cite{Powell2015An-invariance}, in \cite{RenSongSun2017Spine}, we gave a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of critical superprocesses with finite second moment.
-	In this paper, we are able to generalize those arguments for a class of critical superprocesses without the finite second moment, and establish Theorem \ref{thm: main theorem}(2).
-
-	For the conditional weak convergence result, i.e.
-Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform of Zolotarev's distribution can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
-	Using the spine method, we show that the Laplace transform of the one-dimensional conditioned distributions for the superprocess, after a proper rescaling, can also be characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
-	Then, the desired convergence of the distributions can be established by a comparison between equations.	
+	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of critical superprocesses with finite second moment.
+	In this paper, we will  generalize these arguments to a class of critical superprocesses without finite second moment, and establish Theorem \ref{thm: main theorem}(2).
+	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform of Zolotarev's distribution can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
+	Using the spine method, we show that the Laplace transform of the one-dimensional conditioned distributions of the superprocess, after a proper rescaling, can also be characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
+	Then, the desired convergence of the distributions can be established by a comparison between the equations.	
 	Again, the ergodicity of the spine process plays a central role in the comparison.
 
-	A similar idea of establishing conditional weak convergence to the exponential distribution, though a comparison of distributional equations method, have already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
-	To be precise, we characterized the exponential distribution using an $x^2$-transform distributional equation; and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
-	However, the $x^2$-transform of a random variable requires the existence of its finite variance.
-	In this paper, since we don't have the finite variance, we can not use the method of $x^2$-transform.
+	A similar idea of establishing conditional weak convergence to the exponential distribution through a comparison of the equations satisfed by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
+	We characterized the exponential distribution using an $x^2$-transform distribution equation; and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
+	However, the $x^2$-transform of a random variable requires the existence of the second moment.
+	Since we are not assuming the second moment condition, we can not use the method of $x^2$-transform.
 	Instead, a non-linear delay equation is used.
 
-	In \cite{Powell2015An-invariance}, for the critical branching diffusion in a bounded domain with finite variance, and in \cite{RenSongSun2017Spine} and
-	\cite{RenSongZhang2015Limit}, for the critical superprocess with finite variance, when the authors were establishing the conditional weak convergence, they did not prove the results for all general testing functions $f$ at the same time.
-	Instead, the authors first established the results for a specific testing function $\phi$, the principle eigenfunction of the mean matrix of the corresponding processes, and then passed the result to a general testing function $f$.
-	While passing to the general result, \cite{Powell2015An-invariance}, \cite{RenSongZhang2015Limit} and \cite{RenSongSun2017Spine} all used a second moment argument to control the differences.
-
-	However, in this paper, since we simply don't have the second moment, this type of argument fails to hold.
-	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for all general testing function $f$ at the same time.
-	This generalized spine decomposition theorem considered the $X_T(g)$-transform of the superprocess $(X_t)_{0\leq t\leq T}$ for a large class of general function $g$.
-	The transformed process behaves similarly as in the classical case, despite that, the spine processes $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$
-	%is not the same.
+	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in \cite{RenSongSun2017Spine} and
+	\cite{RenSongZhang2015Limit} (for critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
+First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used
+to extend the result to a general functions $f$.
+
+	Since we are not assuming the second moment condition, this type of argument does not work
+	in the present case.
+	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for all general functions $f$ at the same time.
+	This generalized spine decomposition theorem considered the $X_T(g)$-transform of the superprocess $(X_t)_{0\leq t\leq T}$ for a large class of general functions $g$.
+	The transformed process behaves similarly as in the classical case, despite the fact that the spine processes $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$ 
 	are not consistent for all $T>0$.
@@
 \label{sec: Asymptotic equivalence}
-	In this subsection, we give a lemma about the asymptotic equivalence.	
+	In this subsection, we give a lemma on asymptotic equivalence.	
 	Let $t_0 \in [-\infty,\infty]$.
-	For any $f_0, f_1\in s\mathscr B_{\mathbb R}$, we say $f_0$ and $f_1$ are \emph{asymptotic equivalent at $t_0$}, if $\big|\frac{f_0(t)}{f_1(t)} - 1\big| \xrightarrow[t\to t_0]{} 0$;
+	For any $f_0, f_1\in \mathscr B^{++}({\mathbb R})$, we say $f_0$ and $f_1$ are \emph{asymptotically equivalent at $t_0$}, if $\big|\frac{f_0(t)}{f_1(t)} - 1\big| \xrightarrow[t\to t_0]{} 0$;
 	and in this case, we write $f_0(t) \stackrel[t\to t_0]{}{\sim} f_1(t)$.
 	Let $E$ be a measurable space.
-	For any $g_0, g_1\in s\mathscr B_{\mathbb R\times E}$, we say $g_0$ and $g_1$ are \emph{uniformly asymptotic equivalent at $t_0$}, if $\sup_{x\in E}\big|\frac{g_0(t,x)}{g_1(t,x)} - 1\big| \xrightarrow[t\to t_0]{} 0$; and in this case, we write $g_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}g_1(t,x)$.
+	For any $g_0, g_1\in \mathscr B^{++}({\mathbb R\times E})$, we say $g_0$ and $g_1$ are \emph{uniformly asymptotically equivalent at $t_0$}, if $\sup_{x\in E}\big|\frac{g_0(t,x)}{g_1(t,x)} - 1\big| \xrightarrow[t\to t_0]{} 0$; and in this case, we write $g_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}g_1(t,x)$.
 
@@
 \label{lem: asymptotic equivalent of integration}
-	Suppose that $f_0,f_1\in spb\mathscr B_{\mathbb R \times E}$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
-	Let $m \in \mathcal M^1_E$. Then we have
+	Suppose that $f_0,f_1\in \mathscr B^{++}_b({\mathbb R \times E})$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
+	If $m \in \mathcal M^1_E$, then 
 \[
@@
 \begin{proof}
-	We see that
+Since 
 \[\begin{split}
@@
 \end{split}\]
-	as required.
+the assertion is valid.
 \end{proof}
 
-\subsection{Regularly variation}
+\subsection{Regular variation}
 \label{sec: Regularly variation}
-	In this subsection, we give some preliminary results on the regularly variation.
-	We refer the reader to \cite{BinghamGoldieTeugels1989Regular} as a classical reference for regularly varying functions.
-	For $f\in sp\mathscr B_{(0,\infty)}$, we say $f$ is regularly varying at $\infty$ (respt.
-at $0$) with index $\gamma \in (-\infty,\infty)$ and denote that $f\in \mathcal R^\infty_\gamma$ (respt.
-$f\in \mathcal R^0_\gamma$) if for any $\lambda \in (0,\infty)$,
+	In this subsection, we give some preliminary results on regular variation.
+	We refer the reader to \cite{BinghamGoldieTeugels1989Regular} for more results on  regular variation.
+	For $f\in \mathscr B^{++}((0,\infty))$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\gamma \in (-\infty,\infty)$ if for any $\lambda \in (0,\infty)$,
 \[
@@
 	= \lambda^\gamma
-	\quad (\text{respt. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
+	\quad (\text{resp. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
 	= \lambda^\gamma).
 \]
-	%Further, if $\gamma_0 = 0$,
+In this case we write  $f\in \mathcal R^\infty_\gamma$ (resp. $f\in \mathcal R^0_\gamma$).
 	Further, if $\gamma = 0$,
@@
 \label{lem: exchange slowly varying function and integration}
-	Let $L\in \mathcal R^\infty_0$.
+	Suppose that $L\in \mathcal R^\infty_0$.
 \begin{itemize}
 \item
-	Let $t_0\in (0,\infty)$ be large enough such that $L$ is locally bounded on $[t_0,\infty)$. If $\alpha>0 $, then
+	Let $t_0\in (0,\infty)$ be large enough so that $L$ is locally bounded on $[t_0,\infty)$. If $\alpha>0 $, then
 \[
@@
 \label{cro: power law and ingetration}
-	Let $l\in \mathcal R^0_0$.
+	Suppose that $l\in \mathcal R^0_0$.
 \begin{itemize}
 \item
-	Let $s_0\in (0,\infty)$ be small enough such that $l$ is locally bounded on $(0,s_0]$.
+	Let $s_0\in (0,\infty)$ be small enough so that $l$ is locally bounded on $(0,s_0]$.
 	If $\alpha < 0$, then
@@
 \begin{proof}
-	Since $l \in \mathcal R^0_0$, we know that, if one define $L(t):=l(t^{-1})$ for each $t\in (0,\infty)$, then $ L \in \mathcal R^\infty_0$.
+	Since $l \in \mathcal R^0_0$, we know that, if one defines $L(t):=l(t^{-1})$ for each $t\in (0,\infty)$, then $ L \in \mathcal R^\infty_0$.
 	Therefore, there exists $t_0\in (0,\infty)$ such that $L$ is locally bounded on $[t_0,\infty)$.
-	Taking $s_0:= t_0^{-1}$, we then immediately know that $l$ is locally bounded on $(0,s_0]$.
+	Taking $s_0:= t_0^{-1}$, we then immediately get that $l$ is locally bounded on $(0,s_0]$.
 	If $\alpha<0 $, then according to Lemma \ref{lem: exchange slowly varying function and integration}, we have
@@
 
-	The following lemma considered the inverse of an
-%	invertible
-   %R: same change below without mark
-	reversible
-	regularly varying function.
+	The following lemma concerns the inverse of 
+({\bf I think that there is a little problem with the following lemma. When $f$ is invertible
+but not monotone, its inverse is not the same as the generalized inverse	in 
+\cite{BinghamGoldieTeugels1989Regular}. If we do not really use the general version, we can just give the monotone version.})
+an  reversible regularly varying function.
 	In this paper, if a function $f$ is reversible, we write $f^{(-1)}$ for its inverse; if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
@@
 	\iff f^{(-1)}
-	\in \mathcal R^\infty_{1/\alpha},
+	\in \mathcal R^\infty_{1/\alpha}
 \]
@@
 	\iff f^{(-1)}(t)
-	\stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha},
+	\stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}
 \]
@@
 	To see 	\eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} is true, we write $h(t) : = f(t^{-1})^{-1}$.
-	It's easy to verify that $h$ is also invertible with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1} $.
+	It is  easy to verify that $h$ is also invertible with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1} $.
 	Therefore,
@@
 	If $\alpha < 0$, to see	\eqref{eq: inverse of a regularly varying function with alpha < 0} is true, we write $g(t) : = f(t^{-1})$.
-	It's easy to verify that $g$ is also invertible with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
+	It is easy to verify that $g$ is also invertible with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
 	Therefore,
@@
 	This proved one side of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}.
-	The other side of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}, and \eqref{eq: inverse and power equivalent at 0 with alpha > 0}, as well as \eqref{eq: inverse and power equivalent with alpha < 0}, can be proved similarly.
+	The other direction of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}, and \eqref{eq: inverse and power equivalent at 0 with alpha > 0}, as well as \eqref{eq: inverse and power equivalent with alpha < 0}, can be proved similarly.
 \end{proof}
@@
 	Let $E$ be a measurable space with a non-degenerate measure $m \in \mathcal M^1_E$.
-	Let $ \gamma \in b\mathscr B_E$ with
+	Let $ \gamma \in \mathscr B_b(E)$ with
 \[
@@
 	Then $\big(\int_E t^{\gamma(x)} m(dx)\big)_{t\in (0,\infty)} \in \mathcal R^0_{\gamma_0}$.
-	Further, if $m\{x:\gamma(x) = \gamma_0\}>0$ then
+	Further, if $m\{x:\gamma(x) = \gamma_0\}>0$, then
 \[
@@
 \end{split}\]
-	where the last convergence is due to monotone convergence theorem.
+	where the last convergence is due to the monotone convergence theorem.
 	Therefore
@@
 \]
-	To sum up we have
+	Summarizing the above,  we get
 \[
@@
 
-	If further we have $m\{x:\gamma(x) = \gamma_0\}>0$, then by monotone convergence theorem  it is easy to see that
+	If further we have $m\{x:\gamma(x) = \gamma_0\}>0$, then by the monotone convergence theorem  it is easy to see that
 \[
@@
 \label{sec: Superprocesses}
-	In this subsection, we will recall some known results about the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
-\subsubsection{FKPP equations}
+	In this subsection, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
+\subsubsection%{FKPP equations}
 	It is known, see \cite[Theorem 2.23]{Li2011Measure-valued} for example, that \eqref{eq:FKPP_in_definition} can be written as
@@
 	= P^\beta_t f(x),
-	\quad f \in bp\mathscr B_E, t \geq 0,x \in E,
+	\quad f \in \mathscr B^+_b(E), t \geq 0,x \in E,
 \]
@@
 \]
-%	Suppose that Assumption \ref{asp: 1} and \ref{asp: 2} is true.
-    Suppose that Assumptions \ref{asp: 1} and \ref{asp: 2} hold.
-%	Integrating with measure $\phi^*dm$, we can derive from \eqref{eq:mean-fkpp} that
+    Suppose that Assumptions \ref{asp: 1}--\ref{asp: 2} hold. 
 Integrating both sides of\eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we arrive that
@@
 	= \langle V_sf,\phi^*\rangle_m,
-%	\quad s,t\geq 0, f\in bp\mathscr B_E.
-	\quad t\geq s\geq 0, f\in bp\mathscr B_E.
+	\quad t\geq s\geq 0, f\in \mathscr B^+_b(E).
 	\]
@@
 	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued cadlag paths on $[0,\infty)$.
-	We refer to $\mathbb W$ the \emph{canonical space of $X$}.
-	In fact, $X$ can be viewed as a $\mathbb W$-valued random element.
-	Denoted by $(W_t)_{t\geq 0}$ the \emph{coordinate process of $\mathbb W$}.
+	We refer to $\mathbb W$ as the \emph{canonical space of $X$}.
+	In fact, $X$ can be viewed as a $\mathbb W$-valued random variable.
+	We denote the \emph{coordinate process of $\mathbb W$} by $(W_t)_{t\geq 0}$.
 
 	We say that $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$ for all $x\in E$ and $t> 0$.
-	Suppose that $X$ is non-persistent, then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ s.t.
+	Suppose that $X$ is non-persistent, then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
 \begin{itemize}
@@
 	\item
-	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Possion random %measure in some
+	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Possion random 
 	measure defined on some
@@
 \end{itemize}
-	We refer to $(\mathbb N_x)_{x\in E}$ the \emph{Kuznestov measures} of $X$.
+	We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznestov measures} of $X$.
 	For the existence and further properties of such measures, we refer our readers to \cite{Li2011Measure-valued}.
-	It's worth mention that in the classical literature, the Kuznestov measures are defined in the following space of excursion paths:
+	We mention that, in the literature, the Kuznestov measures are usually defined in the following space of excursion paths:
 	\[\begin{split}
@@
 
-	From the Campbell's formula, see  the proof of \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
+	From  Campbell's formula, see  the proof of \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
 \[ \label{eq: equation for N measure}
@@
 	v_t(x)
-%	:= \lim_{t\to \infty} V_t(\mathbf 1_E)(x)
 	:= \lim_{\lambda\to \infty} V_t(\lambda\mathbf 1_E)(x)
 	= -\log \mathbf P_{\delta_x} [X_t \equiv 0]
-%	= \mathbb N_x[X_t\not \equiv 0],
 	= \mathbb N_x[W_t\not \equiv 0],
@@
 \]
-	For each $\mu \in \mathcal M_E^1$ and $t > 0$, by \eqref{eq: equation for N measure}, \eqref{eq: definition of v_t(x)} and monotone convergence theorem, we have
+	For each $\mu \in \mathcal M_E^1$ and $t > 0$, by \eqref{eq: equation for N measure}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem, we have
 \[ \label{eq: equation for mu v-t}\begin{split}
-%	\mathbb N_\mu[X_t\not \equiv 0]
 \mathbb N_\mu[W_t\not \equiv 0]
@@
 
-%new added
-It is know that for any $f\in bp\mathcal{B}_E$,
+%It is know that for any $f\in bp{\cal B}_E$,
+It is know that for any $f\in bp{\mathscr B}$,
 \[\label{mean-N}
@@
 The we see that $\{(X_t(\phi))_{t\geq 0};\mathbf P_{\mu}\}$ is nonnegative martingale,  and $\{(W_t(\phi))_{t\geq 0};\mathbb N_{\mu}\}$ is also a nonnegative martingale.
-%end new
 
@@
 \label{sec: Spine decompositions}
-	Let $(\Omega, \mathscr F)$ be a measurable space with $\sigma$-finite measure $\mu$, which is not necessarily a probability measure or a finite measure.
-	For any $F\in r\mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and
-	%$\mu [f] \in (0,\infty)$.
+	Let $(\Omega, \mathscr F)$ be a measurable space with a $\sigma$-finite measure $\mu$.
+	For any $F\in \mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and 
 	$\mu [F] \in (0,\infty)$.
-	And if this happens, define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ s.t.
-%  $d\mu^F= \frac{F}{\mu[F]}d \mu.$
+	In this case, we define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ such that
 	$$d\mu^F= \frac{F}{\mu[F]}d \mu.$$
@@
 	Let $\mu \in \mathcal M^1_E$ and $T>0$.
-	Suppose that $g\in p\mathscr B_E$ satisfies that $\mu(P^\beta_Tg) \in (0,\infty)$.
-	Denote by $\mathbb N^{W_T(g)}_\mu$ and $\mathbf P_\mu^{X_T(g)}$, the $W_T(g)$-transform of $\mathbb N_\mu$ and the $X_T(g)$-transform of $\mathbf P_\mu$, respectively.
-	The so-called spine decomposition theorem characterize the law of $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ in two steps.
-	The first step of the theorem says that $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the summation of two independent measure valued processes:
+	Suppose that $g\in \mathscr B^+(E)$ satisfies that $\mu(P^\beta_Tg) \in (0,\infty)$.
+	We denote  the $W_T(g)$-transform of $\mathbb N_\mu$ and the $X_T(g)$-transform of $\mathbf P_\mu$ 
+	by $\mathbb N^{W_T(g)}_\mu$ and $\mathbf P_\mu^{X_T(g)}$ respectively.
+	The  spine decomposition theorem characterizes the law of $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ in two steps.
+	The first step of the theorem says that $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the sum of two independent measure-valued processes:
 
@@
 \end{thm}
-	The second step of the theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has the so-called spine representation:
+	The second step of the theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
 	We say $\{(Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is \emph{the spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
@@
 \item
-	\emph{The spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) e^{-\int_0^T \beta(\xi_s)ds}$-transform of measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
+	\emph{The spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) e^{-\int_0^T \beta(\xi_s)ds}$-transform of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
 \item
-	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with \emph{its conditioned mean measure} defined by
+	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$
+	%with \emph{its conditioned mean measure} defined by
+	with \emph{mean measure}
 \[
@@
 
-%	Note that if we have an a.s. event $\{B;P\}$, i.e. $P(B) = 1$, then under any possible size-biased transform of probability $P$, $B$ is still an a.s. event.
-%	From this, we have that
 Note that
 		$\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
-%	Note that $\mathbb N_\mu$ is not typically a probability measure.
 Also note that  $\mathbb N_\mu$ is not a probability measure.
 	But after the transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
-%	Since $\mathbb N_x(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.
 	Since $\mathbb N_{\mu}(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.
@@
 \label{rem: initial configuration of transformed process}
-	Note that $\Pi_{\mu}$ is not typically a probability measure. ({\bf Remark: why  $\Pi_{\mu}$ is not probability measure？})
-	But after the transformation, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
-	We can verify that
-%moved from below with modification
-Note that
+	Note that $\Pi_{\mu}$ is not typically a probability measure. 
+	%({\bf Remark: why  $\Pi_{\mu}$ is not probability measure?})
+	%RS This because $\mu$ may not be a probability measure.
+	But after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
+We claim that
 \[
@@
 	= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } f(\xi_0) ]
-%	= \mu(S_T g)^{-1}
 	= \mu(P^\beta_T g)^{-1} 
@@
 which says that
-%end move
 \[
@@
 	= \mu(P^\beta_T g)^{-1}
-%S_T g(x)\mu(dx),
     P^\beta_T g(x)\mu(dx),
@@
 \]
-%The following is moved forward	
-%	In fact,
-%\[
-%	\Pi_{\mu}^{(T,g)} [ f(\xi_0) ]
-%	= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } %f(\xi_0) ]
-%	= \mu(S_T g)^{-1}
-%	\int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx).
-%\]
 \end{rem}
 
-	Now, suppose that $\{\xi; \Pi\}$ satisfies the Assumption \ref{asp: 1}.
+	Now, suppose that $\{\xi; \Pi\}$ satisfies Assumption \ref{asp: 1}.
 	Denote by $\phi$ the principal eigenfunction of the mean semigroup of $X$.
 	The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, considered the case when $g = \phi$ only.
-	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov extension theorem.
-	In another word, process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$, on the finite interval $[0,T]$.
-	In fact, one can also verify that this consistence property is satisfied by all those families of probabilities: $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)$.
-	Therefore, the actual statement of the classical spine decomposition theorem is a little different from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}, and doesn't restrict the corresponding processes on the finite interval $[0,T]$.
-	Because of its theoretical importance, we state the classical spine decomposition theorem explicitly:
+	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem,
+that is,  the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$, on the finite interval $[0,T]$.
+	In fact, one can also check that this consistence property is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)$.
+	Therefore, the actual statement of the classical spine decomposition theorem is a little different from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}, and there is no need to restrict the corresponding processes on the finite interval $[0,T]$.
+	Because of its theoretical importance, we state the classical spine decomposition theorem explicitly here:
 
@@
 \]
-	Here, probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of process $(X_t)_{t\geq 0}$ is defined by
+	Here, the probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of the process $(X_t)_{t\geq 0}$ is defined by
 \[
@@
 \]
-	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of process $(W_t)_{t\geq 0}$ is defined by
+	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of the process $(W_t)_{t\geq 0}$ is defined by
 \[
@@
 \item
-	\emph{The spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of process $(\xi_t)_{t\geq 0}$ is defined by
+	\emph{The spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is defined by
 \[
@@
 \item
-	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with \emph{its conditioned mean measure} defined by
+	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with
+%	\emph{its conditioned mean measure} defined by
+\emph{mean measure}
 \[\label{eq:meanMeasImmigr}
@@
 	For the sake of generality, the spine decomposition theorems above are all stated with respect to a general initial configuration $\mu$.
-	If $\mu = \delta_x$ for some $x\in E$, then from Remark \ref{rem: initial configuration of transformed process}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$.
+	If $\mu = \delta_x$ for some $x\in E$, then by  Remark \ref{rem: initial configuration of transformed process}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$.
 	Similarly, we write $\Pi_x^{(\phi)}$ for $\Pi_{\delta_x}^{(\phi)}$.
@@
 \label{sec: Ergodicity}
-	In this subsection, we discuss the ergodicity property of the spine processes $\{\xi; \Pi^{(\phi)}_x\}$ under Assumptions \ref{asp: 1}, \ref{asp: 2} and \ref{asp: 3}.
-	One can verify that $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
+	In this subsection, we discuss the ergodicity of the spine processes $\{\xi; \Pi^{(\phi)}_x\}$ under Assumptions \ref{asp: 1}-- \ref{asp: 3}.
+	One can check that $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
 \[
@@
 \]
-	If we take constants $c_0>0$ and $c_1>0$ as in \eqref{eq:q(t,x,y)}, then we have
+Let   $c_0>0$ and $c_1>0$ be the constants  in \eqref{eq:q(t,x,y)}, then we have
 \[\label{eq: asymptotic for q_t(x,y)}
@@
 \]
-	This characterize the ergodicity of process $\{\xi; \Pi^{(\phi)}_x\}$.
-	One can easily verify from \eqref{eq: asymptotic for q_t(x,y)} that $(\phi\phi^*)(x)m(dx)$ is the unique invariant probability measure of $\{\xi; \Pi^{(\phi)}_x\}$.
+	This implies that the process $\{\xi; \Pi^{(\phi)}_x\}$ is ergodic.
+	One can easily get from \eqref{eq: asymptotic for q_t(x,y)} that $(\phi\phi^*)(x)m(dx)$ is the unique invariant probability measure of $\{\xi; \Pi^{(\phi)}_x\}$.
 	The following two lemmas are also simple consequences of \eqref{eq: asymptotic for q_t(x,y)}.
@@
 \begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
-	If $F$ is bounded and Borel measurable on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$.
-	Then we have
+	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, 
+	then we have
 \[
 	\int_0^1 F(\xi_{(1-u)t},u,t) du
-%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)} ; L^2}
 \xrightarrow[t\to \infty]{ L^2(\Pi_x^{(\phi)})} 
@@
 \begin{lem}\label{lem: Fatou-ergodic lemma for the uderlying process}
-	Let $F$ be a non-negative bounded Borel measurable on $E\times [0,1]\times [0,\infty)$.
+	Let $F$ be a non-negative bounded Borel function on $E\times [0,1]\times [0,\infty)$.
 	Define $F(y,u):= \limsup_{t\to \infty} F(y,u,t)$ for each $y\in E$ and $u \in [0,1]$.
@@
 	For each $(y,u,t)\in E\times [0,1]\times [0,\infty)$, define $\bar F(y,u,t) := \sup_{s:s\geq t} F(y,u,s)$.
-	Then $\bar F$ is a bounded Borel measurable function on $E\times [0,1]\times [0,\infty)$ with
+	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$ with
 \[
@@
 \]
-	Therefore, according to Lemma \ref{lem: ergodicity of the underlying process}, we have that
+	Therefore it follows from Lemma \ref{lem: ergodicity of the underlying process} that
 \[
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
-%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2}
 	\xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})}
@@
 \]
-%new added
-wwhich implies convergence in probability.
-%end new
+which implies convergence in probability.
 	The bounded convergence theorem then gives that, for each $p \geq 1$,
@@
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
-%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^p}
 	\xrightarrow[t\to \infty]{L^p(\Pi_x^{(\phi)})}
@@
 \]
-	Finally, note that that $0\leq F \leq \bar F$, we have
+	Finally, noting that that $0\leq F \leq \bar F$, we get
 \[\begin{split}
@@
 \label{sec: proof of result 1}
-	Let $\{X; \mathbf P\}$ be a superprocess satisfies
-	%Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
-	Assumptions \ref{asp: 1}-\ref{asp: 4}.
-%	In this section, we will proof the following stronger result:
+	Let $\{X; \mathbf P\}$ be a superprocess satisfying
+	Assumptions \ref{asp: 1}--\ref{asp: 4}.
     In this section, we will prove the following stronger result:
@@
 	For each $x\in E$, let $\tilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\tilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$.
-	Then, we know that $\tilde \kappa = \kappa$ and $\tilde \gamma = \gamma$ almost everywhere with respect to measure $m$.
-	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z) $ almost everywhere with respect to measure $m$.
+	Then, we know that $\tilde \kappa = \kappa$ and $\tilde \gamma = \gamma$ almost everywhere with respect to the measure $m$.
+	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z) $ almost everywhere with respect to the measure $m$.
 	Therefore, if we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
@@
 	So, we can view $\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
-	Define another branching mechanism for a continuous state branching process:
+	Define 
 \[
@@
 	As a consequence,
-	%by \cite[Lemma 2.3]{RenSongZhang2015Limit},
 	we have the desired result.
@@
 	Let $\{X; \mathbf P\}$ be a superprocess satisfies 
-	%Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
-	Assumptions \ref{asp: 1}-\ref{asp: 4}.
+	Assumptions \ref{asp: 1}--\ref{asp: 4}.
 	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent.
-	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have $\mathbf P_{\delta_x}(X_t \equiv 0)<1$, for each $x\in E$ and $t>0$.
-	Therefore, from \eqref{eq: definition of v_t(x)}, we have that $v_t \in spb\mathscr B_E$.
+	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have $\mathbf P_{\delta_x}(X_t \equiv 0)<1$ for each $x\in E$ and $t>0$.
+	Therefore, from \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$.
 	According to \eqref{eq:mean-fkpp}, by monotonicity, we see that $(v_t)$ satisfies the equation
@@
 	Then, according to \eqref{eq:langleVtfphiranglem_equation}
-%	, by monotonicity,
 and monotone convergence theorem,
@@
 \]
-	One of the consequence of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example, $\phi^{-1}v_t$ converges to $0$ uniformly when $t\to\infty$.
-	Therefore, it is natural to ask the speed of this convergence.
-	This is answered in two steps, the first step says that $(\phi^{-1}v_t)(x)$ will convergence to $0$ in a same speed of $\langle v_t,\phi^*\rangle_m $, uniformly in $x\in E$:
+	One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example, $\phi^{-1}v_t$ converges to $0$ uniformly when $t\to\infty$.
+	Therefore, it is natural to look for the speed of this convergence.
+	This is answered in two steps. The first step says that $(\phi^{-1}v_t)(x)$ will converge to $0$ in the same speed as $\langle v_t,\phi^*\rangle_m $, uniformly in $x\in E$:
 
@@
 \label{prop: asymptotic equivalence of vtphi}
-	The second step characterize this speed:
+	The second step characterizes this speed:
 \begin{prop}
 \label{prop: regularly varying of vt-phi-star}
-	$\langle v_t,\phi^*\rangle_m $ is regularly varying with index $-\frac{1}{\gamma_0-1}$ while $t\to \infty$.
+	$\langle v_t,\phi^*\rangle_m $ is regularly varying with index $-\frac{1}{\gamma_0-1}$ at $\infty$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
@@
 
-	Note that Theorem \ref{thm: main theorem}(2) is simply a corollary of Proposition \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.
+	Note that Theorem \ref{thm: main theorem}(2) is simply a corollary of Propositions \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.
 
 \begin{proof}[Proof of Proposition \ref{prop: convergence in a same speed}]
-	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2rd moment.
+	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
 	For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t)_{t\geq 0}, (\xi_t)_{t\geq 0},\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$. 
-%	According to \eqref{eq: definition of v_t(x)} and Theorem \ref{thm: size-biased decomposition},
 	According to \eqref	{eq: equation for mu v-t} and Theorem \ref{thm: spine representation}, 
@@
 	Therefore, to complete the proof, 
-	%we only have to show that
 	we only need to show that
@@
 
-	For any $t>0$ and any $G\in \mathscr B_{(0,t]}$, define
+	For any $t>0$ and any $G\in \mathscr B((0,t])$, define
 $
@@
 $
-	Then for any $0 < t_0 < t$, we can decompose $Y_t$ by
+	Then for any $0 < t_0 < t$, we can decompose $Y_t$ into
 $
@@
 	 \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
-	= \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] + \epsilon_x^1(t_0,t) +\epsilon_x^2(t_0,t)
+	= \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] + \epsilon_x^1(t_0,t) +\epsilon_x^2(t_0,t),
 \]
@@
 
-	From the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$,
-	%the following identity can be verified:
-	 we have the following identities:
+	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, 
+	 one can check that
 \[\label{eq: some equations for PY-1}\begin{split}
@@
 
-	Taking constants $c_0, c_1>0$ as in \eqref{eq:q(t,x,y)},
-	%if $t_0 > 1$, then it has been argued in the proof of 	\cite[Lemma 5.3]{RenSongSun2017Spine} that
-	it has been argued in the proof of
-	\cite[Lemma 5.3]{RenSongSun2017Spine} that, if $t_0>1$,
+	Let  $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}. Using an argument similar
+	to that used in the proof of
+	\cite[Lemma 5.3]{RenSongSun2017Spine}, we can get that, if $t_0>1$,
 $
@@
 \end{split}\]
-	On the other hand, since $\phi^{-1}v_s$ convergence to $0$ uniformly while $s\to \infty$, we can chose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
-	Then, if $t-s > t-t_0 \geq s_0$, note that $v_t$ is non-increasing in $t$, we have
+	On the other hand, since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
+	Then, if $t-s > t-t_0 \geq s_0$, using the fact that  that $v_t$ is non-increasing in $t$, we get
 \[\begin{split}
@@
 	= -\log \lim_{\lambda \to \infty}
-	%e^{- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ]}
 	\exp(- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ])
@@
 \end{split}\]
-	Then \eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-final} and \eqref{eq:firstpart-of-Y} implies \eqref{eq:upperbound_of_epsilon-2}.
+	Then combining\eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-final} and \eqref{eq:firstpart-of-Y}, we arrive at \eqref{eq:upperbound_of_epsilon-2}.
 
@@
 \end{split}\]
-	Since $\phi^{-1}v_s$ convergence to $0$ uniformly while $s\to \infty$, there exists a map $t\mapsto t_0(t)$ such that,
+	Since $\phi^{-1}v_s$ converges to $0$ uniformly as $s\to \infty$, there exists a map $t\mapsto t_0(t)$ such that,
 \[
@@
 \]
-	Now notice that
+	Note that
 \[\label{eq:k2}\begin{split}
@@
 \end{split}\]
-	Finally, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we have
+	Now, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
 \[
@@
 	On the other hand, since $\phi^{-1}v_t$ converges to $0$ uniformly in $E$, we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
-	Therefore, mapping $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$ which we denote by $R : (0,\infty) \to (0,\infty)$.
+	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$ which we denote by $R : (0,\infty) \to (0,\infty)$.
 
@@
 \]
-	almost everywhere for $r\in (0,\infty)$ with respect to Lebesgue measure.
+	almost everywhere for $r\in (0,\infty)$ with respect to the Lebesgue measure.
 	Therefore, we have
@@
 \end{split}\]
-	While $t\to 0$, we have that
+	Letting $t\to 0$, we get 
 \[
@@
 
-	We are interested in the regularly varying property of $R(r)$ while $r\to 0$.
-	This can be down by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ while $u \to 0$.
-%	In fact, since $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$ and
+	We are interested in checking the regularly varying property of $R(r)$ at $ 0$.
+	This can be done by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at $0$.
 In fact, according to Proposition \ref{prop: convergence in a same speed},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$. Since
@@
 \end{split}\]
-	Therefore, we can write $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ convergence to constant $C_X^{-1}$ while $u \to 0$.
+	Therefore, we can write $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
 	Now according to Corollary \ref{cro: power law and ingetration} we have that
@@
 
-\subsection{Characterizing the conditional distribution}
+\subsection{Characterization of the conditional distribution}
 \label{sec: conditional distribution}
 	Let $\{X; \mathbf P\}$ be a superprocess satisfies
-	%Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
-	Assumptions \ref{asp: 1}-\ref{asp: 4}.
+	Assumptions \ref{asp: 1}--\ref{asp: 4}.
 	Suppose that $m(x: \gamma(x) = \gamma_0)>0$.
 	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | X_t \not \equiv 0\big)\big\}$
-	%convergence weakly
 	converges weakly
-	to a non-degenerate distribution for a large class of testing function $f$ and initial configuration $\mu$.
+	to a non-degenerate distribution for a large class of functions $f$ and initial configuration $\mu$.
 	Our guess of $(\eta_t)$ is
@@
 \]
-	because in this case $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ have the mean convergence:
+	because in this case 
  \[
@@
  	From the Laplace transform point of view, the desired result that $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$
- %	weakly convergence
  converge weakly 
- 	to some probability distribution $F_{f,x}$, is equivalent to the following convergence:
+ 	to some probability distribution $F_{f,x}$ is equivalent to the following convergence:
 \[\begin{split}
@@
 \end{split}\]
-	Further, note that $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
+	Further, since $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
 \[\label{eq: equivalent result}
@@
 	Therefore, to 
-%	actually
-	establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$, one only have to verify \eqref{eq: equivalent result}.
-
-	In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, we need to characterizes the dynamic of $V_t(\theta f)$ while $\theta$ is varying.
-	(Note that \eqref{eq:mean-fkpp} only characterize the dynamic of $V_t(\theta f)$ while $t$ is varying.)
+	establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
+
+	In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, we need to characterize the dynamics of $V_t(\theta f)$ as $\theta$ is varying.
+	(Note that \eqref{eq:mean-fkpp} only characterizes the dynamics of $V_t(\theta f)$ as $t$ is varying.)
 	This is done by the following proposition:
@@
 \begin{prop}
-	For any $f\in pb\mathscr B_E,\theta \geq 0,x\in E$ and $T>0$, we have
+	For any $f\in pb\mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we have
 \[\label{eq: equation for Vt(theta f) for theta}
@@
 \begin{proof}
-	It follows by Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
+	It follows from Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
 \[
@@
 	where $\{Y; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with spine process $\xi$, 
-%	immigrate measure
 immigration measure
 	$\mathbf n_T$ and 
-%	its conditioned mean measure
 conditional mean measure
@@
 \[ \label{eq: dynamic of theta on v_t theta reason 1}
-%	\partial_\theta
 	\frac{\partial}{\partial_\theta}
@@
 	= \int_0^\theta
-%	S_Tf(x)
 P^\beta_Tf(x)
@@
 
-%\\subsection{Characterizing the Zolotarev's distribution}
 \subsection{Zolotarev's distribution}
@@
 
-	Recall that a non negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have the Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
+	Recall that a non negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
 \[
@@
 \]
-	It turns out that we can characterize this distribution by the following Lemma:
+	It turns out that we can characterize this distribution by the following result:
 
@@
 
-	We first give a convention of notation:
-	If $f$ is a measurable function which is $L^p$ integrable on a measurable space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
+	We first introduce some notation:
+	If $f$ is a measurable function which is $L^p$ integrable on the measurable space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
 \[
@@
 \]
-	Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to measure $\mu$.	
-	In order to proof the above Lemma, we will need the following Lemma:
+	Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to the measure $\mu$.	
+	In order to prove the above lemma, we will need the following:
 
 \begin{lem}\label{lem: F is zero}
-	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying that there exists a constant $C>0$ s.t. for all $\theta \geq 0$ we have $F(\theta) \leq C\theta$ and
+	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
 \[
@@
 \]
-	Then, $F \equiv 0$.
+	Then $F \equiv 0$.
 \end{lem}
@@
 \begin{proof}
-%	We proof this Lemma by a contradiction.
-We prove this lemma using contradiction method.
+We prove this lemma by contradiction.
 	Assume that $\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty$.
@@
 	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
-	This, however, is a contradiction to the definition of $\rho$.
+	This, however, contradicts the definition of $\rho$.
 	The proof is complete.
@@
 \end{split}\]
-	The last equality are due to $G(0) = 0$ and
+	The last equality is due to $G(0) = 0$ and
 \[\begin{split}
@@
 \end{split}\]
-	In another word, there is a constant $C_0:= \gamma_0^{\frac{1}{\gamma_0 - 1}}>0$ s.t. \eqref{eq: inequality of F(theta)} is true.
+	In other words, there is a constant $C_0:= \gamma_0^{\frac{1}{\gamma_0 - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
 	On the other hand, according to \eqref{eq: equation for the distribution}, we have that $G(\theta) \leq c\theta$ and $G_0(\theta) \leq c \theta$.
-	Therefore, we also have that there is a constant $C_1 > 0$ s.t. $F(\theta) \leq C_1 \theta$.
+	Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
 	Finally, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
@@
 \label{sec: proof of result 3}
-	Consider the $(\xi, \psi)$-superprocess $\{X;\mathbf P\}$ which satisfies %Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
-	Assumptions \ref{asp: 1}-\ref{asp: 4}.
+	Consider the $(\xi, \psi)$-superprocess $\{X;\mathbf P\}$ which satisfies 
+	Assumptions \ref{asp: 1}--\ref{asp: 4}.
 	Suppose that $m\{ x:\gamma(x)=\gamma_0 \}>0$.
-	Let $f \in p\mathscr B$ be a testing function such that $ \langle f, \phi^* \rangle_m > 0$  and $c_f:=\| \phi^{-1}f \|_\infty < \infty$.
-
-	Without loss any of generality, we assume that $\langle f, \phi^* \rangle_m = 1$.
+	Let $f \in \mathscr B^+(E)$ be  such that $ \langle f, \phi^* \rangle_m > 0$  and $c_f:=\| \phi^{-1}f \|_\infty < \infty$.
+
+	Without loss of generality, we assume that $\langle f, \phi^* \rangle_m = 1$.
 	As have been discussed in Section \ref{sec: conditional distribution}, 
-	% in order to proof Theorem \ref{thm: main theorem}(3), we only have to show that
 	in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
@@
 \]
-	The underlying idea is to make comparison between \eqref{eq: equation for normalized V_T} and \eqref{eq: equation for the distribution}.
+	The underlying idea is to make a comparison between \eqref{eq: equation for normalized V_T} and \eqref{eq: equation for the distribution}.
 
@@
 	J'_G(t,r,\xi):=
-	\gamma_0 (\gamma_0 - 1) t \int_0^1 \Big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \Big) (\xi_{(1-u)t}) du.
+	\gamma_0 (\gamma_0 - 1) t \int_0^1 \Big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \Big) (\xi_{(1-u)t}) du
 \]
@@
 \]
-	The underlying idea of the proof is to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense while $t\to \infty$.
-
-	Step 1: We will give upper bounds for $G,g,J_G,J'_G,J_g$ and $J'_g$, respectively.
+	The underlying idea of the proof is to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense when $t\to \infty$.
+
+	Step 1: We will give some upper bounds for $G,g, J_G, J'_G, J_g$ and $J'_g$ respectively.
 	From \eqref{eq: equation for G} we have
@@
 \end{split}\]
-	From \eqref{eq: definition of J'_g}, \eqref{eq: upper bound for g} and definition of $\eta_t$, we have
+	From \eqref{eq: definition of J'_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
 \[\begin{split}
@@
 \end{split}\]
-	From \eqref{eq: definition of J'_G}, \eqref{eq: upper bound for G} and definition of $\eta_t$, we have
+	From \eqref{eq: definition of J'_G}, \eqref{eq: upper bound for G} and the definition of $\eta_t$, we have
 \[\label{eq: upper bound for J'_G} \begin{split}
@@
 \]
-	Therefore, by the Minkoviski inequality we have that
+	Therefore, by the Minkowski inequality we have that
 \[\begin{split}
@@
 	J_G(r) - J'_G(t,r,\xi)
-%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)};L^2}
 	\xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})}
@@
 \end{split}\]
-	Now, with \eqref{eq: expression for J_g - J'_g}, \eqref{eq: integer in the expression of J_g - J'_g convergences to 0} and \eqref{eq: upper bound for J_g - J'_g}, we can apply Lemma \ref{lem: ergodicity of the underlying process} to function
+	Now, with \eqref{eq: expression for J_g - J'_g}, \eqref{eq: integer in the expression of J_g - J'_g convergences to 0} and \eqref{eq: upper bound for J_g - J'_g}, we can apply Lemma \ref{lem: ergodicity of the underlying process} to the function
 \[
@@
 	J_g(t,r,\xi) - J'_g(t,r,\xi)
-%	\xrightarrow[t\to \infty]{\Pi_x^{(\phi)}; L^2} 0.
 \xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})} 0.
@@
 \end{split}\]
-	Therefore, fixing an $r\geq 0$, we can apply Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process} to function
+	Therefore, fixing an $r\geq 0$, we can apply Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process} to the function
 \[
@@
 \]
-	since it is bounded and Borel measurable on $E\times (0,1) \times [0,\infty)$.
-	Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process},  \eqref{eq: differences between J'_G and J'_g} and definition of $M(r,x), M(r)$ and $C_X$, we have
+	since it is a bounded Borel function on $E\times (0,1) \times [0,\infty)$.
+	Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process},  \eqref{eq: differences between J'_G and J'_g} and the definition of $M(r,x), M(r)$ and $C_X$, we have
 \[\label{eq: limsup of J_G - J'_g}\begin{split}
@@
 \end{split}\]
-	We now recall the reverse Fatou's lemma in the sense of $L^p$ norm with $p\geq 1$: Let $(f_n)_{n\in \mathbb N}$ be a sequence of non-negative measurable functions defined on a measure space $S$ with $\sigma$-finite measure $\mu$.
+	We now recall the reverse Fatou's lemma in $L^p$ with $p\geq 1$: Let $(f_n)_{n\in \mathbb N}$ be a sequence of non-negative measurable functions defined on a measure space $S$ with $\sigma$-finite measure $\mu$.
 If there exists a non-negative $L^p(\mu)$-integrable function $g$ on $S$ such that $f_n \leq g$ for all $n$, then according to the classical reverse Fatou's lemma, we have
@@
 \]
-	Now, use this version of Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
+	Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
 \[\begin{split}
@@
 	for some constant $c_M > 0$.
-	In fact, a direct application of step 2-6 gives that, for each $t\geq 0$ and $x\in E$:
+	In fact, a direct application of Steps 2-6 gives that, for each $t\geq 0$ and $x\in E$:
 \[\begin{split}
@@
 \]
-	Finally, according to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality which gives us the desired result.
+	Finally, according to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
 

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
 
-%\subsection{Motivation and literature review}
 \subsection{Background}
-
-The study of the asymptotic behavior of 
-%the critical branching particle system has a long history.
-critical branching particle systems has a long history
-	It is well known that for a critical Galton-Watson process $(Z_n)$, we have
+    The study of the asymptotic behavior of critical branching particle systems has a long history.
+	It is well known that for a critical Galton-Watson 
+    %process $(Z_n)$, 
+    process $\{(Z_n)_{n = 0,1,\dots}; P\}$,	
+	we have
 	\[\label{eq: Kolmogorov's result with finite variance}
@@
 
-%Note that result \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2rd moment is infinite, i.e.
-$\sigma^2 = \infty$.
-Note that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
-%In this case, the scaling limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so more proper scaling is required.
+    %Note that 
+    Notice that, see \cite{KestenNeySpitzer1966The-Galton-Watson} for example,
+    \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
     In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so a more appropriate scaling is needed.
 	This was first obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
-	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson process $(Z_n)$ with infinite variance.
-	Assuming that the offspring generating function $f(s)$ is of the form
+	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson 
+	%process $(Z_n)$ 
+	process $\{(Z_n)_{n = 0,1,\dots}; P\}$
+	with infinite variance.
+	Assuming that 
+	%the offspring generating function $f(s)$ 
+	the corresponding offspring generating function $f(s)$
+	is of the form
 \[\label{eq: offspring generating function with alpha moment}
@@
 	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
-	Denote by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
-	and  by $\mathbf F_n(\mathbf s), \quad n>1$ its iterates. 
+	%Denote by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
+	Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the corresponding offspring probability generating function,
+	%and  by $\mathbf F_n(\mathbf s), \quad n>1$ its iterates.
+	and  by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
 	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right principal  eigenvectors respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
@@
 \[\label{eq: regularly varying condition for multitype branching process}
-	\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u
+	%\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u
+	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
 	= x^\alpha l(x),
@@
 \]
-	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and  the matrix $E(\mathbf s)$ is defined by
+	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and 
+	%the matrix $E(\mathbf s)$ is defined by
+	the matrix $G(\mathbf s)$ is defined by
 \[
 	\mathbf 1 - \mathbf F(\mathbf s)
-	= (M - E(\mathbf s))(\mathbf 1 - \mathbf s),
+	%= (M - E(\mathbf s))(\mathbf 1 - \mathbf s),
+	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
 	\quad \mathbf s \in \mathbb R_+^d.
 \]
-Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
+    Let 
+    %$a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, 
+    $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$,
+    with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
 It was shown in \cite{GoldsteinHoppe1978Critical} that,
@@
 \]
-	and for each $\mathbf j \in \mathbb N_0^d$
+	and for each $\mathbf j \in \mathbb N_0^d$,
 \[\label{eq: conditioned normalized multitype branching process}
 	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
-	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)}.
-\]
+	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
+\]
+%new
+    where $\mathbf z^{(\alpha)}$ is Zolotarev's random variable with index $\alpha$. 
+%end new
 	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
@@
 
-	Asmussen and Hering \cite{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$ (see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
-	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite{AsmussenHering1983Branching} for critical branching Markov processes,
-see \cite[Theorem 4.2]{AsmussenHering1983Branching}.
-
-%	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
-%	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
-In this paper, we are interested in a class of measure-valued branching Markov process 
-known as $(\xi, \psi)$-superprocesses.
-$\xi$, the spatial motion of the superprocess, is a a Hunt process on a locally 
-compact, separable, metric space $E$, $\psi$, the branching mechanism of the superprocess,
-is function $\psi$ on $E \times [0,\infty)$ of the form
+	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
+%deleted	
+	%(see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
+%end deleted
+	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite[Theorem~4.2]{AsmussenHering1983Branching} for critical branching Markov processes.
+%deleted    
+    %see \cite[Theorem 4.2]{AsmussenHering1983Branching}.
+%end deleted
+
+    In this paper, we are interested in a class of measure-valued branching Markov process known as $(\xi, \psi)$-superprocesses:
+    $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact, separable, metric space $E$; 
+    $\psi$, the branching mechanism of the superprocess, 
+    %is function $\psi$ on $E \times [0,\infty)$ of the form
+    is a function on $E \times [0,\infty)$ of the form
 \[ \label{eq: branching mechanism}
@@
 	In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.
-%	We refer our readers to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
-%	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.
 
@@
 	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$.
-	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$ and the branching mechanism $\psi$ satisfies the following second moment condition:
+	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition,
 \[\label{eq: second moment condition}
@@
 	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
-	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to\eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
+	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
 
@@
 	A simpler
-	version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements.
-	Kyprianou \cite{Kyprianou2008Continuous} considered CSBP's $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$.
-He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
+	version of this question has already been answered in the context of continuous-state branching processes %(CSBP) 
+	(CSBPs)
+	which can be viewed as superprocesses without spatial movements.
+	Kyprianou \cite{Kyprianou2008Continuous} considered 
+	%CSBP's $(Y_t)$ 
+	CSBPs $\{(Y_t); P\}$
+	with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
 \[ \label{eq: conditional limit of CSBP with stable branching}
 	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
-	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
-\]
-	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBP's with branching mechanism
+	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
+\]
+%new
+    where $\mathbf z^{(\gamma - 1)}$ is Zolotarev's random variable with index $\gamma - 1$.
+%end new
+	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied 
+	%CSBP's 
+	CSBPs $\{(Y_t); P\}$
+	with branching mechanism
 \[\label{eq: regular varing of branching mechanism of a CSBP}
@@
 	satisfying Grey's condition.
-	In order for the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
-
-%	In this paper, we establish a result paralleling 
+	In order for the left side of \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for 
+	%some positive function $(\lambda_t)$,
+	some positive constants $(\lambda_t)_{t\geq 0}$, 
+	one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
+
 In this paper, we will establish a result parallel
@@
 	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
-	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and is regularly varying with index $\frac{1}{\gamma_0 - 1}$ at $\infty$..
+	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and 
+	%is regularly varying with index $\frac{1}{\gamma_0 - 1}$ at $\infty$..
+	is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
 	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
@@
 	\mathbf P_{\delta_x}( X_t \not \equiv 0)
-	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t
+	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
 \]
 	and for a large class of non-negative testing functions $f$,
-\[
+\[\label{eq: result2}
 	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
@@
 \]
-	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
-	Precise statements of the assumptions and the results are presented in the next subsection.
-It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ depend primarily on the lowest index $\gamma_0$.
+	%where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
+	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a Zolotarev's random variable with index $\gamma_0 - 1$.
+	Precise statements of the assumptions and the results are presented in the next 
+	%subsection.
+	section.
+    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ 
+    %depend 
+    depends primarily on the lowest index $\gamma_0$.
 
@@
 	Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
-	For simplicity, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$.
+	For simplicity, we write 
+	%$\mu(f)$ 
+	$\mu(f)$ and sometimes $\langle \mu, f\rangle$
+	for the integration of a function $f$ with respect to a measure $\mu$.
     We also write $\langle f, g\rangle_m$ for $\int_E fg dm$  
-    to emphasize that it is the inner product in the Hilbert space $L^2(dm)$.
-	For any $\phi \in \mathscr E^+$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
+    to emphasize that it is the inner product 
+    %in the Hilbert space $L^2(dm)$.
+    in the Hilbert space $L^2(m)$.
+	%For any $\phi \in \mathscr E^+$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
+	For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
 	In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
@@
 	We now give the definition of a $(\xi, \psi)$-superprocess:
-	Let t$E$ be a locally compact separable metric space,
+	Let $E$ be a locally compact separable metric space,
 	the spatial motion
-%	$\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ 
    $\xi:=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ 
-	be a $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ 
-be a function on $E\times[0,\infty)$ given by
+	be a $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by
 	\eqref{eq: branching mechanism}.
-	We say a $\mathcal M^1_E$-valued Hunt process $\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
+	We say a $\mathcal M^1_E$-valued Hunt process 
+	%$\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ 
+	$\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$
+	is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
 \[
@@
 	P^\beta_tf(x)
-	= \Pi_x \big[e^{\int_0^{t} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
+	%= 
+	:=
+	\Pi_x \big[e^{\int_0^{t} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
 	\quad t\geq 0, x\in E, f\in \mathscr B_b(E).
@@
 	(Notice that if $\beta \equiv 0$,
-%	 $P_t:= P^0_t$ is the \emph{transition semigroup} of process $\xi:=\{(\xi)_{t\ge 0}; (\Pi)_{x\in E}\}$.)
 then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
@@
 	= \mu(P^\beta_t f),
-	\quad \mu \in \mathcal M_f, t \geq 0,f \in \mathscr B_b(E).
+	%\quad \mu \in \mathcal M_f, 
+	\quad \mu \in \mathcal M^1_E, 
+	t \geq 0,f \in \mathscr B_b(E).
 	\]
 	This mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
-	As discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} or \eqref{eq: Ygalom type result without 2rd moment}, we have to establish the asymptotic behavior of the mean semigroup first.
-	This can be done under the following assumptions on the underlying motion $\{\xi; \Pi\}$:
+	As discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} 
+	%or \eqref{eq: Ygalom type result without 2rd moment}, 
+	or \eqref{eq: result2},
+	we have to establish the asymptotic behavior of the mean semigroup first.
+	This can be done under the following assumptions on the underlying motion 
+	%$\{\xi; \Pi\}$:
+	$\{(\xi_t); (\Pi_x)\}$:
 \begin{asp}{1}
@@
 	\emph{density of semigroup $(P^\beta_t)$}.
-	Define a family of kernels $(P^{\beta *}_t)_{t \geq 0}$ on $E$ by
+	%Define a family of kernels $(P^{\beta *}_t)_{t \geq 0}$ on $E$ by
+	Define the dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ by
 \[
@@
 \]
-	It is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and its dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+	It is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that 
+	%$(P^\beta_t)_{t \geq 0}$ and its dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ 
+	$(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$
+	are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
 	Let $L$ and $L^*$ be the generators of the semigroups $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$, respectively.
@@
 	We further normalize $\phi$ and $\phi^*$ by $\langle\phi, \phi\rangle_m = \langle\phi,\phi^*\rangle_m = 1$ so that they are unique.
-	Moreover, for each $t\geq 0,x\in E$, we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
-	We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of 
-%the simegroup $(P^\beta_t)_{t\geq 0}$ (respct. $(P^{\beta *}_t)_{t\geq 0}$).
-$L$ (resp. $L^*$).
+	Moreover, for each 
+	%$t\geq 0,x\in E$, 
+	$t\geq 0$ and $x\in E$,
+	we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
+	We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of $L$ (resp. $L^*$).
 
@@
 \]
-It is also shown in \cite{KimSong2008Intrinsic} that $(e^{-\lambda t}p^\beta_t(x,y))_{x,y\in E}$ 
-%	is asymptotic equivalent to 
-	is,  uniformly in $x$ and $y$, asymptotically equivalent to 
-%	$\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ uniformly in $x$ and $y$, and exponentially fast while $t\to \infty$, 
-$\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ as $t\to \infty$
-in the sense that, there are constants $c_0, c_1 > 0$ such that
+    It is also shown in \cite{KimSong2008Intrinsic} that 
+%deleted    
+    %$(e^{-\lambda t}p^\beta_t(x,y))_{x,y\in E}$ is,  uniformly in $x$ and $y$, asymptotically equivalent to $\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ as $t\to \infty$ in the sense that,
+%deleted
+    there are constants $c_0, c_1 > 0$ such that
 \[\label{eq:q(t,x,y)}
-	\sup_{x,y\in E} \big|\frac{e^{-\lambda t}p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \big| \leq c_0 e^{-c_1 t},
+	%\sup_{x,y\in E} \big|\frac{e^{-\lambda t}p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \big| \leq c_0 e^{-c_1 t},
+	\sup_{x,y\in E} \big|\frac{p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \big| \leq c_0 e^{-c_1 t},
 	\quad t > 1.
@@
 
-	In this paper, we will only consider superprocesses with the following spatially dependent stable branching mechanism:
+	%In this paper, we will only consider superprocesses with the following spatially dependent stable branching mechanism:
+	Our assumption on the branching mechanism is the following:
 \begin{asp}{4} \label{asp: 4}
-	The branching mechanism $\psi$ is of  the following form:
+	The branching mechanism $\psi$ is of 
+	% the following form:
+	the form:
 \[\begin{split}
@@
 	Suppose that $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M_E^1}\}$ is a $(\xi, \psi)$-superprocess satisfying 
-%Assumptions \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}. Then,
 Assumptions \ref{asp: 1}--\ref{asp: 4}. Then,
@@
 	\item[(1)] $\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$.
-	\item[(2)] For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$ converges to $0$ as $t\to \infty$, and is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
+	\item[(2)] For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$ 
+	%converges to $0$ as $t\to \infty$, and is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
+	converges to $0$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$, as $t\to \infty$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
@@
 \end{itemize}
-	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
+	%Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
+	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a Zolotarev's random variable with index $\gamma_0 - 1$
 \end{thm}
@@
 
-	In this paper, to establish the Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition of  $\{X; \mathbf P\}$.
+	%In this paper, to establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition of  $\{X; \mathbf P\}$.
+	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use spine decomposition theorem for  $\{X; \mathbf P\}$:
 	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
@@
 	Therefore, this size-biased transform can be viewed as a martingale change of measure.
-	Under the Assumption \ref{asp: 1} and \ref{asp: 3}, 
 	Under the Assumptions \ref{asp: 1} and \ref{asp: 3}, 
@@
 
-	This idea has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
-	Let $(Y_t)$ be a branching diffusion processes in a bounded domain with finite second moment.
+	%This idea 
+	Similar idea
+	has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
+	%Let $(Y_t)$ 
+	Let $\{(Y_t)_{t\geq 0}; P\}$
+	be a branching diffusion processes in a bounded domain with finite second moment.
 	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation
@@
 	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform of Zolotarev's distribution can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
-	Using the spine method, we show that the Laplace transform of the one-dimensional conditioned distributions of the superprocess, after a proper rescaling, can also be characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
+	Using the spine method, we show that the Laplace transform of 
+	%the one-dimensional conditioned distributions 
+	the one-dimensional distributions 
+	of the superprocess, after a proper rescaling, 
+	%can also be 
+	can be
+	characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
 	Then, the desired convergence of the distributions can be established by a comparison between the equations.	
@@
 
-	A similar idea of establishing conditional weak convergence to the exponential distribution through a comparison of the equations satisfed by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
-	We characterized the exponential distribution using an $x^2$-transform distribution equation; and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
-	However, the $x^2$-transform of a random variable requires the existence of the second moment.
-	Since we are not assuming the second moment condition, we can not use the method of $x^2$-transform.
-	Instead, a non-linear delay equation is used.
+	%A similar idea of establishing conditional weak convergence to the exponential distribution through a comparison of the equations satisfed by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
+	A similar idea of establishing weak convergence through a comparison of the equations satisfed by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
+	We characterized the exponential distribution 
+	%using an $x^2$-transform distribution equation; 
+	using its double size-biased transform;
+	and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
+	However, the 
+	%$x^2$-transform of a random variable requires the existence of the second moment.
+	double-size-biased transform of a random variable requires its second moment being finite.
+	%Since we are not assuming the second moment condition, we can not use the method of $x^2$-transform.
+	Since in this paper, we do not assume the second moment condition, we can not use the method of double size-biased transform.
+	%Instead, a non-linear delay equation is used.
 
@@
 	\cite{RenSongZhang2015Limit} (for critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
-First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used
-to extend the result to a general functions $f$.
-
-	Since we are not assuming the second moment condition, this type of argument does not work
-	in the present case.
-	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for all general functions $f$ at the same time.
-	This generalized spine decomposition theorem considered the $X_T(g)$-transform of the superprocess $(X_t)_{0\leq t\leq T}$ for a large class of general functions $g$.
-	The transformed process behaves similarly as in the classical case, despite the fact that the spine processes $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$ 
-	are not consistent for all $T>0$.
+    First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used to extend the result to
+    %a general functions $f$.
+    more general testing functions.
+	%Since we are not assuming the second moment condition, this type of argument does not work in the present case.
+	However, in the present case, since we are not assuming the second moment condition, this type of argument does not work.
+	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for 
+	%all general functions $f$ at the same time.
+	a large class of general testing functions at the same time.
+%deleted
+	%This generalized spine decomposition theorem considered the $X_T(g)$-transform of the superprocess $(X_t)_{0\leq t\leq T}$ for a large class of general functions $g$.
+	%The transformed process behaves similarly as in the classical case, despite the fact that the spine processes $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$ are not consistent for all $T>0$.
+%end deleted
 
@@
 	Finally, in Section \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
+
+\newpage
 \section{Preliminaries}
@@
 \label{sec: Asymptotic equivalence}
-	In this subsection, we give a lemma on asymptotic equivalence.	
+	In this section, we give a lemma on asymptotic equivalence.	
 	Let $t_0 \in [-\infty,\infty]$.
@@
 	= \lambda^\gamma
-	\quad (\text{resp. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
-	= \lambda^\gamma).
+	\quad \Big(\text{resp. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
+	= \lambda^\gamma\Big).
 \]
@@
 	L(t)
-	= c(t) e^{\int_{t_0}^t \epsilon(u) \frac{du}{u}},\quad t\geq t_0,
+	%= c(t) e^{\int_{t_0}^t \epsilon(u) \frac{du}{u}},\quad t\geq t_0,
+	= c(t) \exp\Big\{\int_{t_0}^t \epsilon(u) \frac{du}{u}\Big\},\quad t\geq t_0,
 \]
@@
 	The following lemma concerns the inverse of 
-({\bf I think that there is a little problem with the following lemma. When $f$ is invertible
-but not monotone, its inverse is not the same as the generalized inverse	in 
-\cite{BinghamGoldieTeugels1989Regular}. If we do not really use the general version, we can just give the monotone version.})
-an  reversible regularly varying function.
-	In this paper, if a function $f$ is reversible, we write $f^{(-1)}$ for its inverse; if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
+%({\bf I think that there is a little problem with the following lemma. When $f$ is invertible
+%but not monotone, its inverse is not the same as the generalized inverse	in 
+%\cite{BinghamGoldieTeugels1989Regular}. If we do not really use the general version, we can just give the monotone version.})
+%ZY: I agree. Let us only give the monotone version.
+    %an  reversible regularly varying function.
+    an invertible, monotone, regularly varying function.
+	In this paper, if a function $f$ is 
+	%reversible, 
+	invertible,
+	we write $f^{(-1)}$ for its inverse; 
+	if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
 
@@
 \label{lem: regularly variation and inverse}
-	Suppose that $f$ is a reversible map from $(0,\infty)$ to $(0,\infty)$. Then, for each $\alpha > 0$, we have
+	%Suppose that $f$ is a reversible map from $(0,\infty)$ to $(0,\infty)$. 
+	Suppose that $f$ is an invertible, monotone map from $(0,\infty)$ to $(0,\infty)$.
+	Then, for each $\alpha > 0$, we have
 \[ \label{eq: inverse of a regularly varying function at infinity with alpha > 0}
@@
 \]
-	Further, if $f$ is invertible and monotone, then for each $\alpha > 0$ and $c > 0$, we have
+	%Further, if $f$ is invertible and monotone, then for each $\alpha > 0$ and $c > 0$, we have
+	Similarly, for each $\alpha > 0$ and $c > 0$, we have
 \[\label{eq: inverse and power equivalent at infinity with alpha > 0}
@@
 \begin{proof}
-	Let $f$ be invertible.
+%deleted
+	%Let $f$ be invertible.
+%end delted
 	If $\alpha>0$, then according to \cite[Theorem 1.5.12.]{BinghamGoldieTeugels1989Regular}, we have \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} is true.
 	To see 	\eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} is true, we write $h(t) : = f(t^{-1})^{-1}$.
-	It is  easy to verify that $h$ is also invertible with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1} $.
+	It is  easy to verify that 
+	%$h$ is also invertible 
+	$h$ is invertible and monotone 
+	with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1}$.
 	Therefore,
@@
 	If $\alpha < 0$, to see	\eqref{eq: inverse of a regularly varying function with alpha < 0} is true, we write $g(t) : = f(t^{-1})$.
-	It is easy to verify that $g$ is also invertible with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
+	It is easy to verify that 
+	%$g$ is also invertible with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
+	$g$ is invertible and monotone with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
 	Therefore,
@@
 
-	Now, further assume that $f$ is invertible and monotone, and $f(t) \stackrel[t\to \infty]{}{\sim} c t^\alpha$ for some $\alpha > 0$ and $c > 0$, we want to show that $f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}$.
-	Note that, since $\alpha >0$, we must have $f$ is non-decreasing.
+	%Now, further assume that $f$ is invertible and monotone, and 
+	Now, assume that
+	$f(t) \stackrel[t\to \infty]{}{\sim} c t^\alpha$ for some $\alpha > 0$ and $c > 0$, we want to show that $f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}$.
+	Notice that, since $\alpha >0$, we must have $f$ is non-decreasing.
 	From the definition of the asymptotic equivalence, we have, for each $\epsilon> 0$,
 \[
-	\big|\frac{f(t)}{c t^\alpha} - 1\big|
+	\Big|\frac{f(t)}{c t^\alpha} - 1\Big|
 	< \epsilon,
@@
 \]
-	The proof is complete.
-
 \end{proof}
@@
 \label{sec: Superprocesses}
-	In this subsection, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
-\subsubsection%{FKPP equations}
+	In this section, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
 	It is known, see \cite[Theorem 2.23]{Li2011Measure-valued} for example, that \eqref{eq:FKPP_in_definition} can be written as
@@
     Suppose that Assumptions \ref{asp: 1}--\ref{asp: 2} hold. 
-Integrating both sides of\eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we arrive that
+    Integrating both sides of \eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we get that
 \[\label{eq:langleVtfphiranglem_equation}
@@
 
-\subsubsection{Non-presistency}
+%\subsubsection{Non-presistency}
 	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued cadlag paths on $[0,\infty)$.
-	We refer to $\mathbb W$ as the \emph{canonical space of $X$}.
-	In fact, $X$ can be viewed as a $\mathbb W$-valued random variable.
+	We refer to $\mathbb W$ as the 
+	%\emph{canonical space of $X$}.
+	\emph{canonical space of $(X_t)$}.
+	%In fact, $X$ can be viewed 
+	In fact, $(X_t)$ can be viewed
+	as a $\mathbb W$-valued random variable.
 	We denote the \emph{coordinate process of $\mathbb W$} by $(W_t)_{t\geq 0}$.
 
-	We say that $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$ for all $x\in E$ and $t> 0$.
-	Suppose that $X$ is non-persistent, then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
+	%We say that $X$ is \emph{non-persistent} 
+	We say that $(X_t)$ is \emph{non-persistent}
+	if $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$ for all $x\in E$ and $t> 0$.
+	%Suppose that $X$ is non-persistent, 
+	Suppose that $(X_t)_{t\geq 0}$ is non-persistent,
+	then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
 \begin{itemize}
@@
 	For the existence and further properties of such measures, we refer our readers to \cite{Li2011Measure-valued}.
-	We mention that, in the literature, the Kuznestov measures are usually defined in the following space of excursion paths:
-	\[\begin{split}
-	\mathbb W^{cad}_{0,ex}:=\{ &w: t \mapsto w_t \text{ is a right-continuous path from $(0,\infty)$ to $\mathcal M_E^1$}
-		\\&\quad \text {having the null measure as a trap}\}.
-	\end{split} \]
-	However, since the underlying process $\xi$ is a Hunt process, the Kuznestov measures can actually be carried on the space $\mathbb W$.
+%deleted
+	%We mention that, in the literature, the Kuznestov measures are usually defined in the following space of excursion paths:
+%\[\begin{split}
+	%\mathbb W^{cad}_{0,ex}:=\{ &w: t \mapsto w_t \text{ is a right-continuous path from $(0,\infty)$ to $\mathcal M_E^1$}
+	%\\&\quad \text {having the null measure as a trap}\}.
+%\end{split} \]
+	%However, since the underlying process $\xi$ is a Hunt process, the Kuznestov measures can actually be carried on the space $\mathbb W$.
 
@@
 	= \mathbb N_\mu[ 1-e^{- W_t(f)}],
-	\quad \mu \in \mathcal M_E^1, t>0, f\in bp\mathscr B_E.
-\]
-	Taking $\mu = \delta_x$ for some $x\in E$ and $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and then taking $\lambda \to \infty$, we can write
+	\quad \mu \in \mathcal M_E^1, t>0, 
+	%f\in bp\mathscr B_E.
+	f\in \mathscr B_b^+(E).
+\]
+	%Taking $\mu = \delta_x$ for some $x\in E$ and $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and then taking $\lambda \to \infty$, we can write
+	Taking $\mu = \delta_x$ for some $x\in E$, $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and taking $\lambda \to \infty$, we can write
 \[ \label{eq: definition of v_t(x)}
@@
 \end{split}\]
-
-%It is know that for any $f\in bp{\cal B}_E$,
     It is know that for any $f\in bp{\mathscr B}$,
-\[\label{mean-N}
-\mathbb N_{\mu}[W_t(f)]=\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
+\[\label{eq: mean of kuz measure}
+    \mathbb N_{\mu}[W_t(f)]
+    =\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
 \]
     see \cite[Lemma 3.3]{RenSongSun2017Spine} for example. 
-The we see that $\{(X_t(\phi))_{t\geq 0};\mathbf P_{\mu}\}$ is nonnegative martingale,  and $\{(W_t(\phi))_{t\geq 0};\mathbb N_{\mu}\}$ is also a nonnegative martingale.
+%deleted    
+    %The we see that $\{(X_t(\phi))_{t\geq 0};\mathbf P_{\mu}\}$ is nonnegative martingale,  and $\{(W_t(\phi))_{t\geq 0};\mathbb N_{\mu}\}$ is also a nonnegative martingale.
+%end delted
 
@@
 \item
-	\emph{The spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) e^{-\int_0^T \beta(\xi_s)ds}$-transform of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
+	\emph{The spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is 
+	%the $g(\xi_T) e^{-\int_0^T \beta(\xi_s)ds}$-transform 
+	the $g(\xi_T) \exp\{-\int_0^T \beta(\xi_s)ds\}$-transform
+	of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
 \item
 	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$
-	%with \emph{its conditioned mean measure} defined by
-	with \emph{mean measure}
+	%with \emph{mean measure}
+	with density
 \[
@@
 
-Note that
-		$\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
-Also note that  $\mathbb N_\mu$ is not a probability measure.
-	But after the transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
+    Notice that $\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
+    Also notice that $\mathbb N_\mu$ is not a probability measure, but after the transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
 	Since $\mathbb N_{\mu}(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.
-
-\begin{rem}
-\label{rem: initial configuration of transformed process}
-	Note that $\Pi_{\mu}$ is not typically a probability measure. 
-	%({\bf Remark: why  $\Pi_{\mu}$ is not probability measure?})
-	%RS This because $\mu$ may not be a probability measure.
-	But after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
-We claim that
-\[
+	%Note that $\Pi_{\mu}$ is not typically a probability measure. 
+	Similarly, $\Pi_{\mu}$ is not typically a probability measure, 
+	but after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
+    %We claim that
+    We verify that
+\[\begin{split}
 	\Pi_{\mu}^{(T,g)} [ f(\xi_0) ]
-	= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } f(\xi_0) ]
-	= \mu(P^\beta_T g)^{-1} 
+	%= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } f(\xi_0) ]
+	&= \frac{1}{\mu(P^\beta_Tg)}\Pi_{\mu}\Big[g(\xi_T) \exp\Big\{-\int_0^T \beta(\xi_s)ds \Big\} f(\xi_0) \Big]
+	\\&= \frac{1}{\mu(P^\beta_T g)} 
 	\int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx),
-\]
+\end{split}\]
     which says that
-\[
+\[\label{eq: initial distribution of spine}
 	\Pi_{\mu}^{(T,g)} (\xi_0 \in dx)
-	= \mu(P^\beta_T g)^{-1}
-    P^\beta_T g(x)\mu(dx),
+	= \frac{1}{\mu(P^\beta_T g)} (P^\beta_T g)(x)\mu(dx),
 	\quad x\in E.
 \]
-\end{rem}
 
@@
 	The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, considered the case when $g = \phi$ only.
-	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem,
-that is,  the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$, on the finite interval $[0,T]$.
+	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is,  the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$, on the finite interval $[0,T]$.
 	In fact, one can also check that this consistence property is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)$.
-	Therefore, the actual statement of the classical spine decomposition theorem is a little different from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}, and there is no need to restrict the corresponding processes on the finite interval $[0,T]$.
+	Therefore, the actual statement of the classical spine decomposition theorem is 
+	%a little different 
+	different
+	from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}
+	%, and there is 
+	: There is
+	no need to restrict the corresponding processes on the finite interval $[0,T]$.
 	Because of its theoretical importance, we state the classical spine decomposition theorem explicitly here:
@@
 \]
-	Here, the probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of the process $(X_t)_{t\geq 0}$ is defined by
+	Here, the probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of the process $(X_t)_{t\geq 0}$ is 
+%deleted
+	%defined by
+%end delted
 \[
@@
 \]
-	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of the process $(W_t)_{t\geq 0}$ is defined by
+	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of the process $(W_t)_{t\geq 0}$ is 
+%deleted	
+	%defined by
+%end deleted
 \[
@@
 
-	Let $\mu \in \mathcal M^{(\phi)}_\mu$, we say $\{(Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$ is \emph{the spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
+	Let $\mu \in \mathcal M^{(\phi)}_\mu$, we say 
+	%$\{(Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$ 
+	$\{(\xi_t)_{t\geq 0}, \mathbf n, (Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$
+	is \emph{the spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
 \begin{itemize}
 \item
-	\emph{The spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is defined by
+	\emph{The spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is
+%deleted	
+	%defined by
+%end deleted
 \[
@@
 	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with
-%	\emph{its conditioned mean measure} defined by
-\emph{mean measure}
+    %\emph{mean measure}
+    density
 \[\label{eq:meanMeasImmigr}
@@
 	For the sake of generality, the spine decomposition theorems above are all stated with respect to a general initial configuration $\mu$.
-	If $\mu = \delta_x$ for some $x\in E$, then by  Remark \ref{rem: initial configuration of transformed process}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$.
+	If $\mu = \delta_x$ for some $x\in E$, then by 
+	%Remark \ref{rem: initial configuration of transformed process}
+	\eqref{eq: initial distribution of spine}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$.
 	Similarly, we write $\Pi_x^{(\phi)}$ for $\Pi_{\delta_x}^{(\phi)}$.
 
-\subsection{Ergodicity of the spine process $\{\xi; \Pi^{(\phi)}_x\}$}
+%\subsection{Ergodicity of the spine process $\{\xi; \Pi^{(\phi)}_x\}$}
+\subsection{Ergodicity of the spine process}
 \label{sec: Ergodicity}
-	In this subsection, we discuss the ergodicity of the spine processes $\{\xi; \Pi^{(\phi)}_x\}$ under Assumptions \ref{asp: 1}-- \ref{asp: 3}.
-	One can check that $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
+	In this subsection, we discuss the ergodicity of the spine processes 
+	%$\{\xi; \Pi^{(\phi)}_x\}$ 
+	$\{(\xi_t); (\Pi^{(\phi)}_x)\}$ 
+	under Assumptions \ref{asp: 1}--\ref{asp: 3}.
+	%One can check that $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
+	According to \cite{KimSong2008Intrinsic}, $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
 \[
@@
 \]
-	Therefore it follows from Lemma \ref{lem: ergodicity of the underlying process} that
+	%Therefore it follows from Lemma \ref{lem: ergodicity of the underlying process} that
+	From Lemma \ref{lem: ergodicity of the underlying process}, we know that
 \[
@@
 \]
-	Finally, noting that that $0\leq F \leq \bar F$, we get
+	Finally, 
+	%noting that that 
+	notice that
+	$0\leq F \leq \bar F$, we get
 \[\begin{split}
@@
 \begin{proof}
+    %new added
+    Recall that $\kappa_0 : = \text{essinf}_{m(dx)} \kappa(x) $ and $\gamma_0 := \text{essinf}_{m(dx)} \gamma(x)$.
+%end new added
 	For each $x\in E$, let $\tilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\tilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$.
-	Then, we know that $\tilde \kappa = \kappa$ and $\tilde \gamma = \gamma$ almost everywhere with respect to the measure $m$.
+%	Then, we know that $\tilde \kappa = \kappa$ and $\tilde \gamma = \gamma$ almost everywhere with respect to the measure $m$.
+    Then, we know that $m(\tilde \kappa \neq \kappa) = 0$ and $m(\tilde \gamma \neq \gamma) = 0$.
 	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z) $ almost everywhere with respect to the measure $m$.
-	Therefore, if we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
+
+	%Therefore, 
+	If we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
 \[
@@
 \]
-	So, we can view $\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
+	So, %we can view 
+	we can consider
+	$\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
 	Define 
@@
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
-	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent.
-	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have $\mathbf P_{\delta_x}(X_t \equiv 0)<1$ for each $x\in E$ and $t>0$.
-	Therefore, from \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$.
-	According to \eqref{eq:mean-fkpp}, by monotonicity, we see that $(v_t)$ satisfies the equation
+	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent,
+%new added
+    i.e. 
+\[
+    \mathbf P_{\delta_x}(X_t \equiv 0) 
+    > 0,
+    \quad t>0, x \in E.
+\]
+%end new added
+	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have 
+\[
+    \mathbf P_{\delta_x}(X_t \equiv 0)<1,
+    \quad t>0, x \in E.
+\]
+	%Therefore, 
+	From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$.
+	%According to \eqref{eq:mean-fkpp}, 
+	According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp},
+	by monotonicity, we see that $(v_t)$ satisfies the equation
 \[
@@
 
-	Note that, under the Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
-	Therefore, we have $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
-	Then, according to \eqref{eq:langleVtfphiranglem_equation}
-and monotone convergence theorem,
+	%Note that, 
+	Notice that,
+	under the Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
+	%Therefore, we have $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
+	Therefore, $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
+
+	%Then, according to \eqref{eq:langleVtfphiranglem_equation}
+	According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and monotone convergence theorem,
 	we have another equation
@@
 \]
-	One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example, $\phi^{-1}v_t$ converges to $0$ uniformly when $t\to\infty$.
-	Therefore, it is natural to look for the speed of this convergence.
-	This is answered in two steps. The first step says that $(\phi^{-1}v_t)(x)$ will converge to $0$ in the same speed as $\langle v_t,\phi^*\rangle_m $, uniformly in $x\in E$:
+	One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example, %$\phi^{-1}v_t$ converges to $0$ uniformly when $t\to\infty$.
+\[\label{eq: uniform converges to 0}
+    \|\phi^{-1}v_t\|_{\infty} \xrightarrow[t\to \infty]{} 0.
+\]
+	%Therefore, it is natural to look for the speed of this convergence.
+	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only have to consider the speed of this convergence.
+	This is answered in two steps. 
+	The first step says that $(\phi^{-1}v_t)(x)$ will converge to $0$ in the same speed as $\langle v_t,\phi^*\rangle_m $, uniformly in $x\in E$:
 
@@
 
-	Note that Theorem \ref{thm: main theorem}(2) is simply a corollary of Propositions \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.
+	%Note that 
+	Notice that
+	Theorem \ref{thm: main theorem}(2) is simply a corollary of Propositions \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.
 
@@
 	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
-	For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t)_{t\geq 0}, (\xi_t)_{t\geq 0},\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$. 
-	According to \eqref	{eq: equation for mu v-t} and Theorem \ref{thm: spine representation}, 
+	For each $\mu\in\mathcal M^\phi_E$, denote by 
+	%$\{(Y_t)_{t\geq 0}, (\xi_t)_{t\geq 0},\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ 
+	$\{(Y_t), (\xi_t),\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$
+	the spine representation of $\mathbb N^{(\phi)}_\mu$. 
+	%According to \eqref	{eq: equation for mu v-t} and Theorem \ref{thm: spine representation}, 
+	According to \eqref	{eq: equation for mu v-t}, \eqref{eq: mean of kuz measure} and Theorem \ref{thm: spine representation}, 
 	we have that for each $t>0$,
@@
 	= \mathbb N_\mu[W_t(\phi)] \mathbb N^{W_t(\phi)}_\mu [W_t(\phi)^{-1}]
-	= \mathbb N_\mu[W_t(\phi) > 0]
-	= \langle \mu,v_t \rangle.
+	%= \mathbb N_\mu[W_t(\phi) > 0]
+	= \mathbb N_\mu(W_t(\phi) > 0)
+	%= \langle \mu,v_t \rangle.
+	= \mu(v_t).
 \end{split}\]
@@
 	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, 
-	 one can check that
+	%one can check that
+	we verify that
 \[\label{eq: some equations for PY-1}\begin{split}
@@
 
-	Let  $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}. Using an argument similar
-	to that used in the proof of
-	\cite[Lemma 5.3]{RenSongSun2017Spine}, we can get that, if $t_0>1$,
-$
+	Let  $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}. 
+	%Using an argument similar to that used in the proof of \cite[Lemma 5.3]{RenSongSun2017Spine}, we can get that, if $t_0>1$,
+	We claim that
+\[\label{eq: bound for epsilon1}
 	|\epsilon_x^1(t_0,t)|
-	\leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m .
-$
+	\leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m,
+%new
+    \quad t_0 > 1.
+%end new
+\]
 	In fact,
@@
 
-	In fact, we have
+	%In fact, we have
+	In fact, using the Markov property of the spine process $(\xi_t)$, and the property of the Poisson random measure, we have 
 \[\label{eq:epsilon-2}\begin{split}
@@
 \end{split}\]
-	Therefore, by Campbell's formula, while $t-t_0 \geq s_0$,
-\[\label{eq:firstpart-of-Y}\begin{split}
+	%Therefore, by Campbell's formula, while $t-t_0 \geq s_0$,
+	Therefore, while $t-t_0 \geq s_0$, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have 
+\[\begin{split}
 	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]
 	\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]\big)
-	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
-	= -\log \lim_{\lambda \to \infty}
-	\exp(- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ])
-	\\&\quad = \mathbf m^\xi [\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0}]
+	%\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
+	=  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
+	%= -\log \lim_{\lambda \to \infty}
+	\\&\quad = -\log \lim_{\lambda \to \infty}
+	%\exp(- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ])
+	\exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
+	%\\&\quad = \mathbf m^\xi [\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0}]
+	\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0} \mathbf m^\xi(ds,dw)
 	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{X_{t-s} \not\equiv 0}]\pi(\xi_s,dy)
@@
 \end{split}\]
-	Then combining\eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-final} and \eqref{eq:firstpart-of-Y}, we arrive at \eqref{eq:upperbound_of_epsilon-2}.
-
-	Now, for each $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)} and \eqref{eq: some equations for PY-1}, we have
+	%Then combining \eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-final} and \eqref{eq:firstpart-of-Y}, we arrive at \eqref{eq:upperbound_of_epsilon-2}.
+	Combine this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
+
+	Now, for each $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, 
+	%according to \eqref{eq: starting point of phi-1v_t(x)} and \eqref{eq: some equations for PY-1}, we have
+	according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1}, \eqref{eq: bound for epsilon1} and \eqref{eq:epsilon-2-final}, we have
 \[\label{vts-inequality}\begin{split}
@@
 	\leq \frac{|\epsilon_x^1(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m} + \frac{|\epsilon_x^2(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m}\\
-	&\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-s}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
-\end{split}\]
-	Since $\phi^{-1}v_s$ converges to $0$ uniformly as $s\to \infty$, there exists a map $t\mapsto t_0(t)$ such that,
+	&\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty} 
+	%\cdot \|\phi^{-1}v_{t-s}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
+	\cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
+\end{split}\]
+	%Since $\phi^{-1}v_s$ converges to $0$ uniformly as $s\to \infty$, 
+	According to \eqref{eq: uniform converges to 0},
+	there exists a map $t\mapsto t_0(t)$ such that,
 \[
@@
 \]
-	Note that
+	%Note that
+	Notice that
 \[\label{eq:k2}\begin{split}
@@
 	From \eqref{eq: equation of <vt,phi>} we know that $\langle v_t,\phi^* \rangle_m$ is continuous and strictly decreasing in $t \in (0,\infty)$.
-	Since $X$ is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$, $\mathbf P_\mu (X_t \not \equiv 0) \xrightarrow[t\to 0]{} 1$.
+	%Since $X$ 
+	Since the superprocess $(X_t)_{t\geq 0}$
+	is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$, $\mathbf P_\mu (X_t \not \equiv 0) \xrightarrow[t\to 0]{} 1$.
 	Taking $\mu = \nu$, according to \eqref{eq: equation for mu v-t}, we have that $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to 0]{} +\infty$.
-	On the other hand, since $\phi^{-1}v_t$ converges to $0$ uniformly in $E$, we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
-	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$ which we denote by $R : (0,\infty) \to (0,\infty)$.
+	On the other hand, 
+	%since $\phi^{-1}v_t$ converges to $0$ uniformly in $E$, 
+	according to \eqref{eq: uniform converges to 0},
+	we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
+	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$ which we denote by 
+	%$R : (0,\infty) \to (0,\infty)$.
+\[
+	R: (0,\infty) \to (0,\infty).
+\]
 
@@
 	Then, we have
-\[
+\[\label{eq: change variable using inverse}
 	v_t(x)
@@
 	Further, by Proposition \ref{prop: convergence in a same speed} and $R(u)\xrightarrow[u\to 0]{} \infty$, we have
-$
+\[\label{eq: epsilon R converges to 0}
 	\sup_{x\in E}|\epsilon_{R(u)}(x)|
 	\xrightarrow[u\to 0]{} 0.
-$
+\]
 
@@
 	= \int_s^t \langle \psi_0(\cdot ,v_r), \phi^*\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
-	\\&= \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle \phi \big), \phi^* \big\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
+	\\&\overset{\text{by \eqref{eq: change variable using inverse} }}{=} \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle \phi \big), \phi^* \big\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
 	\\&= \int_{\langle v_s,\phi^*\rangle}^{\langle v_t, \phi^* \rangle} \big\langle \psi_0 \big( \cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du.
@@
 \]
-	This implies that
-\[
+	%This implies that
+	Since $R$ is the inverse of $t\mapsto \langle v_t,\phi^*\rangle$, the above implies that
+\[\label{eq: integral equation for R}
 	R(r)
@@
 
-	We are interested in checking the regularly varying property of $R(r)$ at $ 0$.
-	This can be done by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at $0$.
-In fact, according to Proposition \ref{prop: convergence in a same speed},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$. Since
-$\gamma(\cdot)$ is bounded, we have $\big(1+ \epsilon_{R(u)}(x)\big)^{\gamma(x)}\stackrel[u\to 0]{x\in E}{\sim} 1$.
+	We are interested in checking the regularly varying property of $R(r)$ at 
+	%$ 0$.
+	$r=0$.
+	This can be done by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at 
+	%$0$.
+	$u = 0$.
+    %In fact, according to Proposition \ref{prop: convergence in a same speed},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$. 
+    According to \eqref{eq: epsilon R converges to 0},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$. 
+    Since $\gamma(\cdot)$ is bounded, we have $\big(1+ \epsilon_{R(u)}(x)\big)^{\gamma(x)}\stackrel[u\to 0]{x\in E}{\sim} 1$.
 	Therefore, from Lemma \ref{lem: asymptotic equivalent of integration}, we have that
-\[\label{eq: }\begin{split}
+\[\label{eq: regularly part in the integration}\begin{split}
 	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
@@
 \end{split}\]
-	According to Lemma \ref{lem:regularly_variation_and_integration}, this implies that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
-	According to Corollary \ref{cro: power law and ingetration}, this implies that $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
+	%According to Lemma \ref{lem:regularly_variation_and_integration}, this implies that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
+	According to Lemma \ref{lem:regularly_variation_and_integration}, and the fact that $\kappa(x)\phi(x)^\gamma(x)$ is bounded and measure $\phi^* dm$ is finite, we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
+	%According to Corollary \ref{cro: power law and ingetration}, this implies that $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
+	Notice that $-\gamma_0 < 0$, according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
 	Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and \eqref{eq: inverse of a regularly varying function with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.
 
-	Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration}, we know that
+	%Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration}, we know that
+	Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration} and \eqref{eq: regularly part in the integration}, we know that
 \[\begin{split}
 	&\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
-	\stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_m.
-	\\ & \stackrel[u\to 0]{}{\sim}  \langle \mathbf 1_{\gamma(x)= \gamma_0}, \kappa (x)\phi(x)^{\gamma_0} \phi^*(x) \rangle_m u^{\gamma_0}
+	\stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) 
+	%\rangle_m.
+	\rangle_{m(dx)}.
+	\\ &\quad \stackrel[u\to 0]{}{\sim}  \langle \mathbf 1_{\gamma(x)= \gamma_0}, \kappa (x)\phi(x)^{\gamma_0} \phi^*(x) 
+	%\rangle_m u^{\gamma_0}
+	\rangle_{m(dx)} u^{\gamma_0}
 	=: C_X u^{\gamma_0}.
@@
 	Therefore, we can write $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
-	Now according to Corollary \ref{cro: power law and ingetration} we have that
+	Now according to 
+	%Corollary \ref{cro: power law and ingetration} 
+	Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R} 
+	we have that
 \[\begin{split}
@@
 \end{split}\]
-	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from \eqref{eq: inverse and power equivalent with alpha < 0}, we have
+	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from 
+	%\eqref{eq: inverse and power equivalent with alpha < 0},
+	\eqref{eq: inverse and power equivalent with alpha < 0} and above, 
+	we have
 \[
@@
 
-\subsection{Characterization of the conditional distribution}
+%\subsection{Characterization of the conditional distribution}
+\subsection{Characterization of the one dimensional distribution}
 \label{sec: conditional distribution}
-	Let $\{X; \mathbf P\}$ be a superprocess satisfies
+	%Let $\{X; \mathbf P\}$ be a superprocess satisfies
+	Let $\{(X_t)_{t\geq 0}; \mathbf P\}$ be a superprocess satisfies
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
@@
 	Our guess of $(\eta_t)$ is
-\[
+\[\label{eq: definition of eta}
 	\eta_t
@@
 \begin{prop}
-	For any $f\in pb\mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we have
+	%For any $f\in pb\mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we 
+	For any $f\in \mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we have
 \[\label{eq: equation for Vt(theta f) for theta}
 	V_T ( \theta f) ( x)
-	= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr.
+	%= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr.
+	= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr.
 \]
@@
 \]
-	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Campbell's formula and \eqref{eq: definition of Gamma function}, we have
+	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, 
+	%then by Campbell's formula and \eqref{eq: definition of Gamma function}, we have
+	then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
 \[\label{eq: dynamic of theta on v_t theta reason 2}\begin{split}
@@
 	\dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
-	\\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \big[e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds}\big] dr
-	\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr,
+	%\\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \big[e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds}\big] dr
+	\\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \Big[\exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds\Big\}\Big] dr
+	%\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr,
+	\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr,
 \end{split}\]
@@
 	&\frac{V_T(\theta \eta_T f)(x)}{\eta_T}
-	= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
-	\\&\quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
-	\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} e^{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du}\Big] dr.
+	%= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
+	\\&\quad= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
+	%\\&\quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
+	\\&\quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
+	%\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} e^{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du}\Big] dr.
+	\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} \exp\Big\{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du\Big\}\Big] dr.
 \end{split}\]
@@
 	G( \theta)
-	= \int_0^\theta e^{ - \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1} })^{\gamma_0 - 1}\frac{du}{u} } dr,
+	%= \int_0^\theta e^{ - \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1} })^{\gamma_0 - 1}\frac{du}{u} } dr,
+	= \int_0^\theta \exp\Big\{ - \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1} })^{\gamma_0 - 1}\frac{du}{u} \Big\} dr,
 	\quad \theta \geq 0,
@@
 	G(\theta)
-	= \big(\frac{1}{1+\theta^{-(\gamma_0 - 1)}}\big)^{\frac{1}{\gamma_0 - 1}},
+	%= \big(\frac{1}{1+\theta^{-(\gamma_0 - 1)}}\big)^{\frac{1}{\gamma_0 - 1}},
+	= \Big(\frac{1}{1+\theta^{-(\gamma_0 - 1)}}\Big)^{\frac{1}{\gamma_0 - 1}},
 	\quad \theta \geq 0.
@@
 	We first introduce some notation:
-	If $f$ is a measurable function which is $L^p$ integrable on the measurable space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
+	If $f$ is a measurable function which is $L^p$ integrable on the 
+	%measurable space 
+	measure space
+	$(S,\mathscr S,\mu)$ with $p > 0$, then we write
 \[
@@
     We prove this lemma by contradiction.
-	Assume that $\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty$.
+	Assume that 
+\[\label{eq: definition of rho}
+	\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
+\]
 	Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
@@
 	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
-	This, however, contradicts the definition of $\rho$.
-	The proof is complete.
+	%This, however, contradicts the definition of $\rho$.
+	This, however, contradicts \eqref{eq: definition of rho}.
+%deleted
+    %The proof is complete.
+%end deleted
 \end{proof}
@@
 \[\begin{split}
-	& \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}} dr
-	\\&\quad = \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 \frac{du}{u+r^{-(\gamma_0 - 1)}} } dr
-	= \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \log\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} } } dr
+	%& \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}} dr
+	& \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}\Big\} dr
+	%\\&\quad = \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 \frac{du}{u+r^{-(\gamma_0 - 1)}} } dr
+	\\&\quad = \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 \frac{du}{u+r^{-(\gamma_0 - 1)}} \Big\} dr
+	%= \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \log\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} } } dr
+	= \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \log\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} } \Big\} dr
 	\\&\quad = \int_0^\theta \big(\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} }\big)^{- \frac{\gamma_0} {\gamma_0 - 1}} dr
@@
 \]
-	We claim that the non-negative function $F$ satisfies the following equation:
+	We claim that the non-negative function $F$ satisfies 
+	%the following equation:
+	the following inequality:
 \[\label{eq: inequality of F(theta)}
@@
 	\\ & \quad \leq \Big\| \gamma_0\int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} - \gamma_0\int_0^1 G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}}
-	\\ & \quad \leq \gamma_0 \Big( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} - G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}| \frac{du}{u} \Big)^{\frac{1}{\gamma_0 - 1}} dr \Big)^{\gamma_0 - 1}.
+	\\ & \quad \leq \gamma_0 \Bigg( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} - G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}| \frac{du}{u} \Big)^{\frac{1}{\gamma_0 - 1}} dr \Bigg)^{\gamma_0 - 1}.
 \end{split}\]
 	In other words, there is a constant $C_0:= \gamma_0^{\frac{1}{\gamma_0 - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
-	On the other hand, according to \eqref{eq: equation for the distribution}, we have that $G(\theta) \leq c\theta$ and $G_0(\theta) \leq c \theta$.
+	On the other hand, according to \eqref{eq: equation for the distribution}, 
+	%we have that $G(\theta) \leq c\theta$ and $G_0(\theta) \leq c \theta$.
+	we have that $G(\theta) \leq \theta$ and $G_0(\theta) \leq \theta$.
 	Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
-	Finally, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
+	%Finally, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
+	Therefore, according to Lemma \ref{lem: F is zero} and \eqref{eq: inequality of F(theta)}, we have $F \equiv 0$ as desired.
 \end{proof}
@@
 	\xrightarrow[t\to \infty]{} G(\theta)
-	:= ( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} )^{ \frac{1}{\gamma_0 - 1} },
+	:= \Big( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} \Big)^{ \frac{1}{\gamma_0 - 1} },
 	\quad x\in E, \theta \geq 0.
 \]
-	The underlying idea is to make a comparison between \eqref{eq: equation for normalized V_T} and \eqref{eq: equation for the distribution}.
-
-	In fact, from Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we can rewrite the equation for $G$:
+	%The underlying idea is to make a comparison between \eqref{eq: equation for normalized V_T} and \eqref{eq: equation for the distribution}.
+
+	%In fact, from Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we can rewrite the equation for $G$:
+	From Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we have an equation for $G$:
 \[\label{eq: equation for G}
@@
 \]
-	According to \eqref{eq: equation for normalized V_T}, we can rewrite the equation for $g$:
+	%According to \eqref{eq: equation for normalized V_T}, we can rewrite the equation for $g$:
+	According to \eqref{eq: equation for normalized V_T}, we have an equation for $g$:
 \[\label{eq: equation for g}
@@
 	J_g(t,r,\xi):=
-	(\gamma_0 - 1)t\int_0^1 \Big(  \kappa\gamma \big(   \phi \eta_{ut}   \big)^{\gamma - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot \big)^{\gamma-1}  \Big) \big(  \xi_{(1-u)t}  \big) du.
+	(\gamma_0 - 1)t\int_0^1 \big(  \kappa\gamma (   \phi \eta_{ut}  )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) (  \xi_{(1-u)t}  ) du.
 \]
@@
 	J'_G(t,r,\xi):=
-	\gamma_0 (\gamma_0 - 1) t \int_0^1 \Big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \Big) (\xi_{(1-u)t}) du
+	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big) (\xi_{(1-u)t}) du
 \]
@@
 	J'_g(t,r,\xi):=
-	\gamma_0 (\gamma_0 - 1) t \int_0^1 \Big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \Big) (\xi_{(1-u)t})  du.
+	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \big) (\xi_{(1-u)t})  du.
 \]
@@
 
-	Step 1: We will give some upper bounds for $G,g, J_G, J'_G, J_g$ and $J'_g$ respectively.
+	Step 1: 
+	%We will give some upper bounds for $G,g, J_G, J'_G, J_g$ and $J'_g$ respectively.
+	We will give upper bounds for $G,g, J_G, J'_G, J_g$ and $J'_g$ respectively.
 	From \eqref{eq: equation for G} we have
@@
 \]
-	From \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
+	%From \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
+	From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have
 \[\begin{split}
@@
 \end{split}\]
-	From \eqref{eq: definition of J'_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
+	%From \eqref{eq: definition of J'_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
+	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have
 \[\begin{split}
 	J'_g(t,r,\xi)
-	&\leq \gamma_0(\gamma_0 - 1) c_f^{\gamma_0 - 1}r^{\gamma_0 - 1} \|  \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \|_\infty \int_0^1 t \big( C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
+%new	
+	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} (c_f ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
+%end new
+	\\&\leq \gamma_0(\gamma_0 - 1) c_f^{\gamma_0 - 1}r^{\gamma_0 - 1} \|  \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \|_\infty \int_0^1 t \big( C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
 	\\&=: c_3 \cdot r^{\gamma_0 - 1},
@@
 \end{split}\]
-	From \eqref{eq: definition of J'_G}, \eqref{eq: upper bound for G} and the definition of $\eta_t$, we have
+	%From \eqref{eq: definition of J'_G}, \eqref{eq: upper bound for G} and the definition of $\eta_t$, we have
+	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have
 \[\label{eq: upper bound for J'_G} \begin{split}
 	J'_G(t,r,\xi)
-	&\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
+%new	
+	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} (ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
+%end new
+	\\&\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
 	\\&=: c_4 \cdot r^{\gamma_0 - 1},
@@
 
-	Step 2: We will show that
+	Step 2: We will show that, for each $t\geq 0, \theta \geq 0,$ and $x\in E$
 \[\begin{split}
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
-	\\&\quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) +c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x),
-	\quad t\geq 0, \theta \geq 0, x\in E,
+	\\&\quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) +c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x).
 \end{split}\]
@@
 	I_1(t,\theta,x)
-	&:= \big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}} ,
+	&:= \Big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}} ,
 	\\I_2(t,\theta,x)
-	&:= \big\|  \|  J_G(r) - J'_G(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
+	&:= \Big\|  \|  J_G(r) - J'_G(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
 	\\I_3(t,\theta,x)
-	&:= \big\| \|  J'_G(t,r,\xi) - J'_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
+	&:= \Big\| \|  J'_G(t,r,\xi) - J'_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
 \end{split}\]
@@
 	I_4(t,\theta,x)
-	:= \big\| \| J'_g(t,r,\xi) - J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
+	:= \Big\| \| J'_g(t,r,\xi) - J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
 \]
@@
 	g(t,\theta,x)^{\gamma_0 - 1}
-	=\big\| \| (\phi^{-1}f)(\xi_t) ^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
+	=\Big\| \| (\phi^{-1}f)(\xi_t) ^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
 	\quad t\geq 0, \theta \geq 0, x\in E.
@@
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
-	\\&\quad \leq \big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
-	\\&\quad \leq I_1(t,\theta,x) + \big\| \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad \leq I_1(t,\theta,x) + \big\| \|  (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} ( e^{-J_G(r)} - e^{-J_g(t,r,\xi)} )  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1}\big\| \|  J_G(r) -J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\&\quad \leq \Big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
+	\\&\quad \leq I_1(t,\theta,x) + \Big\| \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} - 
+	\\&\quad \qquad \qquad \qquad \qquad \qquad \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\&\quad \leq I_1(t,\theta,x) + \Big\| \|  (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} ( e^{-J_G(r)} - e^{-J_g(t,r,\xi)} )  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1}\Big\| \|  J_G(r) -J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
 	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1} I_2(t,\theta,x) +c_f^{\gamma_0 - 1} I_3(t,\theta,x)+c_f^{\gamma_0 - 1} I_4(t,\theta,x),
@@
 	Step 3: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
-	We first note that, by \eqref{eq: asymptotic for q_t(x,y)},
+	Notice that, 
+	%by \eqref{eq: asymptotic for q_t(x,y)},
+	by \eqref{eq:q(t,x,y)}
 \[
@@
 	&e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
-	\\&\quad =e^{ - J_G(r)} \big( 1   -  \Pi_x^{(\phi)}[ (\phi^{-1}f)(\xi_t) ]^{\gamma_0 - 1}   \big)
+	\\&\quad =e^{ - J_G(r)} \Big( 1   -  \Pi_x^{(\phi)}[ (\phi^{-1}f)(\xi_t) ]^{\gamma_0 - 1}   \Big)
 	\xrightarrow[t\to \infty]{} 0,
@@
 \[
-	\big| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big|
+	\Big| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big|
 	\leq 1+ c_f^{\gamma_0 - 1}.
@@
 	Step 4: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_2(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
-	We first note that, for each $t\geq 0$ and $r\geq 0$,
+	%We first note that, for each $t\geq 0$ and $r\geq 0$,
+	Notice that, according to \eqref{eq: definition for J_G} and \eqref{eq: definition of J'_G}, for each $t\geq 0$ and $r\geq 0$,
 \[\begin{split}
@@
 \end{split}\]
-	We then note that, according to \eqref{eq: upper bound for G}, for each $r \geq 0$, $u\in [0,1]$ and $x\in E$,
+	%We then note that, 
+	Also notice that,
+	according to \eqref{eq: upper bound for G}, for each $r \geq 0$, $u\in [0,1]$ and $x\in E$,
 \[\begin{split}
@@
 \]
-	We first note that, according to \eqref{eq: upper bound for G} and \eqref{eq: upper bound for g}, we have the following bound:
+	%We first note that, 
+	Notice that,
+	according to \eqref{eq: upper bound for G} and \eqref{eq: upper bound for g}, we have the following bound:
 \[\label{eq: upper bound for M(t,r,x)}
@@
 \]	
-	We then note that, from the definition of $J'_G, J'_g$ and $\eta_t$, we have
+	%We then note that, from the definition of $J'_G, J'_g$ and $\eta_t$, we have
+	From the definition of $J'_G, J'_g$ and $\eta_t$, we have
 \[\label{eq: differences between J'_G and J'_g}\begin{split}
@@
 	\limsup_{n\to \infty}\big\| f_n \big\|_{\mu;p}
-	= \big (   \limsup_{n\to \infty}  \int f^p_n d\mu        \big)^{\frac{1}{p}}
-	\leq  \big (   \int \limsup_{n\to \infty} f^p_n d\mu        \big)^{\frac{1}{p}}
+	= \Big (   \limsup_{n\to \infty}  \int f^p_n d\mu        \Big)^{\frac{1}{p}}
+	\leq  \Big (   \int \limsup_{n\to \infty} f^p_n d\mu        \Big)^{\frac{1}{p}}
 	= \big\| \limsup_{n\to \infty} f_n \big\|_{\mu;p}.
@@
 	\\&\quad\leq \Big\| \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	= \gamma_0 \bigg( \int_0^\theta \Big (   \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}   \Big )^{\frac{1}{\gamma_0 - 1}} dr \bigg)^{\gamma_0 - 1}
+	\\&\quad = \gamma_0 \bigg( \int_0^\theta \Big (   \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}   \Big )^{\frac{1}{\gamma_0 - 1}} dr \bigg)^{\gamma_0 - 1}
 	\\&\quad = \gamma_0 \Big(  \int_0^\theta  \| M(r u^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1},
@@
 \]
-	Finally, according to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
+	%according to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
+	According to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
 

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
+%%%----Versions-----------------------------
+%stable-limit4.tex 2018/6/21  by Yanxia-------
+%stable-limit3.tex 2018/6/13  by Zhenyao-------
+
 %---The preamble----------------------
@@
     %process $(Z_n)$,
-    process $\{(Z_n)_{n = 0,1,\dots}; P\}$,	
+    %YX process $\{(Z_n)_{n = 0,1,\dots}; P\}$,	
+    process $\{(Z_n)_{n\geq 0}; P\}$,	
 	we have
@@
 
-    %Note that 
-    Notice that, see \cite{KestenNeySpitzer1966The-Galton-Watson} for example,
-    \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
-    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so a more appropriate scaling is needed.
-	This was first obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
+    %YX Notice that, see \cite{KestenNeySpitzer1966The-Galton-Watson} for example,
+     Notice that,
+    \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid
+  %YX    even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
+   even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
+    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate,
+    %YX so a more appropriate scaling is needed.
+    and then  more appropriate scalings are needed.
+	%YX This was first obtained
+Research in this direction was first gaven
+by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
 	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson
 	%process $(Z_n)$
-	process $\{(Z_n)_{n = 0,1,\dots}; P\}$
+	%YX process $\{(Z_n)_{n = 0,1,\dots}; P\}$
+    process $\{(Z_n)_{n\geq 0}; P\}$
 	with infinite variance.
-	Assuming that 
-	%the offspring generating function $f(s)$ 
-	the corresponding offspring generating function $f(s)$
+%YX	Assuming that  the corresponding offspring generating function $f(s)$
+Assume that the  generating function $f(s)$ of the offspring distribution
 	is of the form
@@
 \]
-	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$, then
+	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$.
+%YX , then
+Then
 \[ \label{eq: extinction probability of critical GW process without 2rd moment}
@@
 	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
-	%Denote by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
 	 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the corresponding offspring probability generating function,
-	%and  by $\mathbf F_n(\mathbf s), \quad n>1$ its iterates.
 	and  by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
@@
 \[\label{eq: regularly varying condition for multitype branching process}
-	%\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u
 	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
@@
 	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and
-	%the matrix $E(\mathbf s)$ is defined by
 	the matrix $G(\mathbf s)$ is defined by
@@
 	\mathbf 1 - \mathbf F(\mathbf s)
-	%= (M - E(\mathbf s))(\mathbf 1 - \mathbf s),
 	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
@@
     Let
-    %$a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, 
     $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$,
@@
 \]
-%new
-    where $\mathbf z^{(\alpha)}$ is Zolotarev's random variable with index $\alpha$. 
-%end new
+  %YX  where $\mathbf z^{(\alpha)}$ is a Zolotarev's random variable with index $\alpha$.
+  where $\mathbf z^{(\alpha)}$ is a random variable with  Zolotarev's distribution with index  $\alpha$.
 	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
@@
 	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
-%deleted	
-	%(see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
-%end deleted
 When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite[Theorem~4.2]{AsmussenHering1983Branching} for critical branching Markov processes.
-%deleted    
-    %see \cite[Theorem 4.2]{AsmussenHering1983Branching}.
-%end deleted
 
@@
     $\psi$, the branching mechanism of the superprocess,
-    %is function $\psi$ on $E \times [0,\infty)$ of the form
     is a function on $E \times [0,\infty)$ of the form
@@
 	a class of critical superprocesses with general branching mechanism and general spatial motions:
-	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$.
+	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from 
+%YX a measure $\mu$.
+a finite measure $\mu$ on $E$.
 	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition,
@@
 \]
+%YX new added
+For any finite measure $\mu$ on $E$ and
+any measurable function $f$ on $E$, we use $\langle f,\mu\rangle$	 to denote the integral of $f$ with respect to $\mu$. 
+Put $\|\mu\|=\langle 1, \mu\rangle$.
+%end new
 	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
 \[\label{eq: Kolmogorov type result with 2rd moment}
-	t \mathbf P_\mu(X_t \not \equiv 0)
-	\xrightarrow[t\to \infty]{} c^{-1} \langle \phi, \mu \rangle_m,
+%Yx in the following "X_t \not \equiv 0" is replaced by "\|\mu\|\neq 0" without noticing
+	t \mathbf P_\mu(\|X_t\| \neq 0)
+	\xrightarrow[t\to \infty]{} c^{-1} 
+%YX \langle \phi, \mu \rangle_m,
+\langle \phi, \mu \rangle,
 \]
@@
 \[\label{eq: Ygalom type result with 2rd moment}
-	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot | X_t \not\equiv 0)\}
+	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot |\|X_t\| \neq 0)\}
 	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
@@
 	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
+%YX new added
+$\langle\cdot, \cdot \rangle$ denotes the inner product in $L^2(E, m)$;
+%end new
 	$\mathbf e$ is an exponential random variable with mean $1$;
 	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
-	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
+	In \cite{RenSongSun2017Spine},  we %YX also
+provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
 
@@
 	A simpler
-	version of this question has already been answered in the context of continuous-state branching processes %(CSBP) 
+	version of this question has already been answered in the context of continuous-state branching processes
 	(CSBPs)
@@
 	Kyprianou \cite{Kyprianou2008Continuous} considered
-	%CSBP's $(Y_t)$ 
-	CSBPs $\{(Y_t); P\}$
+	CSBPs $\{(Y_t)_{t\geq 0}; P\}$
 	with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
@@
 \]
-%new
-    where $\mathbf z^{(\gamma - 1)}$ is Zolotarev's random variable with index $\gamma - 1$.
-%end new
+    where $\mathbf z^{(\gamma - 1)}$ is
+    %a Zolotarev's random variable with index $\gamma - 1$.
+    a random variable with Zolotarev's distribution with index $\gamma - 1$.
 	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
-	%CSBP's 
-	CSBPs $\{(Y_t); P\}$
+	CSBPs $\{(Y_t)_{t\ge 0}; P\}$
 	with branching mechanism
@@
 	In order for the left side of \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for
-	%some positive function $(\lambda_t)$,
 	some positive constants $(\lambda_t)_{t\geq 0}$,
@@
 	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and
-	%is regularly varying with index $\frac{1}{\gamma_0 - 1}$ at $\infty$..
 	is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
@@
 \[
-	\mathbf P_{\delta_x}( X_t \not \equiv 0)
+	\mathbf P_{\delta_x}( \|X_t\| \neq0)
 	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
@@
 \[\label{eq: result2}
-	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
+	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \}
 	\xrightarrow[t\to \infty]{\operatorname{law}}
@@
 \]
-	%where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
 	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a Zolotarev's random variable with index $\gamma_0 - 1$.
 	Precise statements of the assumptions and the results are presented in the next
-	%subsection.
 		section.
-    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ 
-    %depend 
-    depends primarily on the lowest index $\gamma_0$.
+    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$   depends primarily on the lowest index $\gamma_0$.
 
@@
 	For simplicity, we write
-	%$\mu(f)$ 
 		$\mu(f)$ and sometimes $\langle \mu, f\rangle$
@@
     to emphasize that it is the inner product
-    %in the Hilbert space $L^2(dm)$.
     in the Hilbert space $L^2(m)$.
-	%For any $\phi \in \mathscr E^+$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
 		For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
@@
 	We say a $\mathcal M^1_E$-valued Hunt process
-	%$\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ 
-	$\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$
+	%YX $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$
+    $X:=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$
 	is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
@@
 	P^\beta_tf(x)
-	%= 
 		:=
@@
 	= \mu(P^\beta_t f),
-	%\quad \mu \in \mathcal M_f, 
 	\quad \mu \in \mathcal M^1_E,
@@
 	As discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment}
-	%or \eqref{eq: Ygalom type result without 2rd moment}, 
 		or \eqref{eq: result2},
@@
 	This can be done under the following assumptions on the underlying motion
-	%$\{\xi; \Pi\}$:
-	$\{(\xi_t); (\Pi_x)\}$:
+	%YX $\{(\xi_t); (\Pi_x)\}$:
+    $\xi$:
 \begin{asp}{1}
@@
 \]
-	 $(p^\beta_t)$ is called the
-	\emph{density of semigroup $(P^\beta_t)$}.
-	%Define a family of kernels $(P^{\beta *}_t)_{t \geq 0}$ on $E$ by
+%YX	 $(p^\beta_t)$ is called the \emph{density of semigroup $(P^\beta_t)$}.
+    $(p^\beta_t)_{t\geq 0}$ is called the \emph{density of semigroup $(P^\beta_t)_{t\geq 0}$}.
 	Define the dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ by
@@
 	It is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that
-	%$(P^\beta_t)_{t \geq 0}$ and its dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ 
 	$(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$
@@
 	Moreover, for each
-	%$t\geq 0,x\in E$, 
 	$t\geq 0$ and $x\in E$,
@@
 	\mathbf P_\mu[X_t(\phi)]
-	= e^{\lambda t} \mu(\phi).
+%YX = e^{\lambda t} \mu(\phi).
+   = e^{\lambda t} \mu(\phi),
 \]
@@
 \begin{asp}{2} \label{asp: 2}
-	The superprocess $(X_t)$ is critical, i.e., $\lambda = 0$.
+%YX	The superprocess $(X_t)$ is critical, i.e., $\lambda = 0$.
+    The superprocess $X$ is critical, i.e., $\lambda = 0$.
 \end{asp}
 
-	Let $\varphi$ (resp.
-$\varphi^*$) be the principal eigenfunction of (resp.
-the dual of) the transition semigroup $(P_t)$ of the underlying process $\{\xi;\Pi\}$.
-Our second assumption on the underlying process $\{\xi; \Pi\}$ is the following:
+	Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the underlying process 
+%YX $\{\xi; \Pi\}$.
+    $\xi$.
+Our second assumption on the underlying process 
+%YX $\{\xi; \Pi\}$
+    $\xi$
+ is the following:
 
 \begin{asp}{3} \label{asp: 3}
-	$\varphi$ is bounded, and $(P_t)$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
+	$\varphi$ is bounded, and 
+%YX $(P_t)$ 
+    $(P_t)_{t\geq 0}$ 
+is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
 \end{asp}
 
-	Under Assumption \ref{asp: 3},	it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of Feyman-Kac semigroup $(P^\beta_t)$ is also bounded.
-	Moreover, $(P^\beta_t)$ is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
+	Under Assumption \ref{asp: 3},	it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of Feyman-Kac semigroup 
+%YX $(P^\beta_t)$ is also bounded.
+    $(P^\beta_t)_{t\geq 0}$ is also bounded.
+	Moreover, 
+%YX $(P^\beta_t)$ 
+$(P^\beta_t)_{t\geq 0}$ 
+is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
 	In fact, it is proved in \cite{KimSong2008Intrinsic} that for each $t>0$, $(p^\beta_t(x,y))_{x,y\in E}$ is comparable to $(\phi(x)\phi^*(y))_{x,y\in E}$ in the sense that there is a constant $c_t > 1$ such that
@@
     It is also shown in \cite{KimSong2008Intrinsic} that
-%deleted    
-    %$(e^{-\lambda t}p^\beta_t(x,y))_{x,y\in E}$ is,  uniformly in $x$ and $y$, asymptotically equivalent to $\big(\phi(x)\phi^*(y)\big)_{x,y\in E}$ as $t\to \infty$ in the sense that,
-%deleted
     there are constants $c_0, c_1 > 0$ such that
 \[\label{eq:q(t,x,y)}
-	%\sup_{x,y\in E} \big|\frac{e^{-\lambda t}p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \big| \leq c_0 e^{-c_1 t},
 	\sup_{x,y\in E} \big|\frac{p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \big| \leq c_0 e^{-c_1 t},
@@
 
-	%In this paper, we will only consider superprocesses with the following spatially dependent stable branching mechanism:
 		Our assumption on the branching mechanism is the following:
@@
 	The branching mechanism $\psi$ is of
-	% the following form:
 	the form:
@@
 	\item[(2)] For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$
-	%converges to $0$ as $t\to \infty$, and is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
-	converges to $0$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$, as $t\to \infty$.
+	converges to $0$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$
+%YX , 
+as $t\to \infty$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
 \[
-	\mathbf P_{\delta_x}(X_t \not \equiv 0)
+	\mathbf P_{\delta_x}(\|X_t\| \neq 0)
 	\stackrel[t\to \infty]{}{\sim} \phi(x)\eta_t.
@@
 \[
-	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
+	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot |\|X_t\| \neq 0) \}
 	\xrightarrow[t\to \infty]{\operatorname{law}}
@@
 \end{itemize}
-	%Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
-	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a Zolotarev's random variable with index $\gamma_0 - 1$
+	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is
+%a Zolotarev's random variable with index $\gamma_0 - 1$
+ a random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
 \end{thm}
@@
 
-	%In this paper, to establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition of  $\{X; \mathbf P\}$.
-	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use spine decomposition theorem for  $\{X; \mathbf P\}$:
+	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use spine decomposition theorem for  
+%YX $\{X; \mathbf P\}$:
+    $X$:
 	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
@@
 
-	%This idea 
 	Similar idea
 	has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
-	%Let $(Y_t)$ 
     Let $\{(Y_t)_{t\geq 0}; P\}$
@@
 	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation
-	satisfied by the survival probability $(t,x) \mapsto P(Y_t \not\equiv 0)$ is tricky.
+	satisfied by the survival probability
+%YX $(t,x) \mapsto P(Y_t \not\equiv 0)$ is tricky.
+$(t,x) \mapsto P_{\delta_x}(\|Y_t\| \neq 0)$ is tricky.
 	Instead, by using a spine decomposition approach, Powell \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principal eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capturing the uniform speed.
@@
 	Using the spine method, we show that the Laplace transform of
-	%the one-dimensional conditioned distributions 
 		the one-dimensional distributions
 	of the superprocess, after a proper rescaling,
-	%can also be 
-	can be
-	characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
+	can be 	characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
 	Then, the desired convergence of the distributions can be established by a comparison between the equations.	
@@
 
-	%A similar idea of establishing conditional weak convergence to the exponential distribution through a comparison of the equations satisfed by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
-	A similar idea of establishing weak convergence through a comparison of the equations satisfed by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
+		A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
 	We characterized the exponential distribution
-	%using an $x^2$-transform distribution equation; 
 		using its double size-biased transform;
@@
 	However, the
-	%$x^2$-transform of a random variable requires the existence of the second moment.
 	double-size-biased transform of a random variable requires its second moment being finite.
-	%Since we are not assuming the second moment condition, we can not use the method of $x^2$-transform.
 	Since in this paper, we do not assume the second moment condition, we can not use the method of double size-biased transform.
-	%Instead, a non-linear delay equation is used.
 
@@
     First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used to extend the result to
-    %a general functions $f$.
      more general testing functions.
-	%Since we are not assuming the second moment condition, this type of argument does not work in the present case.
 	However, in the present case, since we are not assuming the second moment condition, this type of argument does not work.
 	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for
-	%all general functions $f$ at the same time.
 		a large class of general testing functions at the same time.
-%deleted
-	%This generalized spine decomposition theorem considered the $X_T(g)$-transform of the superprocess $(X_t)_{0\leq t\leq T}$ for a large class of general functions $g$.
-	%The transformed process behaves similarly as in the classical case, despite the fact that the spine processes $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}\}$ are not consistent for all $T>0$.
-%end deleted
 
 	The rest of this paper is organized as follows:
-	In Section \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly varying functions and superprocesses, respectively.
-	In Section \ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem.
-	In Section \ref{sec: Ergodicity}, we discuss the ergodicity of the spine process.
-	In Section \ref{sec: proof of result 1} and \ref{sec: proof of result 2} we give the poof of Theorem \ref{thm: main theorem}(1) and \ref{thm: main theorem}(2), respectively.
-	In Section \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-	In Section \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize Zolotarev's distribution.
-	Finally, in Section \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
-
-\newpage
+%YX	In Section 
+    In Subsections
+\ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly varying functions and superprocesses, respectively.
+%YX In Section 
+In Subsection 
+\ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem.
+%YX In Section
+In Subsection 
+\ref{sec: Ergodicity}, we discuss the ergodicity of the spine process.
+%YX	In Section
+    In Subsections
+\ref{sec: proof of result 1} and \ref{sec: proof of result 2} we give the poof of Theorem \ref{thm: main theorem}(1) and \ref{thm: main theorem}(2), respectively.
+%YX	In Section
+    In Subsection
+\ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
+%YX	In Section
+    In Subsection
+\ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize Zolotarev's distribution.
+	Finally, 
+%YX	In Section
+    In Subsection
+\ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
+
+%YX \newpage
 \section{Preliminaries}
@@
 \label{sec: Asymptotic equivalence}
-	In this section, we give a lemma on asymptotic equivalence.	
+%YX	In this section, 
+  In this subsection, 
+we give a lemma on asymptotic equivalence.	
 	Let $t_0 \in [-\infty,\infty]$.
@@
 	L(t)
-	%= c(t) e^{\int_{t_0}^t \epsilon(u) \frac{du}{u}},\quad t\geq t_0,
 	= c(t) \exp\Big\{\int_{t_0}^t \epsilon(u) \frac{du}{u}\Big\},\quad t\geq t_0,
@@
 	The following lemma concerns the inverse of
-%({\bf I think that there is a little problem with the following lemma. When $f$ is invertible
-%but not monotone, its inverse is not the same as the generalized inverse	in 
-%\cite{BinghamGoldieTeugels1989Regular}. If we do not really use the general version, we can just give the monotone version.})
-%ZY: I agree. Let us only give the monotone version.
-    %an  reversible regularly varying function.
-    an invertible, monotone, regularly varying function.
-	In this paper, if a function $f$ is 
-	%reversible, 
-	invertible,
+  %YX  an invertible, monotone, regularly varying function.
+   an invertible, monotone and regularly varying function.
+	In this paper, if a function $f$ is 	invertible,
 	we write $f^{(-1)}$ for its inverse;
@@
 \]
-	%Further, if $f$ is invertible and monotone, then for each $\alpha > 0$ and $c > 0$, we have
 	Similarly, for each $\alpha > 0$ and $c > 0$, we have
@@
 \begin{proof}
-%deleted
-	%Let $f$ be invertible.
-%end delted
 If $\alpha>0$, then according to \cite[Theorem 1.5.12.]{BinghamGoldieTeugels1989Regular}, we have \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} is true.
@@
 	It is  easy to verify that
-	%$h$ is also invertible 
 	$h$ is invertible and monotone
@@
 	It is easy to verify that
-	%$g$ is also invertible with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
 	$g$ is invertible and monotone with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
@@
 
-	%Now, further assume that $f$ is invertible and monotone, and 
 	Now, assume that
@@
 
-%\subsubsection{Non-presistency}
-	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued cadlag paths on $[0,\infty)$.
+	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued 
+%YX cadlag 
+ c\`{a}dl\`{a}g 
+paths on $[0,\infty)$.
 	We refer to $\mathbb W$ as the
-	%\emph{canonical space of $X$}.
-	\emph{canonical space of $(X_t)$}.
-	%In fact, $X$ can be viewed 
+	\emph{canonical space of
+  %YX  $(X_t)$}.
+    $(X_t)_{t\geq 0}$}.
 	In fact, $(X_t)$ can be viewed
@@
 
-	%We say that $X$ is \emph{non-persistent} 
-	We say that $(X_t)$ is \emph{non-persistent}
-	if $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$ for all $x\in E$ and $t> 0$.
-	%Suppose that $X$ is non-persistent, 
+	We say that 
+%YX  $(X_t)$}
+    $(X_t)_{t\geq 0}$ 
+is \emph{non-persistent}
+	if $\mathbf P_{\delta_x}(\|X_t\|\neq 0) > 0$ for all $x\in E$ and $t> 0$.
 	Suppose that $(X_t)_{t\geq 0}$ is non-persistent,
@@
 	\item
-	$\mathbb N_x [ \forall t \geq 0, W_t \equiv 0] =0$, $\mathbb N_x[W_0 \not\equiv 0] = 0$;
+	$\mathbb N_x [ \forall t \geq 0, \|W_t\|=0] =0$, $\mathbb N_x[\|W_0 \|\neq 0] = 0$;
 	\item
@@
 	probability space with mean measure $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
-	then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\tilde X_0 := \mu$ and $\tilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+	then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
 \end{itemize}
@@
 	For the existence and further properties of such measures, we refer our readers to \cite{Li2011Measure-valued}.
-%deleted
-	%We mention that, in the literature, the Kuznestov measures are usually defined in the following space of excursion paths:
-%\[\begin{split}
-	%\mathbb W^{cad}_{0,ex}:=\{ &w: t \mapsto w_t \text{ is a right-continuous path from $(0,\infty)$ to $\mathcal M_E^1$}
-	%\\&\quad \text {having the null measure as a trap}\}.
-%\end{split} \]
-	%However, since the underlying process $\xi$ is a Hunt process, the Kuznestov measures can actually be carried on the space $\mathbb W$.
 
@@
 	\quad \mu \in \mathcal M_E^1, t>0,
-	%f\in bp\mathscr B_E.
 		f\in \mathscr B_b^+(E).
 \]
-	%Taking $\mu = \delta_x$ for some $x\in E$ and $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and then taking $\lambda \to \infty$, we can write
 	Taking $\mu = \delta_x$ for some $x\in E$, $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and taking $\lambda \to \infty$, we can write
@@
 	:= \lim_{\lambda\to \infty} V_t(\lambda\mathbf 1_E)(x)
-	= -\log \mathbf P_{\delta_x} [X_t \equiv 0]
-	= \mathbb N_x[W_t\not \equiv 0],
+	= -\log \mathbf P_{\delta_x} [\|X_t\|=0]
+	= \mathbb N_x[\|W_t\|\neq 0],
 	\quad t\geq 0, x\in E.
@@
 \[ \label{eq: equation for mu v-t}\begin{split}
-    \mathbb N_\mu[W_t\not \equiv 0]
-	&= -\log \mathbf P_{\mu} [X_t \equiv 0]
+    \mathbb N_\mu[\|W_t\|\neq 0]
+	&= -\log \mathbf P_{\mu} [\|X_t\|=0]
 	= \lim_{\lambda \to \infty} (- \log \mathbf P_\mu [e^{-\lambda X_t(\mathbf 1_E)}])
@@
     see \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
-%deleted    
-    %The we see that $\{(X_t(\phi))_{t\geq 0};\mathbf P_{\mu}\}$ is nonnegative martingale,  and $\{(W_t(\phi))_{t\geq 0};\mathbb N_{\mu}\}$ is also a nonnegative martingale.
-%end delted
 
@@
 	\emph{The spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is
-	%the $g(\xi_T) e^{-\int_0^T \beta(\xi_s)ds}$-transform 
 	the $g(\xi_T) \exp\{-\int_0^T \beta(\xi_s)ds\}$-transform
@@
 	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$
-	%with \emph{mean measure}
 	with density
@@
     Also notice that $\mathbb N_\mu$ is not a probability measure, but after the transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
-	Since $\mathbb N_{\mu}(W_0 \not \equiv 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(W_0 \equiv 0) = 1$.
-	%Note that $\Pi_{\mu}$ is not typically a probability measure. 
+	Since $\mathbb N_{\mu}(\|W_0\|\neq 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(\|W_0\|= 0) = 1$.
 	Similarly, $\Pi_{\mu}$ is not typically a probability measure,
 	but after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
-    %We claim that
      We verify that
@@
 	\Pi_{\mu}^{(T,g)} [ f(\xi_0) ]
-	%= \mu(P^\beta_Tg)^{-1}\Pi_{\mu}[g(\xi_T) e^{-\int_0^T\beta(\xi_s)ds } f(\xi_0) ]
 	&= \frac{1}{\mu(P^\beta_Tg)}\Pi_{\mu}\Big[g(\xi_T) \exp\Big\{-\int_0^T \beta(\xi_s)ds \Big\} f(\xi_0) \Big]
@@
 	Therefore, the actual statement of the classical spine decomposition theorem is
-	%a little different 
 	different
 	from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}
-	%, and there is 
 	: There is
@@
 	Here, the probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of the process $(X_t)_{t\geq 0}$ is
-%deleted
-	%defined by
-%end delted
 \[
@@
 	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of the process $(W_t)_{t\geq 0}$ is
-%deleted	
-	%defined by
-%end deleted
 \[
@@
 	Let $\mu \in \mathcal M^{(\phi)}_\mu$, we say
-	%$\{(Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$ 
 	$\{(\xi_t)_{t\geq 0}, \mathbf n, (Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$
@@
 	\emph{The spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is
-%deleted	
-	%defined by
-%end deleted
 \[
@@
 	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with
-    %\emph{mean measure}
    density
@@
 	If $\mu = \delta_x$ for some $x\in E$, then by
-	%Remark \ref{rem: initial configuration of transformed process}
 	\eqref{eq: initial distribution of spine}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$.
@@
 
-%\subsection{Ergodicity of the spine process $\{\xi; \Pi^{(\phi)}_x\}$}
 \subsection{Ergodicity of the spine process}
@@
 	In this subsection, we discuss the ergodicity of the spine processes
-	%$\{\xi; \Pi^{(\phi)}_x\}$ 
 	$\{(\xi_t); (\Pi^{(\phi)}_x)\}$
 	under Assumptions \ref{asp: 1}--\ref{asp: 3}.
-	%One can check that $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
 	According to \cite{KimSong2008Intrinsic}, $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
@@
 	For each $(y,u,t)\in E\times [0,1]\times [0,\infty)$, define $\bar F(y,u,t) := \sup_{s:s\geq t} F(y,u,s)$.
-	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$ with
+	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$
+%YX with
+such that
 \[
@@
 \]
-	%Therefore it follows from Lemma \ref{lem: ergodicity of the underlying process} that
 	From Lemma \ref{lem: ergodicity of the underlying process}, we know that
@@
 	%noting that that
-	notice that
+	%YX notice that
+     noting that that
 	$0\leq F \leq \bar F$, we get
@@
 \label{prop: non-presistent}
-	For each $t > 0$, $\inf_{x\in E} \mathbf P_{\delta_x}(X_t \equiv 0) > 0$.
+	For each $t > 0$, $\inf_{x\in E} \mathbf P_{\delta_x}(\|X_t\|= 0) > 0$.
 \end{prop}
@@
 \begin{proof}
-    %new added
       Recall that $\kappa_0 : = \text{essinf}_{m(dx)} \kappa(x) $ and $\gamma_0 := \text{essinf}_{m(dx)} \gamma(x)$.
-%end new added
 For each $x\in E$, let $\tilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\tilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$.
-%	Then, we know that $\tilde \kappa = \kappa$ and $\tilde \gamma = \gamma$ almost everywhere with respect to the measure $m$.
     Then, we know that $m(\tilde \kappa \neq \kappa) = 0$ and $m(\tilde \gamma \neq \gamma) = 0$.
@@
 
-	%Therefore, 
 	If we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
@@
 \]
-	So, %we can view 
-	we can consider
+	So, we can consider
 	$\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
@@
 	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent,
-%new added
     i.e.
 \[
-    \mathbf P_{\delta_x}(X_t \equiv 0) 
+    \mathbf P_{\delta_x}(\|X_t\| = 0)
     > 0,
@@
 \]
-%end new added
 	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have
 \[
-    \mathbf P_{\delta_x}(X_t \equiv 0)<1,
+    \mathbf P_{\delta_x}(\|X_t\|= 0)<1,
     \quad t>0, x \in E.
 \]
-	%Therefore, 
 	From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$.
-	%According to \eqref{eq:mean-fkpp}, 
 	According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp},
@@
 
-	%Note that, 
 		Notice that,
 	under the Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
-	%Therefore, we have $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
 	Therefore, $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
 
-	%Then, according to \eqref{eq:langleVtfphiranglem_equation}
 	According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and monotone convergence theorem,
@@
 \]
-	One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example, %$\phi^{-1}v_t$ converges to $0$ uniformly when $t\to\infty$.
+	One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example,
 \[\label{eq: uniform converges to 0}
@@
 \]
-	%Therefore, it is natural to look for the speed of this convergence.
 	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only have to consider the speed of this convergence.
@@
 
-	%Note that 
 	Notice that
@@
 	For each $\mu\in\mathcal M^\phi_E$, denote by
-	%$\{(Y_t)_{t\geq 0}, (\xi_t)_{t\geq 0},\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ 
 	$\{(Y_t), (\xi_t),\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$
 	the spine representation of $\mathbb N^{(\phi)}_\mu$.
-	%According to \eqref	{eq: equation for mu v-t} and Theorem \ref{thm: spine representation}, 
 	According to \eqref	{eq: equation for mu v-t}, \eqref{eq: mean of kuz measure} and Theorem \ref{thm: spine representation},
@@
 	= \mathbb N_\mu[W_t(\phi)] \mathbb N^{W_t(\phi)}_\mu [W_t(\phi)^{-1}]
-	%= \mathbb N_\mu[W_t(\phi) > 0]
 	= \mathbb N_\mu(W_t(\phi) > 0)
-	%= \langle \mu,v_t \rangle.
 	= \mu(v_t).
@@
 	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$,
-	%one can check that
 	we verify that
@@
 	Let  $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}.
-	%Using an argument similar to that used in the proof of \cite[Lemma 5.3]{RenSongSun2017Spine}, we can get that, if $t_0>1$,
 	We claim that
@@
 	\leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m,
-%new
     \quad t_0 > 1.
-%end new
 \]
@@
 \]
-
-	%In fact, we have
-	In fact, using the Markov property of the spine process $(\xi_t)$, and the property of the Poisson random measure, we have 
+	In fact, using the Markov property of the spine process $(\xi_t)$, and the property of the Poisson random measures, we have
 \[\label{eq:epsilon-2}\begin{split}
@@
 \end{split}\]
-	%Therefore, by Campbell's formula, while $t-t_0 \geq s_0$,
-	Therefore, while $t-t_0 \geq s_0$, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have 
+	%YX Therefore, while $t-t_0 \geq s_0$, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have
+Therefore, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have,  for $t-t_0 \geq s_0$,
 \[\begin{split}
@@
 	\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]\big)
-	%\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
+	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
 	=  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
-	%= -\log \lim_{\lambda \to \infty}
 	\\&\quad = -\log \lim_{\lambda \to \infty}
-	%\exp(- \mathbf m^\xi [ 1-e^{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)}  ])
 	\exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
-	%\\&\quad = \mathbf m^\xi [\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0}]
 	\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0} \mathbf m^\xi(ds,dw)
@@
 \end{split}\]
-	%Then combining \eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-final} and \eqref{eq:firstpart-of-Y}, we arrive at \eqref{eq:upperbound_of_epsilon-2}.
-	Combine this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
-
-	Now, for each $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, 
-	%according to \eqref{eq: starting point of phi-1v_t(x)} and \eqref{eq: some equations for PY-1}, we have
+	%YX Combine this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
+Combining this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
+
+%YX	Now, for each
+Now, for
+$0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough,
 	according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1}, \eqref{eq: bound for epsilon1} and \eqref{eq:epsilon-2-final}, we have
@@
 	&\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty}
-	%\cdot \|\phi^{-1}v_{t-s}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
 	\cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
 \end{split}\]
-	%Since $\phi^{-1}v_s$ converges to $0$ uniformly as $s\to \infty$, 
 	According to \eqref{eq: uniform converges to 0},
@@
 \]
-	%Note that
 	Notice that
@@
 	From \eqref{eq: equation of <vt,phi>} we know that $\langle v_t,\phi^* \rangle_m$ is continuous and strictly decreasing in $t \in (0,\infty)$.
-	%Since $X$ 
 	Since the superprocess $(X_t)_{t\geq 0}$
@@
 	On the other hand,
-	%since $\phi^{-1}v_t$ converges to $0$ uniformly in $E$, 
 	according to \eqref{eq: uniform converges to 0},
 	we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
-	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$ which we denote by 
-	%$R : (0,\infty) \to (0,\infty)$.
+	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$
+%YX which we denote by
+which is denoted by
 \[
@@
 \]
-	%This implies that
 	Since $R$ is the inverse of $t\mapsto \langle v_t,\phi^*\rangle$, the above implies that
@@
 
-	We are interested in checking the regularly varying property of $R(r)$ at 
-	%$ 0$.
-	$r=0$.
+	We are interested in checking the regularly varying property of $R(r)$ at $r=0$.
 	This can be done by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at
-	%$0$.
 	$u = 0$.
-    %In fact, according to Proposition \ref{prop: convergence in a same speed},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$. 
     According to \eqref{eq: epsilon R converges to 0},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$.
@@
 \end{split}\]
-	%According to Lemma \ref{lem:regularly_variation_and_integration}, this implies that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
-	According to Lemma \ref{lem:regularly_variation_and_integration}, and the fact that $\kappa(x)\phi(x)^\gamma(x)$ is bounded and measure $\phi^* dm$ is finite, we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
-	%According to Corollary \ref{cro: power law and ingetration}, this implies that $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
+	According to Lemma \ref{lem:regularly_variation_and_integration},
+%YX and the fact that
+ and using the fact that
+$\kappa(x)\phi(x)^\gamma(x)$ is bounded and measure $\phi^* dm$ is finite, we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
 	Notice that $-\gamma_0 < 0$, according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
@@
 
-	%Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration}, we know that
 	Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration} and \eqref{eq: regularly part in the integration}, we know that
@@
 	Now according to
-	%Corollary \ref{cro: power law and ingetration} 
 	Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}
@@
 	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from
-	%\eqref{eq: inverse and power equivalent with alpha < 0},
 	\eqref{eq: inverse and power equivalent with alpha < 0} and above,
@@
 
-%\subsection{Characterization of the conditional distribution}
 \subsection{Characterization of the one dimensional distribution}
 \label{sec: conditional distribution}
-	%Let $\{X; \mathbf P\}$ be a superprocess satisfies
-	Let $\{(X_t)_{t\geq 0}; \mathbf P\}$ be a superprocess satisfies
+	Let $\{(X_t)_{t\geq 0}; \mathbf P\}$
+    %YX  be a superprocess satisfies
+    be a superprocess which satisfies
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
 	Suppose that $m(x: \gamma(x) = \gamma_0)>0$.
-	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | X_t \not \equiv 0\big)\big\}$
+	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | \|X_t\| \neq 0\big)\big\}$
 	converges weakly
@@
  \[
- 	\mathbf P_{\delta_x}[\eta_t X_t(f)|X_t \not \equiv 0]
-	= \frac{\mathbf P_{\delta_x}[\eta_t X_t(f) \mathbf 1_{X_t \not \equiv 0}]} {\mathbf P_{\delta_x}(X_t \not \equiv 0) }
-	= \frac{\eta_t}{\mathbf P_{\delta_x}(X_t \not \equiv 0)} P^\beta_t f(x)
+ 	\mathbf P_{\delta_x}[\eta_t X_t(f)|\|X_t\|\neq 0]
+	= \frac{\mathbf P_{\delta_x}[\eta_t X_t(f) \mathbf 1_{\|X_t\|\neq 0}]} {\mathbf P_{\delta_x}(\|X_t\|\neq 0) }
+	= \frac{\eta_t}{\mathbf P_{\delta_x}(\|X_t\|\neq 0)} P^\beta_t f(x)
 	\stackrel[t\to \infty]{}{\sim}  \langle f,\phi^* \rangle_m.
@@
 
- 	From the Laplace transform point of view, the desired result that $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$
+%YX 	From the Laplace transform point of view, 
+From the point of Laplace transform,
+ the desired result that $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$
  converge weakly
@@
 \[\begin{split}
- 	&\frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\eta_t}
-	= \frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\mathbf P_{\delta_x}(X_t \not \equiv 0)} \frac{ \mathbf P_{\delta_x}(X_t \not \equiv 0) } { \eta_t }
-	= \mathbf P_{\delta_x}[1-e^{-\theta \eta_t X_t(f)}| X_t \not \equiv 0]  \frac{ \mathbf P_{\delta_x}(X_t \not \equiv 0) } { \eta_t }
-	\\&\quad \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
+ 	\frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\eta_t}
+	&= \frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\mathbf P_{\delta_x}(\|X_t\|\neq 0)} \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }\\
+	&= \mathbf P_{\delta_x}[1-e^{-\theta \eta_t X_t(f)}|\|X_t\|\neq 0]  \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }
+	\\& \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
 \end{split}\]
@@
 	Therefore, to
-	establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
+	establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
 
@@
 \begin{prop}
-	%For any $f\in pb\mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we 
 	For any $f\in \mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we have
@@
 	V_T ( \theta f) ( x)
-	%= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr.
 	= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr.
@@
 	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$,
-	%then by Campbell's formula and \eqref{eq: definition of Gamma function}, we have
 	then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
@@
 	\dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
-	%\\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \big[e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds}\big] dr
 	 \\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \Big[\exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds\Big\}\Big] dr
-	%\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } e^{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds} \Big] dr,
 	\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr,
@@
 	&\frac{V_T(\theta \eta_T f)(x)}{\eta_T}
-	%= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
 	\\&\quad= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
-	%\\&\quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  e^{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds}\Big] dr
 	\\&\quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
-	%\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} e^{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du}\Big] dr.
 	\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} \exp\Big\{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du\Big\}\Big] dr.
@@
 
-	Recall that a non negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
+	Recall that a 
+%YX non negative 
+  non-negative 
+random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
 \[
@@
 	G( \theta)
-	%= \int_0^\theta e^{ - \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1} })^{\gamma_0 - 1}\frac{du}{u} } dr,
 	 = \int_0^\theta \exp\Big\{ - \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1} })^{\gamma_0 - 1}\frac{du}{u} \Big\} dr,
@@
 	G(\theta)
-	%= \big(\frac{1}{1+\theta^{-(\gamma_0 - 1)}}\big)^{\frac{1}{\gamma_0 - 1}},
 	= \Big(\frac{1}{1+\theta^{-(\gamma_0 - 1)}}\Big)^{\frac{1}{\gamma_0 - 1}},
@@
 	If $f$ is a measurable function which is $L^p$ integrable on the
-	%measurable space 
 	measure space
@@
 	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
-	%This, however, contradicts the definition of $\rho$.
 	This, however, contradicts \eqref{eq: definition of rho}.
-%deleted
-    %The proof is complete.
-%end deleted
 \end{proof}
@@
 \[\begin{split}
-	%& \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}} dr
 	 & \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}\Big\} dr
-	%\\&\quad = \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 \frac{du}{u+r^{-(\gamma_0 - 1)}} } dr
 	\\&\quad = \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 \frac{du}{u+r^{-(\gamma_0 - 1)}} \Big\} dr
-	%= \int_0^\theta e^{- \frac{\gamma_0} {\gamma_0 - 1} \log\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} } } dr
 	= \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \log\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} } \Big\} dr
@@
 	We claim that the non-negative function $F$ satisfies
-	%the following equation:
 	the following inequality:
@@
 	On the other hand, according to \eqref{eq: equation for the distribution},
-	%we have that $G(\theta) \leq c\theta$ and $G_0(\theta) \leq c \theta$.
 	we have that $G(\theta) \leq \theta$ and $G_0(\theta) \leq \theta$.
 	Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
-	%Finally, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
 	Therefore, according to Lemma \ref{lem: F is zero} and \eqref{eq: inequality of F(theta)}, we have $F \equiv 0$ as desired.
@@
 \]
-	%The underlying idea is to make a comparison between \eqref{eq: equation for normalized V_T} and \eqref{eq: equation for the distribution}.
-
-	%In fact, from Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we can rewrite the equation for $G$:
-	From Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we have an equation for $G$:
+
+	From Lemma \ref{lem: characterize the general Mittag-Leffler distribution},
+%YX we have an equation for $G$:
+we have that $G$ satisfies
 \[\label{eq: equation for G}
@@
 \]
-	%According to \eqref{eq: equation for normalized V_T}, we can rewrite the equation for $g$:
-	According to \eqref{eq: equation for normalized V_T}, we have an equation for $g$:
+	According to \eqref{eq: equation for normalized V_T},
+ %YX we have an equation for $g$:
+  we know that $g$ satisfies that
 \[\label{eq: equation for g}
@@
 	Step 1:
-	%We will give some upper bounds for $G,g, J_G, J'_G, J_g$ and $J'_g$ respectively.
 	We will give upper bounds for $G,g, J_G, J'_G, J_g$ and $J'_g$ respectively.
@@
 \]
-	%From \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
 	From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have
@@
 \end{split}\]
-	%From \eqref{eq: definition of J'_g}, \eqref{eq: upper bound for g} and the definition of $\eta_t$, we have
 	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have
@@
 	J'_g(t,r,\xi)
-%new	
 	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} (c_f ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
-%end new
 	\\&\leq \gamma_0(\gamma_0 - 1) c_f^{\gamma_0 - 1}r^{\gamma_0 - 1} \|  \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \|_\infty \int_0^1 t \big( C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
@@
 \end{split}\]
-	%From \eqref{eq: definition of J'_G}, \eqref{eq: upper bound for G} and the definition of $\eta_t$, we have
 	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have
@@
 	J'_G(t,r,\xi)
-%new	
 	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} (ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
-%end new
 	\\&\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
@@
 	Notice that,
-	%by \eqref{eq: asymptotic for q_t(x,y)},
 	by \eqref{eq:q(t,x,y)}
@@
 	Step 4: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_2(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
-	%We first note that, for each $t\geq 0$ and $r\geq 0$,
 	Notice that, according to \eqref{eq: definition for J_G} and \eqref{eq: definition of J'_G}, for each $t\geq 0$ and $r\geq 0$,
@@
 \end{split}\]
-	%We then note that, 
 	Also notice that,
@@
 \]
-	%We first note that, 
 	Notice that,
@@
 \]	
-	%We then note that, from the definition of $J'_G, J'_g$ and $\eta_t$, we have
 	From the definition of $J'_G, J'_g$ and $\eta_t$, we have
@@
 	since it is a bounded Borel function on $E\times (0,1) \times [0,\infty)$.
-	Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process},  \eqref{eq: differences between J'_G and J'_g} and the definition of $M(r,x), M(r)$ and $C_X$, we have
+	Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process},  \eqref{eq: differences between J'_G and J'_g} and 
+%YX the definition of
+    the definitions of  
+$M(r,x), M(r)$ and $C_X$, we have
 \[\label{eq: limsup of J_G - J'_g}\begin{split}
@@
 \]
-	%according to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
 		According to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
 %%%----Versions-----------------------------
+%stable-limit5.tex 2018/6/22  by
 %stable-limit4.tex 2018/6/21  by Yanxia-------
@@
 \usepackage{autonum}
+%new
+\usepackage{amsmath}
+%end new
 \newtheorem{thm}{Theorem}[section]
@@
 \numberwithin{equation}{section}
+%new
+\allowdisplaybreaks
+%end new
 
@@
 \subsection{Background}
-    The study of the asymptotic behavior of critical branching particle systems has a long history.
+%    The study of the asymptotic behavior 
+   The study of the asymptotic behaviors
+    of critical branching particle systems has a long history.
 	It is well known that for a critical Galton-Watson
-    %process $(Z_n)$,
-    %YX process $\{(Z_n)_{n = 0,1,\dots}; P\}$,	
     process $\{(Z_n)_{n\geq 0}; P\}$,	
@@
 
-    %YX Notice that, see \cite{KestenNeySpitzer1966The-Galton-Watson} for example,
      Notice that,
     \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid
-  %YX    even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
    even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
     In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate,
-    %YX so a more appropriate scaling is needed.
-    and then  more appropriate scalings are needed.
-	%YX This was first obtained
-Research in this direction was first gaven
+%    and then  more appropriate scalings are needed.
+   and thus more appropriate scalings are needed.
+%Research in this direction was first gaven
+Research in this direction was first conducted 
 by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
-	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson
-	%process $(Z_n)$
-	%YX process $\{(Z_n)_{n = 0,1,\dots}; P\}$
+	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite 
+%	variance:  Consider a critical Galton-Watson
+	variance. The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson
     process $\{(Z_n)_{n\geq 0}; P\}$
 	with infinite variance.
-%YX	Assuming that  the corresponding offspring generating function $f(s)$
 Assume that the  generating function $f(s)$ of the offspring distribution
@@
 \]
-	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$.
-%YX , then
+%	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$.
+where $\alpha\in (0, 1]$ and $l$ is a function slowly varying at $0$.
 Then
@@
 \]
-	where $L$ is a slowly varying function at $\infty$, and
+%	where $L$ is a slowly varying function at $\infty$, and
+	where $L$ is a function slowly varying at $\infty$, and
 \[\label{eq: conditional distribution of critical GW process without 2rd moment}
@@
 	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
-	Slack \cite{Slack1972Further} considered the converse of this problem:
-	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must be of  the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
+%	Slack \cite{Slack1972Further} considered the converse of this problem:
+	Slack \cite{Slack1972Further} also considered the converse of this problem:
+%	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have 
+	In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have
+	a non-degenerate weak limit, 
+%	the offspring generating function must be of  
+    the generating function of the offspring distribution must be of  
+	the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
 	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.
 
-	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment condition:
+	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment 
+%	condition:
+    condition. Their main result can be stated as follows. 
 	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
-	 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the corresponding offspring probability generating function,
+	 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ 
+%	 the corresponding offspring probability generating function,
+     the generating function of the offspring distribution,
 	and  by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
-	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right principal  eigenvectors respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
+	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be 
+%	its left and right principal  eigenvectors respectively, 
+	its left and right  eigenvectors, respectively, 
+	corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
 	Suppose that
@@
 	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
-	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha,
+	\xrightarrow[n\to \infty]{} 
+	%(\mathbf i \cdot \mathbf u)^\alpha / \alpha,
+	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
 \]
@@
 \]
-  %YX  where $\mathbf z^{(\alpha)}$ is a Zolotarev's random variable with index $\alpha$.
   where $\mathbf z^{(\alpha)}$ is a random variable with  Zolotarev's distribution with index  $\alpha$.
-	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
+	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} 
+%	has a non-degenerate weak limit, 
+   to have a non-degenerate weak limit, 
+	one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
 	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time mutitype critical Galton-Watson processes.
@@
 	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to
-	a class of critical superprocesses with general branching mechanism and general spatial motions:
+	a class of critical superprocesses with general branching mechanism and general spatial 
+	%motions:
+	 motions. The main results of \cite{RenSongZhang2015Limit} are as follows.
 	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from 
-%YX a measure $\mu$.
 a finite measure $\mu$ on $E$.
@@
 \]
-%YX new added
 For any finite measure $\mu$ on $E$ and
@@
 Put $\|\mu\|=\langle 1, \mu\rangle$.
-%end new
 	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
 \[\label{eq: Kolmogorov type result with 2rd moment}
-%Yx in the following "X_t \not \equiv 0" is replaced by "\|\mu\|\neq 0" without noticing
 	t \mathbf P_\mu(\|X_t\| \neq 0)
 	\xrightarrow[t\to \infty]{} c^{-1} 
-%YX \langle \phi, \mu \rangle_m,
 \langle \phi, \mu \rangle,
@@
 	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
-%YX new added
-$\langle\cdot, \cdot \rangle$ denotes the inner product in $L^2(E, m)$;
-%end new
+%$\langle\cdot, \cdot \rangle$ denotes the inner product in $L^2(E, m)$;
+$\langle\cdot, \cdot \rangle_m$ denotes the inner product in $L^2(E, m)$;
 	$\mathbf e$ is an exponential random variable with mean $1$;
 	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
-	In \cite{RenSongSun2017Spine},  we %YX also
+	In \cite{RenSongSun2017Spine},  we 
 provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
@@
     where $\mathbf z^{(\gamma - 1)}$ is
-    %a Zolotarev's random variable with index $\gamma - 1$.
     a random variable with Zolotarev's distribution with index $\gamma - 1$.
@@
 \]
-	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
+%	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
+	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
 It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
@@
 	satisfying Grey's condition.
-	In order for the left side of \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for
+	In order for the left side of \eqref{eq: conditional limit of CSBP} 
+%	has non-trivial weak limit for
+    to have a non-trivial weak limit for
 	some positive constants $(\lambda_t)_{t\geq 0}$,
@@
 	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and
-	is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
+	is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
 	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
@@
 \]
-	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a Zolotarev's random variable with index $\gamma_0 - 1$.
+	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a
+%	Zolotarev's random variable with index $\gamma_0 - 1$.
+random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
 	Precise statements of the assumptions and the results are presented in the next
-		section.
-    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$   depends primarily on the lowest index $\gamma_0$.
+%		section.
+    subsection.
+    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess 
+%    $(X_t)$   
+   $\{X; \mathbf P\}$
+    depends primarily on the lowest index $\gamma_0$.
 
@@
    $\xi:=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$
-	be a $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by
+%	be a $E$-valued Hunt process with its lifetime denoted by $\zeta$, 
+	be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, 
+	and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by
 	\eqref{eq: branching mechanism}.
-	We say a $\mathcal M^1_E$-valued Hunt process
-	%YX $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$
+%	We say a $\mathcal M^1_E$-valued Hunt process
+	We say an $\mathcal M^1_E$-valued Hunt process
     $X:=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$
@@
 	\]
-	This mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
+%	This mean semigroup plays a central role in the study of the 
+    The  mean semigroup plays a central role in the study of the 
+	asymptotic behavior of superprocesses.
 	As discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment}
@@
 	we have to establish the asymptotic behavior of the mean semigroup first.
-	This can be done under the following assumptions on the underlying motion
-	%YX $\{(\xi_t); (\Pi_x)\}$:
+%	This can be done under the following assumptions on the underlying motion
+	This can be done under the following assumptions on the spatial motion
     $\xi$:
@@
 \]
-%YX	 $(p^\beta_t)$ is called the \emph{density of semigroup $(P^\beta_t)$}.
     $(p^\beta_t)_{t\geq 0}$ is called the \emph{density of semigroup $(P^\beta_t)_{t\geq 0}$}.
@@
 	\mathbf P_\mu[X_t(\phi)]
-%YX = e^{\lambda t} \mu(\phi).
    = e^{\lambda t} \mu(\phi),
@@
 \begin{asp}{2} \label{asp: 2}
-%YX	The superprocess $(X_t)$ is critical, i.e., $\lambda = 0$.
     The superprocess $X$ is critical, i.e., $\lambda = 0$.
@@
 	Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the underlying process 
-%YX $\{\xi; \Pi\}$.
     $\xi$.
-Our second assumption on the underlying process 
-%YX $\{\xi; \Pi\}$
+%Our second assumption on the underlying process 
+Our second assumption on the spatial process 
     $\xi$
@@
 	$\varphi$ is bounded, and 
-%YX $(P_t)$ 
     $(P_t)_{t\geq 0}$ 
@@
 	Under Assumption \ref{asp: 3},	it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of Feyman-Kac semigroup 
-%YX $(P^\beta_t)$ is also bounded.
     $(P^\beta_t)_{t\geq 0}$ is also bounded.
 	Moreover, 
-%YX $(P^\beta_t)$ 
 $(P^\beta_t)_{t\geq 0}$ 
@@
 \]
-	We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of underlying processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
+	We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of 
+%	underlying processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
+    processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
 
@@
 \end{split}\]
-	where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
+	where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
 \end{asp}
-	Here we used the definition of the Gamma function on the negative half line:
+	Here we use the definition of the Gamma function on the negative half line:
 \[\label{eq: definition of Gamma function}
@@
 	converges to $0$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$
-%YX , 
 as $t\to \infty$.
@@
 	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is
-%a Zolotarev's random variable with index $\gamma_0 - 1$
  a random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
@@
 
-	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use spine decomposition theorem for  
-%YX $\{X; \mathbf P\}$:
+	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for  
     $X$:
@@
 	Therefore, this size-biased transform can be viewed as a martingale change of measure.
-	Under the Assumptions \ref{asp: 1} and \ref{asp: 3},
+%	Under the Assumptions \ref{asp: 1} and \ref{asp: 3},
+	Under Assumptions \ref{asp: 1} and \ref{asp: 3},
 	the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process.
@@
     Let $\{(Y_t)_{t\geq 0}; P\}$
-	be a branching diffusion processes in a bounded domain with finite second moment.
+%	be a branching diffusion processes in a bounded domain with finite second moment.
+be a branching diffusion process, in a bounded domain,  with finite second moment.
 	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation
 	satisfied by the survival probability
-%YX $(t,x) \mapsto P(Y_t \not\equiv 0)$ is tricky.
 $(t,x) \mapsto P_{\delta_x}(\|Y_t\| \neq 0)$ is tricky.
 	Instead, by using a spine decomposition approach, Powell \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principal eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capturing the uniform speed.
-	Then, the problem is reduced to the study of a single ODE satisfied by the speed function $a(t)$.
+	Then, the problem is reduced to the study of a single ordinary differential equation satisfied by the speed function $a(t)$.
 	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of critical superprocesses with finite second moment.
-	In this paper, we will  generalize these arguments to a class of critical superprocesses without finite second moment, and establish Theorem \ref{thm: main theorem}(2).
+	In this paper, we will  generalize these arguments to a class of 
+%	critical superprocesses without finite second moment, 
+    general critical superprocesses without finite second moment, 
+	and establish Theorem \ref{thm: main theorem}(2).
 	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform of Zolotarev's distribution can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
@@
 	double-size-biased transform of a random variable requires its second moment being finite.
-	Since in this paper, we do not assume the second moment condition, we can not use the method of double size-biased transform.
+%	Since in this paper, we do not assume the second moment condition, 
+Since we do not assume the second moment condition in this paper,
+	we can not use the method of double size-biased transform.
 
 	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in \cite{RenSongSun2017Spine} and
-	\cite{RenSongZhang2015Limit} (for critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
+%	\cite{RenSongZhang2015Limit} (for critical superprocesses with finite variance), 
+	\cite{RenSongZhang2015Limit} (for general critical superprocesses with finite variance), 
+	the conditional weak convergence was proved in two steps.
     First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used to extend the result to
@@
 	The rest of this paper is organized as follows:
-%YX	In Section 
     In Subsections
 \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly varying functions and superprocesses, respectively.
-%YX In Section 
 In Subsection 
 \ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem.
-%YX In Section
 In Subsection 
 \ref{sec: Ergodicity}, we discuss the ergodicity of the spine process.
-%YX	In Section
     In Subsections
-\ref{sec: proof of result 1} and \ref{sec: proof of result 2} we give the poof of Theorem \ref{thm: main theorem}(1) and \ref{thm: main theorem}(2), respectively.
-%YX	In Section
+\ref{sec: proof of result 1} and \ref{sec: proof of result 2} we give the poofs of Theorem \ref{thm: main theorem}(1) and \ref{thm: main theorem}(2), respectively.
     In Subsection
 \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-%YX	In Section
     In Subsection
@@
 	Finally, 
-%YX	In Section
     In Subsection
@@
 
-%YX \newpage
 \section{Preliminaries}
@@
 \label{sec: Asymptotic equivalence}
-%YX	In this section, 
   In this subsection, 
@@
 	\stackrel[t\to t_0]{}{\sim}
-	\int_E f_1(t,x)m(dx)
+	\int_E f_1(t,x)m(dx).
 \]
@@
 	then we say $f$ is slowly varying.
-	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, if $L$ is a function which is slowly varying at $\infty$, then it can be written in the form
+	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, if $L$ is a function slowly varying at $\infty$, then it can be written in the form
 \[
@@
 	The following lemma concerns the inverse of
-  %YX  an invertible, monotone, regularly varying function.
-   an invertible, monotone and regularly varying function.
-	In this paper, if a function $f$ is 	invertible,
+%   an invertible, monotone and regularly varying function.
+    a strictly monotone, regularly varying function.
+%	In this paper, if a function $f$ is 	invertible,
+	In this paper, if a function $f$ is strictly monotone, 
 	we write $f^{(-1)}$ for its inverse;
@@
 \label{lem: regularly variation and inverse}
-	%Suppose that $f$ is a reversible map from $(0,\infty)$ to $(0,\infty)$.
-	Suppose that $f$ is an invertible, monotone map from $(0,\infty)$ to $(0,\infty)$.
+	Suppose that $f$ is 
+%	an invertible, monotone map 
+   a strictly monotone map 
+	from $(0,\infty)$ to $(0,\infty)$.
 	Then, for each $\alpha > 0$, we have
@@
 	It is  easy to verify that
-	$h$ is invertible and monotone
+%	$h$ is invertible and monotone
+   $h$ is strictly monotone
 	with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1}$.
@@
 	It is easy to verify that
-	$g$ is invertible and monotone with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
+%	$g$ is invertible and monotone 
+	$g$ is strictly monotone 
+	with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
 	Therefore,
@@
 	$f(t) \stackrel[t\to \infty]{}{\sim} c t^\alpha$ for some $\alpha > 0$ and $c > 0$, we want to show that $f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}$.
-	Notice that, since $\alpha >0$, we must have $f$ is non-decreasing.
+	Notice that, since $\alpha >0$, we must have $f$ is 
+%	non-decreasing.
+   strictly increasing.
 	From the definition of the asymptotic equivalence, we have, for each $\epsilon> 0$,
@@
 \]
-	which, by the non-decreasing nature of $f^{(-1)}$, gives that
+%	which, by the non-decreasing nature of $f^{(-1)}$, gives that
+	which, by the increasing nature of $f^{(-1)}$, gives that
 \[\label{eq: inverse and inequality}
@@
 	\limsup_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-	\leq \lambda ^{\gamma_0}.
+%	\leq \lambda ^{\gamma_0}.
+	\leq \lambda ^{\gamma_0}, 	\quad t\in (0,\infty).
 \]
@@
 	\xrightarrow[t\to 0]{} \lambda ^{\gamma_0 + \epsilon},
-	\quad \epsilon\in (0, \infty),
+%	\quad \epsilon\in (0, \infty),
+	\quad t\in (0, \infty),
 \end{split}\]
@@
 	\liminf_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-	\geq \lambda ^{\gamma_0}.
+%	\geq \lambda ^{\gamma_0}.
+	\geq \lambda ^{\gamma_0}, \quad t\in (0, \infty).
 \]
@@
 	= \lambda ^{\gamma_0},	
-	\quad \lambda \in (0,1].
+%	\quad \lambda \in (0,1].
+	\quad \lambda \in (0,1], t\in (0, \infty).
 \]
@@
 	= \big((\lambda^{-1})^{\gamma_0} \big)^{-1}
-	= \lambda ^{\gamma_0}.
-\]
-	This proved the first part of the Lemma.
+%	= \lambda ^{\gamma_0}.
+	= \lambda ^{\gamma_0}, \quad t\in (0, \infty).
+\]
+	This proved the first part of the lemma.
 
@@
 	\frac{\int_E t^{\gamma(x)} m(dx)}{t^{\gamma_0}}
-	\xrightarrow[t\to 0]{} m\{x:\gamma(x) = \gamma_0\}\in (0,\infty) .
+	\xrightarrow[t\to 0]{} m\{x:\gamma(x) = 
+	\gamma_0\}\in (0,\infty) .
 \]
@@
 \label{sec: Superprocesses}
-	In this section, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
+%	In this section, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
+In this subsection, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
 	It is known, see \cite[Theorem 2.23]{Li2011Measure-valued} for example, that \eqref{eq:FKPP_in_definition} can be written as
@@
 	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued 
-%YX cadlag 
  c\`{a}dl\`{a}g 
@@
 	\emph{canonical space of
-  %YX  $(X_t)$}.
     $(X_t)_{t\geq 0}$}.
@@
 	We say that 
-%YX  $(X_t)$}
     $(X_t)_{t\geq 0}$ 
 is \emph{non-persistent}
-	if $\mathbf P_{\delta_x}(\|X_t\|\neq 0) > 0$ for all $x\in E$ and $t> 0$.
+%	if $\mathbf P_{\delta_x}(\|X_t\|\neq 0) > 0$ for all $x\in E$ and $t> 0$.
+if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
 	Suppose that $(X_t)_{t\geq 0}$ is non-persistent,
@@
 \]
-	Taking $\mu = \delta_x$ for some $x\in E$, $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and taking $\lambda \to \infty$, we can write
+	Taking $\mu = \delta_x$ for some $x\in E$, $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, 
+%	and taking $\lambda \to \infty$, we can write
+   and letting $\lambda \to \infty$, we get
 \[ \label{eq: definition of v_t(x)}
@@
 \end{split}\]
-    It is know that for any $f\in bp{\mathscr B}$,
+%    It is know that for any $f\in bp{\mathscr B}$,
+   It is know that for any $f\in\mathscr B_b^+(E)$,
 \[\label{eq: mean of kuz measure}
@@
 	The second step of the theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
-	We say $\{(Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is \emph{the spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
+%	We say $\{(Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is \emph{the spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
+	We say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
 \begin{itemize}
 \item
-	\emph{The spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is
+	The \emph{spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is
 	the $g(\xi_T) \exp\{-\int_0^T \beta(\xi_s)ds\}$-transform
@@
 \item
-	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, \emph{the immigrate measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$
-	with density
+%	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, 
+Given $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, 
+%	\emph{the immigrate measure} 
+the \emph{immigration measure} 
+	$\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$
+%	with density
+	with intensity
 \[
@@
 	but after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
-     We verify that
+     We note that
 \[\begin{split}
@@
 	Now, suppose that $\{\xi; \Pi\}$ satisfies Assumption \ref{asp: 1}.
-	Denote by $\phi$ the principal eigenfunction of the mean semigroup of $X$.
+%	Denote by $\phi$ the principal eigenfunction of the mean semigroup of $X$.
+    Recall that $\phi$ is the principal eigenfunction of the mean semigroup of $X$.
 	The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, considered the case when $g = \phi$ only.
@@
 	$\{(\xi_t)_{t\geq 0}, \mathbf n, (Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$
-	is \emph{the spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
+%	is \emph{the spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
+	is a \emph{spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
 \begin{itemize}
 \item
-	\emph{The spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is
+	The \emph{spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is
 \[
@@
 	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with
-   density
+%   density
+    intensity
 \[\label{eq:meanMeasImmigr}
@@
 	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$
-%YX with
 such that
@@
 	Finally,
-	%noting that that
-	%YX notice that
      noting that that
@@
 \label{sec: proof of result 1}
-	Let $\{X; \mathbf P\}$ be a superprocess satisfying
+%	Let $\{X; \mathbf P\}$ be a superprocess satisfying
+	Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
-    In this section, we will prove the following stronger result:
+%    In this section, we will prove the following stronger result:
+   In this subsection, we will prove the following result stronger than non-persistency:
 
@@
 	For each $t > 0$, $\inf_{x\in E} \mathbf P_{\delta_x}(\|X_t\|= 0) > 0$.
+
 \end{prop}
@@
 \begin{proof}
-      Recall that $\kappa_0 : = \text{essinf}_{m(dx)} \kappa(x) $ and $\gamma_0 := \text{essinf}_{m(dx)} \gamma(x)$.
+      Recall that $\kappa_0 = \text{essinf}_{m(dx)} \kappa(x) $ and $\gamma_0 = \text{essinf}_{m(dx)} \gamma(x)$.
 For each $x\in E$, let $\tilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\tilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$.
     Then, we know that $m(\tilde \kappa \neq \kappa) = 0$ and $m(\tilde \gamma \neq \gamma) = 0$.
-	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z) $ almost everywhere with respect to the measure $m$.
+	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z) $
+	%almost everywhere with respect to the measure $m$.
+	$m$-almost everywhere.
 
@@
 \label{sec: proof of result 2}
-	Let $\{X; \mathbf P\}$ be a superprocess satisfies
+%	Let $\{X; \mathbf P\}$ be a superprocess satisfies
+	Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
 	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent,
-    i.e.
+    that is, 
 \[
@@
 	According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp},
-	by monotonicity, we see that $(v_t)$ satisfies the equation
+	by monotonicity, we see that $v_t$ satisfies the equation
 \[
@@
 		Notice that,
-	under the Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
+	under  Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
 	Therefore, $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
 
-	According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and monotone convergence theorem,
-	we have another equation
+	According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem,
+%	we have another equation
+$v_t$ also satisfies the equation
 \[ \label{eq: equation of <vt,phi>}
@@
 \]
-	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only have to consider the speed of this convergence.
+	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only 
+	%have to consider the speed of this convergence.
+	 need to consider the speed of this convergence.
 	This is answered in two steps.
@@
 \label{prop: regularly varying of vt-phi-star}
-	$\langle v_t,\phi^*\rangle_m $ is regularly varying with index $-\frac{1}{\gamma_0-1}$ at $\infty$.
+	$\langle v_t,\phi^*\rangle_m $ is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
@@
 	For each $\mu\in\mathcal M^\phi_E$, denote by
-	$\{(Y_t), (\xi_t),\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$
+%	$\{(Y_t), (\xi_t),\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$
+$\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$
 	the spine representation of $\mathbb N^{(\phi)}_\mu$.
@@
 $
-	Using this decomposition, for each $0<t_0<t<\infty$ and $x\in E$, we can write
+	Using this decomposition, for each $0<t_0<t<\infty$ and $x\in E$, we have
 \[\label{eq: starting point of phi-1v_t(x)}
@@
 	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$,
-	we verify that
+	we have that
 \[\label{eq: some equations for PY-1}\begin{split}
@@
 \]
-	In fact, using the Markov property of the spine process $(\xi_t)$, and the property of the Poisson random measures, we have
+	In fact, using the Markov property of the spine process $(\xi_t)$ and the property of Poisson random measures, we have
 \[\label{eq:epsilon-2}\begin{split}
@@
 \end{split}\]
-	%YX Therefore, while $t-t_0 \geq s_0$, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have
 Therefore, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have,  for $t-t_0 \geq s_0$,
@@
 \end{split}\]
-	%YX Combine this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
 Combining this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
 
-%YX	Now, for each
 Now, for
@@
 	we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
-	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse (in the strict sense) on $(0,\infty)$
-%YX which we denote by
+	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse on $(0,\infty)$
 which is denoted by
@@
 \]
-	Further, by Proposition \ref{prop: convergence in a same speed} and $R(u)\xrightarrow[u\to 0]{} \infty$, we have
+	Further, by Proposition \ref{prop: convergence in a same speed} and 
+	the fact that $R(u)\xrightarrow[u\to 0]{} \infty$, we have
 \[\label{eq: epsilon R converges to 0}
@@
 \]
-	almost everywhere for $r\in (0,\infty)$ with respect to the Lebesgue measure.
-	Therefore, we have
+%	almost everywhere for $r\in (0,\infty)$ with respect to the Lebesgue measure.
+for Lebesgue 
+	Therefore, we have almost every $r\in (0,\infty)$.
 \[\begin{split}
@@
 
-	We are interested in checking the regularly varying property of $R(r)$ at $r=0$.
-	This can be done by considering the regularly varying property of $\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at
-	$u = 0$.
+%	We are interested in checking the regularly varying property of $R(r)$ at $r=0$.
+We now check the regularly varying property of $R(r)$ at $r=0$.
+	This can be done by considering the regularly varying property of 
+	%$\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at
+%	$u = 0$.
+ $u\to \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$
+ at 0.
     According to \eqref{eq: epsilon R converges to 0},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$.
@@
 	According to Lemma \ref{lem:regularly_variation_and_integration},
-%YX and the fact that
  and using the fact that
-$\kappa(x)\phi(x)^\gamma(x)$ is bounded and measure $\phi^* dm$ is finite, we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
+$\kappa(x)\phi(x)^\gamma(x)$ is bounded and the measure $\phi^* dm$ is finite, we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
 	Notice that $-\gamma_0 < 0$, according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
@@
 	\stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x)
-	%\rangle_m.
-	\rangle_{m(dx)}.
+	\rangle_{m(dx)}
 	\\ &\quad \stackrel[u\to 0]{}{\sim}  \langle \mathbf 1_{\gamma(x)= \gamma_0}, \kappa (x)\phi(x)^{\gamma_0} \phi^*(x)
-	%\rangle_m u^{\gamma_0}
 	\rangle_{m(dx)} u^{\gamma_0}
@@
 \end{split}\]
-	Therefore, we can write $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
+	Therefore, we have $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
 	Now according to
@@
 	Let $\{(X_t)_{t\geq 0}; \mathbf P\}$
-    %YX  be a superprocess satisfies
-    be a superprocess which satisfies
+    be a $(\xi, \psi)$-superprocess satisfying
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
-	Suppose that $m(x: \gamma(x) = \gamma_0)>0$.
+	Suppose  $m(x: \gamma(x) = \gamma_0)>0$.
 	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | \|X_t\| \neq 0\big)\big\}$
 	converges weakly
-	to a non-degenerate distribution for a large class of functions $f$ and initial configuration $\mu$.
+	to a non-degenerate distribution for a large class of functions $f$ and initial configurations $\mu$.
 	Our guess of $(\eta_t)$ is
@@
 
-%YX 	From the Laplace transform point of view, 
-From the point of Laplace transform,
- the desired result that $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$
+%From the point of Laplace transform,
+From the point of view of Laplace transforms,
+% the desired result that 
+the desired result that, for any $f\in \mathscr B^+_b(E)$ and $x\in E$,
+ $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$
  converge weakly
@@
 
-	In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, we need to characterize the dynamics of $V_t(\theta f)$ as $\theta$ is varying.
-	(Note that \eqref{eq:mean-fkpp} only characterizes the dynamics of $V_t(\theta f)$ as $t$ is varying.)
-	This is done by the following proposition:
+	In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, 
+	%we need to characterize the dynamics of $V_t(\theta f)$ as $\theta$ is varying.
+	we need to investigate the properties of $\theta\to V_t(\theta f)$.
+	(Note that \eqref{eq:mean-fkpp} 
+	%only characterizes the dynamics of $V_t(\theta f)$ as $t$ is varying.)
+	only gives the the dynamics of $t\to V_t(\theta f)$.)
+	This is done in the following proposition:
 
@@
 \]
-	where $\{Y; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with spine process $\xi$,
-immigration measure
-	$\mathbf n_T$ and
-conditional mean measure
-	$\mathbf m^\xi_T$.
+%	where $\{Y; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with spine process $\xi$,
+%immigration measure
+%	$\mathbf n_T$ and
+%conditional mean measure
+%	$\mathbf m^\xi_T$.
+where $\{(\xi)_{0\le t\le T}, \mathbf n_T, (Y)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$ is a spine representation of $\mathbb N^{W_T(f)}_x$ with $\mathbf m^\xi_T$ being the 
+intensity if the immigration measure $\mathbf n_T$ conditioned on $\{(\xi)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$.
 	From this, we have
@@
 	Recall that a 
-%YX non negative 
   non-negative 
@@
 \]
-	It turns out that we can characterize this distribution by the following result:
+	It turns out that we can characterize this distribution by the following result.
 
@@
 	F_\alpha (\theta)
-	&\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-	=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) \big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+	&\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) 
+	%\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+	\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr\\
+%	=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) 
+   &=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big )
+	\big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
 	\\& =  C\int_0^\theta \|F_{\alpha u^{\frac{1}{\gamma_0 - 1}}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-	\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%	\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} } 
+  \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} } 
+	\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
 	\\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-	\leq C^{k+1} (\rho C+1) \theta^{k+1} .
+%	\leq C^{k+1} (\rho C+1) \theta^{k+1} .
+\\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
 \end{split}\]
@@
 	for some constant $C_0 > 0$.
-	In fact, according to the Minkowski inequality of the $L^p$ norm with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
+	In fact, %according to 
+%	the Minkowski inequality of the $L^p$ norm with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
+by the $L^p$ Minkowski inequality with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
 \[\begin{split}
@@
 	Without loss of generality, we assume that $\langle f, \phi^* \rangle_m = 1$.
-	As have been discussed in Section \ref{sec: conditional distribution},
+	As have been discussed in Subsection \ref{sec: conditional distribution},
 	in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
@@
 	From Lemma \ref{lem: characterize the general Mittag-Leffler distribution},
-%YX we have an equation for $G$:
 we have that $G$ satisfies
@@
 	According to \eqref{eq: equation for normalized V_T},
- %YX we have an equation for $g$:
   we know that $g$ satisfies that
@@
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
-	\\&\quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) +c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x).
+	\\&\quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) 
+	%+c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x).
+	+c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x),
 \end{split}\]
@@
 \]
-	Therefore, by the Minkowski inequality we have that
+	Therefore, by Minkowski's inequality we have that
 \[\begin{split}
@@
 	Notice that,
-	by \eqref{eq:q(t,x,y)}
+	by \eqref{eq:q(t,x,y)},
 \[
@@
 \]
-	where the constant $c_6$ is not related to $t$ and $x$.
+%	where the constant $c_6$ is not related to $t$ and $x$.
+	where the constant $c_6$ is independent of $t$ and $x$.
 	Therefore, we have
@@
 	Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process},  \eqref{eq: differences between J'_G and J'_g} and 
-%YX the definition of
     the definitions of  
@@
 
-	Finally, recalling the definition of $M$, by showing that $M\equiv 0$, the proof is complete.
+	Finally, 
+	%recalling the definition of $M$, by showing that $M\equiv 0$, the proof is complete.
+	by the definition of $M$,  $M\equiv 0$ implies the desired assertion.
 

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
+%!TEX spellcheck
 %%%----Versions-----------------------------
-%stable-limit5.tex 2018/6/22  by
+%stable-limit6.tex 2018/6/27 by Zhenyao-----
+%stable-limit5.tex 2018/6/22 by Renming------
 %stable-limit4.tex 2018/6/21 by Yanxia-------
 %stable-limit3.tex 2018/6/13 by Zhenyao-------
-
 %---The preamble----------------------
@@
 \usepackage{hyperref}
+%new added
+\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
+\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
+%end new added
 \usepackage{mathrsfs}
 \usepackage{mathtools}
+%new added
+\mathtoolsset{showonlyrefs}
+%end new added
 \usepackage{stackrel}
-\usepackage{autonum}
-%new
-\usepackage{amsmath}
-%end new
+%Deleted
+%\usepackage{autonum}
+%\usepackage{amsmath}
+%end Deleted 
+%ZY: \mathtoolsset{showonlyrefs} commond can do the trick of 'autonum' package.
+%ZY: amsmath package is included in the amsart document class
 \newtheorem{thm}{Theorem}[section]
@@
 \newtheorem{exa}[thm]{Example}
-\newtheorem{innerasp}{Assumption}
-\newenvironment{asp}[1]{\renewcommand\theinnerasp{#1}\innerasp}{\endinnerasp}
+\newtheorem{asp}{Assumption}
+%\newtheorem{innerasp}{Assumption}
+%\newenvironment{asp}[1]{\renewcommand\theinnerasp{#1}\innerasp}{\endinnerasp}
 \numberwithin{equation}{section}
-%new
 \allowdisplaybreaks
-%end new
-
 %---Top matter------------------------------
@@
 \title
-	[Manuscript]
+	%[Manuscript]
+	[Superprocesses with stable branching]
 	{\large Limit theorems for a class of critical superprocesses with stable branching}
-\author{Yan-Xia Ren, Renming Song and Zhenyao Sun}
+	%\author{Yan-Xia Ren, Renming Song and Zhenyao Sun}
+	\author[Y.-X. Ren, R. Song and Z. Sun]{Yan-Xia Ren, Renming Song and Zhenyao Sun}
 %---Yan-Xia Ren
@@
 	Beijing, P. R. China, 100871}
-\curraddr
-	{Department of Mathematics\\
-	University of Illinois at Urbana-Champaign\\
-	Urbana, IL 61801}
+%\curraddr
+	%{Department of Mathematics\\
+	%University of Illinois at Urbana-Champaign\\
+	%Urbana, IL 61801}
 \email{zhenyao.sun@pku.edu.cn}
@@
 \begin{abstract}
+%new
+	In this paper, we consider a critical $(\xi,\psi)$-superprocess $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$.
+	$\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact separable metric space $E$, satisfying an intrinsically ultracontractive condition.
+	$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty]$ of the form
+\begin{equation}
+	\psi(x,z)
+	= -\beta (x) z + \kappa(x) z^{\gamma(x)},
+	\quad x\in E, z \geq 0,
+\end{equation}
+	where $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfy 
+\begin{equation}
+	1 
+	< \gamma(\cdot )
+	<2; 
+	\quad \gamma_0 
+	:= \operatorname{ess\,inf}_{m(dx)} \gamma(x)
+	> 1; 
+	\quad \operatorname{ess\,inf}_{m(dx)}\kappa(x) 
+	> 0.
+\end{equation}
+
+	We show that $\mathbf P_{\delta_x}( \| X_t \| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $(\gamma_0 - 1)^{-1}$.
+	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that 
+\begin{equation}
+	\mathbf P_{\delta_x}( \|X_t\| \neq0) 
+	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
+\end{equation} 
+	and for a large class of non-negative testing functions $f$,  
+\begin{equation}
+	\{\eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \} 
+	\xrightarrow[t\to \infty]{\operatorname{law}} \langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
+\end{equation} 
+	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform
+\begin{equation}
+	E[e^{- u \mathbf z^{(\alpha)}}]
+	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
+	\quad u \geq 0.
+\end{equation}
+%new added
 \end{abstract}
@@
 \subsection{Background}
-%    The study of the asymptotic behavior 
-   The study of the asymptotic behaviors
-    of critical branching particle systems has a long history.
-	It is well known that for a critical Galton-Watson
-    process $\{(Z_n)_{n\geq 0}; P\}$,	
-	we have
-	\[\label{eq: Kolmogorov's result with finite variance}
+	The study of the asymptotic behaviors of critical branching particle systems has a long history.
+	It is well known that for a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$, we have
+\begin{equation}\label{eq: Kolmogorov's result with finite variance}
 	n P(Z_n > 0)
 	\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
-	\]
+\end{equation}
 	and
-	\[\label{eq: Yaglom's result with finite variance}
+\begin{equation}\label{eq: Yaglom's result with finite variance}
 	\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
 	\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
-	\]
+\end{equation}
 	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
@@
 
-     Notice that,
-    \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid
-   even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
-    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate,
-%    and then  more appropriate scalings are needed.
-   and thus more appropriate scalings are needed.
-%Research in this direction was first gaven
-Research in this direction was first conducted 
-by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
-	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite 
-%	variance:  Consider a critical Galton-Watson
-	variance. The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson
-    process $\{(Z_n)_{n\geq 0}; P\}$
+	Notice that, \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
+    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, and thus more appropriate scalings are needed.
+	Research in this direction was first conducted by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up, which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance.
+	The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$
 	with infinite variance.
-Assume that the  generating function $f(s)$ of the offspring distribution
-	is of the form
-\[\label{eq: offspring generating function with alpha moment}
+	Assume that the  generating function $f(s)$ of the offspring distribution is of the form
+\begin{equation}\label{eq: offspring generating function with alpha moment}
 	f(s)
@@
 	\quad s\geq 0,
-\]
-%	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$.
+\end{equation}
 	where $\alpha\in (0, 1]$ and $l$ is a function slowly varying at $0$.
 	Then
-\[ \label{eq: extinction probability of critical GW process without 2rd moment}
-	P(Z_n > 0) = n^{-1/\alpha} L(n),
-\]
-%	where $L$ is a slowly varying function at $\infty$, and
+\begin{equation} \label{eq: extinction probability of critical GW process without 2rd moment}
+	P(Z_n > 0) 
+	= n^{-1/\alpha} L(n),
+\end{equation}
 	where $L$ is a function slowly varying at $\infty$, and
-\[\label{eq: conditional distribution of critical GW process without 2rd moment}
+\begin{equation} \label{eq: conditional distribution of critical GW process without 2rd moment}
 	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
 	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
-\]
+\end{equation}
 	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
-\[
+\begin{equation}
 	E[e^{- u \mathbf z^{(\alpha)}}]
@@
 	\quad u \geq 0.
-\]
+\end{equation}
 	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
-%	Slack \cite{Slack1972Further} considered the converse of this problem:
 	Slack \cite{Slack1972Further} also considered the converse of this problem:
-%	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have 
 	In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have
 	a non-degenerate weak limit, 
-%	the offspring generating function must be of  
     the generating function of the offspring distribution must be of  
@@
 	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment 
-%	condition:
     condition. Their main result can be stated as follows. 
 	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
-	 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ 
-%	 the corresponding offspring probability generating function,
-     the generating function of the offspring distribution,
-	and  by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
-	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be 
-%	its left and right principal  eigenvectors respectively, 
-	its left and right  eigenvectors, respectively, 
-	corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
+	Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
+	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right  eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
 	Suppose that
-\[\label{eq: regularly varying condition for multitype branching process}
+\begin{equation}\label{eq: regularly varying condition for multitype branching process}
 	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
@@
 	\quad x > 0,
-\]
-	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and
-	the matrix $G(\mathbf s)$ is defined by
-\[
+\end{equation}
+	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; 
+	and the matrix $G(\mathbf s)$ is defined by
+\begin{equation}
 	\mathbf 1 - \mathbf F(\mathbf s)
@@
 	\quad \mathbf s \in \mathbb R_+^d.
-\]
-    Let
-    $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$,
-    with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
-It was shown in \cite{GoldsteinHoppe1978Critical} that,
- for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
-\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
+\end{equation}
+    Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
+	It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
+\begin{equation} \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
 	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
 	\xrightarrow[n\to \infty]{} 
-	%(\mathbf i \cdot \mathbf u)^\alpha / \alpha,
 	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
-\]
+\end{equation}
 	and for each $\mathbf j \in \mathbb N_0^d$,
-\[\label{eq: conditioned normalized multitype branching process}
+\begin{equation}\label{eq: conditioned normalized multitype branching process}
 	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
 	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
-\]
+\end{equation}
 	where $\mathbf z^{(\alpha)}$ is a random variable with  Zolotarev's distribution with index  $\alpha$.
-	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} 
-%	has a non-degenerate weak limit, 
-   to have a non-degenerate weak limit, 
-	one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
-	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time mutitype critical Galton-Watson processes.
+	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
+	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time multitype critical Galton-Watson processes.
 
@@
     $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact, separable, metric space $E$;
-    $\psi$, the branching mechanism of the superprocess,
-    is a function on $E \times [0,\infty)$ of the form
-\[ \label{eq: branching mechanism}
+    $\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty)$ of the form
+\begin{equation} \label{eq: branching mechanism}
 	\psi(x,z):=
@@
 	\quad x\in E, z\geq 0,
-\]
+\end{equation}
 	where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
 	For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
-	In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.
+%deleted	
+	%In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.
+%end delted
 
@@
 	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses with branching mechanism of the form $(x,z)\mapsto z^2$ and with the spatial motion satisfying some ergodicity conditions.
-	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to
-	a class of critical superprocesses with general branching mechanism and general spatial 
-	%motions:
-	 motions. The main results of \cite{RenSongZhang2015Limit} are as follows.
-	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from 
-a finite measure $\mu$ on $E$.
+	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to a class of critical superprocesses with general branching mechanism and general spatial motions.
+	The main results of \cite{RenSongZhang2015Limit} are as follows.
+	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a finite measure $\mu$ on $E$.
 	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition,
-\[\label{eq: second moment condition}
+\begin{equation}\label{eq: second moment condition}
 	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
 	< \infty.
-\]
-For any finite measure $\mu$ on $E$ and
-any measurable function $f$ on $E$, we use $\langle f,\mu\rangle$	 to denote the integral of $f$ with respect to $\mu$. 
+\end{equation}
+	For any finite measure $\mu$ on $E$ and any measurable function $f$ on $E$, we use $\langle f,\mu\rangle$ to denote the integral of $f$ with respect to $\mu$. 
 	Put $\|\mu\|=\langle 1, \mu\rangle$.
 	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
-\[\label{eq: Kolmogorov type result with 2rd moment}
+\begin{equation}\label{eq: Kolmogorov type result with 2rd moment}
 	t \mathbf P_\mu(\|X_t\| \neq 0)
@@
 \langle \phi, \mu \rangle,
-\]
+\end{equation}
 	and for a large class of testing functions $f$ on $E$,
-\[\label{eq: Ygalom type result with 2rd moment}
+\begin{equation}\label{eq: Ygalom type result with 2rd moment}
 	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot |\|X_t\| \neq 0)\}
 	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
-\]
+\end{equation}
 	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
-%$\langle\cdot, \cdot \rangle$ denotes the inner product in $L^2(E, m)$;
 $\langle\cdot, \cdot \rangle_m$ denotes the inner product in $L^2(E, m)$;
@@
 	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
-	In \cite{RenSongSun2017Spine},  we 
-provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
+	In \cite{RenSongSun2017Spine}, we provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.
 
 	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
-	A simpler
-	version of this question has already been answered in the context of continuous-state branching processes
+	A simpler version of this question has already been answered in the context of continuous-state branching processes
 	(CSBPs)
 	which can be viewed as superprocesses without spatial movements.
-	Kyprianou \cite{Kyprianou2008Continuous} considered
-	CSBPs $\{(Y_t)_{t\geq 0}; P\}$
-	with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
-\[ \label{eq: conditional limit of CSBP with stable branching}
+	Kyprianou \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. 
+	He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
+\begin{equation} \label{eq: conditional limit of CSBP with stable branching}
 	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
 	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
-\]
-    where $\mathbf z^{(\gamma - 1)}$ is
-    a random variable with Zolotarev's distribution with index $\gamma - 1$.
+\end{equation}
+    where $\mathbf z^{(\gamma - 1)}$ is a random variable with Zolotarev's distribution with index $\gamma - 1$.
 	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
-	CSBPs $\{(Y_t)_{t\ge 0}; P\}$
-	with branching mechanism
-\[\label{eq: regular varing of branching mechanism of a CSBP}
+	CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
+\begin{equation}\label{eq: regular varing of branching mechanism of a CSBP}
 	\psi(z)
@@
 	\quad z\geq 0.
-\]
-%	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
+\end{equation}
 	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
 	It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
-\[\label{eq: conditional limit of CSBP}
+\begin{equation}\label{eq: conditional limit of CSBP}
 	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
 	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
-\]
-	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$
-	satisfying Grey's condition.
-	In order for the left side of \eqref{eq: conditional limit of CSBP} 
-%	has non-trivial weak limit for
-    to have a non-trivial weak limit for
-	some positive constants $(\lambda_t)_{t\geq 0}$,
-	one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
-
-In this paper, we will establish a result parallel
-	to \eqref{eq: conditional limit of CSBP with stable branching} for some
-   critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$
-	with spatially dependent stable branching mechanism.
+\end{equation}
+	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: 
+	%Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ satisfying Grey's condition.
+	Suppose that $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP with critical branching mechanism $\psi$ satisfying Grey's condition.
+	In order for the left side of \eqref{eq: conditional limit of CSBP} to have a non-trivial weak limit for some positive constants $(\lambda_t)_{t\geq 0}$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
+
+	In this paper, we will establish a result parallel to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
 	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
-\[
+\begin{equation}
 	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
 	\quad x\in E, z \geq 0,
-\]
+\end{equation}
 	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
-	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and
-	is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
-	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
-\[
+	%We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
+	We will show that $\mathbf P_{\delta_x}( \| X_t\| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
+	%Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
+	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we will show that
+\begin{equation}
 	\mathbf P_{\delta_x}( \|X_t\| \neq0)
 	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
-\]
+\end{equation}
 	and for a large class of non-negative testing functions $f$,
-\[\label{eq: result2}
+\begin{equation}\label{eq: result2}
 	\{ \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \}
@@
 	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
-\]
-	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a
-%	Zolotarev's random variable with index $\gamma_0 - 1$.
-random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
-	Precise statements of the assumptions and the results are presented in the next
-%		section.
-    subsection.
-    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess 
-%    $(X_t)$   
-   $\{X; \mathbf P\}$
-    depends primarily on the lowest index $\gamma_0$.
+\end{equation}
+	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
+	Precise statements of the assumptions and the results are presented in the next subsection.
+    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $\{X; \mathbf P\}$ depends primarily on the lowest index $\gamma_0$.
 
@@
 	Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
-	Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$, $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.	
+	%Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$, $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
+	Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$ and $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
 	Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
 	Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
-	For simplicity, we write
-		$\mu(f)$ and sometimes $\langle \mu, f\rangle$
-	for the integration of a function $f$ with respect to a measure $\mu$.
-    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$
-    to emphasize that it is the inner product
-    in the Hilbert space $L^2(m)$.
+	For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
+    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(m)$.
 	For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
@@
 	We now give the definition of a $(\xi, \psi)$-superprocess:
-	Let $E$ be a locally compact separable metric space,
-	the spatial motion
-   $\xi:=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$
-%	be a $E$-valued Hunt process with its lifetime denoted by $\zeta$, 
-	be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, 
-	and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by
-	\eqref{eq: branching mechanism}.
-%	We say a $\mathcal M^1_E$-valued Hunt process
-	We say an $\mathcal M^1_E$-valued Hunt process
-    $X:=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$
-	is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
-\[
+	Let $E$ be a locally compact separable metric space, the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by \eqref{eq: branching mechanism}.
+	We say an $\mathcal M^1_E$-valued Hunt process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
+\begin{equation}
 	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
-\]
-	where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is defined as the unique locally bounded positive solution to the equation
-\[\label{eq:FKPP_in_definition}
+\end{equation}
+	%where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is defined as the unique locally bounded positive solution to the equation
+	where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
+\begin{equation}\label{eq:FKPP_in_definition}
 	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
-	=\Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],\quad
-	t\geq 0, x \in E.
-\]
+	= \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
+	\quad t \geq 0, x \in E.
+\end{equation}
 	(In this paper, for any real-valued function $F$ on $E\times [0,\infty)$ and real-valued function $f$ on $E$, we write $F(x,f):= F(x,f(x))$ for simplicity.)
 
-	Define the \emph{Feyman-Kac semigroup}
-\[
+	Define the \emph{Feynman-Kac semigroup}
+\begin{equation}
 	P^\beta_tf(x)
-		:=
-	\Pi_x \big[e^{\int_0^{t} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
+	:= \Pi_x \big[e^{\int_0^{t} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
 	\quad t\geq 0, x\in E, f\in \mathscr B_b(E).
-\]
-	(Notice that if $\beta \equiv 0$,
-then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
+\end{equation}
+	(Notice that if $\beta \equiv 0$, then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
 	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that 
-	\[ \label{eq: Ygalom type result without 2rd moment}
+\begin{equation} \label{eq: Ygalom type result without 2rd moment}
 	\mathbf P_\mu [X_t(f)]
@@
 	t \geq 0,f \in \mathscr B_b(E).
-	\]
-%	This mean semigroup plays a central role in the study of the 
-    The  mean semigroup plays a central role in the study of the 
-	asymptotic behavior of superprocesses.
-	As discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment}
-		or \eqref{eq: result2},
-	we have to establish the asymptotic behavior of the mean semigroup first.
-%	This can be done under the following assumptions on the underlying motion
-	This can be done under the following assumptions on the spatial motion
-    $\xi$:
-\begin{asp}{1}
-\label{asp: 1}
+\end{equation}
+    The  mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
+	As discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} or \eqref{eq: result2}, we have to establish the asymptotic behavior of the mean semigroup first.
+	This can be done under the following assumptions on the spatial motion $\xi$:
+\begin{asp} \label{asp: 1}
 	There exists an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$, and a family of strictly positive, bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that,
-\[\begin{split}
+\begin{equation}\begin{split}
 	\Pi_x[ f(\xi_t)\mathbf 1_{t < \zeta} ]
@@
 	&\quad t> 0;
-\end{split}\]
-	and the functions $x \mapsto \int_E p_t(x,y)^2 m(dy)$
-and
-	$x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous.
+\end{split}\end{equation}
+	and the functions $x \mapsto \int_E p_t(x,y)^2 m(dy)$ and $x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous.
 \end{asp}
@@
 	Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
-\[
+\begin{equation}
 	e^{-\|\beta\|_\infty t} p_t(x,y)
@@
 	\quad t>0, x, y\in E,
-\]
+\end{equation}
 	and that for any $t>0, x\in E$ and $f \in \mathscr B_b(E)$,
-\[
+\begin{equation}
 	P^\beta_t f(x)
 	= \int_E p_t^\beta (x,y) f(y) m(dy).
-\]
+\end{equation}
     $(p^\beta_t)_{t\geq 0}$ is called the \emph{density of semigroup $(P^\beta_t)_{t\geq 0}$}.
 	Define the dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ by
-\[
+\begin{equation}
 	P^{\beta *}_0 = I;
@@
 	\quad t>0, x\in E, f\in \mathscr B_b(E).
-\]
-	It is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that
-	$(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$
-	are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+\end{equation}
+	It is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
 	Let $L$ and $L^*$ be the generators of the semigroups $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$, respectively.
@@
 	We further normalize $\phi$ and $\phi^*$ by $\langle\phi, \phi\rangle_m = \langle\phi,\phi^*\rangle_m = 1$ so that they are unique.
-	Moreover, for each
-	$t\geq 0$ and $x\in E$,
-	we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
+	Moreover, for each $t\geq 0$ and $x\in E$, we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
 	We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of $L$ (resp. $L^*$).
@@
 	Now, from
-\[
+\begin{equation}
 	\mathbf P_\mu[X_t(\phi)]
 	= e^{\lambda t} \mu(\phi),
-\]
+\end{equation}
 	we see that, if $\lambda > 0$, the mean of $X_t(\phi)$ will increase exponentially; if $\lambda < 0$, the mean of $X_t(\phi)$ will decrease exponentially; and if $\lambda = 0$, the mean of $X_t(\phi)$ will be a constant.
@@
 	Since we are only interested in the critical case, we assume the following:
-\begin{asp}{2} \label{asp: 2}
+\begin{asp} \label{asp: 2}
     The superprocess $X$ is critical, i.e., $\lambda = 0$.
@@
 
-	Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the underlying process 
-    $\xi$.
-%Our second assumption on the underlying process 
-Our second assumption on the spatial process 
-    $\xi$
- is the following:
-
-\begin{asp}{3} \label{asp: 3}
-	$\varphi$ is bounded, and 
-    $(P_t)_{t\geq 0}$ 
-is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
+	Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the underlying process $\xi$.
+	Our second assumption on the spatial process $\xi$ is the following:
+
+\begin{asp} \label{asp: 3}
+	$\varphi$ is bounded, and $(P_t)_{t\geq 0}$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
 \end{asp}
 
-	Under Assumption \ref{asp: 3},	it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of Feyman-Kac semigroup 
-    $(P^\beta_t)_{t\geq 0}$ is also bounded.
-	Moreover, 
-$(P^\beta_t)_{t\geq 0}$ 
-is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
+	Under Assumption \ref{asp: 3}, it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of Feynman-Kac semigroup $(P^\beta_t)_{t\geq 0}$ is also bounded.
+	Moreover, $(P^\beta_t)_{t\geq 0}$ is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
 	In fact, it is proved in \cite{KimSong2008Intrinsic} that for each $t>0$, $(p^\beta_t(x,y))_{x,y\in E}$ is comparable to $(\phi(x)\phi^*(y))_{x,y\in E}$ in the sense that there is a constant $c_t > 1$ such that
-\[\label{eq: p-t-beta is comparable to phi phi-star}
+\begin{equation}\label{eq: p-t-beta is comparable to phi phi-star}
 	c_t^{-1}
@@
 	\quad x,y \in E.
-\]
-    It is also shown in \cite{KimSong2008Intrinsic} that
-    there are constants $c_0, c_1 > 0$ such that
-\[\label{eq:q(t,x,y)}
-	\sup_{x,y\in E} \big|\frac{p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \big| \leq c_0 e^{-c_1 t},
+\end{equation}
+    It is also shown in \cite{KimSong2008Intrinsic} that there are constants $c_0, c_1 > 0$ such that
+\begin{equation}\label{eq:q(t,x,y)}
+	\sup_{x,y\in E} \Big|\frac{p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \Big| 
+	\leq c_0 e^{-c_1 t},
 	\quad t > 1.
-\]
-	We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of 
-%	underlying processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
-    processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
+\end{equation}
+	We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
 
 	Our assumption on the branching mechanism is the following:
-\begin{asp}{4} \label{asp: 4}
-	The branching mechanism $\psi$ is of
-	the form:
-\[\begin{split}
+\begin{asp} \label{asp: 4}
+	The branching mechanism $\psi$ is of the form:
+\begin{equation}\begin{split}
 	\psi(x,z)
@@
 	\quad x\in E, z \geq 0,
-\end{split}\]
+\end{split}\end{equation}
 	where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
@@
 	Here we use the definition of the Gamma function on the negative half line:
-\[\label{eq: definition of Gamma function}
+\begin{equation}\label{eq: definition of Gamma function}
 	\Gamma(x)
@@
 	\quad -n< x< -n+1, n\in \mathbb N.
-\]
+\end{equation}
 
@@
 
-\begin{thm}
-\label{thm: main theorem}
-	Suppose that $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M_E^1}\}$ is a $(\xi, \psi)$-superprocess satisfying
-Assumptions \ref{asp: 1}--\ref{asp: 4}. Then,
+\begin{thm} \label{thm: main theorem}
+	Suppose that $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M_E^1}\}$ is a $(\xi, \psi)$-superprocess satisfying Assumptions \ref{asp: 1}--\ref{asp: 4}. 
+	Then,
 \begin{itemize}
-	\item[(1)] $\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}(X_t \equiv 0) > 0$.
-	\item[(2)] For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$
-	converges to $0$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$
-as $t\to \infty$.
+\item[(1)] 
+	%$\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}( X_t \equiv 0) > 0$.
+	$\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}( \| X_t\| \neq 0) > 0$.
+\item[(2)] 
+	%For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$ converges to $0$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$ as $t\to \infty$.
+	For each $\mu \in \mathcal M^1_E$, $\mathbf P_{\mu}(\|X_t\| \neq 0)$ converges to $0$, and is regularly varying with index $-(\gamma_0-1)^{-1}$ as $t \to \infty$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
-\[
-	\mathbf P_{\delta_x}(\|X_t\| \neq 0)
-	\stackrel[t\to \infty]{}{\sim} \phi(x)\eta_t.
-\]
-	\item[(3)] Suppose $m( x:\gamma(x)=\gamma_0 )>0$.
-	Let $f \in \mathscr B^+(E)$ be  such that $\langle f, \phi^* \rangle_m > 0$  and $\| \phi^{-1}f \|_\infty < \infty$, then
-\[
-	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot |\|X_t\| \neq 0) \}
-	\xrightarrow[t\to \infty]{\operatorname{law}}
-	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}.
-\]
+\begin{equation}
+	\mathbf P_{\mu}(\|X_t\| \neq 0)
+	\stackrel[t\to \infty]{}{\sim} \mu(\phi) \eta_t.
+\end{equation}
+\item[(3)] 
+	Suppose $m( x:\gamma(x)=\gamma_0 )>0$.
+	%Let $f \in \mathscr B^+(E)$ be such that $\langle f, \phi^* \rangle_m > 0$ and $\| \phi^{-1}f \|_\infty < \infty$, then
+	Let $f \in \mathscr B^+(E)$ be such that $\langle f, \phi^* \rangle_m > 0$ and $\| \phi^{-1}f \|_\infty < \infty$. Then for each $\mu \in \mathcal M_E^1$,
+\begin{equation}
+	%\{\eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot |\|X_t\| \neq 0) \}
+	\{\eta_t X_t(f) ; \mathbf P_{\mu}(\cdot |\|X_t\| \neq 0) \}
+	\xrightarrow[t\to \infty]{\operatorname{law}} \langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}.
+\end{equation}
 \end{itemize}
-	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is
- a random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
+	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
 \end{thm}
@@
 	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 
-    $X$:
+	%$X$:
+	$X$.
 	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
@@
 	Therefore, this size-biased transform can be viewed as a martingale change of measure.
-%	Under the Assumptions \ref{asp: 1} and \ref{asp: 3},
-	Under Assumptions \ref{asp: 1} and \ref{asp: 3},
-	the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process.
+	Under Assumptions \ref{asp: 1} and \ref{asp: 3}, the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process.
 	We take advantage of this ergodicity to study the asymptotic behavior of the superprocess.
 
-	Similar idea
-	has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
-    Let $\{(Y_t)_{t\geq 0}; P\}$
-%	be a branching diffusion processes in a bounded domain with finite second moment.
-be a branching diffusion process, in a bounded domain,  with finite second moment.
-	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation
-	satisfied by the survival probability
-$(t,x) \mapsto P_{\delta_x}(\|Y_t\| \neq 0)$ is tricky.
+	Similar idea has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
+    Let $\{(Y_t)_{t\geq 0}; P\}$ be a branching diffusion process, in a bounded domain,  with finite second moment.
+	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation satisfied by the survival probability $(t,x) \mapsto P_{\delta_x}(\|Y_t\| \neq 0)$ is tricky.
 	Instead, by using a spine decomposition approach, Powell \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principal eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capturing the uniform speed.
@@
 	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of critical superprocesses with finite second moment.
-	In this paper, we will  generalize these arguments to a class of 
-%	critical superprocesses without finite second moment, 
-    general critical superprocesses without finite second moment, 
-	and establish Theorem \ref{thm: main theorem}(2).
+	In this paper, we will  generalize these arguments to a class of general critical superprocesses without finite second moment, and establish Theorem \ref{thm: main theorem}(2).
 	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform of Zolotarev's distribution can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
-	Using the spine method, we show that the Laplace transform of
-		the one-dimensional distributions
-	of the superprocess, after a proper rescaling,
-	can be 	characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
+	Using the spine method, we show that the Laplace transform of the one-dimensional distributions of the superprocess, after a proper rescaling, can be 	characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
 	Then, the desired convergence of the distributions can be established by a comparison between the equations.	
@@
 	A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
-	We characterized the exponential distribution
-		using its double size-biased transform;
+	We characterized the exponential distribution using its double size-biased transform;
 	and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
-	However, the
-	double-size-biased transform of a random variable requires its second moment being finite.
-%	Since in this paper, we do not assume the second moment condition, 
-Since we do not assume the second moment condition in this paper,
-	we can not use the method of double size-biased transform.
-
-	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in \cite{RenSongSun2017Spine} and
-%	\cite{RenSongZhang2015Limit} (for critical superprocesses with finite variance), 
-	\cite{RenSongZhang2015Limit} (for general critical superprocesses with finite variance), 
-	the conditional weak convergence was proved in two steps.
-    First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used to extend the result to
-     more general testing functions.
+	However, the double-size-biased transform of a random variable requires its second moment being finite.
+	Since we do not assume the second moment condition in this paper, we can not use the method of double size-biased transform.
+
+	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in \cite{RenSongSun2017Spine} and \cite{RenSongZhang2015Limit} (for general critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
+    First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used to extend the result to more general testing functions.
 	However, in the present case, since we are not assuming the second moment condition, this type of argument does not work.
-	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for
-		a large class of general testing functions at the same time.
+	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for a large class of general testing functions at the same time.
 
 	The rest of this paper is organized as follows:
-    In Subsections
-\ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly varying functions and superprocesses, respectively.
-In Subsection 
-\ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem.
-In Subsection 
-\ref{sec: Ergodicity}, we discuss the ergodicity of the spine process.
-    In Subsections
-\ref{sec: proof of result 1} and \ref{sec: proof of result 2} we give the poofs of Theorem \ref{thm: main theorem}(1) and \ref{thm: main theorem}(2), respectively.
-    In Subsection
-\ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-    In Subsection
-\ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize Zolotarev's distribution.
+    In Subsections \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly varying functions and superprocesses, respectively.
+	In Subsection \ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem.
+	In Subsection \ref{sec: Ergodicity}, we discuss the ergodicity of the spine process.
+    In Subsections \ref{sec: proof of result 1} and \ref{sec: proof of result 2} we give the poofs of Theorem \ref{thm: main theorem}(1) and \ref{thm: main theorem}(2), respectively.
+    In Subsection \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
+    In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize Zolotarev's distribution.
 	Finally, 
-    In Subsection
+    %In Subsection
+    in Subsection 
     \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
 
-\section{Preliminaries}
-\label{sec: Preliminaries}
-
-\subsection{Asymptotic equivalence}
-\label{sec: Asymptotic equivalence}
-  In this subsection, 
-we give a lemma on asymptotic equivalence.	
+\section{Preliminaries} \label{sec: Preliminaries}
+\subsection{Asymptotic equivalence} \label{sec: Asymptotic equivalence}
+	In this subsection, we give a lemma on asymptotic equivalence.	
 	Let $t_0 \in [-\infty,\infty]$.
@@
 
-\begin{lem}
-\label{lem: asymptotic equivalent of integration}
+\begin{lem} \label{lem: asymptotic equivalent of integration}
 	Suppose that $f_0,f_1\in \mathscr B^{++}_b({\mathbb R \times E})$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
 	If $m \in \mathcal M^1_E$, then
-\[
+\begin{equation}
 	\int_E f_0(t,x)m(dx)
@@
 	\int_E f_1(t,x)m(dx).
-\]
+\end{equation}
 \end{lem}
@@
 	Since
-\[\begin{split}
+\begin{equation}\begin{split}
 	&\Big| \frac{	\int_E f_0(t,x)m(dx) }{ 	\int_E f_1(t,x)m(dx)  } - 1 \Big|
@@
 	\xrightarrow[t\to t_0]{} 0,
-\end{split}\]
+\end{split}\end{equation}
 	the assertion is valid.
@@
 	For $f\in \mathscr B^{++}((0,\infty))$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\gamma \in (-\infty,\infty)$ if for any $\lambda \in (0,\infty)$,
-\[
+\begin{equation}
 	\lim_{t\to\infty}\frac{f(\lambda t)}{f(t)}
@@
 	= \lambda^\gamma\Big).
-\]
+\end{equation}
 	In this case we write  $f\in \mathcal R^\infty_\gamma$ (resp. $f\in \mathcal R^0_\gamma$).
-	Further, if $\gamma = 0$,
-	then we say $f$ is slowly varying.
+	Further, if $\gamma = 0$, then we say $f$ is slowly varying.
 	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, if $L$ is a function slowly varying at $\infty$, then it can be written in the form
-\[
+\begin{equation}
 	L(t)
 	= c(t) \exp\Big\{\int_{t_0}^t \epsilon(u) \frac{du}{u}\Big\},\quad t\geq t_0,
-\]
+\end{equation}
 	for some $t_0>0$, where $(c(t))_{t\geq t_0}$ and $(\epsilon(t))_{t\geq t_0}$ are measurable functions with $c(t) \xrightarrow[t\to \infty]{} c \in (0,\infty)$ and $\epsilon(t) \xrightarrow[t\to \infty]{} 0$.
@@
 	Let $t_0\in (0,\infty)$ be large enough so that $L$ is locally bounded on $[t_0,\infty)$. If $\alpha>0 $, then
-\[
+\begin{equation}
 	\int_{t_0}^t L(u)du^\alpha
 	\stackrel[t\to \infty]{}{\sim} t^\alpha L(t).
-\]
+\end{equation}
 \item
 	If $\alpha< 0$ then $\int_t^\infty L(u) du^\alpha < \infty$ for $t$ large enough, and
-\[
+\begin{equation}
 	-\int_t^\infty L(u)du^\alpha
 	\stackrel[t\to \infty]{}{\sim} t^\alpha L(t).
-\]
+\end{equation}
 \end{itemize}
@@
 	If $\alpha < 0$, then
-	\[
+\begin{equation}
 	-\int_s^{s_0} l(u)du^\alpha
 	\stackrel[s\to 0]{}{\sim} s^{\alpha} l(s).
-	\]
+\end{equation}
 \item
 	If $\alpha > 0$, then $\int_0^s l(u)du^\alpha<\infty$ for $s$ small enough, and
-\[
+\begin{equation}
 	\int_0^s l(u)du^\alpha
 	\stackrel[s\to 0]{}{\sim} s^{\alpha} l(s).
-\]
+\end{equation}
 \end{itemize}
@@
 	If $\alpha<0 $, then according to Lemma \ref{lem: exchange slowly varying function and integration}, we have
-\[
+\begin{equation}
 	\int_{t_0}^t L(u)du^{-\alpha}
 	\stackrel[t\to \infty]{}{\sim} t^{-\alpha}  L(t).
-\]
+\end{equation}
 	Replacing $t$ with $s^{-1}$, we have
-\[
+\begin{equation}
 	-\int_{s}^{s_0} l(u)du^{\alpha}
@@
 	=s^\alpha l(s),
-\]
+\end{equation}
 	as desired.
@@
 
-	The following lemma concerns the inverse of
-%   an invertible, monotone and regularly varying function.
-    a strictly monotone, regularly varying function.
-%	In this paper, if a function $f$ is 	invertible,
-	In this paper, if a function $f$ is strictly monotone, 
-	we write $f^{(-1)}$ for its inverse;
-	if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
-
-\begin{lem}
-\label{lem: regularly variation and inverse}
-	Suppose that $f$ is 
-%	an invertible, monotone map 
-   a strictly monotone map 
-	from $(0,\infty)$ to $(0,\infty)$.
-	Then, for each $\alpha > 0$, we have
-\[ \label{eq: inverse of a regularly varying function at infinity with alpha > 0}
-	f
-	\in \mathcal R^\infty_{\alpha}
-	\iff f^{(-1)}
-	\in \mathcal R^\infty_{1/\alpha}
-\]
-	and
-\[ \label{eq: inverse of a regularly varying function at 0 with alpha > 0}
-	f
-	\in \mathcal R^0_{\alpha}
-	\iff f^{(-1)}
-	\in \mathcal R^0_{1/\alpha};
-\]
-	for each $\alpha < 0$, we have
-\[ \label{eq: inverse of a regularly varying function with alpha < 0}
-	f
-	\in \mathcal R^\infty_{\alpha}
-	\iff f^{(-1)}
-	\in \mathcal R^0_{1/\alpha}.
-\]
-	Similarly, for each $\alpha > 0$ and $c > 0$, we have
-\[\label{eq: inverse and power equivalent at infinity with alpha > 0}
-	f(t)
-	\stackrel[t\to \infty]{}{\sim} c t^\alpha
-	\iff f^{(-1)}(t)
-	\stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}
-\]
-	and
-\[\label{eq: inverse and power equivalent at 0 with alpha > 0}
-	f(t)
-	\stackrel[t\to 0]{}{\sim} c t^\alpha
-	\iff f^{(-1)}(t)
-	\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha};
-\]
-	for each $\alpha < 0$ and $c > 0$, we have
-\[\label{eq: inverse and power equivalent with alpha < 0}
-	f(t)
-	\stackrel[t\to \infty]{}{\sim} c t^\alpha
-	\iff f^{(-1)}(t)
-	\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha}.
-\]
+%deleted
+	%The following lemma concerns the inverse of a strictly monotone, regularly varying function.
+	%In this paper, if a function $f$ is strictly monotone, 
+	%we write $f^{(-1)}$ for its inverse;
+	%if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
+
+%\begin{lem}
+%\label{lem: regularly variation and inverse}
+	%Suppose that $f$ is a strictly monotone map from $(0,\infty)$ to $(0,\infty)$.
+	%Then, for each $\alpha > 0$, we have
+%\begin{equation} \label{eq: inverse of a regularly varying function at infinity with alpha > 0}
+	%f
+	%\in \mathcal R^\infty_{\alpha}
+	%\iff f^{(-1)}
+	%\in \mathcal R^\infty_{1/\alpha}
+%\end{equation}
+	%and
+%\begin{equation} \label{eq: inverse of a regularly varying function at 0 with alpha > 0}
+	%f
+	%\in \mathcal R^0_{\alpha}
+	%\iff f^{(-1)}
+	%\in \mathcal R^0_{1/\alpha};
+%\end{equation}
+	%for each $\alpha < 0$, we have
+%\begin{equation} \label{eq: inverse of a regularly varying function with alpha < 0}
+	%f
+	%\in \mathcal R^\infty_{\alpha}
+	%\iff f^{(-1)}
+	%\in \mathcal R^0_{1/\alpha}.
+%\end{equation}
+	%Similarly, for each $\alpha > 0$ and $c > 0$, we have
+%\begin{equation}\label{eq: inverse and power equivalent at infinity with alpha > 0}
+	%f(t)
+	%\stackrel[t\to \infty]{}{\sim} c t^\alpha
+	%\iff f^{(-1)}(t)
+	%\stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}
+%\end{equation}
+	%and
+%\begin{equation}\label{eq: inverse and power equivalent at 0 with alpha > 0}
+	%f(t)
+	%\stackrel[t\to 0]{}{\sim} c t^\alpha
+	%\iff f^{(-1)}(t)
+	%\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha};
+%\end{equation}
+	%for each $\alpha < 0$ and $c > 0$, we have
+%\begin{equation}\label{eq: inverse and power equivalent with alpha < 0}
+	%f(t)
+	%\stackrel[t\to \infty]{}{\sim} c t^\alpha
+	%\iff f^{(-1)}(t)
+	%\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha}.
+%\end{equation}
+%\end{lem}
+%\begin{proof}
+%If $\alpha>0$, then according to \cite[Theorem 1.5.12.]{BinghamGoldieTeugels1989Regular}, we have \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} is true.
+	%To see 	\eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} is true, we write $h(t) : = f(t^{-1})^{-1}$.
+	%It is  easy to verify that $h$ is strictly monotone with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1}$.
+	%Therefore,
+%\begin{equation}
+	%f
+	%\in \mathcal R^0_{\alpha}
+	%\iff h
+	%\in \mathcal R^\infty_{\alpha}
+	%\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} }   }{\iff} h^{(-1)}
+	%\in \mathcal R^\infty_{1/\alpha}
+	%\iff f^{(-1)}
+	%\in \mathcal R^0_{1/\alpha}.
+%\end{equation}
+
+	%If $\alpha < 0$, to see	\eqref{eq: inverse of a regularly varying function with alpha < 0} is true, we write $g(t) : = f(t^{-1})$.
+	%It is easy to verify that $g$ is strictly monotone with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
+	%Therefore,
+%\begin{equation}
+	%f
+	%\in \mathcal R^\infty_{\alpha}
+	%\iff g
+	%\in \mathcal R^0_{-\alpha}
+	%\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} }   }{\iff} g^{(-1)}
+	%\in \mathcal R^0_{-1/\alpha}
+	%\iff f^{(-1)}
+	%\in \mathcal R^0_{1/\alpha}.
+%\end{equation}
+
+	%Now, assume that $f(t) \stackrel[t\to \infty]{}{\sim} c t^\alpha$ for some $\alpha > 0$ and $c > 0$, we want to show that $f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}$.
+	%Notice that, since $\alpha >0$, we must have $f$ is strictly increasing.
+	%From the definition of the asymptotic equivalence, we have, for each $\epsilon> 0$,
+%\begin{equation}
+	%\Big|\frac{f(t)}{c t^\alpha} - 1\Big|
+	%< \epsilon,
+	%\quad t \text{ large enough.}
+%\end{equation}
+	%This is equivalent to
+%\begin{equation}
+	%(1-\epsilon) c t^{\alpha}
+	%< f(t)
+	%< (1+ \epsilon)c t^{\alpha},
+	%\quad t \text{ large enough,}
+%\end{equation}
+	%which, by the increasing nature of $f^{(-1)}$, gives that
+%\begin{equation}\label{eq: inverse and inequality}
+	%f^{(-1)}[(1-\epsilon) c t^{\alpha}] \leq t \leq f^{(-1)}[(1+ \epsilon)c t^{\alpha}], \quad t \text{ large enough.}
+%\end{equation}
+	%If we replace $(1-\epsilon) c t^{\alpha}$ with $y$ on the left side of \eqref{eq: inverse and inequality}, and respectively, replace $(1+\epsilon) c t^{\alpha}$ with $y$ on the right side of \eqref{eq: inverse and inequality}, then we get
+%\begin{equation}
+	%\Big(\frac{y}{c(1-\epsilon)}\Big)^{1/\alpha}
+	%\leq f^{(-1)}(y) \leq \Big(\frac{y}{c(1+\epsilon)}\Big)^{1/\alpha},
+	%\quad y \text{ large enough.}
+%\end{equation}
+	%This, in fact, implies that $ f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}. $
+	%This proved one side of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}.
+	%The other direction of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}, and \eqref{eq: inverse and power equivalent at 0 with alpha > 0}, as well as \eqref{eq: inverse and power equivalent with alpha < 0}, can be proved similarly.
+%\end{proof}
+%end deleted
+
+%new added
+\begin{lem}[{\cite[Theorem 1.5.12]{BinghamGoldieTeugels1989Regular}}] \label{lem: regularly variation and inverse}
+	If $f \in \mathcal R_\alpha^\infty$ with $\alpha > 0$, there exists $g \in \mathcal R^\infty_{1/\alpha}$ with
+\begin{equation}
+	g(f(t))
+	\stackrel[t\to \infty]{}{\sim}
+	f(g(t))
+	\stackrel[t\to \infty]{}{\sim}
+	t.
+\end{equation}
+	Here $g$ is determined uniquely up to asymptotic equivalence as $t\to \infty$.
 \end{lem}
+\begin{cro} \label{cro: regularly varing and inverse with alpha < 0}
+	If $f \in \mathcal R_\alpha^0$ with $\alpha < 0$, there exists $g \in \mathcal R^\infty_{1/\alpha}$ with
+\begin{equation} \label{eq: asymptotic inverse with alpha < 0}
+	g(f(t))
+	\stackrel[t\to 0]{}{\sim}
+	t;
+	\quad
+	f(g(t))
+	\stackrel[t\to \infty]{}{\sim}
+	t.
+\end{equation}
+	Here $g$ is determined uniquely up to asymptotic equivalence as $t\to \infty$.
+\end{cro}
 \begin{proof}
-If $\alpha>0$, then according to \cite[Theorem 1.5.12.]{BinghamGoldieTeugels1989Regular}, we have \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} is true.
-	To see 	\eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} is true, we write $h(t) : = f(t^{-1})^{-1}$.
-	It is  easy to verify that
-%	$h$ is invertible and monotone
-   $h$ is strictly monotone
-	with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1}$.
-	Therefore,
-\[
-	f
-	\in \mathcal R^0_{\alpha}
-	\iff h
-	\in \mathcal R^\infty_{\alpha}
-	\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} }   }{\iff} h^{(-1)}
-	\in \mathcal R^\infty_{1/\alpha}
-	\iff f^{(-1)}
-	\in \mathcal R^0_{1/\alpha}.
-\]
-
-	If $\alpha < 0$, to see	\eqref{eq: inverse of a regularly varying function with alpha < 0} is true, we write $g(t) : = f(t^{-1})$.
-	It is easy to verify that
-%	$g$ is invertible and monotone 
-	$g$ is strictly monotone 
-	with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
-	Therefore,
-\[
-	f
-	\in \mathcal R^\infty_{\alpha}
-	\iff g
-	\in \mathcal R^0_{-\alpha}
-	\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} }   }{\iff} g^{(-1)}
-	\in \mathcal R^0_{-1/\alpha}
-	\iff f^{(-1)}
-	\in \mathcal R^0_{1/\alpha}.
-\]
-
-	Now, assume that
-	$f(t) \stackrel[t\to \infty]{}{\sim} c t^\alpha$ for some $\alpha > 0$ and $c > 0$, we want to show that $f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}$.
-	Notice that, since $\alpha >0$, we must have $f$ is 
-%	non-decreasing.
-   strictly increasing.
-	From the definition of the asymptotic equivalence, we have, for each $\epsilon> 0$,
-\[
-	\Big|\frac{f(t)}{c t^\alpha} - 1\Big|
-	< \epsilon,
-	\quad t \text{ large enough.}
-\]
-	This is equivalent to
-\[
-	(1-\epsilon) c t^{\alpha}
-	< f(t)
-	< (1+ \epsilon)c t^{\alpha},
-	\quad t \text{ large enough,}
-\]
-%	which, by the non-decreasing nature of $f^{(-1)}$, gives that
-	which, by the increasing nature of $f^{(-1)}$, gives that
-\[\label{eq: inverse and inequality}
-	f^{(-1)}[(1-\epsilon) c t^{\alpha}] \leq t \leq f^{(-1)}[(1+ \epsilon)c t^{\alpha}], \quad t \text{ large enough.}
-\]
-	If we replace $(1-\epsilon) c t^{\alpha}$ with $y$ on the left side of \eqref{eq: inverse and inequality}, and respectively, replace $(1+\epsilon) c t^{\alpha}$ with $y$ on the right side of \eqref{eq: inverse and inequality}, then we get
-\[
-	\Big(\frac{y}{c(1-\epsilon)}\Big)^{1/\alpha}
-	\leq f^{(-1)}(y) \leq \Big(\frac{y}{c(1+\epsilon)}\Big)^{1/\alpha},
-	\quad y \text{ large enough.}
-\]
-	This, in fact, implies that $ f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}. $
-	This proved one side of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}.
-	The other direction of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}, and \eqref{eq: inverse and power equivalent at 0 with alpha > 0}, as well as \eqref{eq: inverse and power equivalent with alpha < 0}, can be proved similarly.
+	Since $f \in \mathcal R_\alpha^0$, we know that $\tilde f \in \mathcal R_{-\alpha}^\infty$ with $\tilde f(t):= f(t^{-1})$. 
+	Noticing that $-\alpha > 0$, according to Lemma \ref{lem: regularly variation and inverse}, there exists $h \in \mathcal R_{-1/\alpha}^{\infty}$ such that
+\begin{equation} \label{eq: inverse between h and f}
+	h(\tilde f(t))
+	\stackrel[t\to \infty]{}{\sim}
+	t;
+	\quad
+	\tilde f(h(t))
+	\stackrel[t\to \infty]{}{\sim}
+	t.
+\end{equation}
+	Denoting by $g := h^{-1} \in \mathcal R_{1/\alpha}^\infty$, the above translates to \eqref{eq: asymptotic inverse with alpha < 0}.
+
+	Now, suppose that there is another $g_0 \in \mathcal R_{1/\alpha}^\infty$ satisfies \eqref{eq: asymptotic inverse with alpha < 0} with $g$ replaced by $g_0$.
+	Denoting by $h_0 := g_0^{-1}$, we can verify that \eqref{eq: inverse between h and f} is valid with $h$ replaced by $h_0$.
+	According to Lemma \ref{lem: regularly variation and inverse}, $h$ and $h_0$ are asymptotic equivalent at $\infty$. 
+	Hence, so are $g$ and $g_0$.
 \end{proof}
-
+%end new added
 \begin{lem}\label{lem:regularly_variation_and_integration}
@@
 	Let $ \gamma \in \mathscr B_b(E)$ with
-\[
+\begin{equation}
 	\gamma_0
@@
 	:= \sup\{r:m(x:\gamma(x) < r) = 0\}.
-\]
+\end{equation}
 	Then $\big(\int_E t^{\gamma(x)} m(dx)\big)_{t\in (0,\infty)} \in \mathcal R^0_{\gamma_0}$.
 	Further, if $m\{x:\gamma(x) = \gamma_0\}>0$, then
-\[
+\begin{equation}
 	\int_E t^{\gamma(x)} m(dx)
 	\stackrel[t\to 0]{}{\sim}  m\{x:\gamma(x) = \gamma_0\} t^{\gamma_0}.
-\]
-
+\end{equation}
 \end{lem}
@@
 	If $\lambda \in (0,1]$, then we have
-\[
+\begin{equation}
 	\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
@@
 	\quad t\in (0,\infty).
-\]
+\end{equation}
 	This implies that
-\[
-	\limsup_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-%	\leq \lambda ^{\gamma_0}.
-	\leq \lambda ^{\gamma_0}, 	\quad t\in (0,\infty).
-\]
+\begin{equation}
+	%\limsup_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
+	\limsup_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
+	%\leq \lambda ^{\gamma_0}, 	
+	\leq \lambda ^{\gamma_0}.
+	%\quad t\in (0,\infty).
+\end{equation}
 	Also, for any $\epsilon \in (0,\infty)$, we have
-\[\begin{split}
+\begin{equation}\begin{split}
 	&\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
@@
 	\\&\quad \geq \lambda^{ \gamma_0 + \epsilon} \frac{ \int_{ \gamma(x) \leq \gamma_0 + \epsilon } t^{ \gamma(x)} m(dx) } { \int_{ \gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)}m(dx)+ \int_{\gamma(x) > \gamma_0 + \epsilon} t^{\gamma(x)}m(dx)}
-	\\&\quad = \lambda^{\gamma_0 + \epsilon} \frac{1}{1+ \frac{\int_{\gamma(x) > \gamma_0 + \epsilon}t^{\gamma(x) - (\gamma_0 + \epsilon)}m(dx)}{\int_{\gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)- (\gamma_0 + \epsilon)}m(dx)}}
-	\xrightarrow[t\to 0]{} \lambda ^{\gamma_0 + \epsilon},
-%	\quad \epsilon\in (0, \infty),
+	\\&\quad = \lambda^{\gamma_0 + \epsilon} \frac{1}{1+ \frac{\int_{\gamma(x) > \gamma_0 + \epsilon}t^{\gamma(x) - (\gamma_0 + \epsilon)}m(dx)}{\int_{\gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)- (\gamma_0 + \epsilon)}m(dx)}},
+	%\xrightarrow[t\to 0]{} \lambda ^{\gamma_0 + \epsilon},
+	%\quad t\in (0, \infty),
 	\quad t\in (0, \infty),
-\end{split}\]
+	\\&\quad \xrightarrow[(0,\infty) \ni t\to 0]{} \lambda ^{\gamma_0 + \epsilon}.
+\end{split}\end{equation}
 	where the last convergence is due to the monotone convergence theorem.
 	Therefore
-\[
-	\liminf_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-%	\geq \lambda ^{\gamma_0}.
-	\geq \lambda ^{\gamma_0}, \quad t\in (0, \infty).
-\]
+\begin{equation}
+	%\liminf_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
+	\liminf_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
+	\geq \lambda ^{\gamma_0}. 
+	%, \quad t\in (0, \infty).
+\end{equation}
 	Summarizing the above,  we get
-\[
-	\lim_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
+\begin{equation}
+	%\lim_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
+	\lim_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
 	= \lambda ^{\gamma_0},	
-%	\quad \lambda \in (0,1].
-	\quad \lambda \in (0,1], t\in (0, \infty).
-\]
+	\quad \lambda \in (0,1]. %, t\in (0, \infty).
+\end{equation}
 	If $\lambda \in (1,\infty)$, taking $f(x, t):= t^{\gamma(x)}$, from what we have proved, we also have that
-\[
-	\lim_{t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)}
-	= \lim_{t\to 0}\frac{\int_E f(x,t)m(dx)}{\int_E f(x, \lambda^{-1} t)m(dx)}
+\begin{equation}
+	%\lim_{t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)}
+	\lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)}
+	%= \lim_{t\to 0}\frac{\int_E f(x,t)m(dx)}{\int_E f(x, \lambda^{-1} t)m(dx)}
+	= \lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,t)m(dx)}{\int_E f(x, \lambda^{-1} t)m(dx)}
 	= \big((\lambda^{-1})^{\gamma_0} \big)^{-1}
-%	= \lambda ^{\gamma_0}.
-	= \lambda ^{\gamma_0}, \quad t\in (0, \infty).
-\]
+	= \lambda ^{\gamma_0}.%, \quad t\in (0, \infty).
+\end{equation}
 	This proved the first part of the lemma.
@@
 	If further we have $m\{x:\gamma(x) = \gamma_0\}>0$, then by the monotone convergence theorem  it is easy to see that
-\[
+\begin{equation}
 	\frac{\int_E t^{\gamma(x)} m(dx)}{t^{\gamma_0}}
-	\xrightarrow[t\to 0]{} m\{x:\gamma(x) = 
-	\gamma_0\}\in (0,\infty) .
-\]
+	%\xrightarrow[t\to 0]{} m\{x:\gamma(x) = 
+	\xrightarrow[(0,\infty)\ni t\to 0]{} m\{x:\gamma(x) = 
+	\gamma_0\}\in (0,\infty).
+	\qedhere
+\end{equation}
 \end{proof}
 
-\subsection{Superprocesses}
-\label{sec: Superprocesses}
-%	In this section, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
+\subsection{Superprocesses} \label{sec: Superprocesses}
 	In this subsection, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
 	It is known, see \cite[Theorem 2.23]{Li2011Measure-valued} for example, that \eqref{eq:FKPP_in_definition} can be written as
-\[\label{eq:mean-fkpp}
+\begin{equation}\label{eq:mean-fkpp}
 	V_t f(x) + \int_0^t P^\beta_{t-r} \psi_0(x,V_r f) dr
@@
 	\quad f \in \mathscr B^+_b(E), t \geq 0,x \in E,
-\]
+\end{equation}
 	where
-\[
+\begin{equation}
 	\psi_0(x,z)
@@
 	\quad x \in E,z \geq 0.
-\]
+\end{equation}
     Suppose that Assumptions \ref{asp: 1}--\ref{asp: 2} hold.
     Integrating both sides of \eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we get that
-\[\label{eq:langleVtfphiranglem_equation}
+\begin{equation}\label{eq:langleVtfphiranglem_equation}
 	\langle V_tf,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,V_r f) , \phi^*\rangle_mdr
@@
 	\quad t\geq s\geq 0, f\in \mathscr B^+_b(E).
-\]
-
-	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued 
- c\`{a}dl\`{a}g 
-paths on $[0,\infty)$.
-	We refer to $\mathbb W$ as the
-	\emph{canonical space of
-    $(X_t)_{t\geq 0}$}.
-	In fact, $(X_t)$ can be viewed
-	as a $\mathbb W$-valued random variable.
+\end{equation}
+
+	Let $\mathbb W$ be the collection of all $\mathcal M^1_E$-valued c\`{a}dl\`{a}g paths on $[0,\infty)$.
+	We refer to $\mathbb W$ as the \emph{canonical space of $(X_t)_{t\geq 0}$}.
+	In fact, $(X_t)$ can be viewed as a $\mathbb W$-valued random variable.
 	We denote the \emph{coordinate process of $\mathbb W$} by $(W_t)_{t\geq 0}$.
 
-	We say that 
-    $(X_t)_{t\geq 0}$ 
-is \emph{non-persistent}
-%	if $\mathbf P_{\delta_x}(\|X_t\|\neq 0) > 0$ for all $x\in E$ and $t> 0$.
-if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
-	Suppose that $(X_t)_{t\geq 0}$ is non-persistent,
-	then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
+	We say that $(X_t)_{t\geq 0}$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
+	Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
 \begin{itemize}
 \item
-	$\mathbb N_x [ \forall t \geq 0, \|W_t\|=0] =0$, $\mathbb N_x[\|W_0 \|\neq 0] = 0$;
+	%$\mathbb N_x [ \forall t \geq 0, \|W_t\|=0] =0$, $\mathbb N_x[\|W_0 \|\neq 0] = 0$;
+	$\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$; 
 \item
-	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Possion random
-	measure defined on some
-	probability space with mean measure $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
+	$\mathbb N_x(\|W_0 \|\neq 0) = 0$;
+\item
+	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure defined on some probability space 
+	%with mean measure $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
+	with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
 	then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
 \end{itemize}
-	We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznestov measures} of $X$.
+	We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
 	For the existence and further properties of such measures, we refer our readers to \cite{Li2011Measure-valued}.
@@
 	From  Campbell's formula, see  the proof of \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
-\[ \label{eq: equation for N measure}
+\begin{equation} \label{eq: equation for N measure}
 	- \log \mathbf P_\mu [e^{-X_t(f)}]
 	= \mathbb N_\mu[ 1-e^{- W_t(f)}],
-	\quad \mu \in \mathcal M_E^1, t>0,
-		f\in \mathscr B_b^+(E).
-\]
-	Taking $\mu = \delta_x$ for some $x\in E$, $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, 
-%	and taking $\lambda \to \infty$, we can write
-   and letting $\lambda \to \infty$, we get
-\[ \label{eq: definition of v_t(x)}
+	\quad \mu \in \mathcal M_E^1, t>0, f\in \mathscr B_b^+(E).
+\end{equation}
+	%Taking $\mu = \delta_x$ for some $x\in E$, $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and letting $\lambda \to \infty$, we get
+	For each $x\in E$ and $t\geq 0$, taking $\mu = \delta_x$ and $f = \lambda \mathbf 1_E$ with $\lambda > 0$ in the above equation, letting $\lambda \to \infty$, we get
+\begin{equation} \label{eq: definition of v_t(x)}
 	v_t(x)
 	:= \lim_{\lambda\to \infty} V_t(\lambda\mathbf 1_E)(x)
-	= -\log \mathbf P_{\delta_x} [\|X_t\|=0]
-	= \mathbb N_x[\|W_t\|\neq 0],
-	\quad t\geq 0, x\in E.
-\]
+	= -\log \mathbf P_{\delta_x} (\|X_t\|=0)
+	= \mathbb N_x(\|W_t\|\neq 0).
+\end{equation}
 	For each $\mu \in \mathcal M_E^1$ and $t > 0$, by \eqref{eq: equation for N measure}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem, we have
-\[ \label{eq: equation for mu v-t}\begin{split}
-    \mathbb N_\mu[\|W_t\|\neq 0]
-	&= -\log \mathbf P_{\mu} [\|X_t\|=0]
+\begin{equation} \label{eq: equation for mu v-t} \begin{split}
+    \mathbb N_\mu(\|W_t\|\neq 0)
+	&= -\log \mathbf P_{\mu} (\|X_t\|=0)
 	= \lim_{\lambda \to \infty} (- \log \mathbf P_\mu [e^{-\lambda X_t(\mathbf 1_E)}])
@@
 	= \mu(v_t).
-\end{split}\]
-%    It is know that for any $f\in bp{\mathscr B}$,
+\end{split} \end{equation}
 	It is know that for any $f\in\mathscr B_b^+(E)$,
-\[\label{eq: mean of kuz measure}
+\begin{equation}\label{eq: mean of kuz measure}
     \mathbb N_{\mu}[W_t(f)]
     =\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
-\]
+\end{equation}
     see \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
@@
 	Let $(\Omega, \mathscr F)$ be a measurable space with a $\sigma$-finite measure $\mu$.
-	For any $F\in \mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and
-	$\mu [F] \in (0,\infty)$.
+	For any $F\in \mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and $\mu [F] \in (0,\infty)$.
 	In this case, we define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ such that
-	$$d\mu^F= \frac{F}{\mu[F]}d \mu.$$
+\begin{equation}	
+	d\mu^F
+	= \frac{F}{\mu[F]}d \mu.
+\end{equation}
 
@@
 	Suppose that $g\in \mathscr B^+(E)$ satisfies that $\mu(P^\beta_Tg) \in (0,\infty)$.
-	We denote  the $W_T(g)$-transform of $\mathbb N_\mu$ and the $X_T(g)$-transform of $\mathbf P_\mu$
-	by $\mathbb N^{W_T(g)}_\mu$ and $\mathbf P_\mu^{X_T(g)}$ respectively.
-	The  spine decomposition theorem characterizes the law of $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ in two steps.
-	The first step of the theorem says that $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the sum of two independent measure-valued processes:
+%new 
+	Then, according to \eqref{eq: mean of kuz measure}, $\mathbf P_\mu$ (resp. $\mathbb N_\mu$) can be size-biased by $X_T(g)$ (resp. $W_T(g)$).
+%end new
+	%We denote  the $W_T(g)$-transform of $\mathbb N_\mu$ and the $X_T(g)$-transform of $\mathbf P_\mu$ by $\mathbb N^{W_T(g)}_\mu$ and $\mathbf P_\mu^{X_T(g)}$ respectively.
+	Denote by $\mathbf P_\mu^{X_T(g)}$ (resp. $\mathbb N^{W_T(g)}_\mu$) the $X_T(g)$-transform of $\mathbf P_\mu$ (resp. the $W_T(g)$-transform of $\mathbb N_\mu$).
+	%The spine decomposition theorem characterizes the law of $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ in two steps.
+	The spine decomposition theorem characterizes the law of $\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}$ in two steps.
+	%The first step of the theorem says that $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the sum of two independent measure-valued processes:
+	The first step of the theorem says that $\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the sum of two independent measure-valued processes:
 
 \begin{thm}[Size-biased decomposition,  \cite{RenSongSun2017Spine}]\label{thm: size-biased decomposition}
-\[
+%\begin{equation}
+	%\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}
+	%\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{W_T(g)}_\mu\}.
+%\end{equation}
+\begin{equation}
 	\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}
-	\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{W_T(g)}_\mu\}.
-\]
+	\overset{f.d.d.}{=} \{(X_t+W_t)_{t\geq 0}; \mathbf P_\mu  \otimes \mathbb N^{W_T(g)}_\mu\}.
+\end{equation}
 \end{thm}
 	The second step of the theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
-%	We say $\{(Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is \emph{the spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
 	We say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
@@
 \item
-	The \emph{spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is
-	the $g(\xi_T) \exp\{-\int_0^T \beta(\xi_s)ds\}$-transform
-	of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
+	The \emph{spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) \exp\{-\int_0^T \beta(\xi_s)ds\}$-transform of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
 \item
-%	Conditioned on $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, 
-Given $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, 
-%	\emph{the immigrate measure} 
-the \emph{immigration measure} 
-	$\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$
-%	with density
-	with intensity
-\[
+	Given $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, the \emph{immigration measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
+\begin{equation}
 	\mathbf m^\xi_T(ds,dw)
 	:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\]
+\end{equation}
 \item
 	$\{(Y_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is an $\mathcal M^1_E$-valued process defined by
-\[
+\begin{equation}
 	Y_t
@@
 	\quad 0 \leq t\leq T.
-\]
+\end{equation}
 \end{itemize}
@@
 	Then we have
-\[
+\begin{equation}
 	\{(Y_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}
 	\overset{f.d.d.}{=} \{(W_t)_{0\leq t\leq T}; \mathbb N_\mu^{W_T(g)}\}.
-\]
+\end{equation}
 \end{thm}
@@
 	Since $\mathbb N_{\mu}(\|W_0\|\neq 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(\|W_0\|= 0) = 1$.
-	Similarly, $\Pi_{\mu}$ is not typically a probability measure,
-	but after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
+	Similarly, $\Pi_{\mu}$ is not typically a probability measure, but after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
     We note that
-\[\begin{split}
+\begin{equation}\begin{split}
 	\Pi_{\mu}^{(T,g)} [ f(\xi_0) ]
@@
 	\int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx),
-\end{split}\]
+\end{split}\end{equation}
     which says that
-\[\label{eq: initial distribution of spine}
+\begin{equation}\label{eq: initial distribution of spine}
 	\Pi_{\mu}^{(T,g)} (\xi_0 \in dx)
@@
 	\quad x\in E.
-\]
+\end{equation}
 
 	Now, suppose that $\{\xi; \Pi\}$ satisfies Assumption \ref{asp: 1}.
-%	Denote by $\phi$ the principal eigenfunction of the mean semigroup of $X$.
     Recall that $\phi$ is the principal eigenfunction of the mean semigroup of $X$.
 	The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, considered the case when $g = \phi$ only.
-	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is,  the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$, on the finite interval $[0,T]$.
-	In fact, one can also check that this consistence property is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)$.
-	Therefore, the actual statement of the classical spine decomposition theorem is
-	different
-	from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}
-	: There is
-	no need to restrict the corresponding processes on the finite interval $[0,T]$.
+	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is, the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$,
+	%on the finite interval $[0,T]$.
+	on the finite time interval $[0,T]$.
+	%In fact, one can also check that this consistence property is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)$.
+	In fact, one can also check that 
+	%this consistence property 
+	this consistency property
+	is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)_{T\geq 0}$.
+	Therefore, the actual statement of the classical spine decomposition theorem is different from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}:
+	%There is no need to restrict the corresponding processes on the finite interval $[0,T]$.
+	There is no need to restrict the corresponding processes on the finite time interval $[0,T]$.
 	Because of its theoretical importance, we state the classical spine decomposition theorem explicitly here:
@@
 	For each $\mu \in \mathcal M_E^\phi \cap \mathcal M_E^1$, we have
-\[
+%\begin{equation}
+	%\{(X_t)_{t\geq 0}; \mathbf P_\mu^{(\phi)}\}
+	%\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{(\phi)}_\mu\}.
+%\end{equation}
+\begin{equation}
 	\{(X_t)_{t\geq 0}; \mathbf P_\mu^{(\phi)}\}
-	\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{(\phi)}_\mu\}.
-\]
+	\overset{f.d.d.}{=} \{(X_t + W_t)_{t\geq 0}; \mathbf P_\mu \otimes \mathbb N^{(\phi)}_\mu\}.
+\end{equation}
 	Here, the probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of the process $(X_t)_{t\geq 0}$ is
-\[
-	d ( \mathbf P_\mu^{(\phi)}|_{\mathscr F_t^X}) = \frac{X_t(\phi)}{ \mu(\phi)} d(\mathbf P_\mu|_{\mathscr F_t^X}),
+\begin{equation}
+	d ( \mathbf P_\mu^{(\phi)}|_{\mathscr F_t^X}) 
+	= \frac{X_t(\phi)}{ \mu(\phi)} d(\mathbf P_\mu|_{\mathscr F_t^X}),
 	\quad t\geq 0;
-\]
+\end{equation}
 	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of the process $(W_t)_{t\geq 0}$ is
-\[
+\begin{equation}
 	d(\mathbb N_\mu^{(\phi)} |_{\mathscr F^W_t}  )
@@
 	\quad t\geq 0.
-\]
+\end{equation}
 \end{cro}
 
-	Let $\mu \in \mathcal M^{(\phi)}_\mu$, we say
-	$\{(\xi_t)_{t\geq 0}, \mathbf n, (Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$
-%	is \emph{the spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
-	is a \emph{spine representation of $\mathbb N^{(\phi)}_\mu$}  if:
+	Let $\mu \in \mathcal M^{(\phi)}_\mu$, we say $\{(\xi_t)_{t\geq 0}, \mathbf n, (Y_t)_{ t\geq 0}; \dot {\mathbf P}^{(\phi)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{(\phi)}_\mu$} if:
 \begin{itemize}
@@
 	The \emph{spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is
-\[
+\begin{equation}
 	d(\Pi_{\mu}^{(\phi)} |_{\mathscr F_t^\xi})
@@
 	\quad t\geq 0;
-\]
+\end{equation}
 \item
 	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with
-%   density
     intensity
-\[\label{eq:meanMeasImmigr}
+\begin{equation}\label{eq:meanMeasImmigr}
 	\mathbf m^\xi(ds,dw)
 	:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\]
+\end{equation}
 \item
 	$\{(Y_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is an $\mathcal M^1_E$-valued process defined by
-\[\label{eq:defSpinImmigr}
+\begin{equation}\label{eq:defSpinImmigr}
 	Y_t
@@
 	\quad t\geq 0.
-\]
+\end{equation}
 \end{itemize}
@@
 	Then we have
-\[
+\begin{equation}
 	\{(Y_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}
 	\overset{f.d.d.}{=} \{(W_t)_{t\geq 0}; \mathbb N_\mu^{(\phi)}\}.
-\]
+\end{equation}
 \end{cro}
@@
 	For the sake of generality, the spine decomposition theorems above are all stated with respect to a general initial configuration $\mu$.
-	If $\mu = \delta_x$ for some $x\in E$, then by
-	\eqref{eq: initial distribution of spine}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$.
+	If $\mu = \delta_x$ for some $x\in E$, then by \eqref{eq: initial distribution of spine}, we have $\Pi_{\delta_x}^{(T,g)} (\xi_0 = x) = 1$, so sometimes we write $\Pi_x^{(T,g)}$ for $\Pi_{\delta_x}^{(T,g)}$.
 	Similarly, we write $\Pi_x^{(\phi)}$ for $\Pi_{\delta_x}^{(\phi)}$.
@@
 \label{sec: Ergodicity}
-	In this subsection, we discuss the ergodicity of the spine processes
-	$\{(\xi_t); (\Pi^{(\phi)}_x)\}$
-	under Assumptions \ref{asp: 1}--\ref{asp: 3}.
+	%In this subsection, we discuss the ergodicity of the spine processes $\{(\xi_t); (\Pi^{(\phi)}_x)\}$ under Assumptions \ref{asp: 1}--\ref{asp: 3}.
+	In this subsection, we discuss the ergodicity of the spine process $\{(\xi_t)_{t\geq 0}; (\Pi^{(\phi)}_x)_{x\in E}\}$ under Assumptions \ref{asp: 1}--\ref{asp: 3}.
 	According to \cite{KimSong2008Intrinsic}, $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
-\[
+\begin{equation}
 	q_t(x,y) := \frac{\phi(y)}{\phi(x)} p^\beta_t(x,y),
 	\quad x,y\in E, t>0.
-\]
+\end{equation}
 	Let $c_0>0$ and $c_1>0$ be the constants  in \eqref{eq:q(t,x,y)}, then we have
-\[\label{eq: asymptotic for q_t(x,y)}
+\begin{equation}\label{eq: asymptotic for q_t(x,y)}
 	\sup_{x\in E} \Big| \frac{q_t(x,y)}{\phi(y)\phi^*(y)} - 1\Big|
@@
 	\quad t > 1.
-\]
+\end{equation}
 	This implies that the process $\{\xi; \Pi^{(\phi)}_x\}$ is ergodic.
@@
 	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, 
-	then we have
-\[
+	%then we have
+	then
+\begin{equation}
 	\int_0^1 F(\xi_{(1-u)t},u,t) du
@@
 	\quad x\in E.
-\]
+\end{equation}
 \end{lem}
@@
 	Define $F(y,u):= \limsup_{t\to \infty} F(y,u,t)$ for each $y\in E$ and $u \in [0,1]$.
-	Then, for each $x\in E$ and $p \geq 1$, we have
-\[
+	Then, for each $x\in E$ and $p \geq 1$, %we have
+\begin{equation}
 	\limsup_{ t \to \infty}  \Big\| \int_0^1 F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
@@
 	For each $(y,u,t)\in E\times [0,1]\times [0,\infty)$, define $\bar F(y,u,t) := \sup_{s:s\geq t} F(y,u,s)$.
-	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$
-such that
-\[
+	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$ such that
+\begin{equation}
 	F(x,u)
@@
 	\quad x\in E, u\in [0,1].
-\]
+\end{equation}
 	From Lemma \ref{lem: ergodicity of the underlying process}, we know that
-\[
+\begin{equation}
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
@@
 	\quad x\in E,
-\]
+\end{equation}
     which implies convergence in probability.
 	The bounded convergence theorem then gives that, for each $p \geq 1$,
-\[
+\begin{equation}
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
@@
 	\quad x\in E.
-\]
+\end{equation}
 	Finally,
-     noting that that
-	$0\leq F \leq \bar F$, we get
-\[\begin{split}
+    %noting that that
+    noting that $0\leq F \leq \bar F$, we get
+\begin{equation}\begin{split}
 	& \limsup_{ t \to \infty}  \Big\| \int_0^1 F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
@@
 	\\& \quad = \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle du,
-	\quad x\in E,
-\end{split}\]
-	as desired.
+	%\quad x\in E,
+	\quad x\in E. \qedhere
+\end{split}\end{equation}
 \end{proof}
@@
 \label{sec: proof of result 1}
-%	Let $\{X; \mathbf P\}$ be a superprocess satisfying
 	Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
-%    In this section, we will prove the following stronger result:
 	In this subsection, we will prove the following result stronger than non-persistency:
 
-\begin{prop}
-\label{prop: non-presistent}
+\begin{prop} \label{prop: non-presistent}
 	For each $t > 0$, $\inf_{x\in E} \mathbf P_{\delta_x}(\|X_t\|= 0) > 0$.
-
 \end{prop}
@@
 \begin{proof}
-      Recall that $\kappa_0 = \text{essinf}_{m(dx)} \kappa(x) $ and $\gamma_0 = \text{essinf}_{m(dx)} \gamma(x)$.
+    Recall that $\kappa_0 = \operatorname{ess\,inf}_{m(dx)} \kappa(x) $ and $\gamma_0 = \operatorname{ess\,inf}_{m(dx)} \gamma(x)$.
 	For each $x\in E$, let $\tilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\tilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$.
     Then, we know that $m(\tilde \kappa \neq \kappa) = 0$ and $m(\tilde \gamma \neq \gamma) = 0$.
-	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then we have that, for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z) $
-	%almost everywhere with respect to the measure $m$.
-	$m$-almost everywhere.
+	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, 
+	%then we have that, 
+	then for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z),$ $m$-almost everywhere.
 
 	If we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
-\[
+\begin{equation}
 	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \widetilde \psi (\xi_s,V_{t-s} f) ds \Big]
 	=\Pi_x \big[ f(\xi_t)\mathbf 1_{t<\zeta} \big].
-\]
-	So, we can consider
-	$\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
+\end{equation}
+	So, we can consider $\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
 	Define
-\[
+\begin{equation}
 	\widehat\psi(z)
@@
 	\quad z\geq 0.
-\]
+\end{equation}
 	Using the fact that $\gamma_0 > 1$ and $\kappa_0 > 0$, it is easy to verify that
-\[
+\begin{equation}
 	\inf_{x\in E}\widetilde \psi(x,z)
@@
 	\quad \hat \psi(+\infty) = +\infty.
-\]
+\end{equation}
 	Therefore $\widetilde \psi$ satisfies the condition of \cite[Lemma 2.3]{RenSongZhang2015Limit}.
-	As a consequence,
-	we have the desired result.
+	As a consequence, we have the desired result.
 \end{proof}
@@
 \label{sec: proof of result 2}
-%	Let $\{X; \mathbf P\}$ be a superprocess satisfies
 	Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
-	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent,
-    that is, 
-\[
+	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent, that is, 
+\begin{equation}
     \mathbf P_{\delta_x}(\|X_t\| = 0)
@@
     \quad t>0, x \in E.
-\]
+\end{equation}
 	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have
-\[
+\begin{equation}
     \mathbf P_{\delta_x}(\|X_t\|= 0)<1,
     \quad t>0, x \in E.
-\]
-	From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$.
-	According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp},
-	by monotonicity, we see that $v_t$ satisfies the equation
-\[
+\end{equation}
+	%From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$.
+	From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
+	According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp}, by monotonicity, 
+	%we see that $v_t$ satisfies the equation
+	we see that $(v_t)_{t > 0}$ satisfies the equation
+\begin{equation}
 	v_{s+t}(x) + \int_0^t P^\beta_{t-r} \psi_0(x,v_{s+r}) dr
@@
 	\quad s>0, t \geq 0,x \in E.
-\]
-
-		Notice that,
-	under  Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
+\end{equation}
+
+	Notice that, under Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
 	Therefore, $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
@@
 	According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem, 
-%	we have another equation
-$v_t$ also satisfies the equation
-\[ \label{eq: equation of <vt,phi>}
+	%$v_t$ also satisfies the equation
+	$(v_t)_{t> 0}$ also satisfies the equation
+\begin{equation} \label{eq: equation of <vt,phi>}
 	\langle v_t,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,v_t) , \phi^*\rangle_m dr
@@
 	\quad s, t > 0.
-\]
+\end{equation}
 	One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example,
-\[\label{eq: uniform converges to 0}
+\begin{equation} \label{eq: uniform converges to 0}
     \|\phi^{-1}v_t\|_{\infty} \xrightarrow[t\to \infty]{} 0.
-\]
-	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only 
-	%have to consider the speed of this convergence.
-	 need to consider the speed of this convergence.
+\end{equation}
+	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only need to consider the speed of this convergence.
 	This is answered in two steps.
@@
 \label{prop: regularly varying of vt-phi-star}
-	$\langle v_t,\phi^*\rangle_m $ is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
+	%$\langle v_t,\phi^*\rangle_m $ is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
+	$(\langle v_t,\phi^*\rangle_m)_{t> 0} $ is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
-\[
+\begin{equation}
 	\langle v_t,\phi^*\rangle_m
 	\stackrel[t\to \infty]{}{\sim} \big(C_X(\gamma_0-1) t \big)^{-\frac{1}{\gamma_0 - 1}},
-\]
+\end{equation}
 	where $C_X:= \langle \mathbf 1_{\gamma= \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m $.
@@
 
-	Notice that
-	Theorem \ref{thm: main theorem}(2) is simply a corollary of Propositions \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.
+%deleted
+	%Notice that Theorem \ref{thm: main theorem}(2) is simply a corollary of Propositions \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.
+%end delted
 
@@
 	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
-	For each $\mu\in\mathcal M^\phi_E$, denote by
-%	$\{(Y_t), (\xi_t),\mathbf m^\xi, \mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$
-$\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$
-	the spine representation of $\mathbb N^{(\phi)}_\mu$.
+	For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$.
 	According to \eqref	{eq: equation for mu v-t}, \eqref{eq: mean of kuz measure} and Theorem \ref{thm: spine representation},
 	we have that for each $t>0$,
-\[\begin{split}\label{eq:vt-and-Y}
+\begin{equation}\begin{split}\label{eq:vt-and-Y}
 	&\langle \mu,\phi \rangle \dot {\mathbf P}^{(\phi)}_\mu [Y_t(\phi)^{-1}]
@@
 	= \mu(v_t).
-\end{split}\]
+\end{split}\end{equation}
 	Taking $\mu = \delta_x$ in \eqref{eq:vt-and-Y}, we get $(\phi^{-1}v_t)(x) =\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]$.
 	Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
-	Therefore, to complete the proof,
-	we only need to show that
-\[
+	Therefore, to complete the proof, we only need to show that
+\begin{equation}
 	\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
 	\stackrel[t\to \infty]{x\in E}{\sim}  \dot {\mathbf P}_\nu^{(\phi)} [Y_t(\phi)^{-1}].
-\]
+\end{equation}
 
 	For any $t>0$ and any $G\in \mathscr B((0,t])$, define
-$
+\begin{equation}
 	Y^G_t
 	:= \int_{G\times \mathbb W} w_{t-s} \mathbf n(ds,dw).
-$
+\end{equation}
 	Then for any $0 < t_0 < t$, we can decompose $Y_t$ into
-$
+\begin{equation}
 	Y_t
 	= Y^{(0,t_0]}_t + Y^{(t_0,t]}_t.
-$
+\end{equation}
 	Using this decomposition, for each $0<t_0<t<\infty$ and $x\in E$, we have
-\[\label{eq: starting point of phi-1v_t(x)}
+\begin{equation}\label{eq: starting point of phi-1v_t(x)}
 	 \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
 	= \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] + \epsilon_x^1(t_0,t) +\epsilon_x^2(t_0,t),
-\]
+\end{equation}
 	where
-\[\begin{split}
+\begin{equation}\begin{split}
 	\epsilon_x^1(t_0,t)
@@
 	&:= \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1} - Y^{(t_0,t]}_t(\phi)^{-1}].
-\end{split}\]
-
-	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$,
-	we have that
-\[\label{eq: some equations for PY-1}\begin{split}
+\end{split}\end{equation}
+
+	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, we have that
+\begin{equation}\label{eq: some equations for PY-1}\begin{split}
 	\dot{\mathbf P}^{(\phi)} [Y_t^{(t_0,t]}(\phi)^{-1}|\mathscr F^\xi_{t_0}]
@@
 	=  \int_E  q_{t_0}(x,y)(\phi^{-1}v_{t-t_0})(y) m(dy).
-\end{split}\]
+\end{split}\end{equation}
 
@@
 	We claim that
-\[\label{eq: bound for epsilon1}
+\begin{equation}\label{eq: bound for epsilon1}
 	|\epsilon_x^1(t_0,t)|
@@
     \quad t_0 > 1.
-\]
+\end{equation}
 	In fact,
-\[\label{eq:epsilon-1}\begin{split}
+\begin{equation}\label{eq:epsilon-1}\begin{split}
 	|\epsilon_x^1(t_0,t)|
 	& = \big| \dot {\mathbf P}_{\delta_x}^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] - \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] \big| \\
-	& = \big|  \int_E  q_{t_0}(x,y)(\phi^{-1}v_{t-t_0})(y) m(dy) - \langle v_{t-t_0},\phi^* \rangle_m \big|\\
+	& = \Big|  \int_E  q_{t_0}(x,y)(\phi^{-1}v_{t-t_0})(y) m(dy) - \langle v_{t-t_0},\phi^* \rangle_m \Big|\\
 	& \leq \int_{y\in E} \big| q_{t_0}(x,y) - (\phi\phi^*)(y) \big| (\phi^{-1}v_{t-t_0})(y) m(dy)\\
 	& \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m .
-\end{split}\]
+\end{split}\end{equation}
 
 	We now claim that, if $t_0 > 1$ and $t-t_0$ is large enough, then
-\[\label{eq:upperbound_of_epsilon-2}
+\begin{equation}\label{eq:upperbound_of_epsilon-2}
 	|\epsilon_x^2(t_0,t)|
 	\leq t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
-\]
-	In fact, using the Markov property of the spine process $(\xi_t)$ and the property of Poisson random measures, we have
-\[\label{eq:epsilon-2}\begin{split}
+\end{equation}
+	%In fact, using the Markov property of the spine process $(\xi_t)$ and the property of Poisson random measures, we have
+	In fact, using the Markov property of the spine process and the property of Poisson random measures, we have
+\begin{equation}\label{eq:epsilon-2}\begin{split}
 	|\epsilon_x^2(t_0,t)|
@@
 	\\&= \dot{\mathbf P}_{\delta_x}^{(\phi)} \big[\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}(\phi)\neq 0}|\mathscr F^\xi_{t_0}] \cdot \dot{\mathbf P}_{\delta_x}^{(\phi)} [ Y^{(t_0,t]}_t(\phi)^{-1}|\mathscr F^\xi_{t_0}] \big].
-\end{split}\]
+\end{split}\end{equation}
 	On one hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1}, we know that
-\[\label{eq:epsilon-2-final}\begin{split}
+\begin{equation}\label{eq:epsilon-2-final}\begin{split}
 	\dot{\mathbf P}_{\delta_x}^{(\phi)}[ Y^{(t_0,t]}_t(\phi)^{-1}]
 	\leq (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
-\end{split}\]
+\end{split}\end{equation}
 	On the other hand, since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
-	Then, if $t-s > t-t_0 \geq s_0$, using the fact that  that $v_t$ is non-increasing in $t$, we get
-\[\begin{split}
+	Then, if $t-s > t-t_0 \geq s_0$, 
+	%using the fact that that $v_t$ is non-increasing in $t$, we get
+	using the fact that $v_t$ is non-increasing in $t$, we get
+\begin{equation}\begin{split}
 	\kappa(x)\gamma(x) v_{t-s}(x)^{\gamma(x)-1}
@@
 	\leq \|\kappa\gamma\phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
-\end{split}\]
+\end{split}\end{equation}
 	Therefore, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have,  for $t-t_0 \geq s_0$,
-\[\begin{split}
-	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]
-	\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]\big)
+\begin{equation}\begin{split}
+	%&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]
+	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
+	%\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]\big)
+	\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{ \| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]\big)
 	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
 	=  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
-	\\&\quad = -\log \lim_{\lambda \to \infty}
-	\exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
-	\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{w_{t-s} \not \equiv 0} \mathbf m^\xi(ds,dw)
-	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{X_{t-s} \not\equiv 0}]\pi(\xi_s,dy)
+	\\&\quad = -\log \lim_{\lambda \to \infty} \exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
+	%\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{ w_{t-s} \not \equiv 0} \mathbf m^\xi(ds,dw)
+	\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{ \|w_{t-s}\| \neq 0} \mathbf m^\xi(ds,dw)
+	%= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{X_{t-s} \not\equiv 0}]\pi(\xi_s,dy)
+	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{ \|X_{t-s}\| \neq 0}]\pi(\xi_s,dy)
 	\\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
@@
 	\\&\quad \leq  t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
-\end{split}\]
+\end{split}\end{equation}
 Combining this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
 
-Now, for
-$0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough,
-	according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1}, \eqref{eq: bound for epsilon1} and \eqref{eq:epsilon-2-final}, we have
-\[\label{vts-inequality}\begin{split}
+	Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1}, \eqref{eq: bound for epsilon1} and \eqref{eq:epsilon-2-final}, we have
+\begin{equation}\label{vts-inequality}\begin{split}
 	&\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0},\phi^* \rangle_m}-1 \Big|
@@
 	\cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
-\end{split}\]
-	According to \eqref{eq: uniform converges to 0},
-	there exists a map $t\mapsto t_0(t)$ such that,
-\[
+\end{split}\end{equation}
+	According to \eqref{eq: uniform converges to 0}, there exists a map $t\mapsto t_0(t)$ such that,
+\begin{equation}
 	t_0(t)
@@
 	\xrightarrow[t\to\infty]{} 0.
-\]
+\end{equation}
 	Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
-\[\label{eq:k1}
+\begin{equation}\label{eq:k1}
 	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
 	\xrightarrow[t\to\infty]{} 0.
-\]
+\end{equation}
 	Notice that
-\[\label{eq:k2}\begin{split}
+\begin{equation}\label{eq:k2}\begin{split}
 	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
@@
 	\xrightarrow[t\to\infty]{} 0.
-\end{split}\]
+\end{split}\end{equation}
 	Now, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
-\[
+\begin{equation}
 	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
 	\xrightarrow[t\to\infty]{} 0,
-\]
+\end{equation}
 	as desired.
@@
 	From \eqref{eq: equation of <vt,phi>} we know that $\langle v_t,\phi^* \rangle_m$ is continuous and strictly decreasing in $t \in (0,\infty)$.
-	Since the superprocess $(X_t)_{t\geq 0}$
-	is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$, $\mathbf P_\mu (X_t \not \equiv 0) \xrightarrow[t\to 0]{} 1$.
+	Since the superprocess $(X_t)_{t\geq 0}$ is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$, 
+	%$\mathbf P_\mu (X_t \not \equiv 0) \xrightarrow[t\to 0]{} 1$.
+	$\mathbf P_\mu (\|X_t\| \neq 0) \xrightarrow[t\to 0]{} 1$.
 	Taking $\mu = \nu$, according to \eqref{eq: equation for mu v-t}, we have that $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to 0]{} +\infty$.
-	On the other hand,
-	according to \eqref{eq: uniform converges to 0},
-	we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
-	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse on $(0,\infty)$
-which is denoted by
-\[
+	On the other hand, according to \eqref{eq: uniform converges to 0}, we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
+	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse on $(0,\infty)$ which is denoted by
+\begin{equation}
 	R: (0,\infty) \to (0,\infty).
-\]
+\end{equation}
 
 	Now, if we denote by
-\[
+\begin{equation}
 	\epsilon_{t}(x)
@@
 	\quad t>0, x\in E.
-\]
+\end{equation}
 	Then, we have
-\[\label{eq: change variable using inverse}
+\begin{equation}\label{eq: change variable using inverse}
 	v_t(x)
@@
 	\quad t>0, x\in E.
-\]
+\end{equation}
 	Further, by Proposition \ref{prop: convergence in a same speed} and 
 	the fact that $R(u)\xrightarrow[u\to 0]{} \infty$, we have
-\[\label{eq: epsilon R converges to 0}
+\begin{equation}\label{eq: epsilon R converges to 0}
 	\sup_{x\in E}|\epsilon_{R(u)}(x)|
 	\xrightarrow[u\to 0]{} 0.
-\]
+\end{equation}
 
 	Now, by \eqref{eq: equation of <vt,phi>}, we have
-\[
+\begin{equation}
 	\frac{d \langle v_r, \phi^* \rangle_m}{dr}
@@
 	> 0
-\]
-%	almost everywhere for $r\in (0,\infty)$ with respect to the Lebesgue measure.
-for Lebesgue 
-	Therefore, we have almost every $r\in (0,\infty)$.
-\[\begin{split}
+%new 
+	\quad a.e..
+%end new
+\end{equation}
+%for Lebesgue 
+	%Therefore, we have almost every $r\in (0,\infty)$.
+	Therefore,
+\begin{equation}\begin{split}
 	s-t
@@
 	\\&= \int_{\langle v_s,\phi^*\rangle}^{\langle v_t, \phi^* \rangle} \big\langle \psi_0 \big( \cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du.
-\end{split}\]
+\end{split}\end{equation}
 	Letting $t\to 0$, we get
-\[
+\begin{equation}
 	s
@@
 	\quad s\in (0,\infty).
-\]
+\end{equation}
 	Since $R$ is the inverse of $t\mapsto \langle v_t,\phi^*\rangle$, the above implies that
-\[\label{eq: integral equation for R}
+\begin{equation}\label{eq: integral equation for R}
 	R(r)
-	= \int_r^\infty \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)}(x) ) u \phi \big), \phi^* \big\rangle_m^{-1} du,
+	%= \int_r^\infty \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)}(x) ) u \phi \big), \phi^* \big\rangle_m^{-1} du,
+	= \int_r^\infty \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du,
 	\quad r\in (0,\infty).
-\]
-
-%	We are interested in checking the regularly varying property of $R(r)$ at $r=0$.
+\end{equation}
+
 	We now check the regularly varying property of $R(r)$ at $r=0$.
-	This can be done by considering the regularly varying property of 
-	%$\big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at
-%	$u = 0$.
- $u\to \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$
- at 0.
+	This can be done by considering the regularly varying property of $u\to \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m$ at 0.
     According to \eqref{eq: epsilon R converges to 0},  $1+ \epsilon_{R(u)}(x) \stackrel[u\to 0]{x\in E}{\sim} 1$.
@@
 	Therefore, from Lemma \ref{lem: asymptotic equivalent of integration}, we have that
-\[\label{eq: regularly part in the integration}\begin{split}
+\begin{equation}\label{eq: regularly part in the integration}\begin{split}
 	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
@@
 	\\ &\quad \stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_{m(dx)}.
-\end{split}\]
+\end{split}\end{equation}
 	According to Lemma \ref{lem:regularly_variation_and_integration}, 
- and using the fact that
-$\kappa(x)\phi(x)^\gamma(x)$ is bounded and the measure $\phi^* dm$ is finite, we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
-	Notice that $-\gamma_0 < 0$, according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
-	Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and \eqref{eq: inverse of a regularly varying function with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.
+	%and using the fact that $\kappa(x)\phi(x)^\gamma(x)$ is bounded and the measure $\phi^* dm$ is finite, 
+	and using the fact that $\kappa(x)\phi(x)^{\gamma(x)}$ is bounded and the measure $\phi^* dm$ is finite, 
+	we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
+	%Notice that $-\gamma_0 < 0$, 
+	Noticing that $-(\gamma_0 - 1) < 0$,
+	according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
+	%Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and \eqref{eq: inverse of a regularly varying function with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.
+	Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and Corollary \ref{cro: regularly varing and inverse with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.
 
 	Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration} and \eqref{eq: regularly part in the integration}, we know that
-\[\begin{split}
-	&\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
+\begin{equation}\begin{split}
+	%&\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
+	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
 	\stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x)
@@
 	=: C_X u^{\gamma_0}.
-\end{split}\]
-	Therefore, we have $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
-	Now according to
-	Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}
-	we have that
-\[\begin{split}
+\end{split}\end{equation}
+	%Therefore, we have $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
+	Therefore, we have $\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
+	Now according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R} we have that
+\begin{equation}\begin{split}
 	R(r)
-	&= \int_r^\infty \big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
+	%&= \int_r^\infty \big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
+	&= \int_r^\infty \big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
 	= \int_r^\infty u^{-\gamma_0} l(u) du
@@
 	\\&\stackrel[r\to 0]{}{\sim} C_X^{-1} (\gamma_0-1)^{-1} r^{-(\gamma_0 - 1)}.
-\end{split}\]
-	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from
-	\eqref{eq: inverse and power equivalent with alpha < 0} and above,
+\end{split}\end{equation}
+	%Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from \eqref{eq: inverse and power equivalent with alpha < 0} and above,
+	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from Corollary \ref{cro: regularly varing and inverse with alpha < 0} and above,
 	we have
-\[
+\begin{equation}
 	\langle v_r,\phi^*\rangle_m
-	\stackrel[r\to \infty]{}{\sim} \big(C_X (\gamma_0-1) r \big)^{-\frac{1}{\gamma_0 - 1}}.
-\]
+	\stackrel[r\to \infty]{}{\sim} \big(C_X (\gamma_0-1) r \big)^{-\frac{1}{\gamma_0 - 1}}. \qedhere
+\end{equation}
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{thm: main theorem}(2)]
+	According to \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0}, 
+\begin{equation}
+	- \log \mathbf P_\mu(\|X_t\| = 0) 
+	= \mu(v_t)
+	\leq \mu(\phi) \| \phi^{-1} v_t\|_{\infty}
+	\xrightarrow[t\to \infty]{} 0.
+\end{equation}
+	Therefore, $\mathbf P_\mu(\|X_t\| \neq 0) \xrightarrow[t\to \infty]{} 0$.
+
+	Noticing that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, according to \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed}, we have
+\begin{equation}
+	\mathbf P_\mu(\|X_t\| \neq 0)
+	\stackrel[t\to \infty]{}{\sim} - \log \mathbf P_\mu(\|X_t\| = 0)
+	= \mu(\phi \phi^{-1}v_t)
+	\stackrel[t\to\infty]{}{\sim} \mu(\phi) \langle v_t, \phi^*\rangle_m.
+\end{equation}
+	Therefore, according to Proposition \ref{prop: regularly varying of vt-phi-star}, we get the desired result.
 \end{proof}
@@
 \label{sec: conditional distribution}
-	Let $\{(X_t)_{t\geq 0}; \mathbf P\}$
-    be a $(\xi, \psi)$-superprocess satisfying
+	Let $\{(X_t)_{t\geq 0}; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
 	Suppose  $m(x: \gamma(x) = \gamma_0)>0$.
-	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | \|X_t\| \neq 0\big)\big\}$
-	converges weakly
-	to a non-degenerate distribution for a large class of functions $f$ and initial configurations $\mu$.
+	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | \|X_t\| \neq 0\big)\big\}$ converges weakly to a non-degenerate distribution for a large class of functions $f$ and initial configurations $\mu$.
 	Our guess of $(\eta_t)$ is
-\[\label{eq: definition of eta}
+\begin{equation}\label{eq: definition of eta}
 	\eta_t
@@
 	\quad t\geq 0,
-\]
+\end{equation}
 	because in this case
- \[
+ \begin{equation}
  	\mathbf P_{\delta_x}[\eta_t X_t(f)|\|X_t\|\neq 0]
@@
 	\stackrel[t\to \infty]{}{\sim}  \langle f,\phi^* \rangle_m.
- \]
+ \end{equation}
  	Here we have used Theorem \ref{thm: main theorem}(2) and the fact that (see \eqref{eq:q(t,x,y)})
- \[
+ \begin{equation}
  	P^\beta_t f(x)
@@
  	\xrightarrow[t\to \infty]{}  \phi(x) \langle f,\phi^*\rangle_m.
- \]
-
-%From the point of Laplace transform,
-From the point of view of Laplace transforms,
-% the desired result that 
-the desired result that, for any $f\in \mathscr B^+_b(E)$ and $x\in E$,
- $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$
- converge weakly
- 	to some probability distribution $F_{f,x}$ is equivalent to the following convergence:
-\[\begin{split}
- 	\frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\eta_t}
-	&= \frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\mathbf P_{\delta_x}(\|X_t\|\neq 0)} \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }\\
-	&= \mathbf P_{\delta_x}[1-e^{-\theta \eta_t X_t(f)}|\|X_t\|\neq 0]  \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }
-	\\& \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
-\end{split}\]
-	Further, since $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
-\[\label{eq: equivalent result}
-	\frac{V_t(\theta \eta_t f)(x)}{\eta_t}
-	\quad \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
-\]
-	Therefore, to
-	establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
-
-	In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, 
-	%we need to characterize the dynamics of $V_t(\theta f)$ as $\theta$ is varying.
-	we need to investigate the properties of $\theta\to V_t(\theta f)$.
-	(Note that \eqref{eq:mean-fkpp} 
-	%only characterizes the dynamics of $V_t(\theta f)$ as $t$ is varying.)
-	only gives the the dynamics of $t\to V_t(\theta f)$.)
+ \end{equation}
+
+	%From the point of view of Laplace transforms, the desired result that, for any $f\in \mathscr B^+_b(E)$ and $x\in E$, $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ converge weakly to some probability distribution $F_{f,x}$ is equivalent to the following convergence:
+	From the point of view of Laplace transforms, the desired result that, for any $f\in \mathscr B^+_b(E)$ and $\mu\in \mathcal M_E^1$, $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\mu}(\cdot | \|X_t\| \neq 0)\big\}$ converge weakly to some probability distribution
+	%$F_{f,x}$ 
+	$F_f$
+	is equivalent to the following convergence:
+\begin{equation}
+ 	%\frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\eta_t}
+	%&= \frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\mathbf P_{\delta_x}(\|X_t\|\neq 0)} \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }\\
+	%&= \mathbf P_{\delta_x}[1-e^{-\theta \eta_t X_t(f)}|\|X_t\|\neq 0]  \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }
+	%\\& \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du). 
+	\mathbf P_\mu[1- e^{-\theta \eta_t X_t(f)} | \|X_t\|\neq 0]
+	= \frac{1- \exp\{- \mu\big(V_t(\theta \eta_t f)\big) \}}{\mathbf P_\mu(\|X_t\|\neq 0)}
+	\xrightarrow[t\to \infty]{} \int_{[0,\infty)}(1-e^{-\theta u}) F_f(du).
+\end{equation}
+	%Further, since $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
+	According to Theorem \ref{thm: main theorem}(2) and $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
+\begin{equation}\label{eq: equivalent result}
+	%\frac{V_t(\theta \eta_t f)(x)}{\eta_t}
+	%\quad \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
+	\frac{\mu\big( V_t(\theta \eta_t f) \big)}{ \eta_t}
+	\quad \xrightarrow[t\to \infty]{} \mu(\phi) \int_{[0,\infty)}(1-e^{-\theta u})F_{f}(du).
+\end{equation}
+	%Therefore, to establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
+	Therefore, to establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
+
+	%In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, 
+	In order to investigate the convergence of $\mu\big( V_t(\theta \eta_t f) \big)/ \eta_t$, we need to investigate the properties of $\theta\to V_t(\theta f)$.
+	(Note that \eqref{eq:mean-fkpp} only gives the the dynamics of $t\to V_t(\theta f)$.)
 	This is done in the following proposition:
@@
 	For any $f\in \mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we have
-\[\label{eq: equation for Vt(theta f) for theta}
+\begin{equation}\label{eq: equation for Vt(theta f) for theta}
 	V_T ( \theta f) ( x)
 	= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr.
-\]
+\end{equation}
 \end{prop}
@@
 	It follows from Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
-\[
+\begin{equation}
 	\frac{ \mathbf P_{\delta_x}[X_T(f)e^{-\theta X_T(f)}] } {  \mathbf P_{\delta_x} [X_T(f)] }
@@
 	= \mathbf P_{\delta_x} [e^{-\theta X_T(f)}] \dot {\mathbf P}_x^{(T,f)}[e^{-\theta Y_T(f)}],
-\]
-%	where $\{Y; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with spine process $\xi$,
-%immigration measure
-%	$\mathbf n_T$ and
-%conditional mean measure
-%	$\mathbf m^\xi_T$.
-where $\{(\xi)_{0\le t\le T}, \mathbf n_T, (Y)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$ is a spine representation of $\mathbb N^{W_T(f)}_x$ with $\mathbf m^\xi_T$ being the 
-intensity if the immigration measure $\mathbf n_T$ conditioned on $\{(\xi)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$.
+\end{equation}
+	where $\{(\xi)_{0\le t\le T}, \mathbf n_T, (Y)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$ is a spine representation of $\mathbb N^{W_T(f)}_x$ with $\mathbf m^\xi_T$ being the intensity of the immigration measure $\mathbf n_T$ conditioned on $\{(\xi)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$.
 	From this, we have
-\[ \label{eq: dynamic of theta on v_t theta reason 1}
+\begin{equation} \label{eq: dynamic of theta on v_t theta reason 1}
 	\frac{\partial}{\partial_\theta}
@@
 	= P^\beta_T f(x) \dot {\mathbf P}_x^{(T,f)}[e^{-\theta Y_T(f)}].
-\]
-	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$,
-	then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
-\[\label{eq: dynamic of theta on v_t theta reason 2}\begin{split}
+\end{equation}
+	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
+\begin{equation}\label{eq: dynamic of theta on v_t theta reason 2}\begin{split}
 	&-\log \dot {\mathbf P}^{(T,f)}_{x}[e^{-\theta \mathbf n_T(F)}|\mathbf m_T^\xi]
@@
 	\\&\quad = \int_0^T \big(\kappa\gamma V_{T-s}(\theta f)^{\gamma-1}\big)(\xi_s) ds.
-\end{split}\]
+\end{split}\end{equation}
 	Note that, since $\mathbf n_T(F)= Y_T(f)$, we can derive from \eqref{eq: dynamic of theta on v_t theta reason 1} and \eqref{eq: dynamic of theta on v_t theta reason 2} that
-\[\begin{split}
+\begin{equation}\begin{split}
 	V_T(\theta f)(x)
 	&= -\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}]
-	= \int_0^\theta
-P^\beta_Tf(x)
+	= \int_0^\theta P^\beta_Tf(x)
 	\dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
@@
 	\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr,
-\end{split}\]
+\end{split}\end{equation}
 	as required.
@@
 
-\[\label{eq: equation for normalized V_T}\begin{split}
+\begin{equation}\label{eq: equation for normalized V_T}\begin{split}
 	&\frac{V_T(\theta \eta_T f)(x)}{\eta_T}
@@
 	\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} \exp\Big\{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du\Big\}\Big] dr.
-\end{split}\]
+\end{split}\end{equation}
 
@@
 
-	Recall that a 
-  non-negative 
-random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
-\[
+	Recall that a non-negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
+\begin{equation}
 	E[1-e^{-\theta\mathbf z^{(\gamma_0 - 1)}}]
 	=\Big( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} \Big)^{\frac{1}{\gamma_0 - 1}}.
-\]
+\end{equation}
 	It turns out that we can characterize this distribution by the following result.
 
-\begin{lem}
-\label{lem: characterize the general Mittag-Leffler distribution}
+\begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
 	The non-linear delay equation
-\[\label{eq: equation for the distribution}
+\begin{equation} \label{eq: equation for the distribution}
 	G( \theta)
@@
 	\quad \theta \geq 0,
-\]
+\end{equation}
 	has a unique solution:
-\[\label{eq: solution for the equation}
+\begin{equation}\label{eq: solution for the equation}
 	G(\theta)
@@
 	\quad \theta \geq 0.
-\]
+\end{equation}
 \end{lem}
@@
 	We first introduce some notation:
-	If $f$ is a measurable function which is $L^p$ integrable on the
-	measure space
-	$(S,\mathscr S,\mu)$ with $p > 0$, then we write
-\[
-	\|f\|_{\mu;p} := \Big(\int_{S} |f|^p d\mu \Big)^{\frac{1}{p}}.
-\]
+	If $f$ is a measurable function which is $L^p$ integrable on the measure space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
+\begin{equation}
+	\|f\|_{\mu;p} 
+	:= \Big(\int_{S} |f|^p d\mu \Big)^{\frac{1}{p}}.
+\end{equation}
 	Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to the measure $\mu$.	
@@
 	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
-\[
+\begin{equation}
 	F(\theta)
 	\leq C \int_0^\theta \|  F(ru^{ \frac{1}{\gamma_0- 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0.
-\]
+\end{equation}
 	Then $F \equiv 0$.
@@
 	Assume that
-\[\label{eq: definition of rho}
+\begin{equation}\label{eq: definition of rho}
 	\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
-\]
+\end{equation}
 	Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
 	We first claim that
-\[
+\begin{equation}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-\]
+\end{equation}
 	In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
-\[\begin{split}
+\begin{equation}\begin{split}
 	F_\alpha (\theta)
@@
 	\leq C(\rho C + 1) \theta.
-\end{split}\]
+\end{split}\end{equation}
 	We then claim that, if
-\[\label{eq: FATLC}
+\begin{equation}\label{eq: FATLC}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
-\]
+\end{equation}
 	for some $k \in \mathbb N$, then
-\[
+\begin{equation}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-	\]
+	\end{equation}
 	In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
-\[\begin{split}
+\begin{equation}\begin{split}
 	F_\alpha (\theta)
 	&\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) 
-	%\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
 	\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr\\
-%	=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) 
    &=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big )
@@
 	\\& =  C\int_0^\theta \|F_{\alpha u^{\frac{1}{\gamma_0 - 1}}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%	\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} } 
   \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} } 
@@
 	\\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-%	\leq C^{k+1} (\rho C+1) \theta^{k+1} .
 \\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
-\end{split}\]
+\end{split}\end{equation}
 	Therefore, by induction, we have
-\[
+\begin{equation}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
-\]
+\end{equation}
 	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
@@
 	In fact, if $G(\theta) = (\frac{1}{1+ \theta^{-(\gamma_0 - 1)}})^{\frac{1}{\gamma_0 - 1}}$, then
-\[\begin{split}
+\begin{equation}\begin{split}
 	 & \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}\Big\} dr
@@
 	= G(\theta).
-\end{split}\]
+\end{split}\end{equation}
 	The last equality is due to $G(0) = 0$ and
-\[\begin{split}
-	&\frac{d}{d\theta}G(\theta)
-	= - \frac{1}{\gamma_0 - 1} \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{1}{\gamma_0 - 1} - 1} \frac{d}{d\theta} \theta^{-(\gamma_0 - 1)}
-	\\&\quad =  \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{\gamma_0}{\gamma_0 - 1} } \theta^{-\gamma_0}.
-\end{split}\]
+\begin{equation}\begin{split}
+	\frac{d}{d\theta}G(\theta)
+	&= - \frac{1}{\gamma_0 - 1} \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{1}{\gamma_0 - 1} - 1} \frac{d}{d\theta} \theta^{-(\gamma_0 - 1)}
+	\\& =  \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{\gamma_0}{\gamma_0 - 1} } \theta^{-\gamma_0}.
+\end{split}\end{equation}
 
@@
 	This can be done by showing that $F(\theta) = 0$ where
-\[
-		F(\theta) := |G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|^{\frac{1}{\gamma_0 - 1}},
+\begin{equation}
+	F(\theta) 
+	:= |G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|^{\frac{1}{\gamma_0 - 1}},
 	\quad \theta \geq 0.
-\]
+\end{equation}
 	We claim that the non-negative function $F$ satisfies
 	the following inequality:
-\[\label{eq: inequality of F(theta)}
+\begin{equation}\label{eq: inequality of F(theta)}
 	F(\theta)
 	\leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\gamma_0 - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0,
-\]
+\end{equation}
 	for some constant $C_0 > 0$.
-	In fact, %according to 
-%	the Minkowski inequality of the $L^p$ norm with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
-by the $L^p$ Minkowski inequality with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
-\[\begin{split}
+	In fact, by the $L^p$ Minkowski inequality with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
+\begin{equation}\begin{split}
 	&|G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|
@@
 	\\ & \quad \leq \gamma_0 \Bigg( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} - G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}| \frac{du}{u} \Big)^{\frac{1}{\gamma_0 - 1}} dr \Bigg)^{\gamma_0 - 1}.
-\end{split}\]
+\end{split}\end{equation}
 	In other words, there is a constant $C_0:= \gamma_0^{\frac{1}{\gamma_0 - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
-	On the other hand, according to \eqref{eq: equation for the distribution},
-	we have that $G(\theta) \leq \theta$ and $G_0(\theta) \leq \theta$.
+	On the other hand, according to \eqref{eq: equation for the distribution}, we have that $G(\theta) \leq \theta$ and $G_0(\theta) \leq \theta$.
 	Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
@@
 	Suppose that $m\{ x:\gamma(x)=\gamma_0 \}>0$.
-	Let $f \in \mathscr B^+(E)$ be  such that $ \langle f, \phi^* \rangle_m > 0$  and $c_f:=\| \phi^{-1}f \|_\infty < \infty$.
+	Let $f \in \mathscr B^+(E)$ be  such that $ \langle f, \phi^* \rangle_m > 0$  and $c_f :=\| \phi^{-1}f \|_\infty < \infty$.
 
 	Without loss of generality, we assume that $\langle f, \phi^* \rangle_m = 1$.
-	As have been discussed in Subsection \ref{sec: conditional distribution},
-	in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
-\[
+	%As have been discussed in Subsection \ref{sec: conditional distribution}, in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
+	We claim that, in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
+\begin{equation}\label{eq: we only need to proof this}
 	g(t,\theta,x)
@@
 	\quad x\in E, \theta \geq 0.
-\]
-
-	From Lemma \ref{lem: characterize the general Mittag-Leffler distribution},
-we have that $G$ satisfies
-\[\label{eq: equation for G}
+\end{equation}
+%new
+	In fact, by \eqref{eq: equation for normalized V_T}, we have $\|V_t(\theta \eta_t f)/ \eta_t \|_\infty \leq \theta \|\phi\|_\infty \|\phi^{-1}f\|_\infty.$
+	Therefore, if \eqref{eq: we only need to proof this} is true, then by the bounded convergence theorem,
+\begin{equation}
+	\frac{\mu\big(V_t (\theta \eta_t f)\big)}{\eta_t }
+	\xrightarrow[t\to \infty]{} \mu(\phi)G(\theta),
+\end{equation}
+	which, by the discussion in Subsection \ref{sec: conditional distribution}, is equivalent to Theorem \ref{thm: main theorem}(3). 
+%end new
+
+	From Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we have that $G$ satisfies
+\begin{equation}\label{eq: equation for G}
 	G(\theta)
@@
 	\quad \theta \geq 0,
-\]
+\end{equation}
 	where
-\[\label{eq: definition for J_G}
+\begin{equation}\label{eq: definition for J_G}
 	J_G(r):=
@@
 	\quad r\geq 0 .
-\]
-	According to \eqref{eq: equation for normalized V_T},
-  we know that $g$ satisfies that
-\[\label{eq: equation for g}
+\end{equation}
+	According to \eqref{eq: equation for normalized V_T}, we know that $g$ satisfies
+\begin{equation}\label{eq: equation for g}
 	g(t,\theta, x)= \int_0^{\theta} \Pi_x^{(\phi)} [ (\phi^{-1}f)(\xi_t) e^{-\frac{1}{\gamma_0 - 1} J_g(t,r,\xi) } ] dr,
 	\quad t\geq 0, \theta \geq 0, x\in E,
-\]
+\end{equation}
 	where, for each $t\geq 0, r\geq 0$,
-\[\label{eq: definition for J_g}
+\begin{equation}\label{eq: definition for J_g}
 	J_g(t,r,\xi):=
 	(\gamma_0 - 1)t\int_0^1 \big(  \kappa\gamma (   \phi \eta_{ut}  )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) (  \xi_{(1-u)t}  ) du.
-\]
+\end{equation}
 	For each $t\geq 0$ and $r\geq 0$, define
-\[\label{eq: definition of J'_G}
+\begin{equation}\label{eq: definition of J'_G}
 	J'_G(t,r,\xi):=
 	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big) (\xi_{(1-u)t}) du
-\]
+\end{equation}
 	and
-\[\label{eq: definition of J'_g}
+\begin{equation}\label{eq: definition of J'_g}
 	J'_g(t,r,\xi):=
 	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \big) (\xi_{(1-u)t})  du.
-\]
+\end{equation}
 	The underlying idea of the proof is to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense when $t\to \infty$.
@@
 	From \eqref{eq: equation for G} we have
-\[\label{eq: upper bound for G}
+\begin{equation}\label{eq: upper bound for G}
 	G(r)
@@
 	\quad r \geq 0.
-\]	
+\end{equation}	
 	From \eqref{eq: definition for J_G} and \eqref{eq: upper bound for G}, we have
-\[\label{eq: upper bound for J_G}
+\begin{equation}\label{eq: upper bound for J_G}
 	J_G(r)
@@
 	\quad r \geq 0.
-\]
+\end{equation}
 	From \eqref{eq: equation for g}, we have
-\[\label{eq: upper bound for g}
+\begin{equation}\label{eq: upper bound for g}
 	g(t,r, x) \leq c_f r,
 	\quad t\geq 0, r \geq 0, x\in E.
-\]
+\end{equation}
 	From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have
-\[\begin{split}
+\begin{equation}\begin{split}
 	J_g(t,r, \xi)
@@
 	\quad t\geq 1, r\geq 0.
-\end{split}\]
+\end{split}\end{equation}
 	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have
-\[\begin{split}
+\begin{equation}\begin{split}
 	J'_g(t,r,\xi)
@@
 	\quad t\geq 0, r\geq 0.
-\end{split}\]
+\end{split}\end{equation}
 	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have
-\[\label{eq: upper bound for J'_G} \begin{split}
+\begin{equation}\label{eq: upper bound for J'_G} \begin{split}
 	J'_G(t,r,\xi)
@@
 	\quad t\geq 0, r\geq 0.
-\end{split}\]
+\end{split}\end{equation}
 
 	Step 2: We will show that, for each $t\geq 0, \theta \geq 0,$ and $x\in E$
-\[\begin{split}
+\begin{equation}\begin{split}
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
 	\\&\quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) 
-	%+c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x).
 	+c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x),
-\end{split}\]
+\end{split}\end{equation}
 	where
-\[\begin{split}
+\begin{equation}
+\begin{split}
 	I_1(t,\theta,x)
@@
 	&:= \Big\| \|  J'_G(t,r,\xi) - J'_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
-\end{split}\]
+\end{split}
+\end{equation}
 	and
-\[
+\begin{equation}
 	I_4(t,\theta,x)
 	:= \Big\| \| J'_g(t,r,\xi) - J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
-\]
+\end{equation}
 	In fact, we can rewrite \eqref{eq: equation for G} and \eqref{eq: equation for g} as:
-\[
+\begin{equation}
 	G(\theta)^{\gamma_0 - 1} =
@@
 	\quad \theta \geq 0,
-\]	
+\end{equation}	
 	and
-\[
+\begin{equation}
 	g(t,\theta,x)^{\gamma_0 - 1}
@@
 	\quad t\geq 0, \theta \geq 0, x\in E.
-\]
+\end{equation}	
 	Therefore, by Minkowski's inequality we have that
-\[\begin{split}
+\begin{equation}\begin{split}
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
@@
 	\quad t\geq 0, \theta \geq 0, x\in E.
-\end{split}\]
+\end{split}
+\end{equation}
 
@@
 	by \eqref{eq:q(t,x,y)},
-\[
+\begin{equation}
 	\Pi_x^{(\phi)} [(\phi^{-1}f)(\xi_t)]
@@
 	\quad x\in E.
-\]
+\end{equation}
 	Therefore,
-\[\begin{split}
+\begin{equation}\begin{split}
 	&e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
@@
 	\quad x\in E, r\geq 0.
-\end{split}\]
+\end{split}\end{equation}
 	We also have the following bound:
-\[
+\begin{equation}
 	\Big| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big|
 	\leq 1+ c_f^{\gamma_0 - 1}.
-\]
+\end{equation}
 	Therefore, by the bounded convergence theorem, we have that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta, x) \xrightarrow[t\to \infty]{} 0$.
@@
 	Notice that, according to \eqref{eq: definition for J_G} and \eqref{eq: definition of J'_G}, for each $t\geq 0$ and $r\geq 0$,
-\[\begin{split}
+\begin{equation}\begin{split}
 	&J_G(r) - J'_G(t,r,\xi)
@@
 	\\&\quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}.
-\end{split}\]
+\end{split}\end{equation}
 	Also notice that,
 	according to \eqref{eq: upper bound for G}, for each $r \geq 0$, $u\in [0,1]$ and $x\in E$,
-\[\begin{split}
+\begin{equation}\begin{split}
 	&\big| \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \frac{1}{u} \big|
@@
 	\\&\quad \leq \gamma_0r^{\gamma_0 - 1} \big( 1+ \big\|C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big\|_\infty \big).
-\end{split} \]
+\end{split} \end{equation}
 	Therefore, according to Lemma \ref{lem: ergodicity of the underlying process} and the definition of $C_X$, we have that, for each $r\geq 0$ and $x\in E$,
-\[
+\begin{equation}
 	J_G(r) - J'_G(t,r,\xi)
@@
 	=0.
-\]
+\end{equation}
 	According to \eqref{eq: upper bound for J_G} and \eqref{eq: upper bound for J'_G}, we have that, for each $r\geq 0$ and $t\geq 0$,
-\[ \label{eq: upper bound for J_G - J'_G}
+\begin{equation} \label{eq: upper bound for J_G - J'_G}
 	\big| J_G(r) - J'_G(t,r,\xi)\big|
 	\leq (\gamma_0 + c_4) r^{\gamma_0 - 1}.
-\]
+\end{equation}
 	Therefore, according to the bounded convergence theorem, we have that, for each $r\geq 0$ and $x\in E$,
-\[
+\begin{equation}
 	 \big\|  J_G(r) - J'_G(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
 	 \xrightarrow[t\to \infty]{} 0.
-\]
+\end{equation}
 	According to \eqref{eq: upper bound for J_G - J'_G}, we have that, for each $\theta \geq 0$, $r\in [0,\theta]$ and $x\in E$,
-\[
+\begin{equation}
 	\big\|  J_G(r) - J'_G(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
 	\leq (\gamma_0 + c_4) \theta^{\gamma_0 - 1}.
-\]
+\end{equation}
 	Finally, according to the bounded convergence theorem, we have that, for each $\theta\geq 0$ and $x\in E$, $I_2(t,\theta,x)\xrightarrow[t\to \infty]{} 0$.
@@
 	We first note that, for each $t\geq 0$ and $r\geq 0$, we have
-\[\label{eq: expression for J_g - J'_g}
+\begin{equation}\label{eq: expression for J_g - J'_g}
 	J_g(t,r,\xi) - J'_g(t,r,\xi)
 	= (\gamma_0 - 1)t\int_0^1 \big( \mathbf 1_{\gamma(\cdot )> \gamma_0}  \kappa\gamma (   \phi \eta_{ut}   )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) \big(  \xi_{(1-u)t}  \big) du.
-\]
+\end{equation}
 	We then note that, according \eqref{eq: upper bound for g} and the definition of $\eta_t$, for each $r\geq 0$, $u\in (0,1)$ and $x\in E$, we have
-\[\label{eq: integer in the expression of J_g - J'_g convergences to 0}\begin{split}
+\begin{equation}\label{eq: integer in the expression of J_g - J'_g convergences to 0}\begin{split}
 	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
@@
 	\\&\quad \xrightarrow[t\to \infty]{} 0.
-\end{split}\]
+\end{split}\end{equation}
 	This also gives an upper bound: For each $r\geq 0$, $u \in (0,1)$, $x\in E$ and $t\geq 1$, we have
-\[\label{eq: upper bound for the integrator of J_g - J'_g} \begin{split}
+\begin{equation}\label{eq: upper bound for the integrator of J_g - J'_g} \begin{split}
 	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
 	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
-\end{split}\]
+\end{split}\end{equation}
 	Now, with \eqref{eq: expression for J_g - J'_g}, \eqref{eq: integer in the expression of J_g - J'_g convergences to 0} and \eqref{eq: upper bound for J_g - J'_g}, we can apply Lemma \ref{lem: ergodicity of the underlying process} to the function
-\[
+\begin{equation}
 	(y,u,t)\mapsto (\gamma_0 - 1)t  \mathbf 1_{\gamma(y)> \gamma_0}  \kappa(y)\gamma(y) \big(   \phi(y) \eta_{ut}   \big)^{\gamma(y) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},y \big)^{\gamma(y)-1},
-\]
+\end{equation}
 	which says that, for each $r\geq 0$,
-\[
+\begin{equation}
 	J_g(t,r,\xi) - J'_g(t,r,\xi)
 \xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})} 0.
-\]
+\end{equation}
 	According to \eqref{eq: expression for J_g - J'_g} and \eqref{eq: upper bound for the integrator of J_g - J'_g}, for each $r\geq 0$ and $t\geq 1$, we have that
-\[\label{eq: upper bound for J_g - J'_g}
+\begin{equation}\label{eq: upper bound for J_g - J'_g}
 	\big |	J_g(t,r,\xi) - J'_g(t,r,\xi)  \big |
 	\leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
-\]
+\end{equation}
 	Therefore, according to the bounded convergence theorem, for each $r\geq 0$ and $x\in E$, we have that
-\[
+\begin{equation}
 	\big\| J'_g(t,r,\xi) - J_g(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
 	\xrightarrow[t\to \infty]{} 0.
-\]
+\end{equation}
 	According to \eqref{eq: upper bound for J_g - J'_g}, for each $\theta \geq 0$, $r\in [0,\theta]$ , $t\geq 1$ and $x\in E$, we have that
-\[
+\begin{equation}
 	\big\| J'_g(t,r,\xi) - J_g(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
 	\leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f \theta \phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
-\]
+\end{equation}
 	Therefore, according to the bounded convergence theorem, for each $\theta \geq 0$ and $x\in E$, we have that $I_4(t,\theta, x) \xrightarrow[t\to \infty]{} 0$.
@@
 	Step 6: We will show that
-\[
+\begin{equation}
 	\limsup_{t\to \infty} I_3(t,\theta,x)
@@
 	\quad \theta \geq 0, x\in E,
-\]
+\end{equation}
 	where
-\[
+\begin{equation}
 	M(t,r,x)
@@
 	\quad t\geq 0, r\geq 0, x\in E,
-\]
+\end{equation}
 	and
-\[
+\begin{equation}
 	M(r,x)
@@
 	\quad r\geq 0, x\in E.
-\]
-	Notice that,
-	according to \eqref{eq: upper bound for G} and \eqref{eq: upper bound for g}, we have the following bound:
-\[\label{eq: upper bound for M(t,r,x)}
+\end{equation}
+	Notice that, according to \eqref{eq: upper bound for G} and \eqref{eq: upper bound for g}, we have the following bound:
+\begin{equation}\label{eq: upper bound for M(t,r,x)}
 	M(t,r,x)
@@
 	=: c_6 r,
-\]
-%	where the constant $c_6$ is not related to $t$ and $x$.
+\end{equation}
 	where the constant $c_6$ is independent of $t$ and $x$.
 	Therefore, we have
-\[
+\begin{equation}
 	M(r,x)
@@
 	\quad r\geq 0, x\in E.
-\]	
+\end{equation}	
 	From the definition of $J'_G, J'_g$ and $\eta_t$, we have
-\[\label{eq: differences between J'_G and J'_g}\begin{split}
+\begin{equation}\label{eq: differences between J'_G and J'_g}\begin{split}
 	&|J'_G(t,r,\xi) - J'_g(t,r,\xi)|
@@
 	\quad t\geq 0, r\geq 0.
-\end{split}\]
+\end{split}\end{equation}
 	According to \eqref{eq: upper bound for M(t,r,x)}, we have the following upper bound:
-\[\begin{split}
+\begin{equation}\begin{split}
 		u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}}, x)
@@
 		\quad u\in (0,1), r\geq 0, t\geq 0, x\in E.
-\end{split}\]
+\end{split}\end{equation}
 	Therefore, fixing an $r\geq 0$, we can apply Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process} to the function
-\[
+\begin{equation}
 	(y,u,t)
 	\mapsto \gamma_0 C_X^{-1}\mathbf 1_{\gamma(y) = \gamma_0} \kappa(y)  \phi(y)^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},y)^{\gamma_0 - 1}
-\]
+\end{equation}
 	since it is a bounded Borel function on $E\times (0,1) \times [0,\infty)$.
@@
 $M(r,x), M(r)$ and $C_X$, we have
-\[\label{eq: limsup of J_G - J'_g}\begin{split}
+\begin{equation}\label{eq: limsup of J_G - J'_g}\begin{split}
 	&\limsup_{t\to \infty} \| J_G'(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{\phi};\frac{1}{\gamma_0 - 1}}
@@
 	\\&\quad\leq  \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}.
-\end{split}\]
+\end{split}\end{equation}
 	We now recall the reverse Fatou's lemma in $L^p$ with $p\geq 1$: Let $(f_n)_{n\in \mathbb N}$ be a sequence of non-negative measurable functions defined on a measure space $S$ with $\sigma$-finite measure $\mu$.
 If there exists a non-negative $L^p(\mu)$-integrable function $g$ on $S$ such that $f_n \leq g$ for all $n$, then according to the classical reverse Fatou's lemma, we have
-\[
+\begin{equation}
 	\limsup_{n\to \infty}\big\| f_n \big\|_{\mu;p}
@@
 	= \big\| \limsup_{n\to \infty} f_n \big\|_{\mu;p}.
-\]
+\end{equation}
 	Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
-\[\begin{split}
+\begin{equation}\begin{split}
 	&\limsup_{t\to \infty} I_3(t,\theta, x)
@@
 	\quad \theta \geq 0, x\in E.
-\end{split}\]
+\end{split}\end{equation}
 
@@
 	We first claim that
-\[
+\begin{equation}
 	M(\theta)
@@
 	\quad \theta \geq 0,
-\]
+\end{equation}
 	for some constant $c_M > 0$.
 	In fact, a direct application of Steps 2-6 gives that, for each $t\geq 0$ and $x\in E$:
-\[\begin{split}
+\begin{equation}\begin{split}
 	&M(r,x)^{\gamma_0 - 1}
@@
 	\leq c_f^{\gamma_0 - 1} \gamma_0 \Big(  \int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1}.
-\end{split}\]
+\end{split}\end{equation}
 	Therefore, for each $\theta \geq 0$,
-\[
+\begin{equation}
 	M(\theta)
@@
 	\leq c_f \gamma_0^{\frac{1}{\gamma_0 - 1}} \int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr.
-\]
+\end{equation}
 	According to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
 
-	Finally, 
-	%recalling the definition of $M$, by showing that $M\equiv 0$, the proof is complete.
-	by the definition of $M$,  $M\equiv 0$ implies the desired assertion.
-
+	%Finally, by the definition of $M$,  $M\equiv 0$ implies the desired assertion.
+	Finally, by the definition of $M$,  $M\equiv 0$ implies the desired assertion \eqref{eq: we only need to proof this}.
+
+%ZY: I changed the format of the bibliography without marks 
 \begin{thebibliography}{10}
@@
 	\bibitem{AsmussenHering1983Branching}
-	S.~Asmussen and H.~Hering, \emph{Branching processes}, Progress in Probability
-	and Statistics, vol.~3, Birkh{\"a}user Boston, Inc., Boston, MA, 1983.
+	Asmussen, S. and Hering, H.: 
+	\emph{Branching processes}. 
+	Progress in Probability and Statistics, 3. 
+	Birkh{\"a}user Boston, Inc., Boston, MA, 1983.
 	\MR{701538}
@@
 	\bibitem{AthreyaNey1974Functionals}
-	K.~Athreya and P.~Ney, \emph{Functionals of critical multitype branching
-		processes}, Ann. Probability \textbf{2} (1974), 339--343. \MR{0356264}
+	Athreya, K.~B. and Ney, P.~E.:
+	\emph{Functionals of critical multitype branching processes}. 
+	Ann. Probability \textbf{2} (1974), 339--343. \MR{0356264}
 
 	\bibitem{AthreyaNey1972Branching}
-	K.~B. Athreya and P.~E. Ney, \emph{Branching processes}, Springer-Verlag, New
-	York-Heidelberg, 1972, Die Grundlehren der mathematischen Wissenschaften,
-	Band 196. \MR{0373040}
+	Athreya, K. and Ney, P.: 
+	\emph{Branching processes}. 
+	Die Grundlehren der mathematischen Wissenschaften, Band 196.
+	Springer-Verlag, New York-Heidelberg, 1972. 
+	\MR{0373040}
 
 	\bibitem{BinghamGoldieTeugels1989Regular}
-	N.~H. Bingham, C.~M. Goldie, and J.~L. Teugels, \emph{Regular variation},
-	Encyclopedia of Mathematics and its Applications, vol.~27, Cambridge
-	University Press, Cambridge, 1989. \MR{1015093}
+	Bingham, N.~H., Goldie, C.~M. and Teugels J.~L.:
+	\emph{Regular variation}.
+	Encyclopedia of Mathematics and its Applications, 27. 
+	Cambridge University Press, Cambridge, 1989. 
+	\MR{1015093}
 
 	\bibitem{Borovkov1989Method}
-	K.~A. Borovkov, \emph{A method of proving limit theorems for branching
-		processes}, Theory of Probability \& Its Applications \textbf{33} (1989),
-	no.~1, 105--113.
+	Borovkov, K.~A.: 
+	\emph{A method for the proof of limit theorems for branching processes}.
+	Teor. Veroyatnost. i Primenen. \textbf{33} (1988), no. 1, 115--123;
+	translation in Theory Probab. Appl. \textbf{33} (1988), no. 1, 105–113.
+	\MR{0939993}
 
 	\bibitem{EckhoffKyprianouWinkel2015Spines}
-	M.~Eckhoff, A.~E. Kyprianou, and M.~Winkel, \emph{Spines, skeletons and the
-		strong law of large numbers for superdiffusions}, Ann. Probab. \textbf{43}
-	(2015), no.~5, 2545--2610. \MR{3395469}
+	Eckhoff, M., Kyprianou, A.~E., Winkel, M.:
+	\emph{Spines, skeletons and the strong law of large numbers for superdiffusions.}
+	Ann. Probab. \textbf{43} (2015), no. 5, 2545–2610.
+	\MR{3395469}
 
 	\bibitem{EnglanderKyprianou2004Local}
-	J.~Engl{\"a}nder and A.~E. Kyprianou, \emph{Local extinction versus local
-		exponential growth for spatial branching processes}, Ann. Probab. \textbf{32}
-	(2004), no.~1A, 78--99. \MR{2040776}
+	Engländer, J., Kyprianou, A.~E.:
+	\emph{Local extinction versus local exponential growth for spatial branching processes.}
+	Ann. Probab. \textbf{32} (2004), no. 1A, 78–99.
+	\MR{2040776}
 
 	\bibitem{EvansPerkins1990Measure-valued}
-	S.~N. Evans and E.~Perkins, \emph{Measure-valued {M}arkov branching processes
-		conditioned on nonextinction}, Israel J. Math. \textbf{71} (1990), no.~3,
-	329--337. \MR{1088825}
+	Evans, S.~N., Perkins, E.:
+	\emph{Measure-valued Markov branching processes conditioned on nonextinction.}
+	Israel J. Math. \textbf{71} (1990), no. 3, 329–337. 
+	\MR{1088825}
 
 	\bibitem{GoldsteinHoppe1978Critical}
-	M.~I. Goldstein and F.~M. Hoppe, \emph{Critical multitype branching processes
-		with infinite variance}, Journal of Mathematical Analysis and Applications
-	\textbf{65} (1978), no.~3, 675--686.
+	Goldstein, M.~I., Hoppe, F.~M.:
+	\emph{Critical multitype branching processes with infinite variance.}
+	J. Math. Anal. Appl. \textbf{65} (1978), no. 3, 675–686. 
+	\MR{0510478}
 
 	\bibitem{Harris2002The-theory}
-	T.~E. Harris, \emph{The theory of branching processes}, Dover Phoenix Editions,
-	Dover Publications, Inc., Mineola, NY, 2002, Corrected reprint of the 1963
-	original [Springer, Berlin; MR0163361 (29 \#664)]. \MR{1991122}
+	Harris, T. E.:
+	\emph{The theory of branching processes.}
+	Die Grundlehren der Mathematischen Wissenschaften, Bd. 119 Springer-Verlag, Berlin; Prentice-Hall, Inc., Englewood Cliffs, N.J. 1963.
+	\MR{0163361}
 
 	\bibitem{IyerLegerPego2015Limit}
-	G.~Iyer, N.~Leger, and R.~L. Pego, \emph{Limit theorems for {S}moluchowski
-		dynamics associated with critical continuous-state branching processes}, Ann.
-	Appl. Probab. \textbf{25} (2015), no.~2, 675--713. \MR{3313753}
+	Iyer, G., Leger, N., Pego, R.~L.:
+	\emph{Limit theorems for Smoluchowski dynamics associated with critical continuous-state branching processes.}
+	Ann. Appl. Probab. \textbf{25} (2015), no. 2, 675–713.
+	\MR{3313753}
 
 	\bibitem{JoffeSpitzer1967On-multitype}
-	A.~Joffe and F.~Spitzer, \emph{On multitype branching processes with {$\rho
-			\leq 1$}}, J. Math. Anal. Appl. \textbf{19} (1967), 409--430. \MR{0212895}
+	Joffe, A. and Spitzer, F.:
+	\emph{On multitype branching processes with {$\rho \leq 1$}.} 
+	J. Math. Anal. Appl. \textbf{19} (1967), 409--430. 
+	\MR{0212895}
 
 	\bibitem{KestenNeySpitzer1966The-Galton-Watson}
-	H.~Kesten, P.~Ney, and F.~Spitzer, \emph{The {G}alton-{W}atson process with
-		mean one and finite variance}, Teor. Verojatnost. i Primenen. \textbf{11}
-	(1966), 579--611. \MR{0207052}
+	Kesten, H., Ney, P. and Spitzer, F.: 
+	\emph{The {G}alton-{W}atson process with mean one and finite variance.} 
+	Teor. Verojatnost. i Primenen. \textbf{11} (1966), 579--611. 
+	\MR{0207052}
 
 	\bibitem{KimSong2008Intrinsic}
-	P.~Kim and R.~Song, \emph{Intrinsic ultracontractivity of non-symmetric
-		diffusion semigroups in bounded domains}, Tohoku Math. J. (2) \textbf{60}
-	(2008), no.~4, 527--547. \MR{2487824}
+	Kim, P. and Song, R.: 
+	\emph{Intrinsic ultracontractivity of non-symmetric diffusion semigroups in bounded domains.} 
+	Tohoku Math. J. (2) \textbf{60} (2008), no.~4, 527--547. 
+	\MR{2487824}
 
 	\bibitem{Kolmogorov1938Zur-losung}
-	A.~N. Kolmogorov, \emph{Zur l{\"o}sung einer biologischen aufgabe}, Comm. Math.
-	Mech. Chebyshev Univ. Tomsk \textbf{2} (1938), no.~1, 1--12.
+	Kolmogorov, A.~N.: 
+	\emph{Zur l{\"o}sung einer biologischen aufgabe.} 
+	Comm. Math. Mech. Chebyshev Univ. Tomsk \textbf{2} (1938), no.~1, 1--12.
 
 	\bibitem{Kyprianou2014Fluctuations}
-	A.~E. Kyprianou, \emph{Fluctuations of {L}{\'e}vy processes with applications},
-	second ed., Universitext, Springer, Heidelberg, 2014, Introductory lectures.
+	Kyprianou, A.~E.:
+	\emph{Fluctuations of Lévy processes with applications.} 
+	Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
 	\MR{3155252}
@@
 	\bibitem{Kyprianou2008Continuous}
-	A.~E. Kyprianou and J.~C. Pardo, \emph{Continuous-state branching processes and
-		self-similarity}, Journal of Applied Probability \textbf{45} (2008), no.~4,
-	1140--1160.
+	Kyprianou, A.~E., Pardo, J. C.:
+	\emph{Continuous-state branching processes and self-similarity.}
+	J. Appl. Probab. \text{45} (2008), no. 4, 1140–1160. 
+	\MR{2484167}
 
 	\bibitem{Li2011Measure-valued}
-	Z.~Li, \emph{Measure-valued branching {M}arkov processes}, Probability and its
-	Applications (New York), Springer, Heidelberg, 2011. \MR{2760602}
+	Li, Z.: 
+	\emph{Measure-valued branching {M}arkov processes.} 
+	Probability and its Applications (New York), Springer, Heidelberg, 2011. 
+	\MR{2760602}
 
 	\bibitem{LiuRenSong2009Llog}
-	R.~Liu, Y.-X. Ren, and R.~Song, \emph{{$L\log L$} criterion for a class of
-		superdiffusions}, J. Appl. Probab. \textbf{46} (2009), no.~2, 479--496.
+	Liu, R.-L., Ren, Y.-X. and Song, R. 
+	\emph{{$L\log L$} criterion for a class of superdiffusions.} 
+	J. Appl. Probab. \textbf{46} (2009), no.~2, 479--496.
 	\MR{2535827}
@@
 	\bibitem{Pakes2010Critical}
-	A.~G. Pakes, \emph{Critical {M}arkov branching process limit theorems allowing
-		infinite variance}, Adv. in Appl. Probab. \textbf{42} (2010), no.~2,
-	460--488. \MR{2675112}
+	Pakes, A.~G.: 
+	\emph{Critical {M}arkov branching process limit theorems allowing infinite variance.} 
+	Adv. in Appl. Probab. \textbf{42} (2010), no.~2, 460--488. 
+	\MR{2675112}
 
 	\bibitem{Powell2015An-invariance}
-	E.~Powell, \emph{An invariance principle for branching diffusions in bounded
-		domains}, arXiv preprint arXiv:1512.00031 (2015).
+	Powell, E.: 
+	\emph{An invariance principle for branching diffusions in bounded domains.} 
+	\ARXIV{1512.00031}
 
 	\bibitem{RenSongSun2017A-2-spine}
-	Y.-X. Ren, R.~Song, and Z.~Sun, \emph{A 2-spine decomposition of the critical
-		galton-watson tree and a probabilistic proof of yaglom's theorem}, arXiv
-	preprint arXiv:1706.07125 (2017).
+	Ren, Y.-X., Song, R. and Sun, Z.: 
+	\emph{A 2-spine decomposition of the critical galton-watson tree and a probabilistic proof of yaglom's theorem.} 
+	\ARXIV{1706.07125}
 
 	\bibitem{RenSongSun2017Spine}
-	\bysame, \emph{Spine decompositions and limit theorems for a class of critical
-		superprocesses}, arXiv preprint arXiv:1711.09188 (2017).
+	\bysame: 
+	\emph{Spine decompositions and limit theorems for a class of critical superprocesses.} 
+	\ARXIV{1711.09188}
 
 	\bibitem{RenSongZhang2015Limit}
-	Y.-X. Ren, R.~Song, and R.~Zhang, \emph{Limit theorems for some critical
-		superprocesses}, Illinois J. Math. \textbf{59} (2015), no.~1, 235--276.
+	Ren, Y.-X., Song, R. and Zhang, R.: 
+	\emph{Limit theorems for some critical superprocesses.} 
+	Illinois J. Math. \textbf{59} (2015), no.~1, 235--276.
 	\MR{3459635}
@@
 	\bibitem{RenSongZhang2017Central}
-	\bysame, \emph{Central limit theorems for supercritical branching nonsymmetric
-		{M}arkov processes}, Ann. Probab. \textbf{45} (2017), no.~1, 564--623.
+	\bysame: 
+	\emph{Central limit theorems for supercritical branching nonsymmetric {M}arkov processes.} 
+	Ann. Probab. \textbf{45} (2017), no.~1, 564--623.
 	\MR{3601657}
@@
 	\bibitem{RenYangZhao2014Conditional}
-	Y.-X. Ren, T.~Yang, and G.~Zhao, \emph{Conditional limit theorems for critical
-		continuous-state branching processes}, Science China Mathematics \textbf{57}
-	(2014), no.~12, 2577--2588.
+	Ren, Y.-X., Yang, T., Zhao, G.-H.:
+	\emph{Conditional limit theorems for critical continuous-state branching processes.}
+	Sci. China Math. \textbf{57} (2014), no. 12, 2577–2588. 
+	\MR{3275407}
 
 	\bibitem{Schaefer1974Banach}
-	H.~H. Schaefer, \emph{Banach lattices and positive operators}, Springer-Verlag,
-	New York-Heidelberg, 1974, Die Grundlehren der mathematischen Wissenschaften,
-	Band 215. \MR{0423039}
+	Schaefer, H.~H.:
+	\emph{Banach lattices and positive operators.}
+	Die Grundlehren der mathematischen Wissenschaften, Band 215. Springer-Verlag, New York-Heidelberg, 1974.
+	\MR{0423039}
 
 	\bibitem{Slack1968A-branching}
-	R.~S. Slack, \emph{A branching process with mean one and possibly infinite
-		variance}, Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{9} (1968),
-	139--145. \MR{0228077}
+	Slack, R.~S.:
+	\emph{A branching process with mean one and possibly infinite variance.}
+	Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{9} (1968), 139--145. 
+	\MR{0228077}
 
 	\bibitem{Slack1972Further}
-	\bysame, \emph{Further notes on branching processes with mean 1}, Zeitschrift
-	f{\"u}r Wahrscheinlichkeitstheorie und Verwandte Gebiete \textbf{25} (1972),
-	no.~1, 31--38.
+	\bysame: \emph{Further notes on branching processes with mean {$1$}.} 
+	Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{25} (1972/73), 31–38.
+	\MR{0331539}
 
 	\bibitem{Vatutin1977Limit}
-	V.~A. Vatutin, \emph{Limit theorems for critical markov branching processes
-		with several types of particles and infinite second moments}, Sbornik:
-	Mathematics \textbf{32} (1977), no.~2, 215--225.
+	Vatutin, V. A.:
+	\emph{Limit theorems for critical multitype Markov branching processes with infinite second moments.} 
+	Mat. Sb. (N.S.) \textbf{103(145)} (1977), no. 2, 253–264, 319.
+	\MR{0443115}
 
 	\bibitem{Yaglom1947Certain}
-	A.~M. Yaglom, \emph{Certain limit theorems of the theory of branching random
-		processes}, Doklady Akad. Nauk SSSR (N.S.) \textbf{56} (1947), 795--798.
+	Yaglom, A. M.:
+	\emph{Certain limit theorems of the theory of branching random processes.}
+	Doklady Akad. Nauk SSSR (N.S.) \textbf{56} (1947). 795–798. 
 	\MR{0022045}
@@
 	\bibitem{Zolotarev1957More}
-	V.~M. Zolotarev, \emph{More exact statements of several theorems in the theory
-		of branching processes}, Theory of Probability \& Its Applications \textbf{2}
-	(1957), no.~2, 245--253.
+	Zolotarev, V. M.:
+	\emph{More exact statements of several theorems in the theory of branching processes.}
+	Teor. Veroyatnost. i Primenen. \textbf{2} (1957), 256–266.
+	\MR{0096321}
 

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
 	Beijing, P. R. China, 100871}
-%\curraddr
-	%{Department of Mathematics\\
-	%University of Illinois at Urbana-Champaign\\
-	%Urbana, IL 61801}
 \email{zhenyao.sun@pku.edu.cn}
-%\thanks{Zhenyao Sun is supported by the China Scholarship Council.}
 \begin{abstract}
-%new
-	In this paper, we consider a critical $(\xi,\psi)$-superprocess $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$.
-	$\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact separable metric space $E$, satisfying an intrinsically ultracontractive condition.
+	In this paper, we consider a critical $(\xi,\psi)$-superprocess 
+%	$\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$.
+$\{X; \mathbf P_\mu\}$.
+	$\xi$, the spatial motion of the superprocess, is a 
+%	Hunt process on a locally compact separable metric space $E$, 
+Hunt process, on a locally compact separable metric space $E$, 
+	satisfying an intrinsically ultracontractive condition.
 	$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty]$ of the form
@@
 \end{equation}
-	where $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfy 
+%	where $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfy 
+with $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfying
 \begin{equation}
@@
 \end{equation}
-%new added
 \end{abstract}
@@
 \maketitle
-%\tableofcontents
-%---Contents-----------------------
 \section{Introduction}
@@
 	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
-	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.
-
-	Notice that, \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
+%	Since then, lots of analogous results were obtained for more general 
+	Since then, lots of analogous results have been obtained for more general
+	critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.
+
+	Notice that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
     In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, and thus more appropriate scalings are needed.
@@
 
-	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
-	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite[Theorem~4.2]{AsmussenHering1983Branching} for critical branching Markov processes.
+%	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} 
+	Asmussen and Hering \cite[Sections~6.3~and~6.4]{AsmussenHering1983Branching} 
+	discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
+	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in
+%\cite[Theorem~4.2]{AsmussenHering1983Branching} 
+\cite[Theorem~6.4.2]{AsmussenHering1983Branching} 
+for critical branching Markov processes.
 
     In this paper, we are interested in a class of measure-valued branching Markov process known as $(\xi, \psi)$-superprocesses:
-    $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact, separable, metric space $E$;
+    $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact separable metric space $E$;
     $\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty)$ of the form
@@
 	For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
-%deleted	
-	%In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.
-%end delted
 
@@
 	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a finite measure $\mu$ on $E$.
-	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition,
+	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition
 \begin{equation}\label{eq: second moment condition}
@@
 	= c z^\gamma l(z),
-	\quad z\geq 0.
+%	\quad z\geq 0.
+	\quad z\geq 0,
 \end{equation}
@@
 	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: 
-	%Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ satisfying Grey's condition.
-	Suppose that $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP with critical branching mechanism $\psi$ satisfying Grey's condition.
+%	Suppose that $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP 
+Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP 
+	with critical branching mechanism $\psi$ satisfying Grey's condition.
 	In order for the left side of \eqref{eq: conditional limit of CSBP} to have a non-trivial weak limit for some positive constants $(\lambda_t)_{t\geq 0}$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
@@
 	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
-	%We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
 	We will show that $\mathbf P_{\delta_x}( \| X_t\| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
-	%Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
 	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we will show that
@@
 	Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
-	%Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$, $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
 	Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$ and $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
@@
 	In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
-	If $E$ is a topological space, denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
+	If $E$ is a topological space, we denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
 
@@
 \end{equation}
-	%where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is defined as the unique locally bounded positive solution to the equation
 	where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
@@
 \begin{asp} \label{asp: 1}
-	There exists an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$, and a family of strictly positive, bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that,
+%	There exists an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$, and a family of strictly positive, 
+There exist an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$ and a family of strictly positive, 
+	bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that,
 \begin{equation}\begin{split}
@@
 
-	Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
+	Under Assumption \ref{asp: 1}, it is proved in 
+%	\cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} 
+	\cite{RenSongZhang2015Limit, RenSongZhang2017Central} 
+	that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
 \begin{equation}
@@
 \end{equation}
-    $(p^\beta_t)_{t\geq 0}$ is called the \emph{density of semigroup $(P^\beta_t)_{t\geq 0}$}.
+    $(p^\beta_t)_{t\geq 0}$ is called the 
+%    \emph{density of semigroup $(P^\beta_t)_{t\geq 0}$}.
+    \emph{density}  of the semigroup $(P^\beta_t)_{t\geq 0}$.
 	Define the dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ by
@@
 \end{equation}
-	It is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+	It is proved in 
+%	\cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} 
+	\cite{RenSongZhang2015Limit, RenSongZhang2017Central} 
+	that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
 	Let $L$ and $L^*$ be the generators of the semigroups $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$, respectively.
 	Denote by $\sigma(L)$ and $\sigma(L^*)$ the spectra of $L$ and $L^*$, respectively.
-	According to \cite[Theorem V.6.6.]{Schaefer1974Banach}, $\lambda := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common eigenvalue of multiplicity $1$ for both $L$ and $L^*$.
+%	According to \cite[Theorem V.6.6.]{Schaefer1974Banach}, 
+	According to \cite[Theorem V.6.6]{Schaefer1974Banach}, 
+	$\lambda := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common eigenvalue of multiplicity $1$ for both $L$ and $L^*$.
 	Using the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\phi$ of $L$ and $\phi^*$ of $L^*$ associated with the eigenvalue $\lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
@@
 
-	Under Assumption \ref{asp: 3}, it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of Feynman-Kac semigroup $(P^\beta_t)_{t\geq 0}$ is also bounded.
+	Under Assumption \ref{asp: 3}, it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that the principal eigenfunction $\phi$ of the Feynman-Kac semigroup $(P^\beta_t)_{t\geq 0}$ is also bounded.
 	Moreover, $(P^\beta_t)_{t\geq 0}$ is also \emph{intrinsically ultracontractive}, in the sense that for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p^\beta_t(x,y) \leq c_t \phi(x) \phi^*(y)$.
@@
 \item[(1)] 
-	%$\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}( X_t \equiv 0) > 0$.
-	$\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, $\mathbf P_{\delta_x}( \| X_t\| \neq 0) > 0$.
+	$\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$, 
+%	$\mathbf P_{\delta_x}( \| X_t\| \neq 0) > 0$.
+	$\mathbf P_{\delta_x}( \| X_t\| = 0) > 0$.
 \item[(2)] 
-	%For each $x\in E$, $\mathbf P_{\delta_x}(X_t \not \equiv 0)$ converges to $0$, and is regularly varying with index $-\frac{1}{\gamma_0-1}$ as $t\to \infty$.
-	For each $\mu \in \mathcal M^1_E$, $\mathbf P_{\mu}(\|X_t\| \neq 0)$ converges to $0$, and is regularly varying with index $-(\gamma_0-1)^{-1}$ as $t \to \infty$.
+	For each $\mu \in \mathcal M^1_E$, $\mathbf P_{\mu}(\|X_t\| \neq 0)$ converges to 
+	%$0$, and is regularly varying with index $-(\gamma_0-1)^{-1}$ as $t \to \infty$.
+	$0$ as $t \to \infty$ and is regularly varying at infinity with index $-(\gamma_0-1)^{-1}$.
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
@@
 	Suppose $m( x:\gamma(x)=\gamma_0 )>0$.
-	%Let $f \in \mathscr B^+(E)$ be such that $\langle f, \phi^* \rangle_m > 0$ and $\| \phi^{-1}f \|_\infty < \infty$, then
 	Let $f \in \mathscr B^+(E)$ be such that $\langle f, \phi^* \rangle_m > 0$ and $\| \phi^{-1}f \|_\infty < \infty$. Then for each $\mu \in \mathcal M_E^1$,
 \begin{equation}
-	%\{\eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot |\|X_t\| \neq 0) \}
 	\{\eta_t X_t(f) ; \mathbf P_{\mu}(\cdot |\|X_t\| \neq 0) \}
@@
 
-	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 
-	%$X$:
-	$X$.
+	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 	$X$.
 	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
@@
 	Then, the problem is reduced to the study of a single ordinary differential equation satisfied by the speed function $a(t)$.
-	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of critical superprocesses with finite second moment.
+	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of 
+%	critical superprocesses with finite second moment.
+ general critical superprocesses with finite second moment.
 	In this paper, we will  generalize these arguments to a class of general critical superprocesses without finite second moment, and establish Theorem \ref{thm: main theorem}(2).
@@
 
-	A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
+	A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in 
+%	\cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
+	\cite{RenSongSun2017A-2-spine, RenSongSun2017Spine}.
 	We characterized the exponential distribution using its double size-biased transform;
@@
 
-	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in \cite{RenSongSun2017Spine} and \cite{RenSongZhang2015Limit} (for general critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
+	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in 
+%	\cite{RenSongSun2017Spine} and \cite{RenSongZhang2015Limit} 
+	\cite{RenSongSun2017Spine, RenSongZhang2015Limit} 
+	(for general critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
     First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used to extend the result to more general testing functions.
@@
     In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize Zolotarev's distribution.
-	Finally, 
-    %In Subsection
-    in Subsection 
+	Finally,  in Subsection 
     \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
@@
 	Further, if $\gamma = 0$, then we say $f$ is slowly varying.
-	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, if $L$ is a function slowly varying at $\infty$, then it can be written in the form
+%	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, 
+	According to \cite[Theorem 1.3.1]{BinghamGoldieTeugels1989Regular}, 
+	if $L$ is a function slowly varying at $\infty$, then it can be written in the form
 \begin{equation}
@@
 
-\begin{lem}[{\cite[Propositions 1.5.8. and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
+%\begin{lem}[{\cite[Propositions 1.5.8. and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
+\begin{lem}[{\cite[Propositions 1.5.8 and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
 \label{lem: exchange slowly varying function and integration}
@@
 
-%deleted
-	%The following lemma concerns the inverse of a strictly monotone, regularly varying function.
-	%In this paper, if a function $f$ is strictly monotone, 
-	%we write $f^{(-1)}$ for its inverse;
-	%if a function $f\neq 0$, we write $f^{-1} := \frac{1}{f} $.
-
-%\begin{lem}
-%\label{lem: regularly variation and inverse}
-	%Suppose that $f$ is a strictly monotone map from $(0,\infty)$ to $(0,\infty)$.
-	%Then, for each $\alpha > 0$, we have
-%\begin{equation} \label{eq: inverse of a regularly varying function at infinity with alpha > 0}
-	%f
-	%\in \mathcal R^\infty_{\alpha}
-	%\iff f^{(-1)}
-	%\in \mathcal R^\infty_{1/\alpha}
-%\end{equation}
-	%and
-%\begin{equation} \label{eq: inverse of a regularly varying function at 0 with alpha > 0}
-	%f
-	%\in \mathcal R^0_{\alpha}
-	%\iff f^{(-1)}
-	%\in \mathcal R^0_{1/\alpha};
-%\end{equation}
-	%for each $\alpha < 0$, we have
-%\begin{equation} \label{eq: inverse of a regularly varying function with alpha < 0}
-	%f
-	%\in \mathcal R^\infty_{\alpha}
-	%\iff f^{(-1)}
-	%\in \mathcal R^0_{1/\alpha}.
-%\end{equation}
-	%Similarly, for each $\alpha > 0$ and $c > 0$, we have
-%\begin{equation}\label{eq: inverse and power equivalent at infinity with alpha > 0}
-	%f(t)
-	%\stackrel[t\to \infty]{}{\sim} c t^\alpha
-	%\iff f^{(-1)}(t)
-	%\stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}
-%\end{equation}
-	%and
-%\begin{equation}\label{eq: inverse and power equivalent at 0 with alpha > 0}
-	%f(t)
-	%\stackrel[t\to 0]{}{\sim} c t^\alpha
-	%\iff f^{(-1)}(t)
-	%\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha};
-%\end{equation}
-	%for each $\alpha < 0$ and $c > 0$, we have
-%\begin{equation}\label{eq: inverse and power equivalent with alpha < 0}
-	%f(t)
-	%\stackrel[t\to \infty]{}{\sim} c t^\alpha
-	%\iff f^{(-1)}(t)
-	%\stackrel[t\to 0]{}{\sim} c^{-1/\alpha} t^{1/\alpha}.
-%\end{equation}
-%\end{lem}
-%\begin{proof}
-%If $\alpha>0$, then according to \cite[Theorem 1.5.12.]{BinghamGoldieTeugels1989Regular}, we have \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} is true.
-	%To see 	\eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} is true, we write $h(t) : = f(t^{-1})^{-1}$.
-	%It is  easy to verify that $h$ is strictly monotone with $h^{(-1)}(t) := f^{(-1)}(t^{-1})^{-1}$.
-	%Therefore,
-%\begin{equation}
-	%f
-	%\in \mathcal R^0_{\alpha}
-	%\iff h
-	%\in \mathcal R^\infty_{\alpha}
-	%\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at infinity with alpha > 0} }   }{\iff} h^{(-1)}
-	%\in \mathcal R^\infty_{1/\alpha}
-	%\iff f^{(-1)}
-	%\in \mathcal R^0_{1/\alpha}.
-%\end{equation}
-
-	%If $\alpha < 0$, to see	\eqref{eq: inverse of a regularly varying function with alpha < 0} is true, we write $g(t) : = f(t^{-1})$.
-	%It is easy to verify that $g$ is strictly monotone with $g^{(-1)}(t) := f^{(-1)}(t)^{-1}$.
-	%Therefore,
-%\begin{equation}
-	%f
-	%\in \mathcal R^\infty_{\alpha}
-	%\iff g
-	%\in \mathcal R^0_{-\alpha}
-	%\stackrel{  \text{ by \eqref{eq: inverse of a regularly varying function at 0 with alpha > 0} }   }{\iff} g^{(-1)}
-	%\in \mathcal R^0_{-1/\alpha}
-	%\iff f^{(-1)}
-	%\in \mathcal R^0_{1/\alpha}.
-%\end{equation}
-
-	%Now, assume that $f(t) \stackrel[t\to \infty]{}{\sim} c t^\alpha$ for some $\alpha > 0$ and $c > 0$, we want to show that $f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}$.
-	%Notice that, since $\alpha >0$, we must have $f$ is strictly increasing.
-	%From the definition of the asymptotic equivalence, we have, for each $\epsilon> 0$,
-%\begin{equation}
-	%\Big|\frac{f(t)}{c t^\alpha} - 1\Big|
-	%< \epsilon,
-	%\quad t \text{ large enough.}
-%\end{equation}
-	%This is equivalent to
-%\begin{equation}
-	%(1-\epsilon) c t^{\alpha}
-	%< f(t)
-	%< (1+ \epsilon)c t^{\alpha},
-	%\quad t \text{ large enough,}
-%\end{equation}
-	%which, by the increasing nature of $f^{(-1)}$, gives that
-%\begin{equation}\label{eq: inverse and inequality}
-	%f^{(-1)}[(1-\epsilon) c t^{\alpha}] \leq t \leq f^{(-1)}[(1+ \epsilon)c t^{\alpha}], \quad t \text{ large enough.}
-%\end{equation}
-	%If we replace $(1-\epsilon) c t^{\alpha}$ with $y$ on the left side of \eqref{eq: inverse and inequality}, and respectively, replace $(1+\epsilon) c t^{\alpha}$ with $y$ on the right side of \eqref{eq: inverse and inequality}, then we get
-%\begin{equation}
-	%\Big(\frac{y}{c(1-\epsilon)}\Big)^{1/\alpha}
-	%\leq f^{(-1)}(y) \leq \Big(\frac{y}{c(1+\epsilon)}\Big)^{1/\alpha},
-	%\quad y \text{ large enough.}
-%\end{equation}
-	%This, in fact, implies that $ f^{(-1)}(t) \stackrel[t\to \infty]{}{\sim} c^{-1/\alpha} t^{1/\alpha}. $
-	%This proved one side of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}.
-	%The other direction of \eqref{eq: inverse and power equivalent at infinity with alpha > 0}, and \eqref{eq: inverse and power equivalent at 0 with alpha > 0}, as well as \eqref{eq: inverse and power equivalent with alpha < 0}, can be proved similarly.
-%\end{proof}
-%end deleted
-
-%new added
 \begin{lem}[{\cite[Theorem 1.5.12]{BinghamGoldieTeugels1989Regular}}] \label{lem: regularly variation and inverse}
@@
 \end{proof}
-%end new added
+
 \begin{lem}\label{lem:regularly_variation_and_integration}
@@
 \begin{equation}
-	%\limsup_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
 	\limsup_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}	
-	%\leq \lambda ^{\gamma_0}, 	
 	\leq \lambda ^{\gamma_0}.
-	%\quad t\in (0,\infty).
 \end{equation}
@@
 	\\&\quad = \lambda^{\gamma_0 + \epsilon} \frac{1}{1+ \frac{\int_{\gamma(x) > \gamma_0 + \epsilon}t^{\gamma(x) - (\gamma_0 + \epsilon)}m(dx)}{\int_{\gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)- (\gamma_0 + \epsilon)}m(dx)}},
-	%\xrightarrow[t\to 0]{} \lambda ^{\gamma_0 + \epsilon},
-	%\quad t\in (0, \infty),
 	\quad t\in (0, \infty),
-	\\&\quad \xrightarrow[(0,\infty) \ni t\to 0]{} \lambda ^{\gamma_0 + \epsilon}.
+	\\&\quad \xrightarrow[(0,\infty) \ni t\to 0]{} 
+	%\lambda ^{\gamma_0 + \epsilon}.
+	\lambda ^{\gamma_0 + \epsilon},
 \end{split}\end{equation}
@@
 \begin{equation}
-	%\liminf_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
 	\liminf_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
 	\geq \lambda ^{\gamma_0}. 
-	%, \quad t\in (0, \infty).
 \end{equation}
@@
 \begin{equation}
-	%\lim_{t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
 	\lim_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
 	= \lambda ^{\gamma_0},	
-	\quad \lambda \in (0,1]. %, t\in (0, \infty).
+	\quad \lambda \in (0,1]. 
 \end{equation}
@@
 \begin{equation}
-	%\lim_{t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)}
 	\lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)}
-	%= \lim_{t\to 0}\frac{\int_E f(x,t)m(dx)}{\int_E f(x, \lambda^{-1} t)m(dx)}
 	= \lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,t)m(dx)}{\int_E f(x, \lambda^{-1} t)m(dx)}
 	= \big((\lambda^{-1})^{\gamma_0} \big)^{-1}
-	= \lambda ^{\gamma_0}.%, \quad t\in (0, \infty).
+	= \lambda ^{\gamma_0}.
 \end{equation}
@@
 	\frac{\int_E t^{\gamma(x)} m(dx)}{t^{\gamma_0}}
-	%\xrightarrow[t\to 0]{} m\{x:\gamma(x) = 
 	\xrightarrow[(0,\infty)\ni t\to 0]{} m\{x:\gamma(x) = 
@@
 	We say that $(X_t)_{t\geq 0}$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
-	Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
+	Suppose that $(X_t)_{t\geq 0}$ is non-persistent, 
+%	then according to \cite[Section 8]{Li2011Measure-valued}, 
+	then according to \cite[Section 8.4]{Li2011Measure-valued},
+	there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
 \begin{itemize}
 \item
-	%$\mathbb N_x [ \forall t \geq 0, \|W_t\|=0] =0$, $\mathbb N_x[\|W_0 \|\neq 0] = 0$;
 	$\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$; 
@@
 	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure defined on some probability space 
-	%with mean measure $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
 	with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
@@
 \end{equation}
-	%Taking $\mu = \delta_x$ for some $x\in E$, $f = \lambda \mathbf 1_E$ for $\lambda > 0$ in the above equation, and letting $\lambda \to \infty$, we get
-	For each $x\in E$ and $t\geq 0$, taking $\mu = \delta_x$ and $f = \lambda \mathbf 1_E$ with $\lambda > 0$ in the above equation, letting $\lambda \to \infty$, we get
+	For each $x\in E$ and $t\geq 0$, taking $\mu = \delta_x$ and $f = \lambda \mathbf 1_E$ with $\lambda > 0$ in the above equation, and letting $\lambda \to \infty$, we get
 \begin{equation} \label{eq: definition of v_t(x)}
@@
 	Suppose that $g\in \mathscr B^+(E)$ satisfies that $\mu(P^\beta_Tg) \in (0,\infty)$.
-%new 
 	Then, according to \eqref{eq: mean of kuz measure}, $\mathbf P_\mu$ (resp. $\mathbb N_\mu$) can be size-biased by $X_T(g)$ (resp. $W_T(g)$).
-%end new
-	%We denote  the $W_T(g)$-transform of $\mathbb N_\mu$ and the $X_T(g)$-transform of $\mathbf P_\mu$ by $\mathbb N^{W_T(g)}_\mu$ and $\mathbf P_\mu^{X_T(g)}$ respectively.
 	Denote by $\mathbf P_\mu^{X_T(g)}$ (resp. $\mathbb N^{W_T(g)}_\mu$) the $X_T(g)$-transform of $\mathbf P_\mu$ (resp. the $W_T(g)$-transform of $\mathbb N_\mu$).
-	%The spine decomposition theorem characterizes the law of $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ in two steps.
 	The spine decomposition theorem characterizes the law of $\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}$ in two steps.
-	%The first step of the theorem says that $\{(X_t); \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the sum of two independent measure-valued processes:
 	The first step of the theorem says that $\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}$ can be decomposed in law as the sum of two independent measure-valued processes:
@@
 \begin{thm}[Size-biased decomposition,  \cite{RenSongSun2017Spine}]\label{thm: size-biased decomposition}
-%\begin{equation}
-	%\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}
-	%\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{W_T(g)}_\mu\}.
-%\end{equation}
 \begin{equation}
@@
 
-\begin{thm}[Spine representation,\cite{RenSongSun2017Spine}]\label{thm: spine representation}
+\begin{thm}[Spine representation, \cite{RenSongSun2017Spine}]\label{thm: spine representation}
 	Let $\{(Y_t)_{0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ be the spine representation of $\mathbb N^{W_T(g)}_\mu$ defined above.
@@
 	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is, the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$,
-	%on the finite interval $[0,T]$.
 	on the finite time interval $[0,T]$.
-	%In fact, one can also check that this consistence property is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)$.
 	In fact, one can also check that 
-	%this consistence property 
 	this consistency property
@@
 	Therefore, the actual statement of the classical spine decomposition theorem is different from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}:
-	%There is no need to restrict the corresponding processes on the finite interval $[0,T]$.
 	There is no need to restrict the corresponding processes on the finite time interval $[0,T]$.
@@
 	For each $\mu \in \mathcal M_E^\phi \cap \mathcal M_E^1$, we have
-%\begin{equation}
-	%\{(X_t)_{t\geq 0}; \mathbf P_\mu^{(\phi)}\}
-	%\overset{law}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu \} \otimes \{(W_t)_{t\geq 0}; \mathbb N^{(\phi)}_\mu\}.
-%\end{equation}
 \begin{equation}
@@
 \label{sec: Ergodicity}
-	%In this subsection, we discuss the ergodicity of the spine processes $\{(\xi_t); (\Pi^{(\phi)}_x)\}$ under Assumptions \ref{asp: 1}--\ref{asp: 3}.
 	In this subsection, we discuss the ergodicity of the spine process $\{(\xi_t)_{t\geq 0}; (\Pi^{(\phi)}_x)_{x\in E}\}$ under Assumptions \ref{asp: 1}--\ref{asp: 3}.
@@
 	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, 
-	%then we have
 	then
@@
 	Define $F(y,u):= \limsup_{t\to \infty} F(y,u,t)$ for each $y\in E$ and $u \in [0,1]$.
-	Then, for each $x\in E$ and $p \geq 1$, %we have
+	Then, for each $x\in E$ and $p \geq 1$, 
 \begin{equation}
@@
 	Finally,
-    %noting that that
     noting that $0\leq F \leq \bar F$, we get
@@
 	\\& \quad = \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle du,
-	%\quad x\in E,
 	\quad x\in E. \qedhere
@@
 	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, 
-	%then we have that, 
 	then for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z),$ $m$-almost everywhere.
@@
 \end{equation}
-	%From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$.
 	From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
 	According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp}, by monotonicity, 
-	%we see that $v_t$ satisfies the equation
 	we see that $(v_t)_{t > 0}$ satisfies the equation
@@
 	According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem, 
-	%$v_t$ also satisfies the equation
 	$(v_t)_{t> 0}$ also satisfies the equation
@@
 \label{prop: regularly varying of vt-phi-star}
-	%$\langle v_t,\phi^*\rangle_m $ is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
 	$(\langle v_t,\phi^*\rangle_m)_{t> 0} $ is regularly varying at $\infty$ with index $-\frac{1}{\gamma_0-1}$.
@@
 \end{prop}
-
-%deleted
-	%Notice that Theorem \ref{thm: main theorem}(2) is simply a corollary of Propositions \ref{prop: asymptotic equivalence of vtphi} and \ref{prop: regularly varying of vt-phi-star}.
-%end delted
 
@@
 \end{equation}
-	%In fact, using the Markov property of the spine process $(\xi_t)$ and the property of Poisson random measures, we have
 	In fact, using the Markov property of the spine process and the property of Poisson random measures, we have
@@
 	Then, if $t-s > t-t_0 \geq s_0$, 
-	%using the fact that that $v_t$ is non-increasing in $t$, we get
 	using the fact that $v_t$ is non-increasing in $t$, we get
@@
 \begin{equation}\begin{split}
-	%&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]
 	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
-	%\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}\not \equiv  0}|\mathscr F^\xi_{t_0}]\big)
 	\leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{ \| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]\big)
@@
 	\\&\quad = -\log \lim_{\lambda \to \infty} \exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
-	%\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{ w_{t-s} \not \equiv 0} \mathbf m^\xi(ds,dw)
 	\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{ \|w_{t-s}\| \neq 0} \mathbf m^\xi(ds,dw)
-	%= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{X_{t-s} \not\equiv 0}]\pi(\xi_s,dy)
 	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{ \|X_{t-s}\| \neq 0}]\pi(\xi_s,dy)
@@
 	Since the superprocess $(X_t)_{t\geq 0}$ is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$, 
-	%$\mathbf P_\mu (X_t \not \equiv 0) \xrightarrow[t\to 0]{} 1$.
 	$\mathbf P_\mu (\|X_t\| \neq 0) \xrightarrow[t\to 0]{} 1$.
@@
 	> 0
-%new 
 	\quad a.e..
-%end new
-\end{equation}
-%for Lebesgue 
-	%Therefore, we have almost every $r\in (0,\infty)$.
+\end{equation}
 	Therefore,
@@
 	R(r)
-	%= \int_r^\infty \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)}(x) ) u \phi \big), \phi^* \big\rangle_m^{-1} du,
 	= \int_r^\infty \big\langle \psi_0 \big(\cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du,
@@
 	According to Lemma \ref{lem:regularly_variation_and_integration}, 
-	%and using the fact that $\kappa(x)\phi(x)^\gamma(x)$ is bounded and the measure $\phi^* dm$ is finite, 
 	and using the fact that $\kappa(x)\phi(x)^{\gamma(x)}$ is bounded and the measure $\phi^* dm$ is finite, 
 	we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
-	%Notice that $-\gamma_0 < 0$, 
 	Noticing that $-(\gamma_0 - 1) < 0$,
 	according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
-	%Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and \eqref{eq: inverse of a regularly varying function with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.
 	Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and Corollary \ref{cro: regularly varing and inverse with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.
@@
 \begin{equation}\begin{split}
-	%&\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
 	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
@@
 \end{split}\end{equation}
-	%Therefore, we have $\big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
-	Therefore, we have $\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$ where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
+	Therefore, we have $\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$, where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
 	Now according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R} we have that
@@
 	R(r)
-	%&= \int_r^\infty \big\langle \psi_0 \big(x,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
 	&= \int_r^\infty \big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
@@
 \end{split}\end{equation}
-	%Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from \eqref{eq: inverse and power equivalent with alpha < 0} and above,
-	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from Corollary \ref{cro: regularly varing and inverse with alpha < 0} and above,
+	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from Corollary \ref{cro: regularly varing and inverse with alpha < 0} and the above,
 	we have
@@
 
-	%From the point of view of Laplace transforms, the desired result that, for any $f\in \mathscr B^+_b(E)$ and $x\in E$, $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ converge weakly to some probability distribution $F_{f,x}$ is equivalent to the following convergence:
 	From the point of view of Laplace transforms, the desired result that, for any $f\in \mathscr B^+_b(E)$ and $\mu\in \mathcal M_E^1$, $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\mu}(\cdot | \|X_t\| \neq 0)\big\}$ converge weakly to some probability distribution
-	%$F_{f,x}$ 
 	$F_f$
@@
 \begin{equation}
- 	%\frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\eta_t}
-	%&= \frac{1-e^{- V_t(\theta \eta_t f)(x)}}{\mathbf P_{\delta_x}(\|X_t\|\neq 0)} \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }\\
-	%&= \mathbf P_{\delta_x}[1-e^{-\theta \eta_t X_t(f)}|\|X_t\|\neq 0]  \frac{ \mathbf P_{\delta_x}(\|X_t\|\neq 0) } { \eta_t }
-	%\\& \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du). 
 	\mathbf P_\mu[1- e^{-\theta \eta_t X_t(f)} | \|X_t\|\neq 0]
@@
 \end{equation}
-	%Further, since $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
 	According to Theorem \ref{thm: main theorem}(2) and $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
 \begin{equation}\label{eq: equivalent result}
-	%\frac{V_t(\theta \eta_t f)(x)}{\eta_t}
-	%\quad \xrightarrow[t\to \infty]{} \phi(x) \int_{[0,\infty)}(1-e^{-\theta u})F_{f,x}(du).
 	\frac{\mu\big( V_t(\theta \eta_t f) \big)}{ \eta_t}
@@
 \end{equation}
-	%Therefore, to establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
 	Therefore, to establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
 
-	%In order to investigate the convergence of $(\frac{ V_t(\theta \eta_t f)(x)}{\eta_t})$, 
 	In order to investigate the convergence of $\mu\big( V_t(\theta \eta_t f) \big)/ \eta_t$, we need to investigate the properties of $\theta\to V_t(\theta f)$.
@@
 	Without loss of generality, we assume that $\langle f, \phi^* \rangle_m = 1$.
-	%As have been discussed in Subsection \ref{sec: conditional distribution}, in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
 	We claim that, in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
@@
 \end{equation}
-%new
 	In fact, by \eqref{eq: equation for normalized V_T}, we have $\|V_t(\theta \eta_t f)/ \eta_t \|_\infty \leq \theta \|\phi\|_\infty \|\phi^{-1}f\|_\infty.$
@@
 	which, by the discussion in Subsection \ref{sec: conditional distribution}, is equivalent to Theorem \ref{thm: main theorem}(3).
-%end new
 
@@
 	According to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
-
-	%Finally, by the definition of $M$,  $M\equiv 0$ implies the desired assertion.
 	Finally, by the definition of $M$,  $M\equiv 0$ implies the desired assertion \eqref{eq: we only need to proof this}.
 
-%ZY: I changed the format of the bibliography without marks 
 \begin{thebibliography}{10}

### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@
 %%%----Versions-----------------------------
+%stable-limit7.tex 2018/6/29 by Renming-----
 %stable-limit6.tex 2018/6/27 by Zhenyao-----
@@
 \setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
+\usepackage[utf8]{inputenc}
 \usepackage{hyperref}
-%new added
 \def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
 \def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
-%end new added
 \usepackage{mathrsfs}
 \usepackage{mathtools}
-%new added
 \mathtoolsset{showonlyrefs}
-%end new added
 \usepackage{stackrel}
-%Deleted
-%\usepackage{autonum}
-%\usepackage{amsmath}
-%end Deleted 
-%ZY: \mathtoolsset{showonlyrefs} commond can do the trick of 'autonum' package.
-%ZY: amsmath package is included in the amsart document class
 \newtheorem{thm}{Theorem}[section]
@@
 \newtheorem{asp}{Assumption}
-%\newtheorem{innerasp}{Assumption}
-%\newenvironment{asp}[1]{\renewcommand\theinnerasp{#1}\innerasp}{\endinnerasp}
 \numberwithin{equation}{section}
@@
 	{\large Limit theorems for a class of critical superprocesses with stable branching}
-	%\author{Yan-Xia Ren, Renming Song and Zhenyao Sun}
 		\author[Y.-X. Ren, R. Song and Z. Sun]{Yan-Xia Ren, Renming Song and Zhenyao Sun}
@@
 	In this paper, we consider a critical $(\xi,\psi)$-superprocess
-%	$\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$.
 $\{X; \mathbf P_\mu\}$.
 	$\xi$, the spatial motion of the superprocess, is a
-%	Hunt process on a locally compact separable metric space $E$, 
-Hunt process, on a locally compact separable metric space $E$, 
-	satisfying an intrinsically ultracontractive condition.
+%Hunt process, on a locally compact separable metric space $E$,
+%	satisfying an intrinsically ultracontractive condition.
+Hunt process on a locally compact separable metric space $E$ with reference measure $m$.
 	$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty]$ of the form
@@
 \end{equation}
-%	where $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfy 
   with $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfying
@@
 
-	We show that $\mathbf P_{\delta_x}( \| X_t \| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $(\gamma_0 - 1)^{-1}$.
-	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that 
-\begin{equation}
-	\mathbf P_{\delta_x}( \|X_t\| \neq0) 
-	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
+%	We show that 
+	We show that, under some conditions, 
+	$\mathbf P_{\delta_x}( \| X_t \| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $(\gamma_0 - 1)^{-1}$.
+	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, 
+%	we show that
+ we show that, for any finite initial measure $\mu$ on $E$, 
+\begin{equation}
+%	\mathbf P_{\delta_x}( \|X_t\| \neq0)
+%	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
+\mathbf P_{\mu}( \|X_t\| \neq0)
+	\stackrel[t\to \infty]{}{\sim} \langle\phi \eta_t,
 \end{equation}
@@
 \end{equation}
-	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform
+%	where 
+ where $\phi$ ($\phi^*$, resp.) is the principal eigenfunction of the mean semigroup 
+ (the dual of of the eman semigroup) of the superprocess, 	
+	$\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform
 \begin{equation}
@@
 %\subjclass[2010]{60J80, 60F05}
-%\keywords{}
+\subjclass[2010]{Premary: 60J68; 60F05. Secondary 60J80; 60J25}
+\keywords{Critical superprocess; stable branching, scaling limit; intrinsic ultracontractivity; regular variation}
 %\date{}
@@
 	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
-%	Since then, lots of analogous results were obtained for more general 
 	Since then, lots of analogous results have been obtained for more general
@@
 	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
-\begin{equation}
+%\begin{equation}
+\begin{equation}\label{e:zloltarev}
 	E[e^{- u \mathbf z^{(\alpha)}}]
@@
 \end{equation}
-	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
+%	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
 	Slack \cite{Slack1972Further} also considered the converse of this problem:
@@
 \end{equation}
-	where $\mathbf z^{(\alpha)}$ is a random variable with  Zolotarev's distribution with index  $\alpha$.
+	where $\mathbf z^{(\alpha)}$ is a random variable with  
+%	Zolotarev's distribution with index  $\alpha$.
+   Laplace transform given by \eqref{e:zloltarev}.
 	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
@@
 
-%	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} 
 	Asmussen and Hering \cite[Sections~6.3~and~6.4]{AsmussenHering1983Branching}
@@
 	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in
-%\cite[Theorem~4.2]{AsmussenHering1983Branching} 
 \cite[Theorem~6.4.2]{AsmussenHering1983Branching}
@@
 	which can be viewed as superprocesses without spatial movements.
-	Kyprianou \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. 
+	Kyprianou \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$.
 	He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
@@
 \end{equation}
-    where $\mathbf z^{(\gamma - 1)}$ is a random variable with Zolotarev's distribution with index $\gamma - 1$.
+    where $\mathbf z^{(\gamma - 1)}$ is a random variable with 
+%    Zolotarev's distribution with index $\gamma - 1$.
+     Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
 	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
@@
 	= c z^\gamma l(z),
-%	\quad z\geq 0.
 	\quad z\geq 0,
@@
 	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem:
-%	Suppose that $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP 
     Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP
@@
 \end{equation}
-	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
+	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with
+%	Zolotarev's distribution with index $\gamma_0 - 1$.
+   Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
 	Precise statements of the assumptions and the results are presented in the next subsection.
@@
 	For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
-    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(m)$.
+    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space
+    %$L^2(m)$.
+    $L^2(E, m)$.
 	For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
@@
 \begin{asp} \label{asp: 1}
-%	There exists an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$, and a family of strictly positive, 
     There exist an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$ and a family of strictly positive,
@@
 	Under Assumption \ref{asp: 1}, it is proved in
-%	\cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} 
 	\cite{RenSongZhang2015Limit, RenSongZhang2017Central}
@@
     $(p^\beta_t)_{t\geq 0}$ is called the
-%    \emph{density of semigroup $(P^\beta_t)_{t\geq 0}$}.
     \emph{density}  of the semigroup $(P^\beta_t)_{t\geq 0}$.
@@
 	It is proved in
-%	\cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} 
 	\cite{RenSongZhang2015Limit, RenSongZhang2017Central}
@@
 	Denote by $\sigma(L)$ and $\sigma(L^*)$ the spectra of $L$ and $L^*$, respectively.
-%	According to \cite[Theorem V.6.6.]{Schaefer1974Banach}, 
 	According to \cite[Theorem V.6.6]{Schaefer1974Banach},
@@
 	$\{X; \mathbf P\}$ is non-persistent, that is, for each $t > 0$ and $x\in E$,
-%	$\mathbf P_{\delta_x}( \| X_t\| \neq 0) > 0$.
 	$\mathbf P_{\delta_x}( \| X_t\| = 0) > 0$.
@@
 	For each $\mu \in \mathcal M^1_E$, $\mathbf P_{\mu}(\|X_t\| \neq 0)$ converges to
-	%$0$, and is regularly varying with index $-(\gamma_0-1)^{-1}$ as $t \to \infty$.
 	$0$ as $t \to \infty$ and is regularly varying at infinity with index $-(\gamma_0-1)^{-1}$.
@@
 \begin{equation}
-	\mathbf P_{\mu}(\|X_t\| \neq 0)
-	\stackrel[t\to \infty]{}{\sim} \mu(\phi) \eta_t.
+%	\mathbf P_{\mu}(\|X_t\| \neq 0)
+%	\stackrel[t\to \infty]{}{\sim} \mu(\phi) \eta_t.
+\lim_{t\to\infty} \eta_t^{-1}\mathbf P_{\mu}(\|X_t\| \neq 0)=\mu(\phi).
 \end{equation}
@@
 \end{itemize}
-	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Zolotarev's distribution with index $\gamma_0 - 1$.
+	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with
+%	Zolotarev's distribution with index $\gamma_0 - 1$.
+   Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
 \end{thm}
@@
 	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of
-%	critical superprocesses with finite second moment.
  general critical superprocesses with finite second moment.
 	In this paper, we will  generalize these arguments to a class of general critical superprocesses without finite second moment, and establish Theorem \ref{thm: main theorem}(2).
-	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform of Zolotarev's distribution can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
+	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that 
+%	the Laplace transform of Zolotarev's distribution can be characterized by a non-linear 
+the Laplace transform given in \eqref{e:zloltarev} can be characterized by a non-linear 
+	delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
 	Using the spine method, we show that the Laplace transform of the one-dimensional distributions of the superprocess, after a proper rescaling, can be 	characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
@@
 	A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in
-%	\cite{RenSongSun2017A-2-spine} and \cite{RenSongSun2017Spine}.
 	\cite{RenSongSun2017A-2-spine, RenSongSun2017Spine}.
@@
 	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in
-%	\cite{RenSongSun2017Spine} and \cite{RenSongZhang2015Limit} 
 	\cite{RenSongSun2017Spine, RenSongZhang2015Limit}
@@
     In Subsection \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-    In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize Zolotarev's distribution.
+    In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize 
+%    Zolotarev's distribution.
+   the distribution with Laplace transform \eqref{e:zloltarev}.
 	Finally,  in Subsection
@@
 	Further, if $\gamma = 0$, then we say $f$ is slowly varying.
-%	According to \cite[Theorem 1.3.1.]{BinghamGoldieTeugels1989Regular}, 
 	According to \cite[Theorem 1.3.1]{BinghamGoldieTeugels1989Regular},
@@
 
-%\begin{lem}[{\cite[Propositions 1.5.8. and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
 \begin{lem}[{\cite[Propositions 1.5.8 and 1.5.10]{BinghamGoldieTeugels1989Regular}}]
@@
 	\\&\quad \xrightarrow[(0,\infty) \ni t\to 0]{}
-	%\lambda ^{\gamma_0 + \epsilon}.
 	\lambda ^{\gamma_0 + \epsilon},
@@
 	Suppose that $(X_t)_{t\geq 0}$ is non-persistent,
-%	then according to \cite[Section 8]{Li2011Measure-valued}, 
 	then according to \cite[Section 8.4]{Li2011Measure-valued},
@@
 
-\subsection{Zolotarev's distribution}
+%\subsection{Zolotarev's distribution}
+\subsection{Distribution with Laplace transform (\ref{e:zloltarev})}
 \label{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}
 
-	Recall that a non-negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
-\begin{equation}
-	E[1-e^{-\theta\mathbf z^{(\gamma_0 - 1)}}]
-	=\Big( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} \Big)^{\frac{1}{\gamma_0 - 1}}.
-\end{equation}
-	It turns out that we can characterize this distribution by the following result.
+%Recall that a non-negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
+%\begin{equation}
+%	E[1-e^{-\theta\mathbf z^{(\gamma_0 - 1)}}]
+%	=\Big( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} \Big)^{\frac{1}{\gamma_0 - 1}}.
+%\end{equation}
+%	It turns out that we can characterize this distribution by the following result.
+The distribution with Laplace transform \eqref{e:zloltarev} can be characterized by the
+following result.
 
@@
 	Ren, Y.-X., Song, R. and Sun, Z.:
-	\emph{A 2-spine decomposition of the critical galton-watson tree and a probabilistic proof of yaglom's theorem.} 
+	\emph{A 2-spine decomposition of the critical 
+% galton-watson tree and a probabilistic proof of yaglom's theorem.}
+Galton-Watson tree and a probabilistic proof of Yaglom's theorem.}
 	\ARXIV{1706.07125}

### 2019-03-30 stableLimit.tex
change stableLimit.tex submitted180701

@@
-%!TEX spellcheck
-%%%----Versions-----------------------------
-%stable-limit7.tex 2018/6/29 by Renming-----
-%stable-limit6.tex 2018/6/27 by Zhenyao-----
-%stable-limit5.tex 2018/6/22 by Renming------
-%stable-limit4.tex 2018/6/21 by Yanxia-------
-%stable-limit3.tex 2018/6/13 by Zhenyao-------
 %---The preamble----------------------
-\documentclass[12pt, a4paper]{amsart}
+\documentclass[12pt,a4paper]{amsart}
 \setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
@@
 \title
-	%[Manuscript]
 	[Superprocesses with stable branching]
@@
 \email{zhenyao.sun@pku.edu.cn}
+\thanks{Zhenyao Sun is the corresponding author.}
 \begin{abstract}
-	In this paper, we consider a critical $(\xi,\psi)$-superprocess
-$\{X; \mathbf P_\mu\}$.
-	$\xi$, the spatial motion of the superprocess, is a
-%Hunt process, on a locally compact separable metric space $E$,
-%	satisfying an intrinsically ultracontractive condition.
-Hunt process on a locally compact separable metric space $E$ with reference measure $m$.
-	$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty]$ of the form
-\begin{equation}
-	\psi(x,z)
-	= -\beta (x) z + \kappa(x) z^{\gamma(x)},
-	\quad x\in E, z \geq 0,
-\end{equation}
-  with $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfying
-\begin{equation}
-	1
-	< \gamma(\cdot )
-	<2;
-	\quad \gamma_0
-	:= \operatorname{ess\,inf}_{m(dx)} \gamma(x)
-	> 1;
-	\quad \operatorname{ess\,inf}_{m(dx)}\kappa(x)
-	> 0.
-\end{equation}
-
-%	We show that 
-	We show that, under some conditions, 
-	$\mathbf P_{\delta_x}( \| X_t \| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $(\gamma_0 - 1)^{-1}$.
-	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, 
-%	we show that
- we show that, for any finite initial measure $\mu$ on $E$, 
-\begin{equation}
-%	\mathbf P_{\delta_x}( \|X_t\| \neq0)
-%	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
-\mathbf P_{\mu}( \|X_t\| \neq0)
-	\stackrel[t\to \infty]{}{\sim} \langle\phi \eta_t,
-\end{equation}
-	and for a large class of non-negative testing functions $f$,
-\begin{equation}
-	\{\eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \}
-	\xrightarrow[t\to \infty]{\operatorname{law}} \langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
-\end{equation}
-%	where 
- where $\phi$ ($\phi^*$, resp.) is the principal eigenfunction of the mean semigroup 
- (the dual of of the eman semigroup) of the superprocess, 	
-	$\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform
-\begin{equation}
-	E[e^{- u \mathbf z^{(\alpha)}}]
-	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
-	\quad u \geq 0.
-\end{equation}
+We consider a critical superprocess $\{X;\mathbf P_\mu\}$ with general spatial motion and spatially dependent stable branching mechanism with lowest stable index $\gamma_0 > 1$.
+We first show that, under some conditions, $\mathbf P_{\mu}(\|X_t\|\neq 0)$ converges to $0$ as $t\to \infty$ and is regularly varying with index $(\gamma_0-1)^{-1}$.
+Then we show that, for a large class of non-negative testing functions $f$, the distribution of $\{X_t(f);\mathbf P_\mu(\cdot|\|X_t\|\neq 0)\}$, after appropriate rescaling, converges weakly to a positive random variable $\mathbf z^{(\gamma_0-1)}$ with Laplace transform $E[e^{-u\mathbf z^{(\gamma_0-1)}}]=1-(1+u^{-(\gamma_0-1)})^{-1/(\gamma_0-1)}.$
 \end{abstract}
-%\subjclass[2010]{60J80, 60F05}
-\subjclass[2010]{Premary: 60J68; 60F05. Secondary 60J80; 60J25}
+\subjclass[2010]{Primary: 60J68; 60F05. Secondary 60J80; 60J25}
 \keywords{Critical superprocess; stable branching, scaling limit; intrinsic ultracontractivity; regular variation}
-%\date{}
 \maketitle
@@
 	It is well known that for a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$, we have
-\begin{equation}\label{eq: Kolmogorov's result with finite variance}
+\begin{align}\label{eq: Kolmogorov's result with finite variance}
 	n P(Z_n > 0)
 	\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
-\end{equation}
+\end{align}
 	and
-\begin{equation}\label{eq: Yaglom's result with finite variance}
+\begin{align}\label{eq: Yaglom's result with finite variance}
 	\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
 	\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
-\end{equation}
+\end{align}
 	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
 	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
-	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
+	For further references to these results, see 
+	\cite{Harris2002The-theory, KestenNeySpitzer1966The-Galton-Watson}.
 	Since then, lots of analogous results have been obtained for more general
-	critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.
-
-	Notice that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
+	critical branching processes with finite 2nd moment, 
+	see \cite{AsmussenHering1983Branching, AthreyaNey1974Functionals, AthreyaNey1972Branching, JoffeSpitzer1967On-multitype} for example.
+
+	Notice that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid when  $\sigma^2 = \infty$,  
+	see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
     In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, and thus more appropriate scalings are needed.
@@
 	Assume that the  generating function $f(s)$ of the offspring distribution is of the form
-\begin{equation}\label{eq: offspring generating function with alpha moment}
+\begin{align}\label{eq: offspring generating function with alpha moment}
 	f(s)
@@
 	\quad s\geq 0,
-\end{equation}
+\end{align}
 	where $\alpha\in (0, 1]$ and $l$ is a function slowly varying at $0$.
 	Then
-\begin{equation} \label{eq: extinction probability of critical GW process without 2rd moment}
+\begin{align} \label{eq: extinction probability of critical GW process without 2rd moment}
 	P(Z_n > 0)
 	= n^{-1/\alpha} L(n),
-\end{equation}
+\end{align}
 	where $L$ is a function slowly varying at $\infty$, and
-\begin{equation} \label{eq: conditional distribution of critical GW process without 2rd moment}
+\begin{align} \label{eq: conditional distribution of critical GW process without 2rd moment}
 	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
 	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
-\end{equation}
+\end{align}
 	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
-%\begin{equation}
-\begin{equation}\label{e:zloltarev}
+\begin{align}\label{e:zloltarev}
 	E[e^{- u \mathbf z^{(\alpha)}}]
@@
 	\quad u \geq 0.
-\end{equation}
-%	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
-	Slack \cite{Slack1972Further} also considered the converse of this problem:
+\end{align}
+In  \cite{Slack1972Further}, Slack also considered the converse of this problem:
 	In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have
@@
 	the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
-	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.
+	For shorter and more unified approaches to these results, we refer our readers to \cite{Borovkov1989Method, Pakes2010Critical}.
 
@@
 	Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
-	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right  eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
+	Let $M$ be the mean matrix of $\mathbf Z$. Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, 
+	respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
 	Suppose that
-\begin{equation}\label{eq: regularly varying condition for multitype branching process}
+\begin{align}\label{eq: regularly varying condition for multitype branching process}
 	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
@@
 	\quad x > 0,
-\end{equation}
-	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$;
+\end{align}
+	where $0 < \alpha \leq 1$; 
+	$l$ is slowly varying at $0$;
 	and the matrix $G(\mathbf s)$ is defined by
-\begin{equation}
+\begin{align}
 	\mathbf 1 - \mathbf F(\mathbf s)
@@
 	\quad \mathbf s \in \mathbb R_+^d.
-\end{equation}
+\end{align}
     Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
 	It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
-\begin{equation} \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
-	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
+\begin{align} \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
+    n l(a_n)
+	\operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
 	\xrightarrow[n\to \infty]{}
 	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
-\end{equation}
+\end{align}
 	and for each $\mathbf j \in \mathbb N_0^d$,
-\begin{equation}\label{eq: conditioned normalized multitype branching process}
+\begin{align}\label{eq: conditioned normalized multitype branching process}
 	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
 	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
-\end{equation}
-	where $\mathbf z^{(\alpha)}$ is a random variable with  
-%	Zolotarev's distribution with index  $\alpha$.
-   Laplace transform given by \eqref{e:zloltarev}.
+\end{align}
+	where $\mathbf z^{(\alpha)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev}.
 	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
@@
     $\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty)$ of the form
-\begin{equation} \label{eq: branching mechanism}
+\begin{align} \label{eq: branching mechanism}
 	\psi(x,z):=
@@
 	\quad x\in E, z\geq 0,
-\end{equation}
+\end{align}
 	where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
@@
 	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition
-\begin{equation}\label{eq: second moment condition}
+\begin{align}\label{eq: second moment condition}
 	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
 	< \infty.
-\end{equation}
+\end{align}
 	For any finite measure $\mu$ on $E$ and any measurable function $f$ on $E$, we use $\langle f,\mu\rangle$ to denote the integral of $f$ with respect to $\mu$.
@@
 	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
-\begin{equation}\label{eq: Kolmogorov type result with 2rd moment}
+\begin{align}\label{eq: Kolmogorov type result with 2rd moment}
 	t \mathbf P_\mu(\|X_t\| \neq 0)
@@
 \langle \phi, \mu \rangle,
-\end{equation}
+\end{align}
 	and for a large class of testing functions $f$ on $E$,
-\begin{equation}\label{eq: Ygalom type result with 2rd moment}
+\begin{align}\label{eq: Ygalom type result with 2rd moment}
 	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot |\|X_t\| \neq 0)\}
 	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
-\end{equation}
+\end{align}
 	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
@@
 	which can be viewed as superprocesses without spatial movements.
-	Kyprianou \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$.
+	Kyprianou and Pardo \cite{Kyprianou2008Continuous} 
+	considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
 	He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
-\begin{equation} \label{eq: conditional limit of CSBP with stable branching}
+\begin{align} \label{eq: conditional limit of CSBP with stable branching}
 	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
 	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
-\end{equation}
-    where $\mathbf z^{(\gamma - 1)}$ is a random variable with 
-%    Zolotarev's distribution with index $\gamma - 1$.
-     Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
+\end{align}
+    where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
 	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
 	CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
-\begin{equation}\label{eq: regular varing of branching mechanism of a CSBP}
+\begin{align}\label{eq: regular varing of branching mechanism of a CSBP}
 	\psi(z)
@@
 	\quad z\geq 0,
-\end{equation}
+\end{align}
 	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
 	It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
-\begin{equation}\label{eq: conditional limit of CSBP}
+\begin{align}\label{eq: conditional limit of CSBP}
 	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
 	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
-\end{equation}
+\end{align}
 	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem:
@@
 	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
-\begin{equation}
+\begin{align}
 	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
 	\quad x\in E, z \geq 0,
-\end{equation}
+\end{align}
 	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
-	We will show that $\mathbf P_{\delta_x}( \| X_t\| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
+	Let $\mu$ be an arbitrary finite initial measure on $E$.
+	We will show that 
+	$\mathbf P_{\mu}( \| X_t\| \neq 0) $
+	converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
 	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we will show that
-\begin{equation}
-	\mathbf P_{\delta_x}( \|X_t\| \neq0)
-	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
-\end{equation}
+\begin{align}
+	\lim_{t\to \infty}\eta^{-1}_t \mathbf P_{\mu}( \|X_t\| \neq0)
+	= \mu(\phi),
+\end{align}
 	and for a large class of non-negative testing functions $f$,
-\begin{equation}\label{eq: result2}
-	\{ \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \}
+\begin{align}\label{eq: result2}
+	\{ \eta_t X_t(f) ; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0) \}
 	\xrightarrow[t\to \infty]{\operatorname{law}}
 	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
-\end{equation}
-	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with
-%	Zolotarev's distribution with index $\gamma_0 - 1$.
-   Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
+\end{align}
+	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ 
+	$C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ 
+	and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} 
+	(with $\alpha=\gamma_0-1$).
 	Precise statements of the assumptions and the results are presented in the next subsection.
@@
 	For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
-    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space
-    %$L^2(m)$.
-    $L^2(E, m)$.
+    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
 	For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
@@
 	We say an $\mathcal M^1_E$-valued Hunt process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
-\begin{equation}
+\begin{align}
 	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
-\end{equation}
+\end{align}
 	where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
-\begin{equation}\label{eq:FKPP_in_definition}
+\begin{align}\label{eq:FKPP_in_definition}
 	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
@@
 	\quad t \geq 0, x \in E.
-\end{equation}
+\end{align}
 	(In this paper, for any real-valued function $F$ on $E\times [0,\infty)$ and real-valued function $f$ on $E$, we write $F(x,f):= F(x,f(x))$ for simplicity.)
@@
 	Define the \emph{Feynman-Kac semigroup}
-\begin{equation}
+\begin{align}
 	P^\beta_tf(x)
@@
 	\quad t\geq 0, x\in E, f\in \mathscr B_b(E).
-\end{equation}
+\end{align}
 	(Notice that if $\beta \equiv 0$, then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
 	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
-\begin{equation} \label{eq: Ygalom type result without 2rd moment}
+\begin{align} \label{eq: Ygalom type result without 2rd moment}
 	\mathbf P_\mu [X_t(f)]
@@
 	t \geq 0,f \in \mathscr B_b(E).
-\end{equation}
+\end{align}
     The  mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
@@
     There exist an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$ and a family of strictly positive,
-	bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that,
-\begin{equation}\begin{split}
+	bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that
+\begin{align}
 	\Pi_x[ f(\xi_t)\mathbf 1_{t < \zeta} ]
@@
 	&\quad t> 0;
-\end{split}\end{equation}
+\end{align}
 	and the functions $x \mapsto \int_E p_t(x,y)^2 m(dy)$ and $x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous.
@@
 	that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
-\begin{equation}
+\begin{align}
 	e^{-\|\beta\|_\infty t} p_t(x,y)
@@
 	\quad t>0, x, y\in E,
-\end{equation}
+\end{align}
 	and that for any $t>0, x\in E$ and $f \in \mathscr B_b(E)$,
-\begin{equation}
+\begin{align}
 	P^\beta_t f(x)
 	= \int_E p_t^\beta (x,y) f(y) m(dy).
-\end{equation}
+\end{align}
     $(p^\beta_t)_{t\geq 0}$ is called the
@@
 	Define the dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ by
-\begin{equation}
+\begin{align}
 	P^{\beta *}_0 = I;
@@
 	\quad t>0, x\in E, f\in \mathscr B_b(E).
-\end{equation}
+\end{align}
 	It is proved in
@@
 	Now, from
-\begin{equation}
+\begin{align}
 	\mathbf P_\mu[X_t(\phi)]
 	= e^{\lambda t} \mu(\phi),
-\end{equation}
+	\quad t \geq 0,
+\end{align}
 	we see that, if $\lambda > 0$, the mean of $X_t(\phi)$ will increase exponentially; if $\lambda < 0$, the mean of $X_t(\phi)$ will decrease exponentially; and if $\lambda = 0$, the mean of $X_t(\phi)$ will be a constant.
@@
 
-	Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the underlying process $\xi$.
+	Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the spatial process $\xi$.
 	Our second assumption on the spatial process $\xi$ is the following:
@@
 	In fact, it is proved in \cite{KimSong2008Intrinsic} that for each $t>0$, $(p^\beta_t(x,y))_{x,y\in E}$ is comparable to $(\phi(x)\phi^*(y))_{x,y\in E}$ in the sense that there is a constant $c_t > 1$ such that
-\begin{equation}\label{eq: p-t-beta is comparable to phi phi-star}
+\begin{align}\label{eq: p-t-beta is comparable to phi phi-star}
 	c_t^{-1}
@@
 	\quad x,y \in E.
-\end{equation}
+\end{align}
     It is also shown in \cite{KimSong2008Intrinsic} that there are constants $c_0, c_1 > 0$ such that
-\begin{equation}\label{eq:q(t,x,y)}
+\begin{align}\label{eq:q(t,x,y)}
 	\sup_{x,y\in E} \Big|\frac{p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \Big|
@@
 	\quad t > 1.
-\end{equation}
+\end{align}
 	We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
@@
 	The branching mechanism $\psi$ is of the form:
-\begin{equation}\begin{split}
+\begin{align}
 	\psi(x,z)
@@
 	\quad x\in E, z \geq 0,
-\end{split}\end{equation}
+\end{align}
 	where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
@@
 	Here we use the definition of the Gamma function on the negative half line:
-\begin{equation}\label{eq: definition of Gamma function}
+\begin{align}\label{eq: definition of Gamma function}
 	\Gamma(x)
@@
 	\quad -n< x< -n+1, n\in \mathbb N.
-\end{equation}
+\end{align}
 
@@
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
-\begin{equation}
-%	\mathbf P_{\mu}(\|X_t\| \neq 0)
-%	\stackrel[t\to \infty]{}{\sim} \mu(\phi) \eta_t.
-\lim_{t\to\infty} \eta_t^{-1}\mathbf P_{\mu}(\|X_t\| \neq 0)=\mu(\phi).
-\end{equation}
+\begin{align}
+	\lim_{t\to\infty} \eta_t^{-1}\mathbf P_{\mu}(\|X_t\| \neq 0)
+	=\mu(\phi).
+\end{align}
 \item[(3)]
@@
 	Let $f \in \mathscr B^+(E)$ be such that $\langle f, \phi^* \rangle_m > 0$ and $\| \phi^{-1}f \|_\infty < \infty$. Then for each $\mu \in \mathcal M_E^1$,
-\begin{equation}
+\begin{align}
 	\{\eta_t X_t(f) ; \mathbf P_{\mu}(\cdot |\|X_t\| \neq 0) \}
 	\xrightarrow[t\to \infty]{\operatorname{law}} \langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}.
-\end{equation}
+\end{align}
 \end{itemize}
-	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with
-%	Zolotarev's distribution with index $\gamma_0 - 1$.
-   Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
+	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ 
+	and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} 
+	(with $\alpha=\gamma_0 -1$).
+
 \end{thm}
@@
 	To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 	$X$.
-	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local}, \cite{LiuRenSong2009Llog}.
+	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
 	The family of functions used for the size-biased transform is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$, which is a martingale.
@@
 	As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation satisfied by the survival probability $(t,x) \mapsto P_{\delta_x}(\|Y_t\| \neq 0)$ is tricky.
-	Instead, by using a spine decomposition approach, Powell \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$ where $\phi(x)$ is the principal eigenfunction of the mean semigroup of $(Y_t)$, and $a(t)$ is a function capturing the uniform speed.
-	Then, the problem is reduced to the study of a single ordinary differential equation satisfied by the speed function $a(t)$.
+	Instead, by using a spine decomposition approach, Powell \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$, where $\phi(x)$ is the principal eigenfunction of the mean semigroup of $(Y_t)$ and $a(t)$ is a function capturing the uniform speed.
+	Then, the problem is reduced to the study of a single ordinary differential equation satisfied by $a(t)$.
 	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of
  general critical superprocesses with finite second moment.
-	In this paper, we will  generalize these arguments to a class of general critical superprocesses without finite second moment, and establish Theorem \ref{thm: main theorem}(2).
-	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that 
-%	the Laplace transform of Zolotarev's distribution can be characterized by a non-linear 
-the Laplace transform given in \eqref{e:zloltarev} can be characterized by a non-linear 
+	In this paper, we will  generalize these arguments to a class of general critical superprocesses without finite second moment and establish Theorem \ref{thm: main theorem}(2).
+	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform given in \eqref{e:zloltarev} can be characterized by a non-linear 
 	delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
@@
 	(for general critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
-    First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding processes, and then the second moment condition was used to extend the result to more general testing functions.
+    First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding process, and then the second moment condition was used to extend the result to more general testing functions.
 	However, in the present case, since we are not assuming the second moment condition, this type of argument does not work.
-	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for a large class of general testing functions at the same time.
+	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for a large class of general testing functions
+	in one stroke.
 
@@
     In Subsection \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-    In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize 
-%    Zolotarev's distribution.
-   the distribution with Laplace transform \eqref{e:zloltarev}.
-	Finally,  in Subsection
-    \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
+    In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
+	Finally, in Subsection \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
 
@@
 	If $m \in \mathcal M^1_E$, then
-\begin{equation}
+\begin{align}
 	\int_E f_0(t,x)m(dx)
@@
 	\int_E f_1(t,x)m(dx).
-\end{equation}
+\end{align}
 \end{lem}
@@
 	Since
-\begin{equation}\begin{split}
+\begin{align}
 	&\Big| \frac{	\int_E f_0(t,x)m(dx) }{ 	\int_E f_1(t,x)m(dx)  } - 1 \Big|
@@
 	\xrightarrow[t\to t_0]{} 0,
-\end{split}\end{equation}
+\end{align}
 	the assertion is valid.
@@
 	For $f\in \mathscr B^{++}((0,\infty))$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\gamma \in (-\infty,\infty)$ if for any $\lambda \in (0,\infty)$,
-\begin{equation}
+\begin{align}
 	\lim_{t\to\infty}\frac{f(\lambda t)}{f(t)}
@@
 	= \lambda^\gamma\Big).
-\end{equation}
+\end{align}
 	In this case we write  $f\in \mathcal R^\infty_\gamma$ (resp. $f\in \mathcal R^0_\gamma$).
@@
 	if $L$ is a function slowly varying at $\infty$, then it can be written in the form
-\begin{equation}
+\begin{align}
 	L(t)
 	= c(t) \exp\Big\{\int_{t_0}^t \epsilon(u) \frac{du}{u}\Big\},\quad t\geq t_0,
-\end{equation}
+\end{align}
 	for some $t_0>0$, where $(c(t))_{t\geq t_0}$ and $(\epsilon(t))_{t\geq t_0}$ are measurable functions with $c(t) \xrightarrow[t\to \infty]{} c \in (0,\infty)$ and $\epsilon(t) \xrightarrow[t\to \infty]{} 0$.
@@
 	Let $t_0\in (0,\infty)$ be large enough so that $L$ is locally bounded on $[t_0,\infty)$. If $\alpha>0 $, then
-\begin{equation}
+\begin{align}
 	\int_{t_0}^t L(u)du^\alpha
 	\stackrel[t\to \infty]{}{\sim} t^\alpha L(t).
-\end{equation}
+\end{align}
 \item
 	If $\alpha< 0$ then $\int_t^\infty L(u) du^\alpha < \infty$ for $t$ large enough, and
-\begin{equation}
+\begin{align}
 	-\int_t^\infty L(u)du^\alpha
 	\stackrel[t\to \infty]{}{\sim} t^\alpha L(t).
-\end{equation}
+\end{align}
 \end{itemize}
@@
 	If $\alpha < 0$, then
-\begin{equation}
+\begin{align}
 	-\int_s^{s_0} l(u)du^\alpha
 	\stackrel[s\to 0]{}{\sim} s^{\alpha} l(s).
-\end{equation}
+\end{align}
 \item
 	If $\alpha > 0$, then $\int_0^s l(u)du^\alpha<\infty$ for $s$ small enough, and
-\begin{equation}
+\begin{align}
 	\int_0^s l(u)du^\alpha
 	\stackrel[s\to 0]{}{\sim} s^{\alpha} l(s).
-\end{equation}
+\end{align}
 \end{itemize}
@@
 	If $\alpha<0 $, then according to Lemma \ref{lem: exchange slowly varying function and integration}, we have
-\begin{equation}
+\begin{align}
 	\int_{t_0}^t L(u)du^{-\alpha}
 	\stackrel[t\to \infty]{}{\sim} t^{-\alpha}  L(t).
-\end{equation}
+\end{align}
 	Replacing $t$ with $s^{-1}$, we have
-\begin{equation}
+\begin{align}
 	-\int_{s}^{s_0} l(u)du^{\alpha}
@@
 	=s^\alpha l(s),
-\end{equation}
+\end{align}
 	as desired.
@@
 	If $f \in \mathcal R_\alpha^\infty$ with $\alpha > 0$, there exists $g \in \mathcal R^\infty_{1/\alpha}$ with
-\begin{equation}
+\begin{align}
 	g(f(t))
@@
 	t.
-\end{equation}
+\end{align}
 	Here $g$ is determined uniquely up to asymptotic equivalence as $t\to \infty$.
@@
 	If $f \in \mathcal R_\alpha^0$ with $\alpha < 0$, there exists $g \in \mathcal R^\infty_{1/\alpha}$ with
-\begin{equation} \label{eq: asymptotic inverse with alpha < 0}
+\begin{align} \label{eq: asymptotic inverse with alpha < 0}
 	g(f(t))
@@
 	Noticing that $-\alpha > 0$, according to Lemma \ref{lem: regularly variation and inverse}, there exists $h \in \mathcal R_{-1/\alpha}^{\infty}$ such that
-\begin{equation} \label{eq: inverse between h and f}
+\begin{align} \label{eq: inverse between h and f}
 	h(\tilde f(t))
@@
 	t.
-\end{equation}
+\end{align}
 	Denoting by $g := h^{-1} \in \mathcal R_{1/\alpha}^\infty$, the above translates to \eqref{eq: asymptotic inverse with alpha < 0}.
@@
 	Let $ \gamma \in \mathscr B_b(E)$ with
-\begin{equation}
+\begin{align}
 	\gamma_0
@@
 	:= \sup\{r:m(x:\gamma(x) < r) = 0\}.
-\end{equation}
+\end{align}
 	Then $\big(\int_E t^{\gamma(x)} m(dx)\big)_{t\in (0,\infty)} \in \mathcal R^0_{\gamma_0}$.
 	Further, if $m\{x:\gamma(x) = \gamma_0\}>0$, then
-\begin{equation}
+\begin{align}
 	\int_E t^{\gamma(x)} m(dx)
 	\stackrel[t\to 0]{}{\sim}  m\{x:\gamma(x) = \gamma_0\} t^{\gamma_0}.
-\end{equation}
+\end{align}
 \end{lem}
@@
 	If $\lambda \in (0,1]$, then we have
-\begin{equation}
+\begin{align}
 	\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
@@
 	\quad t\in (0,\infty).
-\end{equation}
+\end{align}
 	This implies that
-\begin{equation}
+\begin{align}
 	\limsup_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}	
 	\leq \lambda ^{\gamma_0}.
-\end{equation}
+\end{align}
 	Also, for any $\epsilon \in (0,\infty)$, we have
-\begin{equation}\begin{split}
+\begin{align}
 	&\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
@@
 	\lambda ^{\gamma_0 + \epsilon},
-\end{split}\end{equation}
+\end{align}
 	where the last convergence is due to the monotone convergence theorem.
 	Therefore
-\begin{equation}
+\begin{align}
 	\liminf_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
 	\geq \lambda ^{\gamma_0}.
-\end{equation}
+\end{align}
 	Summarizing the above,  we get
-\begin{equation}
+\begin{align}
 	\lim_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
@@
 	\quad \lambda \in (0,1].
-\end{equation}
+\end{align}
 	If $\lambda \in (1,\infty)$, taking $f(x, t):= t^{\gamma(x)}$, from what we have proved, we also have that
-\begin{equation}
+\begin{align}
 	\lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)}
@@
 	= \lambda ^{\gamma_0}.
-\end{equation}
+\end{align}
 	This proved the first part of the lemma.
 
-	If further we have $m\{x:\gamma(x) = \gamma_0\}>0$, then by the monotone convergence theorem  it is easy to see that
+	If further 
+	we have $m(x:\gamma(x) = \gamma_0)>0$,
+	then by the monotone convergence theorem  it is easy to see that
 \begin{equation}
 	\frac{\int_E t^{\gamma(x)} m(dx)}{t^{\gamma_0}}
-	\xrightarrow[(0,\infty)\ni t\to 0]{} m\{x:\gamma(x) =
-	\gamma_0\}\in (0,\infty).
+	\xrightarrow[(0,\infty)\ni t\to 0]{} m(x:\gamma(x) = \gamma_0)\in (0,\infty).
 	\qedhere
@@
 	It is known, see \cite[Theorem 2.23]{Li2011Measure-valued} for example, that \eqref{eq:FKPP_in_definition} can be written as
-\begin{equation}\label{eq:mean-fkpp}
+\begin{align}\label{eq:mean-fkpp}
 	V_t f(x) + \int_0^t P^\beta_{t-r} \psi_0(x,V_r f) dr
@@
 	\quad f \in \mathscr B^+_b(E), t \geq 0,x \in E,
-\end{equation}
+\end{align}
 	where
-\begin{equation}
+\begin{align}
 	\psi_0(x,z)
@@
 	\quad x \in E,z \geq 0.
-\end{equation}
+\end{align}
     Suppose that Assumptions \ref{asp: 1}--\ref{asp: 2} hold.
     Integrating both sides of \eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we get that
-\begin{equation}\label{eq:langleVtfphiranglem_equation}
+\begin{align}\label{eq:langleVtfphiranglem_equation}
 	\langle V_tf,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,V_r f) , \phi^*\rangle_mdr
@@
 	\quad t\geq s\geq 0, f\in \mathscr B^+_b(E).
-\end{equation}
+\end{align}
 
@@
 	From  Campbell's formula, see  the proof of \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
-\begin{equation} \label{eq: equation for N measure}
+\begin{align} \label{eq: equation for N measure}
 	- \log \mathbf P_\mu [e^{-X_t(f)}]
@@
 	\quad \mu \in \mathcal M_E^1, t>0, f\in \mathscr B_b^+(E).
-\end{equation}
+\end{align}
 	For each $x\in E$ and $t\geq 0$, taking $\mu = \delta_x$ and $f = \lambda \mathbf 1_E$ with $\lambda > 0$ in the above equation, and letting $\lambda \to \infty$, we get
-\begin{equation} \label{eq: definition of v_t(x)}
+\begin{align} \label{eq: definition of v_t(x)}
 	v_t(x)
@@
 	= \mathbb N_x(\|W_t\|\neq 0).
-\end{equation}
+\end{align}
 	For each $\mu \in \mathcal M_E^1$ and $t > 0$, by \eqref{eq: equation for N measure}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem, we have
-\begin{equation} \label{eq: equation for mu v-t} \begin{split}
+\begin{align}
     \mathbb N_\mu(\|W_t\|\neq 0)
@@
 	= \lim_{\lambda \to \infty} (- \log \mathbf P_\mu [e^{-\lambda X_t(\mathbf 1_E)}])
-	\\&= \lim_{\lambda \to \infty} \langle \mu, V_t(\lambda \mathbf 1_E)\rangle
+	\\\label{eq: equation for mu v-t} 
+	&= \lim_{\lambda \to \infty} \langle \mu, V_t(\lambda \mathbf 1_E)\rangle
 	= \mu(v_t).
-\end{split} \end{equation}
+\end{align}
 	It is know that for any $f\in\mathscr B_b^+(E)$,
-\begin{equation}\label{eq: mean of kuz measure}
+\begin{align}\label{eq: mean of kuz measure}
     \mathbb N_{\mu}[W_t(f)]
     =\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
-\end{equation}
+	\quad t \geq 0,
+\end{align}
     see \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
@@
 	Let $(\Omega, \mathscr F)$ be a measurable space with a $\sigma$-finite measure $\mu$.
-	For any $F\in \mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and $\mu [F] \in (0,\infty)$.
+	For any $F\in \mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and 
+	$\mu(F) \in (0,\infty)$.
 	In this case, we define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ such that
-\begin{equation}	
+\begin{align}	
 	d\mu^F
-	= \frac{F}{\mu[F]}d \mu.
-\end{equation}
+	= \frac{F}{\mu(F)}d \mu.
+\end{align}
 
@@
 \begin{thm}[Size-biased decomposition,  \cite{RenSongSun2017Spine}]\label{thm: size-biased decomposition}
-\begin{equation}
+\begin{align}
 	\{(X_t)_{t\geq 0}; \mathbf P_\mu^{X_T(g)}\}
 	\overset{f.d.d.}{=} \{(X_t+W_t)_{t\geq 0}; \mathbf P_\mu  \otimes \mathbb N^{W_T(g)}_\mu\}.
-\end{equation}
+\end{align}
 \end{thm}
-	The second step of the theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
+	The second step of the spine decomposition theorem
+	says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
 	We say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
@@
 \item
-	The \emph{spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) \exp\{-\int_0^T \beta(\xi_s)ds\}$-transform of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
+	The \emph{spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, 
+	where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) \exp\{\int_0^T \beta(\xi_s)ds\}$-transform
+	of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
 \item
 	Given $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$, the \emph{immigration measure} $\{\mathbf n_T; \dot{\mathbf P}^{(g,T)}_\mu[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
-\begin{equation}
+\begin{align}
 	\mathbf m^\xi_T(ds,dw)
 	:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\end{equation}
+\end{align}
 \item
 	$\{(Y_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is an $\mathcal M^1_E$-valued process defined by
-\begin{equation}
+\begin{align}
 	Y_t
@@
 	\quad 0 \leq t\leq T.
-\end{equation}
+\end{align}
 \end{itemize}
@@
 	Then we have
-\begin{equation}
+\begin{align}
 	\{(Y_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}
 	\overset{f.d.d.}{=} \{(W_t)_{0\leq t\leq T}; \mathbb N_\mu^{W_T(g)}\}.
-\end{equation}
+\end{align}
 \end{thm}
@@
     We note that
-\begin{equation}\begin{split}
+\begin{align}
 	\Pi_{\mu}^{(T,g)} [ f(\xi_0) ]
-	&= \frac{1}{\mu(P^\beta_Tg)}\Pi_{\mu}\Big[g(\xi_T) \exp\Big\{-\int_0^T \beta(\xi_s)ds \Big\} f(\xi_0) \Big]
+	&= \frac{1}{\mu(P^\beta_Tg)}\Pi_{\mu}\Big[g(\xi_T) 
+	\exp\Big\{\int_0^T \beta(\xi_s)ds \Big\} f(\xi_0) \Big]
 	\\&= \frac{1}{\mu(P^\beta_T g)}
 	\int_E (P^\beta_T g)(x) \cdot f(x)\mu(dx),
-\end{split}\end{equation}
+\end{align}
     which says that
-\begin{equation}\label{eq: initial distribution of spine}
+\begin{align}\label{eq: initial distribution of spine}
 	\Pi_{\mu}^{(T,g)} (\xi_0 \in dx)
@@
 	\quad x\in E.
-\end{equation}
+\end{align}
 
@@
 	For each $\mu \in \mathcal M_E^\phi \cap \mathcal M_E^1$, we have
-\begin{equation}
+\begin{align}
 	\{(X_t)_{t\geq 0}; \mathbf P_\mu^{(\phi)}\}
 	\overset{f.d.d.}{=} \{(X_t + W_t)_{t\geq 0}; \mathbf P_\mu \otimes \mathbb N^{(\phi)}_\mu\}.
-\end{equation}
+\end{align}
 	Here, the probability $\mathbf P_\mu^{(\phi)}$ is Doob's $h$-transform of $\mathbf P_\mu$ whose restriction on the natural filtration $(\mathscr F_t^X)$ of the process $(X_t)_{t\geq 0}$ is
-\begin{equation}
+\begin{align}
 	d ( \mathbf P_\mu^{(\phi)}|_{\mathscr F_t^X})
@@
 	\quad t\geq 0;
-\end{equation}
+\end{align}
 	and $\mathbb N_\mu^{(\phi)}$ is a probability measure on $\mathbb W$ whose restriction on the natural filtration $(\mathscr F_t^W)$ of the process $(W_t)_{t\geq 0}$ is
-\begin{equation}
+\begin{align}
 	d(\mathbb N_\mu^{(\phi)} |_{\mathscr F^W_t}  )
@@
 	\quad t\geq 0.
-\end{equation}
+\end{align}
 \end{cro}
@@
 	The \emph{spine process} $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is a copy of $\{(\xi_t)_{t\geq 0}; \Pi^{(\phi)}_{\mu}\}$ where the probability $\Pi_{\mu}^{(\phi)}$ is Doob's $h$-transform of $\Pi_\mu$ whose restriction on the natural filtration $(\mathscr F_t^\xi)$ of the process $(\xi_t)_{t\geq 0}$ is
-\begin{equation}
+\begin{align}
 	d(\Pi_{\mu}^{(\phi)} |_{\mathscr F_t^\xi})
-	= \frac{\phi(\xi_t)e^{-\int_0^t \beta(\xi_s)ds}}{\mu(\phi)} d(\Pi_{\mu} |_{\mathscr F_t^\xi}),
+	= \frac{\phi(\xi_t)e^{\int_0^t \beta(\xi_s)ds}}{\mu(\phi)} d(\Pi_{\mu} |_{\mathscr F_t^\xi}),
 	\quad t\geq 0;
-\end{equation}
+\end{align}
 \item
@@
     intensity
-\begin{equation}\label{eq:meanMeasImmigr}
+\begin{align}\label{eq:meanMeasImmigr}
 	\mathbf m^\xi(ds,dw)
 	:= 2 \alpha(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
-\end{equation}
+\end{align}
 \item
 	$\{(Y_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is an $\mathcal M^1_E$-valued process defined by
-\begin{equation}\label{eq:defSpinImmigr}
+\begin{align}\label{eq:defSpinImmigr}
 	Y_t
@@
 	\quad t\geq 0.
-\end{equation}
+\end{align}
 \end{itemize}
@@
 	Then we have
-\begin{equation}
+\begin{align}
 	\{(Y_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}
 	\overset{f.d.d.}{=} \{(W_t)_{t\geq 0}; \mathbb N_\mu^{(\phi)}\}.
-\end{equation}
+\end{align}
 \end{cro}
@@
 	According to \cite{KimSong2008Intrinsic}, $\{\xi; \Pi^{(\phi)}_x\}$ is a time homogeneous Hunt process and its transition density with respect to the measure $m$ is
-\begin{equation}
+\begin{align}
 	q_t(x,y) := \frac{\phi(y)}{\phi(x)} p^\beta_t(x,y),
 	\quad x,y\in E, t>0.
-\end{equation}
+\end{align}
 	Let $c_0>0$ and $c_1>0$ be the constants  in \eqref{eq:q(t,x,y)}, then we have
-\begin{equation}\label{eq: asymptotic for q_t(x,y)}
+\begin{align}\label{eq: asymptotic for q_t(x,y)}
 	\sup_{x\in E} \Big| \frac{q_t(x,y)}{\phi(y)\phi^*(y)} - 1\Big|
@@
 	\quad t > 1.
-\end{equation}
+\end{align}
 	This implies that the process $\{\xi; \Pi^{(\phi)}_x\}$ is ergodic.
@@
 	then
-\begin{equation}
+\begin{align}
 	\int_0^1 F(\xi_{(1-u)t},u,t) du
@@
 	\quad x\in E.
-\end{equation}
+\end{align}
 \end{lem}
@@
 	Then, for each $x\in E$ and $p \geq 1$,
-\begin{equation}
+\begin{align}
 	\limsup_{ t \to \infty}  \Big\| \int_0^1 F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
-	\leq \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle du,
+	\leq \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle_m du,
 	\quad x\in E.
-\end{equation}
+\end{align}
 \end{lem}
@@
 	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$ such that
-\begin{equation}
+\begin{align}
 	F(x,u)
@@
 	\quad x\in E, u\in [0,1].
-\end{equation}
+\end{align}
 	From Lemma \ref{lem: ergodicity of the underlying process}, we know that
-\begin{equation}
+\begin{align}
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
 	\xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})}
-	\int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
+	\int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle_m du,
 	\quad x\in E,
-\end{equation}
+\end{align}
     which implies convergence in probability.
 	The bounded convergence theorem then gives that, for each $p \geq 1$,
-\begin{equation}
+\begin{align}
 	\int_0^1 \bar F(\xi_{(1-u)t},u,t) du
 	\xrightarrow[t\to \infty]{L^p(\Pi_x^{(\phi)})}
-	\int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle du,
+	\int_0^1 \langle F(\cdot , u), \phi\phi^*\rangle_m du,
 	\quad x\in E.
-\end{equation}
+\end{align}
 	Finally,
     noting that $0\leq F \leq \bar F$, we get
-\begin{equation}\begin{split}
-	& \limsup_{ t \to \infty}  \Big\| \int_0^1 F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
-	\leq 	\limsup_{ t \to \infty}  \Big\| \int_0^1 \bar F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
-	\\& \quad = \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle du,
+\begin{align}
+	\limsup_{ t \to \infty}  \Big\| \int_0^1 F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
+	&\leq \limsup_{ t \to \infty}  \Big\| \int_0^1 \bar F(\xi_{(1-u) t },u,t) du  \Big\|_{\Pi_x^{(\phi)};L^p}
+	\\& = \int_0^1 \langle F(\cdot, u), \phi \phi^*\rangle_m du,
 	\quad x\in E. \qedhere
-\end{split}\end{equation}
+\end{align}
 \end{proof}
@@
 	If we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
-\begin{equation}
+\begin{align}
 	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \widetilde \psi (\xi_s,V_{t-s} f) ds \Big]
 	=\Pi_x \big[ f(\xi_t)\mathbf 1_{t<\zeta} \big].
-\end{equation}
+\end{align}
 	So, we can consider $\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
 	Define
-\begin{equation}
+\begin{align}
 	\widehat\psi(z)
@@
 	\quad z\geq 0.
-\end{equation}
+\end{align}
 	Using the fact that $\gamma_0 > 1$ and $\kappa_0 > 0$, it is easy to verify that
-\begin{equation}
+\begin{align}
 	\inf_{x\in E}\widetilde \psi(x,z)
@@
 	\quad \hat \psi(+\infty) = +\infty.
-\end{equation}
+\end{align}
 	Therefore $\widetilde \psi$ satisfies the condition of \cite[Lemma 2.3]{RenSongZhang2015Limit}.
@@
 	From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent, that is,
-\begin{equation}
+\begin{align}
     \mathbf P_{\delta_x}(\|X_t\| = 0)
@@
     \quad t>0, x \in E.
-\end{equation}
+\end{align}
 	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have
-\begin{equation}
+\begin{align}
     \mathbf P_{\delta_x}(\|X_t\|= 0)<1,
     \quad t>0, x \in E.
-\end{equation}
+\end{align}
 	From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
@@
 	we see that $(v_t)_{t > 0}$ satisfies the equation
-\begin{equation}
+\begin{align}
 	v_{s+t}(x) + \int_0^t P^\beta_{t-r} \psi_0(x,v_{s+r}) dr
@@
 	\quad s>0, t \geq 0,x \in E.
-\end{equation}
+\end{align}
 
@@
 	$(v_t)_{t> 0}$ also satisfies the equation
-\begin{equation} \label{eq: equation of <vt,phi>}
+\begin{align} \label{eq: equation of <vt,phi>}
 	\langle v_t,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,v_t) , \phi^*\rangle_m dr
@@
 	\quad s, t > 0.
-\end{equation}
+\end{align}
 	One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example,
-\begin{equation} \label{eq: uniform converges to 0}
+\begin{align} \label{eq: uniform converges to 0}
     \|\phi^{-1}v_t\|_{\infty} \xrightarrow[t\to \infty]{} 0.
-\end{equation}
+\end{align}
 	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only need to consider the speed of this convergence.
@@
 	Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
-\begin{equation}
+\begin{align}
 	\langle v_t,\phi^*\rangle_m
 	\stackrel[t\to \infty]{}{\sim} \big(C_X(\gamma_0-1) t \big)^{-\frac{1}{\gamma_0 - 1}},
-\end{equation}
+\end{align}
 	where $C_X:= \langle \mathbf 1_{\gamma= \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m $.
@@
 	we have that for each $t>0$,
-\begin{equation}\begin{split}\label{eq:vt-and-Y}
-	&\langle \mu,\phi \rangle \dot {\mathbf P}^{(\phi)}_\mu [Y_t(\phi)^{-1}]
+\begin{align}\label{eq:vt-and-Y}
+	\langle \mu,\phi \rangle \dot {\mathbf P}^{(\phi)}_\mu [Y_t(\phi)^{-1}]
 	= \mathbb N_\mu[W_t(\phi)] \mathbb N^{W_t(\phi)}_\mu [W_t(\phi)^{-1}]
@@
 	= \mu(v_t).
-\end{split}\end{equation}
+\end{align}
 	Taking $\mu = \delta_x$ in \eqref{eq:vt-and-Y}, we get $(\phi^{-1}v_t)(x) =\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]$.
@@
 	Therefore, to complete the proof, we only need to show that
-\begin{equation}
+\begin{align}
 	\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
 	\stackrel[t\to \infty]{x\in E}{\sim}  \dot {\mathbf P}_\nu^{(\phi)} [Y_t(\phi)^{-1}].
-\end{equation}
+\end{align}
 
 	For any $t>0$ and any $G\in \mathscr B((0,t])$, define
-\begin{equation}
+\begin{align}
 	Y^G_t
 	:= \int_{G\times \mathbb W} w_{t-s} \mathbf n(ds,dw).
-\end{equation}
+\end{align}
 	Then for any $0 < t_0 < t$, we can decompose $Y_t$ into
-\begin{equation}
+\begin{align}
 	Y_t
 	= Y^{(0,t_0]}_t + Y^{(t_0,t]}_t.
-\end{equation}
+\end{align}
 	Using this decomposition, for each $0<t_0<t<\infty$ and $x\in E$, we have
-\begin{equation}\label{eq: starting point of phi-1v_t(x)}
+\begin{align}\label{eq: starting point of phi-1v_t(x)}
 	 \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
 	= \dot {\mathbf P}_\nu^{(\phi)} [Y^{(t_0,t]}_t(\phi)^{-1}] + \epsilon_x^1(t_0,t) +\epsilon_x^2(t_0,t),
-\end{equation}
+\end{align}
 	where
-\begin{equation}\begin{split}
+\begin{align}
 	\epsilon_x^1(t_0,t)
@@
 	&:= \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1} - Y^{(t_0,t]}_t(\phi)^{-1}].
-\end{split}\end{equation}
+\end{align}
 
 	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, we have that
-\begin{equation}\label{eq: some equations for PY-1}\begin{split}
-	\dot{\mathbf P}^{(\phi)} [Y_t^{(t_0,t]}(\phi)^{-1}|\mathscr F^\xi_{t_0}]
-	&= \dot{\mathbf P}_{\delta_{\xi_{t_0}}}^{(\phi)}  [Y_{t-t_0}(\phi)^{-1}]
+\begin{align}
+	\label{eq: some equations for PY-1-1}
+	&\dot{\mathbf P}^{(\phi)} [Y_t^{(t_0,t]}(\phi)^{-1}|\mathscr F^\xi_{t_0}]
+	= \dot{\mathbf P}_{\delta_{\xi_{t_0}}}^{(\phi)}  [Y_{t-t_0}(\phi)^{-1}]
 	= (\phi^{-1}v_{t-t_0})(\xi_{t_0});
-	\\ \dot{\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]
-	&= \Pi_{\nu}^{(\phi)}[(\phi^{-1}v_{t-t_0})(\xi_{t_0}) ]
+	\\ \label{eq: some equations for PY-1-2}
+	&\dot{\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]
+	= \Pi_{\nu}^{(\phi)}[(\phi^{-1}v_{t-t_0})(\xi_{t_0}) ]
 	= \langle v_{t-t_0},\phi^* \rangle_m;
-	\\ \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]
-	&= \Pi_x^{(\phi)}[(\phi^{-1}v_{t-t_0})(\xi_{t_0}) ]
+	\\ \label{eq: some equations for PY-1-3}
+	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]
+	= \Pi_x^{(\phi)}[(\phi^{-1}v_{t-t_0})(\xi_{t_0}) ]
 	=  \int_E  q_{t_0}(x,y)(\phi^{-1}v_{t-t_0})(y) m(dy).
-\end{split}\end{equation}
+\end{align}
 
@@
 	We claim that
-\begin{equation}\label{eq: bound for epsilon1}
+\begin{align}\label{eq: bound for epsilon1}
 	|\epsilon_x^1(t_0,t)|
@@
     \quad t_0 > 1.
-\end{equation}
+\end{align}
 	In fact,
-\begin{equation}\label{eq:epsilon-1}\begin{split}
+\begin{align}
 	|\epsilon_x^1(t_0,t)|
@@
 	& \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m .
-\end{split}\end{equation}
+\end{align}
 
 	We now claim that, if $t_0 > 1$ and $t-t_0$ is large enough, then
-\begin{equation}\label{eq:upperbound_of_epsilon-2}
+\begin{align}\label{eq:upperbound_of_epsilon-2}
 	|\epsilon_x^2(t_0,t)|
 	\leq t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
-\end{equation}
+\end{align}
 	In fact, using the Markov property of the spine process and the property of Poisson random measures, we have
-\begin{equation}\label{eq:epsilon-2}\begin{split}
+\begin{align}\label{eq:epsilon-2}
 	|\epsilon_x^2(t_0,t)|
 	&= \big| \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1} - Y^{(t_0,t]}_t(\phi)^{-1}] \big|
-	= \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t^{(0,t_0]}(\phi)\cdot Y_t(\phi)^{-1}\cdot Y^{(t_0,t]}_t(\phi)^{-1}]
+	\\&= \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t^{(0,t_0]}(\phi)\cdot Y_t(\phi)^{-1}\cdot Y^{(t_0,t]}_t(\phi)^{-1}]
 	\\&\leq \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}(\phi)\neq 0}\cdot Y^{(t_0,t]}_t(\phi)^{-1}]
 	\\&= \dot{\mathbf P}_{\delta_x}^{(\phi)} \big[\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{Y_t^{(0,t_0]}(\phi)\neq 0}|\mathscr F^\xi_{t_0}] \cdot \dot{\mathbf P}_{\delta_x}^{(\phi)} [ Y^{(t_0,t]}_t(\phi)^{-1}|\mathscr F^\xi_{t_0}] \big].
-\end{split}\end{equation}
-	On one hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1}, we know that
-\begin{equation}\label{eq:epsilon-2-final}\begin{split}
+\end{align}
+	On one hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
+\begin{align}\label{eq:epsilon-2-final}
 	\dot{\mathbf P}_{\delta_x}^{(\phi)}[ Y^{(t_0,t]}_t(\phi)^{-1}]
 	\leq (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
-\end{split}\end{equation}
+\end{align}
 	On the other hand, since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
@@
 	using the fact that $v_t$ is non-increasing in $t$, we get
-\begin{equation}\begin{split}
+\begin{align}
 	\kappa(x)\gamma(x) v_{t-s}(x)^{\gamma(x)-1}
@@
 	\leq \|\kappa\gamma\phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
-\end{split}\end{equation}
+\end{align}
 	Therefore, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have,  for $t-t_0 \geq s_0$,
-\begin{equation}\begin{split}
+\begin{align}
 	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
@@
 	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
-	=  - \log \lim_{\lambda \to \infty}\dot{\mathbf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
 	\\&\quad = -\log \lim_{\lambda \to \infty} \exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
@@
 	\\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
-	= \int_0^{t_0} \big( \kappa \gamma (v_{t-s})^{\gamma - 1} \big) (\xi_s)ds
+	= \int_0^{t_0} \big( \kappa \gamma  v_{t-s}^{\gamma - 1} \big) (\xi_s)ds
 	\\&\quad \leq  t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
-\end{split}\end{equation}
+\end{align}
 Combining this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
 
-	Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1}, \eqref{eq: bound for epsilon1} and \eqref{eq:epsilon-2-final}, we have
-\begin{equation}\label{vts-inequality}\begin{split}
+	Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq: some equations for PY-1-3}, \eqref{eq: bound for epsilon1} and \eqref{eq:epsilon-2-final}, we have
+\begin{align} \label{vts-inequality}
 	&\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0},\phi^* \rangle_m}-1 \Big|
@@
 	\cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
-\end{split}\end{equation}
+\end{align}
 	According to \eqref{eq: uniform converges to 0}, there exists a map $t\mapsto t_0(t)$ such that,
-\begin{equation}
+\begin{align}
 	t_0(t)
@@
 	\xrightarrow[t\to\infty]{} 0.
-\end{equation}
+\end{align}
 	Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
-\begin{equation}\label{eq:k1}
+\begin{align}\label{eq:k1}
 	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
 	\xrightarrow[t\to\infty]{} 0.
-\end{equation}
+\end{align}
 	Notice that
-\begin{equation}\label{eq:k2}\begin{split}
+\begin{align}\label{eq:k2}
 	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
@@
 	\xrightarrow[t\to\infty]{} 0.
-\end{split}\end{equation}
+\end{align}
 	Now, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
-\begin{equation}
+\begin{align}
 	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
 	\xrightarrow[t\to\infty]{} 0,
-\end{equation}
+\end{align}
 	as desired.
@@
 	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse on $(0,\infty)$ which is denoted by
-\begin{equation}
+\begin{align}
 	R: (0,\infty) \to (0,\infty).
-\end{equation}
+\end{align}
 
 	Now, if we denote by
-\begin{equation}
+\begin{align}
 	\epsilon_{t}(x)
@@
 	\quad t>0, x\in E.
-\end{equation}
+\end{align}
 	Then, we have
-\begin{equation}\label{eq: change variable using inverse}
+\begin{align}\label{eq: change variable using inverse}
 	v_t(x)
@@
 	\quad t>0, x\in E.
-\end{equation}
+\end{align}
 	Further, by Proposition \ref{prop: convergence in a same speed} and
 	the fact that $R(u)\xrightarrow[u\to 0]{} \infty$, we have
-\begin{equation}\label{eq: epsilon R converges to 0}
+\begin{align}\label{eq: epsilon R converges to 0}
 	\sup_{x\in E}|\epsilon_{R(u)}(x)|
 	\xrightarrow[u\to 0]{} 0.
-\end{equation}
+\end{align}
 
 	Now, by \eqref{eq: equation of <vt,phi>}, we have
-\begin{equation}
+\begin{align}
 	\frac{d \langle v_r, \phi^* \rangle_m}{dr}
@@
 	\quad a.e..
-\end{equation}
+\end{align}
 	Therefore,
-\begin{equation}\begin{split}
+\begin{align}
 	s-t
@@
 	\\&= \int_{\langle v_s,\phi^*\rangle}^{\langle v_t, \phi^* \rangle} \big\langle \psi_0 \big( \cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du.
-\end{split}\end{equation}
+\end{align}
 	Letting $t\to 0$, we get
-\begin{equation}
+\begin{align}
 	s
@@
 	\quad s\in (0,\infty).
-\end{equation}
+\end{align}
 	Since $R$ is the inverse of $t\mapsto \langle v_t,\phi^*\rangle$, the above implies that
-\begin{equation}\label{eq: integral equation for R}
+\begin{align}\label{eq: integral equation for R}
 	R(r)
@@
 	\quad r\in (0,\infty).
-\end{equation}
+\end{align}
 
@@
 	Therefore, from Lemma \ref{lem: asymptotic equivalent of integration}, we have that
-\begin{equation}\label{eq: regularly part in the integration}\begin{split}
+\begin{align}\label{eq: regularly part in the integration}
 	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
-	= \big\langle \kappa (x)\big( 1 + \epsilon_{R(u)}(x)\big )^{\gamma(x)} u^{\gamma(x)} \phi(x)^{\gamma(x)} , \phi^*(x) \big\rangle_{m(dx)}
+	\\&\quad = \big\langle \kappa (x)\big( 1 + \epsilon_{R(u)}(x)\big )^{\gamma(x)} u^{\gamma(x)} \phi(x)^{\gamma(x)} , \phi^*(x) \big\rangle_{m(dx)}
 	\\ &\quad \stackrel[u\to 0]{}{\sim} \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_{m(dx)}.
-\end{split}\end{equation}
+\end{align}
 	According to Lemma \ref{lem:regularly_variation_and_integration},
@@
 	Further, if $m\{x: \gamma(x) = \gamma_0\}> 0$, then according to Lemma \ref{lem:regularly_variation_and_integration} and \eqref{eq: regularly part in the integration}, we know that
-\begin{equation}\begin{split}
+\begin{align}
 	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
@@
 	=: C_X u^{\gamma_0}.
-\end{split}\end{equation}
+\end{align}
 	Therefore, we have $\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} = u^{-\gamma_0} l(u)$, where $l(u)$ converges to the constant $C_X^{-1}$ when $u \to 0$.
 	Now according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R} we have that
-\begin{equation}\begin{split}
+\begin{align}
 	R(r)
@@
 	\\&\stackrel[r\to 0]{}{\sim} C_X^{-1} (\gamma_0-1)^{-1} r^{-(\gamma_0 - 1)}.
-\end{split}\end{equation}
-	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from Corollary \ref{cro: regularly varing and inverse with alpha < 0} and the above,
+\end{align}
+	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, 
+	from \cite[Proposition 1.5.15.]{BinghamGoldieTeugels1989Regular} and the above,
 	we have
@@
 	\langle v_r,\phi^*\rangle_m
-	\stackrel[r\to \infty]{}{\sim} \big(C_X (\gamma_0-1) r \big)^{-\frac{1}{\gamma_0 - 1}}. \qedhere
+	\stackrel[r\to \infty]{}{\sim} \big(C_X (\gamma_0-1) r \big)^{-\frac{1}{\gamma_0 - 1}}. 
+	\qedhere
 \end{equation}
@@
 	According to \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0},
-\begin{equation}
+\begin{align}
 	- \log \mathbf P_\mu(\|X_t\| = 0)
@@
 	\xrightarrow[t\to \infty]{} 0.
-\end{equation}
+\end{align}
 	Therefore, $\mathbf P_\mu(\|X_t\| \neq 0) \xrightarrow[t\to \infty]{} 0$.
@@
 	Noticing that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, according to \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed}, we have
-\begin{equation}
+\begin{align}
 	\mathbf P_\mu(\|X_t\| \neq 0)
@@
 	\stackrel[t\to\infty]{}{\sim} \mu(\phi) \langle v_t, \phi^*\rangle_m.
-\end{equation}
+\end{align}
 	Therefore, according to Proposition \ref{prop: regularly varying of vt-phi-star}, we get the desired result.
@@
 	Our guess of $(\eta_t)$ is
-\begin{equation}\label{eq: definition of eta}
+\begin{align}\label{eq: definition of eta}
 	\eta_t
@@
 	\quad t\geq 0,
-\end{equation}
+\end{align}
 	because in this case
- \begin{equation}
+ \begin{align}
  	\mathbf P_{\delta_x}[\eta_t X_t(f)|\|X_t\|\neq 0]
@@
 	\stackrel[t\to \infty]{}{\sim}  \langle f,\phi^* \rangle_m.
- \end{equation}
+ \end{align}
  	Here we have used Theorem \ref{thm: main theorem}(2) and the fact that (see \eqref{eq:q(t,x,y)})
- \begin{equation}
+ \begin{align}
  	P^\beta_t f(x)
@@
  	\xrightarrow[t\to \infty]{}  \phi(x) \langle f,\phi^*\rangle_m.
- \end{equation}
+ \end{align}
 
@@
 	is equivalent to the following convergence:
-\begin{equation}
+\begin{align}
 	\mathbf P_\mu[1- e^{-\theta \eta_t X_t(f)} | \|X_t\|\neq 0]
@@
 	\xrightarrow[t\to \infty]{} \int_{[0,\infty)}(1-e^{-\theta u}) F_f(du).
-\end{equation}
+\end{align}
 	According to Theorem \ref{thm: main theorem}(2) and $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
-\begin{equation}\label{eq: equivalent result}
+\begin{align}\label{eq: equivalent result}
 	\frac{\mu\big( V_t(\theta \eta_t f) \big)}{ \eta_t}
 	\quad \xrightarrow[t\to \infty]{} \mu(\phi) \int_{[0,\infty)}(1-e^{-\theta u})F_{f}(du).
-\end{equation}
+\end{align}
 	Therefore, to establish the weak convergence of $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0)\big\}$, one only needs to verify \eqref{eq: equivalent result}.
@@
 	For any $f\in \mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we have
-\begin{equation}\label{eq: equation for Vt(theta f) for theta}
+\begin{align}\label{eq: equation for Vt(theta f) for theta}
 	V_T ( \theta f) ( x)
 	= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr.
-\end{equation}
+\end{align}
 \end{prop}
@@
 	It follows from Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
-\begin{equation}
+\begin{align}
 	\frac{ \mathbf P_{\delta_x}[X_T(f)e^{-\theta X_T(f)}] } {  \mathbf P_{\delta_x} [X_T(f)] }
@@
 	= \mathbf P_{\delta_x} [e^{-\theta X_T(f)}] \dot {\mathbf P}_x^{(T,f)}[e^{-\theta Y_T(f)}],
-\end{equation}
+\end{align}
 	where $\{(\xi)_{0\le t\le T}, \mathbf n_T, (Y)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$ is a spine representation of $\mathbb N^{W_T(f)}_x$ with $\mathbf m^\xi_T$ being the intensity of the immigration measure $\mathbf n_T$ conditioned on $\{(\xi)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$.
 	From this, we have
-\begin{equation} \label{eq: dynamic of theta on v_t theta reason 1}
-	\frac{\partial}{\partial_\theta}
+\begin{align} \label{eq: dynamic of theta on v_t theta reason 1}
+	\frac{\partial}{\partial \theta}
 	(-\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}])
@@
 	= P^\beta_T f(x) \dot {\mathbf P}_x^{(T,f)}[e^{-\theta Y_T(f)}].
-\end{equation}
+\end{align}
 	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
-\begin{equation}\label{eq: dynamic of theta on v_t theta reason 2}\begin{split}
+\begin{align}\label{eq: dynamic of theta on v_t theta reason 2}
 	&-\log \dot {\mathbf P}^{(T,f)}_{x}[e^{-\theta \mathbf n_T(F)}|\mathbf m_T^\xi]
@@
 	\\&\quad = \int_0^T \big(\kappa\gamma V_{T-s}(\theta f)^{\gamma-1}\big)(\xi_s) ds.
-\end{split}\end{equation}
+\end{align}
 	Note that, since $\mathbf n_T(F)= Y_T(f)$, we can derive from \eqref{eq: dynamic of theta on v_t theta reason 1} and \eqref{eq: dynamic of theta on v_t theta reason 2} that
-\begin{equation}\begin{split}
+\begin{align}
 	V_T(\theta f)(x)
@@
 	\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr,
-\end{split}\end{equation}
+\end{align}
 	as required.
@@
 
-\begin{equation}\label{eq: equation for normalized V_T}\begin{split}
+\begin{align}\label{eq: equation for normalized V_T}
 	&\frac{V_T(\theta \eta_T f)(x)}{\eta_T}
@@
 	\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} \exp\Big\{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du\Big\}\Big] dr.
-\end{split}\end{equation}
-
-%\subsection{Zolotarev's distribution}
+\end{align}
+
 \subsection{Distribution with Laplace transform (\ref{e:zloltarev})}
@@
 
-%Recall that a non-negative random variable $\mathbf z^{(\gamma_0 - 1)}$ is said to have Zolotarev's distribution with parameter $\gamma_0 - 1 \in (0,1)$ if
-%\begin{equation}
-%	E[1-e^{-\theta\mathbf z^{(\gamma_0 - 1)}}]
-%	=\Big( \frac{1}{1+\theta^{-(\gamma_0 - 1)}} \Big)^{\frac{1}{\gamma_0 - 1}}.
-%\end{equation}
-%	It turns out that we can characterize this distribution by the following result.
 The distribution with Laplace transform \eqref{e:zloltarev} can be characterized by the
@@
 	The non-linear delay equation
-\begin{equation} \label{eq: equation for the distribution}
+\begin{align} \label{eq: equation for the distribution}
 	G( \theta)
@@
 	\quad \theta \geq 0,
-\end{equation}
+\end{align}
 	has a unique solution:
-\begin{equation}\label{eq: solution for the equation}
+\begin{align}\label{eq: solution for the equation}
 	G(\theta)
@@
 	\quad \theta \geq 0.
-\end{equation}
+\end{align}
 \end{lem}
@@
 	If $f$ is a measurable function which is $L^p$ integrable on the measure space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
-\begin{equation}
+\begin{align}
 	\|f\|_{\mu;p}
 	:= \Big(\int_{S} |f|^p d\mu \Big)^{\frac{1}{p}}.
-\end{equation}
+\end{align}
 	Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to the measure $\mu$.	
@@
 	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
-\begin{equation}
+\begin{align}
 	F(\theta)
 	\leq C \int_0^\theta \|  F(ru^{ \frac{1}{\gamma_0- 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0.
-\end{equation}
+\end{align}
 	Then $F \equiv 0$.
@@
 	Assume that
-\begin{equation}\label{eq: definition of rho}
+\begin{align}\label{eq: definition of rho}
 	\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
-\end{equation}
+\end{align}
 	Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
 	We first claim that
-\begin{equation}
+\begin{align}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-\end{equation}
+\end{align}
 	In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
-\begin{equation}\begin{split}
+\begin{align}
 	F_\alpha (\theta)
@@
 	\leq C(\rho C + 1) \theta.
-\end{split}\end{equation}
+\end{align}
 	We then claim that, if
-\begin{equation}\label{eq: FATLC}
+\begin{align}\label{eq: FATLC}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
-\end{equation}
+\end{align}
 	for some $k \in \mathbb N$, then
-\begin{equation}
+\begin{align}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-	\end{equation}
+	\end{align}
 	In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
-\begin{equation}\begin{split}
+\begin{align}
 	F_\alpha (\theta)
@@
 	\big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-	\\& =  C\int_0^\theta \|F_{\alpha u^{\frac{1}{\gamma_0 - 1}}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+	\\& =  C\int_0^\theta \|F_{\alpha u^{1/(\gamma_0 - 1)}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
   \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} }
@@
 \\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
-\end{split}\end{equation}
+\end{align}
 	Therefore, by induction, we have
-\begin{equation}
+\begin{align}
 	F_\alpha (\theta)
@@
 	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
-\end{equation}
+\end{align}
 	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
@@
 	In fact, if $G(\theta) = (\frac{1}{1+ \theta^{-(\gamma_0 - 1)}})^{\frac{1}{\gamma_0 - 1}}$, then
-\begin{equation}\begin{split}
+\begin{align}
 	 & \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}\Big\} dr
@@
 	= G(\theta).
-\end{split}\end{equation}
+\end{align}
 	The last equality is due to $G(0) = 0$ and
-\begin{equation}\begin{split}
+\begin{align}
 	\frac{d}{d\theta}G(\theta)
@@
 	\\& =  \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{\gamma_0}{\gamma_0 - 1} } \theta^{-\gamma_0}.
-\end{split}\end{equation}
+\end{align}
 
@@
 	This can be done by showing that $F(\theta) = 0$ where
-\begin{equation}
+\begin{align}
 	F(\theta)
@@
 	\quad \theta \geq 0.
-\end{equation}
+\end{align}
 	We claim that the non-negative function $F$ satisfies
 	the following inequality:
-\begin{equation}\label{eq: inequality of F(theta)}
+\begin{align}\label{eq: inequality of F(theta)}
 	F(\theta)
 	\leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\gamma_0 - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0,
-\end{equation}
+\end{align}
 	for some constant $C_0 > 0$.
 	In fact, by the $L^p$ Minkowski inequality with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
-\begin{equation}\begin{split}
+\begin{align}
 	&|G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|
@@
 	\\ & \quad \leq \gamma_0 \Bigg( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} - G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}| \frac{du}{u} \Big)^{\frac{1}{\gamma_0 - 1}} dr \Bigg)^{\gamma_0 - 1}.
-\end{split}\end{equation}
+\end{align}
 	In other words, there is a constant $C_0:= \gamma_0^{\frac{1}{\gamma_0 - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
@@
 	Assumptions \ref{asp: 1}--\ref{asp: 4}.
-	Suppose that $m\{ x:\gamma(x)=\gamma_0 \}>0$.
+	Suppose that $m( x:\gamma(x)=\gamma_0 )>0$.
 	Let $f \in \mathscr B^+(E)$ be  such that $ \langle f, \phi^* \rangle_m > 0$  and $c_f :=\| \phi^{-1}f \|_\infty < \infty$.
@@
 	We claim that, in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
-\begin{equation}\label{eq: we only need to proof this}
+\begin{align}\label{eq: we only need to proof this}
 	g(t,\theta,x)
@@
 	\quad x\in E, \theta \geq 0.
-\end{equation}
+\end{align}
 	In fact, by \eqref{eq: equation for normalized V_T}, we have $\|V_t(\theta \eta_t f)/ \eta_t \|_\infty \leq \theta \|\phi\|_\infty \|\phi^{-1}f\|_\infty.$
-	Therefore, if \eqref{eq: we only need to proof this} is true, then by the bounded convergence theorem,
-\begin{equation}
+	Therefore, if \eqref{eq: we only need to proof this} is true, then by the bounded convergence theorem, for each $\mu \in \mathcal M^1_E$,
+\begin{align}
 	\frac{\mu\big(V_t (\theta \eta_t f)\big)}{\eta_t }
 	\xrightarrow[t\to \infty]{} \mu(\phi)G(\theta),
-\end{equation}
+\end{align}
 	which, by the discussion in Subsection \ref{sec: conditional distribution}, is equivalent to Theorem \ref{thm: main theorem}(3).
@@
 	From Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we have that $G$ satisfies
-\begin{equation}\label{eq: equation for G}
+\begin{align}\label{eq: equation for G}
 	G(\theta)
@@
 	\quad \theta \geq 0,
-\end{equation}
+\end{align}
 	where
-\begin{equation}\label{eq: definition for J_G}
+\begin{align}\label{eq: definition for J_G}
 	J_G(r):=
@@
 	\quad r\geq 0 .
-\end{equation}
+\end{align}
 	According to \eqref{eq: equation for normalized V_T}, we know that $g$ satisfies
-\begin{equation}\label{eq: equation for g}
+\begin{align}\label{eq: equation for g}
 	g(t,\theta, x)= \int_0^{\theta} \Pi_x^{(\phi)} [ (\phi^{-1}f)(\xi_t) e^{-\frac{1}{\gamma_0 - 1} J_g(t,r,\xi) } ] dr,
 	\quad t\geq 0, \theta \geq 0, x\in E,
-\end{equation}
-	where, for each $t\geq 0, r\geq 0$,
-\begin{equation}\label{eq: definition for J_g}
+\end{align}
+	where, for each $t\geq 0$ and $r\geq 0$,
+\begin{align}\label{eq: definition for J_g}
 	J_g(t,r,\xi):=
-	(\gamma_0 - 1)t\int_0^1 \big(  \kappa\gamma (   \phi \eta_{ut}  )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) (  \xi_{(1-u)t}  ) du.
-\end{equation}
+	(\gamma_0 - 1)t\int_0^1 \big(  \kappa \gamma \cdot (   \phi \eta_{ut}  )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) (  \xi_{(1-u)t}  ) du.
+\end{align}
 	For each $t\geq 0$ and $r\geq 0$, define
-\begin{equation}\label{eq: definition of J'_G}
+\begin{align}\label{eq: definition of J'_G}
 	J'_G(t,r,\xi):=
-	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big) (\xi_{(1-u)t}) du
-\end{equation}
+	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big) (\xi_{(1-u)t}) du
+\end{align}
 	and
@@
 	J'_g(t,r,\xi):=
-	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \big) (\xi_{(1-u)t})  du.
+	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \big) (\xi_{(1-u)t})  du.
 \end{equation}
@@
 	From \eqref{eq: equation for G} we have
-\begin{equation}\label{eq: upper bound for G}
+\begin{align}\label{eq: upper bound for G}
 	G(r)
@@
 	\quad r \geq 0.
-\end{equation}	
+\end{align}	
 	From \eqref{eq: definition for J_G} and \eqref{eq: upper bound for G}, we have
-\begin{equation}\label{eq: upper bound for J_G}
+\begin{align}\label{eq: upper bound for J_G}
 	J_G(r)
@@
 	\quad r \geq 0.
-\end{equation}
+\end{align}
 	From \eqref{eq: equation for g}, we have
-\begin{equation}\label{eq: upper bound for g}
+\begin{align}\label{eq: upper bound for g}
 	g(t,r, x) \leq c_f r,
 	\quad t\geq 0, r \geq 0, x\in E.
-\end{equation}
+\end{align}
 	From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have
-\begin{equation}\begin{split}
+\begin{align}
 	J_g(t,r, \xi)
@@
 	\quad t\geq 1, r\geq 0.
-\end{split}\end{equation}
+\end{align}
 	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have
-\begin{equation}\begin{split}
+\begin{align}
 	J'_g(t,r,\xi)
-	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} (c_f ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
+	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} (c_f ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
 	\\&\leq \gamma_0(\gamma_0 - 1) c_f^{\gamma_0 - 1}r^{\gamma_0 - 1} \|  \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \|_\infty \int_0^1 t \big( C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
@@
 	\quad t\geq 0, r\geq 0.
-\end{split}\end{equation}
+\end{align}
 	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have
-\begin{equation}\label{eq: upper bound for J'_G} \begin{split}
+\begin{align}\label{eq: upper bound for J'_G}
 	J'_G(t,r,\xi)
-	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} (ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
+	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} (ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
 	\\&\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
@@
 	\quad t\geq 0, r\geq 0.
-\end{split}\end{equation}
+\end{align}
 
 	Step 2: We will show that, for each $t\geq 0, \theta \geq 0,$ and $x\in E$
-\begin{equation}\begin{split}
+\begin{align}
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
@@
 	+c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x),
-\end{split}\end{equation}
+\end{align}
 	where
-\begin{equation}
-\begin{split}
+\begin{align}
+\begin{aligned}
 	I_1(t,\theta,x)
@@
 	&:= \Big\| \|  J'_G(t,r,\xi) - J'_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
-\end{split}
-\end{equation}
+\end{aligned}
+\end{align}
 	and
-\begin{equation}
+\begin{align}
 	I_4(t,\theta,x)
 	:= \Big\| \| J'_g(t,r,\xi) - J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
-\end{equation}
+\end{align}
 	In fact, we can rewrite \eqref{eq: equation for G} and \eqref{eq: equation for g} as:
-\begin{equation}
+\begin{align}
 	G(\theta)^{\gamma_0 - 1} =
@@
 	\quad \theta \geq 0,
-\end{equation}	
+\end{align}	
 	and
-\begin{equation}
+\begin{align}
 	g(t,\theta,x)^{\gamma_0 - 1}
@@
 	\quad t\geq 0, \theta \geq 0, x\in E.
-\end{equation}	
-	Therefore, by Minkowski's inequality we have that
-\begin{equation}\begin{split}
+\end{align}	
+	Therefore, by Minkowski's inequality we have that, for each $t\geq 0, \theta \geq 0$ and $x\in E$,
+\begin{align}
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
-	\\&\quad \leq \Big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}.
+	\\&\quad \leq \Big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
 	\\&\quad \leq I_1(t,\theta,x) + \Big\| \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} -
@@
 	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1}\Big\| \|  J_G(r) -J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1} I_2(t,\theta,x) +c_f^{\gamma_0 - 1} I_3(t,\theta,x)+c_f^{\gamma_0 - 1} I_4(t,\theta,x),
-	\quad t\geq 0, \theta \geq 0, x\in E.
-\end{split}
-\end{equation}
-
+	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1} I_2(t,\theta,x) +c_f^{\gamma_0 - 1} I_3(t,\theta,x)+c_f^{\gamma_0 - 1} I_4(t,\theta,x).
+\end{align}	
 	Step 3: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
@@
 	by \eqref{eq:q(t,x,y)},
-\begin{equation}
+\begin{align}
 	\Pi_x^{(\phi)} [(\phi^{-1}f)(\xi_t)]
@@
 	\quad x\in E.
-\end{equation}
+\end{align}
 	Therefore,
-\begin{equation}\begin{split}
+\begin{align}
 	&e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
@@
 	\quad x\in E, r\geq 0.
-\end{split}\end{equation}
+\end{align}
 	We also have the following bound:
-\begin{equation}
+\begin{align}
 	\Big| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big|
 	\leq 1+ c_f^{\gamma_0 - 1}.
-\end{equation}
+\end{align}
 	Therefore, by the bounded convergence theorem, we have that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta, x) \xrightarrow[t\to \infty]{} 0$.
@@
 	Notice that, according to \eqref{eq: definition for J_G} and \eqref{eq: definition of J'_G}, for each $t\geq 0$ and $r\geq 0$,
-\begin{equation}\begin{split}
+\begin{align}
 	&J_G(r) - J'_G(t,r,\xi)
@@
 	\\&\quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}.
-\end{split}\end{equation}
+\end{align}
 	Also notice that,
 	according to \eqref{eq: upper bound for G}, for each $r \geq 0$, $u\in [0,1]$ and $x\in E$,
-\begin{equation}\begin{split}
+\begin{align}
 	&\big| \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \frac{1}{u} \big|
@@
 	\\&\quad \leq \gamma_0r^{\gamma_0 - 1} \big( 1+ \big\|C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big\|_\infty \big).
-\end{split} \end{equation}
+\end{align}
 	Therefore, according to Lemma \ref{lem: ergodicity of the underlying process} and the definition of $C_X$, we have that, for each $r\geq 0$ and $x\in E$,
-\begin{equation}
+\begin{align}
 	J_G(r) - J'_G(t,r,\xi)
@@
 	=0.
-\end{equation}
+\end{align}
 	According to \eqref{eq: upper bound for J_G} and \eqref{eq: upper bound for J'_G}, we have that, for each $r\geq 0$ and $t\geq 0$,
-\begin{equation} \label{eq: upper bound for J_G - J'_G}
+\begin{align} \label{eq: upper bound for J_G - J'_G}
 	\big| J_G(r) - J'_G(t,r,\xi)\big|
 	\leq (\gamma_0 + c_4) r^{\gamma_0 - 1}.
-\end{equation}
+\end{align}
 	Therefore, according to the bounded convergence theorem, we have that, for each $r\geq 0$ and $x\in E$,
-\begin{equation}
+\begin{align}
 	 \big\|  J_G(r) - J'_G(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
 	 \xrightarrow[t\to \infty]{} 0.
-\end{equation}
+\end{align}
 	According to \eqref{eq: upper bound for J_G - J'_G}, we have that, for each $\theta \geq 0$, $r\in [0,\theta]$ and $x\in E$,
-\begin{equation}
+\begin{align}
 	\big\|  J_G(r) - J'_G(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
 	\leq (\gamma_0 + c_4) \theta^{\gamma_0 - 1}.
-\end{equation}
+\end{align}
 	Finally, according to the bounded convergence theorem, we have that, for each $\theta\geq 0$ and $x\in E$, $I_2(t,\theta,x)\xrightarrow[t\to \infty]{} 0$.
@@
 	We first note that, for each $t\geq 0$ and $r\geq 0$, we have
-\begin{equation}\label{eq: expression for J_g - J'_g}
+\begin{align}\label{eq: expression for J_g - J'_g}
 	J_g(t,r,\xi) - J'_g(t,r,\xi)
-	= (\gamma_0 - 1)t\int_0^1 \big( \mathbf 1_{\gamma(\cdot )> \gamma_0}  \kappa\gamma (   \phi \eta_{ut}   )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) \big(  \xi_{(1-u)t}  \big) du.
-\end{equation}
+	= (\gamma_0 - 1)t\int_0^1 \big( \mathbf 1_{\gamma(\cdot )> \gamma_0}  \kappa\gamma \cdot (   \phi \eta_{ut}   )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) \big(  \xi_{(1-u)t}  \big) du.
+\end{align}
 	We then note that, according \eqref{eq: upper bound for g} and the definition of $\eta_t$, for each $r\geq 0$, $u\in (0,1)$ and $x\in E$, we have
-\begin{equation}\label{eq: integer in the expression of J_g - J'_g convergences to 0}\begin{split}
+\begin{align}\label{eq: integer in the expression of J_g - J'_g convergences to 0}
 	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
-	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \eta_{ut}^{\gamma(x) - 1} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
-	\\&\quad = (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \big( C_X(\gamma_0 - 1) ut\big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
-	\\&\quad \leq (\gamma_0 - 1) \mathbf 1_{\gamma(x) > \gamma_0} t^{1-\frac{\gamma(x) - 1}{\gamma_0 - 1}}\big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}
+	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \eta_{ut}^{\gamma(x) - 1} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
+	\\&\quad = (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \big( C_X(\gamma_0 - 1) ut\big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
+	\\&\quad \leq (\gamma_0 - 1) \mathbf 1_{\gamma(x) > \gamma_0} t^{1-\frac{\gamma(x) - 1}{\gamma_0 - 1}}\big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}
 	\\&\quad \xrightarrow[t\to \infty]{} 0.
-\end{split}\end{equation}
+\end{align}
 	This also gives an upper bound: For each $r\geq 0$, $u \in (0,1)$, $x\in E$ and $t\geq 1$, we have
-\begin{equation}\label{eq: upper bound for the integrator of J_g - J'_g} \begin{split}
+\begin{align}\label{eq: upper bound for the integrator of J_g - J'_g}
 	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
-	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
-\end{split}\end{equation}
+	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
+\end{align}
 	Now, with \eqref{eq: expression for J_g - J'_g}, \eqref{eq: integer in the expression of J_g - J'_g convergences to 0} and \eqref{eq: upper bound for J_g - J'_g}, we can apply Lemma \ref{lem: ergodicity of the underlying process} to the function
-\begin{equation}
+\begin{align}
 	(y,u,t)\mapsto (\gamma_0 - 1)t  \mathbf 1_{\gamma(y)> \gamma_0}  \kappa(y)\gamma(y) \big(   \phi(y) \eta_{ut}   \big)^{\gamma(y) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},y \big)^{\gamma(y)-1},
-\end{equation}
+\end{align}
 	which says that, for each $r\geq 0$,
-\begin{equation}
+\begin{align}
 	J_g(t,r,\xi) - J'_g(t,r,\xi)
 \xrightarrow[t\to \infty]{L^2(\Pi_x^{(\phi)})} 0.
-\end{equation}
+\end{align}
 	According to \eqref{eq: expression for J_g - J'_g} and \eqref{eq: upper bound for the integrator of J_g - J'_g}, for each $r\geq 0$ and $t\geq 1$, we have that
@@
 	\big |	J_g(t,r,\xi) - J'_g(t,r,\xi)  \big |
-	\leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
+	\leq (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
 \end{equation}
 	Therefore, according to the bounded convergence theorem, for each $r\geq 0$ and $x\in E$, we have that
-\begin{equation}
+\begin{align}
 	\big\| J'_g(t,r,\xi) - J_g(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
 	\xrightarrow[t\to \infty]{} 0.
-\end{equation}
+\end{align}
 	According to \eqref{eq: upper bound for J_g - J'_g}, for each $\theta \geq 0$, $r\in [0,\theta]$ , $t\geq 1$ and $x\in E$, we have that
-\begin{equation}
+\begin{align}
 	\big\| J'_g(t,r,\xi) - J_g(t,r,\xi)  \big\|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
-	\leq (\gamma_0 - 1) \big\| \kappa \gamma (c_f \theta \phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
-\end{equation}
+	\leq (\gamma_0 - 1) \big\| \kappa \gamma\cdot (c_f \theta \phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
+\end{align}
 	Therefore, according to the bounded convergence theorem, for each $\theta \geq 0$ and $x\in E$, we have that $I_4(t,\theta, x) \xrightarrow[t\to \infty]{} 0$.
@@
 	Step 6: We will show that
-\begin{equation}
+\begin{align}
 	\limsup_{t\to \infty} I_3(t,\theta,x)
@@
 	\quad \theta \geq 0, x\in E,
-\end{equation}
+\end{align}
 	where
-\begin{equation}
+\begin{align}
 	M(t,r,x)
@@
 	\quad t\geq 0, r\geq 0, x\in E,
-\end{equation}
+\end{align}
 	and
-\begin{equation}
+\begin{align}
 	M(r,x)
@@
 	\quad r\geq 0, x\in E.
-\end{equation}
+\end{align}
 	Notice that, according to \eqref{eq: upper bound for G} and \eqref{eq: upper bound for g}, we have the following bound:
-\begin{equation}\label{eq: upper bound for M(t,r,x)}
+\begin{align}\label{eq: upper bound for M(t,r,x)}
 	M(t,r,x)
@@
 	=: c_6 r,
-\end{equation}
+\end{align}
 	where the constant $c_6$ is independent of $t$ and $x$.
 	Therefore, we have
-\begin{equation}
+\begin{align}
 	M(r,x)
@@
 	\quad r\geq 0, x\in E.
-\end{equation}	
-	From the definition of $J'_G, J'_g$ and $\eta_t$, we have
-\begin{equation}\label{eq: differences between J'_G and J'_g}\begin{split}
+\end{align}	
+	From the definition of $J'_G, J'_g$ and $\eta_t$, we have for each $t \geq 0$ and $r\geq 0$,
+\begin{align}
+	\label{eq: differences between J'_G and J'_g}
 	&|J'_G(t,r,\xi) - J'_g(t,r,\xi)|
-	\\&\quad \leq \gamma_0(\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa (\phi \eta_{ut})^{\gamma_0 - 1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du
-	\\&\quad = \gamma_0 C_X^{-1}\int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa  \phi^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du,
-	\quad t\geq 0, r\geq 0.
-\end{split}\end{equation}
+	\\&\quad \leq \gamma_0(\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du
+	\\&\quad = \gamma_0 C_X^{-1}\int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa  \phi^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du.
+\end{align}
 	According to \eqref{eq: upper bound for M(t,r,x)}, we have the following upper bound:
-\begin{equation}\begin{split}
+\begin{align}
 		u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}}, x)
@@
 		\quad u\in (0,1), r\geq 0, t\geq 0, x\in E.
-\end{split}\end{equation}
+\end{align}
 	Therefore, fixing an $r\geq 0$, we can apply Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process} to the function
-\begin{equation}
+\begin{align}
 	(y,u,t)
 	\mapsto \gamma_0 C_X^{-1}\mathbf 1_{\gamma(y) = \gamma_0} \kappa(y)  \phi(y)^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},y)^{\gamma_0 - 1}
-\end{equation}
+\end{align}
 	since it is a bounded Borel function on $E\times (0,1) \times [0,\infty)$.
@@
 $M(r,x), M(r)$ and $C_X$, we have
-\begin{equation}\label{eq: limsup of J_G - J'_g}\begin{split}
+\begin{align}\label{eq: limsup of J_G - J'_g}
 	&\limsup_{t\to \infty} \| J_G'(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{\phi};\frac{1}{\gamma_0 - 1}}
@@
 	\\&\quad\leq  \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}.
-\end{split}\end{equation}
+\end{align}
 	We now recall the reverse Fatou's lemma in $L^p$ with $p\geq 1$: Let $(f_n)_{n\in \mathbb N}$ be a sequence of non-negative measurable functions defined on a measure space $S$ with $\sigma$-finite measure $\mu$.
 If there exists a non-negative $L^p(\mu)$-integrable function $g$ on $S$ such that $f_n \leq g$ for all $n$, then according to the classical reverse Fatou's lemma, we have
-\begin{equation}
+\begin{align}
 	\limsup_{n\to \infty}\big\| f_n \big\|_{\mu;p}
@@
 	= \big\| \limsup_{n\to \infty} f_n \big\|_{\mu;p}.
-\end{equation}
+\end{align}
 	Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
-\begin{equation}\begin{split}
+\begin{align}
 	&\limsup_{t\to \infty} I_3(t,\theta, x)
@@
 	\quad \theta \geq 0, x\in E.
-\end{split}\end{equation}
+\end{align}
 
@@
 	We first claim that
-\begin{equation}
+\begin{align}
 	M(\theta)
@@
 	\quad \theta \geq 0,
-\end{equation}
+\end{align}
 	for some constant $c_M > 0$.
 	In fact, a direct application of Steps 2-6 gives that, for each $t\geq 0$ and $x\in E$:
-\begin{equation}\begin{split}
+\begin{align}
 	&M(r,x)^{\gamma_0 - 1}
@@
 	\leq c_f^{\gamma_0 - 1} \gamma_0 \Big(  \int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1}.
-\end{split}\end{equation}
+\end{align}
 	Therefore, for each $\theta \geq 0$,
-\begin{equation}
+\begin{align}
 	M(\theta)
@@
 	\leq c_f \gamma_0^{\frac{1}{\gamma_0 - 1}} \int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr.
-\end{equation}
+\end{align}
 	According to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
@@
 	Ren, Y.-X., Song, R. and Sun, Z.:
-	\emph{A 2-spine decomposition of the critical 
-% galton-watson tree and a probabilistic proof of yaglom's theorem.}
-Galton-Watson tree and a probabilistic proof of Yaglom's theorem.}
+	\emph{A 2-spine decomposition of the critical Galton-Watson tree and a probabilistic proof of Yaglom's theorem.}
 	\ARXIV{1706.07125}

### 2019-05-29 presentation/stableLimit_beamer.tex
add stableLimit_beamer.tex
presentation/stableLimit_beamer.tex

% * Preamble
\documentclass[xcolor=dvipsnames]{beamer}
\synctex=1
\usepackage[UTF8,scheme=plain]{ctex}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{comment}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usetheme{Madrid}
\usecolortheme{seahorse}
\usecolortheme{rose}
\usefonttheme{serif}
\usefonttheme{structurebold}
\setbeamerfont{title}{shape=\itshape,family=\rmfamily}
\setbeamercolor{title}{fg=red!80!black,bg=red!20!white}
% * Top matter
\title[Critical Superprocesses]{Limit theorems for a class of critical superprocesses with stable branching}
\author[Z. Sun]{
{\bf \Large Zhenyao Sun}\inst{1} \\
}
\institute[PKU]{
  Based on a joint work with {\bf Yan-Xia Ren}\inst{1} and {\bf Renming Song}\inst{2}\\
  \inst{1} Peking University \\
  \inst{2} University of Illinois at Urbana-Champaign\\
}
\date[UIBE, June, 2019]{
  University of International Business and Economics\\ 
  June, 2019}
\begin{document}

% * Title page
\begin{frame}
  \titlepage
\end{frame}
% * Outline
\begin{frame}
  \frametitle{Outline}
  \tableofcontents
\end{frame}

% * Background
\section{Background}
% ** Kolmogorov's result
\subsection{Kolmogorov's result}
\begin{frame}{Background/Kolmogorov's result}
  \begin{theorem}[Kesten, Ney and Spitzer (1966)]
Let $(Z_n)_{n\in \mathbb N}$ be a critical Galton-Watson process with offspring variance $\sigma^2 \in (0,\infty)$. 
Then
\begin{align}
n P(Z_n > 0) \xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}.
\end{align}
\end{theorem}
\begin{itemize}
\item
Kolmogorov (1938) obtained the above Theorem under a three moment condition.
\end{itemize}
\end{frame}

% ** Yaglom's result
\subsection{Yaglom's result}
\begin{frame}{Background/Yaglom's result}
\begin{theorem}[Kesten, Ney and Spitzer (1966)]
Let $(Z_n)_{n\in \mathbb N}$ be a critical Galton-Watson process with offspring variance $\sigma^2 \in (0,\infty)$.
Then 
\begin{align}
  \left\{ \frac{Z_n}{n}; P(\cdot | Z_n > 0) \right\} 
\xrightarrow[n\to \infty]{d} \frac{\sigma^2}{2} {\color{red} \mathbf e},
\end{align}
where {\color{red} $\mathbf e$} is an exponential random variable with mean $1$.
\end{theorem}
\begin{itemize}
\item
Yaglom (1947) obtained the above Theorem under a stronger condition.
\end{itemize}
\end{frame}

% ** Slack's result
\subsection{Slack's result}
\begin{frame}{Background/Slack's result}
\begin{theorem}[Slack (1968)]
	Let $(Z_n)_{n\geq 0}$ be a critical Galton-Watson process with offspring generating function
$
	f(s)
	= s + (1-s)^{\alpha} l(1-s)
$
  where $\alpha \in (1,2]$ and $l$ is a slowly varing function at $0$.
  Then
$
	P(Z_n > 0) = n^{-1/(\alpha-1)} L(n)
$ 
where $L$ is slowly varying at $\infty$;
 and
\[
  \big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{d} {\color{red}\mathbf z^{(\alpha-1)} },
\]
	where {\color{red} $\mathbf z^{(\alpha-1)}$} is a positive random variable with Laplace transform
\[
	E[e^{- u {\color{red} \mathbf z^{(\alpha-1)}} } ]
	= 1 - (1+ u^{-(\alpha-1)})^{-1/(\alpha-1)},
	\quad u \geq 0.
\]
\end{theorem}
\begin{itemize}
\item
  Zolotarev (1957) obtained the above Theorem under a stronger condition.
\end{itemize}
\end{frame}

\begin{frame}
\begin{table}[] 
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|}
\hline
& $\alpha = 2$: Analytical 
& $\alpha = 2$: Probabilistic 
& $\alpha \in (1,2)$ 
\\ \hline
\begin{tabular}[c]{@{}l@{}} Galton-Watson \\ (GW) processes \end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Kolmogorov (1938)\\ Yaglom (1947)\\ Kesten, Ney \\ and Spitzer (1966) \end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Lyons, Pemantle \\ and Peres (1995)\\ Geiger (1999) \\ Geiger (2000)\\ {\color{red} Ren, Song} \\ {\color{red} and Sun (2018)}\end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Zolotarev (1957)\\ Slack (1968)\end{tabular} 
\\ \hline
\begin{tabular}[c]{@{}l@{}} Multitype GW \end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Joffe and Spitzer \\ (1967)\end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Vatutin and \\ Dyakonova (2001)\end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Goldstein and Hoppe \\ (1978)\end{tabular} 
\\ \hline
\begin{tabular}[c]{@{}l@{}} Continuous time \\ GW process \end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Athreya and Ney \\ (1972)\end{tabular} 
& - 
& Vatutin (1977) 
\\ \hline
\begin{tabular}[c]{@{}l@{}} Continuous time \\ Multitype \\ GW process \end{tabular}
& \begin{tabular}[c]{@{}l@{}} Athreya and Ney\\ (1974)\end{tabular} 
& - 
& Vatutin (1977) 
\\ \hline
\begin{tabular}[c]{@{}l@{}} Branching Markov \\ processes \end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Asmussen and \\ Hering (1983)\end{tabular} 
& Powell (2015) 
& \begin{tabular}[c]{@{}l@{}} Asmussen and Hering \\ (1983)\end{tabular} 
\\ \hline
\begin{tabular}[c]{@{}l@{}} Continuous-state \\ branching processes \end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Li (2000)\\ Lambert (2007)\end{tabular} 
& \begin{tabular}[c]{@{}l@{}} {\color{red} Ren, Song} \\ {\color{red} and Sun (2019)}\end{tabular} 
& \begin{tabular}[c]{@{}l@{}} Kyprianou and Pardo \\ (2008)\\ Ren, Yang \\ and Zhao (2014)\end{tabular} 
\\ \hline
Superprocesses 
& \begin{tabular}[c]{@{}l@{}} Evans and Perkins (1990) \\ Ren, Song \\ and Zhang (2015)\end{tabular} 
& \begin{tabular}[c]{@{}l@{}} {\color{red} Ren, Song} \\ {\color{red} and Sun (2019)}\end{tabular} 
& \begin{tabular}[c]{@{}l@{}} {\color{red} Ren, Song} \\ {\color{red} and Sun (2019+)}\end{tabular} 
\\ \hline
\end{tabular}%
}
\end{table} 
\end{frame}

\section{Model}
% ** Settings
\subsection{Settings}
\begin{frame}{Model/Settings}
  \begin{itemize}
  \item
    {\color{red}$E$} be a locally compact separable metric space;
  \item
    {\color{red} $\mathcal M$} be the collection of all the finite Borel measures on $E$; 
  \item
    Spatial motion {\color{red} $\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in E}\}$} be an $E$-valued Hunt process with transition semigroup {\color{red} $(P_t)_{t\geq 0}$};
  \item
    Branching mechanism {\color{red} $\psi$} be a function from $E\times [0,\infty)$ to $[0,\infty)$ s.t.
    \[
      \psi(x,z) 
      := -{\color{red} \beta(x)}z+\alpha(x)z^2 +\int_{(0,\infty)}(e^{-zy}-1+zy)\pi(x,dy),
    \]
    where ${\color{red}\beta}$ is a bounded measurable function on $E$, $\alpha$ is a bounded non-negative measurable function on $E$, and $\pi$ is a kernel from $E$ to $(0,\infty)$ s.t. 
    \[
      \sup_{x\in E} \int_{(0,\infty)}(y\wedge y^2)\pi(x,dy)<\infty.
    \] 
  \end{itemize}
\end{frame}

% ** Superprocesses
\subsection{Superprocesses}
\begin{frame}{Model/Superprocesses}
\begin{itemize}
\item
For each measure $\mu$ and function $f$, write
$\mu(f) : = \int f d\mu$ whenever the integral make sense.
\item
We say a measurable function $f$ on $\mathbb R_+ \times E$ is {\color{blue} locally bounded} if
\begin{align}
\sup_{s\in [0,t], x\in E} |f(s,x)| < \infty, \quad t\in \mathbb R_+.
\end{align}
\end{itemize}
\begin{definition}[Superprocesses]
An $\mathcal M$-valued Markov process {\color{red} $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu\in \mathcal M}\}$} is called a $(\xi,\psi)$-superprocess if for each $\mu \in \mathcal M, f\in b\mathscr B_+$ and $t\geq 0$ we have
\[
  \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu( {\color{red} V_tf} )}.
\]
Here, $(t,x) \mapsto {\color{red} V_tf(x)}$ on $[0,\infty) \times E$ is the unique {\color{blue} locally bounded} positive solution to the equation
\begin{align*}\label{eq:FKPP_in_definition}
  {\color{red} V_tf(x)} + \int_0^{t} P_{t-s} \psi \big(\cdot, {\color{red} V_sf(\cdot)}\big) (x) ds 
  = P_t f(x).
\end{align*}
\end{definition}
\end{frame}
\begin{frame}{Model/Superprocesses}
\begin{itemize}
\item
  Superprocess arose as high-density limits of branching particle systems. (Watanabe 1968, Dawson 1975, Dynkin 1991).
\end{itemize}
\begin{figure}
  \includegraphics[scale= 0.7]{critical_Superprocess.pdf}
\end{figure}
\end{frame}

% ** Assumptions
\subsection{Assumptions}
% *** Assumptions for spatial motion
\begin{frame}{Model/Assumptions/Spatial motion}
  \begin{itemize}
  \item
    The mean semigroup of the superprocess:
    \[
      \mathbf P_{\delta_x} [X_t(f)] = {\color{red} P_t^\beta} f(x) := \Pi_x[e^{\int_0^{t} \beta (\xi_r) dr}f(\xi_t)].
    \]
  \end{itemize}
  \begin{block}{Assumption 1.}   
    There exist a $\sigma$-finite measure {\color{red} $m$} with full support on $E$ and a family of strictly positive,
    bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that
    \begin{itemize}
    \item $P_tf(x)= \int_E p_t(x,y) f(y) m(dy);$
    \item $\int_E p_t(y,x)m(dy) \leq 1;$
    \item $\int_E \int_E p_t(x,y)^2 m(dx) m(dy)
      <\infty;$
    \item
      $x \mapsto \int_E p_t(x,y)^2 m(dy)$ and $x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Model/Assumptions/Spatial motion}
  Under Assumption 1, we can say the following:
  \begin{itemize}
  \item
    $(P^\beta_t)_{t \geq 0}$ and its disjoint $(P^{\beta *}_t)_{t \geq 0}$ are strongly continuous semigroups of compact operators in $L^2(E,m)$.
  \item
    Let $L$ and $L^*$ be the generators of $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$, respectively. 
    Then ${\color{red} \lambda} := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common {\color{red}eigenvalue} of multiplicity $1$ for both $L$ and $L^*$.
  \item
    The corresponding {\color{red}eigenfunctions} {\color{red} $\phi$} of $L$ and {\color{red} $\phi^*$} of $L^*$ can be chosen to be strictly positive and continuous everywhere on $E$.
  \item
    Normalize $\phi$ and $\phi^*$ by $\langle\phi, \phi\rangle_m = \langle\phi,\phi^*\rangle_m = 1$ so that they are unique.
  \item
    Operator $P_t^\beta$ has transition density {\color{red}$p_t^\beta(x,y)$} with respect to measure $m$.
  \end{itemize}
\end{frame}

% *** Assumptions for Mean semigroup and branching mechanism
\begin{frame}{Model/Assumptions/Mean semigroup and branching mechanism}
\begin{block}{Assumption 2. (Critical and Intrinsic Ultracontractive)}
\begin{itemize}
\item 
  $\lambda = 0$.
\item
  $\forall t > 0, \exists c_t>0, \forall x,y \in E, \quad p_t^\beta (x,y) \leq c_t \phi(x) \phi^*(y)$.
\end{itemize}
\end{block}
\begin{block}{Assumption 3 (Stable branching)}
  The branching mechanism $\psi$ is of the form:
  \begin{align*}
    \psi(x,z)
    = -\beta (x) z + \kappa(x) z^{\gamma(x)},
  \end{align*}
  where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$. 
  We also assume that 
  \[{\color{red} \gamma_0} := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1\] and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
\end{block}
\end{frame}

% ** Slack type result
\subsection{Slack type results}
\begin{frame}{Results/Slack type results}
\begin{block}{Theorem 1}
Under Assumptions 1,2 and 4, we have
\begin{itemize}
\item[(1)]
  $\mathbf P_{\delta_x}( \| X_t\| = 0) > 0$, for each $t > 0$ and $x\in E$.
\item[(2)]
  For each $\mu \in \mathcal M$, $\mathbf P_{\mu}(\|X_t\| \neq 0) = {\color{red} t^{-\frac{1}{\gamma_0 - 1}}} L(t)$ where $L(t)$ is a slowly varing function at $\infty$.
\end{itemize}
Write $C_X := \langle \mathbf 1_{\gamma(\cdot) = {\color{red} \gamma_0}} \kappa\cdot \phi^{ \color{red} \gamma_0}, \phi^* \rangle_m$ and $\eta_t := \big( C_X(\gamma_0 - 1) {\color{red} t} \big)^{\color{red} - 1/(\gamma_0 - 1) }$. 
{\color{red} Further assume} that $m( x:\gamma(x)={\color{red}\gamma_0} )>0$, then
\begin{itemize}
\item[(3)]
$
  \lim_{t\to\infty} \eta_t^{-1}\mathbf P_{\mu}(\|X_t\| \neq 0)
  =\mu(\phi);
$
\item[(4)]
  for each $f \in \mathscr B^+(E)$ with $\langle f, \phi^* \rangle_m > 0$ and $\| \phi^{-1}f \|_\infty < \infty$,
\[
  \{\eta_t X_t(f) ; \mathbf P_{\mu}(\cdot |\|X_t\| \neq 0) \}
  \xrightarrow[t\to \infty]{d} \langle f, \phi^*\rangle_m {\color{red}\mathbf z^{(\gamma_0 - 1)}}.
\]
\end{itemize}
\end{block}
\end{frame}
% * Remarks
\section{Remarks}
\begin{frame}{Remarks/Slack type result}
  \begin{itemize}
  \item
    {\color{red} The asymptotic behavior} of the critical superprocesses with spatially dependent stable branching {\color{red} is dominated by the heaviest tail $\gamma_0$}.
  \item
    The weak limit is {\color{red} universal}: the distribution of $\mathbf z^{(\gamma_0 - 1)}$ is only related to $\gamma_0$.
  \item
    We proof the above results by characterizing some {\color{red} measure transform} of the superprocesses.
  \end{itemize}
  \begin{definition}[Size-biased transform]
    Let $G$ be a non-negative measurable function which is integrable with respect to a $\sigma$-finite measure $Q$.
    A probability measure {\color{red} $Q^G$} is called the $G$-transform of $Q$ if
    \[
      d{\color{red} Q^G} = \frac{G}{Q[G]} dQ.
    \]
  \end{definition}
\end{frame}
% * Methods
\section{Methods} 
% ** Size-biased transforms
\subsection{Size-biased transforms}
\begin{frame}{Methods: Size-biased add-on}
\begin{itemize}
\item Let $X$ be an non-negative r.v. with finite mean. Define
  \begin{align}
    {\color{red} F(\theta)}:= \frac{P^X[e^{-\theta X}]}{P[e^{-\theta X}]}, \quad \theta \geq 0.
  \end{align}
Then it holds that
\[
-\log \mathbf P[e^{-\theta X}] 
= \mathbf P[X] \int_0^\theta {\color{red} F(r)} dr
,\quad \theta \geq 0.
\]
\item
We call ${\color{red} F(\theta)}$ the {\color{red} size-biased add-on} function of the random variable $X$.
\item  
The distribution of $X$ is characterized by its mean and its size-biased add-on function.
\end{itemize}
\end{frame}

% ** Poisson random measures
\subsection{Poisson random measures}
\begin{frame}{Methods/Poisson random measures}
  \begin{block}{Lemma 1}
    Let $\mathcal N$ be a Poisson random measure with intensity measure $N$. 
    Let $F$ be a non-negative testing function with $0 < N[F] < \infty$.
    Then    
    \[
      \{\mathcal N; P^{\mathcal N(F)}\}
      \overset{d}{=} \{\mathcal N + {\color{red} \delta_s}; P \otimes {\color{red}N^F(ds)}\}.
    \]
  \end{block}
  \begin{figure}[h]
    \begin{tabular}{ll}
      \includegraphics[scale=0.08]{001.jpg}
      &
        \includegraphics[scale=0.08]{002.jpg}
    \end{tabular}
  \end{figure}
\end{frame}

% ** Kuznetsov measures
\subsection{Kuznetsov measures}
\begin{frame}{Methods/Kuznetsov measures}
\begin{itemize}
\item
  The {\color{red} Kuznetsov measures $(\mathbb N_x)_{x\in E}$} of superprocess $(X_t)_{t\geq 0}$ is given by the following Theorem:
\end{itemize}
  \begin{theorem}[Li (2011) Theorem 8.24]
There is a family of $\sigma$-finite measures {\color{red} $(\mathbb N_x)_{x\in E}$} on space
\begin{align}
  \mathbb D &:= \{\mathcal M\text{-valued c\`adl\`ag functions on $[0,\infty)$} 
\\ &\qquad \text{with the null measure as a trap}\} 
\end{align}
such that for each $x\in E$, 
\begin{align}
\{(X_t)_{t>0}; \mathbf P_{\delta_x} \}
  \overset{d}{=} \left( \int_{\mathbb D} w_t \mathcal N(dw) \right)_{t>0},
\end{align}
where {\color{red} $\mathcal N$} is a Poisson random measure on $\mathbb D$ with intensity measure {\color{red} $\mathbb N_x$}.
\end{theorem}
\end{frame}

% ** Measure transform of superprocesses 
\subsection{Measure transform of superprocesses}
\begin{frame}{Methods/Measure transform of superprocesses}
\begin{block}{Theorem 3.}
  Let $\mu \in \mathcal M$ and write $\mathbb N_\mu(\cdot) := \int_{E} \mathbb N_x(\cdot)\mu(dx)$.
For each non-negative measurable function $F$ on $\mathbb D$ with $\mathbb N_\mu[F] \in (0,\infty)$, we have 
\begin{align}
\{(X_t)_{t\geq 0}; \mathbf P^{\mathcal N(F)}_\mu\} 
\overset{d}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu\} \otimes \{(w_t)_{t \geq 0}; \mathbb N^F_\mu(dw)\}.
\end{align}
\end{block}
    We can characterize $\{(w_t)_{t \geq 0}; \mathbb N^F_\mu(dw)\}$ while
    \begin{itemize}
    \item 
      $F(w) = w_t(\phi)$ using the {\color{red} classical Spine Decomposition Theorem}.
    \item 
      $F(w) = w_t(f)$ using a {\color{red} generalized Spine Decomposition Theorem}.
    \item 
      $F(w) = w_t(\phi)^2$ using a {\color{red} 2-Spine Decomposition Theorem.}
    \end{itemize}
\end{frame}

% * Few References
\section{Few References}
\begin{frame}
\frametitle<presentation>{Few References}

\begin{thebibliography}{10}

\beamertemplatearticlebibitems

\bibitem{RenSongSun2018Limit}
  Ren, Y.-X., Song, R. and Sun, Z.:
  \emph{Limit theorems for a class of critical superprocesses with stable branching.} ArXiv:1807.02837

  \bibitem{RenSongSun2017A-2-spine}
  Ren, Y.-X., Song, R. and Sun, Z.:
  \emph{A 2-spine decomposition of the critical Galton-Watson tree and a probabilistic proof of Yaglom's theorem.}
  Electron. Commun. Probab. 23 (2018), Paper No. 42, 12 pp.

  \bibitem{RenSongSun2017Spine}
  Ren, Y.-X., Song, R. and Sun, Z.:
  \emph{Spine decompositions and limit theorems for a class of critical superprocesses.}
  Acta Appl. Math. (2019), https://doi.org/10.1007/s10440-019-00243-7

  \end{thebibliography}
\end{frame}
\begin{frame}
  \centering \Large
  \emph{感谢！}
\end{frame}

\end{document}

%%% Local Variables: 
%%% TeX-engine: xetex
%%% End:

### 2019-05-30 presentation/stableLimit_beamer.tex
change stableLimit_beamer.tex sun190530

@@
 \end{frame}
+% ** Size-biased add-on functions
+\subsection{Size-biased add-on functions}
+
+\begin{frame}{Methods/Size-biased add-on functions}
+Recall that
+\begin{align}
+- \log E[e^{\theta \mathbf z^{(\gamma_0 - 1)}}] 
+  \approx 1 -  E[e^{\theta \mathbf z^{(\gamma_0 - 1)}}] 
+= \left( \frac{1}{1+\theta^{-(\gamma_0- 1)}} \right)^{\frac{1}{\gamma_0 - 1}}
+\end{align}
+\begin{block}{Lemma 2}
+The non-linear delay equation 
+ \begin{align}
+{\color{blue} G(\theta) } 
+= \int_0^\theta {\color{red}\exp\left\{ - \frac{\gamma_0}{\gamma_0 - 1} \int_0^1  G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \right\} } dr,
+\quad \theta \geq 0,
+  \end{align}
+has a unique solution:
+\begin{align}
+G(\theta) 
+  = \left( \frac{1}{1+\theta^{-(\gamma_0- 1)}} \right)^{\frac{1}{\gamma_0 - 1}},
+\quad \theta \geq 0. 
+\end{align}
+\end{block}
+
+So the {\color{red} red part} can be considered as an approximation of the size-biased add-on functions of random variable $\mathbf z^{(\gamma_0 - 1)}$.
+\end{frame}
+
+\begin{frame}{Methods/Size-biased add-on functions}
+  Recall that ${\color{blue} V_T(\theta f)(x)} = - \log \mathbf P_{\delta_x}[e^{- \theta X_T(f)}]$
+  \begin{block}{Theorem 4.}
+    For each non-negative bounded measurable function $f$, each $\theta \geq 0, x\in E$ and $T > 0$, we have
+    \begin{align}
+      &{\color{blue}V_T(\theta f)(x)} 
+      \\&= \phi(x) \int_0^\theta {\color{Red} \Pi_{x}^{(\phi)} \left[ \frac{f(\xi_T)}{\phi(\xi_T)} \exp \left\{ - \int_0^T \left( \kappa \gamma V_{T - s}(rf)^{\gamma - 1} (\xi_s) \right) \right\}\right] } dr.
+    \end{align}
+  \end{block}
+\begin{itemize}
+\item
+  The {\color{red} red} part is the size-biased add-on function of $X_T(f)$.
+\item  
+From Theorem 4 and Lemma 2, we can verify (details omitted) that
+  \begin{align}
+    \frac{V_t(\theta \eta_t f)(x)}{\eta_t \phi(x)} 
+    \xrightarrow[t\to \infty]{} G(\theta),\quad \theta >0.
+  \end{align}
+\end{itemize}
+\end{frame}
 

### 2019-07-02 response.tex
add response.tex

% * The preamble
% ! This TeX file uses 'amsart' for its document class. 
\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\calclayout
% ! 'amsmath', 'amsthm', 'amsfonts' package is automatically loaded by 'amsart' class.
% ! Below is the configuration of 'amsmath' package.
\numberwithin{equation}{section}
\allowdisplaybreaks
% ! Below is the configuration of 'amsthm' package.
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollaray}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\newtheorem{iss}{Issue}
\newtheorem{rem}[thm]{Remark}
\newtheorem*{ack}{Acknowledgment}
% ! 'inputenc' package is used to specify the set of characters allowed to input into this TeX file.
% \usepackage[utf8]{inputenc}
% ! 'foutenc' package is used to specify the set of characters allowed to output into the generated pdf file.
% \usepackage[T1]{fontenc}
% ! 'amssymb', 'mathrsfs' and 'mathtools' packages provide additional math symbols from the AMS default symbol fonts. They are compatible with the AMS class and is recommended to be used.
\usepackage{amssymb}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{mathrsfs}
% ! 'hyperref' package is used to handle cross-referencing in the generated pdf file.
\usepackage[backref]{hyperref}
% ! Other packages
\usepackage{xcolor}
\usepackage{comment}
% * Top matter
\begin{document}
\title
[short title]
{Response}
\maketitle
% * Document body
We are grateful to the referees' for their helpful comments.
We have incorporated all the comments made by the referee.
Here are the specific changes in response to the comments of the referees.
\section*{Response to the comments of Referee 1}
\begin{enumerate}
\item

\end{enumerate}
% * Bibliographic references
\bibliographystyle{plain}
\bibliography{../orggtd/bib.bib}
\end{document}

### 2019-07-12 stableLimit.tex
change stableLimit.tex
change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex


change stableLimit.tex

@@
-%---The preamble----------------------
+% * The preamble
 \documentclass[12pt,a4paper]{amsart}
@@
 \usepackage{stackrel}
+\usepackage{comment}
 \newtheorem{thm}{Theorem}[section]
@@
 \allowdisplaybreaks
-%---Top matter------------------------------
+% * Top matter
 \begin{document}
@@
 \author[Y.-X. Ren, R. Song and Z. Sun]{Yan-Xia Ren, Renming Song and Zhenyao Sun}
-%---Yan-Xia Ren
+% ** Yan-Xia Ren
 \address
@@
 \thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
-%---Renming Song
+% ** Renming Song
 \address
@@
 \thanks{The research of Renming Song is supported in part by the Simons Foundation (\#429343, Renming Song).}
-%---Zhenyao Sun
+% ** Zhenyao Sun
 \address
@@
 \maketitle
+% * Main Body
+% ** Introduction
 \section{Introduction}
-
+% *** Background
 \subsection{Background}
@@
 The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
-	For further references to these results, see 
-	\cite{Harris2002The-theory, KestenNeySpitzer1966The-Galton-Watson}.
-	Since then, lots of analogous results have been obtained for more general
-	critical branching processes with finite 2nd moment, 
-	see \cite{AsmussenHering1983Branching, AthreyaNey1974Functionals, AthreyaNey1972Branching, JoffeSpitzer1967On-multitype} for example.
+For further references to these results, see \cite{Harris2002The-theory, KestenNeySpitzer1966The-Galton-Watson}.
+Since then, lots of analogous results have been obtained for more general critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching, AthreyaNey1974Functionals, AthreyaNey1972Branching, JoffeSpitzer1967On-multitype} for example.
 
@@
 Research in this direction was first conducted by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up, which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance.
-	The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$
-	with infinite variance.
+The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$ with infinite variance.
 Assume that the  generating function $f(s)$ of the offspring distribution is of the form
@@
 In \cite{Slack1972Further}, Slack also considered the converse of this problem:
-	In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have
-	a non-degenerate weak limit,
-    the generating function of the offspring distribution must be of
-	the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
+In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit,
+the generating function of the offspring distribution must be of the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
 For shorter and more unified approaches to these results, we refer our readers to \cite{Borovkov1989Method, Pakes2010Critical}.
@@
 condition. Their main result can be stated as follows.
-	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
+% Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
+Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a $d$-type, nonsingular Galton-Watson process with its mean matrix $M:= (E[Z_1^{(j)}| Z_0^{(i)} = 1, Z_0^{(k)} = 0, \forall k \neq i])_{1\leq i,j\leq d}$ being positive regular, that is, all entries of $M$ are finite and there exists a number $n \geq 1$ such that all entries of $M^n$ are positive.
 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
-	Let $M$ be the mean matrix of $\mathbf Z$. Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, 
-	respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
+% Let $M$ be the mean matrix of $\mathbf Z$.  
+Let the process be critical in the sense that the maximal eigenvalue of $M$ is $1$. 
+% Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
+Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to this maximal eigenvalue $1$, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$ where $\mathbf 1$ is the vector $(1,\dots, 1)$.
 Suppose that
-\begin{align}\label{eq: regularly varying condition for multitype branching process}
+\begin{align}
+  \label{eq: regularly varying condition for multitype branching process}
 	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
@@
 It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
-\begin{align} \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
+\begin{align} 
+  \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
   n l(a_n)
@@
 
-	Asmussen and Hering \cite[Sections~6.3~and~6.4]{AsmussenHering1983Branching}
-	discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
-	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in
-\cite[Theorem~6.4.2]{AsmussenHering1983Branching}
-for critical branching Markov processes.
+Asmussen and Hering \cite[Sections~6.3~and~6.4]{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
+When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite[Theorem~6.4.2]{AsmussenHering1983Branching} for critical branching Markov processes.
 
@@
 Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
-\begin{align}\label{eq: Kolmogorov type result with 2rd moment}
+\begin{align}
+\label{eq: Kolmogorov type result with 2rd moment}
 	t \mathbf P_\mu(\|X_t\| \neq 0)
@@
 It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
-	A simpler version of this question has already been answered in the context of continuous-state branching processes
-	(CSBPs)
-	which can be viewed as superprocesses without spatial movements.
-	Kyprianou and Pardo \cite{Kyprianou2008Continuous} 
-	considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
-	He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
+A simpler version of this question has already been answered in the context of continuous-state branching processes	(CSBPs) which can be viewed as superprocesses without spatial movements.
+Kyprianou and Pardo \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
+% He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
+They showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
 \begin{align} \label{eq: conditional limit of CSBP with stable branching}
@@
 \end{align}
-    where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
-	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
-	CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
+% where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
+where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent to the initial position $x$.
+Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
 \begin{align}\label{eq: regular varing of branching mechanism of a CSBP}
@@
 	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
-	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
-\end{align}
+  %	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
+  % \end{align}
+  \xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}
+\end{align}
+where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent to the initial position $x$.
+
 Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem:
@@
 \begin{align}
-	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
+	\psi(x,z)   
+  % = -\beta (x) z + \kappa(x) z^{\gamma(x)},
+  &= - \beta(x) z + \kappa(x) \int_0^\infty (e^{-z y} - 1+ z y) \frac{dy}{\Gamma(- \gamma(x)) y^{1+ \gamma(x)}}
+  \\&=  -\beta (x) z + \kappa(x) z^{\gamma(x)},
 	\quad x\in E, z \geq 0,
@@
 Let $\mu$ be an arbitrary finite initial measure on $E$.
-	We will show that 
-	$\mathbf P_{\mu}( \| X_t\| \neq 0) $
-	converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
+We will show that $\mathbf P_{\mu}( \| X_t\| \neq 0)$ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
 Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we will show that
@@
 \end{align}
-	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ 
-	$C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ 
-	and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} 
-	(with $\alpha=\gamma_0-1$).
+where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0-1$).
+% ADDED
+Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ is independent of the choice of the initial configuration $\mu$.
+% END ADDED
 Precise statements of the assumptions and the results are presented in the next subsection.
@@
 
+% ** Model and Results
 \subsection{Model and results}
@@
 
-	Define the \emph{Feynman-Kac semigroup}
+% Define the \emph{Feynman-Kac semigroup}
+Recall that the branching mechanism $\psi$ is given by \eqref{eq: branching mechanism} and its linear coefficient $\beta$ is a bounded Borel function on $E$. Define the \emph{Feynman-Kac semigroup}
 \begin{align}
@@
 \end{align}
-	(Notice that if $\beta \equiv 0$, then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
-	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
-\begin{align} \label{eq: Ygalom type result without 2rd moment}
+% DELETED
+% (Notice that if $\beta \equiv 0$, then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
+% END DELETED
+% It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
+It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$ in the sense that
+\begin{align} 
+% \label{eq: Ygalom type result without 2rd moment}
+\label{eq:mean_formula}
 	\mathbf P_\mu [X_t(f)]
@@
 
-	Under Assumption \ref{asp: 1}, it is proved in
-	\cite{RenSongZhang2015Limit, RenSongZhang2017Central}
-	that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
+% ADDED
+Define $(P_t^*)_{t\geq 0}$ as the dual of the transition semigroup $(P_t)_{t\geq 0}$, i.e.
+\begin{align}
+  P_0^* = I; 
+  \quad P_t^* f(x) := \int_E p_t(y,x) f(y) m(dy), 
+  \quad t > 0, x\in E, f\in \mathscr B_b(E).
+\end{align}
+Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+Let $\widetilde L$ and $\widetilde L^*$ be the generators of the semigroups $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$, respectively.
+Denote by $\sigma(\widetilde L)$ and $\sigma(\widetilde L^*)$ the spectra of $\widetilde L$ and $\widetilde L^*$, respectively.
+According to \cite[Theorem V.6.6]{Schaefer1974Banach},
+$\widetilde \lambda := \sup \text{Re}(\sigma(\widetilde L)) = \sup \text{Re}(\sigma(\widetilde L^*))$ is a common eigenvalue of multiplicity $1$ for both $\widetilde L$ and $\widetilde L^*$.
+Using the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\widetilde \phi$ of $\widetilde L$ and $\widetilde \phi^*$ of $\widetilde L^*$ associated with the eigenvalue $\widetilde \lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
+We further normalize $\widetilde \phi$ and $\widetilde \phi^*$ by $\big\langle \widetilde \phi, \widetilde \phi \big\rangle_m = \big\langle \widetilde \phi, \widetilde \phi^*\big\rangle_m = 1$ so that they are unique.
+% END ADDED
+
+% Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
+It is also proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
 \begin{align}
@@
 \end{align}
-	It is proved in
-	\cite{RenSongZhang2015Limit, RenSongZhang2017Central}
-	that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+It is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
 Let $L$ and $L^*$ be the generators of the semigroups $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$, respectively.
 Denote by $\sigma(L)$ and $\sigma(L^*)$ the spectra of $L$ and $L^*$, respectively.
-	According to \cite[Theorem V.6.6]{Schaefer1974Banach},
-	$\lambda := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common eigenvalue of multiplicity $1$ for both $L$ and $L^*$.
+According to \cite[Theorem V.6.6]{Schaefer1974Banach}, $\lambda := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common eigenvalue of multiplicity $1$ for both $L$ and $L^*$.
 Using the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\phi$ of $L$ and $\phi^*$ of $L^*$ associated with the eigenvalue $\lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
 We further normalize $\phi$ and $\phi^*$ by $\langle\phi, \phi\rangle_m = \langle\phi,\phi^*\rangle_m = 1$ so that they are unique.
-	Moreover, for each $t\geq 0$ and $x\in E$, we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
+% Moreover, for each $t\geq 0$ and $x\in E$, we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
+Moreover, for each $t\geq 0$ and $x\in E$, we have $P^\beta_t \phi(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi^*(x) = e^{\lambda t} \phi^*(x)$.
 We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of $L$ (resp. $L^*$).
@@
 
-	Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the spatial process $\xi$.
-	Our second assumption on the spatial process $\xi$ is the following:
+% Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the spatial process $\xi$.
+% Our second assumption on the spatial process $\xi$ is the following:
+Our next assumption on the spatial process $\xi$ is the following:
 
 \begin{asp} \label{asp: 3}
-	$\varphi$ is bounded, and $(P_t)_{t\geq 0}$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
+	% $\varphi$ is bounded, and $(P_t)_{t\geq 0}$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
+	$\widetilde \phi$ is bounded, and $(P_t)_{t\geq 0}$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \widetilde \phi(x) \widetilde \phi^*(y)$.
 \end{asp}
@@
 \end{align}
-	where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
+% where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
+where $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
 \end{asp}
-	Here we use the definition of the Gamma function on the negative half line:
+% Here we use the definition of the Gamma function on the negative half line:
+Here we used the definition of the Gamma function on the negative half line:
 \begin{align}\label{eq: definition of Gamma function}
@@
 We now present the main results of this paper:
-
-\begin{thm} \label{thm: main theorem}
+\begin{thm} 
+\label{thm: main theorem}
   Suppose that $\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M_E^1}\}$ is a $(\xi, \psi)$-superprocess satisfying Assumptions \ref{asp: 1}--\ref{asp: 4}.
@@
   \item[(2)]
-	For each $\mu \in \mathcal M^1_E$, $\mathbf P_{\mu}(\|X_t\| \neq 0)$ converges to
-	$0$ as $t \to \infty$ and is regularly varying at infinity with index $-(\gamma_0-1)^{-1}$.
+    For each $\mu \in \mathcal M^1_E$, $\mathbf P_{\mu}(\|X_t\| \neq 0)$ converges to $0$ as $t \to \infty$ and is regularly varying at infinity with index $-(\gamma_0-1)^{-1}$.
     Furthermore, if $m(x: \gamma (x)= \gamma_0)>0$, then
@@
   \end{itemize}
-	Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ 
-	and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} 
+  Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev}
   (with $\alpha=\gamma_0 -1$).
-
 \end{thm}
 
+% ** Methods and overview
 \subsection{Methods and overview}
@@
 To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 	$X$.
-	Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
-	The family of functions used for the size-biased transform is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$, which is a martingale.
-	Therefore, this size-biased transform can be viewed as a martingale change of measure.
+% Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
+Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a martingale change of measure, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an measure-valued immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
+% The family of functions used for the size-biased transform is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$, which is a martingale.
+% Therefore, this size-biased transform can be viewed as a martingale change of measure.
+The martingale used for the change of measure is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$.
 Under Assumptions \ref{asp: 1} and \ref{asp: 3}, the spine process $\{\xi; \Pi^{(\phi)}\}$ is an ergodic process.
@@
 Similar idea has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
-    Let $\{(Y_t)_{t\geq 0}; P\}$ be a branching diffusion process, in a bounded domain,  with finite second moment.
+% Let $\{(Y_t)_{t\geq 0}; P\}$ be a branching diffusion process, in a bounded domain,  with finite second moment.
+Let $\{(Y_t)_{t\geq 0}; P\}$ be a branching diffusion process in a bounded domain with finite second moment.
 As have been discussed in \cite{Powell2015An-invariance}, a direct study of the partial differential equation satisfied by the survival probability $(t,x) \mapsto P_{\delta_x}(\|Y_t\| \neq 0)$ is tricky.
@@
 Then, the problem is reduced to the study of a single ordinary differential equation satisfied by $a(t)$.
-	Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of
- general critical superprocesses with finite second moment.
+Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of general critical superprocesses with finite second moment.
 In this paper, we will  generalize these arguments to a class of general critical superprocesses without finite second moment and establish Theorem \ref{thm: main theorem}(2).
-	For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform given in \eqref{e:zloltarev} can be characterized by a non-linear 
-	delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
+For the conditional weak convergence result, i.e., Theorem \ref{thm: main theorem}(3), we use a fact that the Laplace transform given in \eqref{e:zloltarev} can be characterized by a non-linear delay equation (see Lemma \ref{lem: characterize the general Mittag-Leffler distribution}).
 Using the spine method, we show that the Laplace transform of the one-dimensional distributions of the superprocess, after a proper rescaling, can be 	characterized by a similar equation (see \eqref{eq: equation for normalized V_T}).
@@
 
-	A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in
-	\cite{RenSongSun2017A-2-spine, RenSongSun2017Spine}.
-	We characterized the exponential distribution using its double size-biased transform;
-	and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
+A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine, RenSongSun2017Spine}.
+We characterized the exponential distribution using its double size-biased transform; and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
 However, the double-size-biased transform of a random variable requires its second moment being finite.
@@
 
-	In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in
-	\cite{RenSongSun2017Spine, RenSongZhang2015Limit}
-	(for general critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
+In \cite{Powell2015An-invariance} (for critical branching diffusions in a bounded domain with finite variance) and in \cite{RenSongSun2017Spine, RenSongZhang2015Limit} (for general critical superprocesses with finite variance), the conditional weak convergence was proved in two steps.
 First, a convergence result was established for $\phi$, the principal eigenfunction of the mean semigroup of the corresponding process, and then the second moment condition was used to extend the result to more general testing functions.
 However, in the present case, since we are not assuming the second moment condition, this type of argument does not work.
-	Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for a large class of general testing functions
-	in one stroke.
+Instead, we use a generalized spine decomposition theorem, which is developed in \cite{RenSongSun2017Spine}, to establish Theorem \ref{thm: main theorem}(3) for a large class of general testing functions in one stroke.
 
@@
 In Subsection \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-    In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
+% In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
+In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
 Finally, in Subsection \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
@@
 
+% ** Regular variation
 \subsection{Regular variation}
@@
 We refer the reader to \cite{BinghamGoldieTeugels1989Regular} for more results on  regular variation.
-	For $f\in \mathscr B^{++}((0,\infty))$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\gamma \in (-\infty,\infty)$ if for any $\lambda \in (0,\infty)$,
-\begin{align}
-	\lim_{t\to\infty}\frac{f(\lambda t)}{f(t)}
-	= \lambda^\gamma
-	\quad \Big(\text{resp. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
-	= \lambda^\gamma\Big).
-\end{align}
-	In this case we write  $f\in \mathcal R^\infty_\gamma$ (resp. $f\in \mathcal R^0_\gamma$).
-	Further, if $\gamma = 0$, then we say $f$ is slowly varying.
-	According to \cite[Theorem 1.3.1]{BinghamGoldieTeugels1989Regular},
-	if $L$ is a function slowly varying at $\infty$, then it can be written in the form
+% For $f\in \mathscr B^{++}((0,\infty))$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\gamma \in (-\infty,\infty)$ if for any $\lambda \in (0,\infty)$,
+For $f\in \mathscr B^{++}((0,\infty))$ and $\alpha \in (- \infty, \infty)$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\alpha$ if for any $u \in (0,\infty)$,
+\begin{align}
+	% \lim_{t\to\infty}\frac{f(\lambda t)}{f(t)}
+	\lim_{t\to\infty}\frac{f(ut)}{f(t)}
+	% = \lambda^\gamma
+  = u^\alpha
+	% \quad \Big(\text{resp. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
+	\quad \Big(\text{resp. } \lim_{t\to 0}\frac{f(u t)}{f(t)}
+	% = \lambda^\gamma\Big).
+	= u^\alpha\Big).
+\end{align}
+% In this case we write  $f\in \mathcal R^\infty_\gamma$ (resp. $f\in \mathcal R^0_\gamma$).
+In this case we write  $f\in \mathcal R^\infty_\alpha$ (resp. $f\in \mathcal R^0_\alpha$).
+% Further, if $\gamma = 0$, then we say $f$ is slowly varying.
+Further, if $\alpha = 0$, then we say $f$ is slowly varying.
+According to \cite[Theorem 1.3.1]{BinghamGoldieTeugels1989Regular}, if $L$ is a function slowly varying at $\infty$, then it can be written in the form
 \begin{align}
@@
 	If further 
-	we have $m(x:\gamma(x) = \gamma_0)>0$,
-	then by the monotone convergence theorem  it is easy to see that
+	we have $m(x:\gamma(x) = \gamma_0)>0$, then by the monotone convergence theorem  it is easy to see that
   \begin{equation}
@@
 Suppose that Assumptions \ref{asp: 1}--\ref{asp: 2} hold.
-    Integrating both sides of \eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we get that
+% ADDED
+Noting that $\phi^*$ is the eigenfunction of semigroup $(P_t^{\beta*})_{t\geq 0}$, we have
+\begin{align}
+  \langle P^\beta_{t} f, \phi^* \rangle_m 
+  = \langle f, P^{\beta*}_{t}\phi^* \rangle_m 
+  = \langle f, \phi^* \rangle_m,
+  \quad f\in \mathscr B^+_b(E), t\geq 0. 
+\end{align}
+% END ADDED
+% CHANGED
+% Integrating both sides of \eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we get that
+% \begin{align}\label{eq:langleVtfphiranglem_equation}
+%   \langle V_tf,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,V_r f) , \phi^*\rangle_mdr
+%   = \langle V_sf,\phi^*\rangle_m,
+%   \quad t\geq s\geq 0, f\in \mathscr B^+_b(E).
+% \end{align}
+% CHANGES
+Therefore, integrating the both sides of \eqref{eq:mean-fkpp} with respect to measure $\phi^*dm$, we get that
+\begin{align}
+  \langle V_tf,\phi^*\rangle_m + \int_0^t \langle \psi_0(\cdot ,V_r f) , \phi^*\rangle_mdr
+  = \langle f,\phi^*\rangle_m,
+  \quad t\geq 0, f\in \mathscr B^+_b(E).
+\end{align}
+This can be rearranged as
 \begin{align}\label{eq:langleVtfphiranglem_equation}
@@
 \end{align}    
+% END CHANGED
 
@@
 We say that $(X_t)_{t\geq 0}$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
-	Suppose that $(X_t)_{t\geq 0}$ is non-persistent,
-	then according to \cite[Section 8.4]{Li2011Measure-valued},
-	there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
+Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued}, there is a family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
 \begin{itemize}
@@
 \item
-	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure defined on some probability space
-	with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
-	then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+	% For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure on $\mathbb W$ with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
 \end{itemize}
@@
 Let $(\Omega, \mathscr F)$ be a measurable space with a $\sigma$-finite measure $\mu$.
-	For any $F\in \mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and 
-	$\mu(F) \in (0,\infty)$.
+For any $F\in \mathscr F$, we say \emph{$\mu$ can be size-biased by $F$} if $\mu(F< 0) = 0$ and $\mu(F) \in (0,\infty)$.
 In this case, we define the \emph{$F$-transform of $\mu$} as the probability $\mu^F$ on $(\Omega, \mathscr F)$ such that
@@
 \end{thm}
-	The second step of the spine decomposition theorem
-	says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
-	We say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
+% CHANGE
+% The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
+The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$, the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
+% END CHANGE
+
+% ADDED
+More precisely,
+% END ADDED
+we say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
 \begin{itemize}
 \item
-	The \emph{spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, 
-	where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) \exp\{\int_0^T \beta(\xi_s)ds\}$-transform
-	of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
+	The \emph{spine process} $\{(\xi_t)_{0\leq t\leq T}; \dot{\mathbf P}^{(g,T)}_\mu\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(g,T)}_{\mu}\}$, where $\Pi^{(g,T)}_{\mu}$ is the $g(\xi_T) \exp\{\int_0^T \beta(\xi_s)ds\}$-transform of the measure $\Pi_{\mu}(\cdot):=\int_{E}\mu(dx)\Pi_x(\cdot) $;
 \item
@@
 \end{itemize}
-
 \begin{thm}[Spine representation, \cite{RenSongSun2017Spine}]\label{thm: spine representation}
@@
 The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, considered the case when $g = \phi$ only.
-	In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is, the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$,
-	on the finite time interval $[0,T]$.
-	In fact, one can also check that
-	this consistency property
-	is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)_{T\geq 0}$.
+In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is, the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$,	on the finite time interval $[0,T]$.
+In fact, one can also check that this consistency property is satisfied by  $(\mathbf P_\mu^{X_T(\phi)} )_{T\geq 0}$, $(\mathbb N^{W_T(\phi)}_\mu)_{T\geq 0}$ and $(\dot {\mathbf P}^{(\phi,T)}_\mu)_{T\geq 0}$.
 Therefore, the actual statement of the classical spine decomposition theorem is different from merely replacing $g$ with $\phi$ in Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation}:
@@
 \item
-	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with
-    intensity
+	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with intensity
   \begin{align}\label{eq:meanMeasImmigr}
@@
 
+% ** Ergodicity of the spine process
 \subsection{Ergodicity of the spine process}
@@
 \begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
-	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$,
-	then
+	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, then
 \begin{align}
@@
 \end{align}
-	Finally,
-    noting that $0\leq F \leq \bar F$, we get
+Finally, noting that $0\leq F \leq \bar F$, we get
 \begin{align}
@@
   Then, we know that $m(\tilde \kappa \neq \kappa) = 0$ and $m(\tilde \gamma \neq \gamma) = 0$.
-	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$,
-	then for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z),$ $m$-almost everywhere.
+	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z),$ $m$-almost everywhere.
 
@@
 
-\subsection{Proof of Theorem \ref{thm: main theorem}(2)}
+% ** Proof of the main Theorem 2 
+\subsection{Proof of Theorem \ref{thm: main theorem} (2)}
 \label{sec: proof of result 2}
+% ADDED
+\begin{proof}
+  [Proof of Theorem \ref{thm: main theorem} (2)]
+  % END ADDED
   Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
@@
   \begin{align}
+    % ADDED
+    \label{eq:extinction_probability_is_not_zero}
+    % END ADDED
     \mathbf P_{\delta_x}(\|X_t\| = 0)
@@
   \end{align}
-	Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have
-\begin{align}
+  % Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have
+  According to \eqref{eq:mean_formula}, Assumption \ref{asp: 2} and the fact that $\phi$ is the eigenfunction of semigroup $(P_t^\beta)_{t\geq 0}$, we have $\mathbf P_{\delta_x}[X_t(\phi)] = P_t^\beta \phi(x) = e^{\lambda t} \phi(x)= \phi(x)>0$.
+  Therefore,
+  \begin{align}
+    \label{eq:extinction_probability_is_not_one}
     \mathbf P_{\delta_x}(\|X_t\|= 0)<1,
@@
   \end{align}
-	From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
-	According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp}, by monotonicity,
-	we see that $(v_t)_{t > 0}$ satisfies the equation
+  % From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
+  From \eqref{eq:extinction_probability_is_not_zero}, \eqref{eq:extinction_probability_is_not_one} and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
+
+  According to \eqref{eq: definition of v_t(x)} and \eqref{eq:mean-fkpp}, by monotonicity, we see that $(v_t)_{t > 0}$ satisfies the equation
   \begin{align}
@@
   \end{align}
-
   Notice that, under Assumption \ref{asp: 1}, according to \eqref{eq: p-t-beta is comparable to phi phi-star}, $d\nu:= \phi^* dm$ defines a finite measure on $E$.
   Therefore, $\langle v_t, \phi^*\rangle_m < \infty$ for each $t>0$.
-
-	According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem,
-	$(v_t)_{t> 0}$ also satisfies the equation
-\begin{align} \label{eq: equation of <vt,phi>}
+  According to \eqref{eq:langleVtfphiranglem_equation}, \eqref{eq: definition of v_t(x)} and the monotone convergence theorem, $(v_t)_{t> 0}$ also satisfies the equation
+  \begin{align} 
+    \label{eq: equation of <vt,phi>}
     \langle v_t,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,v_t) , \phi^*\rangle_m dr
@@
   One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example,
-\begin{align} \label{eq: uniform converges to 0}
+  \begin{align} 
+    \label{eq: uniform converges to 0}
     \|\phi^{-1}v_t\|_{\infty} \xrightarrow[t\to \infty]{} 0.
   \end{align}
-	Therefore, to prove Theorem \ref{thm: main theorem}(2), we only need to consider the speed of this convergence.
-	This is answered in two steps.
-	The first step says that $(\phi^{-1}v_t)(x)$ will converge to $0$ in the same speed as $\langle v_t,\phi^*\rangle_m $, uniformly in $x\in E$:
+  % Therefore, to prove Theorem \ref{thm: main theorem}(2), we only need to consider the speed of this convergence.
+  However, to prove Theorem \ref{thm: main theorem}(2), we need to consider the speed of this convergence.
+  % This is answered in two steps.
+  This is answered in the following two propositions whose proof is postponed after the current proof.
+  % The first step says that $(\phi^{-1}v_t)(x)$ will converge to $0$ with the same speed as $\langle v_t,\phi^*\rangle_m$, uniformly in $x\in E$:
+  The first proposition says that $(\phi^{-1}v_t)(x)$ will converge to $0$ with the same speed as $\langle v_t,\phi^*\rangle_m$, uniformly in $x\in E$:
 
@@
   \label{prop: asymptotic equivalence of vtphi}
-	The second step characterizes this speed:
+  % The second step characterizes this speed:
+  The second proposition characterizes this speed:
   \begin{prop}
@@
   \end{prop}
-
-\begin{proof}[Proof of Proposition \ref{prop: convergence in a same speed}]
+% MOVED FROM BELOW
+    % According to \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0},
+    From \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0}, we have
+    \begin{align}
+      - \log \mathbf P_\mu(\|X_t\| = 0)
+      = \mu(v_t)
+      \leq \mu(\phi) \| \phi^{-1} v_t\|_{\infty}
+      \xrightarrow[t\to \infty]{} 0.
+    \end{align}
+    % Therefore, $\mathbf P_\mu(\|X_t\| \neq 0) \xrightarrow[t\to \infty]{} 0$.
+    Therefore, since $- \log (1-x) \to 0$ implies $x \to 0$, we have $\mathbf P_\mu(\|X_t\| \neq 0) \xrightarrow[t\to \infty]{} 0$.
+
+    % Noticing that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, according to \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed}, we have
+    Also from that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed}, we have
+    \begin{align}
+      \mathbf P_\mu(\|X_t\| \neq 0)
+      \stackrel[t\to \infty]{}{\sim} - \log \mathbf P_\mu(\|X_t\| = 0)
+      = \mu(\phi \phi^{-1}v_t)
+      \stackrel[t\to\infty]{}{\sim} \mu(\phi) \langle v_t, \phi^*\rangle_m.
+    \end{align}
+    Therefore, according to Proposition \ref{prop: regularly varying of vt-phi-star}, we get the desired result.
+% END MOVED FROM BELOW
+  % ADDED
+\end{proof}
+% END ADDED
+
+\begin{proof}
+  [Proof of Proposition \ref{prop: convergence in a same speed}]
 	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
 	For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$.
-	According to \eqref	{eq: equation for mu v-t}, \eqref{eq: mean of kuz measure} and Theorem \ref{thm: spine representation},
-	we have that for each $t>0$,
-\begin{align}\label{eq:vt-and-Y}
+	According to \eqref	{eq: equation for mu v-t}, \eqref{eq: mean of kuz measure} and Theorem \ref{thm: spine representation}, we have that for each $t>0$,
+\begin{align}
+\label{eq:vt-and-Y}
 	\langle \mu,\phi \rangle \dot {\mathbf P}^{(\phi)}_\mu [Y_t(\phi)^{-1}]
@@
 \end{align}
+% Taking $\mu = \delta_x$ in \eqref{eq:vt-and-Y}, we get $(\phi^{-1}v_t)(x) =\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]$.
 Taking $\mu = \delta_x$ in \eqref{eq:vt-and-Y}, we get $(\phi^{-1}v_t)(x) =\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]$.
+% Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
+Recall that $d\nu = \phi^* dm$. 
 Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
@@
 \begin{align}
+  \label{eq:desired_for_main_theorem_2}
 	\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
@@
 
+% ADDED
+In order to show this, we consider a decomposition of the immigration process $(Y_t)_{t\geq 0}$.
+% END ADDED
 For any $t>0$ and any $G\in \mathscr B((0,t])$, define
@@
 Using this decomposition, for each $0<t_0<t<\infty$ and $x\in E$, we have
-\begin{align}\label{eq: starting point of phi-1v_t(x)}
+\begin{align}
+  \label{eq: starting point of phi-1v_t(x)}
   \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
@@
 
-	By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, we have that
+% By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, we have that
+By the construction of the spine representation $\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ and its Markov property, we have that
 \begin{align}
@@
 
+% ADDED
+The underline idea of the proof is to show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
+This is done in the following two lemmas whose proofs are postponed after the current proof.
+% END ADDED
+
+% ADDED
 Let $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}.
-	We claim that
-\begin{align}\label{eq: bound for epsilon1}
+\begin{lem}
+  \label{lem:bound_for_epsilon1}
+  For each $t > t_0 > 1$, we have that
+  \begin{align}
     |\epsilon_x^1(t_0,t)|
-	\leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m,
-    \quad t_0 > 1.
-\end{align}
-	In fact,
+    \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m.
+  \end{align}
+\end{lem}
+
+\begin{lem}
+  \label{lem:upperbound_of_epsilon-2}
+  For each $t_0 > 1$ and $t - t_0$ large enough, we have
+  \begin{align}
+    \label{eq:upperbound_of_epsilon-2}
+    |\epsilon_x^2(t_0,t)|
+    \leq t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
+  \end{align}
+\end{lem}
+% END ADDED
+
+% MOVED AND MODIFIED FROM BELOW
+% Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq: some equations for PY-1-3},  Lemma \ref{lem:bound_for_epsilon1} and \eqref{eq:epsilon-2-final}, we have
+Now, for each $t_0 > 1$ and $t-t_0$ large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq:vt-and-Y},  Lemma \ref{lem:bound_for_epsilon1} and Lemma \ref{lem:upperbound_of_epsilon-2}, we have
+\begin{align} \label{vts-inequality}
+	&\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0},\phi^* \rangle_m}-1 \Big|
+   \leq \frac{|\epsilon_x^1(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m} + \frac{|\epsilon_x^2(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m}\\
+   % &\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty}
+     & \quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty}
+       \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
+\end{align}
+According to \eqref{eq: uniform converges to 0}, there exists a map $t\mapsto t_0(t)$ such that,
+\begin{align}
+	t_0(t)
+	\xrightarrow[t\to\infty]{} \infty;
+	\quad t_0(t)\| \phi^{-1}v_{t-t_0(t)}\|^{\gamma_0 - 1}_\infty
+	\xrightarrow[t\to\infty]{} 0.
+\end{align}
+Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
+\begin{align}\label{eq:k1}
+	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
+	\xrightarrow[t\to\infty]{} 0.
+\end{align}
+Notice that
+\begin{align}\label{eq:k2}
+	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
+	% & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle} - 1 \Big| \phi \phi^*(x) m(dx)\\
+    & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big| \phi \phi^*(x) m(dx)\\
+    & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
+      \xrightarrow[t\to\infty]{} 0.
+\end{align}
+Therefore, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
+\begin{align}
+	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
+	\xrightarrow[t\to\infty]{} 0,
+\end{align}
+as desired.
+\end{proof}
+% END MOVED AND MODIFIED FROM BELOW
+
+% Let $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}.
+\begin{proof}
+  [Proof of Lemma \ref{lem:bound_for_epsilon1}]
+  Note that $c_0, c_1>0$ are the constants in \eqref{eq:q(t,x,y)}.
+  % DELETED
+  % We claim that
+  % \begin{align}\label{eq: bound for epsilon1}
+  %   |\epsilon_x^1(t_0,t)|
+  %   \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m,
+  %   \quad t_0 > 1.
+  % \end{align}
+  % END DELETED
+  % In fact,
+  Then for each $t > t_0 > 1$, we have that
   \begin{align}
@@
     & \leq \int_{y\in E} \big| q_{t_0}(x,y) - (\phi\phi^*)(y) \big| (\phi^{-1}v_{t-t_0})(y) m(dy)\\
-	& \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m .
-\end{align}
-
-	We now claim that, if $t_0 > 1$ and $t-t_0$ is large enough, then
-\begin{align}\label{eq:upperbound_of_epsilon-2}
-	|\epsilon_x^2(t_0,t)|
-	\leq t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
-\end{align}
-	In fact, using the Markov property of the spine process and the property of Poisson random measures, we have
+    & \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m.
+    % ADDED
+      \qedhere
+      % END ADDED
+  \end{align}
+% ADDED
+\end{proof}
+% END ADDED
+
+% CHANGE
+% We now claim that, if $t_0 > 1$ and $t-t_0$ is large enough, then
+% \begin{align}\label{eq:upperbound_of_epsilon-2}
+%   |\epsilon_x^2(t_0,t)|
+%   \leq t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
+% \end{align}
+\begin{proof}
+  [Proof of Lemma \ref{lem:upperbound_of_epsilon-2}]
+% In fact, using the Markov property of the spine process and the property of Poisson random measures, we have
+Using the Markov property of the spine process and the property of Poisson random measures, we have
 \begin{align}\label{eq:epsilon-2}
@@
 \end{align}
+
+% CHANGE
+\begin{comment}
 On one hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
+According to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
 \begin{align}\label{eq:epsilon-2-final}
@@
 On the other hand, since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
-	Then, if $t-s > t-t_0 \geq s_0$,
-	using the fact that $v_t$ is non-increasing in $t$, we get
+Then, if $t-s > t-t_0 \geq s_0$, using the fact that $v_t$ is non-increasing in $t$, we get
 \begin{align}
@@
 	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{ \|X_{t-s}\| \neq 0}]\pi(\xi_s,dy)
-	\\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
+	% \\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
+	\\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(\xi_s)}}
 	= \int_0^{t_0} \big( \kappa \gamma  v_{t-s}^{\gamma - 1} \big) (\xi_s)ds
@@
 \end{align}
-Combining this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get \eqref{eq:upperbound_of_epsilon-2}.
-
-	Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq: some equations for PY-1-3}, \eqref{eq: bound for epsilon1} and \eqref{eq:epsilon-2-final}, we have
+Combining this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get Lemma \ref{lem:upperbound_of_epsilon-2}.
+\end{comment}
+
+Since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
+With this $s_0>0$, we claim that for each $t - t_0\geq s_0$ the following holds:
+\begin{align}
+  \label{eq:epsilon-2-one}
+  \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
+  \leq t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
+\end{align}
+We will verify this claim at the end of the current proof.
+
+On the other hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
+\begin{align}\label{eq:epsilon-2-final}
+	\dot{\mathbf P}_{\delta_x}^{(\phi)}[ Y^{(t_0,t]}_t(\phi)^{-1}]
+	\leq (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
+\end{align}
+Therefore, from \eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-one} and \eqref{eq:epsilon-2-final}, we get that
+\begin{align}
+&|\epsilon_x^2(t_0,t)| 
+\leq t_0 \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \|\phi^{-1} v_{t-t_0}\|_\infty^{\gamma_0 - 1} \cdot \dot{\mathbf P}_{\delta_x}^{(\phi)} \big[ Y_t^{(t_0, t]}(\phi)^{-1} \big]
+\\ & \leq t_0 \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \|\phi^{-1} v_{t-t_0}\|_\infty^{\gamma_0 - 1} \cdot (1+ c_0 e^{-c_1 t_0})\langle v_{t-t_0}, \phi^* \rangle_m,
+\end{align}
+as desired for this Lemma.
+
+To complete the proof, we still need to verify the claim \eqref{eq:epsilon-2-one}.
+Note that, if $t-s > t-t_0 \geq s_0$, using the fact that $v_t$ is non-increasing in $t$, we get
+\begin{align}
+	\kappa(x)\gamma(x) v_{t-s}(x)^{\gamma(x)-1}
+	\leq \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1} v_{t-s}\|^{\gamma_0-1}_\infty
+	\leq \|\kappa\gamma\phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
+\end{align}
+Therefore, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have,  for $t-t_0 \geq s_0$,
+\begin{align}
+	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
+   \leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{ \| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]\big)
+	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
+	\\&\quad = -\log \lim_{\lambda \to \infty} \exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
+	\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{ \|w_{t-s}\| \neq 0} \mathbf m^\xi(ds,dw)
+	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{ \|X_{t-s}\| \neq 0}]\pi(\xi_s,dy)
+	% \\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
+	\\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(\xi_s)}}
+	= \int_0^{t_0} \big( \kappa \gamma  v_{t-s}^{\gamma - 1} \big) (\xi_s)ds
+	\\&\quad \leq  t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
+\end{align}
+This ends the verification of the claim \eqref{eq:epsilon-2-one}, and thus also completes the proof of Lemma \ref{lem:upperbound_of_epsilon-2}.
+% END CHANGE
+
+% ADDED
+\end{proof}
+% END ADDED
+
+% MOVED AND MODIFIED TO ABOVE
+\begin{comment}
+Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq: some equations for PY-1-3}, Lemma \ref{lem:bound_for_epsilon1} and \eqref{eq:epsilon-2-final}, we have
 \begin{align} \label{vts-inequality}
@@
    \leq \frac{|\epsilon_x^1(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m} + \frac{|\epsilon_x^2(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m}\\
-	&\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty}
+   % &\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty}
+     & \quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty}
        \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
@@
 	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
-	&\leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle} - 1 \Big| \phi \phi^*(x) m(dx)\\
-	&\leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
+	% & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle} - 1 \Big| \phi \phi^*(x) m(dx)\\
+    & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big| \phi \phi^*(x) m(dx)\\
+    & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
       \xrightarrow[t\to\infty]{} 0.
@@
 \end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop: regularly varying of vt-phi-star}]
-
+\end{comment}
+% END MOVED AND MODIFIED TO ABOVE
+
+\begin{proof}
+  [Proof of Proposition \ref{prop: regularly varying of vt-phi-star}]
 	From \eqref{eq: equation of <vt,phi>} we know that $\langle v_t,\phi^* \rangle_m$ is continuous and strictly decreasing in $t \in (0,\infty)$.
-	Since the superprocess $(X_t)_{t\geq 0}$ is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$,
-	$\mathbf P_\mu (\|X_t\| \neq 0) \xrightarrow[t\to 0]{} 1$.
+	Since the superprocess $(X_t)_{t\geq 0}$ is right continuous in the weak topology with the null measure as an absorbing state, we have that, for each $\mu \in \mathcal M_E^1$, $\mathbf P_\mu (\|X_t\| \neq 0) \xrightarrow[t\to 0]{} 1$.
 	Taking $\mu = \nu$, according to \eqref{eq: equation for mu v-t}, we have that $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to 0]{} +\infty$.
-	On the other hand, according to \eqref{eq: uniform converges to 0}, we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
-	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse on $(0,\infty)$ which is denoted by
+	% On the other hand, according to \eqref{eq: uniform converges to 0}, we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
+	On the other hand, according to \eqref{eq: uniform converges to 0}, we have 
+\begin{align}
+  \langle v_{t}, \phi^*\rangle_m
+  = \langle \phi^{-1} v_t \phi, \phi^*\rangle_m
+  \leq \|\phi^{-1} v_t\|_\infty \cdot \langle \phi, \phi^* \rangle_m
+ \xrightarrow[t\to \infty]{} 0.
+\end{align}
+	% Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse on $(0,\infty)$ which is denoted by
+	Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle_m$ has an inverse on $(0,\infty)$ which is denoted by
 \begin{align}
@@
 	\epsilon_{t}(x)
-	: = \frac{v_t(x)}{\langle v_t, \phi^*\rangle \phi(x)} - 1,
-	\quad t>0, x\in E.
-\end{align}
-	Then, we have
+	% : = \frac{v_t(x)}{\langle v_t, \phi^*\rangle \phi(x)} - 1,
+	: = \frac{v_t(x)}{\langle v_t, \phi^*\rangle_m \phi(x)} - 1,
+	% \quad t>0, x\in E.
+	\quad t>0, x\in E,
+\end{align}
+% Then, we have
+then we have
 \begin{align}\label{eq: change variable using inverse}
 	v_t(x)
-	= \big(1+ \epsilon_{R(\langle v_t,\phi^* \rangle)}(x) \big )\langle v_t,\phi^* \rangle \phi(x),
+	% = \big(1+ \epsilon_{R(\langle v_t,\phi^* \rangle)}(x) \big )\langle v_t,\phi^* \rangle \phi(x),
+	= \big(1+ \epsilon_{R(\langle v_t,\phi^* \rangle_m)}(x) \big )\langle v_t,\phi^* \rangle_m \phi(x),
 	\quad t>0, x\in E.
 \end{align}
-	Further, by Proposition \ref{prop: convergence in a same speed} and
-	the fact that $R(u)\xrightarrow[u\to 0]{} \infty$, we have
+Further, by Proposition \ref{prop: convergence in a same speed} and the fact that $R(u)\xrightarrow[u\to 0]{} \infty$, we have
   \begin{align}\label{eq: epsilon R converges to 0}
@@
       = \int_s^t \langle \psi_0(\cdot ,v_r), \phi^*\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
-	\\&\overset{\text{by \eqref{eq: change variable using inverse} }}{=} \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle \phi \big), \phi^* \big\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
-	\\&= \int_{\langle v_s,\phi^*\rangle}^{\langle v_t, \phi^* \rangle} \big\langle \psi_0 \big( \cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du.
+      % \\&\overset{\text{by \eqref{eq: change variable using inverse} }}{=} \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle \phi \big), \phi^* \big\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
+    \\ & \overset{\text{by \eqref{eq: change variable using inverse} }}{=} \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle_m \phi \big), \phi^* \big\rangle_m^{-1} d\langle v_r ,\phi^* \rangle_m
+    \\ & = \int_{\langle v_s,\phi^*\rangle}^{\langle v_t, \phi^* \rangle} \big\langle \psi_0 \big( \cdot ,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du.
   \end{align}
@@
 \end{align}
-	According to Lemma \ref{lem:regularly_variation_and_integration},
-	and using the fact that $\kappa(x)\phi(x)^{\gamma(x)}$ is bounded and the measure $\phi^* dm$ is finite,
-	we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
-	Noticing that $-(\gamma_0 - 1) < 0$,
-	according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
+According to Lemma \ref{lem:regularly_variation_and_integration}, and using the fact that $\kappa(x)\phi(x)^{\gamma(x)}$ is bounded and the measure $\phi^* dm$ is finite, we have that $\langle \psi_0\big(\cdot,(1+\epsilon_{R(u)})u\phi \big), \phi^* \rangle_m$ is regularly varying at $u = 0$ with index $\gamma_0$.
+Noticing that $-(\gamma_0 - 1) < 0$, according to Corollary \ref{cro: power law and ingetration} and \eqref{eq: integral equation for R}, $R$ is regularly varying at $0$ with index $-(\gamma_0 - 1)$.
 Therefore, from $R(\langle v_s, \phi^*\rangle_m) = s$ and Corollary \ref{cro: regularly varing and inverse with alpha < 0}, we have that $(\langle v_s, \phi^*\rangle_m)_{s\in (0,\infty)}$ is regularly varying at $\infty$ with index $-(\gamma_0 - 1)^{-1}$.
@@
 \begin{align}
-	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
+	& \big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
    \stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x)
    \rangle_{m(dx)}
-	\\ &\quad \stackrel[u\to 0]{}{\sim}  \langle \mathbf 1_{\gamma(x)= \gamma_0}, \kappa (x)\phi(x)^{\gamma_0} \phi^*(x)
-	\rangle_{m(dx)} u^{\gamma_0}
+	\\ & \quad \stackrel[u\to 0]{}{\sim}  \langle \mathbf 1_{\gamma(x)= \gamma_0}, \kappa (x)\phi(x)^{\gamma_0} \phi^*(x) \rangle_{m(dx)} u^{\gamma_0}
        =: C_X u^{\gamma_0}.
@@
 	R(r)
-	&= \int_r^\infty \big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
+	& = \int_r^\infty \big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m^{-1} du
    = \int_r^\infty u^{-\gamma_0} l(u) du
-	\\&= -\frac{1}{\gamma_0-1}\int_r^\infty l(u) du^{-(\gamma_0 - 1)}
-	\\&\stackrel[r\to 0]{}{\sim} C_X^{-1} (\gamma_0-1)^{-1} r^{-(\gamma_0 - 1)}.
-\end{align}
-	Now since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, 
-	from \cite[Proposition 1.5.15.]{BinghamGoldieTeugels1989Regular} and the above,
-	we have
+	\\ & = -\frac{1}{\gamma_0-1}\int_r^\infty l(u) du^{-(\gamma_0 - 1)}
+	\\ & \stackrel[r\to 0]{}{\sim} C_X^{-1} (\gamma_0-1)^{-1} r^{-(\gamma_0 - 1)}.
+\end{align}
+Finally since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from \cite[Proposition 1.5.15.]{BinghamGoldieTeugels1989Regular} and the above, we have
 \begin{equation}
@@
 
+% MOVED ABOVE:
+\begin{comment}
 \begin{proof}[Proof of Theorem \ref{thm: main theorem}(2)]
@@
 \end{proof}
-
+\end{comment}
+% END MOVED ABOVE
+
+% ** Characterization of the one dimensional distribution
 \subsection{Characterization of the one dimensional distribution}
@@
 
-	From the point of view of Laplace transforms, the desired result that, for any $f\in \mathscr B^+_b(E)$ and $\mu\in \mathcal M_E^1$, $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\mu}(\cdot | \|X_t\| \neq 0)\big\}$ converge weakly to some probability distribution
-	$F_f$
-	is equivalent to the following convergence:
+From the point of view of Laplace transforms, the desired result that, for any $f\in \mathscr B^+_b(E)$ and $\mu\in \mathcal M_E^1$, $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\mu}(\cdot | \|X_t\| \neq 0)\big\}$ converge weakly to some probability distribution $F_f$ is equivalent to the following convergence:
 \begin{align}
@@
 \end{align}
-	On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
+% On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
+On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, the spine representation, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
 \begin{align}\label{eq: dynamic of theta on v_t theta reason 2}
@@
    = \mathbf m_T^\xi(1-e^{-\theta F})
-	\\&\quad = \int_0^T ds \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}[1- e^{-\theta X_{T-s}(f)}] \pi(\xi_s,y)
-	\\&\quad = \int_0^T ds \cdot \kappa(\xi_s) \int_{(0,\infty)} \mathbf (1- e^{- y V_{T-s}(\theta f)(\xi_s)}) \frac{dy}{\Gamma(-\gamma(\xi_s)) y^{\gamma(\xi_s)}}
-	\\&\quad = \int_0^T \big(\kappa\gamma V_{T-s}(\theta f)^{\gamma-1}\big)(\xi_s) ds.
+	\\ & \quad = \int_0^T ds \int_{(0,\infty)} y \mathbf P_{y\delta_{\xi_s}}[1- e^{-\theta X_{T-s}(f)}] \pi(\xi_s,y)
+	\\ & \quad = \int_0^T ds \cdot \kappa(\xi_s) \int_{(0,\infty)} \mathbf (1- e^{- y V_{T-s}(\theta f)(\xi_s)}) \frac{dy}{\Gamma(-\gamma(\xi_s)) y^{\gamma(\xi_s)}}
+	\\ & \quad = \int_0^T \big(\kappa\gamma V_{T-s}(\theta f)^{\gamma-1}\big)(\xi_s) ds.
 \end{align}
@@
    \dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
-	\\&=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \Big[\exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds\Big\}\Big] dr
-	\\&= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr,
+	\\ &=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \Big[\exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds\Big\}\Big] dr
+	\\ &= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr,
 \end{align}
@@
 
+% ** Distribution with Laplace transform 
+% MOVED AND MODIFIED BELOW
+\begin{comment}
 \subsection{Distribution with Laplace transform (\ref{e:zloltarev})}
@@
 
+% MINER CHANGES: I changed all \gamma_0 here to \alpha without further noticing.
 \begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
+	% ADDED
+  Suppose that $\alpha \in (1,2).$
+  % END ADDED
   The non-linear delay equation
@@
     G( \theta)
-	= \int_0^\theta \exp\Big\{ - \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1} })^{\gamma_0 - 1}\frac{du}{u} \Big\} dr,
+    = \int_0^\theta \exp\Big\{ - \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1} })^{\alpha - 1}\frac{du}{u} \Big\} dr,
     \quad \theta \geq 0,
@@
     G(\theta)
-	= \Big(\frac{1}{1+\theta^{-(\gamma_0 - 1)}}\Big)^{\frac{1}{\gamma_0 - 1}},
+    = \Big(\frac{1}{1+\theta^{-(\alpha - 1)}}\Big)^{\frac{1}{\alpha - 1}},
     \quad \theta \geq 0.
@@
 Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to the measure $\mu$.	
+% ADDED
+However, when $p \in (0,1)$, $\|\cdot\|_{\mu; p}$ is not a norm.
+% END ADDED
+
 In order to prove the above lemma, we will need the following:
@@
   \begin{align}
+    % ADDED
+    \label{eq:Gronwall_inequlity}
+    % END ADDED
     F(\theta)
-	\leq C \int_0^\theta \|  F(ru^{ \frac{1}{\gamma_0- 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0.
+    \leq C \int_0^\theta \|  F(ru^{ \frac{1}{\alpha - 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0.
   \end{align}
@@
 
+% CHANGES	
+% \begin{proof}
+%   We prove this lemma by contradiction.
+%   Assume that
+%   \begin{align}\label{eq: definition of rho}
+%     \rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
+%   \end{align}
+%   Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
+%   We first claim that
+%   \begin{align}
+%     F_\alpha (\theta)
+%     \leq C(\rho C + 1) \theta,
+%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
+%   \end{align}
+%   In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
+%   \begin{align}
+%     F_\alpha (\theta)
+%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; (\gamma_0 - 1)} dr
+%     \leq C\int_\alpha^{\alpha + \theta} \|Cru^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\&\leq C^2 (\alpha + \theta) \theta \|u^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
+%     \leq C(\rho C + 1) \theta.
+%   \end{align}
+%   We then claim that, if
+%   \begin{align}\label{eq: FATLC}
+%     F_\alpha (\theta)
+%     \leq C^k(\rho C + 1) \theta^k,
+%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
+%   \end{align}
+%   for some $k \in \mathbb N$, then
+%   \begin{align}
+%     F_\alpha (\theta)
+%     \leq C^{k+1}(\rho C + 1) \theta^{k+1},
+%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
+%   \end{align}
+%   In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
+%   \begin{align}
+%     F_\alpha (\theta)
+%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr\\
+%     &=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) \big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\& =  C\int_0^\theta \|F_{\alpha u^{1/(\gamma_0 - 1)}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} }
+%     \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
+%     \\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
+%   \end{align}
+%   Therefore, by induction, we have
+% \begin{align}
+%   F_\alpha (\theta)
+%   \leq C^k(\rho C + 1) \theta^k,
+%   \quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
+% \end{align}
+%	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
+%	This, however, contradicts \eqref{eq: definition of rho}.
+% \end{proof}
 \begin{proof}
-    We prove this lemma by contradiction.
-	Assume that
-\begin{align}\label{eq: definition of rho}
-	\rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
-\end{align}
-	Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
-	We first claim that
-\begin{align}
-	F_\alpha (\theta)
-	\leq C(\rho C + 1) \theta,
-	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-\end{align}
-	In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
-\begin{align}
-	F_\alpha (\theta)
-	&\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; (\gamma_0 - 1)} dr
-	\leq C\int_\alpha^{\alpha + \theta} \|Cru^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-	\\&\leq C^2 (\alpha + \theta) \theta \|u^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-	\leq C(\rho C + 1) \theta.
-\end{align}
-	We then claim that, if
-\begin{align}\label{eq: FATLC}
-	F_\alpha (\theta)
-	\leq C^k(\rho C + 1) \theta^k,
-	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
-\end{align}
-	for some $k \in \mathbb N$, then
-\begin{align}
-	F_\alpha (\theta)
-	\leq C^{k+1}(\rho C + 1) \theta^{k+1},
-	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-	\end{align}
-	In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
-\begin{align}
-	F_\alpha (\theta)
-	&\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}})
-	\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr\\
-   &=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big )
-	\big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-	\\& =  C\int_0^\theta \|F_{\alpha u^{1/(\gamma_0 - 1)}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-  \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} }
-	\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-	\\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-\\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
-\end{align}
-	Therefore, by induction, we have
-\begin{align}
-	F_\alpha (\theta)
-	\leq C^k(\rho C + 1) \theta^k,
-	\quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
-\end{align}
-	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
-	This, however, contradicts \eqref{eq: definition of rho}.
+  We claim that for each $k \in \mathbb N$, we have
+  \begin{align}
+    \label{eq:upperbound_for_F}
+    F(\theta) \leq \frac{C^k \theta^k}{k!},
+    \quad \theta \geq 0.
+  \end{align}
+  In fact, when $k = 1$ this is trival. Now if \eqref{eq:upperbound_for_F} is true for a fixed $k \in \mathbb N$, then from
+  \begin{align}
+    &F(\theta)
+      \leq C \int_0^\theta \left\|  F\left(ru^{ \frac{1}{\alpha - 1}  }\right)\right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+      \leq C \int_0^\theta \left\|  \frac{1}{k!}\left(Cru^{ \frac{1}{\alpha - 1}  } \right)^k \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+    \\ &\leq \frac{C^{k+1}}{k!} \left(\int_0^\theta r^k dr\right) \cdot \left\|u^{\frac{k}{\alpha - 1}} \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
+  \end{align}
+  we have that \eqref{eq:upperbound_for_F} is true for $k+1$. 
+  Therefore, by induction, \eqref{eq:upperbound_for_F} is true for all $k \in \mathbb N$.
+
+  Taking $k \to \infty$ in \eqref{eq:upperbound_for_F}, we get that $F(\theta) = 0$ for each $\theta \geq 0$.
 \end{proof}
+% END CHANGES
 
 \begin{proof}[Proof of Lemma \ref{lem: characterize the general Mittag-Leffler distribution}]
-
 	We first verify that \eqref{eq: solution for the equation}  is a solution of \eqref{eq: equation for the distribution}.
-	In fact, if $G(\theta) = (\frac{1}{1+ \theta^{-(\gamma_0 - 1)}})^{\frac{1}{\gamma_0 - 1}}$, then
-\begin{align}
-	 & \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\frac{du}{u}\Big\} dr
-	\\&\quad = \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \int_0^1 \frac{du}{u+r^{-(\gamma_0 - 1)}} \Big\} dr
-	= \int_0^\theta \exp\Big\{- \frac{\gamma_0} {\gamma_0 - 1} \log\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} } \Big\} dr
-	\\&\quad = \int_0^\theta \big(\frac{1+r^{-(\gamma_0 - 1)}}{r^{-(\gamma_0 - 1)} }\big)^{- \frac{\gamma_0} {\gamma_0 - 1}} dr
-	= \int_0^\theta \big( 1 + r^{ - ( \gamma_0 - 1 ) } \big)^{- \frac{\gamma_0} {\gamma_0 - 1}} r^{-\gamma_0} dr
+	In fact, if $G(\theta) = (\frac{1}{1+ \theta^{-(\alpha - 1)}})^{\frac{1}{\alpha - 1}}$, then
+  \begin{align}
+    & \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1}\frac{du}{u}\Big\} dr
+    \\ & \quad = \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \int_0^1 \frac{du}{u+r^{-(\alpha - 1)}} \Big\} dr
+         = \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \log \frac {1+r^{-(\alpha - 1)}} {r^{-(\alpha - 1)} } \Big\} dr
+    \\ & \quad = \int_0^\theta \big(\frac{1+r^{-(\alpha - 1)}}{r^{-(\alpha - 1)} }\big)^{- \frac{\alpha} {\alpha - 1}} dr
+         = \int_0^\theta \big( 1 + r^{ - ( \alpha - 1 ) } \big)^{- \frac{\alpha} {\alpha - 1}} r^{-\alpha} dr
          = G(\theta).
@@
     \frac{d}{d\theta}G(\theta)
-	&= - \frac{1}{\gamma_0 - 1} \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{1}{\gamma_0 - 1} - 1} \frac{d}{d\theta} \theta^{-(\gamma_0 - 1)}
-	\\& =  \big(1+\theta^{-(\gamma_0 - 1)}\big)^{- \frac{\gamma_0}{\gamma_0 - 1} } \theta^{-\gamma_0}.
+    &= - \frac{1}{\alpha - 1} \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{1}{\alpha - 1} - 1} \frac{d}{d\theta} \theta^{-(\alpha - 1)}
+    \\& =  \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{\alpha}{\alpha - 1} } \theta^{-\alpha}.
 \end{align}
@@
     F(\theta)
-	:= |G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|^{\frac{1}{\gamma_0 - 1}},
+    := |G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|^{\frac{1}{\alpha - 1}},
     \quad \theta \geq 0.
   \end{align}
-	We claim that the non-negative function $F$ satisfies
-	the following inequality:
-\begin{align}\label{eq: inequality of F(theta)}
-	F(\theta)
-	\leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\gamma_0 - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr, \quad \theta \geq 0,
-\end{align}
-	for some constant $C_0 > 0$.
-	In fact, by the $L^p$ Minkowski inequality with $p = \frac{1}{\gamma_0 - 1} > 1$, we have
-\begin{align}
-	&|G(\theta)^{\gamma_0 - 1} - G_0(\theta)^{\gamma_0 - 1}|
-	\\&\quad = \Big| \|e^{-\gamma_0\int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}} - \|e^{-\gamma_0\int_0^1 G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}} \Big|
-	\\ & \quad \leq \| e^{-\gamma_0\int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} - e^{-\gamma_0\int_0^1 G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}}
-	\\ & \quad \leq \Big\| \gamma_0\int_0^1 G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} - \gamma_0\int_0^1 G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\gamma_0 - 1}}
-	\\ & \quad \leq \gamma_0 \Bigg( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} - G_0(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}| \frac{du}{u} \Big)^{\frac{1}{\gamma_0 - 1}} dr \Bigg)^{\gamma_0 - 1}.
-\end{align}
-	In other words, there is a constant $C_0:= \gamma_0^{\frac{1}{\gamma_0 - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
+  % CHANGES
+	% We claim that the non-negative function $F$ satisfies the following inequality:
+  % \begin{align}\label{eq: inequality of F(theta)}
+    % F(\theta)
+    % \leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\alpha - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0,
+  % \end{align}
+	% for some constant $C_0 > 0$.
+  We claim that the non-negative function $F$ satisfies the inequality \eqref{eq:Gronwall_inequlity} with $C = \alpha ^{1/(\alpha - 1)}$.
+  % END CHANGES
+	In fact, by the $L^p$ Minkowski inequality with $p = \frac{1}{\alpha - 1} > 1$, we have
+  \begin{align}
+    &|G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|
+    \\&\quad = \Big| \|e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta} dr; \frac{1}{\alpha - 1}} - \|e^{-\alpha \int_0^1 G_0(ru^{ \frac{1} {\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\alpha - 1}} \Big|
+    \\ & \quad \leq \| e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} - e^{-\alpha \int_0^1 G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1} {\alpha - 1}}
+    \\ & \quad \leq \Big\| \alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u} - \alpha \int_0^1 G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0<r<\theta}dr;\frac{1} {\alpha - 1}}
+    \\ & \quad \leq \alpha \Bigg( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} - G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1}| \frac{du}{u} \Big)^{\frac{1}{\alpha - 1}} dr \Bigg)^{\alpha - 1}.
+  \end{align}
+  % In other words, there is a constant $C_0:= \alpha^{\frac{1}{\alpha - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
+  This implies the claim.
+
   On the other hand, according to \eqref{eq: equation for the distribution}, we have that $G(\theta) \leq \theta$ and $G_0(\theta) \leq \theta$.
   Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
-	Therefore, according to Lemma \ref{lem: F is zero} and \eqref{eq: inequality of F(theta)}, we have $F \equiv 0$ as desired.
+  % Therefore, according to Lemma \ref{lem: F is zero} and \eqref{eq: inequality of F(theta)}, we have $F \equiv 0$ as desired.
+  Therefore, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
 \end{proof}
-
+% END MINER CHANGES: I changed all \gamma_0 here to \alpha without further noticing.
+\end{comment}
+% END MOVED AND MODIFIED BELOW
+
+% ** Proof of main Theorem 3
 \subsection{Proof of Theorem \ref{thm: main theorem}(3)}
@@
 \end{align}
-	From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have
+% From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have
+From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have almost surely
 \begin{align}
@@
 \end{align}
-	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have
+% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have
+From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have almost surely
 \begin{align}
@@
 \end{align}
-	From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have
+% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have
+From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have almost surely
 \begin{align}\label{eq: upper bound for J'_G}
 	J'_G(t,r,\xi)
-	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} (ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
-	\\&\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
-	\\&=: c_4 \cdot r^{\gamma_0 - 1},
+	& \leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} (ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
+	\\ &\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
+	\\ &=: c_4 \cdot r^{\gamma_0 - 1},
        \quad t\geq 0, r\geq 0.
@@
 
+% ADDED
+For the rest of the proof, we use the following notations:
+If $f$ is a measurable function which is $L^p$ integrable on the measure space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
+\begin{align}
+	\|f\|_{\mu;p}
+	:= \Big(\int_{S} |f|^p d\mu \Big)^{\frac{1}{p}}.
+\end{align}
+Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to the measure $\mu$.	
+However, when $p \in (0,1)$, $\|\cdot\|_{\mu; p}$ is not a norm.
+% END ADDED
+
 Step 2: We will show that, for each $t\geq 0, \theta \geq 0,$ and $x\in E$
@@
 	&| G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
-	\\&\quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x)
-	+c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x),
+	\\ & \quad \leq I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) + c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x),
 \end{align}
@@
 	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
-	\\&\quad \leq \Big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad \leq I_1(t,\theta,x) + \Big\| \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} -
-	\\&\quad \qquad \qquad \qquad \qquad \qquad \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad \leq I_1(t,\theta,x) + \Big\| \|  (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} ( e^{-J_G(r)} - e^{-J_g(t,r,\xi)} )  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1}\Big\| \|  J_G(r) -J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1} I_2(t,\theta,x) +c_f^{\gamma_0 - 1} I_3(t,\theta,x)+c_f^{\gamma_0 - 1} I_4(t,\theta,x).
-\end{align}	
+	\\ & \quad \leq \Big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\ & \quad \leq I_1(t,\theta,x) + \Big\| \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} -
+	\\ & \quad \qquad \qquad \qquad \qquad \qquad \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\ & \quad \leq I_1(t,\theta,x) + \Big\| \|  (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} ( e^{-J_G(r)} - e^{-J_g(t,r,\xi)} )  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\ & \quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1}\Big\| \|  J_G(r) -J_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\ & \quad \leq I_1(t,\theta,x) + c_f^{\gamma_0 - 1} I_2(t,\theta,x) +c_f^{\gamma_0 - 1} I_3(t,\theta,x)+c_f^{\gamma_0 - 1} I_4(t,\theta,x).
+\end{align}
+
 Step 3: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
-	Notice that,
-	by \eqref{eq:q(t,x,y)},
+% Notice that, by \eqref{eq:q(t,x,y)},
+Notice that, by \eqref{eq:q(t,x,y)} and since $\langle f,\phi^* \rangle_m = 1$,
 \begin{align}
@@
 \begin{align}
-	&J_G(r) - J'_G(t,r,\xi)
-	\\&\quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- (\gamma_0 - 1) \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} tu\eta_{ut}^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}
-	\\&\quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}.
-\end{align}
-	Also notice that,
-	according to \eqref{eq: upper bound for G}, for each $r \geq 0$, $u\in [0,1]$ and $x\in E$,
-\begin{align}
-	&\big| \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \frac{1}{u} \big|
-	\\&\quad \leq \frac{\gamma_0}{u} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big|\big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \big|
-	\\&\quad \leq \gamma_0r^{\gamma_0 - 1} \big( 1+ \big\|C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big\|_\infty \big).
+	& J_G(r) - J'_G(t,r,\xi)
+	\\ & \quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- (\gamma_0 - 1) \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} tu\eta_{ut}^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}
+	\\ & \quad = \int_0^1 \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(\xi_{(1-u)t}) \frac{du}{u}.
+\end{align}
+Also notice that, according to \eqref{eq: upper bound for G}, for each $r \geq 0$, $u\in [0,1]$ and $x\in E$,
+\begin{align}
+	& \big| \gamma_0 G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \frac{1}{u} \big|
+	\\ & \quad \leq \frac{\gamma_0}{u} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big|\big( 1- C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big)(x) \big|
+	\\ & \quad \leq \gamma_0r^{\gamma_0 - 1} \big( 1+ \big\|C_X^{-1}\mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} \big\|_\infty \big).
 \end{align}
@@
 since it is a bounded Borel function on $E\times (0,1) \times [0,\infty)$.
-	Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process},  \eqref{eq: differences between J'_G and J'_g} and
-    the definitions of
-$M(r,x), M(r)$ and $C_X$, we have
+Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process}, \eqref{eq: differences between J'_G and J'_g} and the definitions of $M(r,x), M(r)$ and $C_X$, we have
 \begin{align}\label{eq: limsup of J_G - J'_g}
 	&\limsup_{t\to \infty} \| J_G'(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{\phi};\frac{1}{\gamma_0 - 1}}
-	\\&\quad\leq  \gamma_0 C_X^{-1} \int_0^1 \big\langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} M(ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}, \phi\phi^* \big\rangle_m \frac{du}{u}
-	\\&\quad\leq  \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}.
-\end{align}
-	We now recall the reverse Fatou's lemma in $L^p$ with $p\geq 1$: Let $(f_n)_{n\in \mathbb N}$ be a sequence of non-negative measurable functions defined on a measure space $S$ with $\sigma$-finite measure $\mu$.
+	\\& \quad \leq  \gamma_0 C_X^{-1} \int_0^1 \big\langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} M(ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}, \phi\phi^* \big\rangle_m \frac{du}{u}
+	\\& \quad \leq  \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}.
+\end{align}
+We recall the reverse Fatou's lemma in $L^p$ with $p\geq 1$: Let $(f_n)_{n\in \mathbb N}$ be a sequence of non-negative measurable functions defined on a measure space $S$ with $\sigma$-finite measure $\mu$.
 If there exists a non-negative $L^p(\mu)$-integrable function $g$ on $S$ such that $f_n \leq g$ for all $n$, then according to the classical reverse Fatou's lemma, we have
@@
 \end{align}
-	Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
+% Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
+Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g} to have that
 \begin{align}
@@
 \begin{align}
-	&M(r,x)^{\gamma_0 - 1}
-	=\limsup_{t\to \infty} M(t,r,x)^{\gamma_0 - 1}
+	& M(r,x)^{\gamma_0 - 1}
+	= \limsup_{t\to \infty} M(t,r,x)^{\gamma_0 - 1}
 	= \limsup_{t\to \infty}|G(r)^{\gamma_0 - 1} - g(t,r,x)^{\gamma_0 - 1}|
-	\\&\quad \leq \limsup_{t\to \infty} \big( I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) +c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x) \big)
-	\\& \quad = c_f^{\gamma_0 - 1} \limsup_{t\to \infty} I_3(t,\theta ,x)
+	\\ & \quad \leq \limsup_{t\to \infty} \big( I_1(t,\theta,x) +c^{\gamma_0 - 1}_f I_2(t,\theta,x) +c^{\gamma_0 - 1}_f I_3(t,\theta,x) + c^{\gamma_0 - 1}_f I_4(t,\theta,x) \big)
+	\\ & \quad = c_f^{\gamma_0 - 1} \limsup_{t\to \infty} I_3(t,\theta ,x)
        \leq c_f^{\gamma_0 - 1} \gamma_0 \Big(  \int_0^\theta  \big\| M(r u^{\frac{1}{\gamma_0 - 1}}) \big\|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1}.
@@
 According to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
-	Finally, by the definition of $M$,  $M\equiv 0$ implies the desired assertion \eqref{eq: we only need to proof this}.
-
+% Finally, by the definition of $M$,  $M\equiv 0$ implies the desired assertion \eqref{eq: we only need to proof this}.
+
+Step 8. Finally, $M \equiv 0$ clearly implies that $\lim_{t\to \infty} I_3(t,\theta, x) = 0$, and thus completes the verification of \eqref{eq: we only need to proof this}.
+
+% MOVED AND MODIFIED FROM ABOVE
+\appendix
+\section{}
+\subsection{Examples}
+TBD
+\subsection{Analytical result}
+\label{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}
+In the proof of Theorem \ref{thm: main theorem}(3), we have used the following notations which we recall here:
+If $f$ is a measurable function which is $L^p$ integrable on the measure space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
+\begin{align}
+	\|f\|_{\mu;p}
+	:= \Big(\int_{S} |f|^p d\mu \Big)^{\frac{1}{p}}.
+\end{align}
+Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to the measure $\mu$.	
+However, when $p \in (0,1)$, $\|\cdot\|_{\mu; p}$ is not a norm.
+
+The following analytical results are used in the proof of Theorem \ref{thm: main theorem} (3). 
+\begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
+  Suppose that $\alpha \in (1,2).$
+  The non-linear delay equation
+  \begin{align} \label{eq: equation for the distribution}
+    G( \theta)
+    = \int_0^\theta \exp\Big\{ - \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1} })^{\alpha - 1}\frac{du}{u} \Big\} dr,
+    \quad \theta \geq 0,
+  \end{align}
+	has a unique solution:
+  \begin{align}\label{eq: solution for the equation}
+    G(\theta)
+    = \Big(\frac{1}{1+\theta^{-(\alpha - 1)}}\Big)^{\frac{1}{\alpha - 1}},
+    \quad \theta \geq 0.
+  \end{align}
+\end{lem}
+
+\begin{lem}\label{lem: F is zero}
+	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
+  \begin{align}
+    % ADDED
+    \label{eq:Gronwall_inequlity}
+    % END ADDED
+    F(\theta)
+    \leq C \int_0^\theta \|  F(ru^{ \frac{1}{\alpha - 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0.
+  \end{align}
+	Then $F \equiv 0$.
+\end{lem}
+
+% CHANGES	
+% \begin{proof}
+%   We prove this lemma by contradiction.
+%   Assume that
+%   \begin{align}\label{eq: definition of rho}
+%     \rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
+%   \end{align}
+%   Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
+%   We first claim that
+%   \begin{align}
+%     F_\alpha (\theta)
+%     \leq C(\rho C + 1) \theta,
+%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
+%   \end{align}
+%   In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
+%   \begin{align}
+%     F_\alpha (\theta)
+%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; (\gamma_0 - 1)} dr
+%     \leq C\int_\alpha^{\alpha + \theta} \|Cru^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\&\leq C^2 (\alpha + \theta) \theta \|u^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
+%     \leq C(\rho C + 1) \theta.
+%   \end{align}
+%   We then claim that, if
+%   \begin{align}\label{eq: FATLC}
+%     F_\alpha (\theta)
+%     \leq C^k(\rho C + 1) \theta^k,
+%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
+%   \end{align}
+%   for some $k \in \mathbb N$, then
+%   \begin{align}
+%     F_\alpha (\theta)
+%     \leq C^{k+1}(\rho C + 1) \theta^{k+1},
+%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
+%   \end{align}
+%   In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
+%   \begin{align}
+%     F_\alpha (\theta)
+%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr\\
+%     &=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) \big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\& =  C\int_0^\theta \|F_{\alpha u^{1/(\gamma_0 - 1)}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} }
+%     \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
+%     \\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
+%     \\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
+%   \end{align}
+%   Therefore, by induction, we have
+% \begin{align}
+%   F_\alpha (\theta)
+%   \leq C^k(\rho C + 1) \theta^k,
+%   \quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
+% \end{align}
+%	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
+%	This, however, contradicts \eqref{eq: definition of rho}.
+% \end{proof}
+\begin{proof}
+  [Proof of Lemma \ref{lem: F is zero}]
+  We claim that for each $k \in \mathbb N$, we have
+  \begin{align}
+    \label{eq:upperbound_for_F}
+    F(\theta) \leq \frac{C^k \theta^k}{k!},
+    \quad \theta \geq 0.
+  \end{align}
+  In fact, when $k = 1$ this is trival. Now if \eqref{eq:upperbound_for_F} is true for a fixed $k \in \mathbb N$, then from
+  \begin{align}
+    &F(\theta)
+      \leq C \int_0^\theta \left\|  F\left(ru^{ \frac{1}{\alpha - 1}  }\right)\right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+      \leq C \int_0^\theta \left\|  \frac{1}{k!}\left(Cru^{ \frac{1}{\alpha - 1}  } \right)^k \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+    \\ &\leq \frac{C^{k+1}}{k!} \left(\int_0^\theta r^k dr\right) \cdot \left\|u^{\frac{k}{\alpha - 1}} \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
+  \end{align}
+  we have that \eqref{eq:upperbound_for_F} is true for $k+1$. 
+  Therefore, by induction, \eqref{eq:upperbound_for_F} is true for all $k \in \mathbb N$.
+
+  Taking $k \to \infty$ in \eqref{eq:upperbound_for_F}, we get that $F(\theta) = 0$ for each $\theta \geq 0$.
+\end{proof}
+% END CHANGES
+
+\begin{proof}[Proof of Lemma \ref{lem: characterize the general Mittag-Leffler distribution}]
+	We first verify that \eqref{eq: solution for the equation}  is a solution of \eqref{eq: equation for the distribution}.
+	In fact, if $G(\theta) = (\frac{1}{1+ \theta^{-(\alpha - 1)}})^{\frac{1}{\alpha - 1}}$, then
+  \begin{align}
+    & \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1}\frac{du}{u}\Big\} dr
+    \\ & \quad = \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \int_0^1 \frac{du}{u+r^{-(\alpha - 1)}} \Big\} dr
+         = \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \log \frac {1+r^{-(\alpha - 1)}} {r^{-(\alpha - 1)} } \Big\} dr
+    \\ & \quad = \int_0^\theta \big(\frac{1+r^{-(\alpha - 1)}}{r^{-(\alpha - 1)} }\big)^{- \frac{\alpha} {\alpha - 1}} dr
+         = \int_0^\theta \big( 1 + r^{ - ( \alpha - 1 ) } \big)^{- \frac{\alpha} {\alpha - 1}} r^{-\alpha} dr
+         = G(\theta).
+  \end{align}
+	The last equality is due to $G(0) = 0$ and
+  \begin{align}
+    \frac{d}{d\theta}G(\theta)
+    &= - \frac{1}{\alpha - 1} \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{1}{\alpha - 1} - 1} \frac{d}{d\theta} \theta^{-(\alpha - 1)}
+    \\& =  \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{\alpha}{\alpha - 1} } \theta^{-\alpha}.
+\end{align}
+
+Now assume that $G_0$ is another solution to the equation \eqref{eq: equation for the distribution}, we then only have to show that $G_0 = G$.
+This can be done by showing that $F(\theta) = 0$ where
+  \begin{align}
+    F(\theta)
+    := |G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|^{\frac{1}{\alpha - 1}},
+    \quad \theta \geq 0.
+  \end{align}
+  % CHANGES
+	% We claim that the non-negative function $F$ satisfies the following inequality:
+  % \begin{align}\label{eq: inequality of F(theta)}
+    % F(\theta)
+    % \leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\alpha - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0,
+  % \end{align}
+	% for some constant $C_0 > 0$.
+  We claim that the non-negative function $F$ satisfies the inequality \eqref{eq:Gronwall_inequlity} with $C = \alpha ^{1/(\alpha - 1)}$.
+  % END CHANGES
+	In fact, by the $L^p$ Minkowski inequality with $p = \frac{1}{\alpha - 1} > 1$, we have
+  \begin{align}
+    &|G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|
+    \\&\quad = \Big| \|e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta} dr; \frac{1}{\alpha - 1}} - \|e^{-\alpha \int_0^1 G_0(ru^{ \frac{1} {\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\alpha - 1}} \Big|
+    \\ & \quad \leq \| e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} - e^{-\alpha \int_0^1 G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1} {\alpha - 1}}
+    \\ & \quad \leq \Big\| \alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u} - \alpha \int_0^1 G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0<r<\theta}dr;\frac{1} {\alpha - 1}}
+    \\ & \quad \leq \alpha \Bigg( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} - G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1}| \frac{du}{u} \Big)^{\frac{1}{\alpha - 1}} dr \Bigg)^{\alpha - 1}.
+  \end{align}
+  % In other words, there is a constant $C_0:= \alpha^{\frac{1}{\alpha - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
+  This implies the claim.
+
+  On the other hand, according to \eqref{eq: equation for the distribution}, we have that $G(\theta) \leq \theta$ and $G_0(\theta) \leq \theta$.
+  Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
+  % Therefore, according to Lemma \ref{lem: F is zero} and \eqref{eq: inequality of F(theta)}, we have $F \equiv 0$ as desired.
+  Therefore, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
+\end{proof}
+% END MINER CHANGES: I changed all \gamma_0 here to \alpha without further noticing.
+% END MOVED AND MODIFIED FROM ABOVE
+
+\subsection*{Acknowledgment:} 
+We thank the referees for helpful comments on the first version of this paper.
+
+% * Bibliography
 \begin{thebibliography}{10}
@@
 	Birkh{\"a}user Boston, Inc., Boston, MA, 1983.
-	\MR{701538}
+	% \MR{701538}
 
 \bibitem{AthreyaNey1974Functionals}
-	Athreya, K.~B. and Ney, P.~E.:
+	% Athreya, K.~B. and Ney, P.~E.:
+	Athreya, K. and Ney, P.:
 	\emph{Functionals of critical multitype branching processes}.
-	Ann. Probability \textbf{2} (1974), 339--343. \MR{0356264}
+	Ann. Probability \textbf{2} (1974), 339--343. 
+  % \MR{0356264}
 
@@
 	Springer-Verlag, New York-Heidelberg, 1972.
-	\MR{0373040}
+	% \MR{0373040}
 
 \bibitem{BinghamGoldieTeugels1989Regular}
-	Bingham, N.~H., Goldie, C.~M. and Teugels J.~L.:
+	% Bingham, N.~H., Goldie, C.~M. and Teugels J.~L.:
+	Bingham, N., Goldie, C. and Teugels J.:
 	\emph{Regular variation}.
@@
 	Cambridge University Press, Cambridge, 1989.
-	\MR{1015093}
+	% \MR{1015093}
 
 \bibitem{Borovkov1989Method}
-	Borovkov, K.~A.:
+	% Borovkov, K.~A.:
+	Borovkov, K.:
 	\emph{A method for the proof of limit theorems for branching processes}.
@@
 	translation in Theory Probab. Appl. \textbf{33} (1988), no. 1, 105–113.
-	\MR{0939993}
+	% \MR{0939993}
 
 \bibitem{EckhoffKyprianouWinkel2015Spines}
-	Eckhoff, M., Kyprianou, A.~E., Winkel, M.:
+	% Eckhoff, M., Kyprianou, A.~E., Winkel, M.:
+	Eckhoff, M., Kyprianou, A. and Winkel, M.:
 	\emph{Spines, skeletons and the strong law of large numbers for superdiffusions.}
 	Ann. Probab. \textbf{43} (2015), no. 5, 2545–2610.
-	\MR{3395469}
+	% \MR{3395469}
 
 \bibitem{EnglanderKyprianou2004Local}
-	Engländer, J., Kyprianou, A.~E.:
+	% Engländer, J., Kyprianou, A.~E.:
+	Engländer, J. and Kyprianou, A.:
 	\emph{Local extinction versus local exponential growth for spatial branching processes.}
 	Ann. Probab. \textbf{32} (2004), no. 1A, 78–99.
-	\MR{2040776}
+	% \MR{2040776}
 
 \bibitem{EvansPerkins1990Measure-valued}
-	Evans, S.~N., Perkins, E.:
+	% Evans, S.~N., Perkins, E.:
+	Evans, S. and Perkins, E.:
 	\emph{Measure-valued Markov branching processes conditioned on nonextinction.}
 	Israel J. Math. \textbf{71} (1990), no. 3, 329–337.
-	\MR{1088825}
+	% \MR{1088825}
 
 \bibitem{GoldsteinHoppe1978Critical}
-	Goldstein, M.~I., Hoppe, F.~M.:
+	% Goldstein, M.~I., Hoppe, F.~M.:
+	Goldstein, M. and Hoppe, F.:
 	\emph{Critical multitype branching processes with infinite variance.}
 	J. Math. Anal. Appl. \textbf{65} (1978), no. 3, 675–686.
-	\MR{0510478}
+	% \MR{0510478}
 
 \bibitem{Harris2002The-theory}
-	Harris, T. E.:
+	% Harris, T. E.:
+	Harris, T.:
 	\emph{The theory of branching processes.}
 	Die Grundlehren der Mathematischen Wissenschaften, Bd. 119 Springer-Verlag, Berlin; Prentice-Hall, Inc., Englewood Cliffs, N.J. 1963.
-	\MR{0163361}
+	% \MR{0163361}
 
 \bibitem{IyerLegerPego2015Limit}
-	Iyer, G., Leger, N., Pego, R.~L.:
+	% Iyer, G., Leger, N., Pego, R.~L.:
+	Iyer, G., Leger, N. and Pego, R.:
 	\emph{Limit theorems for Smoluchowski dynamics associated with critical continuous-state branching processes.}
 	Ann. Appl. Probab. \textbf{25} (2015), no. 2, 675–713.
-	\MR{3313753}
+	% \MR{3313753}
 
@@
 	J. Math. Anal. Appl. \textbf{19} (1967), 409--430.
-	\MR{0212895}
+	% \MR{0212895}
 
@@
 	Teor. Verojatnost. i Primenen. \textbf{11} (1966), 579--611.
-	\MR{0207052}
+	% \MR{0207052}
 
@@
 	Tohoku Math. J. (2) \textbf{60} (2008), no.~4, 527--547.
-	\MR{2487824}
+	% \MR{2487824}
 
 \bibitem{Kolmogorov1938Zur-losung}
-	Kolmogorov, A.~N.:
+	% Kolmogorov, A.~N.:
+	Kolmogorov, A.:
 	\emph{Zur l{\"o}sung einer biologischen aufgabe.}
@@
 \bibitem{Kyprianou2014Fluctuations}
-	Kyprianou, A.~E.:
+	% Kyprianou, A.~E.:
+	Kyprianou, A.:
 	\emph{Fluctuations of Lévy processes with applications.}
 	Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
-	\MR{3155252}
+	% \MR{3155252}
 
 \bibitem{Kyprianou2008Continuous}
-	Kyprianou, A.~E., Pardo, J. C.:
+	% Kyprianou, A.~E., Pardo, J. C.:
+	Kyprianou, A. and Pardo, J.:
 	\emph{Continuous-state branching processes and self-similarity.}
 	J. Appl. Probab. \text{45} (2008), no. 4, 1140–1160.
-	\MR{2484167}
+	% \MR{2484167}
 
@@
 	Probability and its Applications (New York), Springer, Heidelberg, 2011.
-	\MR{2760602}
+	% \MR{2760602}
 
@@
 	J. Appl. Probab. \textbf{46} (2009), no.~2, 479--496.
-	\MR{2535827}
+	% \MR{2535827}
 
 \bibitem{Pakes2010Critical}
-	Pakes, A.~G.:
+	% Pakes, A.~G.:
+	Pakes, A.:
 	\emph{Critical {M}arkov branching process limit theorems allowing infinite variance.}
 	Adv. in Appl. Probab. \textbf{42} (2010), no.~2, 460--488.
-	\MR{2675112}
+	% \MR{2675112}
 
@@
   \emph{An invariance principle for branching diffusions in bounded domains.} 
-	\ARXIV{1512.00031}
+  Probab. Theory Related Fields 173 (2019), no. 3-4, 999–1062.
+
+	% Powell, E.:
+	% \emph{An invariance principle for branching diffusions in bounded domains.}
+	% \ARXIV{1512.00031}
 
@@
   \emph{A 2-spine decomposition of the critical Galton-Watson tree and a probabilistic proof of Yaglom's theorem.} 
-	\ARXIV{1706.07125}
+  Electron. Commun. Probab. 23 (2018), Paper No. 42, 12 pp.
+
+	% Ren, Y.-X., Song, R. and Sun, Z.:
+	% \emph{A 2-spine decomposition of the critical Galton-Watson tree and a probabilistic proof of Yaglom's theorem.}
+	% \ARXIV{1706.07125}
 
 \bibitem{RenSongSun2017Spine}
-	\bysame:
+  Ren, Y.-X., Song, R. and Sun, Z.: 
   \emph{Spine decompositions and limit theorems for a class of critical superprocesses.}
-	\ARXIV{1711.09188}
+  Acta Appl. Math. (2019). https://doi.org/10.1007/s10440-019-00243-7
+
+	% \bysame:
+	% \emph{Spine decompositions and limit theorems for a class of critical superprocesses.}
+	% \ARXIV{1711.09188}
 
@@
 	Illinois J. Math. \textbf{59} (2015), no.~1, 235--276.
-	\MR{3459635}
+	% \MR{3459635}
 
 \bibitem{RenSongZhang2017Central}
-	\bysame:
+	% \bysame:
+	Ren, Y.-X., Song, R. and Zhang, R.:
 	\emph{Central limit theorems for supercritical branching nonsymmetric {M}arkov processes.}
 	Ann. Probab. \textbf{45} (2017), no.~1, 564--623.
-	\MR{3601657}
+	% \MR{3601657}
 
 \bibitem{RenYangZhao2014Conditional}
-	Ren, Y.-X., Yang, T., Zhao, G.-H.:
+	% Ren, Y.-X., Yang, T., Zhao, G.-H.:
+	Ren, Y.-X., Yang, T. and Zhao, G.:
 	\emph{Conditional limit theorems for critical continuous-state branching processes.}
 	Sci. China Math. \textbf{57} (2014), no. 12, 2577–2588.
-	\MR{3275407}
+	% \MR{3275407}
 
 \bibitem{Schaefer1974Banach}
-	Schaefer, H.~H.:
+	% Schaefer, H.~H.:
+	Schaefer, H.:
 	\emph{Banach lattices and positive operators.}
 	Die Grundlehren der mathematischen Wissenschaften, Band 215. Springer-Verlag, New York-Heidelberg, 1974.
-	\MR{0423039}
+	% \MR{0423039}
 
 \bibitem{Slack1968A-branching}
-	Slack, R.~S.:
+	% Slack, R.~S.:
+	Slack, R.:
 	\emph{A branching process with mean one and possibly infinite variance.}
 	Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{9} (1968), 139--145.
-	\MR{0228077}
+	% \MR{0228077}
 
 \bibitem{Slack1972Further}
-	\bysame: \emph{Further notes on branching processes with mean {$1$}.}
+	% \bysame: 
+	Slack, R.:
+  \emph{Further notes on branching processes with mean {$1$}.}
 	Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{25} (1972/73), 31–38.
-	\MR{0331539}
+	% \MR{0331539}
 
 \bibitem{Vatutin1977Limit}
-	Vatutin, V. A.:
+	% Vatutin, V. A.:
+	Vatutin, V.:
 	\emph{Limit theorems for critical multitype Markov branching processes with infinite second moments.}
 	Mat. Sb. (N.S.) \textbf{103(145)} (1977), no. 2, 253–264, 319.
-	\MR{0443115}
+	% \MR{0443115}
 
 \bibitem{Yaglom1947Certain}
-	Yaglom, A. M.:
+	% Yaglom, A. M.:
+	Yaglom, A.:
 	\emph{Certain limit theorems of the theory of branching random processes.}
 	Doklady Akad. Nauk SSSR (N.S.) \textbf{56} (1947). 795–798.
-	\MR{0022045}
+	% \MR{0022045}
 
 \bibitem{Zolotarev1957More}
-	Zolotarev, V. M.:
+	% Zolotarev, V. M.:
+	Zolotarev, V.:
 	\emph{More exact statements of several theorems in the theory of branching processes.}
 	Teor. Veroyatnost. i Primenen. \textbf{2} (1957), 256–266.
-	\MR{0096321}
+	% \MR{0096321}
 
 \end{thebibliography}
-
 \end{document}

### 2019-07-13 response.tex
change response.tex
change response.tex


change response.tex


change response.tex


change response.tex


change response.tex


change stableLimit.tex

@@
 \title
-[short title]
+[Response]
 {Response}
@@
 We are grateful to the referees' for their helpful comments.
-We have incorporated all the comments made by the referee.
+We have incorporated all the comments made by the referees.
 Here are the specific changes in response to the comments of the referees.
@@
 \item
+  p.4 l.4: It has to be They showd that.
 
+  {\it Changed as suggested.}
+\item
+  p.12 l.-10: Equation (2.4) is not only integrating both sides of (2.3), please explain more.
+
+  {\it We added some explanations before (2.4).}
+\item
+  p.20 l.4: In the first equality in the denominator it has to be $y^{1+\gamma(\zeta_s)}$.
+
+  {\it We think the referee means $y^{1+\gamma(\xi_s)}$.
+    Changed as suggested. }
+\item
+  p.20 l.10 eq.(3.11): You don't need to add $x$ in the norm of $\|\kappa \gamma \phi^{\gamma - 1}\|$.
+
+  {\it Done, as suggested.}
+\item
+  p.20 eq.(3.13) and p.21 in 9 more times: You missed an $m$ in $\left\langle v, \phi^* \right\rangle_m$.
+
+  {\it We added them back, as suggested.}
+\item
+  p.21 l.1: I will add: On the other hand, according to (3.2) and Proposition 3.2.
+
+  {\it Added, as suggested.}
+\item
+  p.23 l.-4: I will add then by Assumption 4, the spine representation, Campbell's formula...
+
+  {\it Changed, as suggested.}
+\item
+  p.25 eq.(3.27) and the next equation: I think that in your equations you missed a factorial, i.e.
+  \begin{align}
+    F_\alpha(\theta) 
+    \leq \frac{C^k}{k!} \left( \rho C+1 \right) \theta^k 
+  \end{align}
+  and
+  \begin{align}
+    F_\alpha(\theta) 
+    \leq \frac{C^{k+1}}{(k+1)!} \left( \rho  C+1 \right) \theta^{k+1}
+  \end{align}
+  The reason is that in your next computation, Page 25 line -4 and -3. You missed an $\frac{1}{k+1}$ from the integration. 
+  In this case, you need to add a $\frac{1}{k}$ on the last equation of page 25.
+
+  {\it We give a new proof of this Lemma which is shorter and better.}
+\item
+  p.29 in step 3: I will add: Notice that, by (1.20) and since $\left\langle f, \phi^* \right\rangle_m = 1$.
+
+  {\it Added, as suggested.}
+\end{enumerate}
+\section*{Response to the comments of Referee 2}
+\begin{enumerate}
+\item
+  {\bf (Important!)} General remark: There are a number of restrictive looking assumptions and thus it is crucial that the authors provide examples which are covered by the settings.
+  It is true that before Assumption 4, there is a reference to [24] `for a list of examples,' but this is somewhat hidden.
+  At least a brief summary of examples should be placed at a more visible spot that convinces the reader that the scope is not as restricted as it seems.
+
+  In [24] there are indeed 12 examples given. 
+  I would at least vaguely describe (some of) these, possibly in an appendix and definitely without proofs, just mentioning that details and proofs (of these being examples) are in [24].
+  If it is relegated to an appendix then somewhere at the beginning at a visible spot I'd refer the reader to the appendix.
+
+  {\it TBD.}
+\item
+  p.2 in the middle: define positively regular.
+
+  {\it We added the definition, as suggested.}
+\item
+  p.2. l.4: `They showed' instead `he showed'.
+
+  {\it Changed, as suggested.}
+\item
+  p.4. display.4: Explain how this fits into the general formula with the integral term.
+
+  {\it We explained it with more details.}
+\item
+  p.4. (1.16) and (1.17): perhaps mention that the limits do not depend on $x$ resp. $\mu$.
+
+  {\it Done, as suggested.}
+\item 
+  p.5 right after (1.18): Here $\beta$ has not been defined yet, only later in Assumption 4 it will be.
+
+  {\it We added a new sentence there which gives the function $\beta$.}
+\item
+  p.6 l.-15: Why isn't it $P_t^\beta \phi(x) = e^{\lambda t}\phi(x)$ and $P_t^{\beta*} \phi^*(x) = e^{\lambda t}\phi^*(x)$?
+
+  {\it Should be $P_t^\beta \phi(x) = e^{\lambda t}\phi(x)$ and $P_t^{\beta*} \phi^*(x) = e^{\lambda t}\phi^*(x)$. Corrected as suggested.}
+\item
+  p.6 paragraph after Assumption 2: The notation is a bit confusing.
+So $\phi$ is the principal eigenfunction for the motion with the potential $\beta$ but $\varphi$ is the same without the potential.
+  This should be made more clear.
+
+  {\it We added a paragraph after Assumption 2 to make this more clear. 
+    Note that in the new version the notation $\varphi$ and $\varphi^*$ is changed into $\widetilde \phi$ and $\widetilde \phi^*$, respectively.}
+\item
+  Same place ({\bf Important!}): It is not clear why $\varphi$ is well defined. 
+  Let's say $\xi$ is a diffusion process.
+  If $\mathcal L$ is the elliptic operator corresponding to it and $\lambda(\mathcal L)$ is its (generalized) principal eigenvalue then $\mathcal L - \lambda(\mathcal L)$ may or may not have a Green's function.
+  In the second case everything is fine and $\varphi$ is uniquely determined up to constant multiples; it is the ground state.
+  However, in the first case the cone of positive harmonic functions w.r.t. $\mathcal L - \lambda(\mathcal L)$ is not necessarily one dimensional. 
+  For example, if we know that $\xi$ is recurrent (and so $\lambda(\mathcal L) = 0$), then we are fine.
+  But when it is transient, uniqueness does not follow.
+
+  {\it Assumption 2 excluded the first case. We added a paragraph after Assumption 2 which explains that the principal eigenfunction without the potential is indeed well defined. 
+    Note that in the new version the notations $\varphi$ and $\varphi^*$ are changed into $\widetilde \phi$ and $\widetilde \phi^*$, respectively.}
+\item
+  p.8 l.6: I would rather say that the family of functions is just $(e^{\lambda t} \phi)_{t\geq 0}$, while $(e^{\lambda t} X_t(\phi))_{t\geq 0}$ is indeed the martingale.
+
+  {\it We restated this paragraph to make our intuitive explanations of the spine decomposition theorem more accurate. }
+\item
+  p.11 Lemma 2.4 and Corollary 2.5:
+  Why do we suddenly use $\alpha$ instead of $\gamma$?
+
+  {\it Should always use $\alpha$.
+     We changed several $\gamma$ into $\alpha$ there.} 
+\item
+  p.12: Explain how you get (2.4) from (2.3).
+
+  {\it We explained this with more details.}
+\item
+  p.13 top: Why not `$\mathcal N$ is a Poisson random measure on $\mathbb W$'?
+
+  {\it Changed as suggested.}
+\item
+  p.14 top: Give an intuitive description of what the three bullet points formulate.
+
+  {\it We gave an intuitive explanations in the paragraph before those bullet points. }
+\item
+  p.17 l.-7: The RHS has a factor $e^{\lambda t}$ too. 
+  Also, you should explain that this follows from the ergodicity of the $\phi$-transformed motion.
+  (Two lines later you should refer to Proposition 3.1.)
+
+  {\it We added more details there as suggested.}
+\item
+  p.18 l.8: ... with the same speed.
+
+  {\it Changed, as suggested.}
+\item
+  p.18 l.-11: Please remind us that $\nu = \phi^* m$.
+
+  {\it Done, as suggested.}
+\item
+  p.19 above (3.10): On the other hand,...
+
+  {\it Done, as suggested.}
+\item 
+  p.19-20: It's easier to read the proof backwards. So perhaps you should tell at the beginning that your goal is to show (3.12) and (3.13), etc.
+  For the same reason, I'd move the few lines ``Proof of Thm 1.1(2)'' from p.22 to the beginning so that one can understand why the two propositions are needed.
+
+  {\it We rearranged the Proof of Thm 1.1 (2) so that it is easier for the readers to get the structure of the Proof. }
+\item
+  p.21 l.1: Why is this ``according to (3.2)''?
+
+  {\it We explained this in more details.}
+\item
+  p.21 before (3.14): Make it one sentence: if ... then ...
+
+  {\it Done, as suggested.}
+\item
+  p.21 (3.14): $m$ is missing from the scalar product.
+
+  {\it We added it back, as suggested.}
+\item
+  p.24 Lemma 3.5: Say that the assumption on $\gamma_0$ is $\gamma_0 \in (1,2)$. 
+  This looks like a stand alone lemma, so perhaps the reader does not connect it with the previous definition of $\gamma_0$.
+
+  {\it It is indeed a stand along lemma. 
+    We changed all $\gamma_0$ into $\alpha$ in this Lemma.
+    Similar changes are made in the next Lemma due to same reasons.}
+\item
+  p.24 l.-2: When $0 < p < 1$, this is in fact not even a norm.
+
+  {\it We agree. 
+    This doesn't compromise the later proofs.
+    We emphasized this in the new version to avoid any confusions.}
+\item
+  p.26 l.1: explain a bit more on ``Since this is true for all $k$, we get that $F(\alpha+\theta) = 0$ for all $\theta \leq 1/C, \alpha \leq \rho$, and so $F = 0$ on $[0, \rho+1/C]$.
+
+  {\it The prove of this Lemma is simplified and the concerned argument is deleted.}
+\item
+  pp.24-26: Don't you what to move the analytical lemmas Lemma 3.5 and Lemma 3.6 move into an appendix?
+
+  {\it Those Lemmas are now moved into an appendix as suggested.}
+\item
+  p.26: Instead of (3.28), why don't you simply say that $F$ satisfies the inequality in Lemma 3.6 (number that one) with $C = \gamma_0^{1/(\gamma_0 - 1)}$?
+
+  {\it We should simply say that. 
+    Done, as suggested.}
+\item
+  p.28 end of Step 1: $J_g(t,r,\xi)$ and the two other terms you upper estimate are random variables.
+  So, do you mean the upper bounds almost surely?
+
+  {\it Yes, we mean almost surely. 
+  We added ``almost surely'' at several places as suggested.}
+\item
+  p.29 l.-12: You should also recall that $\left\langle f, \phi^* \right\rangle_m = 1$.
+
+  {\it Done, as suggested.}
+\item
+  p.32 l.-7: reverse instead of revers. 
+  Also ``use this ... to have that ...''.
+
+  {\it Done, as suggested.}
+\item
+  p.33 last sentence: I would say: ``Finally, $M \equiv 0$ clearly implies that $\lim_{t\to \infty} I_3(t,\theta,x) = 0$, and thus completes the verification of (3.29).''
+
+  {\it Done, as suggested.}
 \end{enumerate}

### 2019-07-17 stableLimit.tex
change response.tex
change response.tex


change response.tex


change response.tex


change response.tex


change response.tex


change stableLimit.tex
change stableLimit.tex

@@
 \email{yxren@math.pku.edu.cn}
-\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
+\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009), and LMEQF.
+}
 % ** Renming Song
@@
 {Zhenyao Sun\\
-	School of Mathematical Sciences\\
-	Peking University\\
-	Beijing, P. R. China, 100871}
+%	School of Mathematical Sciences\\
+School of Mathematics and Statistics\\
+%	Peking University\\
+Wuhan University\\
+%	Beijing, P. R. China, 100871}
+Wuhan, Hubei 430072, P. R. China}
 \email{zhenyao.sun@pku.edu.cn}
@@
 condition. Their main result can be stated as follows.
-% Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
   Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a $d$-type, nonsingular Galton-Watson process with its mean matrix $M:= (E[Z_1^{(j)}| Z_0^{(i)} = 1, Z_0^{(k)} = 0, \forall k \neq i])_{1\leq i,j\leq d}$ being positive regular, that is, all entries of $M$ are finite and there exists a number $n \geq 1$ such that all entries of $M^n$ are positive.
 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
-% Let $M$ be the mean matrix of $\mathbf Z$.  
-Let the process be critical in the sense that the maximal eigenvalue of $M$ is $1$. 
-% Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
-Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to this maximal eigenvalue $1$, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$ where $\mathbf 1$ is the vector $(1,\dots, 1)$.
+%Let the process be critical in the sense that the maximal eigenvalue of $M$ is $1$.
+Assume that the process is critical in the sense that the maximal eigenvalue of $M$ is $1$.
+Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to this maximal eigenvalue $1$, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, where $\mathbf 1$ is the vector $(1,\dots, 1)$.
 Suppose that
@@
 For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
-Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time multitype critical Galton-Watson processes.
+Vatutin \cite{Vatutin1977Limit} also considered analogous results for 
+%the continuous time multitype critical Galton-Watson processes.
+continuous time multitype critical Galton-Watson processes.
 
@@
 
-In this paper, we are interested in a class of measure-valued branching Markov process known as $(\xi, \psi)$-superprocesses:
+In this paper, we are interested in a class of measure-valued branching Markov 
+%process known as $(\xi, \psi)$-superprocesses:
+processes known as $(\xi, \psi)$-superprocesses:
 $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact separable metric space $E$;
@@
 Kyprianou and Pardo \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
-% He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
 They showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
@@
 \end{align}
-% where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
-where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent to the initial position $x$.
+where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and 
+%is independent to the initial position $x$.
+is independent of the initial position $x$.
 Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
@@
 	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
-  %	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
-  % \end{align}
   \xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}
 \end{align}
-where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent to the initial position $x$.
+where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and 
+%is independent to the initial position $x$.
+is independent of the initial position $x$.
 
@@
 
-In this paper, we will establish a result parallel to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
+In this paper, we will establish a result parallel to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocesses $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
 In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
@@
 	\psi(x,z)
-  % = -\beta (x) z + \kappa(x) z^{\gamma(x)},
   &= - \beta(x) z + \kappa(x) \int_0^\infty (e^{-z y} - 1+ z y) \frac{dy}{\Gamma(- \gamma(x)) y^{1+ \gamma(x)}}
@@
 where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0-1$).
-% ADDED
-Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ is independent of the choice of the initial configuration $\mu$.
-% END ADDED
+Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$
+%does not depend the initial configuration $\mu$.
+does not depend on the initial configuration $\mu$.
 Precise statements of the assumptions and the results are presented in the next subsection.
@@
 We first fix our notation.
-For any measurable space $(E,\mathscr E)$, we denote by $\mathscr E$ the collection of all real-valued measurable functions on $E$.
-Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
-Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$ and $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
-Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
-Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
+%For any measurable space $(E,\mathscr E)$, we denote by $\mathscr E$ the collection of all real-valued measurable functions on $E$.
+%Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
+%Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$ and $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
+%Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
+%Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
+%For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
+%We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
+%For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
+%In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
+%If $E$ is a topological space, we denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
+Unless stated explicitly otherwise, $E$ is assumed to be a locally compact separable metric space. 
+We use $\mathscr B(E)$ to denote the collection of all  Borel subsets of $E$ and also the collection of all  Borel functions on $E$.
+Define $\mathscr B_b(E) :=\{f \in \mathscr B(E): \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr B^+(E) :=\{f\in \mathscr B(E): \forall x\in E,~f(x)\geq 0\}$ and $\mathscr B^{++}(E) :=\{f\in \mathscr B(E): \forall x\in E,~f(x)> 0\}$.
+Define $\mathscr B^+_b(E) := \mathscr B_b(E) \cap \mathscr B^+(E)$ and $\mathscr B^{++}_b(E):= \mathscr B_b(E) \cap \mathscr B^{++}(E)$.
+Denote by $\mathcal M_E$ the collection of all Borel measures on $E$.
+Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite Borel measures on $E$.
 For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
-We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
-For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
-In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
-If $E$ is a topological space, we denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
+For any $f \in \mathscr B^+(E)$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$. In particular, $\mathcal M^1_E$ is the collection of all  finite Borel measures on $E$.
 
 We now give the definition of a $(\xi, \psi)$-superprocess:
-Let $E$ be a locally compact separable metric space, the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by \eqref{eq: branching mechanism}.
+%Let $E$ be a locally compact separable metric space, the spatial motion 
+Let the spatial motion 
+$\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by \eqref{eq: branching mechanism}.
 We say an $\mathcal M^1_E$-valued Hunt process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
@@
 
-% Define the \emph{Feynman-Kac semigroup}
 Recall that the branching mechanism $\psi$ is given by \eqref{eq: branching mechanism} and its linear coefficient $\beta$ is a bounded Borel function on $E$. Define the \emph{Feynman-Kac semigroup}
@@
 \end{align}
-% DELETED
-% (Notice that if $\beta \equiv 0$, then $P_t:= P^0_t$ is the \emph{transition semigroup} of the process $\xi$.)
-% END DELETED
-% It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
-It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$ in the sense that
-\begin{align} 
-% \label{eq: Ygalom type result without 2rd moment}
+It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is the \emph{mean semigroup} of the superprocess $\{X; \mathbf P\}$ in the sense that
+\begin{align}
 \label{eq:mean_formula}
@@
 
-% ADDED
-Define $(P_t^*)_{t\geq 0}$ as the dual of the transition semigroup $(P_t)_{t\geq 0}$, i.e.
+%moved from above
+We will write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
+%end move
+
+%Define $(P_t^*)_{t\geq 0}$ as the dual of the transition semigroup $(P_t)_{t\geq 0}$, i.e.
+Let $(P_t^*)_{t\geq 0}$ be the dual of the transition semigroup $(P_t)_{t\geq 0}$ in $L^2(E, m)$, i.e.,
 \begin{align}
@@
 $\widetilde \lambda := \sup \text{Re}(\sigma(\widetilde L)) = \sup \text{Re}(\sigma(\widetilde L^*))$ is a common eigenvalue of multiplicity $1$ for both $\widetilde L$ and $\widetilde L^*$.
-Using the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\widetilde \phi$ of $\widetilde L$ and $\widetilde \phi^*$ of $\widetilde L^*$ associated with the eigenvalue $\widetilde \lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
+%Using the argument in \cite{RenSongZhang2015Limit}, 
+By the argument in \cite{RenSongZhang2015Limit},
+the eigenfunctions $\widetilde \phi$ of $\widetilde L$ and $\widetilde \phi^*$ of $\widetilde L^*$ associated with the eigenvalue $\widetilde \lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
 We further normalize $\widetilde \phi$ and $\widetilde \phi^*$ by $\big\langle \widetilde \phi, \widetilde \phi \big\rangle_m = \big\langle \widetilde \phi, \widetilde \phi^*\big\rangle_m = 1$ so that they are unique.
-% END ADDED
-
-% Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
-It is also proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
+
+%It is also proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} 
+It is also proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} 
+that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
 \begin{align}
@@
 According to \cite[Theorem V.6.6]{Schaefer1974Banach}, $\lambda := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common eigenvalue of multiplicity $1$ for both $L$ and $L^*$.
-Using the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\phi$ of $L$ and $\phi^*$ of $L^*$ associated with the eigenvalue $\lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
+%Using the argument in \cite{RenSongZhang2015Limit}, 
+By the argument in \cite{RenSongZhang2015Limit}, 
+the eigenfunctions $\phi$ of $L$ and $\phi^*$ of $L^*$ associated with the eigenvalue $\lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
 We further normalize $\phi$ and $\phi^*$ by $\langle\phi, \phi\rangle_m = \langle\phi,\phi^*\rangle_m = 1$ so that they are unique.
-% Moreover, for each $t\geq 0$ and $x\in E$, we have $P^\beta_t \phi^*(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi(x) = e^{\lambda t} \phi^*(x)$.
   Moreover, for each $t\geq 0$ and $x\in E$, we have $P^\beta_t \phi(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi^*(x) = e^{\lambda t} \phi^*(x)$.
-We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of $L$ (resp. $L^*$).
+%We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ 
+We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ as
+the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of $L$ (resp. $L^*$).
 
@@
 
-% Let $\varphi$ (resp. $\varphi^*$) be the principal eigenfunction of (resp. the dual of) the transition semigroup $(P_t)$ of the spatial process $\xi$.
-% Our second assumption on the spatial process $\xi$ is the following:
-Our next assumption on the spatial process $\xi$ is the following:
+%Our next assumption on the spatial process $\xi$ is the following:
+Our next assumption is on the spatial motion $\xi$:
 
 \begin{asp} \label{asp: 3}
-	% $\varphi$ is bounded, and $(P_t)_{t\geq 0}$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \varphi(x) \varphi^*(y)$.
 	$\widetilde \phi$ is bounded, and $(P_t)_{t\geq 0}$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \widetilde \phi(x) \widetilde \phi^*(y)$.
@@
 \end{align}
-We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
-
-Our assumption on the branching mechanism is the following:
+%We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
+Assumption \ref{asp: 3} is a pretty strong assumption on the semigroup $\{P_t : t \ge 0\}$. However, this assumption is satisfied in a lot of cases.  
+In \cite{RenSongZhang2015Limit},  a list of examples of processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3} were given. 
+For the convenience of our readers, we will
+briefly recall some of these examples in Subsection \ref{sec:examples}.
+
+%Our assumption on the branching mechanism is the following:
+Our assumption is on the branching mechanism:
 \begin{asp} \label{asp: 4}
@@
 \end{align}
-% where $\beta \in \mathscr B_b(E), \gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
 where $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^{++}_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\kappa_0:=\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
 \end{asp}
-% Here we use the definition of the Gamma function on the negative half line:
 Here we used the definition of the Gamma function on the negative half line:
@@
 To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 	$X$.
-% Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a size-biased transform, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
   Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a martingale change of measure, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an measure-valued immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
-% The family of functions used for the size-biased transform is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$, which is a martingale.
-% Therefore, this size-biased transform can be viewed as a martingale change of measure.
 The martingale used for the change of measure is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$.
@@
 Similar idea has already been used by Powell \cite{Powell2015An-invariance} to establish results parallel to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment} for a class of critical branching diffusion processes.
-% Let $\{(Y_t)_{t\geq 0}; P\}$ be a branching diffusion process, in a bounded domain,  with finite second moment.
 Let $\{(Y_t)_{t\geq 0}; P\}$ be a branching diffusion process in a bounded domain with finite second moment.
@@
 Instead, by using a spine decomposition approach, Powell \cite{Powell2015An-invariance} showed that the survival probability decays like $a(t)\phi(x)$, where $\phi(x)$ is the principal eigenfunction of the mean semigroup of $(Y_t)$ and $a(t)$ is a function capturing the uniform speed.
-Then, the problem is reduced to the study of a single ordinary differential equation satisfied by $a(t)$.
+Then the problem is reduced to the study of a single ordinary differential equation satisfied by $a(t)$.
 Later, inspired by \cite{Powell2015An-invariance}, we gave in \cite{RenSongSun2017Spine} a similar proof of \eqref{eq: Kolmogorov type result with 2rd moment} for a class of general critical superprocesses with finite second moment.
@@
 
-A similar idea of establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine, RenSongSun2017Spine}.
+A similar idea for establishing weak convergence through a comparison of the equations satisfied by the distributions has already been used by us in \cite{RenSongSun2017A-2-spine, RenSongSun2017Spine}.
 We characterized the exponential distribution using its double size-biased transform; and to help us make the comparison, we investigated the double size-biased transform of the corresponding processes.
@@
 In Subsection \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-% In Subsection \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
-In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
-Finally, in Subsection \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
+%In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
+%Finally, in Subsection \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
+In Subsection \ref{sec: proof of result 3}, we give the proof of Theorem \ref{thm: main theorem}(3).
+In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterizes the distribution with Laplace transform \eqref{e:zloltarev}, which is used in the proof of Theorem \ref{thm: main theorem}(3) given Subsection \ref{sec: proof of result 3}.
 
@@
 Let $t_0 \in [-\infty,\infty]$.
+%moved from below
+In this Subsection, $(E, \mathscr E)$ is assume to be a  measurable space.
+%emd move 
 For any $f_0, f_1\in \mathscr B^{++}({\mathbb R})$, we say $f_0$ and $f_1$ are \emph{asymptotically equivalent at $t_0$}, if $\big|\frac{f_0(t)}{f_1(t)} - 1\big| \xrightarrow[t\to t_0]{} 0$;
 and in this case, we write $f_0(t) \stackrel[t\to t_0]{}{\sim} f_1(t)$.
-Let $E$ be a measurable space.
-For any $g_0, g_1\in \mathscr B^{++}({\mathbb R\times E})$, we say $g_0$ and $g_1$ are \emph{uniformly asymptotically equivalent at $t_0$}, if $\sup_{x\in E}\big|\frac{g_0(t,x)}{g_1(t,x)} - 1\big| \xrightarrow[t\to t_0]{} 0$; and in this case, we write $g_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}g_1(t,x)$.
+%moved up
+%Let $E$ be a measurable space.
+%end move
+%For any $g_0, g_1\in \mathscr B^{++}({\mathbb R\times E})$, 
+For any strictly positive measurable functions $g_0, g_1$ on $\mathbb R\times E$, 
+we say $g_0$ and $g_1$ are \emph{uniformly asymptotically equivalent at $t_0$}, if $\sup_{x\in E}\big|\frac{g_0(t,x)}{g_1(t,x)} - 1\big| \xrightarrow[t\to t_0]{} 0$; and in this case, we write $g_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}g_1(t,x)$.
 
 \begin{lem} \label{lem: asymptotic equivalent of integration}
-	Suppose that $f_0,f_1\in \mathscr B^{++}_b({\mathbb R \times E})$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
-	If $m \in \mathcal M^1_E$, then
+	Suppose that 
+%	$f_0,f_1\in \mathscr B^{++}_b({\mathbb R \times E})$ 
+$f_0,f_1$ are bounded strictly positive measurable functions on $\mathbb R \times E$
+	and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
+%	If $m \in \mathcal M^1_E$, then
+If $f$ is a finite measure on $(E, \mathscr E)$, then
   \begin{align}
@@
 We refer the reader to \cite{BinghamGoldieTeugels1989Regular} for more results on  regular variation.
-% For $f\in \mathscr B^{++}((0,\infty))$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\gamma \in (-\infty,\infty)$ if for any $\lambda \in (0,\infty)$,
 For $f\in \mathscr B^{++}((0,\infty))$ and $\alpha \in (- \infty, \infty)$, we say $f$ is regularly varying at $\infty$ (resp. at $0$) with index $\alpha$ if for any $u \in (0,\infty)$,
 \begin{align}
-	% \lim_{t\to\infty}\frac{f(\lambda t)}{f(t)}
 	\lim_{t\to\infty}\frac{f(ut)}{f(t)}
-	% = \lambda^\gamma
   = u^\alpha
-	% \quad \Big(\text{resp. } \lim_{t\to 0}\frac{f(\lambda t)}{f(t)}
 	\quad \Big(\text{resp. } \lim_{t\to 0}\frac{f(u t)}{f(t)}
-	% = \lambda^\gamma\Big).
 	= u^\alpha\Big).
 \end{align}
-% In this case we write  $f\in \mathcal R^\infty_\gamma$ (resp. $f\in \mathcal R^0_\gamma$).
 In this case we write  $f\in \mathcal R^\infty_\alpha$ (resp. $f\in \mathcal R^0_\alpha$).
-% Further, if $\gamma = 0$, then we say $f$ is slowly varying.
 Further, if $\alpha = 0$, then we say $f$ is slowly varying.
@@
 	Denoting by $h_0 := g_0^{-1}$, we can verify that \eqref{eq: inverse between h and f} is valid with $h$ replaced by $h_0$.
-	According to Lemma \ref{lem: regularly variation and inverse}, $h$ and $h_0$ are asymptotic equivalent at $\infty$.
+	According to Lemma \ref{lem: regularly variation and inverse}, 
+	%$h$ and $h_0$ are asymptotic equivalent at $\infty$.
+	$h$ and $h_0$ are asymptotically equivalent at $\infty$.
 	Hence, so are $g$ and $g_0$.
@@
 \begin{lem}\label{lem:regularly_variation_and_integration}
-	Let $E$ be a measurable space with a non-degenerate measure $m \in \mathcal M^1_E$.
-	Let $ \gamma \in \mathscr B_b(E)$ with
+%	Let $E$ be a measurable space with a non-degenerate measure $m \in \mathcal M^1_E$.
+Let $(E, \mathscr E)$ be a measurable space and $m$ a  non-degenerate measure
+on $(E, \mathscr E)$
+%	Let $ \gamma \in \mathscr B_b(E)$ with
+Let $f$ be a bounded measurable function on $E$ with 
   \begin{align}
@@
 Suppose that Assumptions \ref{asp: 1}--\ref{asp: 2} hold.
-% ADDED
-Noting that $\phi^*$ is the eigenfunction of semigroup $(P_t^{\beta*})_{t\geq 0}$, we have
+%Noting that $\phi^*$ is the eigenfunction of semigroup $(P_t^{\beta*})_{t\geq 0}$, we have
+Since $\phi^*$ is the principal eigenfunction of the semigroup $(P_t^{\beta*})_{t\geq 0}$, we have
 \begin{align}
@@
 \end{align}
-% END ADDED
-% CHANGED
-% Integrating both sides of \eqref{eq:mean-fkpp}  with respect to  $\phi^*dm$, we get that
-% \begin{align}\label{eq:langleVtfphiranglem_equation}
-%   \langle V_tf,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,V_r f) , \phi^*\rangle_mdr
-%   = \langle V_sf,\phi^*\rangle_m,
-%   \quad t\geq s\geq 0, f\in \mathscr B^+_b(E).
-% \end{align}
-% CHANGES
-Therefore, integrating the both sides of \eqref{eq:mean-fkpp} with respect to measure $\phi^*dm$, we get that
+%Therefore, integrating the both sides of \eqref{eq:mean-fkpp} with respect to measure 
+Therefore, integrating both sides of \eqref{eq:mean-fkpp} with respect to the measure 
+$\phi^*dm$, we get that
 \begin{align}
@@
 \end{align}
-% END CHANGED
 
@@
 \item
-	% For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
 	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure on $\mathbb W$ with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
@@
 \end{thm}
-% CHANGE
-% The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation:
-The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$, the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
-% END CHANGE
-
-% ADDED
+The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$, the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of the spine process in a Poissonian way.
+
 More precisely,
-% END ADDED
 we say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
@@
 Notice that $\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
-Also notice that $\mathbb N_\mu$ is not a probability measure, but after the transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
+Also notice that $\mathbb N_\mu$ is not a probability measure, 
+%but after the transform, 
+but after the size-biased transform, 
+$\mathbb N^{W_T(g)}_\mu$ is a probability measure.
 Since $\mathbb N_{\mu}(\|W_0\|\neq 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(\|W_0\|= 0) = 1$.
-Similarly, $\Pi_{\mu}$ is not typically a probability measure, but after the transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
+Similarly, $\Pi_{\mu}$ is not typically a probability measure, 
+%but after the transform, 
+but after the size-biased transform, 
+$\Pi_{\mu}^{(T,g)}$ is a probability measure.
 We note that
@@
 Recall that $\phi$ is the principal eigenfunction of the mean semigroup of $X$.
-The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, considered the case when $g = \phi$ only.
+The classical spine decomposition theorem, see 
+%\cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, 
+\cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog} for example, 
+considered the case when $g = \phi$ only.
 In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is, the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$,	on the finite time interval $[0,T]$.
@@
 \begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
-	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, then
+%	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ 
+If $F\in \mathscr B_b(E\times [0,1]\times [0,\infty)$ is
+such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, then
 \begin{align}
@@
 \begin{lem}\label{lem: Fatou-ergodic lemma for the uderlying process}
-	Let $F$ be a non-negative bounded Borel function on $E\times [0,1]\times [0,\infty)$.
+%	Let $F$ be a non-negative bounded Borel function on $E\times [0,1]\times [0,\infty)$.
+Let $F\in \mathscr B^+_b(E\times [0,1]\times [0,\infty))$.
 	Define $F(y,u):= \limsup_{t\to \infty} F(y,u,t)$ for each $y\in E$ and $u \in [0,1]$.
@@
 	For each $(y,u,t)\in E\times [0,1]\times [0,\infty)$, define $\bar F(y,u,t) := \sup_{s:s\geq t} F(y,u,s)$.
-	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$ such that
+%	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$ such that
+Then $F\in \mathscr B_b(E\times [0,1]\times [0,\infty))$ and
 \begin{align}
@@
 
-	If we replace $\psi$ with $\tilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
+	If we replace $\psi$ with $\widetilde\psi$ in \eqref{eq:FKPP_in_definition}, the solution $V_tf(x)$ of equation \eqref{eq:FKPP_in_definition} is also the solution of
 \begin{align}
@@
 	\inf_{x\in E}\widetilde \psi(x,z)
-	\geq \hat\psi(z),
+	\geq \widehat\psi(z),
 	\quad z\geq 0;
@@
 	< \infty;
-	\quad \hat \psi(+\infty) = +\infty.
+	\quad \widehat \psi(+\infty) = +\infty.
 \end{align}
@@
 % ** Proof of the main Theorem 2
-\subsection{Proof of Theorem \ref{thm: main theorem} (2)}
+\subsection{Proof of Theorem \ref{thm: main theorem}(2)}
 \label{sec: proof of result 2}
-% ADDED
 \begin{proof}
-  [Proof of Theorem \ref{thm: main theorem} (2)]
-  % END ADDED
+  [Proof of Theorem \ref{thm: main theorem}(2)]
   Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
   Assumptions \ref{asp: 1}--\ref{asp: 4}.
-  From Proposition \ref{prop: non-presistent}, we know that our superprocess $\{X;\mathbf P\}$ is non-persistent, that is,
-  \begin{align}
-    % ADDED
+  From Proposition \ref{prop: non-presistent}, we know that 
+  %our superprocess $\{X;\mathbf P\}$ is non-persistent,
+%  and more precisely,
+that
+  \begin{align}
     \label{eq:extinction_probability_is_not_zero}
-    % END ADDED
-    \mathbf P_{\delta_x}(\|X_t\| = 0)
+   \inf_{x\in E} \mathbf P_{\delta_x}(\|X_t\| = 0)
     > 0,
-    \quad t>0, x \in E.
-  \end{align}
-  % Notice that $\mathbf P_{\delta_x}[X_t(\phi)] = \phi(x)>0$, so we have
-  According to \eqref{eq:mean_formula}, Assumption \ref{asp: 2} and the fact that $\phi$ is the eigenfunction of semigroup $(P_t^\beta)_{t\geq 0}$, we have $\mathbf P_{\delta_x}[X_t(\phi)] = P_t^\beta \phi(x) = e^{\lambda t} \phi(x)= \phi(x)>0$.
+  \end{align}
+ %new
+ which implies that $\{X; \mathbf P\}$ is non-persistent.
+ %end new 
+  According to \eqref{eq:mean_formula}, Assumption \ref{asp: 2} and the fact that $\phi$ is 
+%  the eigenfunction of semigroup $(P_t^\beta)_{t\geq 0}$, 
+the principal eigenfunction of the semigroup $(P_t^\beta)_{t\geq 0}$, 
+  we have $\mathbf P_{\delta_x}[X_t(\phi)] = P_t^\beta \phi(x) = e^{\lambda t} \phi(x)= \phi(x)>0$.
   Therefore,
@@
   \end{align}
-  % From these and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
   From \eqref{eq:extinction_probability_is_not_zero}, \eqref{eq:extinction_probability_is_not_one} and \eqref{eq: definition of v_t(x)}, we have that $v_t \in \mathscr B^{++}_b(E)$ for each $t > 0$.
@@
   \end{align}
-  % Therefore, to prove Theorem \ref{thm: main theorem}(2), we only need to consider the speed of this convergence.
   However, to prove Theorem \ref{thm: main theorem}(2), we need to consider the speed of this convergence.
-  % This is answered in two steps.
-  This is answered in the following two propositions whose proof is postponed after the current proof.
-  % The first step says that $(\phi^{-1}v_t)(x)$ will converge to $0$ with the same speed as $\langle v_t,\phi^*\rangle_m$, uniformly in $x\in E$:
+  This is answered in the following two propositions 
+  %whose proof is postponed after the current proof.
+  whose proofs are postponed after this proof.
   The first proposition says that $(\phi^{-1}v_t)(x)$ will converge to $0$ with the same speed as $\langle v_t,\phi^*\rangle_m$, uniformly in $x\in E$:
@@
   \label{prop: asymptotic equivalence of vtphi}
-  % The second step characterizes this speed:
   The second proposition characterizes this speed:
@@
   \end{prop}
-% MOVED FROM BELOW
-    % According to \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0},
-    From \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0}, we have
+%    From \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0}, we have
+ It follows from \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0} that
     \begin{align}
@@
     \end{align}
-    % Therefore, $\mathbf P_\mu(\|X_t\| \neq 0) \xrightarrow[t\to \infty]{} 0$.
     Therefore, since $- \log (1-x) \to 0$ implies $x \to 0$, we have $\mathbf P_\mu(\|X_t\| \neq 0) \xrightarrow[t\to \infty]{} 0$.
 
-    % Noticing that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, according to \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed}, we have
-    Also from that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed}, we have
+%    Also from that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, 
+It follows from the fact that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, 
+\eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} 
+%and Proposition \ref{prop: convergence in a same speed}, we have
+and Proposition \ref{prop: convergence in a same speed} that
     \begin{align}
@@
     \end{align}
-    Therefore, according to Proposition \ref{prop: regularly varying of vt-phi-star}, we get the desired result.
-% END MOVED FROM BELOW
-  % ADDED
+%    Therefore, according to Proposition \ref{prop: regularly varying of vt-phi-star}, we get the desired result.
+Then the desired result follows immediately from Proposition \ref{prop: regularly varying of vt-phi-star}.
 \end{proof}
-% END ADDED
 
@@
 	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
+%new
+We will prove that for an appropriate map $t_0$ with
+$$
+	t_0(t)
+	\xrightarrow[t\to\infty]{} \infty;
+	\quad t_0(t)\| \phi^{-1}v_{t-t_0(t)}\|^{\gamma_0 - 1}_\infty
+	\xrightarrow[t\to\infty]{} 0,
+$$	
+we have
+$$
+\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
+	\xrightarrow[t\to\infty]{} 0
+$$
+and
+$$
+\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
+     \xrightarrow[t\to\infty]{} 0.
+$$
+Then the desired assertion follows easily from these and properties of uniform convergence.
+
+%end new
 For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$.
@@
 \end{align}
-% Taking $\mu = \delta_x$ in \eqref{eq:vt-and-Y}, we get $(\phi^{-1}v_t)(x) =\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]$.
 Taking $\mu = \delta_x$ in \eqref{eq:vt-and-Y}, we get $(\phi^{-1}v_t)(x) =\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]$.
-% Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
 Recall that $d\nu = \phi^* dm$.
@@
 
-% ADDED
 In order to show this, we consider a decomposition of the immigration process $(Y_t)_{t\geq 0}$.
-% END ADDED
 For any $t>0$ and any $G\in \mathscr B((0,t])$, define
@@
 
-% By the construction and the Markov property of $\{Y,\xi; \dot {\mathbf P}^{\phi}\}$, we have that
 By the construction of the spine representation $\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ and its Markov property, we have that
@@
 
-% ADDED
-The underline idea of the proof is to show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
-This is done in the following two lemmas whose proofs are postponed after the current proof.
-% END ADDED
-
-% ADDED
+%The underline idea of the proof is to show that 
+The main idea is to show that
+both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
+This is done in the following two lemmas whose proofs are postponed after this proof.
+
 Let $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}.
@@
 \end{lem}
-% END ADDED
-
-% MOVED AND MODIFIED FROM BELOW
-% Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq: some equations for PY-1-3},  Lemma \ref{lem:bound_for_epsilon1} and \eqref{eq:epsilon-2-final}, we have
-Now, for each $t_0 > 1$ and $t-t_0$ large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq:vt-and-Y},  Lemma \ref{lem:bound_for_epsilon1} and Lemma \ref{lem:upperbound_of_epsilon-2}, we have
+
+Now, for each $t_0 > 1$ and $t-t_0$ large enough, according to
+\eqref{eq:vt-and-Y},  \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2},
+Lemmas \ref{lem:bound_for_epsilon1} and \ref{lem:upperbound_of_epsilon-2}, we have
 \begin{align} \label{vts-inequality}
@@
    \leq \frac{|\epsilon_x^1(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m} + \frac{|\epsilon_x^2(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m}\\
-   % &\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty}
      & \quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty}
@@
 	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
-	% & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle} - 1 \Big| \phi \phi^*(x) m(dx)\\
       & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big| \phi \phi^*(x) m(dx)\\
@@
 \end{proof}
-% END MOVED AND MODIFIED FROM BELOW
-
-% Let $c_0, c_1>0$ be the constants in \eqref{eq:q(t,x,y)}.
+
 \begin{proof}
@@
   Note that $c_0, c_1>0$ are the constants in \eqref{eq:q(t,x,y)}.
-  % DELETED
-  % We claim that
-  % \begin{align}\label{eq: bound for epsilon1}
-  %   |\epsilon_x^1(t_0,t)|
-  %   \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m,
-  %   \quad t_0 > 1.
-  % \end{align}
-  % END DELETED
-  % In fact,
   Then for each $t > t_0 > 1$, we have that
@@
   \end{align}
-% ADDED
 \end{proof}
-% END ADDED
-
-% CHANGE
-% We now claim that, if $t_0 > 1$ and $t-t_0$ is large enough, then
-% \begin{align}\label{eq:upperbound_of_epsilon-2}
-%   |\epsilon_x^2(t_0,t)|
-%   \leq t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty} \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
-% \end{align}
+
 \begin{proof}
   [Proof of Lemma \ref{lem:upperbound_of_epsilon-2}]
-% In fact, using the Markov property of the spine process and the property of Poisson random measures, we have
-Using the Markov property of the spine process and the property of Poisson random measures, we have
+Using the Markov property of the spine process and 
+%the property of Poisson random measures, we have
+properties Poisson random measures, we have
 \begin{align}\label{eq:epsilon-2}
@@
 
-% CHANGE
-\begin{comment}
-On one hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
-According to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
+Since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
+With this $s_0>0$, we claim that for each $t - t_0\geq s_0$ the following holds:
+\begin{align}
+  \label{eq:epsilon-2-one}
+  \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
+  \leq t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
+\end{align}
+We will verify this claim at the end of this proof.
+
+On the other hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
 \begin{align}\label{eq:epsilon-2-final}
@@
 \end{align}
-On the other hand, since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
-Then, if $t-s > t-t_0 \geq s_0$, using the fact that $v_t$ is non-increasing in $t$, we get
+Therefore, from \eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-one} and \eqref{eq:epsilon-2-final}, we get that
+\begin{align}
+&|\epsilon_x^2(t_0,t)|
+\leq t_0 \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \|\phi^{-1} v_{t-t_0}\|_\infty^{\gamma_0 - 1} \cdot \dot{\mathbf P}_{\delta_x}^{(\phi)} \big[ Y_t^{(t_0, t]}(\phi)^{-1} \big]
+\\ & \leq t_0 \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \|\phi^{-1} v_{t-t_0}\|_\infty^{\gamma_0 - 1} \cdot (1+ c_0 e^{-c_1 t_0})\langle v_{t-t_0}, \phi^* \rangle_m,
+\end{align}
+as desired.
+
+%To complete the proof, we are left to verify the claim \eqref{eq:epsilon-2-one}.
+We now verify the claim \eqref{eq:epsilon-2-one}.
+Note that, if $t-s > t-t_0 \geq s_0$, using the fact that $v_t$ is non-increasing in $t$, we get
 \begin{align}
@@
 	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{ \|X_{t-s}\| \neq 0}]\pi(\xi_s,dy)
-	% \\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
 	  \\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(\xi_s)}}
@@
 \end{align}
-Combining this with \eqref{eq:epsilon-2} and \eqref{eq:epsilon-2-final}, we get Lemma \ref{lem:upperbound_of_epsilon-2}.
-\end{comment}
-
-Since $\phi^{-1}v_s$ converges to $0$ uniformly when $s\to \infty$, we can choose  $s_0>0$ such that for any $s\geq s_0$, we have $\|\phi^{-1}v_s\|_{\infty} \leq 1$.
-With this $s_0>0$, we claim that for each $t - t_0\geq s_0$ the following holds:
-\begin{align}
-  \label{eq:epsilon-2-one}
-  \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
-  \leq t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
-\end{align}
-We will verify this claim at the end of the current proof.
-
-On the other hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
-\begin{align}\label{eq:epsilon-2-final}
-	\dot{\mathbf P}_{\delta_x}^{(\phi)}[ Y^{(t_0,t]}_t(\phi)^{-1}]
-	\leq (1+c_0 e^{-c_1 t_0}) \langle v_{t-t_0},\phi^* \rangle_m.
-\end{align}
-Therefore, from \eqref{eq:epsilon-2}, \eqref{eq:epsilon-2-one} and \eqref{eq:epsilon-2-final}, we get that
-\begin{align}
-&|\epsilon_x^2(t_0,t)| 
-\leq t_0 \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \|\phi^{-1} v_{t-t_0}\|_\infty^{\gamma_0 - 1} \cdot \dot{\mathbf P}_{\delta_x}^{(\phi)} \big[ Y_t^{(t_0, t]}(\phi)^{-1} \big]
-\\ & \leq t_0 \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \|\phi^{-1} v_{t-t_0}\|_\infty^{\gamma_0 - 1} \cdot (1+ c_0 e^{-c_1 t_0})\langle v_{t-t_0}, \phi^* \rangle_m,
-\end{align}
-as desired for this Lemma.
-
-To complete the proof, we still need to verify the claim \eqref{eq:epsilon-2-one}.
-Note that, if $t-s > t-t_0 \geq s_0$, using the fact that $v_t$ is non-increasing in $t$, we get
-\begin{align}
-	\kappa(x)\gamma(x) v_{t-s}(x)^{\gamma(x)-1}
-	\leq \|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1} v_{t-s}\|^{\gamma_0-1}_\infty
-	\leq \|\kappa\gamma\phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
-\end{align}
-Therefore, using Campbell's formula, \eqref{eq: definition of Gamma function} and the fact that $e^{-x} \geq 1-x$, we have,  for $t-t_0 \geq s_0$,
-\begin{align}
-	&\dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{\| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]
-   \leq - \log \big( 1- \dot{\mathbf P}_{\delta_x}^{(\phi)}[\mathbf 1_{ \| Y_t^{(0,t_0]}\|\neq 0}|\mathscr F^\xi_{t_0}]\big)
-	\\&\quad =  - \log \lim_{\lambda \to \infty}\dot{\mathf P}_{\delta_x}^{(\phi)}[e^{- \lambda Y_t^{(0,t_0]}(\mathbf 1_E) }|\mathscr F^\xi_{t_0}]
-	\\&\quad = -\log \lim_{\lambda \to \infty} \exp\Big\{- \int_{[0,t]\times \mathbb W} \big( 1-\exp\{- \mathbf 1_{s\leq t_0} w_{t-s}(\lambda \mathbf 1_E)\}  \big) \mathbf m^\xi(ds,dw)\Big\}
-	\\&\quad = \int_{[0,t]\times \mathbb W}\mathbf 1_{s\leq t_0} \mathbf 1_{ \|w_{t-s}\| \neq 0} \mathbf m^\xi(ds,dw)
-	= \int_0^{t_0} ds \int_{(0,\infty)} y\mathbf P_{y\delta_{\xi_s}}[\mathbf 1_{ \|X_{t-s}\| \neq 0}]\pi(\xi_s,dy)
-	% \\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(x)}}
-	\\&\quad= \int_0^{t_0} ds \int_{(0,\infty)} y (1-e^{-yv_{t-s}(\xi_s)})  \frac{\kappa(\xi_s)dy}{\Gamma(-\gamma(\xi_s)) y^{1+\gamma(\xi_s)}}
-	= \int_0^{t_0} \big( \kappa \gamma  v_{t-s}^{\gamma - 1} \big) (\xi_s)ds
-	\\&\quad \leq  t_0\|\kappa \gamma \phi^{\gamma - 1}\|_\infty \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty.
-\end{align}
 This ends the verification of the claim \eqref{eq:epsilon-2-one}, and thus also completes the proof of Lemma \ref{lem:upperbound_of_epsilon-2}.
-% END CHANGE
-
-% ADDED
 \end{proof}
-% END ADDED
-
-% MOVED AND MODIFIED TO ABOVE
-\begin{comment}
-Now, for $0<t_0<t<\infty$ and $x\in E$, if $t_0 > 1$ and $t-t_0$ is large enough, according to \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, \eqref{eq: some equations for PY-1-3}, Lemma \ref{lem:bound_for_epsilon1} and \eqref{eq:epsilon-2-final}, we have
-\begin{align} \label{vts-inequality}
-	&\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0},\phi^* \rangle_m}-1 \Big|
-   \leq \frac{|\epsilon_x^1(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m} + \frac{|\epsilon_x^2(t_0,t)|}{\langle v_{t-t_0},\phi^* \rangle_m}\\
-   % &\quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa(x)\gamma(x)\phi(x)^{\gamma(x) - 1}\|_{\infty}
-     & \quad \leq c_0e^{-c_1 t_0} +t_0\|\kappa\gamma\phi^{\gamma - 1}\|_{\infty}
-       \cdot \|\phi^{-1}v_{t-t_0}\|^{\gamma_0-1}_\infty (1+c_0 e^{-c_1 t_0}).
-\end{align}
-According to \eqref{eq: uniform converges to 0}, there exists a map $t\mapsto t_0(t)$ such that,
-\begin{align}
-	t_0(t)
-	\xrightarrow[t\to\infty]{} \infty;
-	\quad t_0(t)\| \phi^{-1}v_{t-t_0(t)}\|^{\gamma_0 - 1}_\infty
-	\xrightarrow[t\to\infty]{} 0.
-\end{align}
-Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
-\begin{align}\label{eq:k1}
-	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
-	\xrightarrow[t\to\infty]{} 0.
-\end{align}
-Notice that
-\begin{align}\label{eq:k2}
-	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
-	% & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle} - 1 \Big| \phi \phi^*(x) m(dx)\\
-    & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big| \phi \phi^*(x) m(dx)\\
-    & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
-      \xrightarrow[t\to\infty]{} 0.
-\end{align}
-Now, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
-\begin{align}
-	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
-	\xrightarrow[t\to\infty]{} 0,
-\end{align}
-as desired.
-\end{proof}
-\end{comment}
-% END MOVED AND MODIFIED TO ABOVE
 
@@
 	Taking $\mu = \nu$, according to \eqref{eq: equation for mu v-t}, we have that $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to 0]{} +\infty$.
-	% On the other hand, according to \eqref{eq: uniform converges to 0}, we have $\langle v_{t}, \phi^*\rangle_m \xrightarrow[t\to \infty]{} 0$.
 	On the other hand, according to \eqref{eq: uniform converges to 0}, we have
@@
 \end{align}
-	% Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle$ has an inverse on $(0,\infty)$ which is denoted by
 	  Therefore, the map $t\mapsto \langle v_t,\phi^*  \rangle_m$ has an inverse on $(0,\infty)$ which is denoted by
@@
 	\epsilon_{t}(x)
-	% : = \frac{v_t(x)}{\langle v_t, \phi^*\rangle \phi(x)} - 1,
 	: = \frac{v_t(x)}{\langle v_t, \phi^*\rangle_m \phi(x)} - 1,
-	% \quad t>0, x\in E.
 	\quad t>0, x\in E,
 \end{align}
-% Then, we have
 then we have
@@
 	v_t(x)
-	% = \big(1+ \epsilon_{R(\langle v_t,\phi^* \rangle)}(x) \big )\langle v_t,\phi^* \rangle \phi(x),
 	= \big(1+ \epsilon_{R(\langle v_t,\phi^* \rangle_m)}(x) \big )\langle v_t,\phi^* \rangle_m \phi(x),
@@
       = \int_s^t \langle \psi_0(\cdot ,v_r), \phi^*\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
-      % \\&\overset{\text{by \eqref{eq: change variable using inverse} }}{=} \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle \phi \big), \phi^* \big\rangle _m^{-1} d\langle v_r ,\phi^* \rangle_m
         \\ & \overset{\text{by \eqref{eq: change variable using inverse} }}{=} \int_s^t \big\langle \psi_0\big( \cdot ,(1+ \epsilon_{R(\langle v_r,\phi^* \rangle_m)})\langle v_r,\phi^*\rangle_m \phi \big), \phi^* \big\rangle_m^{-1} d\langle v_r ,\phi^* \rangle_m
@@
 \end{proof}
-
-% MOVED ABOVE:
-\begin{comment}
-\begin{proof}[Proof of Theorem \ref{thm: main theorem}(2)]
-	According to \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0},
-\begin{align}
-	- \log \mathbf P_\mu(\|X_t\| = 0)
-	= \mu(v_t)
-	\leq \mu(\phi) \| \phi^{-1} v_t\|_{\infty}
-	\xrightarrow[t\to \infty]{} 0.
-\end{align}
-Therefore, $\mathbf P_\mu(\|X_t\| \neq 0) \xrightarrow[t\to \infty]{} 0$.
-
-Noticing that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, according to \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed}, we have
-\begin{align}
-	\mathbf P_\mu(\|X_t\| \neq 0)
-	\stackrel[t\to \infty]{}{\sim} - \log \mathbf P_\mu(\|X_t\| = 0)
-	= \mu(\phi \phi^{-1}v_t)
-	\stackrel[t\to\infty]{}{\sim} \mu(\phi) \langle v_t, \phi^*\rangle_m.
-\end{align}
-Therefore, according to Proposition \ref{prop: regularly varying of vt-phi-star}, we get the desired result.
-\end{proof}
-\end{comment}
-% END MOVED ABOVE
 
@@
 \begin{proof}
-	It follows from Theorem \ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
+%	It follows from Theorem 
+	It follows from Theorems
+	\ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
   \begin{align}
@@
 \end{align}
-where $\{(\xi)_{0\le t\le T}, \mathbf n_T, (Y)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$ is a spine representation of $\mathbb N^{W_T(f)}_x$ with $\mathbf m^\xi_T$ being the intensity of the immigration measure $\mathbf n_T$ conditioned on $\{(\xi)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$.
+where $\{(\xi)_{0\le t\le T}, \mathbf n_T, (Y)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$ is the spine representation of $\mathbb N^{W_T(f)}_x$ with $\mathbf m^\xi_T$ being the intensity of the immigration measure $\mathbf n_T$ conditioned on $\{(\xi)_{0\le t\le T}; \dot {\mathbf P}^{(f,T)}_x\}$.
 From this, we have
@@
 \end{align}
-% On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
 On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, the spine representation, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
@@
 \end{align}
-
-% ** Distribution with Laplace transform 
-% MOVED AND MODIFIED BELOW
-\begin{comment}
-\subsection{Distribution with Laplace transform (\ref{e:zloltarev})}
-\label{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}
-
-The distribution with Laplace transform \eqref{e:zloltarev} can be characterized by the
-following result.
-
-% MINER CHANGES: I changed all \gamma_0 here to \alpha without further noticing.
-\begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
-	% ADDED
-  Suppose that $\alpha \in (1,2).$
-  % END ADDED
-  The non-linear delay equation
-  \begin{align} \label{eq: equation for the distribution}
-    G( \theta)
-    = \int_0^\theta \exp\Big\{ - \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1} })^{\alpha - 1}\frac{du}{u} \Big\} dr,
-    \quad \theta \geq 0,
-  \end{align}
-	has a unique solution:
-  \begin{align}\label{eq: solution for the equation}
-    G(\theta)
-    = \Big(\frac{1}{1+\theta^{-(\alpha - 1)}}\Big)^{\frac{1}{\alpha - 1}},
-    \quad \theta \geq 0.
-  \end{align}
-\end{lem}
-
-We first introduce some notation:
-If $f$ is a measurable function which is $L^p$ integrable on the measure space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
-\begin{align}
-	\|f\|_{\mu;p}
-	:= \Big(\int_{S} |f|^p d\mu \Big)^{\frac{1}{p}}.
-\end{align}
-Notice that, when $p\geq 1$, $\|f\|_{\mu;p}$ is simply the $L^p$ norm of $f$ with respect to the measure $\mu$.	
-% ADDED
-However, when $p \in (0,1)$, $\|\cdot\|_{\mu; p}$ is not a norm.
-% END ADDED
-
-In order to prove the above lemma, we will need the following:
-
-\begin{lem}\label{lem: F is zero}
-	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
-  \begin{align}
-    % ADDED
-    \label{eq:Gronwall_inequlity}
-    % END ADDED
-    F(\theta)
-    \leq C \int_0^\theta \|  F(ru^{ \frac{1}{\alpha - 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0.
-  \end{align}
-	Then $F \equiv 0$.
-\end{lem}
-
-% CHANGES	
-% \begin{proof}
-%   We prove this lemma by contradiction.
-%   Assume that
-%   \begin{align}\label{eq: definition of rho}
-%     \rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
-%   \end{align}
-%   Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
-%   We first claim that
-%   \begin{align}
-%     F_\alpha (\theta)
-%     \leq C(\rho C + 1) \theta,
-%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-%   \end{align}
-%   In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
-%   \begin{align}
-%     F_\alpha (\theta)
-%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; (\gamma_0 - 1)} dr
-%     \leq C\int_\alpha^{\alpha + \theta} \|Cru^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\&\leq C^2 (\alpha + \theta) \theta \|u^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-%     \leq C(\rho C + 1) \theta.
-%   \end{align}
-%   We then claim that, if
-%   \begin{align}\label{eq: FATLC}
-%     F_\alpha (\theta)
-%     \leq C^k(\rho C + 1) \theta^k,
-%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
-%   \end{align}
-%   for some $k \in \mathbb N$, then
-%   \begin{align}
-%     F_\alpha (\theta)
-%     \leq C^{k+1}(\rho C + 1) \theta^{k+1},
-%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-%   \end{align}
-%   In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
-%   \begin{align}
-%     F_\alpha (\theta)
-%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr\\
-%     &=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) \big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\& =  C\int_0^\theta \|F_{\alpha u^{1/(\gamma_0 - 1)}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} }
-%     \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-%     \\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
-%   \end{align}
-%   Therefore, by induction, we have
-% \begin{align}
-%   F_\alpha (\theta)
-%   \leq C^k(\rho C + 1) \theta^k,
-%   \quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
-% \end{align}
-%	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
-%	This, however, contradicts \eqref{eq: definition of rho}.
-% \end{proof}
-\begin{proof}
-  We claim that for each $k \in \mathbb N$, we have
-  \begin{align}
-    \label{eq:upperbound_for_F}
-    F(\theta) \leq \frac{C^k \theta^k}{k!},
-    \quad \theta \geq 0.
-  \end{align}
-  In fact, when $k = 1$ this is trival. Now if \eqref{eq:upperbound_for_F} is true for a fixed $k \in \mathbb N$, then from
-  \begin{align}
-    &F(\theta)
-      \leq C \int_0^\theta \left\|  F\left(ru^{ \frac{1}{\alpha - 1}  }\right)\right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
-      \leq C \int_0^\theta \left\|  \frac{1}{k!}\left(Cru^{ \frac{1}{\alpha - 1}  } \right)^k \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
-    \\ &\leq \frac{C^{k+1}}{k!} \left(\int_0^\theta r^k dr\right) \cdot \left\|u^{\frac{k}{\alpha - 1}} \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
-  \end{align}
-  we have that \eqref{eq:upperbound_for_F} is true for $k+1$. 
-  Therefore, by induction, \eqref{eq:upperbound_for_F} is true for all $k \in \mathbb N$.
-
-  Taking $k \to \infty$ in \eqref{eq:upperbound_for_F}, we get that $F(\theta) = 0$ for each $\theta \geq 0$.
-\end{proof}
-% END CHANGES
-
-\begin{proof}[Proof of Lemma \ref{lem: characterize the general Mittag-Leffler distribution}]
-	We first verify that \eqref{eq: solution for the equation}  is a solution of \eqref{eq: equation for the distribution}.
-	In fact, if $G(\theta) = (\frac{1}{1+ \theta^{-(\alpha - 1)}})^{\frac{1}{\alpha - 1}}$, then
-  \begin{align}
-    & \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1}\frac{du}{u}\Big\} dr
-    \\ & \quad = \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \int_0^1 \frac{du}{u+r^{-(\alpha - 1)}} \Big\} dr
-         = \int_0^\theta \exp\Big\{- \frac{\alpha} {\alpha - 1} \log \frac {1+r^{-(\alpha - 1)}} {r^{-(\alpha - 1)} } \Big\} dr
-    \\ & \quad = \int_0^\theta \big(\frac{1+r^{-(\alpha - 1)}}{r^{-(\alpha - 1)} }\big)^{- \frac{\alpha} {\alpha - 1}} dr
-         = \int_0^\theta \big( 1 + r^{ - ( \alpha - 1 ) } \big)^{- \frac{\alpha} {\alpha - 1}} r^{-\alpha} dr
-         = G(\theta).
-  \end{align}
-	The last equality is due to $G(0) = 0$ and
-  \begin{align}
-    \frac{d}{d\theta}G(\theta)
-    &= - \frac{1}{\alpha - 1} \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{1}{\alpha - 1} - 1} \frac{d}{d\theta} \theta^{-(\alpha - 1)}
-    \\& =  \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{\alpha}{\alpha - 1} } \theta^{-\alpha}.
-\end{align}
-
-Now assume that $G_0$ is another solution to the equation \eqref{eq: equation for the distribution}, we then only have to show that $G_0 = G$.
-This can be done by showing that $F(\theta) = 0$ where
-  \begin{align}
-    F(\theta)
-    := |G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|^{\frac{1}{\alpha - 1}},
-    \quad \theta \geq 0.
-  \end{align}
-  % CHANGES
-	% We claim that the non-negative function $F$ satisfies the following inequality:
-  % \begin{align}\label{eq: inequality of F(theta)}
-    % F(\theta)
-    % \leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\alpha - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0,
-  % \end{align}
-	% for some constant $C_0 > 0$.
-  We claim that the non-negative function $F$ satisfies the inequality \eqref{eq:Gronwall_inequlity} with $C = \alpha ^{1/(\alpha - 1)}$.
-  % END CHANGES
-	In fact, by the $L^p$ Minkowski inequality with $p = \frac{1}{\alpha - 1} > 1$, we have
-  \begin{align}
-    &|G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|
-    \\&\quad = \Big| \|e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta} dr; \frac{1}{\alpha - 1}} - \|e^{-\alpha \int_0^1 G_0(ru^{ \frac{1} {\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\alpha - 1}} \Big|
-    \\ & \quad \leq \| e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} - e^{-\alpha \int_0^1 G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1} {\alpha - 1}}
-    \\ & \quad \leq \Big\| \alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u} - \alpha \int_0^1 G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0<r<\theta}dr;\frac{1} {\alpha - 1}}
-    \\ & \quad \leq \alpha \Bigg( \int_0^\theta \Big( \int_0^1 |G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} - G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1}| \frac{du}{u} \Big)^{\frac{1}{\alpha - 1}} dr \Bigg)^{\alpha - 1}.
-  \end{align}
-  % In other words, there is a constant $C_0:= \alpha^{\frac{1}{\alpha - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
-  This implies the claim.
-
-  On the other hand, according to \eqref{eq: equation for the distribution}, we have that $G(\theta) \leq \theta$ and $G_0(\theta) \leq \theta$.
-  Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
-  % Therefore, according to Lemma \ref{lem: F is zero} and \eqref{eq: inequality of F(theta)}, we have $F \equiv 0$ as desired.
-  Therefore, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
-\end{proof}
-% END MINER CHANGES: I changed all \gamma_0 here to \alpha without further noticing.
-\end{comment}
-% END MOVED AND MODIFIED BELOW
 
@@
 \end{equation}
-The underlying idea of the proof is to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense when $t\to \infty$.
+%The underlying idea of the proof is 
+The main idea is
+to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense when $t\to \infty$.
 
@@
 \end{align}
-% From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have
 From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have almost surely
@@
 \end{align}
-% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have
 From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have almost surely
@@
 \end{align}
-% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have
 From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have almost surely
@@
 
-% ADDED
-For the rest of the proof, we use the following notations:
+%For the rest of the proof, we use the following notation:
+In the remainder of this proof, we use the following notation:
 If $f$ is a measurable function which is $L^p$ integrable on the measure space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
@@
 However, when $p \in (0,1)$, $\|\cdot\|_{\mu; p}$ is not a norm.
-% END ADDED
 
@@
 Step 3: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
-% Notice that, by \eqref{eq:q(t,x,y)},
 Notice that, by \eqref{eq:q(t,x,y)} and since $\langle f,\phi^* \rangle_m = 1$,
@@
 \end{align}
-% Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we have that
-Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g} to have that
+%  Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g} to have that
+Using this version of the reverse Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we get that
 \begin{align}
@@
 
-Step 7. We will show that $M(\theta) = 0$ for each $\theta \geq 0$.
+Step 7: We will show that $M(\theta) = 0$ for each $\theta \geq 0$.
 We first claim that
@@
 According to that $M(\theta) \leq c_6 \theta$ for each $\theta$, we can apply Lemma \ref{lem: F is zero} to the above inequality to get the desired result.
-% Finally, by the definition of $M$,  $M\equiv 0$ implies the desired assertion \eqref{eq: we only need to proof this}.
-
-Step 8. Finally, $M \equiv 0$ clearly implies that $\lim_{t\to \infty} I_3(t,\theta, x) = 0$, and thus completes the verification of \eqref{eq: we only need to proof this}.
-
-% MOVED AND MODIFIED FROM ABOVE
+
+Step 8: Finally, $M \equiv 0$ clearly implies that $\lim_{t\to \infty} I_3(t,\theta, x) = 0$, and thus completes the verification of \eqref{eq: we only need to proof this}.
+
 \appendix
@@
 \subsection{Examples}
-TBD
-\subsection{Analytical result}
+%new
+\label{sec:examples}
+
+In this Subsection, we briefly recall from \cite{RenSongZhang2015Limit} some examples of Markov processes satisfying Assumptions \ref{asp: 1} and \ref{asp: 3}. We will not try to give the most
+general examples. For details and more examples, we refer our readers to \cite{RenSongZhang2015Limit}.
+
+\begin{exa} {\rm
+Suppose that $E$ is a bounded Lipschitz connected  open set of $\mathbb R^d$ and that $m$ denotes the Lebesgue measure on $E$.
+Let $\xi$ be the subprocess in $E$ of a diffusion
+process in $\mathbb{R}^d$ corresponding to a uniformly elliptic divergence form second order
+differential operator.  Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
+Assumptions \ref{asp: 1} and \ref{asp: 3}. 
+}
+\end{exa}
+
+\begin{exa} {\rm
+Suppose that $E$ is the closure of a bounded $C^2$ connected  open set of $\mathbb R^d$ and that $m$ denotes the Lebesgue measure on $E$.
+Let $\xi$ be the reflecting Brownian motion
+in $E$. Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
+Assumptions \ref{asp: 1} and \ref{asp: 3}. 
+}
+\end{exa}
+
+\begin{exa} {\rm
+Suppose that $E$ is a bounded   open set of $\mathbb R^d$ and  $m$ denotes the Lebesgue measure on $E$.
+$\xi$ be the subprocesses in $E$ of any of
+the subordinate Brownian motions studied in \cite{KSV1, KSV2}.  Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
+Assumptions \ref{asp: 1} and \ref{asp: 3}. 
+}
+\end{exa}
+
+\begin{exa} {\rm
+Suppose $a>2$ is a constant.
+Assume that $E=\mathbb{R}^d$ and $m$ is the Lebesgue measure on $\mathbb{R}^d$.
+Let $\xi$ be a Markov process on $\mathbb{R}^d$ corresponding to the infinitesimal
+generator $\Delta-|x|^a$. Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
+Assumption \ref{asp: 1} and \ref{asp: 3}. 
+}
+\end{exa}
+
+\begin{exa} {\rm
+Assume that $E=\mathbb{R}^d$ and $m$ is the Lebesgue measure on $\mathbb{R}^d$.
+Suppose that $V$ is a nonnegative and locally bounded function on  $\mathbb{R}^d$
+such that there exist $R>0$ and $M\ge 1$ such that for all $|x|>R$,
+$$
+M^{-1}(1+V(x))\le V(y)\le M(1+V(x)), \qquad y\in B(x, 1),
+$$
+and that
+$$
+\lim_{|x|\to\infty}\frac{V(x)}{\log|x|}=\infty.
+$$
+Suppose $\beta\in (0, 2)$ is a constant.
+Let $\xi$ be a Markov process on $\mathbb{R}^d$ corresponding to the infinitesimal
+generator $-(-\Delta)^{\beta/2}-V(x)$. 
+Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
+Assumptions \ref{asp: 1} and \ref{asp: 3}. 
+}
+\end{exa}
+
+\begin{exa} {\rm
+Suppose that $\beta\in (0, 2)$ and that $\xi^{(1)}=\{\xi^{(1)}_t: t\ge0\}$ is a strictly
+$\beta$-stable process in $\mathbb{R}^d$. Suppose that, in the case $d\ge 2$, the spherical
+part $\eta$ of the L\'evy measure $\mu$ of $\xi^{(1)}$ satisfies the following assumption: there
+exist a positive function $\Phi$ on the unit sphere $S$ in $\mathbb{R}^d$ and $\kappa>1$
+such that
+$$
+\Phi=\frac{d\eta}{d\sigma} \quad \mbox{and} \quad
+\kappa^{-1}\le \Phi(z)\le \kappa \quad \mbox{on } S
+$$
+where $\sigma$ is the surface measure on $S$. In the case $d=1$, we assume that the L\'evy
+measure of $\xi^{(1)}$ is given by
+$$
+\mu(dx)=c_1x^{-1-\beta}1_{\{x>0\}}+ c_2|x|^{-1-\beta}1_{\{x<0\}}
+$$
+with $c_1, c_2>0$. Suppose that $E$ is a bounded open set in $\mathbb{R}^d$
+and $m$ is the Lebesgue measure on $E$.
+Let $\xi$ be the process in $E$ obtained by killing $\xi^{(1)}$ upon exiting $E$.
+Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
+Assumptions \ref{asp: 1} and \ref{asp: 3}. 
+}
+\end{exa}
+%end new
+
+\subsection{Analytical results}
 \label{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}
-In the proof of Theorem \ref{thm: main theorem}(3), we have used the following notations which we recall here:
+%In the proof of Theorem \ref{thm: main theorem}(3), we have used the following notations which we recall here:
+In this Subsection, we give the proofs of the two lemmas used in the proof of Theorem \ref{thm: main theorem}(3). We think these two lemmas are of independent interest.
+
+We first recall the following notation:
 If $f$ is a measurable function which is $L^p$ integrable on the measure space $(S,\mathscr S,\mu)$ with $p > 0$, then we write
@@
 
-The following analytical results are used in the proof of Theorem \ref{thm: main theorem} (3). 
+%The following analytical results are used in the proof of Theorem \ref{thm: main theorem} (3).
+
+%moved below
+\begin{comment}
 \begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
@@
 \end{lem}
+\end{comment}
+%end move
 
@@
   \begin{align}
-    % ADDED
     \label{eq:Gronwall_inequlity}
-    % END ADDED
     F(\theta)
@@
 
-% CHANGES	
-% \begin{proof}
-%   We prove this lemma by contradiction.
-%   Assume that
-%   \begin{align}\label{eq: definition of rho}
-%     \rho :=  \sup\{x: F(\theta) = 0, \theta \in [0,x)\} < \infty.
-%   \end{align}
-%   Write $F_\alpha (\theta) := F(\alpha + \theta)$ for each $\alpha, \theta \geq 0$.
-%   We first claim that
-%   \begin{align}
-%     F_\alpha (\theta)
-%     \leq C(\rho C + 1) \theta,
-%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-%   \end{align}
-%   In fact, if $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$, then
-%   \begin{align}
-%     F_\alpha (\theta)
-%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; (\gamma_0 - 1)} dr
-%     \leq C\int_\alpha^{\alpha + \theta} \|Cru^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\&\leq C^2 (\alpha + \theta) \theta \|u^{\frac{1}{\gamma_0 - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-%     \leq C(\rho C + 1) \theta.
-%   \end{align}
-%   We then claim that, if
-%   \begin{align}\label{eq: FATLC}
-%     F_\alpha (\theta)
-%     \leq C^k(\rho C + 1) \theta^k,
-%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho,
-%   \end{align}
-%   for some $k \in \mathbb N$, then
-%   \begin{align}
-%     F_\alpha (\theta)
-%     \leq C^{k+1}(\rho C + 1) \theta^{k+1},
-%     \quad \theta \leq \frac{1}{C}, \alpha \leq \rho.
-%   \end{align}
-%   In fact, if \eqref{eq: FATLC} is true, then for each $\theta \leq \frac{1}{C}$ and $\alpha \leq \rho$,
-%   \begin{align}
-%     F_\alpha (\theta)
-%     &\leq C\int_\alpha^{\alpha + \theta} \|F(ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr\\
-%     &=  C\int_0^\theta \big \|F\big( (\alpha + r)u^{\frac{1}{\gamma_0 - 1}} \big ) \big \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\& =  C\int_0^\theta \|F_{\alpha u^{1/(\gamma_0 - 1)}}( ru^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\&\leq C\int_0^ \theta \|C^k (\rho C+ 1) r^k u^{\frac{k}{\gamma_0 - 1} }
-%     \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1} dr
-%     \\&\leq C^{k+1} (\rho C + 1) \theta^{k+1} \|u^{\frac{k}{\gamma_0 - 1} } \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \gamma_0 - 1}
-%     \\&\leq C^{k+1} (\rho C+1) \theta^{k+1} .
-%   \end{align}
-%   Therefore, by induction, we have
-% \begin{align}
-%   F_\alpha (\theta)
-%   \leq C^k(\rho C + 1) \theta^k,
-%   \quad \theta \leq \frac{1}{C}, \alpha \leq \rho, k \in \mathbb N.
-% \end{align}
-%	As a consequence, we must have $F(\theta) = 0$ if $\theta < \rho + \frac{1}{C}$.
-%	This, however, contradicts \eqref{eq: definition of rho}.
-% \end{proof}
 \begin{proof}
-  [Proof of Lemma \ref{lem: F is zero}]
+%  [Proof of Lemma \ref{lem: F is zero}]
   We claim that for each $k \in \mathbb N$, we have
@@
 
-  Taking $k \to \infty$ in \eqref{eq:upperbound_for_F}, we get that $F(\theta) = 0$ for each $\theta \geq 0$.
+  Letting $k \to \infty$ in \eqref{eq:upperbound_for_F}, we get that $F(\theta) = 0$ for each $\theta \geq 0$.
 \end{proof}
-% END CHANGES
-
-\begin{proof}[Proof of Lemma \ref{lem: characterize the general Mittag-Leffler distribution}]
+
+%moved from above
+\begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
+  Suppose that $\alpha \in (1,2).$
+  The non-linear delay equation
+  \begin{align} \label{eq: equation for the distribution}
+    G( \theta)
+    = \int_0^\theta \exp\Big\{ - \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1} })^{\alpha - 1}\frac{du}{u} \Big\} dr,
+    \quad \theta \geq 0,
+  \end{align}
+	has a unique solution:
+  \begin{align}\label{eq: solution for the equation}
+    G(\theta)
+    = \Big(\frac{1}{1+\theta^{-(\alpha - 1)}}\Big)^{\frac{1}{\alpha - 1}},
+    \quad \theta \geq 0.
+  \end{align}
+\end{lem}
+
+%end move 
+%\begin{proof}[Proof of Lemma \ref{lem: characterize the general Mittag-Leffler distribution}]
+\begin{proof}
 	We first verify that \eqref{eq: solution for the equation}  is a solution of \eqref{eq: equation for the distribution}.
@@
   \end{align}
-  % CHANGES
-	% We claim that the non-negative function $F$ satisfies the following inequality:
-  % \begin{align}\label{eq: inequality of F(theta)}
-    % F(\theta)
-    % \leq C_0 \int_0^\theta \|  F(ru^{\frac{1}{\alpha - 1}})\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0,
-  % \end{align}
-	% for some constant $C_0 > 0$.
   We claim that the non-negative function $F$ satisfies the inequality \eqref{eq:Gronwall_inequlity} with $C = \alpha ^{1/(\alpha - 1)}$.
-  % END CHANGES
 	In fact, by the $L^p$ Minkowski inequality with $p = \frac{1}{\alpha - 1} > 1$, we have
@@
   \end{align}
-  % In other words, there is a constant $C_0:= \alpha^{\frac{1}{\alpha - 1}}>0$ such that \eqref{eq: inequality of F(theta)} is true.
   This implies the claim.
@@
   Therefore, we also have that there is a constant $C_1 > 0$ such that $F(\theta) \leq C_1 \theta$.
-  % Therefore, according to Lemma \ref{lem: F is zero} and \eqref{eq: inequality of F(theta)}, we have $F \equiv 0$ as desired.
   Therefore, according to Lemma \ref{lem: F is zero}, we have $F \equiv 0$ as desired.
 \end{proof}
-% END MINER CHANGES: I changed all \gamma_0 here to \alpha without further noticing.
-% END MOVED AND MODIFIED FROM ABOVE
 
@@
 	Birkh{\"a}user Boston, Inc., Boston, MA, 1983.
-	% \MR{701538}
 
 \bibitem{AthreyaNey1974Functionals}
-	% Athreya, K.~B. and Ney, P.~E.:
 	Athreya, K. and Ney, P.:
@@
 	Ann. Probability \textbf{2} (1974), 339--343.
-  % \MR{0356264}
 
@@
 	Springer-Verlag, New York-Heidelberg, 1972.
-	% \MR{0373040}
 
 \bibitem{BinghamGoldieTeugels1989Regular}
-	% Bingham, N.~H., Goldie, C.~M. and Teugels J.~L.:
 	Bingham, N., Goldie, C. and Teugels J.:
@@
 	Cambridge University Press, Cambridge, 1989.
-	% \MR{1015093}
 
 \bibitem{Borovkov1989Method}
-	% Borovkov, K.~A.:
 	Borovkov, K.:
@@
 	translation in Theory Probab. Appl. \textbf{33} (1988), no. 1, 105–113.
-	% \MR{0939993}
 
 \bibitem{EckhoffKyprianouWinkel2015Spines}
-	% Eckhoff, M., Kyprianou, A.~E., Winkel, M.:
 	Eckhoff, M., Kyprianou, A. and Winkel, M.:
@@
 	Ann. Probab. \textbf{43} (2015), no. 5, 2545–2610.
-	% \MR{3395469}
 
 \bibitem{EnglanderKyprianou2004Local}
-	% Engländer, J., Kyprianou, A.~E.:
 	Engländer, J. and Kyprianou, A.:
@@
 	Ann. Probab. \textbf{32} (2004), no. 1A, 78–99.
-	% \MR{2040776}
 
 \bibitem{EvansPerkins1990Measure-valued}
-	% Evans, S.~N., Perkins, E.:
 	Evans, S. and Perkins, E.:
@@
 	Israel J. Math. \textbf{71} (1990), no. 3, 329–337.
-	% \MR{1088825}
 
 \bibitem{GoldsteinHoppe1978Critical}
-	% Goldstein, M.~I., Hoppe, F.~M.:
 	Goldstein, M. and Hoppe, F.:
@@
 	J. Math. Anal. Appl. \textbf{65} (1978), no. 3, 675–686.
-	% \MR{0510478}
 
 \bibitem{Harris2002The-theory}
-	% Harris, T. E.:
 	Harris, T.:
@@
 	Die Grundlehren der Mathematischen Wissenschaften, Bd. 119 Springer-Verlag, Berlin; Prentice-Hall, Inc., Englewood Cliffs, N.J. 1963.
-	% \MR{0163361}
 
 \bibitem{IyerLegerPego2015Limit}
-	% Iyer, G., Leger, N., Pego, R.~L.:
 	Iyer, G., Leger, N. and Pego, R.:
@@
 	Ann. Appl. Probab. \textbf{25} (2015), no. 2, 675–713.
-	% \MR{3313753}
 
@@
 	J. Math. Anal. Appl. \textbf{19} (1967), 409--430.
-	% \MR{0212895}
 
@@
 	Teor. Verojatnost. i Primenen. \textbf{11} (1966), 579--611.
-	% \MR{0207052}
 
@@
 	Tohoku Math. J. (2) \textbf{60} (2008), no.~4, 527--547.
-	% \MR{2487824}
+
+%new
+\bibitem{KSV1} Kim, P., Song, R. and Vondracek, Z.:
+Two-sided Green function estimates for killed subordinate Brownian motions.
+\emph{Proc. London Math. Soc.} \textbf{104} (2012), 927--958.
+
+\bibitem{KSV2} Kim, P., Song, R. and Vondracek, Z.:
+Potential theory of subordinate Brownian motions with Gaussian components.
+\emph{Stoch. Proc. Appl.} \textbf{123} (2013), 764--795.
+%end new
 
 \bibitem{Kolmogorov1938Zur-losung}
-	% Kolmogorov, A.~N.:
 	Kolmogorov, A.:
@@
 \bibitem{Kyprianou2014Fluctuations}
-	% Kyprianou, A.~E.:
 	Kyprianou, A.:
@@
 	Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
-	% \MR{3155252}
 
 \bibitem{Kyprianou2008Continuous}
-	% Kyprianou, A.~E., Pardo, J. C.:
 	Kyprianou, A. and Pardo, J.:
 	\emph{Continuous-state branching processes and self-similarity.}
-	J. Appl. Probab. \text{45} (2008), no. 4, 1140–1160.
-	% \MR{2484167}
+	J. Appl. Probab. \textbf{45} (2008), no. 4, 1140–1160.
 
@@
 	Probability and its Applications (New York), Springer, Heidelberg, 2011.
-	% \MR{2760602}
 
@@
 	J. Appl. Probab. \textbf{46} (2009), no.~2, 479--496.
-	% \MR{2535827}
 
 \bibitem{Pakes2010Critical}
-	% Pakes, A.~G.:
 	Pakes, A.:
@@
 	Adv. in Appl. Probab. \textbf{42} (2010), no.~2, 460--488.
-	% \MR{2675112}
 
@@
   \emph{An invariance principle for branching diffusions in bounded domains.}
-  Probab. Theory Related Fields 173 (2019), no. 3-4, 999–1062.
-
-	% Powell, E.:
-	% \emph{An invariance principle for branching diffusions in bounded domains.}
-	% \ARXIV{1512.00031}
+  Probab. Theory Related Fields  \textbf{173} (2019), no. 3-4, 999–1062.
 
@@
   \emph{A 2-spine decomposition of the critical Galton-Watson tree and a probabilistic proof of Yaglom's theorem.}
-  Electron. Commun. Probab. 23 (2018), Paper No. 42, 12 pp.
-
-	% Ren, Y.-X., Song, R. and Sun, Z.:
-	% \emph{A 2-spine decomposition of the critical Galton-Watson tree and a probabilistic proof of Yaglom's theorem.}
-	% \ARXIV{1706.07125}
+  Electron. Commun. Probab. \textbf{23} (2018), Paper No. 42, 12 pp.
 
@@
 
-	% \bysame:
-	% \emph{Spine decompositions and limit theorems for a class of critical superprocesses.}
-	% \ARXIV{1711.09188}
-
 \bibitem{RenSongZhang2015Limit}
@@
 	Illinois J. Math. \textbf{59} (2015), no.~1, 235--276.
-	% \MR{3459635}
 
 \bibitem{RenSongZhang2017Central}
-	% \bysame:
 	Ren, Y.-X., Song, R. and Zhang, R.:
@@
 	Ann. Probab. \textbf{45} (2017), no.~1, 564--623.
-	% \MR{3601657}
 
 \bibitem{RenYangZhao2014Conditional}
-	% Ren, Y.-X., Yang, T., Zhao, G.-H.:
 	Ren, Y.-X., Yang, T. and Zhao, G.:
@@
 	Sci. China Math. \textbf{57} (2014), no. 12, 2577–2588.
-	% \MR{3275407}
 
 \bibitem{Schaefer1974Banach}
-	% Schaefer, H.~H.:
 	Schaefer, H.:
@@
 	Die Grundlehren der mathematischen Wissenschaften, Band 215. Springer-Verlag, New York-Heidelberg, 1974.
-	% \MR{0423039}
 
 \bibitem{Slack1968A-branching}
-	% Slack, R.~S.:
 	Slack, R.:
@@
 	Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{9} (1968), 139--145.
-	% \MR{0228077}
 
 \bibitem{Slack1972Further}
-	% \bysame: 
 	Slack, R.:
@@
 	Z. Wahrscheinlichkeitstheorie und Verw. Gebiete \textbf{25} (1972/73), 31–38.
-	% \MR{0331539}
 
 \bibitem{Vatutin1977Limit}
-	% Vatutin, V. A.:
 	Vatutin, V.:
@@
 	Mat. Sb. (N.S.) \textbf{103(145)} (1977), no. 2, 253–264, 319.
-	% \MR{0443115}
 
 \bibitem{Yaglom1947Certain}
-	% Yaglom, A. M.:
 	Yaglom, A.:
@@
 	Doklady Akad. Nauk SSSR (N.S.) \textbf{56} (1947). 795–798.
-	% \MR{0022045}
 
 \bibitem{Zolotarev1957More}
-	% Zolotarev, V. M.:
 	Zolotarev, V.:
@@
 	Teor. Veroyatnost. i Primenen. \textbf{2} (1957), 256–266.
-	% \MR{0096321}
 

### 2019-07-17 response.tex
change response.tex

@@
 % * Document body
-We are grateful to the referees' for their helpful comments.
+We are grateful to the referees for their helpful comments.
 We have incorporated all the comments made by the referees.
@@
 
-  {\it Done, as suggested.}
+  {\it Done as suggested.}
 \item
@@
 
-  {\it We added them back, as suggested.}
+  {\it We added them as suggested.}
 \item
@@
 
-  {\it Added, as suggested.}
+  {\it Added as suggested.}
 \item
@@
 
-  {\it Changed, as suggested.}
+  {\it Changed as suggested.}
 \item
@@
 
-  {\it Added, as suggested.}
+  {\it Added as suggested.}
 \end{enumerate}
@@
 
-  {\it TBD.}
+  {\it We gave some examples in Appendix A.1 and we also referred the reader Appendix A.1 at the end of the paragraph  after Assumption 3.}
 \item
@@
 \item
-  p.6 paragraph after Assumption 2: The notation is a bit confusing.
-So $\phi$ is the principal eigenfunction for the motion with the potential $\beta$ but $\varphi$ is the same without the potential.
+  p.6 paragraph after Assumption 2: The notation is a bit confusing. So $\phi$ is the principal eigenfunction for the motion with the potential $\beta$ but $\varphi$ is the same without the potential.
   This should be made more clear.
@@
 
-  {\it Assumption 2 excluded the first case. We added a paragraph after Assumption 2 which explains that the principal eigenfunction without the potential is indeed well defined. 
+  {\it
+
+  Assumption 1 excludes the first case. We added a paragraph after Assumption 1
+  which explains that the principal eigenfunction of the original semigroup $(P_t)_{t\ge0}$ is indeed well defined.
     Note that in the new version the notations $\varphi$ and $\varphi^*$ are changed into $\widetilde \phi$ and $\widetilde \phi^*$, respectively.}
@@
   {\it We agree.
-    This doesn't compromise the later proofs.
+    This does not compromise the later proofs.
     We emphasized this in the new version to avoid any confusions.}
@@
 
-  {\it We should simply say that. 
+  {\it 
     Done, as suggested.}

### 2019-07-17 stableLimit.tex
change stableLimit.tex
See if I agree all the changes

@@
 	University of Illinois at Urbana-Champaign\\
-	Urbana, IL 61801}
+	% Urbana, IL 61801}
+	Urbana, IL, USA, 61801}
 \email{rsong@illinois.edu}
@@
 {Zhenyao Sun\\
-%	School of Mathematical Sciences\\
 School of Mathematics and Statistics\\
-%	Peking University\\
 Wuhan University\\
-%	Beijing, P. R. China, 100871}
-Wuhan, Hubei 430072, P. R. China}
+% Wuhan, Hubei 430072, P. R. China}
+Wuhan, Hubei, P. R. China, 430072}
 \email{zhenyao.sun@pku.edu.cn}
@@
 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
-%Let the process be critical in the sense that the maximal eigenvalue of $M$ is $1$.
 Assume that the process is critical in the sense that the maximal eigenvalue of $M$ is $1$.
@@
 For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
-Vatutin \cite{Vatutin1977Limit} also considered analogous results for 
-%the continuous time multitype critical Galton-Watson processes.
-continuous time multitype critical Galton-Watson processes.
+Vatutin \cite{Vatutin1977Limit} also considered analogous results for continuous time multitype critical Galton-Watson processes.
 
@@
 
-In this paper, we are interested in a class of measure-valued branching Markov 
-%process known as $(\xi, \psi)$-superprocesses:
-processes known as $(\xi, \psi)$-superprocesses:
+In this paper, we are interested in a class of measure-valued branching Markov processes known as $(\xi, \psi)$-superprocesses:
 $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact separable metric space $E$;
@@
 \end{align}
-where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and 
-%is independent to the initial position $x$.
-is independent of the initial position $x$.
+where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent of the initial position $x$.
 Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
@@
 \end{align}
-where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and 
-%is independent to the initial position $x$.
-is independent of the initial position $x$.
+where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent of the initial position $x$.
 
@@
 where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0-1$).
-Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$
-%does not depend the initial configuration $\mu$.
-does not depend on the initial configuration $\mu$.
+Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ does not depend on the initial configuration $\mu$.
 Precise statements of the assumptions and the results are presented in the next subsection.
@@
 We first fix our notation.
-%For any measurable space $(E,\mathscr E)$, we denote by $\mathscr E$ the collection of all real-valued measurable functions on $E$.
-%Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
-%Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$ and $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
-%Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
-%Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
-%For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
-%We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
-%For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
-%In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
-%If $E$ is a topological space, we denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
 Unless stated explicitly otherwise, $E$ is assumed to be a locally compact separable metric space. 
@@
 We now give the definition of a $(\xi, \psi)$-superprocess:
-%Let $E$ be a locally compact separable metric space, the spatial motion 
 Let the spatial motion 
@@
 
-%moved from above
 We will write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
-%end move
-
-%Define $(P_t^*)_{t\geq 0}$ as the dual of the transition semigroup $(P_t)_{t\geq 0}$, i.e.
+
 Let $(P_t^*)_{t\geq 0}$ be the dual of the transition semigroup $(P_t)_{t\geq 0}$ in $L^2(E, m)$, i.e.,
@@
 $\widetilde \lambda := \sup \text{Re}(\sigma(\widetilde L)) = \sup \text{Re}(\sigma(\widetilde L^*))$ is a common eigenvalue of multiplicity $1$ for both $\widetilde L$ and $\widetilde L^*$.
-%Using the argument in \cite{RenSongZhang2015Limit}, 
 By the argument in \cite{RenSongZhang2015Limit},
@@
 
-%It is also proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} 
-It is also proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} 
-that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
+It is also proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that there exists a function $p^\beta_t(x,y)$ on $(0,\infty) \times E \times E$ which is continuous in $(x,y)$ for each $t>0$ such that
 \begin{align}
@@
 According to \cite[Theorem V.6.6]{Schaefer1974Banach}, $\lambda := \sup \text{Re}(\sigma(L)) = \sup \text{Re}(\sigma(L^*))$ is a common eigenvalue of multiplicity $1$ for both $L$ and $L^*$.
-%Using the argument in \cite{RenSongZhang2015Limit}, 
-By the argument in \cite{RenSongZhang2015Limit}, 
-the eigenfunctions $\phi$ of $L$ and $\phi^*$ of $L^*$ associated with the eigenvalue $\lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
+By the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\phi$ of $L$ and $\phi^*$ of $L^*$ associated with the eigenvalue $\lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
 We further normalize $\phi$ and $\phi^*$ by $\langle\phi, \phi\rangle_m = \langle\phi,\phi^*\rangle_m = 1$ so that they are unique.
   Moreover, for each $t\geq 0$ and $x\in E$, we have $P^\beta_t \phi(x) = e^{\lambda t} \phi(x)$ and $P^{\beta *}_t \phi^*(x) = e^{\lambda t} \phi^*(x)$.
-%We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ 
-We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ as
-the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of $L$ (resp. $L^*$).
+We refer to $\phi$ (resp. $\phi^*$) and $\lambda$ as the \emph{principal eigenfunction} and the \emph{principal eigenvalue} of $L$ (resp. $L^*$).
 
@@
 
-%Our next assumption on the spatial process $\xi$ is the following:
 Our next assumption is on the spatial motion $\xi$:
@@
 \end{align}
-%We refer our readers to \cite{RenSongZhang2015Limit} for a list of examples of processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3}.
 Assumption \ref{asp: 3} is a pretty strong assumption on the semigroup $\{P_t : t \ge 0\}$. However, this assumption is satisfied in a lot of cases.  
@@
 
-%Our assumption on the branching mechanism is the following:
-Our assumption is on the branching mechanism:
+% DELETED
+% Our assumption is on the branching mechanism:
+% END DELETED
 \begin{asp} \label{asp: 4}
@@
 In Subsection \ref{sec: conditional distribution}, we give the equation that characterize the one-dimensional distributions.
-%In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterize the distribution with Laplace transform \eqref{e:zloltarev}.
-%Finally, in Subsection \ref{sec: proof of result 3}, we make comparison of these two equations and give the proof of Theorem \ref{thm: main theorem}(3).
 In Subsection \ref{sec: proof of result 3}, we give the proof of Theorem \ref{thm: main theorem}(3).
-In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterizes the distribution with Laplace transform \eqref{e:zloltarev}, which is used in the proof of Theorem \ref{thm: main theorem}(3) given Subsection \ref{sec: proof of result 3}.
+% In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterizes the distribution with Laplace transform \eqref{e:zloltarev}, which is used in the proof of Theorem \ref{thm: main theorem}(3) given Subsection \ref{sec: proof of result 3}.
+In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterizes the distribution with Laplace transform \eqref{e:zloltarev}, which is used in the proof of Theorem \ref{thm: main theorem}(3).
 
@@
 Let $t_0 \in [-\infty,\infty]$.
-%moved from below
 In this Subsection, $(E, \mathscr E)$ is assume to be a  measurable space.
-%emd move 
 For any $f_0, f_1\in \mathscr B^{++}({\mathbb R})$, we say $f_0$ and $f_1$ are \emph{asymptotically equivalent at $t_0$}, if $\big|\frac{f_0(t)}{f_1(t)} - 1\big| \xrightarrow[t\to t_0]{} 0$;
 and in this case, we write $f_0(t) \stackrel[t\to t_0]{}{\sim} f_1(t)$.
-%moved up
-%Let $E$ be a measurable space.
-%end move
-%For any $g_0, g_1\in \mathscr B^{++}({\mathbb R\times E})$, 
-For any strictly positive measurable functions $g_0, g_1$ on $\mathbb R\times E$, 
-we say $g_0$ and $g_1$ are \emph{uniformly asymptotically equivalent at $t_0$}, if $\sup_{x\in E}\big|\frac{g_0(t,x)}{g_1(t,x)} - 1\big| \xrightarrow[t\to t_0]{} 0$; and in this case, we write $g_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}g_1(t,x)$.
+For any strictly positive measurable functions $g_0, g_1$ on $\mathbb R\times E$, we say $g_0$ and $g_1$ are \emph{uniformly asymptotically equivalent at $t_0$}, if $\sup_{x\in E}\big|\frac{g_0(t,x)}{g_1(t,x)} - 1\big| \xrightarrow[t\to t_0]{} 0$; and in this case, we write $g_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}g_1(t,x)$.
 
 \begin{lem} \label{lem: asymptotic equivalent of integration}
-	Suppose that 
-%	$f_0,f_1\in \mathscr B^{++}_b({\mathbb R \times E})$ 
-$f_0,f_1$ are bounded strictly positive measurable functions on $\mathbb R \times E$
-	and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
-%	If $m \in \mathcal M^1_E$, then
-If $f$ is a finite measure on $(E, \mathscr E)$, then
+	Suppose that $f_0,f_1$ are bounded strictly positive measurable functions on $\mathbb R \times E$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
+% If $f$ is a finite measure on $(E, \mathscr E)$, then
+If $m$ is a finite measure on $(E, \mathscr E)$, then
   \begin{align}
@@
 \begin{proof}
-	Since $f \in \mathcal R_\alpha^0$, we know that $\tilde f \in \mathcal R_{-\alpha}^\infty$ with $\tilde f(t):= f(t^{-1})$.
+	Since $f \in \mathcal R_\alpha^0$, we know that $\widetilde f \in \mathcal R_{-\alpha}^\infty$ with $\widetilde f(t):= f(t^{-1})$.
 	Noticing that $-\alpha > 0$, according to Lemma \ref{lem: regularly variation and inverse}, there exists $h \in \mathcal R_{-1/\alpha}^{\infty}$ such that
   \begin{align} \label{eq: inverse between h and f}
-    h(\tilde f(t))
+    h(\widetilde f(t))
     \stackrel[t\to \infty]{}{\sim}
@@
     \quad
-    \tilde f(h(t))
+    \widetilde f(h(t))
     \stackrel[t\to \infty]{}{\sim}
@@
 	Denoting by $h_0 := g_0^{-1}$, we can verify that \eqref{eq: inverse between h and f} is valid with $h$ replaced by $h_0$.
-	According to Lemma \ref{lem: regularly variation and inverse}, 
-	%$h$ and $h_0$ are asymptotic equivalent at $\infty$.
-	$h$ and $h_0$ are asymptotically equivalent at $\infty$.
+	According to Lemma \ref{lem: regularly variation and inverse}, $h$ and $h_0$ are asymptotically equivalent at $\infty$.
 	Hence, so are $g$ and $g_0$.
@@
 \begin{lem}\label{lem:regularly_variation_and_integration}
-%	Let $E$ be a measurable space with a non-degenerate measure $m \in \mathcal M^1_E$.
-Let $(E, \mathscr E)$ be a measurable space and $m$ a  non-degenerate measure
-on $(E, \mathscr E)$
-%	Let $ \gamma \in \mathscr B_b(E)$ with
-Let $f$ be a bounded measurable function on $E$ with 
+  % Let $(E, \mathscr E)$ be a measurable space and $m$ a  non-degenerate measure on $(E, \mathscr E)$.
+  Let $(E, \mathscr E)$ be a measurable space and $m$ be a  non-degenerate measure on $(E, \mathscr E)$.
+  % Let $f$ be a bounded measurable function on $E$ with 
+  Let $\gamma$ be a bounded measurable function on $E$ with 
   \begin{align}
@@
 Suppose that Assumptions \ref{asp: 1}--\ref{asp: 2} hold.
-%Noting that $\phi^*$ is the eigenfunction of semigroup $(P_t^{\beta*})_{t\geq 0}$, we have
 Since $\phi^*$ is the principal eigenfunction of the semigroup $(P_t^{\beta*})_{t\geq 0}$, we have
@@
 \end{align}
-%Therefore, integrating the both sides of \eqref{eq:mean-fkpp} with respect to measure 
 Therefore, integrating both sides of \eqref{eq:mean-fkpp} with respect to the measure 
@@
 Notice that $\mathbf P^{X_T(g)}_\mu(X_0 = \mu) = 1$.
-Also notice that $\mathbb N_\mu$ is not a probability measure, 
-%but after the transform, 
-but after the size-biased transform, 
-$\mathbb N^{W_T(g)}_\mu$ is a probability measure.
+Also notice that $\mathbb N_\mu$ is not a probability measure, but after the size-biased transform, $\mathbb N^{W_T(g)}_\mu$ is a probability measure.
 Since $\mathbb N_{\mu}(\|W_0\|\neq 0) = 0$, we have $\mathbb N_\mu^{W_T(g)}(\|W_0\|= 0) = 1$.
-Similarly, $\Pi_{\mu}$ is not typically a probability measure, 
-%but after the transform, 
-but after the size-biased transform, 
-$\Pi_{\mu}^{(T,g)}$ is a probability measure.
+Similarly, $\Pi_{\mu}$ is not typically a probability measure, but after the size-biased transform, $\Pi_{\mu}^{(T,g)}$ is a probability measure.
 We note that
@@
 The classical spine decomposition theorem, see 
-%\cite{EckhoffKyprianouWinkel2015Spines}, \cite{EnglanderKyprianou2004Local} and \cite{LiuRenSong2009Llog} for example, 
 \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog} for example, 
-considered the case when $g = \phi$ only.
+% considered the case when $g = \phi$ only.
+considered the case $g = \phi$ only.
 In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is, the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$,	on the finite time interval $[0,T]$.
@@
 \begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
-%	If $F$ is a bounded Borel function on $E\times [0,1]\times [0,\infty)$ 
 If $F\in \mathscr B_b(E\times [0,1]\times [0,\infty)$ is
@@
 \begin{lem}\label{lem: Fatou-ergodic lemma for the uderlying process}
-%	Let $F$ be a non-negative bounded Borel function on $E\times [0,1]\times [0,\infty)$.
   Let $F\in \mathscr B^+_b(E\times [0,1]\times [0,\infty))$.
@@
 	For each $(y,u,t)\in E\times [0,1]\times [0,\infty)$, define $\bar F(y,u,t) := \sup_{s:s\geq t} F(y,u,s)$.
-%	Then $\bar F$ is a bounded Borel  function on $E\times [0,1]\times [0,\infty)$ such that
-Then $F\in \mathscr B_b(E\times [0,1]\times [0,\infty))$ and
+% Then $F\in \mathscr B_b(E\times [0,1]\times [0,\infty))$ and
+Then $\bar F\in \mathscr B_b(E\times [0,1]\times [0,\infty))$ and
 \begin{align}
@@
   Recall that $\kappa_0 = \operatorname{ess\,inf}_{m(dx)} \kappa(x) $ and $\gamma_0 = \operatorname{ess\,inf}_{m(dx)} \gamma(x)$.
-	For each $x\in E$, let $\tilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\tilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$.
-  Then, we know that $m(\tilde \kappa \neq \kappa) = 0$ and $m(\tilde \gamma \neq \gamma) = 0$.
-	Define $\widetilde \psi(x,z) := - \beta(x)z+ \tilde \kappa(x)z^{\tilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z),$ $m$-almost everywhere.
+	For each $x\in E$, let $\widetilde \kappa(x) := \kappa(x) \mathbf 1_{\kappa(x)\geq \kappa_0} + \kappa_0 \mathbf 1_{\kappa(x) < \kappa_0}$ and $\widetilde \gamma(x) := \gamma(x) \mathbf 1_{\gamma(x)\geq \gamma_0} + \gamma_0 \mathbf 1_{\gamma(x) < \gamma_0}$.
+  Then, we know that $m(\widetilde \kappa \neq \kappa) = 0$ and $m(\widetilde \gamma \neq \gamma) = 0$.
+	Define $\widetilde \psi(x,z) := - \beta(x)z+ \widetilde \kappa(x)z^{\widetilde \gamma(x)}$ for each $x\in E$ and $z\geq 0$, then for each $z\geq 0$, $\widetilde \psi(\cdot, z) = \psi(\cdot , z),$ $m$-almost everywhere.
 
@@
 \end{align}
-So, we can consider $\{X; \mathbf P\}$ as a superprocess with branching mechanism $\tilde \psi$.
+So, we can consider $\{X; \mathbf P\}$ as a superprocess with branching mechanism $\widetilde \psi$.
 Define
@@
   From Proposition \ref{prop: non-presistent}, we know that 
-  %our superprocess $\{X;\mathbf P\}$ is non-persistent,
-%  and more precisely,
-that
   \begin{align}
@@
   \end{align}
- %new
   which implies that $\{X; \mathbf P\}$ is non-persistent.
- %end new 
-  According to \eqref{eq:mean_formula}, Assumption \ref{asp: 2} and the fact that $\phi$ is 
-%  the eigenfunction of semigroup $(P_t^\beta)_{t\geq 0}$, 
-the principal eigenfunction of the semigroup $(P_t^\beta)_{t\geq 0}$, 
-  we have $\mathbf P_{\delta_x}[X_t(\phi)] = P_t^\beta \phi(x) = e^{\lambda t} \phi(x)= \phi(x)>0$.
+  According to \eqref{eq:mean_formula}, Assumption \ref{asp: 2} and the fact that $\phi$ is the principal eigenfunction of the semigroup $(P_t^\beta)_{t\geq 0}$, we have $\mathbf P_{\delta_x}[X_t(\phi)] = P_t^\beta \phi(x) = e^{\lambda t} \phi(x)= \phi(x)>0$.
   Therefore,
@@
   However, to prove Theorem \ref{thm: main theorem}(2), we need to consider the speed of this convergence.
-  This is answered in the following two propositions 
-  %whose proof is postponed after the current proof.
-  whose proofs are postponed after this proof.
+  This is answered in the following two propositions whose proofs are postponed after this proof.
   The first proposition says that $(\phi^{-1}v_t)(x)$ will converge to $0$ with the same speed as $\langle v_t,\phi^*\rangle_m$, uniformly in $x\in E$:
@@
   \end{prop}
-%    From \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0}, we have
   It follows from \eqref{eq: equation for mu v-t} and \eqref{eq: uniform converges to 0} that
@@
 
-%    Also from that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, 
-It follows from the fact that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, 
-\eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} 
-%and Proposition \ref{prop: convergence in a same speed}, we have
-and Proposition \ref{prop: convergence in a same speed} that
+    It follows from the fact that $x \stackrel[x\to 0]{}{\sim} - \log(1-x)$, \eqref{eq: equation for mu v-t}, Lemma \ref{lem: asymptotic equivalent of integration} and Proposition \ref{prop: convergence in a same speed} that
     \begin{align}
@@
     \end{align}
-%    Therefore, according to Proposition \ref{prop: regularly varying of vt-phi-star}, we get the desired result.
     Then the desired result follows immediately from Proposition \ref{prop: regularly varying of vt-phi-star}.
@@
 	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
-%new
 We will prove that for an appropriate map $t_0$ with
@@
 
-%The underline idea of the proof is to show that 
-The main idea is to show that
-both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
+The main idea is to show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
 This is done in the following two lemmas whose proofs are postponed after this proof.
@@
     & \leq c_0 e^{-c_1 t_0}\langle v_{t-t_0},\phi^* \rangle_m.
-    % ADDED
     \qedhere
-      % END ADDED
   \end{align}
@@
   [Proof of Lemma \ref{lem:upperbound_of_epsilon-2}]
-Using the Markov property of the spine process and 
-%the property of Poisson random measures, we have
-properties Poisson random measures, we have
+% Using the Markov property of the spine process and properties Poisson random measures, we have
+Using the Markov property of the spine process and properties of Poisson random measures, we have
 \begin{align}\label{eq:epsilon-2}
@@
 
-%To complete the proof, we are left to verify the claim \eqref{eq:epsilon-2-one}.
 We now verify the claim \eqref{eq:epsilon-2-one}.
@@
 \begin{proof}
-%	It follows from Theorem 
-	It follows from Theorems
-	\ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
+	It follows from Theorems \ref{thm: size-biased decomposition} and \ref{thm: spine representation} that
   \begin{align}
@@
 \end{equation}
-%The underlying idea of the proof is 
-The main idea is
-to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense when $t\to \infty$.
+The main idea is to show that $J_G,J'_G,J_g$ and $J'_g$ are approximately equal in some sense when $t\to \infty$.
 
@@
 
-%For the rest of the proof, we use the following notation:
 In the remainder of this proof, we use the following notation:
@@
 \end{align}
-%  Now, use this version of the revers Fatou's lemma and \eqref{eq: limsup of J_G - J'_g} to have that
 Using this version of the reverse Fatou's lemma and \eqref{eq: limsup of J_G - J'_g}, we get that
@@
 \label{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}
-%In the proof of Theorem \ref{thm: main theorem}(3), we have used the following notations which we recall here:
 In this Subsection, we give the proofs of the two lemmas used in the proof of Theorem \ref{thm: main theorem}(3). We think these two lemmas are of independent interest.
@@
 
-%The following analytical results are used in the proof of Theorem \ref{thm: main theorem} (3).
-
-%moved below
-\begin{comment}
+\begin{lem}\label{lem: F is zero}
+	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
+  \begin{align}
+    \label{eq:Gronwall_inequlity}
+    F(\theta)
+    \leq C \int_0^\theta \|  F(ru^{ \frac{1}{\alpha - 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0.
+  \end{align}
+	Then $F \equiv 0$.
+\end{lem}
+
+\begin{proof}
+  We claim that for each $k \in \mathbb N$, we have
+  \begin{align}
+    \label{eq:upperbound_for_F}
+    F(\theta) \leq \frac{C^k \theta^k}{k!},
+    \quad \theta \geq 0.
+  \end{align}
+  In fact, when $k = 1$ this is trival. Now if \eqref{eq:upperbound_for_F} is true for a fixed $k \in \mathbb N$, then from
+  \begin{align}
+    &F(\theta)
+      \leq C \int_0^\theta \left\|  F\left(ru^{ \frac{1}{\alpha - 1}  }\right)\right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+      \leq C \int_0^\theta \left\|  \frac{1}{k!}\left(Cru^{ \frac{1}{\alpha - 1}  } \right)^k \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+    \\ &\leq \frac{C^{k+1}}{k!} \left(\int_0^\theta r^k dr\right) \cdot \left\|u^{\frac{k}{\alpha - 1}} \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
+  \end{align}
+  we have that \eqref{eq:upperbound_for_F} is true for $k+1$.
+  Therefore, by induction, \eqref{eq:upperbound_for_F} is true for all $k \in \mathbb N$.
+
+  Letting $k \to \infty$ in \eqref{eq:upperbound_for_F}, we get that $F(\theta) = 0$ for each $\theta \geq 0$.
+\end{proof}
+
 \begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
@@
 \end{lem}
-\end{comment}
-%end move
-
-\begin{lem}\label{lem: F is zero}
-	Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
-  \begin{align}
-    \label{eq:Gronwall_inequlity}
-    F(\theta)
-    \leq C \int_0^\theta \|  F(ru^{ \frac{1}{\alpha - 1}  })\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr, \quad \theta \geq 0.
-  \end{align}
-	Then $F \equiv 0$.
-\end{lem}
-
-\begin{proof}
-%  [Proof of Lemma \ref{lem: F is zero}]
-  We claim that for each $k \in \mathbb N$, we have
-  \begin{align}
-    \label{eq:upperbound_for_F}
-    F(\theta) \leq \frac{C^k \theta^k}{k!},
-    \quad \theta \geq 0.
-  \end{align}
-  In fact, when $k = 1$ this is trival. Now if \eqref{eq:upperbound_for_F} is true for a fixed $k \in \mathbb N$, then from
-  \begin{align}
-    &F(\theta)
-      \leq C \int_0^\theta \left\|  F\left(ru^{ \frac{1}{\alpha - 1}  }\right)\right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
-      \leq C \int_0^\theta \left\|  \frac{1}{k!}\left(Cru^{ \frac{1}{\alpha - 1}  } \right)^k \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
-    \\ &\leq \frac{C^{k+1}}{k!} \left(\int_0^\theta r^k dr\right) \cdot \left\|u^{\frac{k}{\alpha - 1}} \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
-  \end{align}
-  we have that \eqref{eq:upperbound_for_F} is true for $k+1$.
-  Therefore, by induction, \eqref{eq:upperbound_for_F} is true for all $k \in \mathbb N$.
-
-  Letting $k \to \infty$ in \eqref{eq:upperbound_for_F}, we get that $F(\theta) = 0$ for each $\theta \geq 0$.
-\end{proof}
-
-%moved from above
-\begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
-  Suppose that $\alpha \in (1,2).$
-  The non-linear delay equation
-  \begin{align} \label{eq: equation for the distribution}
-    G( \theta)
-    = \int_0^\theta \exp\Big\{ - \frac{\alpha} {\alpha - 1} \int_0^1 G(ru^{\frac{1}{\alpha - 1} })^{\alpha - 1}\frac{du}{u} \Big\} dr,
-    \quad \theta \geq 0,
-  \end{align}
-	has a unique solution:
-  \begin{align}\label{eq: solution for the equation}
-    G(\theta)
-    = \Big(\frac{1}{1+\theta^{-(\alpha - 1)}}\Big)^{\frac{1}{\alpha - 1}},
-    \quad \theta \geq 0.
-  \end{align}
-\end{lem}
-
-%end move 
-%\begin{proof}[Proof of Lemma \ref{lem: characterize the general Mittag-Leffler distribution}]
+
 \begin{proof}
@@
 \bibitem{EnglanderKyprianou2004Local}
-	Engländer, J. and Kyprianou, A.:
+	% Engländer, J. and Kyprianou, A.:
+	Engl\"{a}nder, J. and Kyprianou, A.:
 	\emph{Local extinction versus local exponential growth for spatial branching processes.}
@@
 
-%new
-\bibitem{KSV1} Kim, P., Song, R. and Vondracek, Z.:
-Two-sided Green function estimates for killed subordinate Brownian motions.
-\emph{Proc. London Math. Soc.} \textbf{104} (2012), 927--958.
-
-\bibitem{KSV2} Kim, P., Song, R. and Vondracek, Z.:
-Potential theory of subordinate Brownian motions with Gaussian components.
-\emph{Stoch. Proc. Appl.} \textbf{123} (2013), 764--795.
-%end new
+\bibitem{KSV1} 
+  Kim, P., Song, R. and Vondracek, Z.:
+  % Two-sided Green function estimates for killed subordinate Brownian motions.
+  \emph{Two-sided Green function estimates for killed subordinate Brownian motions.}
+  % \emph{Proc. London Math. Soc.} \textbf{104} (2012), 927--958.
+  Proc. London Math. Soc. \textbf{104} (2012), 927--958.
+
+\bibitem{KSV2} 
+  Kim, P., Song, R. and Vondracek, Z.:
+  % Potential theory of subordinate Brownian motions with Gaussian components.
+  \emph{Potential theory of subordinate Brownian motions with Gaussian components.}
+  % \emph{Stoch. Proc. Appl.} \textbf{123} (2013), 764--795.
+  Stoch. Proc. Appl. \textbf{123} (2013), 764--795.
 

### 2019-07-18 stableLimit.tex
change stableLimit.tex
My changes are done.

@@
 \setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
-\usepackage[utf8]{inputenc}
+% \usepackage[utf8]{inputenc}
 \usepackage{hyperref}
-\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
-\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
+% \def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
+% \def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
 \usepackage{mathrsfs}
@@
 Research in this direction was first conducted by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up, which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance.
-The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$ with infinite variance.
+The main result of  \cite{Slack1968A-branching} can be stated as follows. 
+% Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$ with infinite variance.
+Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$.
 Assume that the  generating function $f(s)$ of the offspring distribution is of the form
@@
 $\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty)$ of the form
-\begin{align} \label{eq: branching mechanism}
+\begin{align} 
+\label{eq: branching mechanism}
 	\psi(x,z):=
-	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
+	% - \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
+	- \beta(x) z + \sigma (x)^2 z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
 	\quad x\in E, z\geq 0,
 \end{align}
-where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+% where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+where $\beta, \sigma\in \mathscr B_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
 For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
@@
 We will write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
-
 Let $(P_t^*)_{t\geq 0}$ be the dual of the transition semigroup $(P_t)_{t\geq 0}$ in $L^2(E, m)$, i.e.,
@@
 \end{align}
-Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+% Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators on $L^2(E,m)$.
 Let $\widetilde L$ and $\widetilde L^*$ be the generators of the semigroups $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$, respectively.
@@
 \end{align}
-It is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+% It is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
+It is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators on $L^2(E,m)$.
 Let $L$ and $L^*$ be the generators of the semigroups $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$, respectively.
@@
 
-% DELETED
 % Our assumption is on the branching mechanism:
-% END DELETED
+Recall that the branching mechanism is given by \eqref{eq: branching mechanism}. 
+We assume the following:
 \begin{asp} \label{asp: 4}
@@
 To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 	$X$.
-  Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a martingale change of measure, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an measure-valued immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
+  % Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a martingale change of measure, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an measure-valued immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
+  Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a martingale change of measure, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and a measure-valued immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
 The martingale used for the change of measure is $(e^{-\lambda t} X_t(\phi))_{t\geq 0}$.
@@
 
-\section{Preliminaries} \label{sec: Preliminaries}
-\subsection{Asymptotic equivalence} \label{sec: Asymptotic equivalence}
+\section{Preliminaries} 
+\label{sec: Preliminaries}
+\subsection{Asymptotic equivalence} 
+\label{sec: Asymptotic equivalence}
 In this subsection, we give a lemma on asymptotic equivalence.	
@@
   % If $f$ is a finite measure on $(E, \mathscr E)$, then
-If $m$ is a finite measure on $(E, \mathscr E)$, then
-  \begin{align}
-    \int_E f_0(t,x)m(dx)
+  % If $m$ is a finite measure on $(E, \mathscr E)$, then
+  If $\rho$ is a finite non-degenerate measure on $(E, \mathscr E)$, then
+  % Sun: I changed several m into \rho without further mentioning
+  \begin{align}
+    \int_E f_0(t,x)\rho(dx)
     \stackrel[t\to t_0]{}{\sim}
-    \int_E f_1(t,x)m(dx).
+    \int_E f_1(t,x)\rho(dx).
   \end{align}
@@
 \begin{align}
-	&\Big| \frac{	\int_E f_0(t,x)m(dx) }{ 	\int_E f_1(t,x)m(dx)  } - 1 \Big|
-   = \Big| \int_E \frac{f_0(t,x)}{f_1(t,x)} \frac{f_1(t,x)m(dx)}{	\int_E f_1(t,y)m(dy)  } - 1\Big|
-	\\&\quad \leq \int_E \Big|  \frac{f_0(t,x)}{f_1(t,x)} - 1 \Big| \frac{f_1(t,x)m(dx)}{	\int_E f_1(t,y)m(dy)  }
-	\leq \sup_{x\in E} \Big|  \frac{f_0(t,x)}{f_1(t,x)} - 1 \Big|
+	&\Big| \frac{	\int_E f_0(t,x) \rho(dx) }{ 	\int_E f_1(t,x) \rho(dx)  } - 1 \Big|
+   = \Big| \int_E \frac{f_0(t,x)}{f_1(t,x)} \frac{f_1(t,x) \rho(dx)}{	\int_E f_1(t,y) \rho(dy)  } - 1\Big|
+	\\&\quad \leq \int_E \Big|  \frac{f_0(t,x)}{f_1(t,x)} - 1 \Big| \frac{f_1(t,x) \rho(dx)}{	\int_E f_1(t,y) \rho(dy)  }
+	\leq \sup_{x\in E} \Big|  \frac {f_0(t,x)} {f_1(t,x)} - 1 \Big|
 	\xrightarrow[t\to t_0]{} 0,
@@
   % Let $(E, \mathscr E)$ be a measurable space and $m$ a  non-degenerate measure on $(E, \mathscr E)$.
-  Let $(E, \mathscr E)$ be a measurable space and $m$ be a  non-degenerate measure on $(E, \mathscr E)$.
+  Let $(E, \mathscr E)$ be a measurable space and $\rho$ a finite non-degenerate measure on $(E, \mathscr E)$.
   % Let $f$ be a bounded measurable function on $E$ with 
-  Let $\gamma$ be a bounded measurable function on $E$ with 
-  \begin{align}
-    \gamma_0
-    := \operatorname*{ess\,inf}_{m(dx)} \gamma(x)
-    := \sup\{r:m(x:\gamma(x) < r) = 0\}.
-  \end{align}
-	Then $\big(\int_E t^{\gamma(x)} m(dx)\big)_{t\in (0,\infty)} \in \mathcal R^0_{\gamma_0}$.
-	Further, if $m\{x:\gamma(x) = \gamma_0\}>0$, then
-\begin{align}
-	\int_E t^{\gamma(x)} m(dx)
-	\stackrel[t\to 0]{}{\sim}  m\{x:\gamma(x) = \gamma_0\} t^{\gamma_0}.
+  Let $\alpha$ be a bounded measurable function on $E$ with 
+% Sun: I changed several gamma into alpha without further mentioning. 
+% Sun: I also changed m into \rho in this lemma.
+  \begin{align}
+    \alpha_0
+    := \operatorname*{ess\,inf}_{\rho(dx)} \alpha(x)
+    % := \sup\{r:\rho(x:\alpha(x) < r) = 0\}.
+    := \sup\{r:\rho(x:\alpha(x) < r) = 0\} \in \mathbb R.
+  \end{align}
+	Then $\big(\int_E t^{\alpha(x)} \rho(dx)\big)_{t\in (0,\infty)} \in \mathcal R^0_{\alpha_0}$.
+	Further, if $\rho \{x:\alpha(x) = \alpha_0\}>0$, then
+\begin{align}
+	\int_E t^{\alpha(x)} \rho(dx)
+	\stackrel[t\to 0]{}{\sim}  \rho\{x:\alpha(x) = \alpha_0\} t^{\alpha_0}.
 \end{align}
@@
 \begin{proof}
-	If $\lambda \in (0,1]$, then we have
-  \begin{align}
-    \frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-    \leq \frac{\int_E \lambda^{\gamma_0} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-    = \lambda^{\gamma_0},
+	% If $\lambda \in (0,1]$, then we have
+  % SUN: I changed several \lambda to u without further mentioning.
+	If $u \in (0,1]$, then we have
+  \begin{align}
+    \frac{\int_E u^{\alpha(x)} t^{\alpha(x)} \rho(dx)}{\int_E t^{\alpha(x)} \rho(dx)}
+    \leq \frac{\int_E u^{\alpha_0} t^{\alpha(x)} \rho(dx)}{\int_E t^{\alpha(x)} \rho(dx)}
+    = u^{\alpha_0},
     \quad t\in (0,\infty).
@@
   \begin{align}
-    \limsup_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}	
-    \leq \lambda ^{\gamma_0}.
+    \limsup_{(0,\infty) \ni t\to 0}\frac{\int_E u^{\alpha(x)} t^{\alpha(x)} \rho(dx)}{\int_E t^{\alpha(x)} \rho(dx)}	
+    \leq u^{\alpha_0}.
   \end{align}
@@
   \begin{align}
-    &\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-      \geq \frac{ \int_{ \gamma(x) \leq  \gamma_0 + \epsilon } \lambda^{ \gamma(x) } t^{ \gamma(x)} m(dx) } { \int_E t^{ \gamma(x) } m(dx) }
-    \\&\quad \geq \lambda^{ \gamma_0 + \epsilon} \frac{ \int_{ \gamma(x) \leq \gamma_0 + \epsilon } t^{ \gamma(x)} m(dx) } { \int_{ \gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)}m(dx)+ \int_{\gamma(x) > \gamma_0 + \epsilon} t^{\gamma(x)}m(dx)}
-    \\&\quad = \lambda^{\gamma_0 + \epsilon} \frac{1}{1+ \frac{\int_{\gamma(x) > \gamma_0 + \epsilon}t^{\gamma(x) - (\gamma_0 + \epsilon)}m(dx)}{\int_{\gamma(x) \leq \gamma_0 + \epsilon}t^{\gamma(x)- (\gamma_0 + \epsilon)}m(dx)}},
+    &\frac{\int_E u^{\alpha(x)} t^{\alpha(x)} \rho(dx)}{\int_E t^{\alpha(x)} \rho(dx)}
+      \geq \frac{ \int_{ \alpha(x) \leq  \alpha_0 + \epsilon } u^{ \alpha(x) } t^{ \alpha(x)} \rho(dx) } { \int_E t^{ \alpha(x) } \rho(dx) }
+    \\&\quad \geq u^{ \alpha_0 + \epsilon} \frac{ \int_{ \alpha(x) \leq \alpha_0 + \epsilon } t^{ \alpha(x)} \rho(dx) } { \int_{ \alpha(x) \leq \alpha_0 + \epsilon}t^{\alpha(x)} \rho(dx)+ \int_{\alpha(x) > \alpha_0 + \epsilon} t^{\alpha(x)} \rho(dx)}
+    \\&\quad = u^{\alpha_0 + \epsilon} \frac{1}{1+ \frac{\int_{\alpha(x) > \alpha_0 + \epsilon}t^{\alpha(x) - (\alpha_0 + \epsilon)} \rho(dx)}{\int_{\alpha(x) \leq \alpha_0 + \epsilon}t^{\alpha(x)- (\alpha_0 + \epsilon)} \rho(dx)}},
     \quad t\in (0, \infty),
     \\&\quad \xrightarrow[(0,\infty) \ni t\to 0]{}
-    \lambda ^{\gamma_0 + \epsilon},
+    u^{\alpha_0 + \epsilon},
   \end{align}
@@
   \begin{align}
-    \liminf_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-    \geq \lambda ^{\gamma_0}.
+    \liminf_{(0,\infty) \ni t\to 0}\frac{\int_E u^{\alpha(x)} t^{\alpha(x)} \rho(dx)}{\int_E t^{\alpha(x)} \rho(dx)}
+    \geq u^{\alpha_0}.
   \end{align}
@@
   \begin{align}
-    \lim_{(0,\infty) \ni t\to 0}\frac{\int_E \lambda^{\gamma(x)} t^{\gamma(x)} m(dx)}{\int_E t^{\gamma(x)} m(dx)}
-    = \lambda ^{\gamma_0},	
-    \quad \lambda \in (0,1].
-  \end{align}
-	If $\lambda \in (1,\infty)$, taking $f(x, t):= t^{\gamma(x)}$, from what we have proved, we also have that
-  \begin{align}
-    \lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,\lambda t)m(dx)}{\int_E f(x, t)m(dx)}
-    = \lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,t)m(dx)}{\int_E f(x, \lambda^{-1} t)m(dx)}
-    = \big((\lambda^{-1})^{\gamma_0} \big)^{-1}
-    = \lambda ^{\gamma_0}.
+    \lim_{(0,\infty) \ni t\to 0}\frac{\int_E u^{\alpha(x)} t^{\alpha(x)} \rho(dx)}{\int_E t^{\alpha(x)} \rho(dx)}
+    = u^{\alpha_0},	
+    \quad u \in (0,1].
+  \end{align}
+	If $u \in (1,\infty)$, taking $f(x, t):= t^{\alpha(x)}$, from what we have proved, we also have that
+  \begin{align}
+    \lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,u t) \rho(dx)}{\int_E f(x, t) \rho(dx)}
+    = \lim_{(0,\infty)\ni t\to 0}\frac{\int_E f(x,t) \rho(dx)}{\int_E f(x, u^{-1} t) \rho(dx)}
+    = \big(( u^{-1})^{\alpha_0} \big)^{-1}
+    = u^{\alpha_0}.
   \end{align}
@@
 
-	If further
-	we have $m(x:\gamma(x) = \gamma_0)>0$, then by the monotone convergence theorem  it is easy to see that
+	If further we have $\rho(x:\alpha(x) = \alpha_0)>0$, then by the monotone convergence theorem  it is easy to see that
   \begin{equation}
-    \frac{\int_E t^{\gamma(x)} m(dx)}{t^{\gamma_0}}
-    \xrightarrow[(0,\infty)\ni t\to 0]{} m(x:\gamma(x) = \gamma_0)\in (0,\infty).
+    \frac{\int_E t^{\alpha(x)} \rho(dx)}{t^{\alpha_0}}
+    \xrightarrow[(0,\infty)\ni t\to 0]{} \rho(x:\alpha(x) = \alpha_0)\in (0,\infty).
     \qedhere
@@
 	\psi_0(x,z)
-	:= \alpha(x) z^2 + \int_{(0,\infty)} (e^{-z y} - 1 + z y) \pi(x,dy),
+	% := \alpha(x) z^2 + \int_{(0,\infty)} (e^{-z y} - 1 + z y) \pi(x,dy),
+	:= \psi(x,z) + \beta(x)z,
 	\quad x \in E,z \geq 0.
@@
 \item
-	$\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
+	% $\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
+	for each $x\in E$, $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
 \item
-	$\mathbb N_x(\|W_0 \|\neq 0) = 0$;
+	% $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
+	for each $x\in E$, $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
 \item
-	For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure on $\mathbb W$ with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+	% For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure on $\mathbb W$ with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
+	for any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure on $\mathbb W$ with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)],t>0$.
 \end{itemize}
@@
 \end{align}
-It is know that for any $f\in\mathscr B_b^+(E)$,
+% It is know that for any $f\in\mathscr B_b^+(E)$,
+It is also known that for any $f\in\mathscr B_b^+(E)$,
 \begin{align}\label{eq: mean of kuz measure}
@@
   =\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
-	\quad t \geq 0,
-\end{align}
-see \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
+%	\quad t \geq 0,
+% \end{align}
+% see \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
+  \quad t \geq 0.
+  \end{align}
 
@@
 \end{thm}
-The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$, the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of the spine process in a Poissonian way.
+The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$,
+% the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of the spine process in a Poissonian way.
+the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
 
 More precisely,
-we say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if,
+we say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if:
 \begin{itemize}
@@
 They will be needed in the proof of  Theorem \ref{thm: main theorem}(3).
-\begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
+% \begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
+\begin{lem}[{\cite[Lemma 5.1]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
 If $F\in \mathscr B_b(E\times [0,1]\times [0,\infty)$ is
@@
   \end{align}
-  One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example,
+  % One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example,
+  One of the consequences of this equation is that, see \cite[Lemma 5.2]{RenSongSun2017Spine} for example,
   \begin{align}
@@
 	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
-We will prove that for an appropriate map $t_0$ with
-$$
-	t_0(t)
-	\xrightarrow[t\to\infty]{} \infty;
-	\quad t_0(t)\| \phi^{-1}v_{t-t_0(t)}\|^{\gamma_0 - 1}_\infty
-	\xrightarrow[t\to\infty]{} 0,
-$$	
-we have
-$$
-\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
-	\xrightarrow[t\to\infty]{} 0
-$$
-and
-$$
-\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
+  % CHANGE
+  % We will prove that for an appropriate map $t_0$ with
+  % $$
+  %	t_0(t)
+  %	\xrightarrow[t\to\infty]{} \infty;
+  %	\quad t_0(t)\| \phi^{-1}v_{t-t_0(t)}\|^{\gamma_0 - 1}_\infty
+  %	\xrightarrow[t\to\infty]{} 0,
+  % $$	
+  % we have
+  % $$
+  % \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
+	% \xrightarrow[t\to\infty]{} 0
+  % $$
+  % and
+  % $$
+  % \Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
+  % \xrightarrow[t\to\infty]{} 0.
+  % $$
+  % Then the desired assertion follows easily from these and properties of uniform convergence.
+  We only need to prove that there exists a map $t\mapsto a_t > 0$ such that
+  \begin{align}
+    \label{eq:k1}
+    \sup_{x\in E} \Big| \frac{ ( \phi^{-1} v_t )(x)}{ a_t} - 1 \Big|
+    \xrightarrow[t\to \infty]{} 0.
+  \end{align}
+  In fact, once this is proved, we will have that
+  \begin{align}
+    \label{eq:k2}
+    \Big |\frac {\langle v_t, \phi^*\rangle_m} {a_t } - 1 \Big |
+    & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{ a_t } - 1 \Big| \phi \phi^*(x) m(dx)\\
+    & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{ a_t }-1 \Big|
         \xrightarrow[t\to\infty]{} 0.
-$$
-Then the desired assertion follows easily from these and properties of uniform convergence.
-
-%end new
+  \end{align}
+  Then, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we will get the desired result:
+  \begin{align}
+    \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
+    \xrightarrow[t\to\infty]{} 0.
+  \end{align}
+  % END CHANGE
+
   For each $\mu\in\mathcal M^\phi_E$, denote by $\{(Y_t), (\xi_t),\mathbf n; \dot {\mathbf P}^{(\phi)}_\mu\}$ the spine representation of $\mathbb N^{(\phi)}_\mu$.
@@
   Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
-Therefore, to complete the proof, we only need to show that
-\begin{align}
-  \label{eq:desired_for_main_theorem_2}
-	\dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
-	\stackrel[t\to \infty]{x\in E}{\sim}  \dot {\mathbf P}_\nu^{(\phi)} [Y_t(\phi)^{-1}].
-\end{align}
-
-In order to show this, we consider a decomposition of the immigration process $(Y_t)_{t\geq 0}$.
+  % DELETED
+  % Therefore, to complete the proof, we only need to show that
+  % \begin{align}
+  %  \label{eq:desired_for_main_theorem_2}
+  %  \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
+  %  \stackrel[t\to \infty]{x\in E}{\sim}  \dot {\mathbf P}_\nu^{(\phi)} [Y_t(\phi)^{-1}].
+  % \end{align}
+  % END DELETED
+
+  % In order to show this, we consider a decomposition of the immigration process $(Y_t)_{t\geq 0}$.
+  In order to construct an $(a_t)_{t\geq 0}$ satisfying \eqref{eq:k1}, we consider a decomposition of the immigration process $(Y_t)_{t\geq 0}$.
   For any $t>0$ and any $G\in \mathscr B((0,t])$, define
@@
 
-The main idea is to show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
+  % The main idea is to show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
+  We will show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
   This is done in the following two lemmas whose proofs are postponed after this proof.
@@
 
-Now, for each $t_0 > 1$ and $t-t_0$ large enough, according to
-\eqref{eq:vt-and-Y},  \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2},
-Lemmas \ref{lem:bound_for_epsilon1} and \ref{lem:upperbound_of_epsilon-2}, we have
-\begin{align} \label{vts-inequality}
+  Now, for each $t_0 > 1$ and $t-t_0$ large enough, according to \eqref{eq:vt-and-Y},  \eqref{eq: starting point of phi-1v_t(x)}, \eqref{eq: some equations for PY-1-2}, Lemmas \ref{lem:bound_for_epsilon1} and \ref{lem:upperbound_of_epsilon-2}, we have
+  \begin{align} 
+    \label{vts-inequality}
     &\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0},\phi^* \rangle_m}-1 \Big|
@@
   \end{align}
-Notice that
-\begin{align}\label{eq:k2}
-	\Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
-      & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big| \phi \phi^*(x) m(dx)\\
-    & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
-      \xrightarrow[t\to\infty]{} 0.
-\end{align}
-Therefore, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
-\begin{align}
-	\sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
-	\xrightarrow[t\to\infty]{} 0,
-\end{align}
-as desired.
+  % ADDED
+  Therefore, the desired assertion \eqref{eq:k1} is valid for $a_t := \langle v_{t-t_0(t)},\phi^* \rangle_m$.
+  % END ADDED
+  % DELETED
+  % Notice that
+  % \begin{align}\label{eq:k2}
+  %   \Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
+  %   & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big| \phi \phi^*(x) m(dx)\\
+  %   & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
+  %   \xrightarrow[t\to\infty]{} 0.
+  % \end{align}
+  % Therefore, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
+  % \begin{align}
+  %   \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
+  %   \xrightarrow[t\to\infty]{} 0,
+  % \end{align}
+  % as desired.
+  % END DELETED
 \end{proof}
@@
 \end{align}
-From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have almost surely
+% From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have almost surely
+From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have $\Pi^{(\phi)}_{\cdot}$-almost surely
 \begin{align}
@@
 	\\& \leq \max\{1,r\} \cdot \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \Big\|  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}\Big\|_\infty
-	\\& := c_2 \cdot \max  \{1,r\},
+	% \\& := c_2 \cdot \max  \{1,r\},
+	\\& =: c_2 \cdot \max  \{1,r\},
 	\quad t\geq 1, r\geq 0.
 \end{align}
-From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have almost surely
+% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have almost surely
+From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have $\Pi_{\cdot}^{(\phi)}$-almost surely
 \begin{align}
@@
 \end{align}
-From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have almost surely
+% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have almost surely
+From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have $\Pi^{(\phi)}_\cdot$-almost surely
 \begin{align}\label{eq: upper bound for J'_G}
@@
 
-\begin{exa} {\rm
+% ADDED
+\begin{exa}
+  Suppose that $E$ is a finite state space and $m$ is the counting measure on $E$. 
+  Let $\xi$ be an irreducible, continuous-time Markov chain. 
+  Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies Assumptions \ref{asp: 1} and \ref{asp: 3}.
+\end{exa}
+% END ADDED
+
+\begin{exa} 
 Suppose that $E$ is a bounded Lipschitz connected  open set of $\mathbb R^d$ and that $m$ denotes the Lebesgue measure on $E$.
-Let $\xi$ be the subprocess in $E$ of a diffusion
-process in $\mathbb{R}^d$ corresponding to a uniformly elliptic divergence form second order
-differential operator.  Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
+Let $\xi$ be the subprocess in $E$ of a diffusion process in $\mathbb{R}^d$ corresponding to a uniformly elliptic divergence form second order differential operator.  
+Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies Assumptions \ref{asp: 1} and \ref{asp: 3}.
+\end{exa}
+
+\begin{exa}
+Suppose that $E$ is the closure of a bounded $C^2$ connected  open set of $\mathbb R^d$ and that $m$ denotes the Lebesgue measure on $E$.
+Let $\xi$ be the reflecting Brownian motion in $E$. 
+Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
 Assumptions \ref{asp: 1} and \ref{asp: 3}. 
-}
 \end{exa}
 
-\begin{exa} {\rm
-Suppose that $E$ is the closure of a bounded $C^2$ connected  open set of $\mathbb R^d$ and that $m$ denotes the Lebesgue measure on $E$.
-Let $\xi$ be the reflecting Brownian motion
-in $E$. Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
-Assumptions \ref{asp: 1} and \ref{asp: 3}. 
-}
+\begin{exa}
+  Suppose that $E$ is a bounded   open set of $\mathbb R^d$ and  $m$ denotes the Lebesgue measure on $E$.
+  $\xi$ be the subprocesses in $E$ of any of the subordinate Brownian motions studied in \cite{KSV1, KSV2}.  
+  Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies Assumptions \ref{asp: 1} and \ref{asp: 3}. 
 \end{exa}
 
-\begin{exa} {\rm
-Suppose that $E$ is a bounded   open set of $\mathbb R^d$ and  $m$ denotes the Lebesgue measure on $E$.
-$\xi$ be the subprocesses in $E$ of any of
-the subordinate Brownian motions studied in \cite{KSV1, KSV2}.  Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
-Assumptions \ref{asp: 1} and \ref{asp: 3}. 
-}
-\end{exa}
-
-\begin{exa} {\rm
+\begin{exa}
   Suppose $a>2$ is a constant.
   Assume that $E=\mathbb{R}^d$ and $m$ is the Lebesgue measure on $\mathbb{R}^d$.
-Let $\xi$ be a Markov process on $\mathbb{R}^d$ corresponding to the infinitesimal
-generator $\Delta-|x|^a$. Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
-Assumption \ref{asp: 1} and \ref{asp: 3}. 
-}
+  Let $\xi$ be a Markov process on $\mathbb{R}^d$ corresponding to the infinitesimal generator $\Delta-|x|^a$. 
+  Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies Assumption \ref{asp: 1} and \ref{asp: 3}. 
 \end{exa}
 
-\begin{exa} {\rm
+\begin{exa} 
   Assume that $E=\mathbb{R}^d$ and $m$ is the Lebesgue measure on $\mathbb{R}^d$.
-Suppose that $V$ is a nonnegative and locally bounded function on  $\mathbb{R}^d$
-such that there exist $R>0$ and $M\ge 1$ such that for all $|x|>R$,
-$$
+  Suppose that $V$ is a nonnegative and locally bounded function on  $\mathbb{R}^d$ such that there exist $R>0$ and $M\ge 1$ such that for all $|x|>R$,
+  \begin{align}
     M^{-1}(1+V(x))\le V(y)\le M(1+V(x)), \qquad y\in B(x, 1),
-$$
+  \end{align}
   and that
-$$
+  \begin{align}
     \lim_{|x|\to\infty}\frac{V(x)}{\log|x|}=\infty.
-$$
+  \end{align}
   Suppose $\beta\in (0, 2)$ is a constant.
-Let $\xi$ be a Markov process on $\mathbb{R}^d$ corresponding to the infinitesimal
-generator $-(-\Delta)^{\beta/2}-V(x)$. 
+  Let $\xi$ be a Markov process on $\mathbb{R}^d$ corresponding to the infinitesimal generator $-(-\Delta)^{\beta/2}-V(x)$. 
   Then the semigroup $(P_t)_{t\ge 0}$ of $\xi$ satisfies
   Assumptions \ref{asp: 1} and \ref{asp: 3}. 
-}
 \end{exa}
 
-\begin{exa} {\rm
-Suppose that $\beta\in (0, 2)$ and that $\xi^{(1)}=\{\xi^{(1)}_t: t\ge0\}$ is a strictly
-$\beta$-stable process in $\mathbb{R}^d$. Suppose that, in the case $d\ge 2$, the spherical
-part $\eta$ of the L\'evy measure $\mu$ of $\xi^{(1)}$ satisfies the following assumption: there
-exist a positive function $\Phi$ on the unit sphere $S$ in $\mathbb{R}^d$ and $\kappa>1$
+\begin{exa}
+  Suppose that $\beta\in (0, 2)$ and that $\xi^{(1)}=\{\xi^{(1)}_t: t\ge0\}$ is a strictly $\beta$-stable process in $\mathbb{R}^d$. 
+  Suppose that, in the case $d\ge 2$, the spherical part $\eta$ of the L\'evy measure $\mu$ of $\xi^{(1)}$ satisfies the following assumption: 
+  there exist a positive function $\Phi$ on the unit sphere $S$ in $\mathbb{R}^d$ and $\kappa>1$
 such that
-$$
-\Phi=\frac{d\eta}{d\sigma} \quad \mbox{and} \quad
-\kappa^{-1}\le \Phi(z)\le \kappa \quad \mbox{on } S
-$$
+\begin{align}
+  \Phi=\frac{d\eta}{d\sigma} \quad \text{and} \quad
+  \kappa^{-1}\le \Phi(z)\le \kappa \quad \text{on } S
+\end{align}
 where $\sigma$ is the surface measure on $S$. In the case $d=1$, we assume that the L\'evy
@@
 Assumptions \ref{asp: 1} and \ref{asp: 3}.
-}
 \end{exa}
@@
     &F(\theta)
-      \leq C \int_0^\theta \left\|  F\left(ru^{ \frac{1}{\alpha - 1}  }\right)\right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
-      \leq C \int_0^\theta \left\|  \frac{1}{k!}\left(Cru^{ \frac{1}{\alpha - 1}  } \right)^k \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
-    \\ &\leq \frac{C^{k+1}}{k!} \left(\int_0^\theta r^k dr\right) \cdot \left\|u^{\frac{k}{\alpha - 1}} \right\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
+      \leq C \int_0^\theta \big\|  F(ru^{ \frac{1}{\alpha - 1}  })\big\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+      \leq C \int_0^\theta \Big\|  \frac{1}{k!}(Cru^{ \frac{1}{\alpha - 1}  })^k \Big\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
+    \\ &\leq \frac{C^{k+1}}{k!} \Big(\int_0^\theta r^k dr\Big) \cdot \|u^{\frac{k}{\alpha - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
   \end{align}

### 2019-07-20 stableLimit.tex
change stableLimit.tex

@@
 	University of Illinois at Urbana-Champaign\\
-	% Urbana, IL 61801}
 	Urbana, IL, USA, 61801}
@@
 Wuhan University\\
-% Wuhan, Hubei 430072, P. R. China}
 Wuhan, Hubei, P. R. China, 430072}
@@
 The main result of  \cite{Slack1968A-branching} can be stated as follows. 
-% Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$ with infinite variance.
 Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$.
@@
 	\psi(x,z):=
-	% - \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
 	- \beta(x) z + \sigma (x)^2 z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
@@
 \end{align}
-% where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
-where $\beta, \sigma\in \mathscr B_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+%where $\beta, \sigma\in \mathscr B_b(E)$ 
+where $\beta\in \mathscr B_b(E)$, $\sigma\in \mathscr B_b^+(E)$ 
+and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
 For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
@@
 where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0-1$).
-Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ does not depend on the initial configuration $\mu$.
+Notice that the distribution of the weak limit 
+$\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ does not depend 
+%on the initial configuration $\mu$.
+on the initial distribution $\mu$.
 Precise statements of the assumptions and the results are presented in the next subsection.
@@
 \end{align}
-% Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
 Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators on $L^2(E,m)$.
@@
 \end{align}
-% It is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
 It is proved in \cite{RenSongZhang2015Limit, RenSongZhang2017Central} that $(P^\beta_t)_{t \geq 0}$ and $(P^{\beta *}_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators on $L^2(E,m)$.
@@
 \end{align}
-Assumption \ref{asp: 3} is a pretty strong assumption on the semigroup $\{P_t : t \ge 0\}$. However, this assumption is satisfied in a lot of cases.  
-In \cite{RenSongZhang2015Limit},  a list of examples of processes satisfying Assumption \ref{asp: 1} and \ref{asp: 3} were given. 
+Assumption \ref{asp: 3} is a pretty strong assumption on the semigroup $\{P_t : t \ge 0\}$.
+%new
+For example, it rules out the semigroup of Brownian motion on $\mathbb R^d$ and the semgroup of
+Ornstein-Uhlenbeck process on $\mathbb R^d$.
+%end new
+ However, this assumption is satisfied in a lot of cases.  
+In \cite{RenSongZhang2015Limit},  a list of examples of processes satisfying 
+ Assumptions \ref{asp: 1} and \ref{asp: 3} were given. 
 For the convenience of our readers, we will
@@
 
-% Our assumption is on the branching mechanism:
 Recall that the branching mechanism is given by \eqref{eq: branching mechanism}. 
@@
 
-We now present the main results of this paper:
+%We now present the main results of this paper:
+We now present the main result of this paper:
 \begin{thm}
@@
 To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 	$X$.
-  % Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a martingale change of measure, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and an measure-valued immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
   Roughly speaking, the spine is the trajectory of an immortal moving particle and the spine decomposition theorem says that, after a martingale change of measure, the transformed superprocess can be decomposed in law as the sum of a copy of the original superprocess and a measure-valued immigration process along this spine, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog}.
@@
 The rest of this paper is organized as follows:
-In Subsections \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly varying functions and superprocesses, respectively.
+In Subsections \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, 
+%regularly varying functions and superprocesses, respectively.
+regularly variation and superprocesses, respectively.
 In Subsection \ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem.
@@
 In Subsection \ref{sec: proof of result 3}, we give the proof of Theorem \ref{thm: main theorem}(3).
-% In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterizes the distribution with Laplace transform \eqref{e:zloltarev}, which is used in the proof of Theorem \ref{thm: main theorem}(3) given Subsection \ref{sec: proof of result 3}.
 In Appendix \ref{sec: Characterizing the Zolotarev's distribution using an non-linear delay equation}, we give the equation that characterizes the distribution with Laplace transform \eqref{e:zloltarev}, which is used in the proof of Theorem \ref{thm: main theorem}(3).
@@
 Let $t_0 \in [-\infty,\infty]$.
-In this Subsection, $(E, \mathscr E)$ is assume to be a  measurable space.
+%In this Subsection, $(E, \mathscr E)$ is assume to be a  measurable space.
+In this subsection, $(E, \mathscr E)$ is assumed to be a  measurable space.
 For any $f_0, f_1\in \mathscr B^{++}({\mathbb R})$, we say $f_0$ and $f_1$ are \emph{asymptotically equivalent at $t_0$}, if $\big|\frac{f_0(t)}{f_1(t)} - 1\big| \xrightarrow[t\to t_0]{} 0$;
@@
 	Suppose that $f_0,f_1$ are bounded strictly positive measurable functions on $\mathbb R \times E$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
-  % If $f$ is a finite measure on $(E, \mathscr E)$, then
-  % If $m$ is a finite measure on $(E, \mathscr E)$, then
   If $\rho$ is a finite non-degenerate measure on $(E, \mathscr E)$, then
-  % Sun: I changed several m into \rho without further mentioning
   \begin{align}
@@
 \begin{lem}\label{lem:regularly_variation_and_integration}
-  % Let $(E, \mathscr E)$ be a measurable space and $m$ a  non-degenerate measure on $(E, \mathscr E)$.
+
   Let $(E, \mathscr E)$ be a measurable space and $\rho$ a finite non-degenerate measure on $(E, \mathscr E)$.
-  % Let $f$ be a bounded measurable function on $E$ with 
   Let $\alpha$ be a bounded measurable function on $E$ with 
-% Sun: I changed several gamma into alpha without further mentioning. 
-% Sun: I also changed m into \rho in this lemma.
   \begin{align}
@@
     := \operatorname*{ess\,inf}_{\rho(dx)} \alpha(x)
-    % := \sup\{r:\rho(x:\alpha(x) < r) = 0\}.
     := \sup\{r:\rho(x:\alpha(x) < r) = 0\} \in \mathbb R.
@@
 \begin{proof}
-	% If $\lambda \in (0,1]$, then we have
-  % SUN: I changed several \lambda to u without further mentioning.
 	If $u \in (0,1]$, then we have
@@
 	\psi_0(x,z)
-	% := \alpha(x) z^2 + \int_{(0,\infty)} (e^{-z y} - 1 + z y) \pi(x,dy),
 	:= \psi(x,z) + \beta(x)z,
@@
 \item
-	% $\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
 	for each $x\in E$, $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
 \item
-	% $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
 	for each $x\in E$, $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
 \item
-	% For any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure on $\mathbb W$ with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
 	for any $\mu \in \mathcal M_E^1$, if $\mathcal N$ is a Poisson random measure on $\mathbb W$ with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$, then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)],t>0$.
@@
 \end{align}
-% It is know that for any $f\in\mathscr B_b^+(E)$,
 It is also known that for any $f\in\mathscr B_b^+(E)$,
@@
   =\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
-%	\quad t \geq 0,
-% \end{align}
-% see \cite[Lemma 3.3]{RenSongSun2017Spine} for example.
   \quad t \geq 0.
@@
 The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$,
-% the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of the spine process in a Poissonian way.
-the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
+%the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
+the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as a measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
 
@@
 \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog} for example, 
-% considered the case when $g = \phi$ only.
 considered the case $g = \phi$ only.
@@
 They will be needed in the proof of  Theorem \ref{thm: main theorem}(3).
-% \begin{lem}[{\cite[Lemma 5.6]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
 \begin{lem}[{\cite[Lemma 5.1]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
@@
 	For each $(y,u,t)\in E\times [0,1]\times [0,\infty)$, define $\bar F(y,u,t) := \sup_{s:s\geq t} F(y,u,s)$.
-% Then $F\in \mathscr B_b(E\times [0,1]\times [0,\infty))$ and
 Then $\bar F\in \mathscr B_b(E\times [0,1]\times [0,\infty))$ and
@@
   \end{align}
-  % One of the consequences of this equation is that, see \cite[Lemma 5.1]{RenSongSun2017Spine} for example,
   One of the consequences of this equation is that, see \cite[Lemma 5.2]{RenSongSun2017Spine} for example,
@@
 	We use an argument similar to that used in \cite{RenSongSun2017Spine} for critical superprocesses with finite 2nd moment.
-  % CHANGE
-  % We will prove that for an appropriate map $t_0$ with
-  % $$
-  %	t_0(t)
-  %	\xrightarrow[t\to\infty]{} \infty;
-  %	\quad t_0(t)\| \phi^{-1}v_{t-t_0(t)}\|^{\gamma_0 - 1}_\infty
-  %	\xrightarrow[t\to\infty]{} 0,
-  % $$	
-  % we have
-  % $$
-  % \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
-	% \xrightarrow[t\to\infty]{} 0
-  % $$
-  % and
-  % $$
-  % \Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
-  % \xrightarrow[t\to\infty]{} 0.
-  % $$
-  % Then the desired assertion follows easily from these and properties of uniform convergence.
   We only need to prove that there exists a map $t\mapsto a_t > 0$ such that
@@
   \end{align}
-  % END CHANGE
 
@@
   Taking $\mu = \nu$ in \eqref{eq:vt-and-Y}, we get $\langle v_t, \phi^*\rangle_m = \dot {\mathbf P}_{\nu}^{(\phi)} [Y_t(\phi)^{-1}]$.
-  % DELETED
-  % Therefore, to complete the proof, we only need to show that
-  % \begin{align}
-  %  \label{eq:desired_for_main_theorem_2}
-  %  \dot{\mathbf P}_{\delta_x}^{(\phi)}[Y_t(\phi)^{-1}]
-  %  \stackrel[t\to \infty]{x\in E}{\sim}  \dot {\mathbf P}_\nu^{(\phi)} [Y_t(\phi)^{-1}].
-  % \end{align}
-  % END DELETED
-
-  % In order to show this, we consider a decomposition of the immigration process $(Y_t)_{t\geq 0}$.
+
   In order to construct an $(a_t)_{t\geq 0}$ satisfying \eqref{eq:k1}, we consider a decomposition of the immigration process $(Y_t)_{t\geq 0}$.
@@
 
-  % The main idea is to show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
   We will show that both $\epsilon_x^1(t_0,t)$ and $\epsilon_x^2(t_0,t)$ are very small compared to $\dot {\mathbf P}_\nu^{(\phi)}[Y_t^{(t_0,t]}(\phi)^{-1}]$ provided $t_0$ and $t- t_0$ are large enough.
@@
   \end{align}
-  Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
-  \begin{align}\label{eq:k1}
-    \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
-    \xrightarrow[t\to\infty]{} 0.
-  \end{align}
-  % ADDED
-  Therefore, the desired assertion \eqref{eq:k1} is valid for $a_t := \langle v_{t-t_0(t)},\phi^* \rangle_m$.
-  % END ADDED
-  % DELETED
-  % Notice that
-  % \begin{align}\label{eq:k2}
-  %   \Big |\frac {\langle v_t, \phi^*\rangle_m} {\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big |
-  %   & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)} , \phi^*\rangle_m} - 1 \Big| \phi \phi^*(x) m(dx)\\
-  %   & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
+ % Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
+%  \begin{align}\label{eq:k1}
+ %   \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
  %   \xrightarrow[t\to\infty]{} 0.
  % \end{align}
-  % Therefore, by \eqref{eq:k1}, \eqref{eq:k2} and the property of uniform convergence, we get
-  % \begin{align}
-  %   \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t},\phi^* \rangle_m}-1 \Big|
-  %   \xrightarrow[t\to\infty]{} 0,
-  % \end{align}
-  % as desired.
-  % END DELETED
+ Plugging this choice of $t_0(t)$ into \eqref{vts-inequality}, we get \eqref{eq:k1}.
+  Therefore, the desired assertion \eqref{eq:k1} is valid for $a_t := \langle v_{t-t_0(t)},\phi^* \rangle_m$.
 \end{proof}
@@
   [Proof of Lemma \ref{lem:upperbound_of_epsilon-2}]
-% Using the Markov property of the spine process and properties Poisson random measures, we have
 Using the Markov property of the spine process and properties of Poisson random measures, we have
@@
 \end{align}
-% From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have almost surely
 From \eqref{eq: definition of eta}, \eqref{eq: definition for J_g}, \eqref{eq: upper bound for g} and the fact that $\gamma(\cdot) - 1 < 1$, we have $\Pi^{(\phi)}_{\cdot}$-almost surely
@@
 	\\& \leq \max\{1,r\} \cdot \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \Big\|  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}\Big\|_\infty
-	% \\& := c_2 \cdot \max  \{1,r\},
 	\\& =: c_2 \cdot \max  \{1,r\},
@@
 \end{align}
-% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have almost surely
 From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_g} and \eqref{eq: upper bound for g}, we have $\Pi_{\cdot}^{(\phi)}$-almost surely
@@
 \end{align}
-% From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have almost surely
 From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have $\Pi^{(\phi)}_\cdot$-almost surely
@@
 \subsection{Examples}
-%new
 \label{sec:examples}
@@
 
-% ADDED
 \begin{exa}
@@
 \end{exa}
-% END ADDED
 
@@
 \end{exa}
-%end new
 
@@
 \bibitem{EnglanderKyprianou2004Local}
-	% Engländer, J. and Kyprianou, A.:
 	Engl\"{a}nder, J. and Kyprianou, A.:
@@
   Kim, P., Song, R. and Vondracek, Z.:
-  % Two-sided Green function estimates for killed subordinate Brownian motions.
   \emph{Two-sided Green function estimates for killed subordinate Brownian motions.}
-  % \emph{Proc. London Math. Soc.} \textbf{104} (2012), 927--958.
   Proc. London Math. Soc. \textbf{104} (2012), 927--958.
@@
   Kim, P., Song, R. and Vondracek, Z.:
-  % Potential theory of subordinate Brownian motions with Gaussian components.
+
   \emph{Potential theory of subordinate Brownian motions with Gaussian components.}
-  % \emph{Stoch. Proc. Appl.} \textbf{123} (2013), 764--795.
   Stoch. Proc. Appl. \textbf{123} (2013), 764--795.

### 2019-07-20 response.tex
change response.tex resubmitted190720

@@
 \item
-  p.4 l.4: It has to be They showd that.
+  p.4 l.4: It has to be They showed that.
 
-  {\it Changed as suggested.}
+  {\it Changed as suggested. See p.4 l.8.}
 \item
@@
 
-  {\it We added some explanations before (2.4).}
+  {\it We added some explanations before eq.(2.4).}
 \item
@@
   {\it We think the referee means $y^{1+\gamma(\xi_s)}$.
-    Changed as suggested. }
+    Changed as suggested. 
+    See p.22 l.3. }
 \item
@@
 
-  {\it Done as suggested.}
+  {\it Done as suggested. See eq.(3.11).}
 \item
@@
 
-  {\it We added them as suggested.}
+  {\it We added them as suggested. See p.19-21 Proof of Proposition 3.2.}
 \item
@@
 
-  {\it Added as suggested.}
+  {\it We only need (3.2). We added more details there. See p.22 l.12.}
 \item
@@
 
-  {\it Changed as suggested.}
+  {\it Changed as suggested. See p.25 l.1-2.}
 \item
@@
 
-  {\it We give a new proof of this Lemma which is shorter and better.}
+  {\it We give a new proof of this Lemma which is shorter and better. See p.33 Lemma A.8.}
 \item
@@
 
-  {\it Added as suggested.}
+  {\it Added as suggested. See p.28 Step.3.}
 \end{enumerate}
@@
 
-  {\it We added the definition, as suggested.}
+  {\it We added the definition there, as suggested. See p.2 in the middle.}
 \item
@@
 
-  {\it Changed, as suggested.}
+  {\it Changed, as suggested. See p.4 l.8.}
 \item
@@
 
-  {\it We explained it with more details.}
+  {\it We explained it with more details. See p.4. display.4.}
 \item
@@
 
-  {\it Done as suggested.}
+  {\it Done as suggested. See p.4-5 right after eq.(1.16) and eq.(1.17).}
 \item
@@
 
-  {\it We added a new sentence there which gives the function $\beta$.}
+  {\it We added a new sentence there which gives the function $\beta$. See p.5 l.-10.}
 \item
@@
 
-  {\it Should be $P_t^\beta \phi(x) = e^{\lambda t}\phi(x)$ and $P_t^{\beta*} \phi^*(x) = e^{\lambda t}\phi^*(x)$. Corrected as suggested.}
+  {\it Should be $P_t^\beta \phi(x) = e^{\lambda t}\phi(x)$ and $P_t^{\beta*} \phi^*(x) = e^{\lambda t}\phi^*(x)$. Corrected as suggested. See p.7 l.4.}
 \item
@@
 
-  {\it We added a paragraph after Assumption 2 to make this more clear.
+  {\it We added a paragraph after Assumption 1 to make this more clear.
     Note that in the new version the notation $\varphi$ and $\varphi^*$ is changed into $\widetilde \phi$ and $\widetilde \phi^*$, respectively.}
@@
 
-  {\it We restated this paragraph to make our intuitive explanations of the spine decomposition theorem more accurate. }
+  {\it We restated the first paragraph of Subsection 1.3 to make our intuitive explanations of the spine decomposition theorem more accurate. See p.8. }
 \item
@@
   {\it Should always use $\alpha$.
-     We changed several $\gamma$ into $\alpha$ there.}
+     We changed several $\gamma$ into $\alpha$ in Subsection 2.2.}
 \item
@@
 
-  {\it We explained this with more details.}
+  {\it We explained this with more details. See p.13 from eq.(2.3) to eq.(2.4). }
 \item
@@
 
-  {\it Changed as suggested.}
+  {\it Should be a Poisson random measure on $\mathbb W$. Changed as suggested. See p.13 l.-7.}
 \item
@@
 
-  {\it We gave an intuitive explanations in the paragraph before those bullet points. }
+  {\it We gave an intuitive explanations in the paragraph before those bullet points. Right after Theorem 2.7. See p.14. }
 \item
@@
 
-  {\it We added more details there as suggested.}
+  {\it We added more details there as suggested. See p.18 the line above eq.(3.2).}
 \item
@@
 
-  {\it Changed, as suggested.}
+  {\it Changed, as suggested. See p.18 l.-2.}
 \item
@@
 
-  {\it Done, as suggested.}
+  {\it Done, as suggested. See p.19 l.-2.}
 \item
@@
 
-  {\it Done, as suggested.}
+  {\it Done, as suggested. See p.21 the line above eq.(3.14).}
 \item
@@
 
-  {\it We rearranged the Proof of Thm 1.1 (2) so that it is easier for the readers to get the structure of the Proof. }
+  {\it We rearranged the Proof of Thm 1.1 (2) so that it is easier for the readers to get the structure of the Proof. See p.18-19. }
 \item
@@
 
-  {\it We explained this in more details.}
+  {\it We explained this in more details. See p.22 l.12.}
 \item
@@
 
-  {\it Done, as suggested.}
+  {\it Done, as suggested. See p.22 the line above eq.(3.15).}
 \item
@@
 
-  {\it We added it back, as suggested.}
+  {\it We added it back, as suggested. See p.22 eq.(3.15).}
 \item
@@
     We changed all $\gamma_0$ into $\alpha$ in this Lemma.
-    Similar changes are made in the next Lemma due to same reasons.}
+    Similar changes are made in the next Lemma due to same reasons.
+See p.33-34 Lemma A.8 and A.9.}
 \item
@@
     This does not compromise the later proofs.
-    We emphasized this in the new version to avoid any confusions.}
+    We emphasized this in the new version to avoid any confusions. See p.27 l.-10.}
 \item
@@
 
-  {\it The prove of this Lemma is simplified and the concerned argument is deleted.}
+  {\it The prove of this Lemma is simplified and the concerned argument is deleted. See p.33 proof of Lemma A.8.}
 \item
@@
 
-  {\it Those Lemmas are now moved into an appendix as suggested.}
+  {\it Those Lemmas are now moved into an appendix as suggested. See p.33-34 Lemma A.8 and A.9.}
 \item
@@
   {\it 
-    Done, as suggested.}
+    Done, as suggested. See p.34 l.-5.}
 \item
@@
   {\it Yes, we mean almost surely.
-  We added ``almost surely'' at several places as suggested.}
+  We added ``almost surely'' at several places as suggested.
+  See p.26 step.1.}
 \item
@@
 
-  {\it Done, as suggested.}
+  {\it Done, as suggested. 
+    See p.28 l.-13.}
 \item
@@
 
-  {\it Done, as suggested.}
+  {\it Done, as suggested.  See p.31 l.-7.}
 \item
@@
 
-  {\it Done, as suggested.}
+  {\it Done, as suggested. See p.32 Step.8.}
 \end{enumerate}

### 2019-07-20 stableLimit.tex
change stableLimit.tex
accepting changes
change stableLimit.tex


change stableLimit.tex

@@
 \setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
-% \usepackage[utf8]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{hyperref}
-% \def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
-% \def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
 \usepackage{mathrsfs}
@@
 It is well known that for a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$, we have
-\begin{align}\label{eq: Kolmogorov's result with finite variance}
+\begin{align}
+  \label{eq: Kolmogorov's result with finite variance}
 	n P(Z_n > 0)
@@
 and
-\begin{align}\label{eq: Yaglom's result with finite variance}
+\begin{align}
+\label{eq: Yaglom's result with finite variance}
 	\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
@@
 Assume that the  generating function $f(s)$ of the offspring distribution is of the form
-\begin{align}\label{eq: offspring generating function with alpha moment}
+\begin{align}
+  \label{eq: offspring generating function with alpha moment}
 	f(s)
@@
 Then
-\begin{align} \label{eq: extinction probability of critical GW process without 2rd moment}
+\begin{align} 
+  \label{eq: extinction probability of critical GW process without 2rd moment}
 	P(Z_n > 0)
@@
 where $L$ is a function slowly varying at $\infty$, and
-\begin{align} \label{eq: conditional distribution of critical GW process without 2rd moment}
+\begin{align} 
+  \label{eq: conditional distribution of critical GW process without 2rd moment}
 	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
@@
 where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
-\begin{align}\label{e:zloltarev}
+\begin{align}
+  \label{e:zloltarev}
 	E[e^{- u \mathbf z^{(\alpha)}}]
@@
 In \cite{Slack1972Further}, Slack also considered the converse of this problem:
-In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit,
-the generating function of the offspring distribution must be of the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
+In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the generating function of the offspring distribution must be of the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
 For shorter and more unified approaches to these results, we refer our readers to \cite{Borovkov1989Method, Pakes2010Critical}.
 
-Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment
-condition. Their main result can be stated as follows.
+Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment condition. 
+Their main result can be stated as follows.
 Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a $d$-type, nonsingular Galton-Watson process with its mean matrix $M:= (E[Z_1^{(j)}| Z_0^{(i)} = 1, Z_0^{(k)} = 0, \forall k \neq i])_{1\leq i,j\leq d}$ being positive regular, that is, all entries of $M$ are finite and there exists a number $n \geq 1$ such that all entries of $M^n$ are positive.
@@
 and for each $\mathbf j \in \mathbb N_0^d$,
-\begin{align}\label{eq: conditioned normalized multitype branching process}
+\begin{align}
+  \label{eq: conditioned normalized multitype branching process}
 	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
@@
 \end{align}
-%where $\beta, \sigma\in \mathscr B_b(E)$ 
-where $\beta\in \mathscr B_b(E)$, $\sigma\in \mathscr B_b^+(E)$ 
-and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
+where $\beta, \sigma \in \mathscr B_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
 For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
@@
 Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition
-\begin{align}\label{eq: second moment condition}
+\begin{align}
+  \label{eq: second moment condition}
 	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
@@
 They showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
-\begin{align} \label{eq: conditional limit of CSBP with stable branching}
+\begin{align} 
+  \label{eq: conditional limit of CSBP with stable branching}
 	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
@@
 Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
-\begin{align}\label{eq: regular varing of branching mechanism of a CSBP}
+\begin{align}
+  \label{eq: regular varing of branching mechanism of a CSBP}
 	\psi(z)
@@
 It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
-\begin{align}\label{eq: conditional limit of CSBP}
+\begin{align}
+  \label{eq: conditional limit of CSBP}
 	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
@@
 Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem:
-Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP
-with critical branching mechanism $\psi$ satisfying Grey's condition.
+Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP with critical branching mechanism $\psi$ satisfying Grey's condition.
 In order for the left side of \eqref{eq: conditional limit of CSBP} to have a non-trivial weak limit for some positive constants $(\lambda_t)_{t\geq 0}$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
@@
 and for a large class of non-negative testing functions $f$,
-\begin{align}\label{eq: result2}
+\begin{align}
+  \label{eq: result2}
 	\{ \eta_t X_t(f) ; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0) \}
@@
 where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0-1$).
-Notice that the distribution of the weak limit 
-$\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ does not depend 
-%on the initial configuration $\mu$.
-on the initial distribution $\mu$.
+Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ does not depend on $\mu$.
 Precise statements of the assumptions and the results are presented in the next subsection.
@@
 For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
-For any $f \in \mathscr B^+(E)$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$. In particular, $\mathcal M^1_E$ is the collection of all  finite Borel measures on $E$.
+For any $f \in \mathscr B^+(E)$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$. 
+In particular, $\mathcal M^1_E$ is the collection of all  finite Borel measures on $E$.
 
 We now give the definition of a $(\xi, \psi)$-superprocess:
-Let the spatial motion 
-$\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by \eqref{eq: branching mechanism}.
+Let the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by \eqref{eq: branching mechanism}.
 We say an $\mathcal M^1_E$-valued Hunt process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
@@
 where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
-\begin{align}\label{eq:FKPP_in_definition}
+\begin{align}
+  \label{eq:FKPP_in_definition}
 	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
@@
 This can be done under the following assumptions on the spatial motion $\xi$:
-\begin{asp} \label{asp: 1}
+\begin{asp} 
+  \label{asp: 1}
   There exist an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$ and a family of strictly positive,
@@
 Denote by $\sigma(\widetilde L)$ and $\sigma(\widetilde L^*)$ the spectra of $\widetilde L$ and $\widetilde L^*$, respectively.
-According to \cite[Theorem V.6.6]{Schaefer1974Banach},
-$\widetilde \lambda := \sup \text{Re}(\sigma(\widetilde L)) = \sup \text{Re}(\sigma(\widetilde L^*))$ is a common eigenvalue of multiplicity $1$ for both $\widetilde L$ and $\widetilde L^*$.
-By the argument in \cite{RenSongZhang2015Limit},
-the eigenfunctions $\widetilde \phi$ of $\widetilde L$ and $\widetilde \phi^*$ of $\widetilde L^*$ associated with the eigenvalue $\widetilde \lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
+According to \cite[Theorem V.6.6]{Schaefer1974Banach}, $\widetilde \lambda := \sup \text{Re}(\sigma(\widetilde L)) = \sup \text{Re}(\sigma(\widetilde L^*))$ is a common eigenvalue of multiplicity $1$ for both $\widetilde L$ and $\widetilde L^*$.
+By the argument in \cite{RenSongZhang2015Limit}, the eigenfunctions $\widetilde \phi$ of $\widetilde L$ and $\widetilde \phi^*$ of $\widetilde L^*$ associated with the eigenvalue $\widetilde \lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
 We further normalize $\widetilde \phi$ and $\widetilde \phi^*$ by $\big\langle \widetilde \phi, \widetilde \phi \big\rangle_m = \big\langle \widetilde \phi, \widetilde \phi^*\big\rangle_m = 1$ so that they are unique.
@@
 \end{align}
-$(p^\beta_t)_{t\geq 0}$ is called the
-\emph{density}  of the semigroup $(P^\beta_t)_{t\geq 0}$.
+$(p^\beta_t)_{t\geq 0}$ is called the \emph{density} of the semigroup $(P^\beta_t)_{t\geq 0}$.
 Define the dual semigroup $(P^{\beta *}_t)_{t \geq 0}$ by
@@
 Since we are only interested in the critical case, we assume the following:
-\begin{asp} \label{asp: 2}
+\begin{asp} 
+  \label{asp: 2}
   The superprocess $X$ is critical, i.e., $\lambda = 0$.
@@
 
-\begin{asp} \label{asp: 3}
+\begin{asp} 
+  \label{asp: 3}
 	$\widetilde \phi$ is bounded, and $(P_t)_{t\geq 0}$ is \emph{intrinsically ultracontractive}, that is, for each $t>0$, there is a constant $c_t >0$ such that for each $x,y\in E$, $p_t(x,y) \leq c_t \widetilde \phi(x) \widetilde \phi^*(y)$.
@@
 In fact, it is proved in \cite{KimSong2008Intrinsic} that for each $t>0$, $(p^\beta_t(x,y))_{x,y\in E}$ is comparable to $(\phi(x)\phi^*(y))_{x,y\in E}$ in the sense that there is a constant $c_t > 1$ such that
-\begin{align}\label{eq: p-t-beta is comparable to phi phi-star}
+\begin{align}
+  \label{eq: p-t-beta is comparable to phi phi-star}
 	c_t^{-1}
@@
 It is also shown in \cite{KimSong2008Intrinsic} that there are constants $c_0, c_1 > 0$ such that
-\begin{align}\label{eq:q(t,x,y)}
+\begin{align}
+  \label{eq:q(t,x,y)}
 	\sup_{x,y\in E} \Big|\frac{p^\beta_t(x,y)}{\phi(x)\phi^*(y)} - 1 \Big|
@@
 Assumption \ref{asp: 3} is a pretty strong assumption on the semigroup $\{P_t : t \ge 0\}$.
-%new
-For example, it rules out the semigroup of Brownian motion on $\mathbb R^d$ and the semgroup of
-Ornstein-Uhlenbeck process on $\mathbb R^d$.
-%end new
+For example, it rules out the semigroup of Brownian motion on $\mathbb R^d$ and the semgroup of Ornstein-Uhlenbeck process on $\mathbb R^d$.
 However, this assumption is satisfied in a lot of cases.  
@@
 Assumptions \ref{asp: 1} and \ref{asp: 3} were given. 
-For the convenience of our readers, we will
-briefly recall some of these examples in Subsection \ref{sec:examples}.
+For the convenience of our readers, we will briefly recall some of these examples in Subsection \ref{sec:examples}.
 
@@
 We assume the following:
-\begin{asp} \label{asp: 4}
+\begin{asp} 
+  \label{asp: 4}
 	The branching mechanism $\psi$ is of the form:
@@
 
-%We now present the main results of this paper:
 We now present the main result of this paper:
@@
   \end{itemize}
-  Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev}
-  (with $\alpha=\gamma_0 -1$).
+  Here, $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$, $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0 -1$).
 \end{thm}
@@
 \subsection{Methods and overview}
-
 To establish Theorem \ref{thm: main theorem}(2) and Theorem \ref{thm: main theorem}(3), we use a spine decomposition theorem for 	$X$.
@@
 The rest of this paper is organized as follows:
-In Subsections \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, 
-%regularly varying functions and superprocesses, respectively.
-regularly variation and superprocesses, respectively.
+In Subsections \ref{sec: Asymptotic equivalence}, \ref{sec: Regularly variation} and \ref{sec: Superprocesses}, we give some preliminary results about the asymptotic equivalence, regularly variation and superprocesses, respectively.
 In Subsection \ref{sec: Spine decompositions}, we present the generalized spine decomposition theorem.
@@
 
+% ** Preliminaries
 \section{Preliminaries}
 \label{sec: Preliminaries}
+% *** Asymptotic equivalence
 \subsection{Asymptotic equivalence} 
@@
 Let $t_0 \in [-\infty,\infty]$.
-%In this Subsection, $(E, \mathscr E)$ is assume to be a  measurable space.
 In this subsection, $(E, \mathscr E)$ is assumed to be a  measurable space.
@@
 
-\begin{lem} \label{lem: asymptotic equivalent of integration}
+\begin{lem} 
+  \label{lem: asymptotic equivalent of integration}
 	Suppose that $f_0,f_1$ are bounded strictly positive measurable functions on $\mathbb R \times E$ and $f_0(t,x)\stackrel[t\to t_0]{x\in E}{\sim}f_1(t,x)$.
@@
 
-\begin{lem}[{\cite[Theorem 1.5.12]{BinghamGoldieTeugels1989Regular}}] \label{lem: regularly variation and inverse}
+\begin{lem}[{\cite[Theorem 1.5.12]{BinghamGoldieTeugels1989Regular}}] 
+  \label{lem: regularly variation and inverse}
 	If $f \in \mathcal R_\alpha^\infty$ with $\alpha > 0$, there exists $g \in \mathcal R^\infty_{1/\alpha}$ with
@@
 \end{lem}
-\begin{cro} \label{cro: regularly varing and inverse with alpha < 0}
+\begin{cro} 
+  \label{cro: regularly varing and inverse with alpha < 0}
 	If $f \in \mathcal R_\alpha^0$ with $\alpha < 0$, there exists $g \in \mathcal R^\infty_{1/\alpha}$ with
-  \begin{align} \label{eq: asymptotic inverse with alpha < 0}
+  \begin{align} 
+    \label{eq: asymptotic inverse with alpha < 0}
     g(f(t))
@@
 	Noticing that $-\alpha > 0$, according to Lemma \ref{lem: regularly variation and inverse}, there exists $h \in \mathcal R_{-1/\alpha}^{\infty}$ such that
-  \begin{align} \label{eq: inverse between h and f}
+  \begin{align} 
+    \label{eq: inverse between h and f}
     h(\widetilde f(t))
@@
 
-\begin{lem}\label{lem:regularly_variation_and_integration}
-
+\begin{lem}
+  \label{lem:regularly_variation_and_integration}
   Let $(E, \mathscr E)$ be a measurable space and $\rho$ a finite non-degenerate measure on $(E, \mathscr E)$.
@@
 
-\subsection{Superprocesses} \label{sec: Superprocesses}
+% *** Superprocesses
+\subsection{Superprocesses} 
+\label{sec: Superprocesses}
 In this subsection, we recall some known results on the $(\xi, \psi)$-superprocess $\{X; \mathbf P\}$.
@@
 \end{align}
-Therefore, integrating both sides of \eqref{eq:mean-fkpp} with respect to the measure 
-$\phi^*dm$, we get that
+Therefore, integrating both sides of \eqref{eq:mean-fkpp} with respect to the measure $\phi^*dm$, we get that
 \begin{align}
@@
 This can be rearranged as
-\begin{align}\label{eq:langleVtfphiranglem_equation}
+\begin{align}
+  \label{eq:langleVtfphiranglem_equation}
   \langle V_tf,\phi^*\rangle_m + \int_s^t \langle \psi_0(\cdot ,V_r f) , \phi^*\rangle_mdr
@@
 From  Campbell's formula, see  the proof of \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
-\begin{align} \label{eq: equation for N measure}
+\begin{align} 
+  \label{eq: equation for N measure}
 	- \log \mathbf P_\mu [e^{-X_t(f)}]
@@
 For each $x\in E$ and $t\geq 0$, taking $\mu = \delta_x$ and $f = \lambda \mathbf 1_E$ with $\lambda > 0$ in the above equation, and letting $\lambda \to \infty$, we get
-\begin{align} \label{eq: definition of v_t(x)}
+\begin{align} 
+  \label{eq: definition of v_t(x)}
 	v_t(x)
@@
 It is also known that for any $f\in\mathscr B_b^+(E)$,
-\begin{align}\label{eq: mean of kuz measure}
+\begin{align}
+\label{eq: mean of kuz measure}
   \mathbb N_{\mu}[W_t(f)]
@@
 
+% *** Spine decompositions
 \subsection{Spine decompositions}
@@
 
-\begin{thm}[Size-biased decomposition,  \cite{RenSongSun2017Spine}]\label{thm: size-biased decomposition}
+\begin{thm}[Size-biased decomposition, \cite{RenSongSun2017Spine}]
+  \label{thm: size-biased decomposition}
   \begin{align}
@@
 \end{thm}
-The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$,
-%the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as an measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
-the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as a measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
-
-More precisely,
-we say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if:
+The second step of the spine decomposition theorem says that $\{(W_t)_{0\leq t\leq T}; \mathbb N^{W_T(g)}_\mu\}$ has a spine representation, which intuitively says that, under probability $\mathbb N_\mu^{W_T(g)}$, the measure-valued process $(W_t)_{0\leq t\leq T}$ can be decomposed as a measure-valued immigration process along the trajectory of a spine process in a Poissonian way.
+
+More precisely, we say $\{(\xi_t)_{0\leq t\leq T}, \mathbf n_T,  (Y_t)_{ 0\leq t\leq T}; \dot {\mathbf P}^{(g,T)}_\mu\}$ is a \emph{spine representation of $\mathbb N^{W_T(g)}_\mu$}  if:
 \begin{itemize}
@@
 which says that
-\begin{align}\label{eq: initial distribution of spine}
+\begin{align}
+  \label{eq: initial distribution of spine}
 	\Pi_{\mu}^{(T,g)} (\xi_0 \in dx)
@@
 Recall that $\phi$ is the principal eigenfunction of the mean semigroup of $X$.
-The classical spine decomposition theorem, see 
-\cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog} for example, 
-considered the case $g = \phi$ only.
+The classical spine decomposition theorem, see \cite{EckhoffKyprianouWinkel2015Spines, EnglanderKyprianou2004Local, LiuRenSong2009Llog} for example, considered the case $g = \phi$ only.
 In this case, the family of probabilities $(\Pi_{\mu}^{(\phi,T)})_{T\geq 0}$ is consistent in the sense of Kolmogorov's extension theorem, that is, the process $\{(\xi_t)_{0\leq t\leq T}; \Pi_{\mu}^{(\phi,T)} \}$ can be realized as the restriction of some process, say $\{(\xi_t)_{t\geq 0}; \Pi_{\mu}^{(\phi)}\}$,	on the finite time interval $[0,T]$.
@@
 	Conditioned on $\{(\xi_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$, \emph{the immigration measure} $\{\mathbf n; \dot{\mathbf P}^{(\phi)}_\mu[\cdot |(\xi_t)_{t\geq 0}]\}$ is a Poisson random measure on $[0,\infty ) \times \mathbb W$ with intensity
-  \begin{align}\label{eq:meanMeasImmigr}
+  \begin{align}
+    \label{eq:meanMeasImmigr}
     \mathbf m^\xi(ds,dw)
@@
 	$\{(Y_t)_{t\geq 0}; \dot{\mathbf P}^{(\phi)}_\mu\}$ is an $\mathcal M^1_E$-valued process defined by
-  \begin{align}\label{eq:defSpinImmigr}
+  \begin{align}
+    \label{eq:defSpinImmigr}
     Y_t
@@
 
-% ** Ergodicity of the spine process
+% *** Ergodicity of the spine process
 \subsection{Ergodicity of the spine process}
@@
 Let $c_0>0$ and $c_1>0$ be the constants  in \eqref{eq:q(t,x,y)}, then we have
-\begin{align}\label{eq: asymptotic for q_t(x,y)}
+\begin{align}
+  \label{eq: asymptotic for q_t(x,y)}
 	\sup_{x\in E} \Big| \frac{q_t(x,y)}{\phi(y)\phi^*(y)} - 1\Big|
@@
 They will be needed in the proof of  Theorem \ref{thm: main theorem}(3).
-\begin{lem}[{\cite[Lemma 5.1]{RenSongSun2017Spine}}] \label{lem: ergodicity of the underlying process}
-If $F\in \mathscr B_b(E\times [0,1]\times [0,\infty)$ is
-such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, then
+\begin{lem}[{\cite[Lemma 5.1]{RenSongSun2017Spine}}]
+  \label{lem: ergodicity of the underlying process}
+  If $F\in \mathscr B_b(E\times [0,1]\times [0,\infty)$ is such that $F(y,u):= \lim_{t\to \infty} F(y,u,t)$ exists for each $y\in E$ and $u \in [0,1]$, then
   \begin{align}
@@
 \end{lem}
-\begin{lem}\label{lem: Fatou-ergodic lemma for the uderlying process}
+\begin{lem}
+  \label{lem: Fatou-ergodic lemma for the uderlying process}
   Let $F\in \mathscr B^+_b(E\times [0,1]\times [0,\infty))$.
@@
 
+% ** Proofs
 \section{Proofs}
+% *** Proof of main theorem 1
 \subsection{Proof of Theorem \ref{thm: main theorem}(1)}
 \label{sec: proof of result 1}
-Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
-Assumptions \ref{asp: 1}--\ref{asp: 4}.
+Let $\{X; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying Assumptions \ref{asp: 1}--\ref{asp: 4}.
 In this subsection, we will prove the following result stronger than non-persistency:
 
-\begin{prop} \label{prop: non-presistent}
+\begin{prop} 
+  \label{prop: non-presistent}
 	For each $t > 0$, $\inf_{x\in E} \mathbf P_{\delta_x}(\|X_t\|= 0) > 0$.
@@
 
-% ** Proof of the main Theorem 2
+% *** Proof of the main Theorem 2
 \subsection{Proof of Theorem \ref{thm: main theorem}(2)}
@@
   \end{prop}
-  \label{prop: asymptotic equivalence of vtphi}
   The second proposition characterizes this speed:
@@
     \Big |\frac {\langle v_t, \phi^*\rangle_m} {a_t } - 1 \Big |
-    & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{ a_t } - 1 \Big| \phi \phi^*(x) m(dx)\\
-    & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{ a_t }-1 \Big|
+    & \leq \int \Big | \frac{(\phi^{-1}v_t)(x)}{ a_t } - 1 \Big| \phi \phi^*(x) m(dx)
+    \\ & \leq \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{ a_t }-1 \Big|
          \xrightarrow[t\to\infty]{} 0.
@@
   \end{align}
- % Plugging this choice of $t_0(t)$ back into \eqref{vts-inequality}, we have that
-%  \begin{align}\label{eq:k1}
- %   \sup_{x\in E}\Big|\frac{(\phi^{-1}v_t)(x)}{\langle v_{t-t_0(t)},\phi^* \rangle_m}-1 \Big|
- %   \xrightarrow[t\to\infty]{} 0.
- % \end{align}
- Plugging this choice of $t_0(t)$ into \eqref{vts-inequality}, we get \eqref{eq:k1}.
-  Therefore, the desired assertion \eqref{eq:k1} is valid for $a_t := \langle v_{t-t_0(t)},\phi^* \rangle_m$.
+  Plugging this choice of $t_0(t)$ into \eqref{vts-inequality} and taking $t\to \infty$, we get the desired assertion \eqref{eq:k1} with $a_t := \langle v_{t-t_0(t)},\phi^* \rangle_m$.
 \end{proof}
@@
   Using the Markov property of the spine process and properties of Poisson random measures, we have
-\begin{align}\label{eq:epsilon-2}
+\begin{align}
+  \label{eq:epsilon-2}
 	|\epsilon_x^2(t_0,t)|
@@
 On the other hand, according to \eqref{eq: asymptotic for q_t(x,y)} and \eqref{eq: some equations for PY-1-3}, we know that
-\begin{align}\label{eq:epsilon-2-final}
+\begin{align}
+  \label{eq:epsilon-2-final}
 	\dot{\mathbf P}_{\delta_x}^{(\phi)}[ Y^{(t_0,t]}_t(\phi)^{-1}]
@@
   then we have
-\begin{align}\label{eq: change variable using inverse}
+  \begin{align}
+    \label{eq: change variable using inverse}
     v_t(x)
@@
   Further, by Proposition \ref{prop: convergence in a same speed} and the fact that $R(u)\xrightarrow[u\to 0]{} \infty$, we have
-  \begin{align}\label{eq: epsilon R converges to 0}
+  \begin{align}
+    \label{eq: epsilon R converges to 0}
     \sup_{x\in E}|\epsilon_{R(u)}(x)|
@@
   Since $R$ is the inverse of $t\mapsto \langle v_t,\phi^*\rangle$, the above implies that
-\begin{align}\label{eq: integral equation for R}
+  \begin{align}
+    \label{eq: integral equation for R}
     R(r)
@@
   Therefore, from Lemma \ref{lem: asymptotic equivalent of integration}, we have that
-\begin{align}\label{eq: regularly part in the integration}
-	&\big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
-	\\&\quad = \big\langle \kappa (x)\big( 1 + \epsilon_{R(u)}(x)\big )^{\gamma(x)} u^{\gamma(x)} \phi(x)^{\gamma(x)} , \phi^*(x) \big\rangle_{m(dx)}
-	\\ &\quad \stackrel[u\to 0]{}{\sim} \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_{m(dx)}.
+  \begin{align}
+    \label{eq: regularly part in the integration}
+    & \big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
+    \\ & \quad = \big\langle \kappa (x)\big( 1 + \epsilon_{R(u)}(x)\big )^{\gamma(x)} u^{\gamma(x)} \phi(x)^{\gamma(x)} , \phi^*(x) \big\rangle_{m(dx)}
+    \\ & \quad \stackrel[u\to 0]{}{\sim} \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_{m(dx)}.
   \end{align}
@@
     & \big\langle \psi_0 \big(\cdot,( 1 + \epsilon_{R(u)} ) u \phi \big), \phi^* \big\rangle_m
-   \stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x)
-   \rangle_{m(dx)}
+      \stackrel[u\to 0]{}{\sim}  \langle u^{\gamma(x)} , \kappa (x)\phi(x)^{\gamma(x)} \phi^*(x) \rangle_{m(dx)}
     \\ & \quad \stackrel[u\to 0]{}{\sim}  \langle \mathbf 1_{\gamma(x)= \gamma_0}, \kappa (x)\phi(x)^{\gamma_0} \phi^*(x) \rangle_{m(dx)} u^{\gamma_0}
@@
   Finally since $r\mapsto \langle v_r,\phi^*\rangle_m$ is the inverse of $r\mapsto R(r)$, from \cite[Proposition 1.5.15.]{BinghamGoldieTeugels1989Regular} and the above, we have
-\begin{equation}
+  \begin{align}
     \langle v_r,\phi^*\rangle_m
@@
     \qedhere
-\end{equation}
+  \end{align}
 \end{proof}
 
-% ** Characterization of the one dimensional distribution
+% *** Characterization of the one dimensional distribution
 \subsection{Characterization of the one dimensional distribution}
 \label{sec: conditional distribution}
-Let $\{(X_t)_{t\geq 0}; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying
-Assumptions \ref{asp: 1}--\ref{asp: 4}.
+Let $\{(X_t)_{t\geq 0}; \mathbf P\}$ be a $(\xi, \psi)$-superprocess satisfying Assumptions \ref{asp: 1}--\ref{asp: 4}.
 Suppose  $m(x: \gamma(x) = \gamma_0)>0$.
@@
 Our guess of $(\eta_t)$ is
-\begin{align}\label{eq: definition of eta}
+\begin{align}
+  \label{eq: definition of eta}
 	\eta_t
@@
 According to Theorem \ref{thm: main theorem}(2) and $1-e^{-x} \stackrel[x\to 0]{}{\sim} x$, this is equivalent to
-\begin{align}\label{eq: equivalent result}
+\begin{align}
+  \label{eq: equivalent result}
 	\frac{\mu\big( V_t(\theta \eta_t f) \big)}{ \eta_t}
@@
 	For any $f\in \mathscr B^+_b(E),\theta \geq 0,x\in E$ and $T>0$, we have
-\begin{align}\label{eq: equation for Vt(theta f) for theta}
+  \begin{align}
+    \label{eq: equation for Vt(theta f) for theta}
     V_T ( \theta f) ( x)
@@
   From this, we have
-\begin{align} \label{eq: dynamic of theta on v_t theta reason 1}
+  \begin{align} 
+    \label{eq: dynamic of theta on v_t theta reason 1}
     \frac{\partial}{\partial \theta}
@@
   On the other hand, if we write $F(s,w):= \mathbf 1_{s\leq T} w_{T-s}(f)$, then by Assumption \ref{asp: 4}, the spine representation, Campbell's formula and \eqref{eq: definition of Gamma function}, we have
-\begin{align}\label{eq: dynamic of theta on v_t theta reason 2}
-	&-\log \dot {\mathbf P}^{(T,f)}_{x}[e^{-\theta \mathbf n_T(F)}|\mathbf m_T^\xi]
+  \begin{align}
+    \label{eq: dynamic of theta on v_t theta reason 2}
+    & -\log \dot {\mathbf P}^{(T,f)}_{x}[e^{-\theta \mathbf n_T(F)}|\mathbf m_T^\xi]
       = \mathbf m_T^\xi(1-e^{-\theta F})
@@
     V_T(\theta f)(x)
-	&= -\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}]
+    & = -\log \mathbf P_{\delta_x}[e^{-\theta X_T(f)}]
       = \int_0^\theta P^\beta_Tf(x)
       \dot {\mathbf P}_x^{(T,f)}[e^{-r  Y_T(f)}] dr
-	\\ &=P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \Big[\exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds\Big\}\Big] dr
+    \\ & =P^\beta_Tf(x)\int_0^\theta \Pi_x^{(T,f)} \Big[\exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s)~ds\Big\}\Big] dr
     \\ &= \phi( x) \int_0^\theta \Pi_x^{(\phi)} \Big[ \frac{ f(\xi_T) } { \phi(\xi_T) } \exp\Big\{ - \int_0^T \big( \kappa \gamma V_{T-s} (r f)^{ \gamma - 1} \big) ( \xi_s) ds\Big\} \Big] dr,
@@
 Replacing $\theta$ with $\theta \eta_T$ in \eqref{eq: equation for Vt(theta f) for theta}, we have
-
-\begin{align}\label{eq: equation for normalized V_T}
-	&\frac{V_T(\theta \eta_T f)(x)}{\eta_T}
-	\\&\quad= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
-	\\&\quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
-	\\&\quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} \exp\Big\{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du\Big\}\Big] dr.
-\end{align}
-
-% ** Proof of main Theorem 3
+\begin{align}
+  \label{eq: equation for normalized V_T}
+  & \frac{V_T(\theta \eta_T f)(x)}{\eta_T}
+	\\ & \quad= \phi(x) \frac{1}{\eta_T}\int_0^{\theta \eta_T} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) } \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
+	\\ & \quad = \phi(x) \int_0^{\theta} \Pi_x^{(\phi)} \Big[ \frac { f(\xi_T) } { \phi(\xi_T) }  \exp\Big\{-\int_0^T \big(\kappa\gamma V_{T-s}(r \eta_T f)^{\gamma-1}\big)(\xi_s) ds\Big\}\Big] dr
+	\\ & \quad = \phi(x)\int_0^{\theta} \Pi_x^{(\phi)} \Big[\frac{f(\xi_T)}{\phi(\xi_T)} \exp\Big\{-T\int_0^1 \big(\kappa\gamma V_{uT}(r \eta_T f)^{\gamma-1}\big)(\xi_{(1-u)T}) du\Big\}\Big] dr.
+\end{align}
+
+% *** Proof of main Theorem 3
 \subsection{Proof of Theorem \ref{thm: main theorem}(3)}
 \label{sec: proof of result 3}
-Consider the $(\xi, \psi)$-superprocess $\{X;\mathbf P\}$ which satisfies
-Assumptions \ref{asp: 1}--\ref{asp: 4}.
+Consider the $(\xi, \psi)$-superprocess $\{X;\mathbf P\}$ which satisfies Assumptions \ref{asp: 1}--\ref{asp: 4}.
 Suppose that $m( x:\gamma(x)=\gamma_0 )>0$.
@@
 We claim that, in order to prove Theorem \ref{thm: main theorem}(3), we only need to show that
-\begin{align}\label{eq: we only need to proof this}
+\begin{align}
+  \label{eq: we only need to proof this}
 	g(t,\theta,x)
@@
 From Lemma \ref{lem: characterize the general Mittag-Leffler distribution}, we have that $G$ satisfies
-\begin{align}\label{eq: equation for G}
+\begin{align}
+  \label{eq: equation for G}
 	G(\theta)
@@
 where
-\begin{align}\label{eq: definition for J_G}
+\begin{align}
+  \label{eq: definition for J_G}
 	J_G(r):=
@@
 According to \eqref{eq: equation for normalized V_T}, we know that $g$ satisfies
-\begin{align}\label{eq: equation for g}
-	g(t,\theta, x)= \int_0^{\theta} \Pi_x^{(\phi)} [ (\phi^{-1}f)(\xi_t) e^{-\frac{1}{\gamma_0 - 1} J_g(t,r,\xi) } ] dr,
+\begin{align}
+  \label{eq: equation for g}
+	g(t,\theta, x)
+  = \int_0^{\theta} \Pi_x^{(\phi)} [ (\phi^{-1}f)(\xi_t) e^{-\frac{1}{\gamma_0 - 1} J_g(t,r,\xi) } ] dr,
 	\quad t\geq 0, \theta \geq 0, x\in E,
@@
 where, for each $t\geq 0$ and $r\geq 0$,
-\begin{align}\label{eq: definition for J_g}
-	J_g(t,r,\xi):=
-	(\gamma_0 - 1)t\int_0^1 \big(  \kappa \gamma \cdot (   \phi \eta_{ut}  )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) (  \xi_{(1-u)t}  ) du.
+\begin{align}
+  \label{eq: definition for J_g}
+	J_g(t,r,\xi)
+  :=(\gamma_0 - 1)t\int_0^1 \big(  \kappa \gamma \cdot (   \phi \eta_{ut}  )^{\gamma - 1} g (ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot )^{\gamma-1}  \big) (  \xi_{(1-u)t}  ) du.
 \end{align}
 For each $t\geq 0$ and $r\geq 0$, define
-\begin{align}\label{eq: definition of J'_G}
-	J'_G(t,r,\xi):=
-	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big) (\xi_{(1-u)t}) du
+\begin{align}
+  \label{eq: definition of J'_G}
+	J'_G(t,r,\xi)
+  :=\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} G\big( ru^{\frac{1}{\gamma_0 - 1}} \big) ^{\gamma_0 - 1} \big) (\xi_{(1-u)t}) du
 \end{align}
 and
-\begin{equation}\label{eq: definition of J'_g}
-	J'_g(t,r,\xi):=
-	\gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \big) (\xi_{(1-u)t})  du.
+\begin{equation}
+  \label{eq: definition of J'_g}
+	J'_g(t,r,\xi)
+  := \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} g\big( ut,ru^{\frac{1}{\gamma_0 - 1}}, \cdot \big)^{\gamma_0 - 1}  \big) (\xi_{(1-u)t})  du.
 \end{equation}
@@
 From \eqref{eq: equation for G} we have
-\begin{align}\label{eq: upper bound for G}
+\begin{align}
+  \label{eq: upper bound for G}
 	G(r)
@@
 From \eqref{eq: definition for J_G} and \eqref{eq: upper bound for G}, we have
-\begin{align}\label{eq: upper bound for J_G}
+\begin{align}
+  \label{eq: upper bound for J_G}
 	J_G(r)
@@
 From \eqref{eq: equation for g}, we have
-\begin{align}\label{eq: upper bound for g}
+\begin{align}
+  \label{eq: upper bound for g}
 	g(t,r, x) \leq c_f r,
@@
 	J_g(t,r, \xi)
-	&\leq \|\kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \int_0^1 \big(  t\eta_{ut}^{\gamma - 1} (ru^{\frac{1}{\gamma_0 - 1}} )^{\gamma-1}  \big) \big(  \xi_{(1-u)t} \big) du
-	\\&= \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \int_0^1 \big(  r^{\gamma - 1}t^{1-\frac{\gamma - 1}{\gamma_0 - 1}}  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}  \big) \big( \xi_{(1-u)t} \big) du
-	\\& \leq \max\{1,r\} \cdot \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \Big\|  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}\Big\|_\infty
-	\\& =: c_2 \cdot \max  \{1,r\},
+	& \leq \|\kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \int_0^1 \big(  t\eta_{ut}^{\gamma - 1} (ru^{\frac{1}{\gamma_0 - 1}} )^{\gamma-1}  \big) \big(  \xi_{(1-u)t} \big) du
+	\\ & = \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \int_0^1 \big(  r^{\gamma - 1}t^{1-\frac{\gamma - 1}{\gamma_0 - 1}}  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}  \big) \big( \xi_{(1-u)t} \big) du
+	\\ & \leq \max\{1,r\} \cdot \| \kappa \cdot (c_f\phi)^{\gamma - 1} \|_\infty \Big\|  \big( C_X (\gamma_0 - 1) \big)^{-\frac{\gamma - 1}{\gamma_0 - 1}}\Big\|_\infty
+	\\ & =: c_2 \cdot \max  \{1,r\},
        \quad t\geq 1, r\geq 0.
@@
 	J'_g(t,r,\xi)
-	&\leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} (c_f ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
-	\\&\leq \gamma_0(\gamma_0 - 1) c_f^{\gamma_0 - 1}r^{\gamma_0 - 1} \|  \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \|_\infty \int_0^1 t \big( C_X(\gamma_0 - 1) ut \big)^{- 1} u du
-	\\&=: c_3 \cdot r^{\gamma_0 - 1},
+	& \leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} (c_f ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
+	\\ & \leq \gamma_0(\gamma_0 - 1) c_f^{\gamma_0 - 1}r^{\gamma_0 - 1} \|  \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \|_\infty \int_0^1 t \big( C_X(\gamma_0 - 1) ut \big)^{- 1} u du
+	\\ & =: c_3 \cdot r^{\gamma_0 - 1},
        \quad t\geq 0, r\geq 0.
@@
 From \eqref{eq: definition of eta}, \eqref{eq: definition of J'_G} and \eqref{eq: upper bound for G}, we have $\Pi^{(\phi)}_\cdot$-almost surely
-\begin{align}\label{eq: upper bound for J'_G}
+\begin{align}
+  \label{eq: upper bound for J'_G}
 	J'_G(t,r,\xi)
 	& \leq \gamma_0 (\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} (ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1}\big) (\xi_{(1-u)t}) du
-	\\ &\leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
-	\\ &=: c_4 \cdot r^{\gamma_0 - 1},
+	\\ & \leq \gamma_0(\gamma_0 - 1) r^{\gamma_0 - 1} \big\|   \mathbf 1_{\gamma(\cdot) = \gamma_0}  \kappa \phi^{\gamma_0 - 1} \big\|_\infty \int_0^1 t \big(  C_X(\gamma_0 - 1) ut \big)^{- 1}  u  du
+	\\ & =: c_4 \cdot r^{\gamma_0 - 1},
        \quad t\geq 0, r\geq 0.
@@
 
-Step 2: We will show that, for each $t\geq 0, \theta \geq 0,$ and $x\in E$
+Step 2: 
+We will show that, for each $t\geq 0, \theta \geq 0,$ and $x\in E$
 \begin{align}
@@
 \begin{align}
-\begin{aligned}
     I_1(t,\theta,x)
@@
     &:= \Big\| \|  J'_G(t,r,\xi) - J'_g(t,r,\xi)  \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
-\end{aligned}
 \end{align}
@@
 	g(t,\theta,x)^{\gamma_0 - 1}
-	=\Big\| \| (\phi^{-1}f)(\xi_t) ^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
+	= \Big\| \| (\phi^{-1}f)(\xi_t) ^{\gamma_0 - 1} e^{-J_g(t,r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}},
 	\quad t\geq 0, \theta \geq 0, x\in E.
@@
 \begin{align}
-	&|  G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
+	& | G(\theta)^{\gamma_0 - 1} - g(t,\theta,x)^{\gamma_0 - 1} |
 	\\ & \quad \leq \Big\| e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_g(t, r,\xi)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
@@
 
-Step 3: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
+Step 3: 
+We will show that, for each $\theta \geq 0$ and $x\in E$, $I_1(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
 Notice that, by \eqref{eq:q(t,x,y)} and since $\langle f,\phi^* \rangle_m = 1$,
@@
 \begin{align}
-	&e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
-	\\&\quad =e^{ - J_G(r)} \Big( 1   -  \Pi_x^{(\phi)}[ (\phi^{-1}f)(\xi_t) ]^{\gamma_0 - 1}   \Big)
+	& e^{ - J_G(r)} - \| (\phi^{-1}f)(\xi_t)^{\gamma_0 - 1} e^{-J_G(r)} \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}}
+	\\ & \quad =e^{ - J_G(r)} \Big( 1   -  \Pi_x^{(\phi)}[ (\phi^{-1}f)(\xi_t) ]^{\gamma_0 - 1}   \Big)
        \xrightarrow[t\to \infty]{} 0,
@@
 
-Step 4: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_2(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
+Step 4: 
+We will show that, for each $\theta \geq 0$ and $x\in E$, $I_2(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
 Notice that, according to \eqref{eq: definition for J_G} and \eqref{eq: definition of J'_G}, for each $t\geq 0$ and $r\geq 0$,
@@
 According to \eqref{eq: upper bound for J_G} and \eqref{eq: upper bound for J'_G}, we have that, for each $r\geq 0$ and $t\geq 0$,
-\begin{align} \label{eq: upper bound for J_G - J'_G}
+\begin{align} 
+  \label{eq: upper bound for J_G - J'_G}
 	\big| J_G(r) - J'_G(t,r,\xi)\big|
@@
 
-Step 5: We will show that, for each $\theta \geq 0$ and $x\in E$, $I_4(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
+Step 5: 
+We will show that, for each $\theta \geq 0$ and $x\in E$, $I_4(t,\theta,x) \xrightarrow[t\to \infty]{} 0$.
 We first note that, for each $t\geq 0$ and $r\geq 0$, we have
-\begin{align}\label{eq: expression for J_g - J'_g}
+\begin{align}
+  \label{eq: expression for J_g - J'_g}
 	J_g(t,r,\xi) - J'_g(t,r,\xi)
@@
 We then note that, according \eqref{eq: upper bound for g} and the definition of $\eta_t$, for each $r\geq 0$, $u\in (0,1)$ and $x\in E$, we have
-\begin{align}\label{eq: integer in the expression of J_g - J'_g convergences to 0}
-	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
-	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \eta_{ut}^{\gamma(x) - 1} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
-	\\&\quad = (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \big( C_X(\gamma_0 - 1) ut\big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
-	\\&\quad \leq (\gamma_0 - 1) \mathbf 1_{\gamma(x) > \gamma_0} t^{1-\frac{\gamma(x) - 1}{\gamma_0 - 1}}\big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}
-	\\&\quad \xrightarrow[t\to \infty]{} 0.
+\begin{align}
+  \label{eq: integer in the expression of J_g - J'_g convergences to 0}
+	& (\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
+	\\ & \quad \leq (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \eta_{ut}^{\gamma(x) - 1} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
+	\\ & \quad = (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \mathbf 1_{\gamma(x) > \gamma_0} t \big( C_X(\gamma_0 - 1) ut\big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}} u^{\frac{\gamma(x) - 1}{\gamma_0 - 1}}
+	\\ & \quad \leq (\gamma_0 - 1) \mathbf 1_{\gamma(x) > \gamma_0} t^{1-\frac{\gamma(x) - 1}{\gamma_0 - 1}}\big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}
+	\\ & \quad \xrightarrow[t\to \infty]{} 0.
 \end{align}
 This also gives an upper bound: For each $r\geq 0$, $u \in (0,1)$, $x\in E$ and $t\geq 1$, we have
-\begin{align}\label{eq: upper bound for the integrator of J_g - J'_g}
-	&(\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
-	\\&\quad \leq (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
+\begin{align}
+  \label{eq: upper bound for the integrator of J_g - J'_g}
+	& (\gamma_0 - 1)t  \mathbf 1_{\gamma(x)> \gamma_0}  \kappa(x)\gamma(x) \big(   \phi(x) \eta_{ut}   \big)^{\gamma(x) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},x \big)^{\gamma(x)-1}
+	\\ & \quad \leq (\gamma_0 - 1) \big\| \kappa \gamma \cdot (c_f r\phi)^{\gamma - 1}\big\|_\infty \sup_{x\in E} \big( C_X(\gamma_0 - 1) \big)^{-\frac{\gamma(x) - 1}{\gamma_0 - 1}}.
 \end{align}
@@
 \begin{align}
-	(y,u,t)\mapsto (\gamma_0 - 1)t  \mathbf 1_{\gamma(y)> \gamma_0}  \kappa(y)\gamma(y) \big(   \phi(y) \eta_{ut}   \big)^{\gamma(y) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},y \big)^{\gamma(y)-1},
+	(y,u,t)
+  \mapsto (\gamma_0 - 1)t  \mathbf 1_{\gamma(y)> \gamma_0}  \kappa(y)\gamma(y) \big(   \phi(y) \eta_{ut}   \big)^{\gamma(y) - 1} g \big(ut,ru^{\frac{1}{\gamma_0 - 1}},y \big)^{\gamma(y)-1},
 \end{align}
@@
 According to \eqref{eq: expression for J_g - J'_g} and \eqref{eq: upper bound for the integrator of J_g - J'_g}, for each $r\geq 0$ and $t\geq 1$, we have that
-\begin{equation}\label{eq: upper bound for J_g - J'_g}
+\begin{equation}
+  \label{eq: upper bound for J_g - J'_g}
 	\big |	J_g(t,r,\xi) - J'_g(t,r,\xi)  \big |
@@
 
-Step 6: We will show that
+Step 6: 
+We will show that
 \begin{align}
@@
 Notice that, according to \eqref{eq: upper bound for G} and \eqref{eq: upper bound for g}, we have the following bound:
-\begin{align}\label{eq: upper bound for M(t,r,x)}
+\begin{align}
+  \label{eq: upper bound for M(t,r,x)}
 	M(t,r,x)
@@
 	\label{eq: differences between J'_G and J'_g}
-	&|J'_G(t,r,\xi) - J'_g(t,r,\xi)|
-	\\&\quad \leq \gamma_0(\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du
-	\\&\quad = \gamma_0 C_X^{-1}\int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa  \phi^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du.
+	& |J'_G(t,r,\xi) - J'_g(t,r,\xi)|
+	\\ & \quad \leq \gamma_0(\gamma_0 - 1) t \int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \cdot (\phi \eta_{ut})^{\gamma_0 - 1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du
+	\\ & \quad = \gamma_0 C_X^{-1}\int_0^1 \big( \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa  \phi^{\gamma_0 - 1}  u^{-1} M(ut,ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}\big)(\xi_{(1-u)t}) du.
 \end{align}
@@
 Now, according to Lemma \ref{lem: Fatou-ergodic lemma for the uderlying process}, \eqref{eq: differences between J'_G and J'_g} and the definitions of $M(r,x), M(r)$ and $C_X$, we have
-\begin{align}\label{eq: limsup of J_G - J'_g}
-	&\limsup_{t\to \infty} \| J_G'(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{\phi};\frac{1}{\gamma_0 - 1}}
-	\\& \quad \leq  \gamma_0 C_X^{-1} \int_0^1 \big\langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} M(ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}, \phi\phi^* \big\rangle_m \frac{du}{u}
-	\\& \quad \leq  \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}.
+\begin{align}
+  \label{eq: limsup of J_G - J'_g}
+	& \limsup_{t\to \infty} \| J_G'(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{\phi};\frac{1}{\gamma_0 - 1}}
+	\\ & \quad \leq  \gamma_0 C_X^{-1} \int_0^1 \big\langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0 - 1} M(ru^{\frac{1}{\gamma_0 - 1}},\cdot)^{\gamma_0 - 1}, \phi\phi^* \big\rangle_m \frac{du}{u}
+	\\ & \quad \leq  \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}.
 \end{align}
@@
 \begin{align}
-	&\limsup_{t\to \infty} I_3(t,\theta, x)
+	& \limsup_{t\to \infty} I_3(t,\theta, x)
    \leq \big\| \limsup_{t\to \infty} \|    J'_G(t,r,\xi) - J'_g(t,r,\xi) \|_{\Pi_x^{(\phi)};\frac{1}{\gamma_0 - 1}} \big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad\leq \Big\| \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
-	\\&\quad = \gamma_0 \bigg( \int_0^\theta \Big (   \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}   \Big )^{\frac{1}{\gamma_0 - 1}} dr \bigg)^{\gamma_0 - 1}
-	\\&\quad = \gamma_0 \Big(  \int_0^\theta  \| M(r u^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1},
+	\\ & \quad\leq \Big\| \gamma_0  \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \Big\|_{\mathbf 1_{0\leq r\leq \theta} dr;\frac{1}{\gamma_0 - 1}}
+	\\ & \quad = \gamma_0 \bigg( \int_0^\theta \Big (   \int_0^1  M(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u}   \Big )^{\frac{1}{\gamma_0 - 1}} dr \bigg)^{\gamma_0 - 1}
+	\\ & \quad = \gamma_0 \Big(  \int_0^\theta  \| M(r u^{\frac{1}{\gamma_0 - 1}}) \|_{\mathbf 1_{0\leq u\leq 1}\frac{du}{u};\gamma_0 - 1}  dr\Big)^{\gamma_0 - 1},
 	\quad \theta \geq 0, x\in E.
@@
 
-Step 7: We will show that $M(\theta) = 0$ for each $\theta \geq 0$.
+Step 7: 
+We will show that $M(\theta) = 0$ for each $\theta \geq 0$.
 We first claim that
@@
 
-Step 8: Finally, $M \equiv 0$ clearly implies that $\lim_{t\to \infty} I_3(t,\theta, x) = 0$, and thus completes the verification of \eqref{eq: we only need to proof this}.
-
+Step 8: 
+Finally, $M \equiv 0$ clearly implies that $\lim_{t\to \infty} I_3(t,\theta, x) = 0$, and thus completes the verification of \eqref{eq: we only need to proof this}.
+
+% * Appendix
 \appendix
 \section{}
+% ** Examples
 \subsection{Examples}
@@
 
-In this Subsection, we briefly recall from \cite{RenSongZhang2015Limit} some examples of Markov processes satisfying Assumptions \ref{asp: 1} and \ref{asp: 3}. We will not try to give the most
-general examples. For details and more examples, we refer our readers to \cite{RenSongZhang2015Limit}.
+In this Subsection, we briefly recall from \cite{RenSongZhang2015Limit} some examples of Markov processes satisfying Assumptions \ref{asp: 1} and \ref{asp: 3}. 
+We will not try to give the most general examples. 
+For details and more examples, we refer our readers to \cite{RenSongZhang2015Limit}.
 
@@
   Suppose that, in the case $d\ge 2$, the spherical part $\eta$ of the L\'evy measure $\mu$ of $\xi^{(1)}$ satisfies the following assumption: 
-  there exist a positive function $\Phi$ on the unit sphere $S$ in $\mathbb{R}^d$ and $\kappa>1$
-such that
+  there exist a positive function $\Phi$ on the unit sphere $S$ in $\mathbb{R}^d$ and $\kappa>1$ such that
   \begin{align}
@@
   measure of $\xi^{(1)}$ is given by
-$$
+  \begin{align}
     \mu(dx)=c_1x^{-1-\beta}1_{\{x>0\}}+ c_2|x|^{-1-\beta}1_{\{x<0\}}
-$$
-with $c_1, c_2>0$. Suppose that $E$ is a bounded open set in $\mathbb{R}^d$
-and $m$ is the Lebesgue measure on $E$.
+  \end{align}
+  with $c_1, c_2>0$. Suppose that $E$ is a bounded open set in $\mathbb{R}^d$ and $m$ is the Lebesgue measure on $E$.
   Let $\xi$ be the process in $E$ obtained by killing $\xi^{(1)}$ upon exiting $E$.
@@
 
+% *** Analytical results
 \subsection{Analytical results}
@@
 
-\begin{lem}\label{lem: F is zero}
+\begin{lem}
+  \label{lem: F is zero}
+  Suppose that $\alpha \in (1,2)$.
   Suppose that $F$ is a non-negative function on $[0,\infty)$ satisfying the property that there exists a constant $C>0$ such that  $F(\theta) \leq C\theta$ for all $\theta \geq 0$ and
@@
   \begin{align}
-    &F(\theta)
+    & F(\theta)
       \leq C \int_0^\theta \big\|  F(ru^{ \frac{1}{\alpha - 1}  })\big\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
       \leq C \int_0^\theta \Big\|  \frac{1}{k!}(Cru^{ \frac{1}{\alpha - 1}  })^k \Big\|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} dr
-    \\ &\leq \frac{C^{k+1}}{k!} \Big(\int_0^\theta r^k dr\Big) \cdot \|u^{\frac{k}{\alpha - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
+    \\ & \leq \frac{C^{k+1}}{k!} \Big(\int_0^\theta r^k dr\Big) \cdot \|u^{\frac{k}{\alpha - 1}} \|_{\mathbf 1_{0<u<1}\frac{du}{u}; \alpha - 1} \leq \frac{C^{k+1} \theta^{k+1}}{(k+1)!},
   \end{align}
@@
 
-\begin{lem} \label{lem: characterize the general Mittag-Leffler distribution}
+\begin{lem} 
+  \label{lem: characterize the general Mittag-Leffler distribution}
   Suppose that $\alpha \in (1,2).$
   The non-linear delay equation
-  \begin{align} \label{eq: equation for the distribution}
+  \begin{align} 
+    \label{eq: equation for the distribution}
     G( \theta)
@@
 	has a unique solution:
-  \begin{align}\label{eq: solution for the equation}
+  \begin{align}
+    \label{eq: solution for the equation}
     G(\theta)
@@
     \frac{d}{d\theta}G(\theta)
-    &= - \frac{1}{\alpha - 1} \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{1}{\alpha - 1} - 1} \frac{d}{d\theta} \theta^{-(\alpha - 1)}
-    \\& =  \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{\alpha}{\alpha - 1} } \theta^{-\alpha}.
+    & = - \frac{1}{\alpha - 1} \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{1}{\alpha - 1} - 1} \frac{d}{d\theta} \theta^{-(\alpha - 1)}
+    \\ & =  \big(1+\theta^{-(\alpha - 1)}\big)^{- \frac{\alpha}{\alpha - 1} } \theta^{-\alpha}.
   \end{align}
@@
   \begin{align}
-    &|G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|
-    \\&\quad = \Big| \|e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta} dr; \frac{1}{\alpha - 1}} - \|e^{-\alpha \int_0^1 G_0(ru^{ \frac{1} {\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\alpha - 1}} \Big|
+    & |G(\theta)^{\alpha - 1} - G_0(\theta)^{\alpha - 1}|
+    \\ & \quad = \Big| \|e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta} dr; \frac{1}{\alpha - 1}} - \|e^{-\alpha \int_0^1 G_0(ru^{ \frac{1} {\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1}{\alpha - 1}} \Big|
     \\ & \quad \leq \| e^{-\alpha \int_0^1 G(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} - e^{-\alpha \int_0^1 G_0(ru^{\frac{1}{\alpha - 1}})^{\alpha - 1} \frac{du}{u}} \|_{\mathbf 1_{0<r<\theta}dr;\frac{1} {\alpha - 1}}
@@
 
+% ** Acknowledgment
 \subsection*{Acknowledgment:}
@@
   Kim, P., Song, R. and Vondracek, Z.:
-
   \emph{Potential theory of subordinate Brownian motions with Gaussian components.}
